### 2023-11-24 sections/0intro.tex
Add files via upload

\documentclass[../text]{subfiles}

\begin{document}

\section{Introduction}

In this work we will explore the concepts of factorization algebras and factorization homology over stratified spaces. These two concepts, which at first sight will looks very different, will turn out to be closely related. We will strive to keep the discussion at the level of stratified spaces, while making a comparison to results in the smooth case. Some results we will meet have been proven in the smooth case, but with methods which do not (at the present moment) generalize to the stratified case. We will endeavor to point these out and give proofs that hold more generally. The outline of the text is as follows:

\textbf{\Cref{ch:strat_spaces} Stratified Spaces:} The first section deals with setting up the theory of stratified spaces that we will use. It is essentially a recap of the necessary results from the work of Ayala, Francis and Tanaka \cite{aft_localstrut}, which is one of our main sources. The idea and fundamentals of stratified spaces have existed for a long time in different incarnation beginning with the work of Whitney \cite{whitney92}. The reason why we choose to work with this particular version of stratified spaces is due to them supporting a notion of conical smoothness that is a generalization of smoothness of manifolds. Furthermore, the theory of factorization homology has been developed with these spaces in mind, which eases the process of extending certain results to the stratified case much easier. We will not go into the full details that this incarnation of the theory has to offer, but instead we will only mention results that we will make use of later on. Beyond, conical smoothness, this will include tangential structure and its stratified generalization, together with the packaging of both of these data into the concept of an $\infty$-category of basic singularity types. For the proofs of these statements the reader is encouraged to check \cite{aft_localstrut}.

\textbf{\Cref{ch:fact_hom} Factorization Homology:} The second section will present the theory of factorization homology. Similar to the first section this will mostly be a recap of useful results developed by Ayala, Francis and Tanaka. Specifically, the stratified space results can be found in \cite{aft_fhstrat}, while the results for topological manifolds can be found in \cite{af_fhtop}. For the purposes of the theory we will need the concept of (structured) disk algebras, since this will be the algebraic input. Factorization homology will then return an invariant of a manifold. We will explore the key example of factorization homology over the closed, oriented interval $[-1,1]$, and see how this gives rise to the algebraic concept of the two-sided bar construction. More generally, this underpins the theory because it codifies the property of $\otimes$-excision. Finally, we will also state a classification result about a certain type of disk algebras with stratified structure.

\textbf{\Cref{ch:fact_alg} Factorization Algebras:} The third section introduces the concept of factorization algebras, together with its different variations, like prefactorization algebras and locally constant factorization algebras. Of these, the locally constant factorization algebras will be the ones that capture the different possible stratified structure that a manifold can have, and they will be a large focus of the work. The definitions of these will not be novel. They can be found in the works \cite{cg2016}, \cite{ginot2015} and even \cite{af_primer}. In fact, in the slightly different context of vertex algebras the idea can be traced back to \cite{bd2004}. However, all of the above works take a slightly different perspective in their presentation of the definitions, which we hope to unite in this work. The key result of this section is \cref{thm:disk_alg=lcfa}
%
\begin{theorem}
    There is an equivalence of $\infty$-categories between locally constant factorization algebras over a stratified manifold $M$ and $\disk_{/M}$-algebras
    %
    \begin{equation}
        \int: \alg{\disk_{/M}} (\catC) \xrightarrow{\ \ \simeq \ \ } \lcfa_M (\catC),
    \end{equation}
    %
    given by factorization homology,
\end{theorem}
%
as well as its corollary \cref{cor:disk_alg=falg} for the case of ordinary factorization algebras. These show that the $\infty$-operad governing factorization algebras can be taken to be the slice $\infty$-operad $\disk_{/M}$ (or $\disk[r]_{/M}$ for the ordinary case). We then introduce some operations that we can do with factorization algebras like the pushforward and restriction, as well as state a result for locally constant factorization algebras on product spaces. Finally, we will examine some examples of factorization algebras whose construction is known, specifically, locally constant factorization algebras on the intervals $(-1,1)$, $[-1,1)$ and $[-1,1]$ as well as Euclidean spaces $\mathbb{R}^n$ more generally.

\textbf{\Cref{ch:gluing_disk_alg} Collar-gluings and Disk Algebras:} The fourth section presents a novel result about the behavior of certain types of disk algebras under the operation of collar-gluing in the manifold variable. It essentially shows that one can reproduce a disk algebra on a stratified manifold if we know it on some particular pieces of it together with the data of how to glue them. Formally, we have
%
\begin{theorem}
    Given a collar-gluing of stratified manifolds $f: M \rightarrow [-1,1]$, the $\infty$-category of $\disk_{/M}$-algebras is equivalent to the pullback of $\infty$-categories
    %
    \begin{equation}
        \alg{\disk_{/M}} (\catC) \simeq \alg{\disk_{/M_-}} (\catC) \bigtimes_{\alg{\disk_{/M_0 \times \mathbb{R}}} (\catC)} \alg{\disk_{/M_+}} (\catC).
    \end{equation}
\end{theorem}
%
Together with the results of the previous section this gluing holds for locally constant factorization algebras too, and it hugely expands the number of manifolds for which the $\infty$-category of locally constant factorization algebras can be specified. As a small example, it gives a way work on the spheres $S^n$.

\textbf{\Cref{ch:classif_defect_mfld} Classifying $\lcfa$s on Defect Manifolds:} The fifth section focuses on the stratified structure and gives a way to express what effect this has on the locally constant factorization algebras. Specifically, we look the data of a smooth manifold $M$ with a distinguished, properly embedded submanifold $\sigma$ (also known as a defect) as the data of a stratified manifold $M_\Sigma$. We will show that, along with giving algebras associated to the different pieces, locally constant factorization algebras on these manifolds, in some sense, also encode a module structure associated with $\Sigma$.

\textbf{Further Questions:} The exploration below naturally leads to questions that are beyond the scope of this work. As we will see, factorization algebras only need a topological space to be defined, but locally constant factorization algebras also capture information about the stratified structure. Neither of these, however, capture information about the tangential structure of the manifold, so the question arises:
%
\begin{itemize}
    \item Does there exist a version of factorization algebras that capture information both about the stratified structure of a manifold and about its tangential structure?
\end{itemize}
%
In a similar vein, \cite{cg2016} explain why it's important to have the concept of a $G$-equivariant factorization algebra, where $G$ is a Lie group. In particular, according to them, this asks for some definition of a smooth action of $G$ on factorization algebras.
%
\begin{itemize}
    \item Is there a suitable way to encompass this notion in the formalism presented here?
\end{itemize}

\subsection{Conventions on \texorpdfstring{$\infty$}{infinity}-categories}

The $\infty$-categories in this work will use the quasi-category model of $\infty$-category theory introduced by Joyal in \cite{joyal}, which is based on the simplicial sets introduced by \cite{bv73}. The work by Lurie in \cite{lurie_htt} and \cite{lurie_ha} greatly builds on this theory, and questions about fundamental objects or constructions that are in this text will always be answered in those references. This choice is because a great deal of the theory of factorization homology, as well as factorization algebras deal with $\infty$-categories of functors, which are most easily defined for quasi-categories.

It is also important to note that we will not be making a notational distinction between topological categories, Kan enriched categories and $\infty$-categories because of the functors
%
\begin{equation}
    \{ \mathsf{Top}\mathrm{-categories}\} \xrightarrow{\mathsf{Sing}} \{ \mathsf{Kan}\mathrm{-categories}\} \xrightarrow{\mathsf{N}} \cat,
\end{equation}
%
which are both equivalences in appropriate ways. In particular, we will not distinguish notationally the nerve of an ordinary category from the ordinary category itself. Similarly, we will not distinguish between multicategories and their $\infty$-operadic nerve.

\end{document}

### 2023-11-24 sections/1stratified.tex
Add files via upload

\documentclass[../text]{subfiles}

\begin{document}

\section{Stratified Spaces}\label{ch:strat_spaces}

The spaces that this work will be set in will very often be stratified spaces. Thus, we first need to define what we mean by this concept. There are multiple definitions of stratified spaces in the literature, all of which have their advantages and disadvantages. For our purposes, we will follow the account of \cite{aft_localstrut}. The majority of the work on factorization homology has so far been elaborated using this particular set of definitions, and similarly the stratified spaces used in the literature on factorization algebras are usually subsumed too. Here we will only recap the results that will be of use to us. Further details are, of course, discussed in \cite{aft_localstrut}, where one can find a great explanation of the definitions that are needed, and detailed proofs of the theorems that can be proven.

\subsection{Fundamentals of Stratified Spaces}

\begin{definition}
    We will regard posets as topological spaces by declaring that a map $P \rightarrow P'$ is continuous if, any only if it is a map of posets. This means that we declare a subset $U \subset P$ to be open if for all $a \in U$, any $b \geq a$ is also in $U$. This gives a fully faithful functor
    %
    \begin{equation}
        \mathsf{Poset} \xhookrightarrow{} \mathsf{Top}.
    \end{equation} 
\end{definition}

\begin{definition}[\cite{lurie_ha}]
    Let $P$ be a poset. A \emph{$P$-stratified space} is a topological space $X$ together with a map $X \rightarrow P$, which we call the stratification of $X$. We will sometimes refer to $X$ as the underlying topological space of a stratified space. Furthermore, we denote the preimage of $p \in P$ as $X_p$ and call it the $p$th stratum of $X$.
\end{definition}

\begin{example}
    Any CW complex $X$ can be made into a stratified space $X \rightarrow \mathbb{N}$, which sends all points in $X_{\leq k} \setminus {X_{\leq k-1}}$ to $k$, where $X_{\leq k}$ is the $k$-skeleton of $X$.
\end{example}

\begin{example}
    Inspired by the previous example, any topological space $X$ with a filtration by closed subsets $\emptyset \subset X_{\leq 0} \subset \dots \subset X_{\leq n} = X$, is a stratified space, because the filtration induces a map $X \rightarrow \mathbb{N}$, which sends $X_{\leq i} \setminus X_{\leq i-1}$ to $i$.
\end{example}

\begin{remark}
    Given two stratified spaces $X \xrightarrow{s} P$ and $X' \xrightarrow{s'} P'$, we can form the product stratified space $X \times X' \xlongrightarrow{s \times s'} P \times P'$, where the partial order on the product poset is given by $(p,p') \leq (q, q') \iff (p \leq q) \land (p' \leq q')$.
\end{remark}

\begin{example}
    Consider the poset $[1] = \{0 < 1\}$, and the topological space $\hoint$. The standard stratification that we will give to this space is given by $\hoint \rightarrow [1]$, that sends $0 \mapsto 0$ and $0 \neq x \mapsto 1$. This space will play an important role for factorization algebras later on.
\end{example}

\begin{definition}
    Let $X \rightarrow P$ and $X' \rightarrow P'$ be two stratified spaces. A \emph{continuous stratified map} (or \emph{map of stratified spaces}) is a commutative diagram in $\mathsf{Top}$
    %
    \begin{equation}
        \begin{tikzcd}
            X \arrow[r] \arrow[d] & X' \arrow[d] \\
            P \arrow[r] & P'.
        \end{tikzcd}
    \end{equation}
\end{definition}

\begin{example}\label{ex:forget_strat}
    Every stratified space $(X \rightarrow P)$ has a continuous stratified map that forgets the stratification $(X \rightarrow P) \rightarrow (X \rightarrow *)$, giving data equivalent to an unstratified topological space. 
\end{example}

\begin{definition}
    A continuous stratified map $(f: X \rightarrow X', g: P \rightarrow P')$ is an \emph{open embedding} if $f: X \rightarrow X'$ is an open embedding of topological spaces.
\end{definition}

\begin{remark}
    The above definitions give us a natural notion of an open cover $\{ (U_i \rightarrow P_i) \xhookrightarrow{} (X \rightarrow P)\}_{i \in I}$ of a stratified space $(X \rightarrow P)$, namely, whenever both $\{ U_i \xhookrightarrow{} X\}_{i \in I}$ and $\{ P_i \xhookrightarrow{} P \}_{i \in I}$ are open covers.
\end{remark}

Next, we construct the cone of a stratified space. This plays a very important role in the theory of stratified manifolds, since the neighborhoods of these spaces will always look like a cone over some space with a possible further thickening by some $\mathbb{R}^k$. That is, the cones will be the model space for singularities.

\begin{definition}
    Let $X \rightarrow P$ be a stratified space. The cone $\mathsf{C}(X \rightarrow P)$ is the stratified space constructed as follows. At the level of topological spaces we define the pushout in $\mathsf{Top}$
    %
    \begin{equation}
        \mathsf{C}(X) := * \coprod_{X \times \{0\}} X \times \hoint.
    \end{equation}
    %
    At the level of posets we define the pushout in $\mathsf{Poset}$
    %
    \begin{equation}
        \mathsf{C}(P) := * \coprod_{P \times \{ 0\}} P \times [1].
    \end{equation}
    %
    The standard stratification of $\hoint$ together with the obvious map $* \rightarrow *$ induce a stratification $\mathsf{C}(X) \rightarrow \mathsf{C}(P)$ as a map between pushouts. 
\end{definition}

The equivalent of a topological manifold in the stratified setting is a \emph{$C^0$ stratified space}. We will not be fully precise in the definition of these, since this would stray us from our main goal. We will however cite theorems that show that the spaces we consider in this work are $C^0$ stratified spaces. The reason why the below cannot be the actual definition is because it would partially be a cyclic statement. We cite it because it provides good intuition for the structure of $C^0$ stratified spaces.

\begin{definition}
    A \emph{$C^0$ basic}, which we will also often call a \emph{disk}, is a $C^0$ stratified space of the form $\mathbb{R}^k \times \mathsf{C}(Z)$, where $k \geq 0$, $\mathbb{R}^k$ has the trivial stratification, and $Z$ is a compact $C^0$ stratified space.
\end{definition}

\begin{theorem}[{\cite[lem.2.2.2]{aft_localstrut}}]\label{thm:basics_give_basis}
    Let $X$ be a stratified, second countable, Hausdorff space, and consider the collection of open embeddings
    %
    \begin{equation}
        \{ U \xhookrightarrow{} X\},
    \end{equation}
    %
    where $U$ ranges over the $C^0$ basics. Then this collection forms a basis for the topology of $X$ if and only if $X$ is a $C^0$ stratified space.
\end{theorem}

\begin{theorem}[{\cite[cor.2.3.5]{aft_localstrut}}]
    Let $X \rightarrow P$ be a $C^0$ stratified space. For any $p \in P$, the stratified spaces $X_{\leq p}$, $X_{p}$ and $X_{\nless p}$, defined as the relevant preimages, are $C^0$ stratified spaces. Furthermore, $X_p$ is even a topological manifold.
\end{theorem}

\begin{remark}
    Because of the above theorem, $C^0$ stratified spaces $X \rightarrow P$ have a natural filtration by dimension since there is a map $P \rightarrow \mathbb{N}$, which sends $p \mapsto \mathsf{dim}(X_p)$. In our examples of interest we will always choose dimension as the stratification.
\end{remark}

The smooth version of the above concepts also exists and will be the one that is of main interest. As was the case for $C^0$ stratified spaces, we will not give the precise definition of a \emph{conically smooth stratified space} (or \emph{stratified manifold} for short), since the exact definition is involved. The idea, though, is the same as for smooth manifolds.

A stratified manifold is a $C^0$ stratified space $M$ equipped with an atlas
%
\begin{equation}
    \{\mathbb{R}^{k_\alpha} \times \mathsf{C}(Z_\alpha) \hookrightarrow M\}_\alpha,
\end{equation}
%
whose elements we call basics. This atlas has to be a basis for the topology of $X$, and the transitions maps, open embeddings among basics, have to be conically smooth. General maps of stratified manifolds will then be conically smooth if their representatives in basics are conically smooth.

The reason why the definition is involved is, because unlike in the smooth case the presence of the compact spaces $Z_\alpha$ means that we have to use induction to define conical smoothness.

In lieu of a definition we give the following illuminating example:
%
\begin{example}
    Smooth manifolds fall under the definition of stratified manifolds as those that only have one stratum. A smooth map $f$ between compact smooth manifolds gives rise to a conically smooth map $\mathsf{f}$ between the cones of these manifolds. If we also have a smooth map between Euclidean spaces $g$ then the map $h \times \mathsf{C}(f)$ is also conically smooth. This already allows us to describe stratified manifolds with two strata.
\end{example}

The next    classes of conically smooth maps will be present throughout this work.

\begin{definition}
    Let $f: M \rightarrow N$ be a conically smooth map.
    %
    \begin{enumerate}
        \item $f$ is an \emph{open embedding} if it is an open map that is conically diffeomorphic onto its image.
        \item $f$ is a \emph{refinement} if it's a homeomorphism of underlying topological spaces, and it's restriction to each stratum of $M$ is an embedding.
        \item Let $P_N$ be the stratifying poset of $N$. $f$ is a \emph{constructible bundle} if, for each $p \in P_N$, the restriction $f|_p: M|_{f^{-1} N_p} \rightarrow N_p$ is a fiber bundle of stratified spaces.
    \end{enumerate}
\end{definition}

\begin{remark}
    We will also on occasion use the concept of \emph{weakly constructible bundle}, which is a continuous stratified map $f: M \rightarrow N$ which is a constructible bundle out of a refinement of $M$, i.e. there is a diagram $M \xleftarrow{r} M' \xrightarrow{s} N$, where there is an equality $f = s \circ r$ of the underlying continuous maps. Constructible bundles are obviously also weakly constructible.
\end{remark}

We will now introduce two versions of the category of stratified manifolds that will be ubiquitous throughout this work.

\begin{definition}
    The ordinary category of stratified manifolds $\mfld[r]$ is the category whose objects are stratified manifolds and whose morphisms are open embeddings between them.
\end{definition}

For the next definition we notice that all standard simplices are stratified manifolds.

\begin{definition}
    $\mfld$ is the $\infty$-category whose objects are stratified manifolds and whose morphisms are open embeddings among them. To get the higher categorical structure we consider a simplicial enrichment over $\mathsf{Set}$-valued presheaves on the unenriched category, so that given two objects $M$ and $N$
    %
    \begin{equation}
        \mathsf{Hom}_{\mfld} (M, N): [p] \mapsto \mathsf{Map}_{/\Delta^p} (M \times \Delta^p, N \times \Delta^p),
    \end{equation}
    %
    where $\Delta^p$ is the standard $p$-simplex and $\mathsf{Map}_{/\Delta^p}$ denotes those stratified maps that commute with projecting to $\Delta^p$. It can be shown that this enrichment factors through a $\mathsf{Kan}$-enrichment, which gives the appropriate structure.
\end{definition}

\begin{remark}
    The above definition is not immediately parsable, but it can be shown that reducing to the case of smooth manifolds this definition gives equivalent data to the topological enrichment which to morphism spaces assigns the compact-open topology. 
\end{remark}

\begin{remark}
    There is an obvious inclusion $\mfld[r] \xrightarrow{} \mfld$, which is the identity on objects. In terms of topological categories these categories differ only by the topology of their morphism spaces. The inclusion as a map on morphism spaces is the map from a set with the discrete topology to the same set with a different topology.
\end{remark}

\begin{definition}
    The $\infty$-category of basic singularity types $\bsc \subset \mfld$ is the full $\infty$-subcategory of those objects that are basics.
\end{definition}

\subsection{Stratified Manifolds with Tangential Structure}

In a lot of cases we will want to add to our stratified manifold the data of tangential structure. This, for example, will be the geometric input for factorization homology. Thus, we introduce the concept of tangential structure here, first starting with smooth manifolds and then continuing to the stratified case.

\begin{definition}
    Let $\mfld_n$ be the $\infty$-category defined as a topological category, whose objects are smooth, $n$-dimensional manifolds and whose morphisms are embeddings between them, where the morphism spaces have the compact-open topology. This category can be endowed with a symmetric monoidal structure given by disjoint union.
\end{definition}

Given a smooth, $n$-dimensional manifold $M$, its tangent bundle is a rank-$n$ vector bundle on the manifold, which also makes it a principal $\mathsf{GL}(n)$-bundle. Because of the classification of principal bundles, the tangent bundle of a manifold $M$ can be classified, up to homotopy, by a map called the \emph{tangent classifier}
%
\begin{equation}
    M \xrightarrow{\ \ \tau_M \ \ } \mathsf{BO}(n) \xrightarrow[\simeq]{\mathrm{Gram-Schmidt}} \mathsf{BGL}(n),
\end{equation}
%
where $\mathsf{BO}(n)$ is the classifying space of $\mathsf{O}(n)$. Giving the manifold a $G$-structure, where $G$ is a Lie group with a group homomorphism to $\mathsf{GL}(n)$, is then equivalent to a factorization, up to homotopy, of the tangent classifier through $\mathsf{B}G$, in other words it is a lift $\phi$ of the tangent classifier such that the following diagram is homotopy commutative
%
\begin{equation}
    \begin{tikzcd}[column sep = large]
        & \mathsf{B}G \arrow[d] \\
        M \arrow[ru, dashed, "\phi"] \arrow[r, "\tau_M"] & \mathsf{BO}(n).
    \end{tikzcd}
\end{equation}

It is, in fact, this picture that will generalize to give us tangential structure in the more general case. As a first step, \cite[cor.2.13]{af_fhtop} shows that the tangent classifier can be understood as a functor
%
\begin{equation}
    \tau: \mfld_n \xrightarrow{\mathrm{Yoneda}} \mathsf{PShv}(\mfld_n) \xrightarrow{-|_{\mathbb{R}^n \subset \mfld_n}} \mathsf{PShv}(\mathbb{R}^n) \simeq \mathsf{Spaces}_{/\mathsf{BO}(n)},
\end{equation}
%
and in fact a symmetric monoidal one, where the codomain's symmetric monoidal structure is given by coproduct. Namely, given a smooth manifold $M$, the functor returns the map of spaces $\tau_M:M \rightarrow \mathsf{BO}(n)$.

By fixing a space $B$ with a map $B \rightarrow \mathsf{BO}(n)$ (the role of which was previously played by $\mathsf{B}G$), we can define:
%
\begin{definition}
    The symmetric monoidal $\infty$-category $\mfld_n^B$ of $n$-manifolds with $B$-structure is the pullback of $\infty$-categories
    %
    \begin{equation}
        \begin{tikzcd}
            \mfld_n^B \arrow[dr, phantom, "\ulcorner", very near start] \arrow[r] \arrow[d] & \mathsf{Spaces}_{/B} \arrow[d] \\
            \mfld_n \arrow[r, "\tau"] & \mathsf{Spaces}_{/\mathsf{BO}(n)},
        \end{tikzcd}
    \end{equation}
    %
    where the right vertical arrow is induced by the map $B \rightarrow \mathsf{BO}(n)$.
\end{definition}

\begin{remark}
    Since the tangent classifier $\tau$ is symmetric monoidal, and since the right vertical map is canonically symmetric monoidal with the coproduct on both $\mathsf{Spaces}_{/B}$ and $\mathsf{Spaces}_{/\mathsf{BO}(n)}$, the newly defined $\infty$-category does indeed come with a canonical symmetric monoidal structure.
\end{remark}

\begin{example}
    Classical examples for tangential structure come from principal $G$-bundles as discussed before. Namely, given a Lie group $G$ together with a smooth homomorphism $G \rightarrow \mathsf{GL}(n) \simeq \mathsf{O}(n)$, we have an induced map of spaces $\mathsf{B}G \rightarrow \mathsf{BO}(n)$, which gives rise to the following examples:
    %
    \begin{enumerate}
        \item $(G \rightarrow \mathsf{O}(n)) = (\mathsf{O}(n) \xrightarrow{\mathrm{id}} \mathsf{O}(n))$ reproduces the case of no tangential structure,
        \item $(G \rightarrow \mathsf{O}(n)) = (\mathsf{SO}(n) \xhookrightarrow{} \mathsf{O}(n))$ is the case of oriented smooth manifolds,
        \item $(G \rightarrow \mathsf{O}(n)) = (\mathsf{Spin}(n) \rightarrow \mathsf{SO}(n) \xhookrightarrow{} \mathsf{O}(n))$ is the case of spin structure,
        \item $(G \rightarrow \mathsf{O}(n)) = (* \rightarrow \mathsf{O}(n))$ is the case of framed smooth manifolds.
    \end{enumerate}
\end{example}

Moving on to the stratified setting, we note that the stratified version of the full $\infty$-subcategory $\mathbb{R}^n \subset \mfld_n$ is the $\infty$-category of basic singularity types $\bsc$. We can thus generalize the tangent classifier to this setting as the functor
%
\begin{equation}
    \tau: \mfld \xrightarrow{\mathrm{Yoneda}} \mathsf{PShv}(\mfld) \xrightarrow{-|_{\bsc \subset \mfld}} \mathsf{PShv}(\bsc).
\end{equation}
%
In this case, as in the previous, given a stratified manifold $M$, $\tau(M)$ is the functor that for each basic $U \in \bsc$, assigns the space of stratified smooth open embeddings of $U$ into $M$.

\begin{remark}\label{rem:grothendieck_construction}
    We can say something more about this situation if we use the unstraightening construction \cite[sec.2.2]{lurie_htt} which provides an equivalence between $\mathsf{Spaces}$-valued presheaves on a general $\infty$-category $\catC$ and right fibrations \footnote{More details can be found in the cited references, but for completeness we include the definition of right fibration. A \emph{right fibration} (over $\catC$) is a functor $f:\mathscr{E} \rightarrow \catC$ such that the diagram
    %
    \begin{equation}
        \begin{tikzcd}[ampersand replacement=\&]
            \Lambda^n_i \arrow[r] \arrow[d, hook] \& \mathscr{E} \arrow[d] \\
            \Delta^n \arrow[r] \arrow[ru, dashed] \& \catC        
        \end{tikzcd}
    \end{equation}
    %
    can be filled for any $0 < i \leq n$.} over this $\infty$-category
    %
    \begin{equation}
        \mathsf{PShv}(\catC) \simeq \mathsf{RFib}_{\catC}.
    \end{equation}
    %
    More details on this equivalence in our context can be found in \cite[sec.4.2]{aft_localstrut}
    Appending this equivalence to the definition of the tangent classifier would say that the value of the tangent classifier on a stratified manifold $M$ is given by the right fibration
    %
    \begin{equation}
        \tau_M: \mathsf{Entr}(M) := \bsc_{/M} \rightarrow \bsc,
    \end{equation}
    %
    i.e. the forgetful functor from the slice $\infty$-category. The $\infty$-category $\mathsf{Entr}(M)$ defined here is called the enter-path $\infty$-category of the stratified manifold $M$\footnote{A different version of this $\infty$-cateogry is defined in \cite[app.A.6]{lurie_ha} called the exit-path $\infty$-category of the stratified space $M$. It is shown in the work \cite{afr_homhyp} that this exit-path $\infty$-category is equivalent to the opposite of the enter-path $\infty$-category as defined above.}. In fact the statements that we will make next will take on this perspective for the tangent classifier.
\end{remark}

Having generalized the tangent classifier to stratified manifolds we can now think about adding structure to them. The key realization is that the data which the map of spaces $B \rightarrow \mathsf{BO}(n)$ provided before was the data of a presheaf on $\mathsf{BO}(n)$, standing in as the $\infty$-category of basics with only one object $\mathbb{R}^n$. The analogous construction in the stratified case is to provide a presheaf on $\bsc$, which by \cref{rem:grothendieck_construction} is given by a right fibration over $\bsc$.

\begin{definition}
    An $\infty$-category of basics is a right fibration $\bstr \rightarrow \bsc$
\end{definition}

\begin{definition}
    Given an $\infty$-category of basics $\bstr \rightarrow \bsc$, the $\infty$-category of $\bstr$-manifolds is the pullback
    %
    \begin{equation}
        \begin{tikzcd}
            \mfld(\bstr) \arrow[dr, phantom, "\ulcorner", very near start] \arrow[r] \arrow[d] & (\mathsf{RFib}_{\bsc})_{/\bstr} \arrow[d] \\
            \mfld \arrow[r, "\tau"] & \mathsf{RFib}_{\bsc}.
        \end{tikzcd}
    \end{equation}
\end{definition}

\begin{definition}
    Given an $\infty$-category of basics $\bstr \rightarrow \bsc$, the ordinary category of $\bstr$-manifolds is the further pullback
    %
    \begin{equation}
        \begin{tikzcd}
            \mfld[r](\bstr) \arrow[dr, phantom, "\ulcorner", very near start] \arrow[r] \arrow[d] & \mfld(\bstr) \arrow[d] \\
            \mfld[r] \arrow[r] & \mfld.
        \end{tikzcd}
    \end{equation}
\end{definition}

\begin{remark}
    Specifying to the objects of $\mfld(\bstr)$ (which are also the objects of $\mfld[r](\bstr)$), we have that a $\bstr$-manifold is a stratified manifold $M$ together with a lift $\phi$
    %
    \begin{equation}
        \begin{tikzcd}[column sep = large]
            & \bstr \arrow[d] \\
            \mathsf{Entr}(M) \arrow[ru, "\phi"] \arrow[r, "\tau_M"] & \bsc,
        \end{tikzcd}
    \end{equation}
    %
    i.e. such that the triangle above is homotopy commutative in the $\infty$-category of $\infty$-categories $\cat$. This is how we can encode the stratification information while keeping the basic idea of a lift the same.
\end{remark}

\begin{remark}
    There is an obvious, fully faithful inclusion $\bstr \xhookrightarrow{} \mfld(\bstr)$, just as there was in the case without tangential structure.
\end{remark}

In the case of smooth manifolds we argued that $\mfld_n^B$ was defined in a way that allowed it to inherit disjoint union as a symmetric monoidal structure. A similar argument, found in \cite{aft_fhstrat}, can be made for the stratified case too

\begin{proposition}
    Disjoint union endows $\mfld(\bstr)$ and $\mfld[r](\bstr)$ with a symmetric monoidal structure.
\end{proposition}

\begin{definition}\label{def:collar-gluing}
    A collar-gluing of a stratified manifold $M$ is a weakly constructible bundle $M \xrightarrow{f} [-1,1]$. We denote collar-gluings as
    %
    \begin{equation}
        M \cong M_- \coprod_{M_0 \times \mathbb{R}} M_+,
    \end{equation}
    where $M_- := f^{-1}\left[ -1, 1 \right)$, $M_0 := f^{-1}\{0\}$ and $M_+ := f^{-1} \left( -1, 1 \right]$
\end{definition}

\begin{remark}
    One should think of collar-gluings as analogous to the case of gluing two manifolds with boundary along their boundaries after choosing collars. This is exactly the special thing about them, the overlap region is collared, i.e. looks like a product with $\mathbb{R}$. We also note that the disjoint union is an example of a collar-gluing.
\end{remark}

\begin{theorem}[\cite{aft_localstrut}]\label{thm:decom_strat_man}
    $\mfld(\bstr)$ is generated by $\bstr$ through iteratively forming collar-gluings and taking sequential colimits.
\end{theorem}

\begin{remark}
    \Cref{thm:decom_strat_man} is the analogous theorem to handle decompositions of smooth manifolds. Namely, any compact, smooth manifold can be obtained by handle decomposition, and non-compact smooth manifolds are obtained by sequential colimits of finitary (including compact) smooth manifolds.
\end{remark}

\subsection{Useful \texorpdfstring{$\infty$}{infinite}-categories of Basics}

Along with the already familiar $\infty$-categories of basics $\mathsf{D}_n^{G} := \mathsf{B}G \xrightarrow{\{ \mathbb{R}^n\}} \bsc$, which govern smooth $n$-manifolds with $G$-structure, we introduce a few more $\infty$-categories of basics that will be useful for us. An $\infty$-category of basics that will play a big role for the development of factorization homology to come, is the particularly simple one describing oriented $1$-manifolds with boundary.

\begin{construction}\label{con:d_1^bor_structure}
    Consider the $\infty$-subcategory $\mathsf{D}_1^{\partial} \subset \bsc$ whose objects are $\mathbb{R}$ and $\hoint$. There is a unique right fibration $\mathsf{D}_1^{\partial, \mathsf{or}} \rightarrow \mathsf{D}_1^{\partial}$, whose fiber over $\mathbb{R}$ is a point $\{ \mathbb{R}\}$, and whose fiber over $\hoint$ is two points $\{ \hoint, {\mathbb{R}_{\leq 0}} \}$. In other words, $\mathsf{D}_1^{\partial, \mathsf{or}}$ has objects $\mathbb{R}$, $\hoint$ and $\mathbb{R}_{\leq 0}$ with their canonical orientations, and the morphisms are orientation preserving embeddings between them. In this way, $\mathsf{D}_1^{\partial, \mathsf{or}}$ is the $\infty$-category of basics that describes oriented (or, equivalently in this case, framed), smooth 1-manifolds with boundary.
\end{construction}

Another type of stratified manifold that we will focus on heavily in this work is the case of a smooth manifold with a distinguished, properly embedded, smooth submanifold, which we alternatively call a \emph{defect}. Even though there is a clear picture of what this means we will now formally describe the $\infty$-category of basics that will give rise to these kinds of manifolds.

\begin{construction}[{\cite[ex.5.2.10]{aft_localstrut}}]
    Let $\mathsf{D}_{d \subset n} \subset \bsc$ be the full $\infty$-subcategory whose objects are $\mathbb{R}^n$ and $\mathbb{R}^{d \subset n} := \mathbb{R}^{n-d} \times \mathsf{C}(S^{n-d-1})$, where $d < n$. We elaborate that the morphism spaces are given as follows:
    %
    \begin{enumerate}
        \item $\mathsf{Hom}_{\mathsf{D}_{d \subset n}} (\mathbb{R}^n, \mathbb{R}^n) = \mathsf{Emb}(\mathbb{R}^n, \mathbb{R}^n)$, the space of smooth embeddings of $\mathbb{R}^n$.
        \item $\mathsf{Hom}_{\mathsf{D}_{d \subset n}} (\mathbb{R}^{d \subset n}, \mathbb{R}^n) = \emptyset$
        \item $\mathsf{Hom}_{\mathsf{D}_{d \subset n}} (\mathbb{R}^n, \mathbb{R}^{d \subset n}) = \mathsf{Emb}(\mathbb{R}^n, \mathbb{R}^n \setminus \mathbb{R}^d)$, the space of embeddings that miss the defect.
        \item $\mathsf{Hom}_{\mathsf{D}_{d \subset n}} (\mathbb{R}^{d \subset n}, \mathbb{R}^{d \subset n}) \simeq \mathsf{O}(d) \times \mathsf{O}(n-d)$. This final morphism space is given differently compared to the other ones because of intricacies related to smoothness around the defect. For more details on the matter there is a discussion in \cite[ex.5.1.7]{aft_localstrut}.
    \end{enumerate}
    %
    That $\mathsf{D}_{d \subset n} \rightarrow \bsc$ is a right fibration is immediate from the fact that the objects of $\mathsf{D}_{d \subset n}$ have at most one defect, which means that they don't receive maps from basics that are not in $\mathsf{D}_{d \subset n}$ already.
\end{construction}

\begin{definition}\label{def:mfld_disk_dn}
    The $\infty$-category describing smooth, $n$-dimensional manifolds $M$ which carry a properly embedded smooth, $d$-dimensional submanifold $\Sigma$ is given by $\mfld(\mathsf{D}_{d \subset n})$.
\end{definition}

For later purposes we will also need to define a framed version of these manifolds.

\begin{definition}\label{def:framed_d_under_n_sructure}
    The $\infty$-category of basics describing framed $\mathsf{D}_{d \subset n}$-manifolds is given by the pullback of $\infty$-categories
    %
    \begin{equation}
        \begin{tikzcd}
            \mathsf{D}_{d \subset n}^* \arrow[dr, phantom, "\ulcorner", very near start] \arrow[r] \arrow[d] & \mathsf{D_n^*} \simeq * \arrow[d] \\
            \mathsf{D}_{d \subset n} \arrow[r] & \mathsf{D}_n \simeq \mathsf{BO}(n).
        \end{tikzcd}
    \end{equation}
\end{definition}

\begin{remark}
    To explain what the bottom horizontal functor fully is would initially take us into the realm of piecewise linear manifolds, and away from our goal. To not get into those details we note that in fact one can show that $\mathsf{D}_{d \subset n}^* \simeq \Delta^1$ by sending $\mathbb{R}^n \mapsto 0$ and $\mathbb{R}^{d \subset n} \mapsto 1$, which is an extension of the fact that in the case of no defects framings are governed by $ \mathsf{D}_n^* \simeq \Delta^0 \simeq *$.

    Explaining what exactly we mean by a framed stratified manifold is done in \cite[ex.5.2.12]{aft_localstrut}. According to that example, $\mathsf{D}_{d \subset n}^*$-manifolds are described by the data of a framed smooth $n$-manifold $M$, a properly embedded smooth $d$-submanifold $\Sigma$ together with a null-homotopy of the Gauss map $\Sigma \rightarrow \mathsf{Gr}_d(\mathbb{R}^n)$. In more detail, for a general embedded submanifold $\Sigma \xhookrightarrow{} M$ the Gauss map gives the tangent (or equivalently normal) subspace to $\Sigma$ at every point. That is encoded as a map $\Sigma \rightarrow \mathsf{Gr}_d(\mathsf{T}M)$ to the Grassmann bundle of the tangent bundle of $M$. In our case, the framing of $M$ provides a preferred trivialization of the tangent bundle to $\mathbb{R}^n$. A null-homotopy of this map is a trivialization of the tangent (and subsequently also the normal) bundle of $\Sigma$ in a way that is compatible with the trivialization of $\mathsf{T}M$.
\end{remark}

\end{document}

### 2023-11-24 sections/2homology.tex
Add files via upload

\documentclass[../text]{subfiles}

\begin{document}

\section{Factorization Homology}\label{ch:fact_hom}

Factorization homology (also topological chiral homology) is a construction that to the data of a smooth manifold $M$ and an algebra $A$ valued in a symmetric monoidal $\infty$-category $\catC$ assigns an object
%
\begin{equation}
    \int_{M} A \in \catC.
\end{equation}
%
In fact this is only the simplest variant of factorization homology. Variants that accommodate stratified manifolds instead of smooth ones and even $(\infty,n)$-categories instead of algebras have also been worked out. Fixing the algebra, the construction is functorial with respect to open embeddings in the manifold variable, which is the starting point to show that it is a chain level homology theory in a generalized sense, and giving the name. The initial chiral version was first introduced in \cite{bd2004}, and a topological version was introduced by \cite{lurie_ha}. Later, in \cref{thm:disk_alg=lcfa}, we will also see how factorization homology serves to construct factorization algebras. The theory of factorization homology has been deeply developed in \cite{af_fhtop, aft_fhstrat}, especially in the manner that we introduce it in here. A good introduction, is thus, given by \cite{af_primer}, which we will be following.

In the following, and from now on, we let $\catC$ be a symmetric monoidal $\infty$-category that is \emph{$\otimes$-presentable} \cite{af_fhtop}, i.e. it satisfies:
%
\begin{enumerate}
    \item $\catC$ is presentable: it admits colimits, and every object is a filtered colimit of compact objects\footnote{For the exact meaning of these terms we refer the reader to \cite[sec.5.3]{lurie_htt}. For us, it will suffice to give examples of $\infty$-categories that satisfy these requirements.}, and
    \item the monoidal structure distributes over colimits: for all $c \in \catC$, the functor $c \otimes -: \catC \xrightarrow{} \catC$ takes colimit diagrams to colimit diagrams.
\end{enumerate}

\begin{remark}
    For developing the theory of factorization homology the assumption that $\catC$ has all \emph{sifted}\footnote{Sifted colimits are colimits over a sifted indexing simplicial set $K$, which means that the diagonal functor of $K \neq \emptyset$ is final \[ \mathsf{colim}(K \xrightarrow{} K \times K \xrightarrow{} \catC) \simeq \mathsf{colim}(K \times K \xrightarrow{} \catC).\]} colimits, and the monoidal structure commutes with these, is usually enough. However, if we want the $\infty$-category of algebras valued in $\catC$ to inherit the properties of having sifted colimits that commute with the monoidal structure, then we must require that $\catC$ has \emph{all} (small) colimits. This will similarly be the case for factorization algebras. The stronger requirement also doesn't exclude any of the core examples that we are interested in. In fact, in some situations, the full requirement of presentability makes examples tractable.
\end{remark}

\begin{example}
    The following are examples of $\otimes$-presentable categories:
    %
    \begin{enumerate}
        \item chain complexes $\mathscr{C}\mathsf{h}_{\mathbb{k}}$ over a commutative ring $\mathbb{k}$, where equivalences are given by quasi-isomorphism. The symmetric monoidal structure can be both direct sum $\oplus$ or tensor product $\otimes$.
        \item Any cocomplete, Cartesian closed $\infty$-category together with categorical product. (for example $\mathsf{Spaces}$ or $\cat$).
    \end{enumerate}
    %
    In particular, $(\mathscr{C}\mathsf{h}_{\mathbb{k}}, \otimes)$ is the most useful for the purposes of mathematical physics, which is why it's the choice for the development in \cite{cg2016} and \cite{ginot2015}.
\end{example}

We also fix an $\infty$-category of basics $\bstr \xrightarrow{} \bsc$.

\subsection{Disk Algebras}

\begin{definition}
    The symmetric monoidal $\infty$-category $\disk(\bstr) \subset \mfld(\bstr)$ is the smallest full symmetric monoidal $\infty$-subcategory containing $\bstr$. Namely, the objects of $\disk(\bstr)$ are disjoint unions of objects of $\bstr$.
\end{definition}

We will also need the ordinary version of this category in analogy to $\mfld$ and $\mfld[r]$.

\begin{definition}
    The symmetric monoidal category $\disk[r](\bstr) \subset \mfld[r](\bstr)$ is the smallest full symmetric monoidal $\infty$-subcategory containing 
    %
    \begin{equation}
        \bstr \bigtimes\limits_{\mfld(\bstr)} \mfld[r](\bstr) \subset \mfld[r](\bstr).
    \end{equation}
\end{definition}

\begin{remark}
    Taking into account all categories of disks and manifolds defined up to now we have a commutative diagram in the $\infty$-category of symmetric monoidal $\infty$-categories $\cat^{\otimes}$
    %
    \begin{equation}
        \begin{tikzcd}
            \disk[r](\bstr) \arrow[r] \arrow[d] & \disk (\bstr) \arrow[d] \\
            \mfld[r] (\bstr) \arrow[r] & \mfld (\bstr).
        \end{tikzcd}
    \end{equation}
\end{remark}

\begin{definition}
    The $\infty$-category of disk algebras valued in $\catC$ is the $\infty$-category of symmetric monoidal functors
    %
    \begin{equation}
        \alg{\disk(\bstr)} (\catC) := \mathsf{Fun}^{\otimes}(\disk(\bstr), \catC).
    \end{equation}
\end{definition}

\begin{remark}
    The exact specification of the above $\infty$-category is not immediate, but the explanations given in \cite[def.2.0.0.7]{lurie_ha}, \cite[rem.2.1.2.19]{lurie_ha} and \cite[def.2.1.3.7]{lurie_ha} clarify the matter. A succinct explanation is also given around \cite[def.1.11]{aft_fhstrat}. Informally, the objects will be symmetric monoidal functors from $\disk(\bstr)$ to $\catC$. These are given by functors $F:\disk(\bstr) \xrightarrow{} \catC$ together with maps
    %
    \begin{equation}\label{eq:symmon_maps}
        F(U \sqcup V) \xrightarrow{\ \ \simeq \ \ } F(U) \otimes F(V),
    \end{equation}
    %
    and such that the swap in $\disk(\bstr)$, $U \sqcup V \simeq V \sqcup U$, is sent to the swap in $\catC$, $F(U) \otimes F(V) \simeq F(V) \otimes F(U)$, in a way that is compatible with the maps in \cref{eq:symmon_maps}. A good informal explanation of this and other topics related to disk algebras can be found in the lecture notes \cite{tanaka20}.
\end{remark}

These algebras will be the algebraic input of factorization homology. To convince ourselves that this is not a huge limitation on the types of algebras that can be evaluated we have:
%
\begin{proposition}[{\cite[prop.2.12]{aft_fhstrat}}]\label{prop:framed_ndisk=En}
    Let $(\bstr \xrightarrow{} \bsc) = (* \xrightarrow{\{ \mathbb{R}^n\}} \bsc)$, namely the $\infty$-category of basics describing framed smooth $n$-manifolds. There is an equivalence of $\infty$-categories
    %
    \begin{equation}
        \alg{\disk(\bstr)} (\catC) \simeq \alg{\mathbb{E}_n} (\catC).
    \end{equation}
    %
    Furthermore, if the $\infty$-category of basics is rather $(\bstr \xrightarrow{} \bsc) = (\mathsf{BO}(n) \xrightarrow{\{ \mathbb{R}^n\}} \bsc)$, the one describing unstructured smooth manifolds, then there is an equivalence of $\infty$-categories
    %
    \begin{equation}
        \alg{\disk(\bstr)} (\catC) \simeq \alg{\mathbb{E}_n}(\catC)^{\mathsf{O}(n)},
    \end{equation}
    %
    with the (homotopy) $\mathsf{O}(n)$-invariants, where the action of $\mathsf{O}(n)$ is given by change of framing.
\end{proposition}

\begin{remark}
    For more details on $\mathbb{E}_n$-algebras and why these algebras encompass large portions of the examples one usually cares about see \cite[sec.5.1]{lurie_ha}. %or alternatively in appendix \cref{app:En_algebras}. 
    Roughly speaking, $\mathbb{E}_1$-algebras are homotopy associative algebras and with increasing $n$ we get increasing levels of homotopy commutativity. Having said that, the first part of the proposition is just the classical statement that the little $n$-disks operad and the little $n$-cubes operad are equivalent.
\end{remark}

\begin{definition}
    For $M \in \mfld(\bstr)$ a $\bstr$-manifold the slice $\infty$-category of disks over $M$ is defined by
    %
    \begin{equation}
        \disk(\bstr)_{/M} := \disk(\bstr) \bigtimes\limits_{\mfld(\bstr)} \mfld(\bstr)_{/M}.
    \end{equation}
\end{definition}

\begin{remark}
    $\disk(\bstr)$ is a symmetric monoidal $\infty$-category, however there is no way to inherit this structure to $\disk(\bstr)_{/M}$. Intuitively, this is because disjoint union cannot serve as a monoidal structure now that the disks are equipped with an embedding into a given manifold $M$; they could be such that they intersect. However, as explained in \cite[not.1.21]{aft_fhstrat}, we \emph{can} equip $\disk(\bstr)_{/M}$ with the structure of an $\infty$-operad because the symmetric monoidal unit $\emptyset$ of $\disk(\bstr)$ and $\mfld(\bstr)$ is initial. This is also the case for $\mfld(\bstr)_{/M}$ itself.

    In more details, following \cite[ex.2.5]{aft_fhstrat}, objects of $\disk(\bstr)_{/M}$ are finite sets of open embeddings of disks $(U \xhookrightarrow{} M)$. A morphism between two open embeddings $(U \xhookrightarrow{} M) \xrightarrow{} (V \xhookrightarrow{} M)$ is specified by an open embedding $U \xhookrightarrow{} V$ together with an isotopy between $U \xhookrightarrow{} M$ and $U \xhookrightarrow{} V \xhookrightarrow{} M$. A multi-morphism $((U_1 \xhookrightarrow{} M), (U_2 \xhookrightarrow{} M)) \xrightarrow{} (V \xhookrightarrow{} M)$ is given by an open embedding $U_1 \sqcup U_2 \xhookrightarrow{} V$ together with two isotopies from $U_1 \xhookrightarrow{} M$ to $U_1 \xhookrightarrow{} U_1 \sqcup U_2 \xhookrightarrow{} M$, and from $U_2 \xhookrightarrow{} M$ to $U_2 \xhookrightarrow{} U_1 \sqcup U_2 \xhookrightarrow{} M$.
\end{remark}

\begin{remark}
    The constructions of the slice category also holds, word for word, in the case of $\disk[r](\bstr)_{/M}$ and $\mfld[r](\bstr)_{/M}$. The fact that they are $\infty$-operads is also true. The key difference is what the objects and multi-morphisms are, say, in $\disk[r](\bstr)_{/M}$ as compared to $\disk(\bstr)_{/M}$. The objects are the same as before, i.e. finite sets of open embeddings into $M$. However, the multi-morphisms now contain less information. A morphism $(U \xhookrightarrow{} M) \xrightarrow{} (V \xhookrightarrow{} M)$ is specified only by open embedding $U \xhookrightarrow{} V$, such that $(U \xhookrightarrow{} M) = (U \xhookrightarrow{} V \xhookrightarrow{} M)$, and no further information. Similarly, for the multi-morphisms too.

    That is, a multi-morphism in $\disk(\bstr)_{/M}$ is a diagram in $\disk (\bstr)$
    %
    \begin{equation}
        \begin{tikzcd}
            \coprod\limits_{i} U_i \arrow[rr] \arrow[rd] & & U \arrow[ld] \\
            & M, &
        \end{tikzcd}
    \end{equation}
    %
    which is homotopy commutative, while in $\disk[r](\bstr)_{/M}$ a morphism is a diagram as above that commutes on the nose\footnote{Regarding notation, \cite{lurie_ha} introduces both $\infty$-operads $\disk(\bstr)_{/M}$ and $\disk[r](\bstr)_{/M}$, however there they are denoted by $\mathbb{E}_M^\otimes$ and $\mathrm{N}(\mathrm{Disk}(M))^\otimes$, respectively.}.
\end{remark}

\begin{definition}
    We will refer to the $\infty$-category of algebras over the $\infty$-operads $\disk(\bstr)_{/M}$, $\disk[r](\bstr)_{/M}$, $\mfld(\bstr)_{/M}$ and $\mfld[r](\bstr)_{/M}$ in the usual way as
    %
    \begin{align}
        &\alg{\disk(\bstr)_{/M}} (\catC)& &\alg{\disk[r](\bstr)_{/M}} (\catC)& &\alg{\mfld(\bstr)_{/M}} (\catC)& &\alg{\mfld[r](\bstr)_{/M}} (\catC).&
    \end{align}
\end{definition}

\begin{remark}
    These algebras are defined as described in \cite{lurie_ha} for a general $\infty$-operad. For a superficial understanding what will be most important for us is that algebras $\alg{\mathscr{O}} (\mathscr{C})$, where $\mathscr{O}$ and $\mathscr{C}$ are $\infty$-operads, are described as functors $\mathscr{O} \xrightarrow{} \mathscr{C}$ that satisfy some additional requirements\footnote{Specifically, a functor $F$ between the underlying $\infty$-categories is an algebra if it lies over $\mathsf{Fin}_*$
    %
    \begin{equation}
        \begin{tikzcd}[ampersand replacement=\&]
            \mathscr{O} \arrow[rr, "F"] \arrow[rd] \& \& \mathscr{C} \arrow[ld] \\
            \& \mathsf{Fin}_* \&
        \end{tikzcd},
    \end{equation}
    %
    and if it carries inert morphisms in $\mathscr{O}$ to inert morphisms in $\mathscr{C}$.
    }. The following propositions from \cite{lurie_ha} gives another perspective on how to look at these algebras.
\end{remark}

\begin{proposition}[{\cite[prop.2.2.4.9]{lurie_ha}}]
    Let $\mathscr{O}$ be an $\infty$-operad and let $\catC$ be a symmetric monoidal $\infty$-category. Then there is an equivalence
    %
    \begin{equation}
        \mathsf{Fun}^\otimes (\mathsf{Env}(\mathscr{O}), \catC) \xrightarrow{\ \ \simeq \ \ } \alg{\mathscr{O}} (\catC),
    \end{equation}
    %
    between the $\infty$-categories of $\mathscr{O}$-algebras in $\catC$ and symmetric monoidal functors from the symmetric monoidal envelope\footnote{A full definition of the symmetric monoidal envelope of an $\infty$-operad can be found in \cite[sec.2.2.4]{lurie_ha}. For our purposes the two important facts about $\mathsf{Env}$ are that it is a left adjoint to the forgetful functor $U: \cat^\otimes \xrightarrow{} \mathscr{O}\mathsf{p}_{\infty}$, and that the underlying $\infty$-category of $\mathsf{Env} (\mathscr{O})$ is the $\infty$-subcategory of $\mathscr{O}$ spanned by the active morphisms. Informally, the symmetric monoidal structure of $\mathsf{Env}(\mathscr{O})$ is given by concatenating these active morphisms \cite[rem.2.2.4.6]{lurie_ha}.} of $\mathscr{O}$ to $\catC$.
\end{proposition}

\begin{remark}\label{rem:disk_b=disk_bsc}
    The $\infty$-operad $\disk(\bstr)_{/M}$, so defined, does not actually depend on the $\bstr$-structure; there is an equivalence
    %
    \begin{equation}
        \disk(\bstr)_{/M} \simeq \disk(\bsc)_{/M},
    \end{equation}
    %
    where $M$ on the right-hand side is the underlying stratified manifold of the $\bstr$-manifold also called $M$. This is essentially because the $\infty$-cateogry of basics $\bstr \xrightarrow{} \bsc$ is defined as a right fibration. Intuitively, those disks that have an open embedding into $M$ admit a $\bstr$-structure by restriction since $M$ admits one. From here, since over $\infty$-groupoids are contractible, there is an equivalence between the singleton space consisting of this inherited $\bstr$-structure and the space of $\bstr$-structures the disk originally had. The argument, of course, holds for $\disk(\bstr)_{/M}$ too, as well as $\mfld(\bstr)_{/M}$ and $\mfld[r](\bstr)_{/M}$. This is why, when talking about these slice $\infty$-operads we will simplify the notation down to $\disk_{/M}$, $\disk[r]_{/M}$, $\mfld_{/M}$ and $\mfld[r]_{/M}$.
\end{remark}

Essentially the same argument as above, namely that over $\infty$-groupoids are contractible, also has another important consequence that we will need to make use of later:

\begin{lemma}\label{lem:double_slice}
    Every open embedding $e: N \xhookrightarrow{} M$ induces an equivalence of $\infty$-categories
    %
    \begin{equation}
        (\mfld_{/M})_{/e} \simeq \mfld_{/N}.
    \end{equation}
    %
    The same holds for $\mfld[r]$, as well as, $\disk$ and $\disk[r]$.
\end{lemma}

The next result is of key importance to the technical side of the theory, and will be used extensively throughout. It alone, is essentially the reason for the appearance of constructible bundles in a lot of later developments.

\begin{lemma}[{\cite[lem.2.24]{aft_fhstrat}}]\label{lem:f^-1}
    Let $f: M \xrightarrow{} N$ be a constructible bundle. There is a functor of $\infty$-operads
    %
    \begin{equation}
        f^{-1}: \disk_{/N} \xrightarrow{} \mfld_{/M},
    \end{equation}
    %
    which acts on objects by sending $V \xhookrightarrow{} N$ to $f^{-1}V \xhookrightarrow{} M$.
\end{lemma}

\begin{remark}
    Because of \cref{rem:disk_b=disk_bsc}, the above construction works for manifolds with any general $\bstr$-structure, with no further requirements on the constructible bundle $f$.
\end{remark}

\subsection{Definition of Factorization Homology}

In the previous subsection we defined and explored the algebraic input of factorization homology. We now know that disk algebras are defined at their core as a functor that evaluates disks. Thus, we now gain the appreciation that factorization homology is a way to extend the input of this functor to all stratified manifolds instead of just stratified disks. It comes as no surprise then that factorization homology is defined as a Kan extension:

\begin{definition}
    \emph{(Absolute) factorization homology} is a functor that is a left adjoint to the restriction along $\disk(\bstr) \xhookrightarrow{} \mfld(\bstr)$
    %
    \begin{equation}
        \begin{tikzcd}
            \int : \mathsf{Fun}^\otimes (\disk(\bstr), \catC) \arrow[r, bend left=8] & \mathsf{Fun}^\otimes (\mfld(\bstr), \catC) \arrow[l, bend left=8].
        \end{tikzcd}
    \end{equation}
    %
    Similarly, given a stratified manifold $M$, \emph{(relative) factorization homology} is a functor that is a left adjoint to the restriction along $\disk_{/M} \xhookrightarrow{} \mfld_{/M}$
    %
    \begin{equation}
        \begin{tikzcd}
            \int : \alg{\disk_{/M}} (\catC) \arrow[r, bend left=10] & \alg{\mfld_{/M}} (\catC) \arrow[l, bend left=10].
        \end{tikzcd}
    \end{equation}
\end{definition}

The bulk of the work is then to show that such an adjoint exists and to try to find more concrete forms of factorization homology that would be easier to compute with. Being a left Kan extension one guess on the side of computation would be that we can find its values via colimits, as is usual for pointwise left Kan extensions. Determining under which assumptions factorization homology, in both its forms, exists and is given by a colimit is one of the major results of \cite{af_fhtop} (for the smooth case) and \cite{aft_fhstrat} (for the stratified case). Specifically lemmas \cite[lem.2.16]{aft_fhstrat} and \cite[lem.2.17]{aft_fhstrat} are great encapsulations of all the conditions that are needed.

The upshot is that, with our setup and assumptions on $\catC$, the guess that the value of factorization homology can be calculated by a colimit is correct and given by the standard expressions for left Kan extensions
%
\begin{equation}
    \int_M A \simeq \mathsf{colim} \left(\disk(\bstr)_{/M} \xrightarrow{} \disk(\bstr) \xrightarrow{A} \catC \right)
\end{equation}
%
in the absolute case, and
%
\begin{equation}
    \int_{N \xhookrightarrow{} M} A \simeq \mathsf{colim} \left((\disk_{/M})_{/(N \xhookrightarrow{} M)} \xrightarrow{} \disk_{/M} \xrightarrow{A} \catC \right)
\end{equation}
%
in the relative case. Namely, the left Kan extension of underlying $\infty$-categories lifts to a symmetric monoidal, in the absolute case, and operadic, in the relative case, left Kan extension. In the relative case, we will almost always abuse notation and write $\int_N A$ instead of $\int_{N \xhookrightarrow{} M} A$, but because of \cref{lem:double_slice} this is not much of an abuse. Furthermore, factorization homology is also shown to be fully faithful due to this being true for the inclusion $\disk(\bstr) \xrightarrow{} \mfld(\bstr)$, as well as, the relative version with slices.

\begin{remark}
    In fact, lemmas \cite[lem.2.16]{aft_fhstrat} and \cite[lem.2.17]{aft_fhstrat} are general enough that they already encompass the alternative definitions with $\disk[r]$ and $\disk[r]_{/M}$, so factorization homology is just as easily defined in that context too.
\end{remark}

\subsection{Disk Algebras over Oriented Intervals}\label{ch:fh_on_intervals}

We now focus on describing disk algebras over oriented intervals with and without boundary. Not only is this an important example for what disk algebras look like, but it's also important in defining what it means to say that factorization homology is excisive. The following constructions can be found in the originals \cite{af_fhtop,aft_fhstrat}.

We want to show that disk algebras with $\mathsf{D}_1^{\partial, \mathsf{or}}$-structure, as defined in \cref{con:d_1^bor_structure}, can be described algebraically. For this we set up two $\infty$-operads $\mathsf{Assoc^{RL}}$ and $\mathsf{O^{RL}}$.

\begin{construction}\label{con:assocRL}
    Let $\mathsf{Assoc^{RL}}$ denote the multicategory\footnote{A \emph{multicategory} is like an (ordinary) category except that morphisms (now called multi-morphisms) are allowed to have multiple objects in their domain while still having only a single object in their codomain.} with three objects $R$, $A$ and $L$. To describe the multi-morphisms let $I$ be an arbitrary finite list of the objects of $\mathsf{Assoc^{RL}}$. We have:
    %
    \begin{enumerate}
        \item $\mathsf{Assoc^{RL}}(I, A)$ is empty if either $R$ or $L$ appear on the list $I$; otherwise it is given by the number of total orders of $I$.
        \item $\mathsf{Assoc^{RL}}(I, R)$ is empty if either $L$ appears on the list or $R$ appears on the list more than once; otherwise it is given by the number of total orders of $I$ such that the possible element $R$ is a minimum.
        \item $\mathsf{Assoc^{RL}}(I, L)$ is empty if either $R$ appears on the list or $L$ appears on the list more than once; otherwise it is given by the number of total orders of $I$ such that the possible element $L$ is a minimum.
    \end{enumerate}
    %
    Composition of multi-morphisms is given by concatenation. 
\end{construction}

\begin{remark}
    More informally, what the \cref{con:assocRL} says is that the only multi-morphism domains possible are $\emptyset$, $(A,A,\dots,A)$, $(R,A,\dots,A)$ or $(A,\dots,A, L)$ and that there is one multi-morphism for each permutation of the $A$ entries. This makes it clear that algebras over this $\infty$-operad will be unital, (homotopy) associative algebras, together with a unital left and a unital right module.
\end{remark}

\begin{construction}
    Let $\mathsf{O^{RL}}$ be the (ordinary) category whose objects are totally ordered finite sets $(I, \leq)$ with two distinguished subsets $R \subset I \supset L$, such that each element of $R$ is a minimum and each element of $L$ is a maximum (consequently, $|R| \leq 1$ and $|L| \leq 1$). The morphisms $f:(I, \leq, R, L) \xrightarrow{} (I', \leq', R', L')$ are order preserving maps $f: (I,\leq) \xrightarrow{} (I', \leq')$ which also preserve the distinguished subsets $f(R) = R'$, $f(L) = L'$. Concatenation of total orders gives $\mathsf{O^{RL}}$ a multicategory structure.
\end{construction}

\begin{remark}
    The $\infty$-operads $\mathsf{Assoc^{RL}}$ and $\mathsf{O^{RL}}$ are clearly related, though there are differences. The major difference is that $\mathsf{O^{RL}}$ has objects that have both a distinguished maximal and distinguished minimal element, while in $\mathsf{Assoc^{RL}}$ only one of them exists at a time. In fact, we will see that their symmetric monoidal envelopes are equivalent. Therefore, considering them separately also gives some intuition for the symmetric monoidal envelope, so we choose to do this for expositional reasons. The following propositions make it geometrically clear why this is the case.
\end{remark}

\begin{proposition}\label{prop:disk1bor=assocRL}
    There are equivalences of symmetric monoidal $\infty$-categories between $\mathsf{D}_1^{\partial, \mathsf{or}}$-structured disks and the symmetric monoidal envelope of $\mathsf{Assoc^{RL}}$
    %
    \begin{equation}
        \disk[r] (\mathsf{D}_1^{\partial, \mathsf{or}}) \xrightarrow{\ \ \simeq \ \ } \disk (\mathsf{D}_1^{\partial, \mathsf{or}}) \xrightarrow[\simeq]{\ \ [-] \ \ } \mathsf{Env} (\mathsf{Assoc^{RL}}).
    \end{equation}
    %
    The functor $[-]$ assigns $[\hoint] = R$, $[\mathbb{R}] = A$ and $[\mathbb{R}_{\leq 0}] = L$.
\end{proposition}

\begin{proof}
    The first equivalence comes by inspection of the morphism spaces which are discrete in this particular case. Since $\mathsf{Assoc^{RL}}$ is also born of a discrete nature we only need to find a bijection of morphism spaces. By construction of $\mathsf{Assoc^{RL}}$ such a bijection is immediate.
\end{proof}

\begin{proposition}\label{prop:disk1bor_over_int=ORL}
    There are equivalences of $\infty$-operads
    %
    \begin{equation}
        \disk[r] (\mathsf{D}_1^{\partial, \mathsf{or}})_{/[-1,1]} \xrightarrow{\ \ \simeq \ \ } \disk (\mathsf{D}_1^{\partial, \mathsf{or}})_{/[-1,1]} \xrightarrow{\ \ \simeq \ \ } \mathsf{O^{RL}} \quad
    \end{equation}
    %
    that descend to the equivalences of \cref{prop:disk1bor=assocRL}.
\end{proposition}

\begin{proof}
    As in the proof of \cref{prop:disk1bor=assocRL} the first equivalence is clear. The idea to keep in mind is that since the boundary of $[-1,1]$ consists of a left point and a right point, there can only be oriented embeddings of disks into $[-1,1]$ with at most one of each of $\left[-1,1 \right)$ and $\left( -1, 1 \right]$. These are then clearly the objects that map to the respective distinguished subsets. Observing the definition of $\mathsf{O^{RL}}$ clearly offers a bijections on morphism spaces since they are by definition order preserving maps, and the embeddings are oriented. It is trivial to check that these maps lie over $\mathsf{Fin}_*$ and that they send active morphisms to active morphisms completing the proof.
\end{proof}

In fact in the simple case of intervals, that we're considering here, even more is true:

\begin{proposition}\label{prop:env_ORL=env_assocRL}
    There are equivalences of symmetric monoidal $\infty$-categories
    %
    \begin{equation}
        \mathsf{Env}(\mathsf{O^{RL}}) \xrightarrow{\ \ \simeq \ \ } \mathsf{Env}(\disk (\mathsf{D}_1^{\partial, \mathsf{or}})_{/[-1,1]}) \xrightarrow{\ \ \simeq \ \ } \disk (\mathsf{D}_1^{\partial, \mathsf{or}}) \xrightarrow{\ \ \simeq \ \ } \mathsf{Env} (\mathsf{Assoc^{RL}})
    \end{equation}
\end{proposition}

\begin{proof}
    The only thing to show is the middle equivalence. This follows from \cref{lem:disk/M_to_disk}, which we will introduce later. 
\end{proof}

---------------

\begin{proposition}\label{prop:barconst=intinterval}
    There is an equivalence of functors between the two-sided bar construction
    %
    \begin{equation}
        \mathsf{B}: \alg{\mathsf{Assoc^{RL}}}(\catC) \xrightarrow{} \catC
    \end{equation}
    %
    and factorization homology over the oriented closed interval
    %
    \begin{equation}
        \int_{[-1,1]}: \alg{\mathsf{Assoc^{RL}}}(\catC)\simeq \alg{\disk_{/[-1,1]}} (\catC) \xrightarrow{\ \int \ } \alg{\mfld_{/[-1,1]}} (\catC) \xrightarrow{\ \mathsf{ev}_{[-1,1]} \ } \catC.
    \end{equation}
    %
    In particular, given a unital, (homotopy) associative algebra $A$, a unital right $A$-module $R$ and a unital left $A$-module $L$, there is an equivalence of objects
    %
    \begin{equation}
        \int_{[-1,1]} (R, A, L) \xrightarrow{\ \ \simeq \ \ } R \bigotimes\limits_{A} L.
    \end{equation}
\end{proposition}

\begin{remark}
    The two-sided bar construction here gives the left derived tensor product. We, however, do not make a notational distinction between this left derived tensor product and the standard one since we should be clear from context. The left derived version will always appear due to some two-sided bar construction. 
\end{remark}

\begin{proof}
    The equivalence at the level of objects is exactly \cite[prop.2.34]{aft_fhstrat}, whose proof we recount here for completeness.

    For the purposes of the proof introduce the shorthand notation $\mathscr{D} := \disk(\mathsf{D}_1^{\partial, \mathsf{or}})$. There is a functor $\Delta^{\mathsf{op}} \xhookrightarrow{} \mathsf{O^{RL}}$ from the opposite of the simplex category, whose essential image consists of those objects for which the distinguished subsets with a maximal and minimal element are non-empty. This functor is final\footnote{A functor $F: \catC \xrightarrow{} \mathscr{D}$ between $\infty$-categories is final if precomposition with it preserves colimits \[ \mathsf{colim}(G \circ F) \simeq \mathsf{colim}(G).\]} because adjoining a minimum and maximum gives a left adjoint to it. We recognize the simplicial object
    %
    \begin{equation}
        \mathsf{B}_{\bullet}(R, A, L): \Delta^{\mathsf{op}} \xhookrightarrow{} \mathsf{O^{RL}} \simeq \mathscr{D}_{/[-1,1]} \xrightarrow{} \mathscr{D} \xrightarrow{(R, A, L)} \catC
    \end{equation}
    %
    as the two-sided bar construction. Since $\catC$ has colimits and $\Delta^{\mathsf{op}} \xhookrightarrow{} \mathsf{O^{RL}}$ is final, the geometric realization of the above is
    %
    \begin{equation}
        R \bigotimes\limits_{A} L = |\mathsf{B}_{\bullet}(R, A, L)| \simeq \mathsf{colim} (\mathscr{D}_{/[-1,1]} \xrightarrow{} \mathscr{D} \xrightarrow{(R, A, L)} \catC) = \int_{[-1,1]} (R, A, L).
    \end{equation}
    %
    The naturality of this construction is immediate from the above presentation.
\end{proof}

%\begin{proposition}[{\cite[prop.2.34]{aft_fhstrat}}]\label{prop:barconst=intinterval}
%    Let $A$ be a unital, (homotopy) associative algebra in $\catC$, $R$ be a unital right $A$-module in $\catC$ and $L$ be a unital left $A$-module in $\catC$. Using \cref{prop:disk1bor=assocRL} regard this data as the data of a symmetric monoidal functor $(R, A, L): \disk (\mathsf{D}_1^{\partial, \mathsf{or}}) \xrightarrow{} \catC$. Then there is a canonical equivalence in $\catC$ between factorization homology over the closed interval and the two-sided bar construction
%    %
%    \begin{equation}
%        \int_{[-1,1]} (R, A, L) \xrightarrow{\ \ \simeq \ \ } R \bigotimes\limits_{A} L.
%    \end{equation}
%\end{proposition}

\subsection{Pushforward}

The construction of \cref{lem:f^-1} gives a functor which allows us to change the stratified manifold over which we work. This brings about the important operation of pushforward:

\begin{theorem}[{\cite[thm.2.25]{aft_fhstrat}}]\label{thm:fh_pushforward}
    Let $f: M \xrightarrow{} N$ be a constructible bundle. There is a pushforward functor
    %
    \begin{equation}
        f_*: \alg{\disk_{/M}}(\catC) \xrightarrow{\quad} \alg{\disk_{/N}}(\catC),
    \end{equation}
    %
    which takes a $\disk_{/M}$-algebra $A$ to
    %
    \begin{equation}
        f_*A: \disk_{/N} \xrightarrow{f^{-1}} \mfld_{/M} \xrightarrow{\int_{-} A} \catC.
    \end{equation}
    %
    This functor is such that there is a canonical equivalence in $\catC$
    %
    \begin{equation}
        \int_{M} A \simeq \int_{N} f_* A
    \end{equation}
\end{theorem}

\begin{remark}
    In particular, the above applies to disk algebras with any $\bstr$-structure, since a $\disk(\bstr)$-algebra $A$ can be viewed as a $\disk(\bstr)_{/M}$-algebra for any $\bstr$-manifold $M$ by
    %
    \begin{equation}
        \disk(\bstr)_{/M} \xrightarrow{} \disk(\bstr) \xrightarrow{A} \catC.
    \end{equation}
\end{remark}

\subsection{\texorpdfstring{$\otimes$}{tensor}-excision and Homology Theories}

Now that we have a pushforward operation, we can finally explicitly state what excision is in this context. This is because a collar-gluing of a stratified manifold $M$ is defined exactly as a constructible bundle $f: M \xrightarrow{} [-1,1]$.

\begin{definition}
    Let $F: \mfld(\bstr) \xrightarrow{} \catC$ be a symmetric monoidal functor. Also let $M$ be a $\bstr$-manifold and $f: M \xrightarrow{} [-1,1]$ be a collar-gluing of $M$. This data allows for the construction of a canonical morphism in $\catC$
    %
    \begin{equation}
        F(M_-) \bigotimes\limits_{F(M_0 \times \mathbb{R})} F(M_+) \xrightarrow{\quad} F(M),
    \end{equation}
    %
    where $M_-$, $M_0$ and $M_+$ are as usual. If this morphism is an equivalence for each collar-gluing then we say that $F$ satisfies $\otimes$-excision.
\end{definition}

\begin{proof}
    The definition comes with a claim that the canonical morphism in $\catC$ exists. This we need to show. The data of a collar-gluing $f: M \xrightarrow{} [-1,1]$ allows us to pushforward $F$ to
    %
    \begin{equation}
        f_*F: \disk (\mathsf{D}_1^{\partial, \mathsf{or}})_{/[-1,1]} \xrightarrow{f^{-1}} \mfld(\bstr)_{/M} \xrightarrow{} \mfld(\bstr) \xrightarrow{F} \catC.
    \end{equation}
    %
    By \cref{prop:disk1bor=assocRL} we know that this data defines an $\mathsf{Assoc^{RL}}$-algebra in $\catC$ whose right module, algebra and left module are exactly $F(M_-)$, $F(M_0 \times \mathbb{R})$ and $F(M_+)$. Further using \cref{prop:barconst=intinterval} we have
    %
    \begin{equation}
        F(M_-) \bigotimes\limits_{f(M_0 \times \mathbb{R})}  F(M_+)\simeq \int_{[-1,1]} f_* F \xrightarrow{\quad} F (f^{-1}[-1,1]) = F(M),
    \end{equation}
    %
    where the morphism is given by the fact that factorization homology is a colimit.
\end{proof}

\begin{remark}
    A functor $F: \mfld(\bstr) \xrightarrow{} \catC$ that satisfies $\otimes$-excision and respects sequential colimits is called a homology theory in the terminology of \cite{af_fhtop}. We will not comment on this direction of development further except as a justification for the name of factorization homology. If in the above proof $F$ was given by factorization homology, then in the final step the pushforward would provide the further necessary equivalence so that:
\end{remark}

\begin{proposition}[{\cite{aft_fhstrat}}]\label{prop:homology=disk_alg}
    Factorization homology is a homology theory. In particular, for a collar-gluing of a $\bstr$-manifold $M$, and a $\disk(\bstr)$-algebra $A$
    %
    \begin{equation}
        \int_{M_-} A  \bigotimes\limits_{\int_{M_0 \times \mathbb{R}} A} \int_{M_+} A \xrightarrow{\ \ \simeq \ \ } \int_M A.
    \end{equation}
\end{proposition}

\begin{remark}
    The fact that factorization homology is $\otimes$-excisive is extremely computationally useful, and is the way we evaluate factorization homology in practice.
\end{remark}

\begin{example}
    Checking the definitions we can see that evaluating basics $U \in \disk(\bstr) \xhookrightarrow{} \mfld(\bstr)$ is the same as simply evaluating the disk with the disk algebra. This is simply because factorization homology is a left Kan extension.

    The first nontrivial example is then the oriented circle. We know that the algebras that we will be evaluating with are $\disk (\mathsf{D}_1^{\partial, \mathsf{or}})$-algebras (or even simpler the restriction to $\disk (\mathsf{D}_1^{\mathsf{or}})$ the ones without boundary). The oriented circle can be presented as a collar-gluing
    %
    \begin{equation}
        S^1 \cong \mathbb{R} \coprod\limits_{S^0 \times \mathbb{R}} \mathbb{R} \cong \mathbb{R} \coprod\limits_{\bar{\mathbb{R}}\sqcup \mathbb{R}} \mathbb{R},
    \end{equation}
    %
    where $\bar{\mathbb{R}}$ denotes $\mathbb{R}$ with the opposite orientation to the standard one. Factorization homology then gives
    %
    \begin{equation}
        \int_{S^1} A \simeq \int_{\mathbb{R}} A \bigotimes\limits_{\int_{\mathbb{R}} A \otimes \int_{\bar{\mathbb{R}}} A} \int_{\mathbb{R}} A \simeq A \bigotimes\limits_{A \otimes A^{\mathsf{op}}} A,
    \end{equation}
    %
    where the result is known in the literature as the Hochschild homology (or more properly chains) of the associative algebra $A$.
\end{example}

\subsection{Classification of \texorpdfstring{$\disk(\mathsf{D}_{d \subset n}^{*})$}{diskdn*}-algebras}

All of the above statements about factorization homology and disk algebras did not rely heavily on the stratified structure which we introduced them with. Namely, had we stuck to smooth manifolds (possibly with boundary) we could have made similar statements. In this section we describe a result that clearly uses the stratified structure, and quantifies some additional information it can encode. It is a classification statement about disk algebras whose structure $\mathsf{D}_{d \subset n}^*$ is provided by \cref{def:framed_d_under_n_sructure}.

\begin{theorem}[{\cite[prop.4.8]{aft_fhstrat}}]\label{thm:classif_disk_d_under_n*_alg}
    There is a pullback diagram
    %
    \begin{equation}
        \begin{tikzcd}[row sep=large, column sep = large]
            \alg{\disk(\mathsf{D_{d+1}^*})} \left(\int_{S^{n-d-1} \times \mathbb{R}^{d+1}} A, \mathsf{Z}(B) \right) \arrow[r] \arrow[d] & \alg{\disk(\mathsf{D}_{d \subset n}^*)} \arrow[d] \\
            * \arrow[r, "{\{(A, B)\}}"] & \alg{\disk(\mathsf{D}_{n}^*)} \times \alg{\disk(\mathsf{D}_d^*)},
        \end{tikzcd}
    \end{equation}
    %
    where we have omitted the target $\infty$-category $\catC$ for clarity. In other words, the data of a $\disk(\mathsf{D}_{d \subset n}^*)$-algebra is equivalent to giving a triple $(A, B, \alpha)$, of a $\disk(\mathsf{D}_n^*)$-algebra $A$, a $\disk(\mathsf{D}_d^*)$-algebra $B$ and a map of $\disk(\mathsf{D}_{d+1}^*)$-algebras
    %
    \begin{equation}
        \alpha: \int_{S^{n-d-1} \times \mathbb{R}^{d+1}} A \xrightarrow{\ \ \quad} \mathsf{Z} (B).
    \end{equation}
\end{theorem}

\begin{remark}
    The above theorem is a slight generalization of, and heavily relies on, the proof of the higher Deligne conjecture on Hochschild cohomology as in \cite[sec.5.3]{lurie_ha}. Thus, from \cref{prop:framed_ndisk=En}, we know that it is very important to the theorem to work with framed disks since these are the ones that reproduce the $\mathbb{E}_n$-algebras of the higher Deligne conjecture. The proof of the proposition is not easily generalizable to other tangential structures. The associative algebra $\mathsf{Z} (B)$ is the center of $B$ as defined in \cite[def.5.3.1.6]{lurie_ha}, so that even the statement, which implies that $\mathsf{Z}(B)$ is more than associative, relies on the special structure provided by framing.  
\end{remark}

\begin{remark}
    By definition, the center $\mathsf{Z}(B)$ is the universal object that acts on $B$, i.e. all objects that act on $B$ factor through the action of the center $\mathsf{Z}(B)$ on $B$. Keeping this in mind, we see that, informally, \cref{thm:classif_disk_d_under_n*_alg} is saying that the structure of coupling the defect algebra $B$ to the bulk algebra $A$ is by giving $B$ a suitable module structure over $A$. The complication then lies in proving what this suitable module structure is. 
\end{remark}

\end{document}

### 2023-11-24 sections/3algebras.tex
Add files via upload

\documentclass[../text]{subfiles}

\begin{document}

\section{Factorization Algebras}\label{ch:fact_alg}

\subsection{Definition of Factorization Algebras}

Factorization algebras are a rigorous way to capture the idea of assigning an object to each piece of a space, together with a local-to-global principle that allows one to find out about larger pieces from smaller ones. The first ideas around factorization algebras were introduced by \cite{bd2004} in the context of vertex algebras in CFTs. These were geometric in nature. The topological version that we present was then introduced by Lurie and subsequently further developed in \cite{cg2016}, especially for the purposes of mathematical physics. Here we will present these ideas following \cite{cg2016} and also \cite{af_primer}. A similar exposition can be found in \cite{ginot2015}.

\begin{remark}
    We note that we have fixed a symmetric monoidal $\infty$-category $\catC$ that is $\otimes$-presentable to serve as the $\infty$-category that our algebras will be valued in.
\end{remark}

\begin{definition}
    Let $X$ be a topological space. We regard $\opens[s](X)$ as a multicategory (and consequently as an $\infty$-operad) whose objects are the open sets of $X$, and through the assignment of a unique multi-morphism from $\{U_i\}_{i \in I}$ to $U$ if the $U_i$ are pairwise disjoint and if $\bigcup_{i \in I} U_i \subset U$. A \emph{prefactorization algebra $F$ on $X$ with values in $\catC$} is an algebra in $\catC$ over this $\infty$-operad
    %
    \begin{equation}
        F \in \alg{\opens[s](X)}(\catC).
    \end{equation}
\end{definition}

\begin{remark}
    It is obvious that in the case of (stratified) manifolds we have already seen alternative notation for the $\infty$-operad $\opens(X)$ before, namely $\mfld[r]_{/M}$. This makes a connection to the standard notation used around factorization homology, and is something that we'll make use of later.
\end{remark}

\begin{remark}
    Let's unwind the above definition to understand the underlying data needed to define a prefactorization algebra. On the level of objects, for every open set $U$ we need to assign an object $F(U) \in \catC$. On the level of morphisms, given a pairwise disjoint set of opens $\{U_i\}_{i \in I}$ and an open $U$, such that the $U_i$ all lie in $U$ we need to assign a morphism in $\catC$
    %
    \begin{equation}
        \bigotimes_{i \in I} F(U_i) \xrightarrow{F(\{U_i\},U)} F(U).
    \end{equation}
    %
    As the notation suggests and the operadic symmetry condition guarantees, the maps $F(\{U_i\},U)$ only depend on the set of $U_i$ and not on any particular order of the $U_i$, which is also allowed on the left-hand side by the symmetric monoidal structure of $\catC$. Furthermore, the operadic associativity condition imposes that given pairwise disjoint $\{U_i\}_{i \in I}$ that all lie in $U$, and for each $i \in I$, pairwise disjoint $\{ V_{i, j}\}_{j \in J_i}$ that all lie in $U_i$, there is a commutative diagram in $\catC$
    %
    \begin{equation}
        \begin{tikzcd}
            \bigotimes\limits_{(i,j)} F(V_{i,j}) \arrow[rd, shorten <=-2ex, "\bigotimes\limits_{i} F(\{V_{i, j}\} {,} U_i)"'] \arrow[rr, "F( \{V_{i, j}\} {,} U)"] &   & F(U) \\
            & \bigotimes\limits_{i} F(U_i) \arrow[ru, "F( \{U_i \} {,} U)"'] &,          
            \end{tikzcd}
    \end{equation}
    %
    where the $(i,j)$ tensor product runs over all possible pairs $i \in I$ and $j \in J_i$. Finally, the operadic unitarity condition actually tells us that we don't need to provide the morphisms $F(\{U\}, U)$, because they are equivalent to the identity morphism.

    We also get out that an algebra morphism $\phi: F \rightarrow G$ is simply a family of maps $\phi(U): F(U) \rightarrow G(U)$ for each open set $U$, such that it respects the operations of the algebra. Namely, for each multi-morphism $\{ U_i \}_{i \in I} \rightarrow U$ there is a commuting square
    %
    \begin{equation}\label{cd:fa_morphisms}
        \begin{tikzcd}[row sep=large, column sep = large]
            \bigotimes\limits_{i \in I} F(U_i) \arrow[r, "F(\{ U_i\} {,} U)"] \arrow[d, "\bigotimes\limits_{i \in I} \phi(U_i)"'] & F(U) \arrow[d, "\phi(U)"] \\
            \bigotimes\limits_{i \in I} G(U_i) \arrow[r, "G(\{ U_i\} {,} U)"'] & G(U).
        \end{tikzcd}
    \end{equation}

\end{remark}

\begin{remark}\label{rem:op_to_op}
    There is an obvious embedding functor from the poset $\opens[r](X)$ of open subsets of $X$, ordered by inclusion, to the multicategory $\opens[s](X)$, namely, the one which hits only those multi-morphisms $\{U_i\}_{i \in I} \rightarrow U$, where the cardinality of the finite set $I$ is 1.
\end{remark}

A factorization algebra will be a prefactorization algebra that further satisfies a certain gluing condition that lets us construct its value on `larger' sets if we know it on `smaller' sets. More formally, this will be a kind of cosheaf condition, that we describe now, following \cite{weiss1999,af_primer}.

We endow the poset $\opens[r](X)$ with a Grothendieck topology called the \emph{Weiss} Grothendieck topology \cite{weiss1999}. In this topology a sieve $\mathscr{U} \subset \opens[r](X)_{/U}$ on $U$ is a covering sieve if for each finite subset $S \subset U$, there is an object $(e: V \rightarrow U) \in \mathscr{U}$ for which $S \subset e(V)$. In other words, a family $\{ V_i \rightarrow U\}_{i \in I}$ is a Weiss cover of $U$ if every set of finitely many points in $U$ is contained in some $V_i$. Contrast this with the standard Grothendieck topology on the poset of opens $\opens[r](X)$, in which instead of a finite set we have a one-element set. Thus, every Weiss cover is a cover in the standard sense, but not necessarily the other way around.

\begin{definition}
    The $\infty$-category of \emph{$\catC$-valued Weiss (homotopy) cosheaves on $X$} is the full $\infty$-subcategory
    %
    \begin{equation}
        \csheaves[W]_{X}(\catC) \subset \mathsf{Fun}(\opens[r](X), \catC),
    \end{equation}
    %
    of the $\infty$-category of copresheaves, consisting of those functors $F: \opens[r](X) \rightarrow \catC$ for which, for each Weiss covering sieve $\mathscr{U} \subset \opens[r](X)_{/U}$, the canonical functor
    %
    \begin{equation}
        \mathscr{U}^{\vartriangleright} \rightarrow \opens[r](X)_{/U} \rightarrow \opens[r](X) \xrightarrow{F} \catC,
    \end{equation}
    %
    where $\mathscr{U}^{\vartriangleright} \rightarrow \opens[r](X)_{/U}$ is the functor from the colimit cone that assigns $U$ to the colimit object, is a colimit diagram.
\end{definition}

\begin{remark}
    In other words, $F$ is a Weiss cosheaf if it is a functor that sends colimits (which, in this case, are unions) of Weiss covers $\{ U_i \xhookrightarrow{} U \}_{i \in I}$ to colimits in $\catC$
    %
    \begin{equation}
        F(U) \simeq F \bigg( \bigcup_{i \in I} U_i \bigg) \simeq \mathrm{colim}_{i \in I} F(U_i).
    \end{equation}
\end{remark}

\begin{remark}
    The category $\opens[r](X)$ can be replaced with any other category that supports an analogue of the Weiss Grothendieck topology. In the case of (stratified) manifolds, $\opens[r](X)$ is already the same as $\mfld[r]_{/X}$, be we could just as well define Weiss cosheaves on $\mfld[r]$, i.e. $\csheaves[W](\mfld[r], \catC)$. If we're working with the $\infty$-categories $\mfld$ or $\mfld_{/X}$, then we define cosheaves on them through the pullback
    %
    \begin{equation}
        \begin{tikzcd}
            \csheaves[W] (\mfld, \catC) \arrow[dr, phantom, "\ulcorner", very near start] \arrow[r] \arrow[d] & \mathsf{Fun}(\mfld, \catC) \arrow[d] \\
            \csheaves[W] (\mfld[r], \catC) \arrow[r] & \mathsf{Fun}(\mfld[r], \catC),
        \end{tikzcd}
    \end{equation}
    %
    and similarly for the relative case $\mfld_{/X}$.
\end{remark}

\begin{definition}
    The $\infty$-category of \emph{($\catC$-valued) factorization algebras on $X$}\footnote{These are called homotopy factorization algebras in \cite{cg2016}, however we do not consider the lax version of factorization algebras that they also present.} is the full $\infty$-subcategory of $\alg{\opens[s](X)}$ as in the pullback
    %
    \begin{equation}
        \begin{tikzcd}
            \falg_X (\catC) \arrow[dr, phantom, "\ulcorner", very near start] \arrow[r] \arrow[d] & \alg{\opens[s](X)}(\catC) \arrow[d] \\
            \csheaves[W]_X(\catC) \arrow[r] & \mathsf{Fun}(\opens[r](X), \catC).
        \end{tikzcd}
    \end{equation}
\end{definition}

\begin{proof}
    The previous definition implies that the top horizontal functor is fully faithful, which is something we need to prove. The bottom horizontal functor is fully faithful, by the definition of cosheaf, and the right vertical functor forgets the operations with arity higher than $1$. The key observation is that a Weiss cover is pairwise disjoint only when it consists of a single subset. Thus, the cosheaf condition does not affect the algebra morphisms and an equivalence of morphism spaces is trivial to find, namely one is given by the identity map.
\end{proof}

\begin{remark}\label{rem:check_nerve}
    A factorization algebra is a prefactorization algebra whose restriction to $\opens[r](X)$ is a Weiss cosheaf. This means that the definition can be rewritten in an equivalent way as with all cosheaves. Following \cite{nlab} (which presents the dual case of sheaves) we can express the condition through the \v{C}ech nerve. Let $\mathscr{U}_U = \{ U_i \rightarrow U\}_{i \in I}$ be a (Weiss) cover of an open set $U$ and $F$ be a copresheaf, and define the simplicial object
    %
    \begin{equation}
        \cech_{\bullet}(\mathscr{U}_U, F) := \left( \coprod_{i \in I} F(U_i) \leftleftarrows \coprod_{i, j \in I} F(U_i \cap U_j) \mathrel{\substack{\textstyle\leftarrow\\[-0.6ex]
        \textstyle\leftarrow\\[-0.6ex]\textstyle\leftarrow}} \coprod_{i, j, k \in I} F(U_i \cap U_j \cap U_k) \mathrel{\substack{\textstyle\leftarrow\\[-0.6ex]\textstyle\leftarrow\\[-0.6ex]\textstyle\leftarrow\\[-0.6ex]\textstyle\leftarrow}} \cdots  \right),
    \end{equation}
    %
    where the maps are induced by the value of $F$ on the inclusions of opens. There are canonical maps $F(U_i) \rightarrow F(U)$, so that at the level of simplicial objects there is a canonical map
    %
    \begin{equation}
        \cech_{\bullet} (\mathscr{U}_U, F) \xrightarrow{\quad} F(U)_{\bullet},
    \end{equation}
    %
    to the constant simplicial complex at $F(U)$. Since $\catC$ has (sifted) colimits we can take the geometric realization to obtain a morphism
    %
    \begin{equation}
        \cech(\mathscr{U}_U, F) \xrightarrow{\quad} F(U).
    \end{equation}
    %
    $F$ is a (homotopy) cosheaf if, and only if, this morphism is an equivalence for every open set $U$ and every Weiss cover of it $\mathscr{U}_U$.
\end{remark}

All of our definitions above are valid for all topological spaces, so in particular, also the stratified spaces we introduced at the beginning. For the next definition of locally constant factorization algebras though, it will be important to specify more information about the space. In other words, they will capture information about the stratification.

There is a general definition of locally constant algebra objects in the context of any $\infty$-operad given in \cite[def.2.3.3.20]{lurie_ha}, which, of course, applies here. In our case one can also take a perspective more akin to \cite[def.A.1.12]{lurie_ha} by defining locally constant cosheaves and then pulling back this property to factorization algebras. This is what we will do, along with focusing our attention to stratified (and therefore also to smooth) manifolds. The definitions we will make can in a lot of cases also be expanded for any $C^0$ stratified space or topological manifold.

\begin{definition}
    The $\infty$-category of locally constant Weiss cosheaves on a stratified manifold $M$ (or, equivalently, on $\mfld[r]_{/M}$) is the full $\infty$-subcategory
    %
    \begin{equation}
        \csheaves[W, lc]_M (\catC) \subset \csheaves[W]_M (\catC),
    \end{equation}
    %
    of those Weiss sheaves whose underlying functor $F: \bsc_{/M} \xrightarrow{} \catC$ satisfies the following condition:
    %
    \begin{enumerate}
        \item Denote by $f: \bsc_{/M} \xrightarrow{} \bsc$ the forgetful functor. For all $U, V \in \bsc_{/M}$
        %
        \begin{equation}
            f(U) \simeq f(V) \Rightarrow F(U) \simeq F(V).
        \end{equation}
    \end{enumerate} 
\end{definition}

\begin{remark}
    Thus, a functor is locally constant if it takes open embeddings of basics $V \xhookrightarrow{} U$, with equivalent stratifications to equivalences in $\catC$. We emphasize this last point about stratification; the disks have to have equivalent stratifications inherited from the stratified space. In the case of $\hoint$, for example, open embeddings like $(a, b) \rightarrow \left[0, c\right)$, for $0 \leq a < b \leq c$, would \emph{not} be taken to equivalences since the disks have different stratifications.
\end{remark}

\begin{remark}
    Since being locally constant according to the previous definition is only a property of the underlying functor the definition can easily be used to define locally constant prefactorization algebras too.
\end{remark}

\begin{definition}
    The $\infty$-category $\lcfa_M (\catC)$ of \emph{locally constant factorization algebras on a stratified manifold $M$ valued in $\catC$} is the full $\infty$-subcategory of $\falg_M (\catC)$ as in the pullback
    %
    \begin{equation}
        \begin{tikzcd}
            \lcfa_M (\catC) \arrow[dr, phantom, "\ulcorner", very near start] \arrow[r] \arrow[d] & \falg_M (\catC) \arrow[d] \\
            \csheaves[W, lc]_M (\catC) \arrow[r] & \csheaves[W]_M (\catC).
        \end{tikzcd}
    \end{equation}
\end{definition}

\begin{remark}\label{rem:sym_mon_inheritance}
    The $\infty$-categories of factorization algebras of all varieties acquire a symmetric monoidal structure from the symmetric monoidal structure of $\catC$ pointwise
    %
    \begin{equation}
        (F \otimes G)(U) = F(U) \otimes G(U).
    \end{equation}
    %
    The only subtlety is the cosheaf condition, where the symmetric monoidal structure is induced only if we also take into account that in $\catC$ colimits commute with its symmetric monoidal structure.

    The existence of colimits is also inherited from $\catC$ pointwise through the collection of evaluation functors $\{ \mathsf{ev}_U: \falg_X (\catC) \rightarrow \catC \}$, one for each open $U \subset X$.
\end{remark}

\subsection{The \texorpdfstring{$\infty$-}{infinity }operad of Factorization Algebras}

Now that we have introduced all the varieties of factorization algebras, it's a natural and useful question to ask what the $\infty$-operad governing them is. For prefactorization algebras, the answer comes by definition, but this is not the case for factorization algebras. In the case of stratified manifolds, we will show that the $\infty$-operad that governs locally constant factorization algebras can be taken to be $\disk_{/M}$, and the one that governs ordinary factorization algebras can be taken to be $\disk[r]_{/M}$. This result is immensely helpful in relating factorization algebras to results in the area of disk algebras. We will see one such example in \cref{ch:gluing_disk_alg}.

\begin{proposition}\label{prop:fh_disk_to_lcfa}
    Given $M$ a stratified manifold factorization homology provides a functor between the $\infty$-categories of $\disk_M$-algebras and locally constant factorization algebras $\lcfa_M$
    %
    \begin{equation}
        \int : \alg{\disk_M} (\catC) \xrightarrow{\ \ \ \ } \lcfa_M (\catC).
    \end{equation}
\end{proposition}

\begin{proof}
    We adopt a proof strategy similar to \cite[prop.3.14]{af_primer}. Unlike there, we work in the relative case of $\disk_{/M}$ instead of $\disk(\bstr)$. Since the $\infty$-category of factorization algebras is defined as a pullback, we will look for a commutative diagram involving $\alg{\disk_{/M}}$, so that, by the universal property of the pullback, we get the stated functor.

    We first observe that by definition the $\infty$-operad $\opens(M) := \mfld[r]_{/M}$. There are clear functors of $\infty$-operads
    %
    \begin{equation}
        \disk_{/M} \xhookrightarrow{\ \ \ } \mfld_{/M} \xleftarrow{\ \ \ } \mfld[r]_{/M}.
    \end{equation}
    %
    At the level of algebras over them, they give rise to the commutative diagram
    %
    \begin{equation}
        \begin{tikzcd}
            \alg{\disk_{/M}} (\catC) \arrow[d] & \alg{\mfld_{/M}} (\catC) \arrow[l] \arrow[r] \arrow[d] & \alg{\opens(M)} (\catC) \arrow[d] \\
            \mathsf{Fun}(\disk_{/M}, \catC) & \mathsf{Fun}(\mfld_{/M}, \catC) \arrow[l] \arrow[r] & \mathsf{Fun}(\opens(M), \catC),
        \end{tikzcd}
    \end{equation}
    %
    where the vertical arrows are forgetful functors. Factorization homology as a left Kan extension gives one the adjoints indicated below
    %
    \begin{equation}
        \begin{tikzcd}[row sep = large, column sep = large]
            \alg{\disk_{/M}} (\catC) \arrow[r, bend left=10, "\int"] \arrow[d] & \alg{\mfld_{/M}} (\catC) \arrow[l, bend left=10] \arrow[r] \arrow[d] & \alg{\opens(M)} (\catC) \arrow[d] \\
            \mathsf{Fun}(\disk_{/M}, \catC) \arrow[r, bend left=10, "\int"] & \mathsf{Fun}(\mfld_{/M}, \catC) \arrow[l, bend left=10] \arrow[r] & \mathsf{Fun}(\opens(M), \catC).
        \end{tikzcd}
    \end{equation}
    %
    A result found in \cite[thm.1.2.5]{aft_localstrut} (where they use slightly different notation and call locally constant sheaves constructible) gives us the equivalence
    %
    \begin{equation}
        \csheaves[W](\mfld_{/M}, \catC) \simeq \csheaves[W, lc](\mfld[r]_{/M}, \catC) =: \csheaves[W, lc]_M(\catC),
    \end{equation}
    %
    which at the level of underlying functors, is exactly the restriction along the functor $\opens(M) \xrightarrow{} \mfld_{/M}$, so that we can append this to our commutative diagram
    %
    \begin{equation}
        \begin{tikzcd}[row sep = large, column sep = large]
            \alg{\disk_{/M}} (\catC) \arrow[r, bend left=10, "\int"] \arrow[d] & \alg{\mfld_{/M}} (\catC) \arrow[l, bend left=10] \arrow[r] \arrow[d] & \alg{\opens(M)} (\catC) \arrow[d] \\
            \mathsf{Fun}(\disk_{/M}, \catC) \arrow[r, bend left=10, "\int"] \arrow[dr, dashed] & \mathsf{Fun}(\mfld_{/M}, \catC) \arrow[l, bend left=10] \arrow[r] & \mathsf{Fun}(\opens(M), \catC) \\
            & \csheaves[W](\mfld_{/M}, \catC) \arrow[r, "\simeq"] \arrow[u] & \csheaves[W, lc]_M(\catC) \arrow[u].
        \end{tikzcd}
    \end{equation}
    %
    If we can find the dashed functor which makes the diagram commute, as indicated above, we would be done with the construction. This amounts to showing that the left Kan extension $\int F$ of a functor $F \in \mathsf{Fun}(\disk_{/M}, \catC)$ along $\disk_{/M} \xhookrightarrow{} \mfld_{/M}$ is automatically a Weiss cosheaf. By the definition of $\csheaves[W](\mfld_{/M}, \catC)$, this means that the restriction of $\int F$ to $\mathsf{Fun}(\mfld[r]_{/M}, \catC)$ satisfies the cosheaf property for every Weiss sieve $\mathscr{U} \subset (\mfld[r]_{/M})_{/e}$, where $e:N \xhookrightarrow{} M$ is an open embedding. Here we notice that for the Weiss property to even make sense, we are implicitly using \cref{lem:double_slice}

    Since $\catC$ has all relevant colimits the left Kan extension $\int F$ is given pointwise by
    %
    \begin{equation}\label{eq:pointwiseKan}
        \int_e F \simeq \mathsf{colim} ((\disk_{/M})_{/e} \xrightarrow{} \disk_{/M} \xrightarrow{F} \catC),
    \end{equation}
    %
    so what we need to show is that this colimit is equivalent to the colimit
    %
    \begin{equation}\label{eq:cosheaf_colim_relative}
        \mathsf{colim} (\mathscr{U} \xrightarrow{} (\mfld[r]_{/M})_{/e} \xrightarrow{} \mfld[r]_{/M} \rightarrow \mfld_{/M} \xrightarrow{\int F} \catC),
    \end{equation}
    %
    for each covering sieve $\mathscr{U}$. Since we aren't actually trying to get the value of these colimits we can rewrite \cref{eq:pointwiseKan} into the idiosyncratic form
    %
    \begin{equation}\label{eq:idiosync_form}
        \mathsf{colim} ((\disk_{/M})_{/e} \xrightarrow{} (\mfld_{/M})_{/e} \xrightarrow{} \mfld_{/M} \xrightarrow{\int F} \catC),
    \end{equation}
    %
    which is easier to compare to \cref{eq:cosheaf_colim_relative}. Using the fact that $\disk[r]_{/M} \xrightarrow{} \disk_{/M}$ is a final functor, which is a consequence of \cite[prop.2.22]{aft_fhstrat}, and the equivalences of \cref{lem:double_slice} we can rewrite \cref{eq:idiosync_form} further into
    %
    \begin{align}
        \mathsf{colim} ((\disk[r]_{/M})_{/e} \xrightarrow{} (\disk_{/M})_{/e} \xrightarrow{} (\mfld_{/M})_{/e} \xrightarrow{} \mfld_{/M} \xrightarrow{\int F} \catC) \\ \simeq \mathsf{colim} ((\disk[r]_{/M})_{/e} \xrightarrow{} (\mfld[r]_{/M})_{/e} \xrightarrow{} \mfld[r]_{/M} \xrightarrow{} \mfld_{/M} \xrightarrow{\int F} \catC).
    \end{align}
    %
    Denoting the functor $\mfld[r]_{/N} \simeq (\mfld[r]_{/M})_{/e} \xrightarrow{} \mfld[r]_{/M} \xrightarrow{} \mfld_{/M} \xrightarrow{\int F} \catC$ by $K_F$ and comparing with \cref{eq:cosheaf_colim_relative} we need to show
    %
    \begin{equation}
        \mathsf{colim} (\mathscr{U} \xrightarrow{} \mfld[r]_{/N} \xrightarrow{K_F} C) \simeq \mathsf{colim} (\disk[r]_{N} \xrightarrow{} \mfld[r]_{/N} \xrightarrow{K_F} C),
    \end{equation}
    %
    but this already follows from part 2 of the proof of \cite[prop.2.22]{af_primer}, and is equivalent to the statement that the functor
    %
    \begin{equation}
        \mathsf{colim} (\mathscr{U} \xrightarrow{} \mfld[r]_{/N} \xrightarrow{} \mfld[r] \xrightarrow{\disk_{/-}} \cat) \xrightarrow{} \disk_{/N},
    \end{equation}
    %
    is final.
\end{proof}

\begin{remark}
    The key idea for the proof is that $\disk[r]_{/N}$ is a basis for the Weiss Grothendieck topology on manifolds. This is essentially because for each finite set of points $S \subset N$, and each Weiss cover of it $U_S$, we can take small enough disks $\{ D_s \}_{s \in S}$ around each point, by virtue of $N$ being a manifold, and their disjoint union will cover $S$, as well as satisfy $\sqcup_{s \in S} D_s \subset U_S$.
\end{remark}

From the proof of \cref{prop:fh_disk_to_lcfa} it is easy to see that we can make a similar statement for ordinary factorization algebras too:

\begin{corollary}\label{cor:fh_disk_to_falg}
    Given a stratified manifold $M$ factorization homology provides a functor
    %
    \begin{equation}
        \int: \alg{\disk[r]_{/M}} (\catC) \xrightarrow{\ \ \ \ } \falg_{M} (\catC).
    \end{equation}
\end{corollary}

\begin{theorem}\label{thm:disk_alg=lcfa}
    For each stratified manifold $M$, the previously constructed factorization homology functor provides an equivalence of $\infty$-categories between $\disk_{/M}$-algebras and locally constant factorization algebras on $M$. Equivalently, the $\infty$-operad governing locally constant factorization algebras can be taken to be $\disk_{/M}$
    %
    \begin{equation}
        \alg{\disk_{/M}} (\catC) \xrightarrow{\ \ \simeq \ \ } \lcfa_M (\catC).
    \end{equation}
\end{theorem}

\begin{proof}
    To show essential surjectivity of $\int$, for each $F \in \lcfa_M (\catC)$ we will find an equivalence $\int F| \simeq F$ in $\lcfa_M (\catC)$, with $F|$ to be defined later. Since $\lcfa_M (\catC) \xrightarrow{} \alg{\opens(M)}$ is fully faithful, this amounts to finding equivalences of prefactorization algebras, namely a family of equivalences
    %
    \begin{equation}
        \int_U F| \xrightarrow[\simeq]{\ \ \phi (U) \ \ } F(U),
    \end{equation}
    %
    one for each $(U \xhookrightarrow{} M) \in \mfld[r]_{/M}$, which preserve the multiplicative structure (see \cref{cd:fa_morphisms}). Since $F$ is a locally constant factorization algebra the functor
    %
    \begin{equation}
        \lcfa_M (\catC) \xrightarrow{} \csheaves[W, lc](\mfld[r]_{/M}, \catC) \simeq \csheaves[W](\mfld_{/M}, \catC) \xrightarrow{} \mathsf{Fun}(\mfld_{/M}, \catC),
    \end{equation}
    %
    which we omit in the notation, allows us to consider $F$ as a functor from $\mfld_{/M}$. Furthermore, since $\disk[r]_{/U}$ is a Weiss sieve we can write
    %
    \begin{align}
        F(U) &\simeq \mathsf{colim} (\disk[r]_{/U} \xrightarrow{} \disk[r]_{/M} \xrightarrow{} \mfld[r]_{/M} \xrightarrow{} \mfld_{/M} \xrightarrow{F} \catC).
    \end{align}
    %
    By consulting the commutative diagram
    % 
    \begin{equation}
        \begin{tikzcd}
            \disk[r]_{/U} \arrow[d] \arrow[r] & \disk_{/U} \arrow[d] & \\
            \disk[r]_{/M} \arrow[d] \arrow[r] & \disk_{/M} \arrow[d] \arrow[r, "F|"] & \catC, \\
            \mfld[r]_{/M} \arrow[r] & \mfld_{/M} \arrow[ru, "F"'] &  
        \end{tikzcd}
    \end{equation}
    %
    and using the fact that $\disk[r]_{/U} \xrightarrow{} \disk_{/U}$ is final (\cite[prop.2.22]{aft_fhstrat}) immediately gives us that
    %
    \begin{equation}
        F(U) \simeq \mathsf{colim} (\disk_{/U} \xrightarrow{} \disk_{/M} \xrightarrow{F|} \catC) =: \int_U F|.
    \end{equation}
    %
    To preserve the multiplicative structure, these equivalences have to be natural, and there also has to be a commutative diagram
    %
    \begin{equation}\label{eq:mult_strut_comm_square}
        \begin{tikzcd}
            \otimes_i \int_{U_i} F| \arrow[r, "\simeq"] \arrow[d, "\otimes_i \phi (U_i)"', "\simeq"] & \int_{\sqcup_i U_i} F| \arrow[d, "\phi (\sqcup_i U_i)", "\simeq"']\\
            \otimes_i F (U_i) \arrow[r, "\simeq"] & F (\sqcup_i U_i),
        \end{tikzcd}
    \end{equation}
    %
    for each collection of disjoint open sets $\{U_i\}$. Naturality is immediate from the construction because, as already used, each inclusion of open subsets $V \xhookrightarrow{} U$ gives a full subcategory inclusion $\disk[r]_{/V} \xhookrightarrow{} \disk[r]_{/U}$. On the other hand, the existence of the commutative diagram is guaranteed by the equivalence
    %
    \begin{equation}
        \disk[r]_{/\sqcup_i U_i} \xrightarrow{\ \ \simeq \ \ } \bigtimes_i \disk[r]_{/U_i}.
    \end{equation}

    To show full faithfulness we need to find equivalences of morphism spaces
    %
    \begin{equation}
        \mathsf{Hom}_{\alg{\disk_{/M}} (\catC)} (A, B) \simeq \mathsf{Hom}_{\lcfa_M (\catC)} (\int A, \int B),
    \end{equation}
    %
    for each $A, B \in \alg{\disk_{/M}}$. However, since the functors
    %
    \begin{align}
        &\alg{\disk_{/M}} (\catC) \xrightarrow{\mathsf{f.f.}} \alg{\disk[r]_{/M}} (\catC) &\lcfa_M (\catC) \xrightarrow{\mathsf{f.f.}} \alg{\mfld[r]_{/M}} (\catC)
    \end{align}
    %
    are both fully faithful we are reduced to finding equivalences
    %
    \begin{equation}
        \mathsf{Hom}_{\alg{\disk[r]_{/M}} (\catC)} (A, B) \simeq \mathsf{Hom}_{\alg{\mfld[r]_{/M}} (\catC)} (\int A, \int B).
    \end{equation}
    %
    The existence of these is exactly the requirement that factorization homology in the usual sense is fully faithful, which is part of the statement of \cite[lem.2.17]{aft_fhstrat}
\end{proof}

As before, the case of ordinary factorization algebras gets a similar statement whose proof goes along the same lines:

\begin{corollary}\label{cor:disk_alg=falg}
    The $\infty$-operad governing factorization algebras on a stratified manifold $M$ can be taken to be $\disk[r]_{/M}$,
    %
    \begin{equation}
        \alg{\disk[r]_{/M}} (\catC) \xrightarrow{\ \ \simeq \ \ } \falg_M (\catC).
    \end{equation}
\end{corollary}

\begin{remark}
    A version of \cref{thm:disk_alg=lcfa} was proven as \cite[thm.6]{gtz2014} in the case of smooth manifolds. The proof there, however, made crucial use of choosing a Riemannian metric on the manifold and constructing geodesically convex neighborhoods. This technique is, at least presently, not extendable to the stratified case, but our proof above subverts the need for it. 
\end{remark}

The $\infty$-operad $\disk_{/M}$ is, in general, harder to deal with than its symmetric monoidal counterpart $\disk(\bstr)$. The next lemma outlines a certain situation where this is not the case.

\begin{lemma}\label{lem:disk/M_to_disk}
    Let $M$ be a stratified manifold. If we can find an $\infty$-category of basics $\bstr_M$ such that $M$ admits a $\bstr_M$-structure and such that
    %
    \begin{equation}
        \mathsf{Hom}_{\mfld(\bstr_M)} (V, M) \simeq *
    \end{equation}
    %
    for all $V \in \bstr_M$, then there is an equivalence of symmetric monoidal $\infty$-categories
    %
    \begin{equation}
        \mathsf{Env}(\disk_{/M}) \xrightarrow{\ \ \simeq \ \ } \disk(\bstr_M).
    \end{equation}
\end{lemma}

\begin{remark}
    If we limit $M$ to be a basic then the requirements of the lemma are exactly that $M$ is final in $\bstr_M$.
\end{remark}

\begin{proof}
    We follow the proof of \cite[cor.2.33]{aft_fhstrat}. Using \cref{rem:disk_b=disk_bsc}, the forgetful functor from the slice $\infty$-operad, which is a map of $\infty$-operads, is what will provide the equivalence
    %
    \begin{equation}
        \disk_{/M} \simeq \disk(\bstr_M)_{/M} \xrightarrow{\ \ \ \ } \disk(\bstr_M).
    \end{equation}
    %
    This functor is an equivalence on maximal $\infty$-subgroupoids because for any $V \in \disk(\bstr_M)$ the space of morphisms to $M$ is contractible, so, up to equivalence it is unique. %To check that it is fully faithful we need to show that the induced maps
    %
    %\begin{equation}
    %    \mathsf{Hom}_{\disk(\bstr)_{/U}} (V \xhookrightarrow{} U, V' \xhookrightarrow{} U) \xrightarrow{\ \ \ \ } \mathsf{Hom}_{\disk(\bstr)} (V, V')
    %\end{equation}
    %
    %are equivalences. Giving a functor $\disk (\bstr) \xrightarrow{} \disk (\bstr)_{/U}$ is the same as giving a functor
    %
    %\begin{equation}
    %    \disk (\bstr) ^{\vartriangleright} \xrightarrow{} \disk (\bstr)_{/U},
    %\end{equation}
    %
    %which sends the cone point to $U$ (see e.g. \cite[prop.3.2]{joyal}).
    Full faithfulness is provided by the fact that the functor on the active $\infty$-subcategories $\disk_{/M} \xrightarrow{} \disk(\bstr_M)$ is a right fibration. 
\end{proof}

The lemma says that for stratified manifolds $M$ that satisfy the conditions, the classification of locally constant factorization algebras on $M$, i.e. algebras over $\disk_{/M}$ simplifies to the classification of $\disk(\bstr_M)$-algebras in the usual sense
%
\begin{equation}
    \lcfa_M (\catC) \simeq \mathsf{Fun}^\otimes (\mathsf{Env}(\disk_{/M}), \catC) \simeq \alg{\disk(\bstr_M)} (\catC).
\end{equation}
%
This is an improvement because $\disk(\bstr_M)$-algebras are easier to work with, one reason being that $\disk(\bstr_M)$ has the benefit of being not just an $\infty$-operad but even a symmetric monoidal $\infty$-category.

The results of \cref{thm:disk_alg=lcfa} and \cref{cor:disk_alg=falg} can also be seen as lowering the amount of data that is necessary to say that we have defined a factorization algebra on a stratified manifold. There is a similar, but slightly weaker result by \cite{cg2016}, which nonetheless works for all Hausdorff topological spaces. We recount this result here for comparison.

\begin{definition}
    A \emph{factorizing basis} of a topological space $X$ is a basis $\{ U_i \xhookrightarrow{} X\}_{i \in I}$ for the topology of $X$ which is closed under finite intersections, and which satisfies that for each finite set $S \subset X$, there exists a finite sub-collection of pairwise disjoint open subsets $\{ U_j \xhookrightarrow{} X\}_{j \in J}$, for which $S \subset \bigsqcup_{j \in J} U_j$.
\end{definition}

\begin{definition}
    We will call factorization algebras defined only on the open subsets of an open cover $\mathscr{U}$ (in particular, for example, a factorizing basis), a $\mathscr{U}$-factorization algebra and the $\infty$-category of such $\falg_{\mathscr{U}}(\catC)$.
\end{definition}

\begin{theorem}[\cite{cg2016}]\label{thm:fa_from_basis}
    Given a Hausdorff topological space $X$, there is an equivalence of $\infty$-categories between the $\infty$-categories of $\mathscr{U}$-factorization algebras defined on a factorizing basis $\mathscr{U}$ and factorization algebras defined on the full topological space $X$
    %
    \begin{equation}
        \begin{tikzcd}
            \falg_X(\catC) \arrow[rr, bend left=10, "\mathrm{-|_{\mathscr{U}}}"] &  & \falg_{\mathscr{U}}(\catC) \arrow[ll, bend left=10, "\mathrm{ext}"],
        \end{tikzcd}
    \end{equation}
    %
    where the top functor is given by restriction.
\end{theorem}

\begin{remark}
    Looking into the proof of this statement we see that the value of the extension on open sets $U \subset X$ is defined as
    %
    \begin{equation}
        \mathrm{ext}(F)(U) := \cech(\mathscr{U}_U, F),
    \end{equation}
    %
    where $\mathscr{U}_U$ is a Weiss cover of $U$ generated by $\mathscr{U}$. That such a cover exists is already guaranteed by the Hausdorffness of $X$ and the basis property of $\mathscr{U}$. Namely, given any finite set $S \subset U$, Hausdorffness gives us the existence of pairwise disjoint open sets $\{ V_s \ni s\}_{s \in S}$, while the basis property of $\mathscr{U}$ gives us open subsets $\{ U_s \in \mathscr{U} \}_{s \in S}$ such that $s \in U_s \subset V_s$. $\sqcup_{s \in S} U_s$ then gives an open set that covers $S$.
\end{remark}

\begin{remark}
    The proof of \cref{thm:fa_from_basis} can be found in \cite[ch.7.2]{cg2016}, and we will not reproduce it here. The target category there is the category of chain complexes, but it holds more generally in $\catC$ by considering simplicial objects and their geometric realizations (which exist by the colimit assumption on $\catC$) instead.

    As mentioned, in the stratified manifold case, this is an easy corollary of the proof of \cref{prop:fh_disk_to_lcfa}, where we show that taking all disks as the Weiss cover of choice reproduces the result that we would have gotten with any other Weiss cover. It is important to point out though that disks are not necessarily closed under intersections, which means that we don't have the opposite implication, and the methods to prove \cref{prop:fh_disk_to_lcfa} are necessary.
\end{remark}

\subsection{Operations on Factorization Algebras}

There are a few important operations that we can do with factorization algebras (and the other mentioned variants) that will be important for our considerations. They allow us to compare factorization algebras from different spaces and will play a big role in any kind of classification statement one might make.

\begin{proposition}\label{prop:pushforward}
    Given a continuous map $f:X \rightarrow Y$ between topological spaces, there are pushforward functors
    %
    \begin{align}
        &f_*: \alg{\opens[s](X)} \xrightarrow{\quad} \alg{\opens[s](Y)} &f_*: \falg_X \xrightarrow{\quad} \falg_Y,
    \end{align}
    %
    which, on objects, are given by the prescription
    %
    \begin{equation}
        f_*F (U) := F(f^{-1}U).
    \end{equation}
\end{proposition}

\begin{proof}
    By the definition of continuity, the case of prefactorization algebras is trivial. Thus, the only thing we are left to show is that if $F$ satisfies the Weiss cosheaf property then so does $f_* F$. Given a Weiss cover $\{U_i \xhookrightarrow{} U\}_{i \in I}$ of $U$, we observe that $\{f^{-1}U_i \xhookrightarrow{} f^{-1}U\}_{i \in I}$ is a Weiss cover of $f^{-1}U$. Namely, if $S \subset f^{-1}U$ is a finite subset of $U$, then $f(S)$ is contained in some $U_i$ by the Weiss cover property of $\{U_i \xhookrightarrow{} U\}_{i \in I}$. But in that case $S$ has to be contained in $f^{-1}U_i$, giving it the Weiss cover property too. Thus, by the definition of the pushforward on objects the Weiss cosheaf property is preserved.
\end{proof}

The case of locally constant factorization algebras is different when it comes to the pushforward. This is because it's not immediate that local constancy is preserved when pushed forward. However, if we limit the types of maps we pushforward with we can still construct a functor. The following two results give the flavor of what is required.

\begin{proposition}[{\cite[prop.15]{ginot2015}}]
    If $f: X \rightarrow Y$ is a locally trivial fibration between smooth manifolds then the pushforward functor exists even between the $\infty$-categories of locally constant factorization algebras
    %
    \begin{equation}
        f_*: \lcfa_X \xrightarrow{\quad} \lcfa_Y.
    \end{equation}
\end{proposition}

\begin{corollary}\label{cor:pushforward_for_lc}
    Let $f: M \xrightarrow{} N$ be a constructible bundle of stratified manifolds. Then the pushforward functor for factorization homology of \cref{thm:fh_pushforward} serves as a pushforward
    %
    \begin{equation}
        f_*: \lcfa_M \xrightarrow{\quad} \lcfa_N,
    \end{equation}
    %
    by using \cref{thm:disk_alg=lcfa}.
\end{corollary}

\begin{remark}\label{rem:fh_is_pushingforward}
    Having defined the pushforward functor of factorization algebras we can consider the map $\mathsf{p}:M \rightarrow *$. Given any $A \in \alg{\disk(\bstr)_{/M}}$ the factorization algebra $F_A$ generated by $A$ satisfies
    %
    \begin{equation}
        \int_M A  = F_A(M) \simeq (\mathsf{p}_* F_A)(*).
    \end{equation}
    %
    The one point manifold is a very simple space, which makes the concepts of prefactorization algebras, factorization algebras and locally constant factorization algebras coincide. All of them are in fact given by a pointed object of the target category. Evaluation at $*$ simply returns the underlying object. Thus, in a sense evaluating factorization homology on a space $M$ is the same procedure as pushing-forward by the map $\mathsf{p}$. Versions of factorization homology that can evaluate lower dimensional manifolds (as compared to the structure of the disk algebra), for example as in \cite[cor.2.29]{aft_fhstrat}, can then be seen as relaxing this pushforward from $*$ to a manifold with more structure.
\end{remark}

\begin{lemma}
    Let $u: X \rightarrow \hat{X}$ be the morphism of \cref{ex:forget_strat} that forgets the stratification.
    The functor $u_*: \lcfa_{X} (\catC) \rightarrow \lcfa_{\hat{X}} (\catC)$ has a fully faithful left adjoint.
\end{lemma}

\begin{proof}
    Consider the functor $\hat{-}: \falg_{\hat{X}} \rightarrow \falg_{X}$, which acts as $\hat{F}(U) := F(u(U))$, namely it returns algebras that evaluate open subsets by forgetting their stratification first. We claim this functor is the left adjoint of $u_*$. Indeed, given a morphism $(\phi: \hat{F} \rightarrow G) \in \falg_{X}$, i.e. a family of morphisms $\phi(U): \hat{F}(U) \rightarrow G(U)$ for all opens $U$ in $X$, it is easy to verify that we can construct a morphism of algebras over $\hat{X}$, $\hat{\phi}(u(U)): F(u(U)) \rightarrow u_*G (u(U))$, since $\hat{F}(U) = F(u(U))$ and $u_*G(u(U)) = G(u^{-1}(u(U))) = G(U)$. The last equality holds because $u$ is an injective map. In fact, this last observation also proves that the unit of this adjunction is an isomorphism, granting the full faithfulness.
\end{proof}

\begin{remark}
    In fact, the above proof is true more generally for any map of stratified spaces that is a homeomorphism of the underlying topological spaces. This means that locally constant factorization algebras record the data of coarser stratified structures as $\infty$-subcategories. Forgetting local constancy, the proof, of course, applies to factorization algebras of all flavors, however only locally constant factorization algebras can detect the stratified structure, so in all other cases that we have considered the above functor is even an equivalence, and not just fully-faithful.
\end{remark}

In the opposite direction, we do not, in general, have a pullback functor. \cite{cg2016} provide a construction of a pullback in the case of open immersions, but we will only focus on the case of restrictions. Namely, given an open subset $U \subset X$ of a topological space $X$, and given a factorization algebra $F \in \falg_X$ we can clearly define a factorization algebra $F|_{U} \in \falg_U$ by restricting to those open subsets that are fully contained in $U$. Furthermore, this clearly holds not only for factorization algebras, but prefactorization algebras and locally constant factorization algebras too.

In the special case of product spaces $X \times Y$, we now know that the projections $\pi_1: X \times Y \rightarrow X$ and $\pi_2: X \times Y \rightarrow Y$, give us pushforwards. For $\pi_1$, for example, this essentially uses the fact that if we can evaluate all open sets of $X \times Y$ then we can definitely evaluate the open sets that look like $U \times Y$, with $U \subset X$ an open set. But in this case we can do even more, because we can even evaluate the more granular open subsets $U \times V$ with $U \subset X$ and $V \subset Y$ opens. More formally, we claim:
%
\begin{proposition}\label{prop:exp_of_products}
    Let $X$ and $Y$ be topological spaces. There is a functor from the $\infty$-category of prefactorization algebras on the product $X \times Y$ to the $\infty$-category of prefactorization algebras on $X$ valued in the category of prefactorization algebras on $Y$
    %
    \begin{equation}
        \bar{\pi}: \alg{\opens(X \times Y)}(\catC) \xrightarrow{\qquad} \alg{\opens(X)} (\alg{\opens(Y)} (\catC)).
    \end{equation}
    %
    This functor descends to factorization algebras too
    %
    \begin{equation}
        \bar{\pi}: \falg_{X \times Y}(\catC) \xrightarrow{\qquad} \falg_{X}(\falg_{Y}(\catC)).
    \end{equation}
\end{proposition}

\begin{remark}
    The conditions we imposed on $\catC$ allowed us, in \cref{rem:sym_mon_inheritance}, to inherit a symmetric monoidal structure on the $\infty$-categories of factorization algebras of all varieties. It also allowed us to inherit the existence of colimits. This is the reason why the above can even be stated.
\end{remark}

\begin{proof}
    Indeed, given opens $U \subset X$ and $V \subset Y$, the values we assign are $(\bar{\pi}F) (U)(V) = F(U \times V)$. Fixing an open subset $U \subset X$, we obviously get a prefactorization algebra $(\pi_2|_U)_* (F|_U) \in \alg{\opens(Y)}$ by pushing forward with $\pi_2|_U: U \times Y \rightarrow Y$, which shows that $\bar{\pi}F$ is valued in $\alg{\opens(Y)}$. The only thing left to show is that $\bar{\pi} F$ has the structure of a prefactorization algebra on $X$. To do this, for each multi-morphism $(\{ U_i \}_{i \in I} \rightarrow U) \in \opens(X)$ we assign a map $\bar{\pi}F (\{ U_i \}_{i \in I}, U)$ of factorization algebras on $Y$. Such an algebra map is specified by giving its value on all opens of $Y$ separately. We can thus assign
    %
    \begin{equation}
        \bar{\pi}F (\{ U_i \}_{i \in I}, U)(V) = F(\{ U_i \times V \}_{i \in I}, U \times V),
    \end{equation}
    %
    which uses the projections $\pi_1|_V : X \times V \rightarrow X$ to assign $\pi_1|_V^{-1}(U) = U \times V$.

    It is not hard to check that the above also holds for the example of factorization algebras on topological spaces, by using \cref{thm:fa_from_basis}. However, we'll focus on manifolds, in which case, the construction from above immediately works since we now have to do it for $\disk[r]_{/X}$ instead of $\mfld[r]_{/X}$. The only things to mention is that products of disks are again disks \cite[cor.3.4.9]{aft_localstrut}.
\end{proof}

\begin{proposition}\label{prop:exp_of_products_lc}
    Let $M$ and $N$ be stratified manifolds. The functor $\bar{\pi}$ descends to locally constant factorization algebras, and moreover, it is an equivalence of $\infty$-categories
    %
    \begin{equation}
        \bar{\pi}: \lcfa_{M \times N}(\catC) \xrightarrow{\ \ \simeq \ \ } \lcfa_{M}(\lcfa_{N}(\catC)).
    \end{equation}
\end{proposition}

\begin{remark}
    The above proposition also appears as \cite[prop.18]{ginot2015}. The equivalence proven there is for the case of smooth manifolds and relies on the local proof of \cite{lurie_ha} for $\mathbb{R}^n$. Using \cref{thm:disk_alg=lcfa}, the statement is equivalent to the fact that there is an equivalence of $\infty$-operads
    %
    \begin{equation}
        \disk_{/M} \otimes \disk_{/N} \xrightarrow{\ \ \simeq \ \ } \disk_{/M \times N},
    \end{equation}
    %
    with the tensor product of $\infty$-opeards. Again for smooth manifolds this is found in \cite[ex.5.4.5.5]{lurie_ha}. In fact, this version is the one that easily generalizes to the stratified case.
\end{remark}

\begin{proof}
    The proof of existence of the functor goes along the same lines as the proof of \cref{prop:exp_of_products} because of \cref{thm:disk_alg=lcfa}. The thing to take into account is that the projection maps are both, trivially, constructible bundles so by \cref{cor:pushforward_for_lc}, pushing forward by them yields locally constant factorization algebras again. This combined with the fact that for any $\infty$-operads $\mathscr{O}$, $\mathscr{O}'$ and $\mathscr{C}$ we have an equivalence
    %
    \begin{equation}
        \alg{\mathscr{O}} (\alg{\mathscr{O}'} (\catC)) \simeq \alg{\mathscr{O}'} (\alg{\mathscr{O}} (\catC))
    \end{equation}
    %
    allows us to conclude that the functor lands in locally constant factorization algebras
    %
    \begin{equation}
        \bar{\pi}: \lcfa_{X \times Y}(\catC) \xrightarrow{\ \ \ \ } \lcfa_{X}(\lcfa_{Y}(\catC)).
    \end{equation}

    For the equivalence, we adapt \cite[ex.5.4.5.5]{lurie_ha}, as mentioned above. Namely, using that technology, the only thing we need to prove is that there is an equivalence between $\infty$-categories induced by the functor
    %
    \begin{align}
        \bsc_{/M} \times \bsc_{/N} &\xrightarrow[\simeq]{\ \ \times \ \ } \bsc_{/M \times N} \notag\\
        ((U \xhookrightarrow{} M), (V \xhookrightarrow{} N)) &\mapsto (U \times V \xhookrightarrow{} M \times N).
    \end{align}
    %
    ......
\end{proof}

\begin{remark}
    The discussion at \cref{rem:fh_is_pushingforward} implies that one way to see the above proposition is as related to the Fubini theorem for factorization homology \cite[cor.2.29]{aft_fhstrat}.
\end{remark}

%\subsection{Inheritance from a Covering Space}

%{\color{red} SHOULD THIS STAY? OR JUST CITE SPHERE RESULT FROM SOMEWHERE}

%We can also induce factorization algebras on a space $X$ if we know how to describe them on a covering space of $X$. The proofs of the statements below require the full machinery regarding pullbacks of factorization algebras, so we will omit them. They can be found in \cite[ch.7.2]{cg2016}. For the extension to the stratified case, see \cite{ginot2015}.

%\begin{definition}
%    Let $G$ be a discrete group that acts on a topological space $X$. A $G$-equivariant factorization algebra on $X$ is a factorization algebra $F \in \falg_X (\catC)$ together with a family of equivalences
%    %
%    \begin{equation}
%        \{ \theta_g : g^*F \xrightarrow{\ \ \simeq \ \ } F \}_{g \in G},
%    \end{equation}
%    %
%    such that $\theta_e = \mathrm{id}$ and $\theta_{g h} = \theta_h \circ h^*(\theta_g): h^* g^* F \xrightarrow{\simeq} F$. We write $(\falg_X (\catC))^G$ for the full $\infty$-subcategory spanned by the $G$-equivariant factorization algebras.
%\end{definition}

%\begin{theorem}[{\cite[prop.4.0.1]{cg2016}}]\label{thm:quotient_fas}
%    Let $X$ be a Hausdorff topological space, and $G$ be a discrete group that has a covering space action on $X$. The pullback along the open immersion $q: X \rightarrow X / G$ is an equivalence of $\infty$-categories
%    %
%    \begin{equation}
%        q^* : \falg_{X / G} (\catC) \xrightarrow{\ \ \simeq \ \ } (\falg_{X} (\catC))^G,
%    \end{equation}
%    %
%    between factorization algebras on the quotient space and $G$-equivariant factorization algebras on the covering space. If $X$ is further a stratified manifold the equivalence restricts to an equivalence of the $\infty$-categories of locally constant factorization algebras
%    %
%    \begin{equation}
%        q^* : \lcfa_{X / G} (\catC) \xrightarrow{\ \ \simeq \ \ } (\lcfa_{X}(\catC))^G.
%    \end{equation} 
%\end{theorem}

\subsection{Factorization Algebras on Intervals}\label{ssec:lcfa_on_1d_man}

As was the case with factorization homology, so too with factorization algebras we now turn to a few very important constructions of locally constant factorization algebras on intervals. Namely, we will consider how we can construct a locally constant factorization algebra on the spaces $\mathbb{R}$ (a.k.a. the open interval) and $\hoint$ (a.k.a. the half-open interval). These will be a very important backbone for intuition about locally constant factorization algebras, as well as a key part of proofs later on. We finish with factorization algebras for the closed interval $[-1,1]$.

\begin{construction}\label{con:lcfas_on_R}
    Consider a unital, (homotopy) associative algebra $A$ in the category $\catC$. For a first pass we use \cref{thm:fa_from_basis} to construct a factorization algebra out of this data. We first check that the disks $\disk[r]_{/\mathbb{R}}$ of $\mathbb{R}$ form a factorizing basis. This is true since the disks are always a basis for any manifold, they are factorizing since we have all disjoint unions, and they are closed under finite intersections because the disks of $\mathbb{R}$ are intervals. Therefore, by \cref{thm:fa_from_basis}, we need only assign values to these. Given any disk $U$ we assign the same value, $F_A(U) := A$. Similarly, given a multi-morphism $\sqcup_{i \in I} U_i \xhookrightarrow{} U$, with $I$ non-empty, we assign the map given by the multiplication of $A$
    %
    \begin{equation}
        F_A(\sqcup_{i \in I} U_i \xhookrightarrow{} U) := \otimes_{i \in I} A \rightarrow A.
    \end{equation}
    %
    The implicit convention, is that the ordering of the intervals, provided by the standard orientation (or framing) of $\mathbb{R}$, determines the order in which we multiply. Associativity forbids any other ordering except the completely opposite one, which would yield the opposite multiplication, and thus the opposite algebra. Finally, in the case of $\emptyset \xhookrightarrow{} U$, we assign the map that chooses the unit $\mathbb{1} \rightarrow A$. At this point we have constructed a prefactorization algebra on $\mathbb{R}$. To use \cref{thm:fa_from_basis} we need to first check the Weiss cosheaf condition. But because intervals are closed under finite intersections the \v{C}ech nerve definition of \cref{rem:check_nerve} makes this easy; the simplicial object $\cech_{\bullet}(\disk[r]_{/\mathbb{R}}, F_A)$ in all degrees will be a coproduct of copies of $A$. Thus, $F_A$ is indeed a $\disk[r]_{/\mathbb{R}}$-factorization algebra and can be extended to a factorization algebra on $\mathbb{R}$. By definition, it is also obviously locally constant.

    In this simple case the disks are closed under finite intersections, so the construction works out. More generally, one would need to find another factorizing basis. In the case of smooth manifolds one possible way is to choose a Riemannian metric and take the geodesically convex neighborhoods. An alternative is to get rid of the property of being closed under finite intersections altogether. It turns out, because of \cref{thm:disk_alg=lcfa}, that this is indeed possible, and that we can always stick to using disks even in the most general situations.

    In whatever way we go about it, it is immediate that we have constructed a functor $\alg{\mathbb{E}_1}(\catC) \rightarrow \lcfa_{\mathbb{R}} (\catC)$ from the $\infty$-category of unital, (homotopy) associative algebras, or $\mathbb{E}_1$-algebras to the $\infty$-category of locally constant factorization algebras on $\mathbb{R}$. In fact, we claim that this functor is actually an equivalence, i.e., that every locally constant factorization algebra on $\mathbb{R}$ is equivalent to one induced like in the construction.
\end{construction}

\begin{proposition}\label{prop:R_gives_E1}
    There is an equivalence of $\infty$-categories
    %
    \begin{equation}
        \alg{\mathbb{E}_1}(\catC) \xrightarrow{\simeq} \lcfa_{\mathbb{R}} (\catC).
    \end{equation}
\end{proposition}

\begin{proof}
    What is left to show is the essential surjectivity of the functor. This holds because every disk in $\mathbb{R}$ is diffeomorphic to $\mathbb{R}$ itself. So, given $F \in \lcfa_{\mathbb{R}}$, we can get an underlying object for our $\mathbb{E}_1$ algebra as $A = F(\mathbb{R})$. The previous observation and the local constancy then force the value on each disk to be equivalent to this. The space of embeddings of two disks $\mathbb{R} \sqcup \mathbb{R} \xhookrightarrow{} \mathbb{R}$ is, up to homotopy, equivalent to two points, which provide exactly the multiplication map $ A \otimes A \rightarrow A$ of the algebra and its opposite multiplication.  Associativity, up to homotopy, comes about exactly because all embeddings of any number of disks can, up to homotopy, be factorized through the embedding of two disks at a time. As before, the unit comes from the map $F(\emptyset \xhookrightarrow{} \mathbb{R}) = (\mathbb{1} \rightarrow A)$. Thus, we have constructed an $\mathbb{E}_1$-algebra from the given data, and the proposition holds.
\end{proof}

\begin{construction}\label{con:lcfas_on_hoint}
    Consider a unital, (homotopy) associative algebra $A$ in the category $\catC$, as above, together with a unital right module $M$ of $A$ in the category $\catC$. From this data we will construct a locally constant factorization algebra $F_{(M, A)}$ on the stratified space $\hoint$. Considering \cref{con:lcfas_on_R} and the open embedding $\mathbb{R} \cong \mathbb{R}_{>0} \xhookrightarrow{} \hoint$, we will choose the restriction to be $F_{(M,A)}|_{\mathbb{R}} = F_A$, i.e. any disk that doesn't include the point $0 \in \hoint$, we regard as a disk of $\mathbb{R}$ through the given map, and we assign the value $A$ to it like in the \cref{con:lcfas_on_R}. This leaves us only with the stratified disks $U_*$ that contain the point $0 \in \hoint$. To these we assign the module $F_{(M,A)}(U_*) = M$. Since there can be at most one stratified disk that includes the point $0 \in \hoint$, the maps that we have to assign values to look like $U_* \sqcup (\sqcup_{i \in I} U_i) \xhookrightarrow{} U'_*$, but this is exactly what is provided by the right module structure
    %
    \begin{equation}
        F_{(M,A)} (U_* \sqcup (\sqcup_{i \in I} U_i) \xhookrightarrow{} U'_*) = M \otimes (\otimes_{i \in I} A) \rightarrow M.
    \end{equation}
    %
    Of course the pointing of the module comes from $F_{(M,A)}(\emptyset \xhookrightarrow{} U_*) = \mathbb{1} \rightarrow M$. As before, even more is true:
\end{construction}

\begin{proposition}\label{prop:hoint_gives_modules}
    There is an equivalence of $\infty$-categories between the $\infty$-categories of $\mathbb{E}_1$-algebras together with a right module and locally constant factorization algebras on the half-open interval
    %
    \begin{equation}
        \mathsf{RMod}(\catC) \xrightarrow{\simeq} \lcfa_{\hoint} (\catC).
    \end{equation}
\end{proposition}

\begin{proof}
    The proof goes along the same lines as the proof of \cref{prop:R_gives_E1}. We can find the module by evaluating on $\hoint$, and we can find the algebra by evaluating on $\hoint \setminus \{ 0 \} \cong \mathbb{R}$.
\end{proof}

\begin{remark}\label{rem:left_or_right_module}
    The fact that we chose left modules to provide the data in \cref{prop:hoint_gives_modules}, does not play much of a role because a left module is exactly a right module of the opposite algebra, giving $\mathsf{LMod}(\catC) \simeq \mathsf{RMod}(\catC)$. Where the distinction comes up, is if we want to fix the $\mathbb{E}_1$-algebra away from $0 \in \hoint$ beforehand. In that case we have to use one of the two possible conventions on the order of multiplication. If we choose the increasing convention then the subset containing $0 \in \hoint$ is on the left making it a right module, while with the opposite convention it would be a left module of the opposite algebra.
\end{remark}

It's not hard to extend \cref{con:lcfas_on_R} and \cref{con:lcfas_on_hoint} to the closed interval $[-1,1]$ by hand, but through \cref{thm:disk_alg=lcfa} we can see that \cref{prop:disk1bor_over_int=ORL} and \cref{prop:env_ORL=env_assocRL} already do all the necessary work.

\begin{corollary}
    There is an equivalence between the $\infty$-categories of locally constant factorization algebras on the closed interval and algebras over the $\infty$-operad $\mathsf{Assoc^{RL}}$
    %
    \begin{equation}
        \lcfa_{[-1,1]} (\catC) \xrightarrow{\ \ \simeq \ \ } \alg{\mathsf{Assoc^{RL}}} (\catC).
    \end{equation} 
\end{corollary}

\begin{remark}
    Another perspective on why all of these constructions look the way they do is provided by \cref{lem:disk/M_to_disk}. It applies in all of the above cases:
    %
    \begin{enumerate}
        \item For $\mathbb{R}$, the convenient $\infty$-category of basics is $\bstr = \mathsf{D}_1^*$,
        \item For $\hoint$, the convenient $\infty$-category of basics is $\bstr = \mathsf{D}_1^{\partial, *}$ and
        \item Similarly, for $[-1,1]$ the convenient $\infty$-category of basics is again $\bstr = \mathsf{D}_1^{\partial, *}$.
    \end{enumerate}
    %
    We can see that even though factorization algebras, as we have defined them here, don't detect the tangential structure of the manifold, it is usually favorable, if possible, to give the manifold some structure anyway. In particular, the rigid structure of framing is very useful because it massively reduces the spaces of allowed open embeddings.
\end{remark}

\subsection{Factorization Algebras on Euclidean spaces}\label{ssec:lcfa_on_Rn}

In this section we want to describe locally constant factorization algebras on Euclidean spaces $\mathbb{R}^n$. By \cref{lem:disk/M_to_disk} we can hope for an $\infty$-category of basics such that we simplify the situation down to $\disk (\bstr)$-algebras. In fact, since $\mathbb{R}^n$ is frameable an $\infty$-category of basics that we can choose is $\mathsf{D}_n^* \simeq * \xrightarrow{\{ \mathbb{R}^n\}} \bsc$. Specifically, this makes us focus on framed $n$-dimensional disk algebras
%
\begin{equation}
    \lcfa_{\mathbb{R}^n} (\catC) \simeq \alg{\disk (\mathsf{D}_n^*)} (\catC).
\end{equation}
%

\begin{theorem}[{\cite{lurie_ha}...}]
    There is an equivalence of $\infty$-categories between the $\infty$-categories of locally constant factorization algebras on $\mathbb{R}^n$ and $\mathbb{E}_n$-algebras
    %
    \begin{equation}
        \alg{\mathbb{E}_n} (\catC) \xrightarrow{\ \ \simeq \ \ } \lcfa_{\mathbb{R}^n} (\catC).
    \end{equation}
\end{theorem}

\begin{proof}
    With our setup, thanks to \cref{thm:disk_alg=lcfa} and \cref{lem:disk/M_to_disk}, it is sufficient to show that there is an equivalence of $\infty$-operads
    %
    \begin{equation}
        \disk (\mathsf{D}_n^*) \xrightarrow{\ \ \simeq \ \ } \mathbb{E}_n.
    \end{equation}
    %
    But this is just the classical fact, that the little $n$-disks operad and the little $n$-cubes operad are equivalent, in disguise.
\end{proof}

\begin{remark}
    We already encountered the $n=1$ version of the proposition above when we discussed locally constant factorization algebras on the open interval in \cref{prop:R_gives_E1}, and the construction there gives us an intuition about how to actually construct the locally constant factorization algebra from the data of the $\mathbb{E}_n$-algebra. The theorem formalizes that this assignment is, in fact, an equivalence.
\end{remark}

\begin{remark}[{\cite[prop.3.16]{francis2013}, \cite[ex.5.5.4.16]{lurie_ha}}]
    In the case of Euclidean spaces like $\mathbb{R}^n$, essentially because of translation invariance, a special thing happens when we restrict away from the origin. That is, we know that given a locally constant factorization algebra $F$ on $\mathbb{R}^n$ we can restrict it to any open subset like, for example, $\mathbb{R}^n \setminus \{ 0 \} \cong S^{n-1} \times \mathbb{R}$ to get another locally constant factorization algebra $F|_{S^{n-1} \times \mathbb{R}}$. By \cref{prop:exp_of_products_lc} we know that $F|_{S^{n-1} \times \mathbb{R}} \in \lcfa_{\mathbb{R}} (\lcfa_{S^{n-1}} (\catC))$, so that in particular it is an $\mathbb{E}_1$-algebra. If we pushforward to $\mathbb{R}$, by the discussion at \cref{rem:fh_is_pushingforward} we could denote the resulting $\mathbb{E}_1$-algebra by
    %
    \begin{equation}
        \int_{S^{n-1}} F.
    \end{equation}
    %
    What \cite[prop.3.16]{francis2013} shows is then:
\end{remark}

\begin{proposition}\label{univ_env_for_En}
    Given a locally constant factorization algebra $F$ on $\mathbb{R}^n$, its universal enveloping algebra is given by $\int_{S^{n-1}} F$, i.e. there is an equivalence of $\infty$-categories
    %
    \begin{equation}
        \mathsf{Mod}^{\mathbb{E}_n}_{F} (\catC) \xrightarrow{\ \ \simeq \ \ } \mathsf{LMod}_{\int_{S^{n-1}} F} (\catC).
    \end{equation}
\end{proposition}

Specializing \cref{prop:exp_of_products_lc} to the case of Euclidean spaces gives the famous result of Dunn additivity \cite{dunn1988} which can be found in the following form in \cite{lurie_ha}.

\begin{proposition}
    There is an equivalence of $\infty$-categories
    %
    \begin{equation}
        \alg{\mathbb{E}_{n + m}} (\catC) \xrightarrow{\ \ \simeq \ \ } \alg{\mathbb{E}_n} (\alg{\mathbb{E}_m} (\catC)). 
    \end{equation}
\end{proposition}

\begin{remark}
    The proof of \cref{prop:exp_of_products_lc} given in \cite{ginot2015} actually depends on Dunn additivity to work, instead of the other way around, however the proof presented in \cite{lurie_ha} is independent and thus gives rise to both statements. 
\end{remark}

\end{document}

### 2023-11-24 sections/4gluing.tex
Add files via upload

\documentclass[../text]{subfiles}

\begin{document}

\section{Collar-gluings and Disk Algebras}\label{ch:gluing_disk_alg}

Given a stratified manifold $M$, we defined the $\infty$-category of locally constant factorization algebras on it $\lcfa_M (\catC)$. We want to examine what we can say about the behavior of this $\infty$-category under collar-gluings in the manifold variable. Our discussion will be in terms of disk algebras $\alg{\disk_{/M}} (\catC)$, but using \cref{thm:disk_alg=lcfa} there is no loss at all.

\begin{theorem}\label{thm:gluing_alg_disk/M}
    Given a collar-gluing of stratified manifolds $f: M \rightarrow [-1,1]$, the $\infty$-category of $\disk_{/M}$-algebras is equivalent to the pullback of $\infty$-categories
    %
    \begin{equation}
        \alg{\disk_{/M}} (\catC) \simeq \alg{\disk_{/M_-}} (\catC) \bigtimes_{\alg{\disk_{/M_0 \times \mathbb{R}}} (\catC)} \alg{\disk_{/M_+}} (\catC).
    \end{equation}
\end{theorem}

\begin{proof}
    The data of a collar-gluing provides open embeddings $M_0 \times \mathbb{R} \xhookrightarrow{} M_-$ and $M_0 \times \mathbb{R} \xhookrightarrow{} M_+$, where $M_-$, $M_0$ and $M_+$ have the usual meanings as in \cref{def:collar-gluing}. This can be used to construct the cospan of restriction functors $\alg{\disk_{/M_-}} (\catC) \rightarrow \alg{\disk_{/M_0 \times \mathbb{R}}} (\catC) \leftarrow \alg{\disk_{/M_+}} (\catC)$. Using this data we can define the pullback $\infty$-category
    %
    \begin{equation}
        \mathscr{P} := \alg{\disk_{/M_-}} (\catC) \bigtimes_{\alg{\disk_{/M_0 \times \mathbb{R}}} (\catC)} \alg{\disk_{/M_+}} (\catC).
    \end{equation}
    %
    The further open embeddings of $M_-$, $M_0 \times \mathbb{R}$ and $M_+$ into $M$ again give rise to restriction functors that form a commutative square
    %
    \begin{equation}
        \begin{tikzcd}
            \alg{\disk_{/M}} (\catC) \arrow[r] \arrow[d] & \alg{\disk_{/M_+}} (\catC) \arrow[d] \\
            \alg{\disk_{/M_-}} (\catC) \arrow[r]           & \alg{\disk_{/M_0 \times \mathbb{R}}} (\catC),     
        \end{tikzcd}
    \end{equation}
    %
    which, by the universal property of the pullback, gives us a canonical functor $\rho: \alg{\disk_{/M}} (\catC) \rightarrow \mathscr{P}$. We also want to construct a functor that partially goes in the other direction. Namely, given the data of objects $(A_-, A_+) \in \alg{\disk_{/M_-}} (\catC) \times \alg{\disk_{/M_+}} (\catC)$ such that $A_-|_{M_0 \times \mathbb{R}} = A_+|_{M_0 \times \mathbb{R}} = : A_0$ we want to construct a functor $A: \disk_{/M} \xrightarrow{} \catC$. The construction relies on using factorization homology and the bar construction. Given $(U \xhookrightarrow{} M) \in \disk_{/M}$ we define
    %
    \begin{equation}\label{eq:def_of_A_in_proof}
        A(U) := \int_{U_-} A_- \bigotimes\limits_{\int_{U_0 \times \mathbb{R}} A_0} \int_{U_+} A_+,
    \end{equation}
    %
    where $U_-$, $U_0$ and $U_+$ are defined through the inherited collar-gluing $U \xhookrightarrow{} M \xrightarrow{} [-1,1]$. Well-definition of the bar construction is provided if we have the appropriate left and right module structures on $\int_{U_-} A_-$ and $\int_{U_+} A_+$ over the associative algebra $\int_{U_0 \times \mathbb{R}} A_0$. Pushforward along the restrictions $f|_{U-}: U_- \rightarrow \left[-1, 1\right)$ and $f|_{U+}: U_+ \rightarrow \left(-1, 1\right]$, together with the properties of factorization homology provides these left and right module structures. Furthermore, the associative algebra object is exactly the appropriate one since consecutive restrictions commute on the nose. The above argument is essentially the statement that there is a functor
    %
    \begin{align}
        \gamma: \mathscr{P} \xrightarrow{\ \ \int \ \ } &\alg{\mfld_{/M_-}}(\catC) \bigtimes\limits_{\alg{\mfld_{/M_0 \times \mathbb{R}}} (\catC)} \alg{\mfld_{/M_+}} (\catC)\notag\\ &\xrightarrow{\ - \circ \bar{f} \ } \mathsf{Fun}(\mfld_{/M}, \alg{\mathsf{Assoc^{RL}}} (\catC)) \xrightarrow{\ \mathsf{B} \circ - \ } \mathsf{Fun}(\mfld_{/M},\catC) \xrightarrow{\ } \mathsf{Fun}(\disk_{/M}, \catC),
    \end{align}
    %
    where $\bar{f}: \mfld_{/M} \xrightarrow{} \alg{\mathsf{Assoc^{RL}}} (\mfld_{/M})$ is the functor induced by the collar-gluing, which on objects acts as $(N \xhookrightarrow{} M) \mapsto (N_-, N_0 \times \mathbb{R}, N_+)$, and $\mathsf{B}: \alg{\mathsf{Assoc^{RL}}} (\catC) \xrightarrow{} \catC$ is the bar construction functor.

    We will show that the functor $\rho$ is an equivalence by first checking that it is an equivalences on maximal $\infty$-subgroupoids and subsequently that it is an equivalence on morphism spaces. In accomplishing the first goal we can use the fact that our algebras are valued in a symmetric monoidal $\infty$-category, as opposed to the more general case of an $\infty$-operad. Leveraging the adjunction 
    %
    \begin{equation}
        \begin{tikzcd}
            \cat^{\otimes} \arrow[r, hook, yshift=-1ex] & \mathscr{O} \mathsf{p}_{\infty} \arrow[l, yshift=1ex, "\mathsf{Env}"'],
        \end{tikzcd}
    \end{equation}
    %
    together with the fact that $\mathsf{Hom}_{\mathscr{O} \mathsf{p}_{\infty}} (\mathscr{O}, \mathscr{O}') := \alg{\mathscr{O}} (\mathscr{O}')^{\simeq}$, tells us that there is an equivalence of maximal $\infty$-subgroupoids
    %
    \begin{equation}
        \alg{\disk_{/M}} (\catC)^{\simeq} \simeq \alg{\mathsf{Env}(\disk_{/M})} (\catC)^{\simeq} = \mathsf{Fun}^{\otimes} (\mathsf{Env} (\disk_{/M}), C)^{\simeq}.
    \end{equation}
    %
    This implies that to check that $\rho$ is an equivalence of maximal $\infty$-subgroupoids we need to show that:
    %
    \begin{enumerate}
        \item $A = \gamma (A_-, A_+)$ is actually even a symmetric monoidal functor, when viewed as a functor $\mathsf{Env} (\disk_{/M}) \xrightarrow{} \catC$,
        \item $\rho(A)$ reproduces $(A_-, A_+)$ up to equivalence, and
        \item $\gamma (\rho (A))$ reproduces $A$ up to equivalence.
    \end{enumerate}
    %
    We now check these in order. For the purposes of (1) denote $F_-(U) = \int_{U_-} A_-$, $F_0(U) = \int_{U_0 \times \mathbb{R}} A_0$, $F_+(U) = \int_{U_+} A_+$ and $\mathsf{B}_{\bullet} (R, A, L):\Delta^{\mathsf{op}} \rightarrow \catC$ for the simplicial object of the bar construction of a right module $R$, associative algebra $A$ and left module $L$. Given two objects $(U \xhookrightarrow{} M), (V \xhookrightarrow{} M) \in \mathsf{Env}(\disk_{/M})$ we have 
    %
    \begin{align}
        A(U \sqcup V) &= \mathsf{colim} (\mathsf{B}_{\bullet} (F_-(U \sqcup V), F_0(U \sqcup V), F_+(U \sqcup V)))\notag\\
        &\simeq \mathsf{colim} (\mathsf{B}_{\bullet} (F_-(U) \otimes F_-(V), F_0(U) \otimes F_0(V), F_+(U) \otimes F_+(V)))\notag\\
        &\simeq \mathsf{colim} (\mathsf{B}_{\bullet} (F_-(U), F_0(U), F_+(U)) \otimes \mathsf{B}_{\bullet} (F_-(V), F_0(V), F_+(V)))\notag\\
        &\simeq \mathsf{colim} (\Delta^{\mathsf{op}} \rightarrow \Delta^{\mathsf{op}} \times \Delta^{\mathsf{op}} \xrightarrow{\mathsf{B}_{\bullet} (F_-(U), F_0(U), F_+(U)) \otimes \mathsf{B}_{*} (F_-(V), F_0(V), F_+(V))} \catC)\notag\\
        &\simeq \mathsf{colim} (\Delta^{\mathsf{op}} \times \Delta^{\mathsf{op}} \xrightarrow{\mathsf{B}_{\bullet} (F_-(U), F_0(U), F_+(U)) \otimes \mathsf{B}_{*} (F_-(V), F_0(V), F_+(V))} \catC)\notag\\
        &\simeq \mathsf{colim} (\mathsf{B}_{\bullet} (F_-(U), F_0(U), F_+(U))) \otimes \mathsf{colim} (\mathsf{B}_{*} (F_-(V), F_0(V), F_+(V)))\notag\\
        &\simeq A(U) \otimes A(V),
    \end{align}
    %
    where $\Delta^{\mathsf{op}} \rightarrow \Delta^{\mathsf{op}} \times \Delta^{\mathsf{op}}$ is the diagonal functor. The first equivalence comes about because factorization homology is symmetric monoidal, the second equivalence is given because $\catC$ is a symmetric monoidal $\infty$-category (and not simply monoidal). The fourth equivalence uses the finality of the diagonal functor which comes from the fact that $\Delta^{\mathsf{op}}$ is sifted. Finally, the fifth equivalence exists because the symmetric monoidal structure commutes with (sifted) colimits. This shows that $A$ is a monoidal functor; that it is symmetric too is immediately obvious from the above calculation.

    Checking (2) amounts to evaluating disks $U$ which are contained in only one of the pieces $M_-$, $M_0 \times \mathbb{R}$ and $M_+$. For the case of $U_0 \times \mathbb{R} = \emptyset = U_+$, we have
    %
    \begin{equation}
        A(U) = \int_{U} A_- \bigotimes\limits_{\mathbb{1}} \mathbb{1} \simeq A_- (U),
    \end{equation}
    %
    and similarly if $U_- = \emptyset = U_0 \times \mathbb{R}$. Alternatively, for the case of $U_- = U_0 \times \mathbb{R} = U_+$ we instead have
    %
    \begin{equation}
        A(U) = \int_U A_0 \bigotimes\limits_{\int_{U} A_0} \int_U A_0 \simeq A_0(U).
    \end{equation}
    %
    If $U$ is such that $U_+ = \emptyset$, but $U_0 \times \mathbb{R} \neq \emptyset$ then
    %
    \begin{equation}
        A(U) = \int_U A_- \bigotimes\limits_{\int_{U_0 \times \mathbb{R}} A_-} \mathbb{1} \simeq \int_U A_- \bigotimes\limits_{\int_{U_0 \times \mathbb{R}} A_-} \int_{\emptyset} A_- \simeq \int_{U} A_- = A_-(U),
    \end{equation}
    %
    where the last equivalence is provided by the collar-gluing property of factorization homology. This observation is also what confirms (3).

    Finally, we want to show that $\rho$ is fully faithful, i.e. we need to show that it is an equivalence of morphism spaces
    %
    \begin{equation}
        \mathsf{Hom}_{\alg{\disk_{/M}} (\catC)}(A, B) \simeq \mathsf{Hom}_{\mathscr{P}}((A_-, A_+), (B_-, B_+)),
    \end{equation}
    %
    for each $A, B \in \alg{\disk_{/M}} (\catC)$. By the definition of algebras over an $\infty$-operad we have that $\alg{\disk_{/M}} (\catC)$ is a full $\infty$-subcategory of $\mathsf{Fun}(\disk_{/M}, \catC)$, which reduces the problem to showing that
    %
    \begin{equation}
        \begin{tikzcd}
            \mathsf{Hom}_{\mathsf{Fun}(\disk_{/M}, \catC)}(A, B) \arrow[r, bend left=4, "\rho"] & \mathsf{Hom}_{\mathscr{P}}((A_-, A_+), (B_-, B_+)) \arrow[l, bend left=4, "\gamma"]
        \end{tikzcd}
    \end{equation}
    %
    gives rise to an equivalence. Similar computations as in checking (2) and (3) above yield the necessary requirements.
\end{proof}

Together with \cref{thm:disk_alg=lcfa} we immediately have the following corollary:

\begin{corollary}\label{cor:gluing_lcfas}
    A collar-gluing of smooth manifolds $f: M \rightarrow [-1,1]$ induces an equivalence of $\infty$-categories
    %
    \begin{equation}
        \lcfa_M (\catC) \simeq \lcfa_{M_-} (\catC) \bigtimes_{\lcfa_{M_0 \times \mathbb{R}} (\catC)} \lcfa_{M_+}(\catC).
    \end{equation}
\end{corollary}

\begin{remark}
    The simple case when the collar-gluing is a disjoint union, and the manifolds are smooth can also be found as \cite[ex.5.4.5.4]{lurie_ha}.
\end{remark}

\begin{example}\label{ex:reproduce_lcfas_on_S1}
    Using results from \cite[prop.4.0.1]{cg2016}, namely inheritance from a covering space, \cite[sec.5.5]{ginot2015} characterizes locally constant factorization algebras on the circle $S^1$ as
    %
    \begin{equation}
        \lcfa_{S^1} (\catC) \simeq \aut (\alg{\mathbb{E}_1} (\catC)),
    \end{equation}
    %
    as $\mathbb{E}_1$-algebras together with a self-equivalence. \Cref{cor:gluing_lcfas} allows us to recover this nontrivial result. To wit, the circle can be exhibited as a collar-gluing $S^1 \cong \mathbb{R} \coprod_{S^0 \times \mathbb{R}} \mathbb{R} \cong \mathbb{R} \coprod_{\mathbb{R} \sqcup \mathbb{R}} \mathbb{R}$. For locally constant factorization algebras this means that
    %
    \begin{equation}\label{eq:lcfas_on_S1_gluing}
        \lcfa_{S^1} (\catC) \simeq \lcfa_{\mathbb{R}} (\catC) \bigtimes_{\lcfa_{\mathbb{R} \sqcup \mathbb{R}} (\catC)} \lcfa_{\mathbb{R}} (\catC) \simeq \alg{\mathbb{E}_1} (\catC) \bigtimes_{\lcfa_{\mathbb{R} \sqcup \mathbb{R}} (\catC)} \alg{\mathbb{E}_1} (\catC).
    \end{equation}
    %
    Since a disjoint union is a collar-gluing we also have that $\lcfa_{\mathbb{R} \sqcup \mathbb{R}} \simeq \lcfa_{\mathbb{R}} (\catC) \times \lcfa_{\mathbb{R}} (\catC) \simeq \alg{\mathbb{E}_1} (\catC) \times \alg{\mathbb{E}_1} (\catC)$. Let's denote the restriction functors that restrict to the first and the second component of the disjoint union $\mathbb{R} \sqcup \mathbb{R}$ by $|_1$ and $|_2$ respectively. Going back to \cref{eq:lcfas_on_S1_gluing}, the data of a locally constant factorization algebra on $S^1$ is equivalent to the data of two $\mathbb{E}_1$-algebras $A$ and $B$ such that their restrictions $A|_1 = B|_1$ and $A|_2 = B|_2$ agree. Since all of these are $\mathbb{E}_1$-algebras there are equivalences with the restrictions forming
    %
    \begin{equation}
        \begin{tikzcd}[row sep = small, column sep= small]
            & A|_1 \arrow[r, phantom, "=", description] & B|_1 & \\
            A \arrow[rd, phantom, "\simeq", sloped, description] \arrow[ru, phantom, "\simeq", sloped, description] & & & B \arrow[lu, phantom, "\simeq", sloped, description] \arrow[ld,  phantom, "\simeq", sloped, description] \\
            & A|_2 \arrow[r, phantom, "=", description] & B|_2 &                        
        \end{tikzcd}
    \end{equation}
    %
    That is we have the data of two algebras $A$ and $B$, and two equivalences from $A$ to $B$. It is standard that this data is equivalent (in one direction by composing) to the data of an $\mathbb{E}_1$-algebra with a self-equivalence.
\end{example}

\begin{example}\label{ex:lcfas_on_S^n}
    Just as for the circle, higher spheres can also be described as a collar-gluing $S^n \cong \mathbb{R}^n \coprod_{S^{n-1} \times \mathbb{R}} \mathbb{R^n}$. Thus, we can iterate the procedure from \cref{ex:reproduce_lcfas_on_S1} to get the locally constant factorization algebras on all higher spheres. For example, for the two-sphere $S^2$ we have
    %
    \begin{equation}
        \lcfa_{\mathbb{R}^2}(\catC) \bigtimes_{\lcfa_{S^1 \times \mathbb{R}}(\catC)} \lcfa_{\mathbb{R}^2}(\catC) \simeq \alg{\mathbb{E}_2}(\catC) \bigtimes_{\alg{\mathbb{E}_1}( \aut (\alg{\mathbb{E}_1} (\catC))) } \alg{\mathbb{E}_2} (\catC),
    \end{equation}
    %
    namely, a locally constant factorization algebra on $S^2$ equivalent to two $\mathbb{E}_2$-algebras, such that they restrict on the fattened equator to the same $\mathbb{E}_2$-algebra equipped with an $\mathbb{E}_1$-automorphism. It is nontrivial to describe this data in a simpler way as was possible for $S^1$. We can see, though, that for the higher spheres there are higher coherent equivalences that locally constant factorization algebras keep track of.
\end{example}

\begin{example}{\color{red} GO TO LATER CHAPTER}
    We have an immediate simplification of the result we saw in \cref{thm:ginot_classif_Rn*}, because its right-hand side is of the exact form to be a collar-gluing. Namely, it's the collar-gluing which, somewhat trivially, exhibits $\mathbb{R}^n_*$ as $ \cong \mathbb{R}^n_* \coprod_{\mathbb{R}^n \setminus \{0\}} \mathbb{R}^n \setminus \{0\}$. The result then simplifies to
    %
    \begin{equation}
        \mathsf{Mod}^{\mathbb{E}_n} (\catC) \simeq \lcfa_{\mathbb{R}^n_*} (\catC). 
    \end{equation}
    %
    This would confirm that the intuition we had from the 1 dimensional examples continues to hold in higher dimensions in a form that is easily parsable; introducing point defects on the manifold directly gives modules for the algebra.
\end{example}

\end{document}

### 2023-11-24 sections/5classification.tex
Add files via upload

\documentclass[../text]{subfiles}

\begin{document}

\section{Classifying \texorpdfstring{$\lcfa$}{FAlglc}s on Defect Manifolds}\label{ch:classif_defect_mfld}

Our goal in this section is to lay out a possible roadmap for classifying locally constant factorization algebras on stratified manifolds. Specifically we will focus on the case of stratified manifolds $M_{\Sigma}$, which are described by a smooth, $n$-dimensional manifold $M$ together with a distinguished smooth, properly embedded, $d$-dimensional submanifold $\Sigma \xhookrightarrow{} M$, such that $d < n$. In other words we are considering objects $M_{\Sigma} \in \mfld(\mathsf{D}_{d \subset n})$ as discussed in \cref{def:mfld_disk_dn}. More general statements can be achieved by iterating the procedure and explicating the information of more defects, stratum by stratum, in the stratified manifold.

\begin{remark}\label{rem:disk_not_enough}
    Having already considered the classification of disk algebras with $\mathsf{D}_{d \subset n}^*$-structure in \cref{thm:classif_disk_d_under_n*_alg}, one might wonder whether the classification we are after is already done by simply using the factorization homology functor, and porting over the classification of disk algebras to the setting of locally constant factorization algebras. There are two issues with this direction of inquiry. One problem is that not all $\mathsf{D}_{d \subset n}$-manifolds are frameable since this is not even the case for smooth manifolds; framed disk algebras like in \cref{thm:classif_disk_d_under_n*_alg} can only evaluate framed stratified manifolds.

    The second problem is that having classified all $\disk(\bstr)$-algebras does not immediately give a classification of $\disk_{/M}$-algebras for a given manifold $M$. There is a functor
    %
    \begin{equation}
        \alg{\disk(\bstr)}(\catC) \xrightarrow{\quad} \alg{\disk(\bstr)_{/M}} (\catC),
    \end{equation}
    %
    which is induced by the forgetful functor $\disk_{/M} \rightarrow \disk(\bstr)$, but this functor will, in general, not be an equivalence. We can see this, for example, by using \cref{rem:disk_b=disk_bsc} which tells us that the left-hand side depends on $\bstr$, while the right-hand side doesn't. 
\end{remark}

\subsection{Euclidean Spaces with Defects}

In \cref{ssec:lcfa_on_Rn} we discussed locally constant factorization algebras on Euclidean spaces of different dimension $n$, and we saw that they presented the data of $\mathbb{E}_n$-algebras. In \cref{ssec:lcfa_on_1d_man}, on the other hand we focused on 1 dimensional manifolds, but with different possible stratification structures, and we saw that the data encoded in defects was a module structure. Here, in the spirit of this section, we work to extend both of these developments to the case of Euclidean spaces with the specific kind of defect that we have limited ourselves to, namely, $\mathbb{R}^{d \subset n}$.

Despite \cref{rem:disk_not_enough}, we know from \cref{lem:disk/M_to_disk} that sometimes the classification results for disk algebras can be used for factorization algebras. In particular, this is the case for $\mathbb{R}^{d \subset n}$, since it is final in the $\infty$-category of basics $\bstr = \mathsf{D}_{d \subset n}^*$. This gives us
%
\begin{equation}\label{eq:focus_on_disk_dn}
    \lcfa_{\mathbb{R}^{d \subset n}} (\catC) \simeq \alg{\disk (\mathsf{D}_{d \subset n}^*)} (\catC).
\end{equation}

We will see that the case of $d=0$ is of particular importance. This is the case of pointed Euclidean spaces, which are alternatively denoted $\mathbb{R}^n_*$. To get a better grasp on this case we examine the $\infty$-operad.

\begin{observation}
    For the purposes of the observation we will shorten notation to $\mathscr{D}_* := \disk (\mathsf{D}_{0 \subset n}^*)$. Since the defect is a point there can be at most one disk that contains it per morphism. Thus, the morphism spaces to consider are
    %
    \begin{align}
        &\mathsf{Hom}_{\mathscr{D}_*} ((\mathbb{R}^n)^{\sqcup i}, \mathbb{R}^n),& &\mathsf{Hom}_{\mathscr{D}_*} ((\mathbb{R}^n)^{\sqcup i}, \mathbb{R}^n_*)& &\mathrm{and}& &\mathsf{Hom}_{\mathscr{D}_*} ((\mathbb{R}^n)^{\sqcup i} \sqcup \mathbb{R}^n_*, \mathbb{R}^n_*).&
    \end{align}
    %
    The first of these is equivalent to the space $\mathsf{Emb}^*((\mathbb{R}^n)^{\sqcup i}, \mathbb{R}^n)$ of framed open embeddings, which makes it is obvious that restricting to non-defect disks would give the data of an $\mathbb{E}_n$-algebra. When $i=0$, the third space above is equivalent to a point, which makes it clear that restricting exclusively to pointed disks $\mathbb{R}^n_*$ we give rise to plain objects\footnote{We've omitted mentioning the fact that, because of morphisms like $\emptyset \xrightarrow{} U$, all of the above algebraic objects will be pointed. We have done this to avoid confusion with the use of pointed in the sense of a point defect of the space.} (or $\mathbb{E}_0$-algebra). The structure that connects the two algebras is encoded in the rest of the morphism spaces.

    By definition, the middle space is given by $\mathsf{Emb}^* ((\mathbb{R}^n)^{\sqcup i}, \mathbb{R}^n \setminus \{0\})$. For the last space when $i$ isn't necessarily 0 we can use the same observation as in the proof of \cite[prop.3.16]{francis2013}, namely that we can always translate the disks so that the defect lands at the origin. This gives an equivalence of spaces
    %
    \begin{equation}
        \mathsf{Hom}_{\mathscr{D}_*} ((\mathbb{R}^n)^{\sqcup i} \sqcup \mathbb{R}^n_*, \mathbb{R}^n_*) \simeq \mathsf{Emb}^* ((\mathbb{R}^n)^{\sqcup i}, \mathbb{R}^n \setminus \{0\})
    \end{equation}
    %
    to the framed embeddings that miss the origin. Comparing to the proof of \cref{univ_env_for_En} this suggests that
\end{observation}

\begin{theorem}
    Let $n$ be bigger than 1. There is an equivalence between the $\infty$-category of locally constant factorization algebras on $\mathbb{R}^n_*$ and the $\infty$-category of $\mathbb{E}_n$-modules
    %
    \begin{equation}
        \mathsf{Mod}^{\mathbb{E}_n} (\catC) \xrightarrow{\ \ \simeq \ \ } \lcfa_{\mathbb{R}^n_*} (\catC).
    \end{equation} 
\end{theorem}

%\begin{theorem}
%    Let $n$ be bigger than 1. There is an equivalence between the $\infty$-category of $\mathbb{E}_n$-modules and the $\infty$-category of locally constant factorization algebras on $\mathbb{R}^n_*$
%    %
%    \begin{equation}
%        \mathsf{Mod}^{\mathbb{E}_n} (\catC) \xrightarrow{\ \ \simeq \ \ } \lcfa_{\mathbb{R}^n_*} (\catC).
%    \end{equation}
%\end{theorem}

%\begin{proof}
%    We immediately remark that \cite[lem.2.13]{francis2013} says that the universal enveloping algebra $U_A$ of an algebra $A \in \alg{\mathscr{O}} (\catC)$ is given as the value on $*$ of the left Kan extension of $A$ along the functor $\psi: \mathscr{O} \xrightarrow{} \mathscr{O}_*$ that adds a basepoint. Namely, this is the functor that adds a basepoint to objects and on morphism spaces it sends a map to its extension as a basepoint preserving map. We will argue that this functor is exactly the functor {\color{red} UNFINISHED}
%\end{proof}

The study of these was undertaken in \cite{ginot2015}. There it was shown that

\begin{theorem}[{\cite[cor.8]{ginot2015}}]\label{thm:ginot_classif_Rn*}
    Let $n$ be bigger than 1. There is an equivalence between the $\infty$-categories of $\mathbb{E}_n$-modules and the pullback
    %
    \begin{equation}
        \mathsf{Mod}^{\mathbb{E}_n} (\catC) \xrightarrow{\ \ \simeq \ \ } \lcfa_{\mathbb{R}^n_*} (\catC) \bigtimes_{\lcfa_{\mathbb{R}^n \setminus \{ 0\} } (\catC)} \lcfa_{\mathbb{R}^n} (\catC).
    \end{equation}
\end{theorem}

\begin{remark}
    In the above $\mathsf{Mod}^{\mathbb{E}_n}$ is the $\infty$-category of $\mathbb{E}_n$-modules, which is fibered over $\alg{\mathbb{E}_n}$ the $\infty$-category of $\mathbb{E}_n$-algebras. Informally speaking, the objects of $\mathsf{Mod}^{\mathbb{E}_n}$ are pairs $(A, M)$ consisting of an $\mathbb{E}_n$-algebra $A$ and an $A$-module $M$. However, to make things precise we, as always, use the definitions in \cite[ch.3]{lurie_ha}.
\end{remark}

\begin{remark}
    The version of \cref{thm:ginot_classif_Rn*} cited above is different from the one appearing in the original reference. \cite[cor.8]{ginot2015}, as stated, requires the homotopy pullback, however examining its proof and the later \cite[cor.9]{ginot2015} implies that the correct statement that has been proven is as written above.
\end{remark}

\begin{remark}
    The case of $n=1$ is special because the higher stratum $\mathbb{R} \setminus \{0\}$ is now disconnected. Looking back at the construction leading up to \cref{prop:hoint_gives_modules} and at \cref{rem:left_or_right_module} we can guess that a statement like the following can hold true:
\end{remark}

\begin{proposition}
    There is an equivalence between the $\infty$-category of locally constant factorization algebras on $\mathbb{R}_*$ and the $\infty$-category consisting of two $\mathbb{E}_1$-algebras $A$ and $B$ together with a pointed, left $A \otimes B^\mathsf{op}$-module $M$
    %
    \begin{equation}
        \lcfa_{\mathbb{R}_*} \simeq \mathsf{LMod} (\catC) \bigtimes_{\catC^{\mathbb{1}/}} \mathsf{RMod} (\catC),
    \end{equation}
    %
    where the functors $\mathsf{LMod}(\catC) \rightarrow \catC^{\mathbb{1}/}$ and $\mathsf{RMod}(\catC) \rightarrow \catC^{\mathbb{1}/}$ are the ones giving the underlying (pointed) object of a module.
\end{proposition}

\subsection{The General Case of \texorpdfstring{$M_{\Sigma}$}{M Sigma}}

Locally, near the defect, the locally constant factorization algebra is, of course, going to look like a locally constant factorization algebra over $\mathbb{R}^{d \subset n}$. However, it is possible that the global topology introduces some twisting of this local understanding. Due to \cref{cor:gluing_lcfas}, in any particular case, it's possible that we can find some list of collar-gluings that reduce the problem down to the local case, but this doesn't tell us anything about the general structure. Despite this, there is a particular collar-gluing that is the obvious first step if we're looking at a general manifold $M_\Sigma$. We will now describe this.

The data of an embedding $\Sigma \xhookrightarrow{} M_\Sigma$ allows us to construct a regular neighborhood of our defect, echoing the tubular neighborhood theorem, now in the case of stratified spaces.
%
\begin{theorem}[{\cite[prop.8.2.3, prop.8.2.5]{aft_localstrut}}]
    Let $\Sigma \xhookrightarrow{} M_\Sigma$ be a proper, constructible embedding of stratified manifolds. There exists a stratified map
    %
    \begin{equation}
        \mathsf{C}(\pi) \rightarrow M_\Sigma
    \end{equation}
    %
    under $\Sigma \xhookrightarrow{} M_\Sigma$ such that:
    %
    \begin{enumerate}
        %\item the map is a refinement onto its image,
        \item the image is open, and
        \item $\mathsf{C}(\pi)$ is the fiberwise open cone of the constructible bundle $\mathsf{L}_{\Sigma} \xrightarrow{\pi} \Sigma$ giving the link.
    \end{enumerate}
    %
    If $\Sigma$ is a stratum of $M_\Sigma$ then the map $\mathsf{C}(\pi) \rightarrow M_\Sigma$ is even an open embedding.
\end{theorem}

\begin{remark}
    In more detail, specialized to our situation, the regular neighborhood $\mathsf{C}(\pi)$ is constructed as the pushout of stratified manifolds
    %
    \begin{equation}
        \begin{tikzcd}
            \mathsf{L}_{\Sigma} \times \{0\} \arrow[r, "\pi"] \arrow[d, "\mathrm{id} \times 0"', hook] & \Sigma \arrow[d] \\
            \mathsf{L}_{\Sigma} \times \hoint \arrow[r] & \mathsf{C}(\pi) \arrow[ul, phantom, "\lrcorner", very near start],
        \end{tikzcd}
    \end{equation}
    %
    where $\mathsf{L}_{\Sigma}$ is the link of $\Sigma$ in $M_{\Sigma}$ (see \cite{aft_localstrut}). In our case of interest where the stratified manifold is $M_{\Sigma}$, the link $\mathsf{L}_{\Sigma}$ takes a simple form; it can always be constructed as the sphere bundle of the normal bundle of $\Sigma$ when embedded into $M$ as smooth manifolds.
\end{remark}

\begin{example}
    For the case of $(\Sigma \xhookrightarrow{} M) = {S^1 \xhookrightarrow{} \mathbb{R}^3}$, i.e. a circle defect in Euclidean 3-space, the link $\mathsf{L}_{\Sigma}$ would be a torus.
\end{example}

\begin{construction}
    The existence of $\mathsf{C}(\pi)$ allows us to define a collar-gluing for the stratified manifold $M_\Sigma$
    %
    \begin{equation}\label{eq:M_Sigma_decomposition}
        M_\Sigma \cong \left( M \setminus \Sigma \right) \coprod_{\mathsf{L}_\Sigma \times \mathbb{R}} \mathsf{C}(\pi),
    \end{equation}
    %
    where the map $\mathsf{L}_\Sigma \times \mathbb{R} \rightarrow M \setminus \Sigma$ is provided by $\mathsf{L}_\Sigma \times \mathbb{R} \cong \mathsf{L}_\Sigma \times \mathbb{R}_{\gneq 0} \cong \mathsf{C}(\pi) \setminus \Sigma \xhookrightarrow{} M \setminus \Sigma$. We also note that the properness of the embedding $\Sigma \xhookrightarrow{} M$ makes $M \setminus \Sigma$ an open submanifold of $M$.
\end{construction}

\Cref{cor:gluing_lcfas} allows us to use the collar-gluing from above to write the equivalence of $\infty$-categories
%
\begin{equation}
    \lcfa_{M_\Sigma} (\catC) \simeq \lcfa_{M \setminus \Sigma} (\catC) \bigtimes_{\lcfa_{\mathsf{L}_\Sigma \times \mathbb{R}} (\catC)} \lcfa_{\mathsf{C}(\pi)} (\catC),
\end{equation}
%
as a first step in the classification of locally constant factorization algebras on $M_{\Sigma}$. Since we have focused on stratified manifolds with the particular form $M_{\Sigma}$, the locally constant factorization algebras $\lcfa_{M \setminus \Sigma}$ in this decomposition already live on a smooth manifold, rather than on a stratified one. Similarly, this is the case for the locally constant factorization algebras $\lcfa_{\mathsf{L}_\Sigma \times \mathbb{R}}$. The more prescient question is about the classification of locally constant factorization algebras on the one remaining stratified space $\mathsf{C}(\pi)$.

%--------------

%One hint comes from the following construction:

%\begin{construction}\label{con:norm_map}
%    Using the maps
%    %
%    \begin{align}
%        &\mathsf{L}_{\Sigma} \times \hoint \xrightarrow{\pi \times \mathrm{id}} \Sigma \times \hoint &\Sigma \xrightarrow{\mathrm{id} \times 0} \Sigma \times \hoint,
%    \end{align}
%    %
%    the universal property of the pushout for $\mathsf{C}(\pi)$ defines for us a map
%    %
%    \begin{equation}
%        \mathsf{C}(\pi) \xrightarrow{\ \ n \ \ } \Sigma \times \hoint,
%    \end{equation}
%    %
%    which we call the \emph{fiberwise norm map}. We similarly, define for ease of notation $n^\circ := \pi \times \mathrm{id}: \mathsf{L}_{\Sigma} \times \mathbb{R} \rightarrow \Sigma \times \mathbb{R}$, as the restriction of $n$ to the interior.
%\end{construction}

%\begin{remark}
%    The reason for the name is most visible in the case of point defects, e.g. $M_{\Sigma} = \mathbb{R}^n_{*}$. In this case $\mathsf{C}(\pi) \cong \mathbb{R}^n_{*}$, $\Sigma \times \hoint \cong \hoint$, and the fiberwise norm map $n: \mathbb{R}^n_{*} \rightarrow \hoint$ from above is exactly the norm in the usual sense. When the defect is higher dimensional, the above construction takes the norm in each fiber hence the name fiberwise norm.
%\end{remark}

%\begin{lemma}\label{lem:n_is_bundle}
%    The fiberwise norm map $n: \mathsf{C}(\pi) \rightarrow \Sigma \times \hoint$ is a constructible bundle.
%\end{lemma}

%\begin{proof}
%    The pushout construction of $\mathsf{C}(\pi)$ and \cref{con:norm_map} make it obvious that the necessary restrictions of $\mathsf{C}(\pi)$ over the strata give bundles over $\Sigma$ and $\Sigma \times \mathbb{R}$, fulfilling the conditions.
%\end{proof}

%Using the result mentioned in %\cref{rem:hoint_times_X_conjecture} ..., about locally constant factorization algebras on $\hoint \times \Sigma$ results in:

%\begin{lemma}
%    The pushforward along the fiberwise norm map fits into a commutative diagram
%    %
%    \begin{equation}
%        \begin{tikzcd}[row sep = large, column sep = large]
%            \lcfa_{\mathsf{C}(\pi)} (\catC) \arrow[r, "n_*"] \arrow[d] & \mathsf{LMod} (\lcfa_{\Sigma} (\catC)) \arrow[d] \\
%            \lcfa_{\mathsf{L}_{\Sigma} \times \mathbb{R}} (\catC) \arrow[r, "n^{\circ}_*"] & \alg{\mathbb{E}_1} (\lcfa_{\Sigma} (\catC)).
%        \end{tikzcd}
%    \end{equation}
%\end{lemma}

%\begin{proof}
%    \Cref{lem:n_is_bundle} guarantees that the pushforward $n_*: \lcfa_{\mathsf{C}(\pi)} \rightarrow \lcfa_{\Sigma \times \hoint}$ exists at the level of locally constant factorization algebras. The mentioned \cref{rem:hoint_times_X_conjecture} together with \cref{prop:hoint_gives_modules} then provides the equivalence of the codomain of the pushforward with $\mathsf{LMod} (\lcfa_{\Sigma} (\catC))$. The vertical functors are simply restrictions away from the defect in each case, so that the commutativity if immediate.
%\end{proof}

%\begin{remark}
%    This lemma gives us the direction that defects in general will again be related to a kind of module structure of the algebras, but it does not provide the full classification. If we are able to describe locally constant factorization algebras on the space $\mathsf{C}(\pi)$ in full detail, then we would be able to reconstruct the locally constant factorization algebras on $M_{\Sigma}$.
%\end{remark}

\end{document}

### 2023-11-24 sections/6physics.tex
Add files via upload

\documentclass[../text]{subfiles}

\begin{document}

\section{Applications to Physical Examples}\label{ch:physics}

As we mentioned previously, a lot of the work on factorization algebras can be given a physics interpretation. This is especially visible in \cite{cg2016}, where the motivating examples come from quantum mechanics and quantum field theory, and specifically from the deformation quantization approach. We will introduce some of these examples here, following the exposition in \cite{cg2016}.

\begin{example}[A Barebones Model of Quantum Mechanical Observables]\label{ex:barebones_qm}
    We begin by considering quantum mechanics. Our goal will be to show that the observables of quantum mechanical systems naturally organize to form a prefactorization algebra.

    To avoid issues around measurement in quantum mechanics, we will say that the observables $\mathsf{Obs}(U)$ of a quantum system that occur in a given time period $U \subset \mathbb{R}$ are all the possible ways in which an arbitrary test system can be changed by being coupled to our system. Since we are not being precise the exact definition of what observables are will not matter a lot for now; it is rather their structure and operations that we care about. There are two natural requirements we make on the observable. For one, we require them to be defined for every time interval $U \subset \mathbb{R}$. Secondly, due to the superposition principle, for example, the minimal requirement of linearity is that $\mathsf{Obs}(U)$ is a complex vector space for each $U$.

    We notice that with this setup, if $V \subset \mathbb{R}$ is a smaller time interval contained in $U \subset \mathbb{R}$ then there is a natural restriction map
    %
    \begin{equation}
        \mathsf{Obs} (U) \rightarrow \mathsf{Obs} (V).
    \end{equation}
    %
    In effect, we have defined a copresheaf $\mathsf{Obs}: \opens[r](\mathbb{R}) \rightarrow \mathsf{Vect}_{\mathbb{C}}$ of complex vector spaces on $\mathbb{R}$.

    In the quantum setting, a key observation is that we cannot observe a system in two different ways at once, since observing changes the state of the system itself. However, we can do observations as long as they occur at different times. This is encapsulated as giving maps
    %
    \begin{equation}
        \mathsf{Obs} (U_1) \otimes \mathsf{Obs} (U_2) \xrightarrow{\quad} \mathsf{Obs} (U),
    \end{equation}
    %
    whenever $U_1$ and $U_2$ are disjoint and their union is contained in $U$. We also notice that for such a formulation we have immediately upgraded out target category $\mathsf{Vect}_{\mathbb{C}}$ to a symmetric monoidal category $\mathsf{Vect}_{\mathbb{C}}^{\otimes}$ equipped with the tensor product. Furthermore, we can do any finite number $n$ of measurements which would give us maps
    %
    \begin{equation}
        \bigotimes_{i=1}^{n} \mathsf{Obs} (U_i) \xrightarrow{\quad} \mathsf{Obs} (U),
    \end{equation}
    %
    under the same disjointness and containment criteria, but this maps also have to be compatible in a sense which essentially reproduces associativity. This all shows that under some very natural model assumptions the observables of a quantum mechanical system are organized into a $\mathsf{Vect}_{\mathbb{C}}$-valued prefactorization algebras on $\mathbb{R}$.

    In fact, we can expect even more to be true. Any observation that we get during a time interval $U$ can be refined so that we get the same observation during a shorter interval. We can think of this as increasing the coupling. In such a case the observables would in fact get the additional structure of being a locally constant, $\mathsf{Vect}_{\mathbb{C}}$-valued prefactorization algebra on $\mathbb{R}$.

    Another fact that this teaches us is that associative algebras only appear because of the topology of $\mathbb{R}$, since we know that had the dimensionality been higher like for $\mathbb{R}^n$ we would have gotten $\mathbb{E}_n$-algebras, and even more complicated algebras for other underlying manifolds.
\end{example}

\begin{example}[First Steps Towards Field Theories]
    The machinery of \cref{ex:barebones_qm} is not very advanced, and we can easily see that even if we switch to quantum field theory the previous considerations hold true. However, the way the details are fleshed out will definitely be different. The simplest example of this is the choice of target ($\infty$-)category. The target category that we chose in \cref{ex:barebones_qm} was the (ordinary) category of complex vector spaces. However, we immediately run into problems if we want to extend this to higher dimensions.

    One problem that arises is that $\mathsf{Vect}_{\mathbb{C}}$ is an ordinary category. This means that when viewed as an $\infty$-category its higher homotopies are all given in a trivial manner\footnote{The homotopies are exactly as specified by the nerve functor that turns an ordinary category into an $\infty$-category.}. Mathematically, this gives rise to the fact that the $\infty$-cateogries
    %
    \begin{equation}
        \alg{\mathbb{E}_n} (\mathsf{Vect}_{\mathbb{C}})
    \end{equation}
    %
    for $n \geq 2$ are all equivalent and all give rise to the concept of unital, commutative (and associative) complex algebras. $\mathsf{Vect}_{\mathbb{C}}$ simply does not have enough higher structure to differentiate between them.

    In a similar vein, a physical observation that arises from gauge theories is that the vector spaces we work in are not plain but actually have the structure of cochain complexes. Namely, they are such that in a cochain complex of observables $V$, the `physical' observables are given by the zeroth cohomology $\mathsf{H}^0(V)$. This is because if $v \in V^0$ is an observable of degree 0, the equation $\mathrm{d} v = 0$ means that $v$ is compatible with the gauge symmetries of the theory, thus it has to be in the kernel of the differential. If we have two observables $v, v' \in V^0$, which are both in the kernel of the differential then they could be physically equivalent they always return the same result, which we interpret as $v' = v + \mathrm{d}u$ for some $u \in V^{-1}$, since the exact element $\mathrm{d} u$ can never physically be observed.

    Both of these observations point us to the $\infty$-category of chain (or cochain, depending on conventions) complexes $\mathscr{C}\mathsf{h}_{\mathbb{C}}$. Furthermore, the symmetric monoidal structure is the tensor product $\otimes$ since this is how independent quantum systems are combined.

    $\mathscr{C}\mathsf{h}_{\mathbb{C}}$ (in the cochain convention) has as objects cochain complexes and the morphism spaces can be given the following rough, combinatorial description that can be found in \cite{tanaka20}:
    %
    \begin{enumerate}
        \item The vertices of $\mathsf{Hom}(V, W)$ are maps of chain complexes $f: V \rightarrow W$, i.e. such that $\mathrm{d} f = f \mathrm{d}$.
        \item The edges of $\mathsf{Hom}(V, W)$ are given by triples $(f_0, f_1, H)$, where $f_0$ and $f_1$ are chain maps and $H$ is a chain homotopy, i.e. a degree -1 map $H: V \rightarrow W$ such that $f_1 - f_0 = \mathrm{d} H + H \mathrm{d}$.
        \item Simplices of $\mathsf{Hom}(V, W)$ of dimension $k$ are given by maps of degree $-k$, which exhibit higher homotopies. For example for $k=2$ we have the data
        %
        \begin{equation}
            \begin{tikzcd}[row sep = large, column sep = large]
                & f_1 \arrow[rd, "H_{12}"] \arrow[d, phantom, "G"] & \\
                f_0 \arrow[ru, "H_{01}"] \arrow[rr, "H_{02}"'] & {} & f_2,
            \end{tikzcd}
        \end{equation}
        %
        where $G$ is a degree -2 map that exhibits a homotopy between $H_{02}$ and $H_{12} + H_{01}$.
    \end{enumerate}
\end{example}

\begin{example}[Correlation Functions][\cite[sec.1.4.4]{cg2016}]
    There are some cases where we can very naturally extract correlation functions from the data of a factorization algebra. Working perturbatively, suppose we have a factorization algebra on a manifold $M$ valued in cochain complexes over the ring $\mathbb{R}[\hbar]$
    %
    \begin{equation}
        F \in \falg_M (\mathscr{C}\mathsf{h}_{\mathbb{R}[\hbar]}),
    \end{equation}
    %
    and suppose that
    %
    \begin{equation}\label{eq:H0_is_the_ring}
        \mathsf{H}^0 (F(M)) = \mathbb{R}[\hbar].
    \end{equation}
    %
    As noted in \cite[sec.1.4.4]{cg2016} this condition holds in some natural examples, like Chern--Simons theory on $\mathbb{R}^3$ or for massive scalar field theories on compact manifolds. In such a case, given disjoint open subsets $\{U_i \subset M\}_{i=1, \dots, n}$ the factorization algebra maps gives rise to a multilinear map
    %
    \begin{equation}
        \langle - \rangle: \bigtimes_{i=1}^{n} H^0(F(U_i)) \xrightarrow{\quad} \mathsf{H}^0 (F(M)) = \mathbb{R}[\hbar],
    \end{equation}
    %
    so that given physical observables $O_i \in \mathsf{H}^0(F(U_i))$, we get a formal power series $\langle O_1 \dots O_n \rangle \in \mathbb{R}[\hbar]$.

    If the condition in \cref{eq:H0_is_the_ring} is not satisfied, then there is a variant that works well for $\mathbb{R}^n$. In these cases we can define an $\mathbb{R}[\hbar]$-linear map
    %
    \begin{equation}
        \mathsf{H}^0(F(\mathbb{R}^n)) \rightarrow \mathbb{R}[\hbar]
    \end{equation}
    %
    called the vacuum, that is translation invariant and satisfies a type of cluster decomposition. We then proceed as above. The details of this can be found in \cite{cg2016}.
\end{example}

There are many more things that can be said about the connection of factorization algebras to physics, however the prerequisite material would be too great to state them properly. The two volumes of the book \cite{cg2016} go over the prerequisites and provide exactly this connection in various different ways.

\end{document}

### 2023-11-24 sections/appendices.tex
Add files via upload

\documentclass[../text]{subfiles}

\begin{document}

\section{\texorpdfstring{$\mathbb{E}_n$}{En}-algebras}\label{app:En_algebras}

The operad governing $\mathbb{E}_n$-algebras was first defined in \cite{bv73} as a topological operad, and has since become ubiquitous in algebraic topology. As we saw in \cref{prop:framed_ndisk=En} one incarnation of this operad is as framed embeddings of disks into other disks. Here we follow the exposition of \cite[sec.5.1]{lurie_ha} to define the operad differently, and see how it can be given the structure of an $\infty$-operad.

\begin{definition}\label{def:rect_embedding}
    Let $n$ be an integer, and $S$ be a finite set. We will call a map $f:(-1,1)^n \times S \rightarrow (-1,1)^n$ a \emph{rectilinear embedding} if it is given by
    %
    \begin{equation}
        f(x_1, \dots, x_n, s) = (a^s_1 x_1 + b^s_1, \dots, a^s_n x_n + b^s_n),
    \end{equation}
    %
    where $a^s_i, b^s_i \in \mathbb{R}$ and $a^s_i > 0$ for all $s \in S$ and all $1 \leq i \leq n$. We denote the set of such rectilinear embeddings as $\mathsf{Rect}((-1,1)^n \times S \rightarrow (-1,1)^n)$.
\end{definition}

\begin{remark}
    The set $\mathsf{Rect}((-1,1)^n \times S \rightarrow (-1,1)^n)$ has a natural topology on it given by the subspace topology, when considered as an open subset of $\mathbb{R}^{2n |S|}$, by the map
    %
    \begin{equation}
        \mathsf{Rect}((-1,1)^n \times S \rightarrow (-1,1)^n) \xrightarrow{\quad} \mathbb{R}^{2n |S|},
    \end{equation}
    %
    which sends a rectilinear embedding to the tuple of its coefficients as in \cref{def:rect_embedding}.
\end{remark}

Classically, the $\mathbb{E}_n$ operad was defined as a topological operad according to the following:

\begin{definition}
    Let $n$ be an integer. As a topological operad, $\mathrm{E}_n$ is defined by the collection of spaces
    %
    \begin{equation}
        \left\{ \mathsf{Rect}((-1,1)^n \times \langle k \rangle^\circ \rightarrow (-1,1)^n)\right\}_{k \geq 0},
    \end{equation}
    %
    where $\langle k \rangle^\circ = \{1, 2, \dots, k\}$ and where:
    %
    \begin{enumerate}
        \item The symmetric group $\Sigma_k$ acts on $\mathsf{Rect}((-1,1)^n \times \langle k \rangle^\circ \rightarrow (-1,1)^n)$ by permutations in the finite set $\langle k \rangle^\circ$.
        \item The composition maps are given induced by the maps
        %
        \begin{equation}
            \langle k_1 \rangle^\circ \times \dots \langle k_m \rangle^\circ \xrightarrow{\quad} \langle k_1 + \dots + k_m \rangle^\circ.
        \end{equation}
        \item The unit is given by the map $\mathrm{id} : (-1,1)^n \times \langle 1 \rangle^\circ \cong (-1,1)^n \rightarrow (-1,1)^n$.
    \end{enumerate}
\end{definition}

\begin{remark}
    This is why the operad is sometimes known as the operad of little $n$-cubes.
\end{remark}

Towards an $\infty$-operadic definition, we can construct, now a little more categorically, a topological category $\mathbb{E}_n$.

\begin{definition}[{\cite[def.5.1.0.2]{lurie_ha}}]
    Let $n$ be an integer. Define a topological category $\mathbb{E}_n$ with the following:
    %
    \begin{enumerate}
        \item The objects of $\mathbb{E}_n$ are the sets $\langle k \rangle = \{ *, 1, 2, \dots, k\} \in \mathsf{Fin}_*$.
        \item A morphism from $\langle k \rangle$ to $\langle l \rangle$ is given by a morphism $(\alpha : \langle k \rangle \rightarrow \langle l \rangle) \in \mathsf{Fin}_*$ together with a rectilinear embedding $(-1,1)^n \times \alpha^{-1}\{j\} \xrightarrow{\quad} (-1,1)^n$ for each $j \in \langle l \rangle^\circ$, such that the topology of the morphism space is given by 
        %
        \begin{equation}
            \mathsf{Hom}_{\mathbb{E}_n}(\langle k \rangle \langle l \rangle) = \coprod_{\alpha : \langle k \rangle \rightarrow \langle l \rangle} \prod_{1 \leq j \leq k} \mathsf{Rect} ((-1,1)^n \times \alpha^{-1}\{ j\}, (-1,1)^n).
        \end{equation}
        \item Composition of morphisms is, as usual, defined by partial concatenation.
    \end{enumerate}
\end{definition}

\begin{proposition}[{\cite[prop.5.1.0.3]{lurie_ha}, \cite[cor.1.1.5.12]{lurie_htt}}]
    The obvious functor between (the nerves) $\mathbb{E}_n \rightarrow \mathsf{Fin}_*$ exhibits $\mathbb{E}_n$ as an $\infty$-operad.
\end{proposition}

More intuitively, we can think of the $\mathbb{E}_n$ $\infty$-operad as defining homotopy associative algebras with various levels of commutativity:
%
\begin{enumerate}
    \item $\mathbb{E}_1$ is the operad that describes unital, homotopy associative algebras.
    \item $\mathbb{E}_2$ is the operad that describes unital, homotopy associative algebras for which there exist homotopies that make the multiplication commutative, but the space of those homotopies is generically not contractible.
    \item The higher $n$ is the more and more higher homotopies exist that make the multiplication and all its previous coherences commutative.
    \item In the limit $n \rightarrow \infty$, we get the $\infty$-operad $\mathbb{E}_{\infty}$ that governs homotopy commutative algebras with fully coherent homotopies
\end{enumerate}

A more detailed explanation of this intuitive picture can be found in \cite{tanaka20}.

\begin{remark}
    We should also remember that having defined things operadically, means that we have the freedom to place our algebra in a wide variety of $\infty$-operads or symmetric monoidal $\infty$-categories. However, if the target is the nerve of an ordinary category then it will not be able to tell the difference between $\mathbb{E}_n$-algebras, with $n \geq 2$, they will all look fully commutative.
\end{remark}

\end{document}

### 2023-12-19 sections/1stratified.tex
Add files via upload

@@
 
-\begin{definition}\label{def:framed_d_under_n_sructure}
+\begin{definition}\label{def:framed_d_under_n_structure}
     The $\infty$-category of basics describing framed $\mathsf{D}_{d \subset n}$-manifolds is given by the pullback of $\infty$-categories

### 2023-12-19 sections/2homology.tex
Add files via upload

@@
 A morphism between two open embeddings $(U \xhookrightarrow{} M) \xrightarrow{} (V \xhookrightarrow{} M)$ is specified by an open embedding $U \xhookrightarrow{} V$ together with an isotopy between $U \xhookrightarrow{} M$ and $U \xhookrightarrow{} V \xhookrightarrow{} M$.
-A multi-morphism $((U_1 \xhookrightarrow{} M), (U_2 \xhookrightarrow{} M)) \xrightarrow{} (V \xhookrightarrow{} M)$ is given by an open embedding $U_1 \sqcup U_2 \xhookrightarrow{} V$ together with two isotopies from $U_1 \xhookrightarrow{} M$ to $U_1 \xhookrightarrow{} U_1 \sqcup U_2 \xhookrightarrow{} M$, and from $U_2 \xhookrightarrow{} M$ to $U_2 \xhookrightarrow{} U_1 \sqcup U_2 \xhookrightarrow{} M$.
+A morphism $((U_1 \xhookrightarrow{} M), (U_2 \xhookrightarrow{} M)) \xrightarrow{} (V \xhookrightarrow{} M)$ is given by an open embedding $U_1 \sqcup U_2 \xhookrightarrow{} V$ together with two isotopies from $U_1 \xhookrightarrow{} M$ to $U_1 \xhookrightarrow{} U_1 \sqcup U_2 \xhookrightarrow{} M$, and from $U_2 \xhookrightarrow{} M$ to $U_2 \xhookrightarrow{} U_1 \sqcup U_2 \xhookrightarrow{} M$.
 \end{remark}
@@
 The fact that they are $\infty$-operads is also true.
-The key difference is what the objects and multi-morphisms are, say, in $\disk[r](\bstr)_{/M}$ as compared to $\disk(\bstr)_{/M}$.
+The key difference is what the objects and morphisms are, say, in $\disk[r](\bstr)_{/M}$ as compared to $\disk(\bstr)_{/M}$.
 The objects are the same as before, i.e.
 finite sets of open embeddings into $M$.
-However, the multi-morphisms now contain less information.
+However, the morphisms now contain less information.
 A morphism $(U \xhookrightarrow{} M) \xrightarrow{} (V \xhookrightarrow{} M)$ is specified only by open embedding $U \xhookrightarrow{} V$, such that $(U \xhookrightarrow{} M) = (U \xhookrightarrow{} V \xhookrightarrow{} M)$, and no further information.
-Similarly, for the multi-morphisms too.
+This also holds for higher arity morphisms too.
 
-    That is, a multi-morphism in $\disk(\bstr)_{/M}$ is a diagram in $\disk (\bstr)$
+    That is, a morphism in $\disk(\bstr)_{/M}$ is a diagram in $\disk (\bstr)$
     %
@@
 
-We now focus on describing disk algebras over oriented intervals with and without boundary.
+We now focus on describing disk algebras over oriented intervals (or equivalently, framed intervals) with and without boundary.
 Not only is this an important example for what disk algebras look like, but it's also important in defining what it means to say that factorization homology is excisive.
@@
 
-We want to show that disk algebras with $\mathsf{D}_1^{\partial, \mathsf{or}}$-structure, as defined in \cref{con:d_1^bor_structure}, can be described algebraically.
+We want to show that disk algebras with $\mathsf{D}_1^{\partial, *}$-structure, as defined in \cref{con:d_1^bor_structure}, can be described algebraically.
 For this we set up two $\infty$-operads $\mathsf{Assoc^{RL}}$ and $\mathsf{O^{RL}}$.
@@
 \begin{proposition}\label{prop:disk1bor=assocRL}
-    There are equivalences of symmetric monoidal $\infty$-categories between $\mathsf{D}_1^{\partial, \mathsf{or}}$-structured disks and the symmetric monoidal envelope of $\mathsf{Assoc^{RL}}$
+    There are equivalences of symmetric monoidal $\infty$-categories between $\mathsf{D}_1^{\partial, *}$-structured disks and the symmetric monoidal envelope of $\mathsf{Assoc^{RL}}$
     %
     \begin{equation}
-        \disk[r] (\mathsf{D}_1^{\partial, \mathsf{or}}) \xrightarrow{\ \ \simeq \ \ } \disk (\mathsf{D}_1^{\partial, \mathsf{or}}) \xrightarrow[\simeq]{\ \ [-] \ \ } \mathsf{Env} (\mathsf{Assoc^{RL}}).
+        \disk[r] (\mathsf{D}_1^{\partial, *}) \xrightarrow{\ \ \simeq \ \ } \disk (\mathsf{D}_1^{\partial, *}) \xrightarrow[\simeq]{\ \ [-] \ \ } \mathsf{Env} (\mathsf{Assoc^{RL}}).
     \end{equation}
@@
     \begin{equation}
-        \disk[r] (\mathsf{D}_1^{\partial, \mathsf{or}})_{/[-1,1]} \xrightarrow{\ \ \simeq \ \ } \disk (\mathsf{D}_1^{\partial, \mathsf{or}})_{/[-1,1]} \xrightarrow{\ \ \simeq \ \ } \mathsf{O^{RL}} \quad
+        \disk[r] (\mathsf{D}_1^{\partial, *})_{/[-1,1]} \xrightarrow{\ \ \simeq \ \ } \disk (\mathsf{D}_1^{\partial, *})_{/[-1,1]} \xrightarrow{\ \ \simeq \ \ } \mathsf{O^{RL}} \quad
     \end{equation}
@@
 These are then clearly the objects that map to the respective distinguished subsets.
-Observing the definition of $\mathsf{O^{RL}}$ clearly offers a bijections on morphism spaces since they are by definition order preserving maps, and the embeddings are oriented.
+Observing the definition of $\mathsf{O^{RL}}$ clearly offers a bijection on morphism spaces since they are by definition order preserving maps, and the embeddings are oriented.
 It is trivial to check that these maps lie over $\mathsf{Fin}_*$ and that they send active morphisms to active morphisms completing the proof.
@@
     \begin{equation}
-        \mathsf{Env}(\mathsf{O^{RL}}) \xrightarrow{\ \ \simeq \ \ } \mathsf{Env}(\disk (\mathsf{D}_1^{\partial, \mathsf{or}})_{/[-1,1]}) \xrightarrow{\ \ \simeq \ \ } \disk (\mathsf{D}_1^{\partial, \mathsf{or}}) \xrightarrow{\ \ \simeq \ \ } \mathsf{Env} (\mathsf{Assoc^{RL}})
+        \mathsf{Env}(\mathsf{O^{RL}}) \xrightarrow{\ \ \simeq \ \ } \mathsf{Env}(\disk (\mathsf{D}_1^{\partial, *})_{/[-1,1]}) \xrightarrow{\ \ \simeq \ \ } \disk (\mathsf{D}_1^{\partial, *}) \xrightarrow{\ \ \simeq \ \ } \mathsf{Env} (\mathsf{Assoc^{RL}})
     \end{equation}
@@
 
-    For the purposes of the proof introduce the shorthand notation $\mathscr{D} := \disk(\mathsf{D}_1^{\partial, \mathsf{or}})$.
+    For the purposes of the proof introduce the shorthand notation $\mathscr{D} := \disk(\mathsf{D}_1^{\partial, *})$.
 There is a functor $\Delta^{\mathsf{op}} \xhookrightarrow{} \mathsf{O^{RL}}$ from the opposite of the simplex category, whose essential image consists of those objects for which the distinguished subsets with a maximal and minimal element are non-empty.
@@
     \begin{equation}
-        R \bigotimes\limits_{A} L = |\mathsf{B}_{\bullet}(R, A, L)| \simeq \mathsf{colim} (\mathscr{D}_{/[-1,1]} \xrightarrow{} \mathscr{D} \xrightarrow{(R, A, L)} \catC) = \int_{[-1,1]} (R, A, L).
+        \mathsf{B} (R, A, L) \equiv R \bigotimes\limits_{A} L = |\mathsf{B}_{\bullet}(R, A, L)| \simeq \mathsf{colim} (\mathscr{D}_{/[-1,1]} \xrightarrow{} \mathscr{D} \xrightarrow{(R, A, L)} \catC) = \int_{[-1,1]} (R, A, L).
     \end{equation}
     %
-    The naturality of this construction is immediate from the above presentation.
+    To show the naturality of these equivalences, in the algebra variable, consider the algebra map $(F \xrightarrow{f} G) \in \mathsf{Fun}(\disk_{/[-1,1]}, \catC)$.
+We can consider the colimit as a functor
+    %
+    \begin{equation}
+        \mathsf{colim}: \mathscr{C} \mathsf{at}_{\infty / \catC} \xrightarrow{} \catC,
+    \end{equation}
+    %
+    such that the equivalences arise from composing with the adjoints $\Delta^{\mathsf{op}} \mathrel{\substack{\textstyle\leftarrow\\[-0.1ex]\textstyle\hookrightarrow}} \disk_{/[-1,1]}$.
+The naturality condition is then arranged by the functoriality of $\mathsf{colim}$, namely, by the images of the squares
+    %
+    \begin{equation}
+        \begin{tikzcd}[row sep = small]
+            \Delta^{\mathsf{op}} \arrow[r, hook, shift right] \arrow[dd, equal] & \disk_{/[-1,1]} \arrow[rd, "F"] \arrow[l, shift right] \arrow[dd, phantom, bend left = 60, "f"] \arrow[dd, equal] & \\
+            & & \catC \\
+            \Delta^{\mathsf{op}} \arrow[r, hook, shift right] & \disk_{/[-1,1]} \arrow[ru, "G"'] \arrow[l, shift right] &  
+        \end{tikzcd}
+    \end{equation}
+    %
+    over $\catC$.
 \end{proof}
@@
 %    Let $A$ be a unital, (homotopy) associative algebra in $\catC$, $R$ be a unital right $A$-module in $\catC$ and $L$ be a unital left $A$-module in $\catC$.
-Using \cref{prop:disk1bor=assocRL} regard this data as the data of a symmetric monoidal functor $(R, A, L): \disk (\mathsf{D}_1^{\partial, \mathsf{or}}) \xrightarrow{} \catC$.
+Using \cref{prop:disk1bor=assocRL} regard this data as the data of a symmetric monoidal functor $(R, A, L): \disk (\mathsf{D}_1^{\partial, *}) \xrightarrow{} \catC$.
 Then there is a canonical equivalence in $\catC$ between factorization homology over the closed interval and the two-sided bar construction
@@
     \begin{equation}
-        f_*F: \disk (\mathsf{D}_1^{\partial, \mathsf{or}})_{/[-1,1]} \xrightarrow{f^{-1}} \mfld(\bstr)_{/M} \xrightarrow{} \mfld(\bstr) \xrightarrow{F} \catC.
+        f_*F: \disk (\mathsf{D}_1^{\partial, *})_{/[-1,1]} \xrightarrow{f^{-1}} \mfld(\bstr)_{/M} \xrightarrow{} \mfld(\bstr) \xrightarrow{F} \catC.
     \end{equation}
@@
     The first nontrivial example is then the oriented circle.
-We know that the algebras that we will be evaluating with are $\disk (\mathsf{D}_1^{\partial, \mathsf{or}})$-algebras (or even simpler the restriction to $\disk (\mathsf{D}_1^{\mathsf{or}})$ the ones without boundary).
+We know that the algebras that we will be evaluating with are $\disk (\mathsf{D}_1^{\partial, *})$-algebras (or even simpler the restriction to $\disk (\mathsf{D}_1^{*})$ the ones without boundary).
 The oriented circle can be presented as a collar-gluing
@@
 
-All of the above statements about factorization homology and disk algebras did not rely heavily on the stratified structure which we introduced them with.
+All of the above statements about factorization homology and disk algebras are quite general, and they do not say anything specific about a stratified structure, if there is one.
 Namely, had we stuck to smooth manifolds (possibly with boundary) we could have made similar statements.
 In this section we describe a result that clearly uses the stratified structure, and quantifies some additional information it can encode.
-It is a classification statement about disk algebras whose structure $\mathsf{D}_{d \subset n}^*$ is provided by \cref{def:framed_d_under_n_sructure}.
+It is a classification statement about disk algebras whose structure $\mathsf{D}_{d \subset n}^*$ is provided by \cref{def:framed_d_under_n_structure}.
+We will, in a roundabout way, recover this result in \cref{ch:classif_defect_mfld}, but here we state it in the original form.
 

### 2023-12-19 sections/3algebras.tex
Add files via upload

@@
     %
-    of those Weiss sheaves whose underlying functor $F: \bsc_{/M} \xrightarrow{} \catC$ satisfies the following condition:
-    %
-    \begin{enumerate}
-        \item Denote by $f: \bsc_{/M} \xrightarrow{} \bsc$ the forgetful functor. For all $U, V \in \bsc_{/M}$
+    of those Weiss sheaves whose underlying functor $F: \bsc_{/M} \xrightarrow{} \catC$ satisfies
     %
     \begin{equation}
-            f(U) \simeq f(V) \Rightarrow F(U) \simeq F(V).
+        f(U) \simeq f(V) \Rightarrow F(U) \simeq F(V),
     \end{equation}
-    \end{enumerate} 
+    %
+    for all $U, V \in \bsc_{/M}$, where $f: \bsc_{/M} \xrightarrow{} \bsc$ denotes the forgetful functor.
 \end{definition}
@@
 
-\subsection{Factorization Algebras on Euclidean spaces}\label{ssec:lcfa_on_Rn}
+\subsection{Factorization Algebras on Euclidean Spaces}\label{ssec:lcfa_on_Rn}
 
@@
 
-\begin{proposition}
+\begin{proposition}\label{prop:dunn_additivity}
     There is an equivalence of $\infty$-categories

### 2023-12-19 sections/4gluing.tex
Add files via upload

@@
 
-\begin{example}{\color{red} GO TO LATER CHAPTER}
-    We have an immediate simplification of the result we saw in \cref{thm:ginot_classif_Rn*}, because its right-hand side is of the exact form to be a collar-gluing.
+\begin{example}
+    In \cref{ch:classif_defect_mfld} we will see that fiber bundles are important for the classification of some stratified manifolds.
+Here we will look at line bundles over the circle as a toy example, namely, the cylinder $C$ and M\"obius band $M$.
+The cylinder, as a trivial fiber bundle, is isomorphic to the product space $S^1 \times \mathbb{R}$.
+By \cref{prop:exp_of_products_lc} together with the results of \cref{ex:reproduce_lcfas_on_S1}, locally constant factorization algebras on it are given by $\mathbb{E}_2$-algebras together with an $\mathbb{E}_1$-self-equivalence
+    %
+    \begin{align}
+        \lcfa_C (\catC) \simeq \aut_{\mathbb{E}_1} (\alg{\mathbb{E}_2} (\catC)).
+    \end{align}
+
+    Switching our attention to the M\"obius band $M$, we can use a similar logic as in \cref{ex:reproduce_lcfas_on_S1} to find a collar gluing of $M$.
+The pieces are the same as they would be for the cylinder, namely $M_- \cong M_+ \cong \mathbb{R}^2$, and $M_0 \times \mathbb{R} \cong \mathbb{R}^2 \sqcup \mathbb{R}^2$, but they are glued differently because of the twist.
+Using the notation from \cref{ex:reproduce_lcfas_on_S1} the diagram becomes
+    %
+    \begin{equation}
+        \begin{tikzcd}[row sep = small, column sep= small]
+            & A|_1 \arrow[r, phantom, "=", description] & B|_1^{\mathsf{op_f}} \arrow[r, phantom, "\simeq", description] & B^{\mathsf{op_f}} \\
+            A \arrow[ru, phantom, "\simeq", sloped, description] \arrow[rd, phantom, "\simeq", sloped, description] & & & \\
+            & A|_2 \arrow[r, phantom, "=", description] & B|_2 \arrow[r, phantom, "\simeq", description] & B,
+        \end{tikzcd}
+    \end{equation}
+    %
+    where $^{\mathsf{op_f}}$ is the opposite functor in the fiber direction. Thus, instead of an $\mathbb{E}_1$-\emph{self}-equivalence we have an equivalence with the opposite algebra.
+
+    We should remark that the fact that we can take the opposite algebra in one direction only is a consequence of Dunn additivity \cref{prop:dunn_additivity}.
+Without it, we wouldn't be able to combine the opposite algebra in one direction with the original algebra in the other direction into a well-defined algebra in two dimensions.
+\end{example}
+
+%\begin{example}{\color{red} GO TO LATER CHAPTER}
+%    We have an immediate simplification of the result we saw in \cref{thm:ginot_classif_Rn*}, because its right-hand side is of the exact form to be a collar-gluing.
 Namely, it's the collar-gluing which, somewhat trivially, exhibits $\mathbb{R}^n_*$ as $ \cong \mathbb{R}^n_* \coprod_{\mathbb{R}^n \setminus \{0\}} \mathbb{R}^n \setminus \{0\}$.
 The result then simplifies to
-    %
-    \begin{equation}
-        \mathsf{Mod}^{\mathbb{E}_n} (\catC) \simeq \lcfa_{\mathbb{R}^n_*} (\catC). 
-    \end{equation}
-    %
-    This would confirm that the intuition we had from the 1 dimensional examples continues to hold in higher dimensions in a form that is easily parsable; introducing point defects on the manifold directly gives modules for the algebra.
-\end{example}
+%    %
+%    \begin{equation}
+%        \mathsf{Mod}^{\mathbb{E}_n} (\catC) \simeq \lcfa_{\mathbb{R}^n_*} (\catC). 
+%    \end{equation}
+%    %
+%    This would confirm that the intuition we had from the 1 dimensional examples continues to hold in higher dimensions in a form that is easily parsable; introducing point defects on the manifold directly gives modules for the algebra.
+%\end{example}
 

### 2023-12-19 sections/5classification.tex
Add files via upload

@@
 
-We will see that the case of $d=0$ is of particular importance.
+In fact, technically, the only case we need to consider is when $d=0$.
 This is the case of pointed Euclidean spaces, which are alternatively denoted $\mathbb{R}^n_*$.
-To get a better grasp on this case we examine the $\infty$-operad.
+This is because of the isomorphism
+%
+\begin{equation}
+    \mathbb{R}^{d \subset n} \cong \mathbb{R}^{n-d}_* \times \mathbb{R}^d,
+\end{equation}
+%
+together with \cref{prop:exp_of_products_lc}, which describes locally constant factorization algebras on product spaces. To get a better grasp on $\mathbb{R}^n_*$ case we examine the $\infty$-operad.
 
@@
 %\end{proof}
+
+.....
 
@@
 
+By ....
+$\mathsf{C}(\pi)$ is always a bundle over $\Sigma$, fibered over basics.
+In the special case that $\Sigma$ is a stratum, $\mathsf{C}(\pi)$ is even a fiber bundle with fiber $\mathbb{R}^{n-d}_*$.
+Thus, the classification comes down to the classification of locally constant factorization algebras on stratified fiber bundles.
+
+There is a special case that we can already tackle, which is the case of framed manifolds.
+This is because, as discussed in \cref{def:framed_d_under_n_structure}, $\mathsf{D}_{d \subset n}^*$-manifolds come with a trivialization of the normal bundle of the distinguished submanifold $\Sigma$.
+This, in turn implies a trivialization for $\mathsf{C}(\pi)$ as a bundle over $\Sigma$ with typical fiber $\mathbb{R}^{n-d}_*$, i.e.
+there is an isomorphism
+%
+\begin{equation}
+    \mathsf{C}(\pi) \cong \Sigma \times \mathbb{R}^{n-d}_*.
+\end{equation}
+
+However, \cref{prop:exp_of_products_lc} already gives us a way to classify locally constant factorization algebras on product spaces, if we know them on the product components.
+Having classified locally constant factorization algebras on the pointed Euclidean space in \cref{thm:ginot_classif_Rn*}, we already have the result that
+%
+\begin{equation}
+    \lcfa_{\mathsf{C}(\pi)} (\catC) \simeq \mathsf{Mod}^{\mathbb{E}_{n-d}} (\lcfa_{\Sigma} (\catC)).
+\end{equation}
+
+Going from $\mathsf{C}(\pi)$ to $M_{\Sigma}$ we use the fact that the link is also trivialized, as already mentioned above, which tells us that
+%
+\begin{equation}
+    \lcfa_{\mathsf{L}_{\Sigma} \times \mathbb{R}} (\catC) \simeq \lcfa_{\Sigma \times (\mathbb{R} \setminus \{0\})} (\catC),
+\end{equation}
+%
+and finally, that
+% 
+\begin{equation}
+    \lcfa_{M_\Sigma} (\catC) \simeq \lcfa_{M \setminus \Sigma} (\catC) \bigtimes_{\lcfa_{\mathbb{R} \setminus \{0\}} (\lcfa_{\Sigma} (\catC))} \mathsf{Mod}^{\mathbb{E}_{n-d}} (\lcfa_{\Sigma} (\catC)).
+\end{equation}
+
+Apart from confirming our previous observations that what is encoded is an algebra away from the defect, and algebra on the defect and a module structure relating them, this now exactly specifies what that module structure should be given by.
+
 %--------------

### 2024-02-18 sections/2homology.tex
Add files via upload

@@
 
----------------
+\begin{remark}\label{rem:fin_equiv_natural}
+    A few times in this work we will encounter the fact that a final functor $F: \mathscr{A} \xrightarrow{} \mathscr{B}$ between $\infty$-categories induces an equivalence
+    %
+    \begin{equation}\label{eq:fin_equivs_obj}
+        \mathsf{colim}(G) \xrightarrow{\ \ \simeq \ \ } \mathsf{colim}(G \circ F),
+    \end{equation}
+    %
+    for each functor $G: \mathscr{B} \xrightarrow{} \mathscr{C}$, whenever both colimits exist.
+We remark here that these equivalences are actually even natural in $G$.
+To explain this, we first notice that the equivalences in \cref{eq:fin_equivs_obj} actually arise from equivalences between $\infty$-categories
+    %
+    \begin{equation}\label{eq:fin_equivs_cat}
+        \mathscr{C}_{G/} \xrightarrow{\ \ \simeq \ \ } \mathscr{C}_{G \circ F /},
+    \end{equation}
+    %
+    as discussed in \cite[prop.4.1.1.8]{lurie_htt}, where the functor is the obvious one.
+Furthermore, \cite[\href{https://kerodon.net/tag/016H}{016H}]{lurie_kerodon} tells us that the coslice construction is functorial, which for our purposes defines the functors
+    %
+    \begin{align}
+        &S: \mathsf{Fun}(\mathscr{B}, \mathscr{C}) \xrightarrow{\ \ \ } \cat& \mathrm{and}& &S': \mathsf{Fun}(\mathscr{A}, \mathscr{C}) \xrightarrow{\ \ \ } \cat,&
+    \end{align}
+    %
+    whose value on objects is given by $G \mapsto \mathscr{C}_{G/}$.
+We can now state that by naturality in $G$ we mean that the functors \cref{eq:fin_equivs_cat} assemble into an equivalence of functors
+    %
+    \begin{equation}
+        S \xrightarrow{\ \ \simeq \ \ } S' \circ F^*
+    \end{equation}
+    %
+    in $\mathsf{Fun}(\mathsf{Fun(\mathscr{B}, \mathscr{C})}, \cat)$. But this is obviously the case, given the description of the maps in \cref{eq:fin_equivs_cat}.
+\end{remark}
 
@@
 There is a functor $\Delta^{\mathsf{op}} \xhookrightarrow{} \mathsf{O^{RL}}$ from the opposite of the simplex category, whose essential image consists of those objects for which the distinguished subsets with a maximal and minimal element are non-empty.
-This functor is final\footnote{A functor $F: \catC \xrightarrow{} \mathscr{D}$ between $\infty$-categories is final if precomposition with it preserves colimits \[ \mathsf{colim}(G \circ F) \simeq \mathsf{colim}(G).\]} because adjoining a minimum and maximum gives a left adjoint to it.
+This functor is final because adjoining a minimum and maximum gives a left adjoint to it.
 We recognize the simplicial object
@@
     \end{equation}
-    %
-    To show the naturality of these equivalences, in the algebra variable, consider the algebra map $(F \xrightarrow{f} G) \in \mathsf{Fun}(\disk_{/[-1,1]}, \catC)$.
-We can consider the colimit as a functor
-    %
-    \begin{equation}
-        \mathsf{colim}: \mathscr{C} \mathsf{at}_{\infty / \catC} \xrightarrow{} \catC,
-    \end{equation}
-    %
-    such that the equivalences arise from composing with the adjoints $\Delta^{\mathsf{op}} \mathrel{\substack{\textstyle\leftarrow\\[-0.1ex]\textstyle\hookrightarrow}} \disk_{/[-1,1]}$.
-The naturality condition is then arranged by the functoriality of $\mathsf{colim}$, namely, by the images of the squares
-    %
-    \begin{equation}
-        \begin{tikzcd}[row sep = small]
-            \Delta^{\mathsf{op}} \arrow[r, hook, shift right] \arrow[dd, equal] & \disk_{/[-1,1]} \arrow[rd, "F"] \arrow[l, shift right] \arrow[dd, phantom, bend left = 60, "f"] \arrow[dd, equal] & \\
-            & & \catC \\
-            \Delta^{\mathsf{op}} \arrow[r, hook, shift right] & \disk_{/[-1,1]} \arrow[ru, "G"'] \arrow[l, shift right] &  
-        \end{tikzcd}
-    \end{equation}
-    %
-    over $\catC$.
+
+    Since the equivalences above come from an argument about finality, \cref{rem:fin_equiv_natural} tells us that they are actually even natural in the algebra variable $(R, A, L)$, so that the equivalence lifts to the level of functors.
 \end{proof}
-
-%\begin{proposition}[{\cite[prop.2.34]{aft_fhstrat}}]\label{prop:barconst=intinterval}
-%    Let $A$ be a unital, (homotopy) associative algebra in $\catC$, $R$ be a unital right $A$-module in $\catC$ and $L$ be a unital left $A$-module in $\catC$.
-Using \cref{prop:disk1bor=assocRL} regard this data as the data of a symmetric monoidal functor $(R, A, L): \disk (\mathsf{D}_1^{\partial, *}) \xrightarrow{} \catC$.
-Then there is a canonical equivalence in $\catC$ between factorization homology over the closed interval and the two-sided bar construction
-%    %
-%    \begin{equation}
-%        \int_{[-1,1]} (R, A, L) \xrightarrow{\ \ \simeq \ \ } R \bigotimes\limits_{A} L.
-%    \end{equation}
-%\end{proposition}
 
@@
         \disk(\bstr)_{/M} \xrightarrow{} \disk(\bstr) \xrightarrow{A} \catC.
+    \end{equation}
+\end{remark}
+
+\begin{remark}\label{rem:fh_pushforward_functorial}
+    As was the case with the bar construction the equivalence of \cref{thm:fh_pushforward}, comes about through an argument about a final functor, this means that, through \cref{rem:fin_equiv_natural} there is even an equivalence between functors
+    %
+    \begin{equation}
+        \int_M -, \int_N f_* - : \alg{\disk_{/M}} (\catC) \xrightarrow{\ \ \ \ } \catC.
     \end{equation}

### 2024-02-18 sections/3algebras.tex
Add files via upload

@@
 \begin{proposition}\label{prop:fh_disk_to_lcfa}
-    Given $M$ a stratified manifold factorization homology provides a functor between the $\infty$-categories of $\disk_M$-algebras and locally constant factorization algebras $\lcfa_M$
+    Given $M$ a stratified manifold factorization homology provides a functor between the $\infty$-categories of $\disk_{/M}$-algebras and locally constant factorization algebras $\lcfa_M$
     %
@@
     \begin{equation}
-        \mathsf{colim} (\mathscr{U} \xrightarrow{} \mfld[r]_{/N} \xrightarrow{K_F} C) \simeq \mathsf{colim} (\disk[r]_{N} \xrightarrow{} \mfld[r]_{/N} \xrightarrow{K_F} C),
+        \mathsf{colim} (\mathscr{U} \xrightarrow{} \mfld[r]_{/N} \xrightarrow{K_F} C) \simeq \mathsf{colim} (\disk[r]_{/N} \xrightarrow{} \mfld[r]_{/N} \xrightarrow{K_F} C),
     \end{equation}
@@
 
-\begin{lemma}
+\begin{lemma}\label{lem:ff_functor_to_refinement}
     Let $u: X \rightarrow \hat{X}$ be the morphism of \cref{ex:forget_strat} that forgets the stratification.
@@
 The equivalence proven there is for the case of smooth manifolds and relies on the local proof of \cite{lurie_ha} for $\mathbb{R}^n$.
-Using \cref{thm:disk_alg=lcfa}, the statement is equivalent to the fact that there is an equivalence of $\infty$-operads
+Using \cref{thm:disk_alg=lcfa}, the statement is implied by the fact that there is an equivalence of $\infty$-operads
     %
@@
     %
-    with the tensor product of $\infty$-opeards.
-Again for smooth manifolds this is found in \cite[ex.5.4.5.5]{lurie_ha}.
-In fact, this version is the one that easily generalizes to the stratified case.
+    with the tensor product of $\infty$-opeards. Again for smooth manifolds this is found in \cite[ex.5.4.5.5]{lurie_ha}.
 \end{remark}
@@
 
-    For the equivalence, we adapt \cite[ex.5.4.5.5]{lurie_ha}, as mentioned above.
-Namely, using that technology, the only thing we need to prove is that there is an equivalence between $\infty$-categories induced by the functor
+    One way to show the equivalence is to use factorization homology, as in \cref{thm:disk_alg=lcfa}, to write a locally constant factorization algebra as $\int_{-} A \in \lcfa_{X \times Y} (\catC)$.
+Then using the Fubini theorem \cite[cor.2.29]{aft_fhstrat}\footnote{The notation used in the citation is technically abusive because factorization homology is evaluating lower dimensional manifolds, but it is clear that this is to be understood exactly as the evaluation of the pushforward factorization algebra on the lower dimensional manifold.} for factorization homology we get essential surjectivity because there are equivalences
     %
-    \begin{align}
-        \bsc_{/M} \times \bsc_{/N} &\xrightarrow[\simeq]{\ \ \times \ \ } \bsc_{/M \times N} \notag\\
-        ((U \xhookrightarrow{} M), (V \xhookrightarrow{} N)) &\mapsto (U \times V \xhookrightarrow{} M \times N).
-    \end{align}
+    \begin{equation}
+        \int_{U \times V} A \xrightarrow{\ \ \simeq \ \ } \int_U \int_V \bar{\pi} A
+    \end{equation}
     %
-    ......
+    between objects of $\catC$.
+As argued in the proof of \cref{thm:disk_alg=lcfa}, these equivalences are natural in the open set variables, which means that they rise to equivalences at the level of locally constant factorization algebras.
+In fact, looking at the proof of \cite[thm.2.25]{aft_fhstrat}, which is what underlies the construction of the above equivalences, we see that they arise from an argument about a final functor.
+By \cref{rem:fin_equiv_natural} this means that the equivalences are actually natural in the algebra variable, so it is immediate that the equivalences of individual locally constant factorization algebras lift to a full equivalence of $\infty$-categories.
 \end{proof}
-
-\begin{remark}
-    The discussion at \cref{rem:fh_is_pushingforward} implies that one way to see the above proposition is as related to the Fubini theorem for factorization homology \cite[cor.2.29]{aft_fhstrat}.
-\end{remark}
-
-%\subsection{Inheritance from a Covering Space}
-
-%{\color{red} SHOULD THIS STAY? OR JUST CITE SPHERE RESULT FROM SOMEWHERE}
-
-%We can also induce factorization algebras on a space $X$ if we know how to describe them on a covering space of $X$.
-The proofs of the statements below require the full machinery regarding pullbacks of factorization algebras, so we will omit them.
-They can be found in \cite[ch.7.2]{cg2016}.
-For the extension to the stratified case, see \cite{ginot2015}.
-
-%\begin{definition}
-%    Let $G$ be a discrete group that acts on a topological space $X$.
-A $G$-equivariant factorization algebra on $X$ is a factorization algebra $F \in \falg_X (\catC)$ together with a family of equivalences
-%    %
-%    \begin{equation}
-%        \{ \theta_g : g^*F \xrightarrow{\ \ \simeq \ \ } F \}_{g \in G},
-%    \end{equation}
-%    %
-%    such that $\theta_e = \mathrm{id}$ and $\theta_{g h} = \theta_h \circ h^*(\theta_g): h^* g^* F \xrightarrow{\simeq} F$.
-We write $(\falg_X (\catC))^G$ for the full $\infty$-subcategory spanned by the $G$-equivariant factorization algebras.
-%\end{definition}
-
-%\begin{theorem}[{\cite[prop.4.0.1]{cg2016}}]\label{thm:quotient_fas}
-%    Let $X$ be a Hausdorff topological space, and $G$ be a discrete group that has a covering space action on $X$.
-The pullback along the open immersion $q: X \rightarrow X / G$ is an equivalence of $\infty$-categories
-%    %
-%    \begin{equation}
-%        q^* : \falg_{X / G} (\catC) \xrightarrow{\ \ \simeq \ \ } (\falg_{X} (\catC))^G,
-%    \end{equation}
-%    %
-%    between factorization algebras on the quotient space and $G$-equivariant factorization algebras on the covering space.
-If $X$ is further a stratified manifold the equivalence restricts to an equivalence of the $\infty$-categories of locally constant factorization algebras
-%    %
-%    \begin{equation}
-%        q^* : \lcfa_{X / G} (\catC) \xrightarrow{\ \ \simeq \ \ } (\lcfa_{X}(\catC))^G.
-%    \end{equation} 
-%\end{theorem}
 
@@
 
-\begin{theorem}[{\cite{lurie_ha}...}]
+\begin{theorem}[{\cite[thm.5.5.4.10]{lurie_ha}}]
     There is an equivalence of $\infty$-categories between the $\infty$-categories of locally constant factorization algebras on $\mathbb{R}^n$ and $\mathbb{E}_n$-algebras
@@
 
-Specializing \cref{prop:exp_of_products_lc} to the case of Euclidean spaces gives the famous result of Dunn additivity \cite{dunn1988} which can be found in the following form in \cite{lurie_ha}.
+We can view a Euclidean space $\mathbb{R}^{m+n}$ as a product space $\mathbb{R}^m \times \mathbb{R}^n$, in which case \cref{prop:exp_of_products_lc} specializes to give the famous result of Dunn additivity \cite{dunn1988} which can be found in the following form in \cite{lurie_ha}:
 
@@
 \begin{remark}
-    The proof of \cref{prop:exp_of_products_lc} given in \cite{ginot2015} actually depends on Dunn additivity to work, instead of the other way around, however the proof presented in \cite{lurie_ha} is independent and thus gives rise to both statements.
+    The proof of \cref{prop:exp_of_products_lc}, when specialized to ordinary manifolds, as given in \cite{ginot2015} actually depends on Dunn additivity to work, however the proof presented in \cite{lurie_ha} is independent.
 \end{remark}

### 2024-02-18 sections/4gluing.tex
Add files via upload

@@
     %
-    where the last equivalence is provided by the collar-gluing property of factorization homology. This observation is also what confirms (3).
+    where the last equivalence is provided by the collar-gluing property of factorization homology. This observation is also what confirms (3). Namely,
+    %
+    \begin{equation}
+        \int_U A \simeq \int_{U_-} A \bigotimes\limits_{\int_{U_0 \times \mathbb{R}} A} \int_{U_+} A \simeq \int_{U_-} A_- \bigotimes\limits_{\int_{U_0 \times \mathbb{R}} A_0} \int_{U_+} A_+,
+    \end{equation}
+    %
+    where the first equivalence comes from collar-gluing, while the second is a rewriting using the fact that restricting the algebra doesn't change the value of factorization homology it just changes what we can evaluate with it.
 
@@
     for each $A, B \in \alg{\disk_{/M}} (\catC)$.
-By the definition of algebras over an $\infty$-operad we have that $\alg{\disk_{/M}} (\catC)$ is a full $\infty$-subcategory of $\mathsf{Fun}(\disk_{/M}, \catC)$, which reduces the problem to showing that
+By the definition of algebras over an $\infty$-operad we have that $\alg{\disk_{/M}} (\catC)$ is a full $\infty$-subcategory of $\mathsf{Fun}(\disk_{/M}, \catC)$, and since we already expressed the construction functorially with $\rho$ and $\gamma$, all that remains to be checked is that the already defined maps
     %
@@
     %
-    gives rise to an equivalence. Similar computations as in checking (2) and (3) above yield the necessary requirements.
+    gives rise to an equivalence.
+That is, we have to do similar computations as (2) and (3) above, but now on the level of morphisms.
+Nothing new happens in the case of (2) since its logic essentially only depends on the properties of the bar construction when restricting.
+In the case of (3) we crucially used the collar-gluing property of factorization homology.
+That this property continues to hold at the morphism level is a consequence of the fact that \cref{prop:barconst=intinterval} is an equivalence not only at the level of objects, but also at the level of functors, together with the pushforward property which also holds functorially à la \cref{rem:fh_pushforward_functorial}.
 \end{proof}
@@
 \begin{corollary}\label{cor:gluing_lcfas}
-    A collar-gluing of smooth manifolds $f: M \rightarrow [-1,1]$ induces an equivalence of $\infty$-categories
+    A collar-gluing of stratified manifolds $f: M \rightarrow [-1,1]$ induces an equivalence of $\infty$-categories
     %
@@
     %
-    as $\mathbb{E}_1$-algebras together with a self-equivalence.
+    i.e.
+$\mathbb{E}_1$-algebras together with a self-equivalence.
 \Cref{cor:gluing_lcfas} allows us to recover this nontrivial result.
@@
     %
-    namely, a locally constant factorization algebra on $S^2$ equivalent to two $\mathbb{E}_2$-algebras, such that they restrict on the fattened equator to the same $\mathbb{E}_2$-algebra equipped with an $\mathbb{E}_1$-automorphism.
+    namely, a locally constant factorization algebra on $S^2$ is equivalent to two $\mathbb{E}_2$-algebras, such that they restrict on the fattened equator to the same $\mathbb{E}_2$-algebra equipped with an $\mathbb{E}_1$-automorphism.
 It is nontrivial to describe this data in a simpler way as was possible for $S^1$.
-We can see, though, that for the higher spheres there are higher coherent equivalences that locally constant factorization algebras keep track of.
+
+    From this example we can easily see that beyond the dimensionality $n$ of the space, which is locally kept track of as an $\mathbb{E}_n$-algebra, locally constant factorization algebras for the higher spheres also keep track of higher coherent (self-)equivalences.
 \end{example}

### 2024-02-18 sections/5classification.tex
Add files via upload

@@
 Despite \cref{rem:disk_not_enough}, we know from \cref{lem:disk/M_to_disk} that sometimes the classification results for disk algebras can be used for factorization algebras.
-In particular, this is the case for $\mathbb{R}^{d \subset n}$, since it is final in the $\infty$-category of basics $\bstr = \mathsf{D}_{d \subset n}^*$.
+In particular, this is the case for $\mathbb{R}^{d \subset n}$, since it is final in the $\infty$-category of basics $\bstr = \mathsf{D}_{d \subset n}^*$, as long as $d < n - 1$.
 This gives us
@@
 
-In fact, technically, the only case we need to consider is when $d=0$.
-This is the case of pointed Euclidean spaces, which are alternatively denoted $\mathbb{R}^n_*$.
-This is because of the isomorphism
+In fact, technically, the only cases we need to consider are when $d=0$ --- the case of pointed Euclidean spaces, which are alternatively denoted $\mathbb{R}^n_*$. This is because of the isomorphism
 %
@@
 %
-together with \cref{prop:exp_of_products_lc}, which describes locally constant factorization algebras on product spaces. To get a better grasp on $\mathbb{R}^n_*$ case we examine the $\infty$-operad.
+together with \cref{prop:exp_of_products_lc}, which describes locally constant factorization algebras on product spaces.
+Since $\mathbb{R}^n_*$ is a basic the collar-gluing property \cref{cor:gluing_lcfas} can't help us to analyze the situation.
+We are left with two cases: $n=1$ and $n > 1$.
+To get a better grasp on the data, we first explore the more complicated case of $n > 1$ by examining the $\infty$-operad $\disk(\mathsf{D}_{0 \subset n}^*)$, when $n > 1$.
 
@@
     The first of these is equivalent to the space $\mathsf{Emb}^*((\mathbb{R}^n)^{\sqcup i}, \mathbb{R}^n)$ of framed open embeddings, which makes it is obvious that restricting to non-defect disks would give the data of an $\mathbb{E}_n$-algebra.
-When $i=0$, the third space above is equivalent to a point, which makes it clear that restricting exclusively to pointed disks $\mathbb{R}^n_*$ we give rise to plain objects\footnote{We've omitted mentioning the fact that, because of morphisms like $\emptyset \xrightarrow{} U$, all of the above algebraic objects will be pointed.
-We have done this to avoid confusion with the use of pointed in the sense of a point defect of the space.} (or $\mathbb{E}_0$-algebra).
-The structure that connects the two algebras is encoded in the rest of the morphism spaces.
+This is related to \cref{lem:ff_functor_to_refinement}, which says that forgetting the stratification results in obtaining a full $\infty$-subcategory of locally constant factorization algebras.
+When $i=0$, the third space above is equivalent to a point, which makes it clear that restricting exclusively to pointed disks $\mathbb{R}^n_*$ would give rise to plain objects\footnote{We've omitted mentioning the fact that, because of morphisms like $\emptyset \xrightarrow{} U$, all of the above algebraic objects will be pointed.
+We have done this to avoid confusion with the use of pointed in the sense of a point defect of the space.} (or $\mathbb{E}_0$-algebras).
 
-    By definition, the middle space is given by $\mathsf{Emb}^* ((\mathbb{R}^n)^{\sqcup i}, \mathbb{R}^n \setminus \{0\})$.
-For the last space when $i$ isn't necessarily 0 we can use the same observation as in the proof of \cite[prop.3.16]{francis2013}, namely that we can always translate the disks so that the defect lands at the origin.
-This gives an equivalence of spaces
+    The structure that connects these two algebras is encoded in the rest of the morphism spaces. In fact the second and third space above are equivalent,
     %
     \begin{equation}
-        \mathsf{Hom}_{\mathscr{D}_*} ((\mathbb{R}^n)^{\sqcup i} \sqcup \mathbb{R}^n_*, \mathbb{R}^n_*) \simeq \mathsf{Emb}^* ((\mathbb{R}^n)^{\sqcup i}, \mathbb{R}^n \setminus \{0\})
+        \mathsf{Hom}_{\mathscr{D}_*} ((\mathbb{R}^n)^{\sqcup i}, \mathbb{R}^n_*) \simeq \mathsf{Hom}_{\mathscr{D}_*} ((\mathbb{R}^n)^{\sqcup i} \sqcup \mathbb{R}^n_*, \mathbb{R}^n_*) \simeq \mathsf{Emb}^* ((\mathbb{R}^n)^{\sqcup i}, \mathbb{R}^n \setminus \{0\}),
     \end{equation}
     %
-    to the framed embeddings that miss the origin. Comparing to the proof of \cref{univ_env_for_En} this suggests that
+    for all $i \in \mathbb{N}$, where $\mathsf{Emb}^* ((\mathbb{R}^n)^{\sqcup i}, \mathbb{R}^n \setminus \{0\})$ is the space of framed embeddings of $i$ $n$-dimensional disks into the punctured $\mathbb{R}^n$.
+
+    The isomorphism $\mathbb{R}^n \setminus \{ 0 \} \cong S^{n-1} \times \mathbb{R}$ together with an examination of \cite[prop.3.16]{francis2013}, which we recalled in \cref{univ_env_for_En}, and its proof leads us to suggest that the $\mathbb{E}_n$-algebra $A$ and the $\mathbb{E}_0$-algebra $B$ are further such that $B$ is a module over the universal enveloping algebra $U_A \simeq \int_{S^{n-1}} A$ as an $\mathbb{E}_1$-algebra.
+Remembering that we limited the whole discussion to the case when $n>1$, we propose:
 \end{observation}
@@
 \begin{theorem}
-    Let $n$ be bigger than 1. There is an equivalence between the $\infty$-category of locally constant factorization algebras on $\mathbb{R}^n_*$ and the $\infty$-category of $\mathbb{E}_n$-modules
+    Let $n$ be bigger than 1.
+There is an equivalence between the $\infty$-category of locally constant factorization algebras on $\mathbb{R}^n_*$ and the $\infty$-category of $\mathbb{E}_n$-modules that fits into the commutative diagram
     %
     \begin{equation}
-        \mathsf{Mod}^{\mathbb{E}_n} (\catC) \xrightarrow{\ \ \simeq \ \ } \lcfa_{\mathbb{R}^n_*} (\catC).
+        \begin{tikzcd}
+            \mathsf{Mod}^{\mathbb{E}_n} (\catC) \arrow[r, "\simeq"] \arrow[d] & \lcfa_{\mathbb{R}^n_*} (\catC) \arrow[d, "\cref{lem:ff_functor_to_refinement}"] \\
+            \alg{\mathbb{E}_n} (\catC) \arrow[r, "\simeq"] & \lcfa_{\mathbb{R}^n} (\catC).
+        \end{tikzcd}
     \end{equation}
 \end{theorem}
+
+\begin{remark}
+    In the above $\mathsf{Mod}^{\mathbb{E}_n}$ is the $\infty$-category of $\mathbb{E}_n$-modules, which is fibered over $\alg{\mathbb{E}_n}$ the $\infty$-category of $\mathbb{E}_n$-algebras.
+Informally speaking, the objects of $\mathsf{Mod}^{\mathbb{E}_n}$ are pairs $(A, M)$ consisting of an $\mathbb{E}_n$-algebra $A$ and an $A$-module $M$.
+However, to make things precise we, as always, use the definitions in \cite[ch.3]{lurie_ha}.
+\end{remark}
+
+\begin{proof}
+    Since $\mathsf{Mod}^{\mathbb{E}_n}$ is fibered over $\alg{\mathbb{E}_n}$, with fibers $\mathsf{Mod}^{\mathbb{E}_n}_A$ for $A$ an $\mathbb{E}_n$-algebra
+\end{proof}
 
@@
 
-.....
+%The study of these was undertaken in \cite{ginot2015}. There it was shown that
 
-The study of these was undertaken in \cite{ginot2015}. There it was shown that
+%\begin{theorem}[{\cite[cor.8]{ginot2015}}]\label{thm:ginot_classif_Rn*}
+%    Let $n$ be bigger than 1. There is an equivalence between the $\infty$-categories of $\mathbb{E}_n$-modules and the pullback
+%    %
+%    \begin{equation}
+%        \mathsf{Mod}^{\mathbb{E}_n} (\catC) \xrightarrow{\ \ \simeq \ \ } \lcfa_{\mathbb{R}^n_*} (\catC) \bigtimes_{\lcfa_{\mathbb{R}^n \setminus \{ 0\} } (\catC)} \lcfa_{\mathbb{R}^n} (\catC).
+%    \end{equation}
+%\end{theorem}
 
-\begin{theorem}[{\cite[cor.8]{ginot2015}}]\label{thm:ginot_classif_Rn*}
-    Let $n$ be bigger than 1. There is an equivalence between the $\infty$-categories of $\mathbb{E}_n$-modules and the pullback
-    %
-    \begin{equation}
-        \mathsf{Mod}^{\mathbb{E}_n} (\catC) \xrightarrow{\ \ \simeq \ \ } \lcfa_{\mathbb{R}^n_*} (\catC) \bigtimes_{\lcfa_{\mathbb{R}^n \setminus \{ 0\} } (\catC)} \lcfa_{\mathbb{R}^n} (\catC).
-    \end{equation}
-\end{theorem}
+%\begin{remark}
+%    The version of \cref{thm:ginot_classif_Rn*} cited above is different from the one appearing in the original reference.
+\cite[cor.8]{ginot2015}, as stated, requires the homotopy pullback, however examining its proof and the later \cite[cor.9]{ginot2015} implies that the correct statement that has been proven is as written above.
+%\end{remark}
 
 \begin{remark}
-    In the above $\mathsf{Mod}^{\mathbb{E}_n}$ is the $\infty$-category of $\mathbb{E}_n$-modules, which is fibered over $\alg{\mathbb{E}_n}$ the $\infty$-category of $\mathbb{E}_n$-algebras.
-Informally speaking, the objects of $\mathsf{Mod}^{\mathbb{E}_n}$ are pairs $(A, M)$ consisting of an $\mathbb{E}_n$-algebra $A$ and an $A$-module $M$.
-However, to make things precise we, as always, use the definitions in \cite[ch.3]{lurie_ha}.
-\end{remark}
-
-\begin{remark}
-    The version of \cref{thm:ginot_classif_Rn*} cited above is different from the one appearing in the original reference.
-\cite[cor.8]{ginot2015}, as stated, requires the homotopy pullback, however examining its proof and the later \cite[cor.9]{ginot2015} implies that the correct statement that has been proven is as written above.
-\end{remark}
-
-\begin{remark}
-    The case of $n=1$ is special because the higher stratum $\mathbb{R} \setminus \{0\}$ is now disconnected.
+    The case $n=1$ is special because the higher stratum $\mathbb{R} \setminus \{0\}$ is now disconnected.
 Looking back at the construction leading up to \cref{prop:hoint_gives_modules} and at \cref{rem:left_or_right_module} we can guess that a statement like the following can hold true:
@@
     \begin{equation}
-        \lcfa_{\mathbb{R}_*} \simeq \mathsf{LMod} (\catC) \bigtimes_{\catC^{\mathbb{1}/}} \mathsf{RMod} (\catC),
+        \lcfa_{\mathbb{R}_*} \simeq \mathsf{LMod} (\catC) \bigtimes_{\catC_{\mathbb{1}/}} \mathsf{RMod} (\catC),
     \end{equation}
     %
-    where the functors $\mathsf{LMod}(\catC) \rightarrow \catC^{\mathbb{1}/}$ and $\mathsf{RMod}(\catC) \rightarrow \catC^{\mathbb{1}/}$ are the ones giving the underlying (pointed) object of a module.
+    where the functors $\mathsf{LMod}(\catC) \rightarrow \catC_{\mathbb{1}/}$ and $\mathsf{RMod}(\catC) \rightarrow \catC_{\mathbb{1}/}$ are the ones giving the underlying (pointed) object of a module.
 \end{proposition}

### 2024-02-19 sections/0intro.tex
Add files via upload

@@
 However, all of the above works take a slightly different perspective in their presentation of the definitions, which we hope to unite in this work.
-The key result of this section is \cref{thm:disk_alg=lcfa}
+The key result of this section is \cref{thm:disk_alg=lcfa}:
 %
@@
 %
-as well as its corollary \cref{cor:disk_alg=falg} for the case of ordinary factorization algebras.
+as well as its \cref{cor:disk_alg=falg} for the case of ordinary factorization algebras.
 These show that the $\infty$-operad governing factorization algebras can be taken to be the slice $\infty$-operad $\disk_{/M}$ (or $\disk[r]_{/M}$ for the ordinary case).
@@
 Together with the results of the previous section this gluing holds for locally constant factorization algebras too, and it hugely expands the number of manifolds for which the $\infty$-category of locally constant factorization algebras can be specified.
-As a small example, it gives a way work on the spheres $S^n$.
+As a small example, it gives a way to work on all higher spheres $S^n$, of which, only the circle has been described to date.
 
 \textbf{\Cref{ch:classif_defect_mfld} Classifying $\lcfa$s on Defect Manifolds:} The fifth section focuses on the stratified structure and gives a way to express what effect this has on the locally constant factorization algebras.
-Specifically, we look the data of a smooth manifold $M$ with a distinguished, properly embedded submanifold $\sigma$ (also known as a defect) as the data of a stratified manifold $M_\Sigma$.
-We will show that, along with giving algebras associated to the different pieces, locally constant factorization algebras on these manifolds, in some sense, also encode a module structure associated with $\Sigma$.
+Specifically, we look at the data of a smooth manifold $M$ with a distinguished, properly embedded submanifold $\Sigma$ (also known as a defect) as the data of a stratified manifold $M_\Sigma$.
+We will show that, along with giving algebras associated to the different pieces, locally constant factorization algebras on these manifolds, in some (precise) sense, also encode a module structure associated with $\Sigma$.
 

### 2024-02-19 sections/4gluing.tex
Add files via upload

@@
 Our discussion will be in terms of disk algebras $\alg{\disk_{/M}} (\catC)$, but using \cref{thm:disk_alg=lcfa} there is no loss at all.
+
+\subsection{The Gluing Theorem}
 
@@
 
+\subsection{Some Examples of Gluing}
+
 \begin{example}\label{ex:reproduce_lcfas_on_S1}
@@
 
-\begin{example}
+\begin{example}\label{ex:cylinder_mobius_band}
     In \cref{ch:classif_defect_mfld} we will see that fiber bundles are important for the classification of some stratified manifolds.
@@
 
-%\begin{example}{\color{red} GO TO LATER CHAPTER}
-%    We have an immediate simplification of the result we saw in \cref{thm:ginot_classif_Rn*}, because its right-hand side is of the exact form to be a collar-gluing.
-Namely, it's the collar-gluing which, somewhat trivially, exhibits $\mathbb{R}^n_*$ as $ \cong \mathbb{R}^n_* \coprod_{\mathbb{R}^n \setminus \{0\}} \mathbb{R}^n \setminus \{0\}$.
-The result then simplifies to
-%    %
-%    \begin{equation}
-%        \mathsf{Mod}^{\mathbb{E}_n} (\catC) \simeq \lcfa_{\mathbb{R}^n_*} (\catC). 
-%    \end{equation}
-%    %
-%    This would confirm that the intuition we had from the 1 dimensional examples continues to hold in higher dimensions in a form that is easily parsable; introducing point defects on the manifold directly gives modules for the algebra.
-%\end{example}
-
 \end{document}

### 2024-02-19 sections/5classification.tex
Add files via upload

@@
 
-\section{Classifying \texorpdfstring{$\lcfa$}{FAlglc}s on Defect Manifolds}\label{ch:classif_defect_mfld}
+\section{Towards Classifying \texorpdfstring{$\lcfa$}{FAlglc} on Defect Manifolds}\label{ch:classif_defect_mfld}
 
@@
 
-\begin{observation}
+\begin{observation}\label{obs:explore_D*}
     For the purposes of the observation we will shorten notation to $\mathscr{D}_* := \disk (\mathsf{D}_{0 \subset n}^*)$.
@@
 We have done this to avoid confusion with the use of pointed in the sense of a point defect of the space.} (or $\mathbb{E}_0$-algebras).
-
-    The structure that connects these two algebras is encoded in the rest of the morphism spaces. In fact the second and third space above are equivalent,
+The structure that connects these two algebras is encoded in the rest of the morphism spaces.
+In fact the second and third space above are equivalent,
     %
@@
 
+    All of this is an elaboration of the fact that $\mathsf{D}_{0 \subset n}^*$ is equivalent to $\Delta^1 = \{0 \xrightarrow{} 1\}$ as $\infty$-categories (saying nothing about the right fibration to $\bsc$).
+Namely, the only nontrivial morphism is
+
     The isomorphism $\mathbb{R}^n \setminus \{ 0 \} \cong S^{n-1} \times \mathbb{R}$ together with an examination of \cite[prop.3.16]{francis2013}, which we recalled in \cref{univ_env_for_En}, and its proof leads us to suggest that the $\mathbb{E}_n$-algebra $A$ and the $\mathbb{E}_0$-algebra $B$ are further such that $B$ is a module over the universal enveloping algebra $U_A \simeq \int_{S^{n-1}} A$ as an $\mathbb{E}_1$-algebra.
@@
 
-\begin{theorem}
+\begin{theorem}\label{thm:classif_Rn*}
     Let $n$ be bigger than 1.
@@
         \begin{tikzcd}
-            \mathsf{Mod}^{\mathbb{E}_n} (\catC) \arrow[r, "\simeq"] \arrow[d] & \lcfa_{\mathbb{R}^n_*} (\catC) \arrow[d, "\cref{lem:ff_functor_to_refinement}"] \\
+            \mathsf{Mod}^{\mathbb{E}_n} (\catC) \arrow[r, "\simeq"] \arrow[d] & \lcfa_{\mathbb{R}^n_*} (\catC) \arrow[d, "(\ref{lem:ff_functor_to_refinement})"] \\
             \alg{\mathbb{E}_n} (\catC) \arrow[r, "\simeq"] & \lcfa_{\mathbb{R}^n} (\catC).
@@
 \begin{proof}
-    Since $\mathsf{Mod}^{\mathbb{E}_n}$ is fibered over $\alg{\mathbb{E}_n}$, with fibers $\mathsf{Mod}^{\mathbb{E}_n}_A$ for $A$ an $\mathbb{E}_n$-algebra
+    From \cref{eq:focus_on_disk_dn} we know that when $n > 1$ we have
+    %
+    \begin{equation}
+        \lcfa_{\mathbb{R}^n_*} (\catC) \simeq \alg{\mathscr{D}_*} (\catC),
+    \end{equation}
+    %
+    where we used the notation from \cref{obs:explore_D*}. Specializing \cref{thm:classif_disk_d_under_n*_alg} to the case at hand, and rewriting gives the left pullback square of the diagram
+    %
+    \begin{equation}
+        \begin{tikzcd}
+            \mathsf{Mod}^{\mathbb{E}_n}_A (\catC) \arrow[dr, phantom, "\ulcorner", very near start] \arrow[r] \arrow[d] & \alg{\mathscr{D}_*} (\catC) \arrow[d] \arrow[r, "\simeq"] & \lcfa_{\mathbb{R}^n_*} (\catC) \arrow[d, "(\ref{lem:ff_functor_to_refinement})"] \\
+            * \arrow[r, "\{A\}"] & \alg{\mathbb{E}_n} (\catC) \arrow[r, "\simeq"] & \lcfa_{\mathbb{R}^n} (\catC).
+        \end{tikzcd}
+    \end{equation}
+    %
+    The right square obviously commutes by construction.
+Since, by definition, $\mathsf{Mod}^{\mathbb{E}_n} (\catC)$ is fibered over $\alg{\mathbb{E}_n} (\catC)$, with fibers $\mathsf{Mod}^{\mathbb{E}_n}_A (\catC)$ for $A$ an $\mathbb{E}_n$-algebra, the above diagram gives exactly the desired statement.
 \end{proof}
 
-%\begin{theorem}
-%    Let $n$ be bigger than 1. There is an equivalence between the $\infty$-category of $\mathbb{E}_n$-modules and the $\infty$-category of locally constant factorization algebras on $\mathbb{R}^n_*$
-%    %
-%    \begin{equation}
-%        \mathsf{Mod}^{\mathbb{E}_n} (\catC) \xrightarrow{\ \ \simeq \ \ } \lcfa_{\mathbb{R}^n_*} (\catC).
-%    \end{equation}
-%\end{theorem}
-
-%\begin{proof}
-%    We immediately remark that \cite[lem.2.13]{francis2013} says that the universal enveloping algebra $U_A$ of an algebra $A \in \alg{\mathscr{O}} (\catC)$ is given as the value on $*$ of the left Kan extension of $A$ along the functor $\psi: \mathscr{O} \xrightarrow{} \mathscr{O}_*$ that adds a basepoint.
-Namely, this is the functor that adds a basepoint to objects and on morphism spaces it sends a map to its extension as a basepoint preserving map.
-We will argue that this functor is exactly the functor {\color{red} UNFINISHED}
-%\end{proof}
-
-%The study of these was undertaken in \cite{ginot2015}. There it was shown that
-
-%\begin{theorem}[{\cite[cor.8]{ginot2015}}]\label{thm:ginot_classif_Rn*}
-%    Let $n$ be bigger than 1. There is an equivalence between the $\infty$-categories of $\mathbb{E}_n$-modules and the pullback
-%    %
-%    \begin{equation}
-%        \mathsf{Mod}^{\mathbb{E}_n} (\catC) \xrightarrow{\ \ \simeq \ \ } \lcfa_{\mathbb{R}^n_*} (\catC) \bigtimes_{\lcfa_{\mathbb{R}^n \setminus \{ 0\} } (\catC)} \lcfa_{\mathbb{R}^n} (\catC).
-%    \end{equation}
-%\end{theorem}
-
-%\begin{remark}
-%    The version of \cref{thm:ginot_classif_Rn*} cited above is different from the one appearing in the original reference.
-\cite[cor.8]{ginot2015}, as stated, requires the homotopy pullback, however examining its proof and the later \cite[cor.9]{ginot2015} implies that the correct statement that has been proven is as written above.
-%\end{remark}
+\begin{remark}
+    The study of locally constant factorization algebras on $\mathbb{R}^n_*$ was also undertaken in \cite[sec.6.3]{ginot2015}.
+\Cref{thm:classif_Rn*}, as it appears above, is slightly different in its statement compared to the corresponding \cite[cor.8]{ginot2015}.
+We believe that this is due to the fact that using the homotopy pullback is not what the proof provided in the reference actually does.
+The remaining discrepancy is then explained by our \cref{cor:gluing_lcfas}, which glues locally constant factorization algebras.
+\end{remark}
 
@@
 However, it is possible that the global topology introduces some twisting of this local understanding.
-Due to \cref{cor:gluing_lcfas}, in any particular case, it's possible that we can find some list of collar-gluings that reduce the problem down to the local case, but this doesn't tell us anything about the general structure.
+Due to \cref{cor:gluing_lcfas} and the properties of stratified manifolds, in any particular case, it's possible to find some list of collar-gluings that reduce the problem down to the local case, but this doesn't tell us anything about the general structure.
 Despite this, there is a particular collar-gluing that is the obvious first step if we're looking at a general manifold $M_\Sigma$.
@@
 
-By ....
-$\mathsf{C}(\pi)$ is always a bundle over $\Sigma$, fibered over basics.
-In the special case that $\Sigma$ is a stratum, $\mathsf{C}(\pi)$ is even a fiber bundle with fiber $\mathbb{R}^{n-d}_*$.
+By \cite[ex.3.6.6]{aft_localstrut} $\mathsf{C}(\pi)$ is always a bundle over $\Sigma$, fibered over basics.
+For our particular setup this means that $\mathsf{C}(\pi)$ a fiber bundle over $\Sigma$ with typical fiber $\mathbb{R}^{n-d}_*$.
 Thus, the classification comes down to the classification of locally constant factorization algebras on stratified fiber bundles.
 
-There is a special case that we can already tackle, which is the case of framed manifolds.
+It is outside the scope of this work to finish the classification as outlined above.
+However, there is a special case that we can already tackle, which is the case of framed stratified manifolds.
 This is because, as discussed in \cref{def:framed_d_under_n_structure}, $\mathsf{D}_{d \subset n}^*$-manifolds come with a trivialization of the normal bundle of the distinguished submanifold $\Sigma$.
-This, in turn implies a trivialization for $\mathsf{C}(\pi)$ as a bundle over $\Sigma$ with typical fiber $\mathbb{R}^{n-d}_*$, i.e.
-there is an isomorphism
+This, in turn implies trivializations for $\mathsf{C}(\pi)$ and $\mathsf{L}_{\Sigma} \times \mathbb{R}$ as bundles over $\Sigma$ with typical fibers $\mathbb{R}^{n-d}_*$ and $S^{n-d-1} \times \mathbb{R}$, respectively.
+In other words, there are isomorphisms
 %
-\begin{equation}
-    \mathsf{C}(\pi) \cong \Sigma \times \mathbb{R}^{n-d}_*.
-\end{equation}
+\begin{align}
+    &\mathsf{C}(\pi) \cong \Sigma \times \mathbb{R}^{n-d}_*& &\mathrm{and}& &\mathsf{L}_{\Sigma} \times \mathbb{R} \cong \Sigma \times S^{n-d-1} \times \mathbb{R}.&
+\end{align}
 
 However, \cref{prop:exp_of_products_lc} already gives us a way to classify locally constant factorization algebras on product spaces, if we know them on the product components.
-Having classified locally constant factorization algebras on the pointed Euclidean space in \cref{thm:ginot_classif_Rn*}, we already have the result that
+Having classified locally constant factorization algebras on the pointed Euclidean space in \cref{thm:classif_Rn*}, we already have the result that
 %
@@
 \end{equation}
-
-Going from $\mathsf{C}(\pi)$ to $M_{\Sigma}$ we use the fact that the link is also trivialized, as already mentioned above, which tells us that
+%
+Similarly, we also know that for the link we have
+%
 %
 \begin{equation}
-    \lcfa_{\mathsf{L}_{\Sigma} \times \mathbb{R}} (\catC) \simeq \lcfa_{\Sigma \times (\mathbb{R} \setminus \{0\})} (\catC),
+    \lcfa_{\mathsf{L}_{\Sigma} \times \mathbb{R}} (\catC) \simeq \lcfa_{\mathbb{R}^{n-d} \setminus \{ 0\} } (\lcfa_{\Sigma} (\catC)),
 \end{equation}
 %
-and finally, that
+exactly in such a way that the functor $\mathsf{Mod}^{\mathbb{E}_{n-d}} (\lcfa_{\Sigma} (\catC)) \xrightarrow{} \lcfa_{\mathbb{R}^{n-d} \setminus \{ 0\} } (\lcfa_{\Sigma} (\catC))$ is the one given by $\int_{S^{n-d-1}} -$, which to an algebra assigns its universal enveloping algebra.
+
+Putting it all together, we have the equivalence
 %
 \begin{equation}
-    \lcfa_{M_\Sigma} (\catC) \simeq \lcfa_{M \setminus \Sigma} (\catC) \bigtimes_{\lcfa_{\mathbb{R} \setminus \{0\}} (\lcfa_{\Sigma} (\catC))} \mathsf{Mod}^{\mathbb{E}_{n-d}} (\lcfa_{\Sigma} (\catC)).
+    \lcfa_{M_\Sigma} (\catC) \simeq \lcfa_{M \setminus \Sigma} (\catC) \bigtimes_{\lcfa_{\mathbb{R}^{n-d} \setminus \{0\}} (\lcfa_{\Sigma} (\catC))} \mathsf{Mod}^{\mathbb{E}_{n-d}} (\lcfa_{\Sigma} (\catC)).
 \end{equation}
+%
+where the only functor that we haven't mentioned above is $\lcfa_{M \setminus \Sigma} (\catC) \xrightarrow{} \lcfa_{\mathbb{R}^{n-d} \setminus \{ 0\} } (\lcfa_{\Sigma} (\catC))$, which is given by restriction to the fattened link.
 
-Apart from confirming our previous observations that what is encoded is an algebra away from the defect, and algebra on the defect and a module structure relating them, this now exactly specifies what that module structure should be given by.
-
-%--------------
-
-%One hint comes from the following construction:
-
-%\begin{construction}\label{con:norm_map}
-%    Using the maps
-%    %
-%    \begin{align}
-%        &\mathsf{L}_{\Sigma} \times \hoint \xrightarrow{\pi \times \mathrm{id}} \Sigma \times \hoint &\Sigma \xrightarrow{\mathrm{id} \times 0} \Sigma \times \hoint,
-%    \end{align}
-%    %
-%    the universal property of the pushout for $\mathsf{C}(\pi)$ defines for us a map
-%    %
-%    \begin{equation}
-%        \mathsf{C}(\pi) \xrightarrow{\ \ n \ \ } \Sigma \times \hoint,
-%    \end{equation}
-%    %
-%    which we call the \emph{fiberwise norm map}.
-We similarly, define for ease of notation $n^\circ := \pi \times \mathrm{id}: \mathsf{L}_{\Sigma} \times \mathbb{R} \rightarrow \Sigma \times \mathbb{R}$, as the restriction of $n$ to the interior.
-%\end{construction}
-
-%\begin{remark}
-%    The reason for the name is most visible in the case of point defects, e.g.
-$M_{\Sigma} = \mathbb{R}^n_{*}$.
-In this case $\mathsf{C}(\pi) \cong \mathbb{R}^n_{*}$, $\Sigma \times \hoint \cong \hoint$, and the fiberwise norm map $n: \mathbb{R}^n_{*} \rightarrow \hoint$ from above is exactly the norm in the usual sense.
-When the defect is higher dimensional, the above construction takes the norm in each fiber hence the name fiberwise norm.
-%\end{remark}
-
-%\begin{lemma}\label{lem:n_is_bundle}
-%    The fiberwise norm map $n: \mathsf{C}(\pi) \rightarrow \Sigma \times \hoint$ is a constructible bundle.
-%\end{lemma}
-
-%\begin{proof}
-%    The pushout construction of $\mathsf{C}(\pi)$ and \cref{con:norm_map} make it obvious that the necessary restrictions of $\mathsf{C}(\pi)$ over the strata give bundles over $\Sigma$ and $\Sigma \times \mathbb{R}$, fulfilling the conditions.
-%\end{proof}
-
-%Using the result mentioned in %\cref{rem:hoint_times_X_conjecture} ..., about locally constant factorization algebras on $\hoint \times \Sigma$ results in:
-
-%\begin{lemma}
-%    The pushforward along the fiberwise norm map fits into a commutative diagram
-%    %
-%    \begin{equation}
-%        \begin{tikzcd}[row sep = large, column sep = large]
-%            \lcfa_{\mathsf{C}(\pi)} (\catC) \arrow[r, "n_*"] \arrow[d] & \mathsf{LMod} (\lcfa_{\Sigma} (\catC)) \arrow[d] \\
-%            \lcfa_{\mathsf{L}_{\Sigma} \times \mathbb{R}} (\catC) \arrow[r, "n^{\circ}_*"] & \alg{\mathbb{E}_1} (\lcfa_{\Sigma} (\catC)).
-%        \end{tikzcd}
-%    \end{equation}
-%\end{lemma}
-
-%\begin{proof}
-%    \Cref{lem:n_is_bundle} guarantees that the pushforward $n_*: \lcfa_{\mathsf{C}(\pi)} \rightarrow \lcfa_{\Sigma \times \hoint}$ exists at the level of locally constant factorization algebras.
-The mentioned \cref{rem:hoint_times_X_conjecture} together with \cref{prop:hoint_gives_modules} then provides the equivalence of the codomain of the pushforward with $\mathsf{LMod} (\lcfa_{\Sigma} (\catC))$.
-The vertical functors are simply restrictions away from the defect in each case, so that the commutativity if immediate.
-%\end{proof}
-
-%\begin{remark}
-%    This lemma gives us the direction that defects in general will again be related to a kind of module structure of the algebras, but it does not provide the full classification.
-If we are able to describe locally constant factorization algebras on the space $\mathsf{C}(\pi)$ in full detail, then we would be able to reconstruct the locally constant factorization algebras on $M_{\Sigma}$.
-%\end{remark}
+This description confirms the observation that what a locally constant factorization algebra on a defect manifold encodes is an algebra away from the defect, an algebra on the defect and a module structure relating them.
+Additionally, it exactly specifies what that module structure should be given by.
+In the case where the stratified manifold isn't framed we expect that the above structure will be `twisted' as seen in \cref{ex:cylinder_mobius_band} for the case of the M\"obius band.
 

### 2024-02-19 sections/5classification.tex
Add files via upload

@@
     for all $i \in \mathbb{N}$, where $\mathsf{Emb}^* ((\mathbb{R}^n)^{\sqcup i}, \mathbb{R}^n \setminus \{0\})$ is the space of framed embeddings of $i$ $n$-dimensional disks into the punctured $\mathbb{R}^n$.
-
-    All of this is an elaboration of the fact that $\mathsf{D}_{0 \subset n}^*$ is equivalent to $\Delta^1 = \{0 \xrightarrow{} 1\}$ as $\infty$-categories (saying nothing about the right fibration to $\bsc$).
-Namely, the only nontrivial morphism is
+All of these facts are partially an elaboration of the fact that $\mathsf{D}_{0 \subset n}^*$ is equivalent to $\Delta^1 = \{0 \xrightarrow{} 1\}$ as $\infty$-categories (saying nothing about the right fibration to $\bsc$).
 

### 2024-02-28 sections/2homology.tex
Add files via upload

@@
     %
-    which is homotopy commutative, while in $\disk[r](\bstr)_{/M}$ a morphism is a diagram as above that commutes on the nose\footnote{Regarding notation, \cite{lurie_ha} introduces both $\infty$-operads $\disk(\bstr)_{/M}$ and $\disk[r](\bstr)_{/M}$, however there they are denoted by $\mathbb{E}_M^\otimes$ and $\mathrm{N}(\mathrm{Disk}(M))^\otimes$, respectively.}.
+    which is homotopy commutative, while in $\disk[r](\bstr)_{/M}$ a morphism is a diagram as above that commutes on the nose\footnote{Regarding notation, \cite{lurie_ha} introduces both the $\infty$-operad $\disk(\bstr)_{/M}$ and $\disk[r](\bstr)_{/M}$, however there they are denoted by $\mathbb{E}_M^\otimes$ and $\mathrm{N}(\mathrm{Disk}(M))^\otimes$, respectively.}.
 \end{remark}
@@
 
-The bulk of the work is then to show that such an adjoint exists and to try to find more concrete forms of factorization homology that would be easier to compute with.
+The bulk of the task is then to show that such an adjoint exists and to try to find more concrete forms of factorization homology that would be easier to compute with.
 Being a left Kan extension one guess on the side of computation would be that we can find its values via colimits, as is usual for pointwise left Kan extensions.
@@
 Since $\mathsf{Assoc^{RL}}$ is also born of a discrete nature we only need to find a bijection of morphism spaces.
-By construction of $\mathsf{Assoc^{RL}}$ such a bijection is immediate.
+By the construction of $\mathsf{Assoc^{RL}}$ such a bijection is immediate.
 \end{proof}
@@
     as discussed in \cite[prop.4.1.1.8]{lurie_htt}, where the functor is the obvious one.
-Furthermore, \cite[\href{https://kerodon.net/tag/016H}{016H}]{lurie_kerodon} tells us that the coslice construction is functorial, which for our purposes defines the functors
+Furthermore, \cite[\href{https://kerodon.net/tag/016H}{016H}]{lurie_kerodon} tells us that the coslice construction is functorial, which, after restricting, defines the functors
     %
@@
     %
-    in $\mathsf{Fun}(\mathsf{Fun(\mathscr{B}, \mathscr{C})}, \cat)$. But this is obviously the case, given the description of the maps in \cref{eq:fin_equivs_cat}.
+    in $\mathsf{Fun}(\mathsf{Fun(\mathscr{B}, \mathscr{C})}, \cat)$.
+But this is obviously the case, given the description of the maps in \cref{eq:fin_equivs_cat}, and amounts to nothing more than bookkeeping.
 \end{remark}
@@
     The two-sided bar construction here gives the left derived tensor product.
-We, however, do not make a notational distinction between this left derived tensor product and the standard one since we should be clear from context.
+We, however, do not make a notational distinction between this left derived tensor product and the standard one since it should be clear from context.
 The left derived version will always appear due to some two-sided bar construction.
@@
 \begin{example}
-    Checking the definitions we can see that evaluating basics $U \in \disk(\bstr) \xhookrightarrow{} \mfld(\bstr)$ is the same as simply evaluating the disk with the disk algebra.
+    Checking the definitions we can see that evaluating basics $U \in \disk(\bstr) \xhookrightarrow{} \mfld(\bstr)$ with factorization homology is the same as simply evaluating the disk with the disk algebra.
 This is simply because factorization homology is a left Kan extension.
@@
 It is a classification statement about disk algebras whose structure $\mathsf{D}_{d \subset n}^*$ is provided by \cref{def:framed_d_under_n_structure}.
-We will, in a roundabout way, recover this result in \cref{ch:classif_defect_mfld}, but here we state it in the original form.
+%We will, in a roundabout way, recover this result in \cref{ch:classif_defect_mfld}, but here we state it in the original form.
 

### 2024-02-28 sections/3algebras.tex
Add files via upload

@@
     where the $(i,j)$ tensor product runs over all possible pairs $i \in I$ and $j \in J_i$.
-Finally, the operadic unitarity condition actually tells us that we don't need to provide the morphisms $F(\{U\}, U)$, because they are equivalent to the identity morphism.
+Finally, the operadic unitarity condition actually tells us that the morphisms $F(\{U\}, U)$ are equivalent to the identity morphism.
 
@@
 \begin{proposition}\label{prop:fh_disk_to_lcfa}
-    Given $M$ a stratified manifold factorization homology provides a functor between the $\infty$-categories of $\disk_{/M}$-algebras and locally constant factorization algebras $\lcfa_M$
+    Given a stratified manifold $M$ factorization homology provides a functor between the $\infty$-categories of $\disk_{/M}$-algebras and locally constant factorization algebras $\lcfa_M$
     %
@@
 
-    We first observe that by definition the $\infty$-operad $\opens(M) := \mfld[r]_{/M}$. There are clear functors of $\infty$-operads
+    We first observe that, by definition, the $\infty$-operad $\opens(M) := \mfld[r]_{/M}$. There are clear functors of $\infty$-operads
     %
@@
 \begin{remark}
-    The key idea for the proof is that $\disk[r]_{/N}$ is a basis for the Weiss Grothendieck topology on manifolds.
+    Intuitively, the key idea for the statement and proof is that $\disk[r]_{/N}$ is a basis for the Weiss Grothendieck topology on manifolds.
 This is essentially because for each finite set of points $S \subset N$, and each Weiss cover of it $U_S$, we can take small enough disks $\{ D_s \}_{s \in S}$ around each point, by virtue of $N$ being a manifold, and their disjoint union will cover $S$, as well as satisfy $\sqcup_{s \in S} D_s \subset U_S$.
+The proof of \cite[prop.2.22]{af_primer} makes this precise, and the above proof transports that idea to the relative case.
 \end{remark}
@@
 \begin{remark}
-    In fact, the above proof is true more generally for any map of stratified spaces that is a homeomorphism of the underlying topological spaces.
+    In fact, the above proof is true more generally for any map of stratified spaces that is a homeomorphism of the underlying topological spaces (so, in particular, any refinement).
 This means that locally constant factorization algebras record the data of coarser stratified structures as $\infty$-subcategories.
@@
     One way to show the equivalence is to use factorization homology, as in \cref{thm:disk_alg=lcfa}, to write a locally constant factorization algebra as $\int_{-} A \in \lcfa_{X \times Y} (\catC)$.
-Then using the Fubini theorem \cite[cor.2.29]{aft_fhstrat}\footnote{The notation used in the citation is technically abusive because factorization homology is evaluating lower dimensional manifolds, but it is clear that this is to be understood exactly as the evaluation of the pushforward factorization algebra on the lower dimensional manifold.} for factorization homology we get essential surjectivity because there are equivalences
+Then using the Fubini theorem \cite[cor.2.29]{aft_fhstrat}\footnote{The notation used in the citation is technically abusive because factorization homology is evaluating lower dimensional manifolds, but it is clear that this is to be understood exactly as the evaluation of the pushforward factorization algebra on the lower dimensional manifold (see \cref{rem:fh_is_pushingforward}).} for factorization homology we get essential surjectivity because there are equivalences
     %
@@
     \begin{equation}
-        \alg{\mathbb{E}_1}(\catC) \xrightarrow{\simeq} \lcfa_{\mathbb{R}} (\catC).
+        \alg{\mathbb{E}_1}(\catC) \xrightarrow{\ \ \simeq \ \ } \lcfa_{\mathbb{R}} (\catC).
     \end{equation}
@@
 This holds because every disk in $\mathbb{R}$ is diffeomorphic to $\mathbb{R}$ itself.
-So, given $F \in \lcfa_{\mathbb{R}}$, we can get an underlying object for our $\mathbb{E}_1$ algebra as $A = F(\mathbb{R})$.
+So, given $F \in \lcfa_{\mathbb{R}}$, we can get an underlying object for our $\mathbb{E}_1$-algebra as $A = F(\mathbb{R})$.
 The previous observation and the local constancy then force the value on each disk to be equivalent to this.
@@
     \begin{equation}
-        \mathsf{RMod}(\catC) \xrightarrow{\simeq} \lcfa_{\hoint} (\catC).
+        \mathsf{RMod}(\catC) \xrightarrow{\ \ \simeq \ \ } \lcfa_{\hoint} (\catC).
     \end{equation}
@@
     The proof goes along the same lines as the proof of \cref{prop:R_gives_E1}.
-We can find the module by evaluating on $\hoint$, and we can find the algebra by evaluating on $\hoint \setminus \{ 0 \} \cong \mathbb{R}$.
+We can find the module by evaluating on $\hoint$, and we can find the algebra by evaluating on $\hoint \setminus \{ 0 \} \cong \mathbb{R}$, as a specified stratum of $\hoint$.
 \end{proof}
@@
 By \cref{prop:exp_of_products_lc} we know that $F|_{S^{n-1} \times \mathbb{R}} \in \lcfa_{\mathbb{R}} (\lcfa_{S^{n-1}} (\catC))$, so that in particular it is an $\mathbb{E}_1$-algebra.
-If we pushforward to $\mathbb{R}$, by the discussion at \cref{rem:fh_is_pushingforward} we could denote the resulting $\mathbb{E}_1$-algebra by
+If we pushforward to $\mathbb{R}$, by the discussion at \cref{rem:fh_is_pushingforward} we could denote the resulting $\mathbb{E}_1$-algebra by \footnote{We again refer the reader to \cref{rem:fh_is_pushingforward} for a reason why this notation is good.}
     %
@@
     What \cite[prop.3.16]{francis2013} shows is then:
-\end{remark}
 
@@
     \end{proposition}
+    %
+    This result goes towards an explanation of the appearance of factorization homology over higher spheres in the classification statement of \cref{thm:classif_disk_d_under_n*_alg}.
+\end{remark}
 

### 2024-02-28 sections/4gluing.tex
Add files via upload

@@
 
+Before me move on to the proof we show a few useful lemmas.
+
+\begin{lemma}\label{lem:fbar_func}
+    A collar-gluing $f:M \xrightarrow{} [-1,1]$ of a stratified manifold $M$ induces a functor
+    %
+    \begin{equation}
+        \bar{f}: \mfld_{/M} \xrightarrow{\ \ \ \ } \alg{\mathsf{Assoc^{RL}}} (\mfld_{/M}),
+    \end{equation}
+    %
+    which on objects acts as $(N \xhookrightarrow{} M) \mapsto (N_- \xhookrightarrow{} M, N_0 \times \mathbb{R} \xhookrightarrow{} M, N_+ \xhookrightarrow{} M)$.
+Moreover, this functor is even an algebra.
+\end{lemma}
+
 \begin{proof}
+    Let us first look at the case of $\mfld[r]_{/M}$ instead of $\mfld_{/M}$.
+In this case the underlying $\infty$-category is actually (the nerve of) an ordinary category.
+In particular, morphisms are given by the data of an embedding $N \xhookrightarrow{} N'$ such that $N \xhookrightarrow{} N' \xhookrightarrow{} M = N \xhookrightarrow{} M$ on the nose.
+
+    A collar-gluing of $M$ restricts to a collar-gluing of any $N$ that has an embedding into $M$ like the objects of our category.
+On the right-hand side, at the level of objects, the associative algebra structure is provided by embeddings that differ in the $\mathbb{R}$ factor and the module maps are provided by embeddings of the middle $N_0 \times \mathbb{R}$ into $N_-$ and $N_+$.
+At the level of morphisms we send the morphism $e: N \xhookrightarrow{} N'$ to
+    %
+    \begin{equation}
+        (e_-: N_- \xhookrightarrow{} N'_-, \ e_0: N_0 \times \mathbb{R} \xhookrightarrow{} N'_0 \times \mathbb{R}, \ e_+: N_+ \xhookrightarrow{} N'_+).
+    \end{equation}
+    %
+    The existence of these maps can be stated as the existence of a unique factorization, as in e.g.
+    %
+    \begin{equation}
+        \begin{tikzcd}
+            N_- \arrow[r, hook] \arrow[rd, dashed, hook, "e_-"'] & N \arrow[r, hook, "e"] & N', \\
+            & N'_- \arrow[ru, hook] &
+            \end{tikzcd}
+    \end{equation}
+    %
+    where the diagram commutes on the nose. This also points out the difficulties that we will have to deal with in the case of $\mfld_{/M}$ concerning the higher morphisms.
+
+    Sticking to $\mfld[r]_{/M}$ though, the assignment clearly plays well with the algebra structure of the right-hand side, through the existence of (on the nose) commutative diagrams like e.g.
+    %
+    \begin{equation}
+        \begin{tikzcd}
+            N_0 \times \mathbb{R} \arrow[r, hook, "e_0"] \arrow[d, hook] & N'_0 \times \mathbb{R} \arrow[d, hook]\\
+            N_- \arrow[r, hook, "e_-"] & N'_-,
+            \end{tikzcd}
+    \end{equation}
+    %
+    so that we clearly get a functor
+    %
+    \begin{equation}
+        \bar{f}: \mfld[r]_{/M} \xrightarrow{\ \ \ \ } \alg{\mathsf{Assoc^{RL}}} (\mfld[r]_{/M}).
+    \end{equation}
+
+    Need to be extended to $\mfld_{/M}$ by dealing with the homotopies.
+
+    %Formally, the relevant definition is \cite[def.2.1.2.7]{lurie_ha}, which says that we have to check two things: that the constructed functor $\gamma(A_-, A_+)$ lies over $\mathsf{Fin}_*$ and that it sends inert morphisms to inert morphisms.
+Factorization homology, $\int_- A_{0,\pm}$, satisfies this almost by definition, while \cref{lem:B_sym_mon} tells us that the bar construction similarly does so.
+All that is left to show is that $\bar{f}$ is a map of $\infty$-operads.
+But this is obviously the case since all it is doing is splitting the input into pieces while keeping track of how they relate to each other.
+\end{proof}
+
+\begin{lemma}\label{lem:B_sym_mon}
+    The bar construction $\mathsf{B}: \alg{\mathsf{Assoc^{RL}}} (\catC) \xrightarrow{\ \ } \catC$ is a symmetric monoidal functor.
+\end{lemma}
+
+\begin{proof}
+    The symmetric monoidal structure of $\alg{\mathsf{Assoc^{RL}}} (\catC)$ is inherited from $\catC$ pointwise.
+We denote the objects of $\alg{\mathsf{Assoc^{RL}}} (\catC)$ as $(R,A,L)$, and use $\mathsf{B}_{\bullet} (R, A, L):\Delta^{\mathsf{op}} \rightarrow \catC$ for the simplicial object of the bar construction.
+Using the language of \cite[def.2.1.2.7]{lurie_ha}, to prove that $\mathsf{B}$ is symmetric monoidal amounts to showing that for each basepoint-preserving map of based finite sets $f: I_* \xrightarrow{} J_*$ there is a commutative diagram of $\infty$-categories
+    %
+    \begin{equation}
+        \begin{tikzcd}
+            \alg{\mathsf{Assoc^{RL}}} (\catC)^I \arrow[r, "\mathsf{B}^I"] \arrow[d, "f_*"] & \catC^I \arrow[d, "f_*"] \\
+            \alg{\mathsf{Assoc^{RL}}} (\catC)^J \arrow[r, "\mathsf{B}^J"] & \catC^J.
+        \end{tikzcd}
+    \end{equation}
+
+    Following \cite[rem.2.1.2.2]{lurie_ha}, each $f$ admits a unique factorization as a composition of an active and an inert map.
+We can also further uniquely decompose the active maps into surjective active maps and injective active maps.
+So we will examine the above for each type of map separately.
+The case of inert maps is trivial as always, because of the simplicity of $f_*$.
+The case of injective active maps is essentially guaranteeing that $\mathsf{B}$ maps the monoidal unit to the monoidal unit.
+In this case the existence of the commutative diagram is provided by
+    %
+    \begin{equation}
+        \mathsf{B} (\mathbb{1}_{\alg{\mathsf{Assoc^{RL}}} (\catC)}) = \mathsf{colim} (\mathsf{B}_{\bullet} (\mathbb{1},\mathbb{1},\mathbb{1})) \simeq \mathsf{colim} (\Delta^{\mathsf{op}} \xrightarrow{\{ \mathbb{1}\}} \catC) \simeq \mathbb{1}.
+    \end{equation}
+    %
+    Finally, the case of surjective active morphisms describes what happens when we use the monoidal product to multiply.
+In this case we will look at the model calculation for the active map $f: \langle 2 \rangle \xrightarrow{} \langle 1 \rangle$.
+All other possibilities go along similar lines.
+Given two objects $H = (R,A,L)$ and $H' = (R',A',L')$ we have
+    %
+    \begin{align}
+        \mathsf{B}(H \otimes H') &= \mathsf{colim} (\mathsf{B}_{\bullet} ((R,A,L) \otimes (R',A',L')))\notag\\
+        &= \mathsf{colim} (\mathsf{B}_{\bullet} (R \otimes R', A \otimes A', L \otimes L'))\notag\\
+        &\simeq \mathsf{colim} (\mathsf{B}_{\bullet} (R, A, L) \otimes \mathsf{B}_{\bullet} (R', A', L'))\notag\\
+        &= \mathsf{colim} (\Delta^{\mathsf{op}} \rightarrow \Delta^{\mathsf{op}} \times \Delta^{\mathsf{op}} \xrightarrow{\mathsf{B}_{\bullet} (R, A, L) \otimes \mathsf{B}_{*} (R', A', L')} \catC)\notag\\
+        &\simeq \mathsf{colim} (\Delta^{\mathsf{op}} \times \Delta^{\mathsf{op}} \xrightarrow{\mathsf{B}_{\bullet} (R, A, L) \otimes \mathsf{B}_{*} (R', A', L')} \catC)\notag\\
+        &\simeq \mathsf{colim} (\mathsf{B}_{\bullet} (R, A, L)) \otimes \mathsf{colim} (\mathsf{B}_{*} (R', A', L'))\notag\\
+        &= \mathsf{B}(H) \otimes \mathsf{B}(H'),
+    \end{align}
+    %
+    where $\Delta^{\mathsf{op}} \rightarrow \Delta^{\mathsf{op}} \times \Delta^{\mathsf{op}}$ is the diagonal functor.
+The first equivalence comes from the symmetric monoidal structure of $\catC$ dues to reshuffling in the simplicial object.
+The second equivalence uses the finality of the diagonal functor which comes from the fact that $\Delta^{\mathsf{op}}$ is sifted.
+Finally, the third equivalence exists because the symmetric monoidal structure of $\catC$ commutes with (sifted) colimits.
+\end{proof}
+
+\begin{proof}[Proof of \cref{thm:gluing_alg_disk/M}]
     The data of a collar-gluing provides open embeddings $M_0 \times \mathbb{R} \xhookrightarrow{} M_-$ and $M_0 \times \mathbb{R} \xhookrightarrow{} M_+$, where $M_-$, $M_0$ and $M_+$ have the usual meanings as in \cref{def:collar-gluing}.
@@
     %
-    which, by the universal property of the pullback, gives us a canonical functor $\rho: \alg{\disk_{/M}} (\catC) \rightarrow \mathscr{P}$.
-We also want to construct a functor that partially goes in the other direction.
-Namely, given the data of objects $(A_-, A_+) \in \alg{\disk_{/M_-}} (\catC) \times \alg{\disk_{/M_+}} (\catC)$ such that $A_-|_{M_0 \times \mathbb{R}} = A_+|_{M_0 \times \mathbb{R}} = : A_0$ we want to construct a functor $A: \disk_{/M} \xrightarrow{} \catC$.
-The construction relies on using factorization homology and the bar construction.
+    which, by the universal property of the pullback, gives us a canonical functor $\rho: \alg{\disk_{/M}} (\catC) \rightarrow \mathscr{P}$. Our job is to find an inverse to this functor.
+
+    Consider the following construction.
+Given the data of an object $(A_-, A_+) \in \alg{\disk_{/M_-}} (\catC) \times \alg{\disk_{/M_+}} (\catC)$ such that $A_-|_{M_0 \times \mathbb{R}} = A_+|_{M_0 \times \mathbb{R}} = : A_0$ we want to construct a functor $A: \disk_{/M} \xrightarrow{} \catC$.
+We do this by relying on factorization homology and the bar construction.
 Given $(U \xhookrightarrow{} M) \in \disk_{/M}$ we define
@@
 Well-definition of the bar construction is provided if we have the appropriate left and right module structures on $\int_{U_-} A_-$ and $\int_{U_+} A_+$ over the associative algebra $\int_{U_0 \times \mathbb{R}} A_0$.
-Pushforward along the restrictions $f|_{U-}: U_- \rightarrow \left[-1, 1\right)$ and $f|_{U+}: U_+ \rightarrow \left(-1, 1\right]$, together with the properties of factorization homology provides these left and right module structures.
+Pushforward along the restrictions $f|_{U_-}: U_- \rightarrow \left[-1, 1\right)$ and $f|_{U_+}: U_+ \rightarrow \left(-1, 1\right]$, together with the properties of factorization homology provides these left and right module structures.
 Furthermore, the associative algebra object is exactly the appropriate one since consecutive restrictions commute on the nose.
@@
     %
-    where $\bar{f}: \mfld_{/M} \xrightarrow{} \alg{\mathsf{Assoc^{RL}}} (\mfld_{/M})$ is the functor induced by the collar-gluing, which on objects acts as $(N \xhookrightarrow{} M) \mapsto (N_-, N_0 \times \mathbb{R}, N_+)$, and $\mathsf{B}: \alg{\mathsf{Assoc^{RL}}} (\catC) \xrightarrow{} \catC$ is the bar construction functor.
+    where $\bar{f}$ is the functor from \cref{lem:fbar_func}.
 
-    We will show that the functor $\rho$ is an equivalence by first checking that it is an equivalences on maximal $\infty$-subgroupoids and subsequently that it is an equivalence on morphism spaces.
-In accomplishing the first goal we can use the fact that our algebras are valued in a symmetric monoidal $\infty$-category, as opposed to the more general case of an $\infty$-operad.
-Leveraging the adjunction
+    Our first order of business is to show that $\gamma$ actually even lands in $\alg{\disk_{/M}} (\catC)$, and not just $\mathsf{Fun}(\disk_{/M}, \catC)$.
+Since we have expressed the construction $A = \gamma(A_-, A_+)$ functorially, we can see that $A$ will inherit the structure of an algebra from the fact that factorization homology and the bar construction are symmetric monoidal functors (see \cref{lem:B_sym_mon} for the latter), together with \cref{lem:fbar_func} that lends this property to $\bar{f}$.
+With that we have constructed a functor
     %
     \begin{equation}
-        \begin{tikzcd}
-            \cat^{\otimes} \arrow[r, hook, yshift=-1ex] & \mathscr{O} \mathsf{p}_{\infty} \arrow[l, yshift=1ex, "\mathsf{Env}"'],
-        \end{tikzcd}
+        \gamma : \mathscr{P} \xrightarrow{\ \ \ \ } \alg{\disk_{/M}} (\catC).
     \end{equation}
-    %
-    together with the fact that $\mathsf{Hom}_{\mathscr{O} \mathsf{p}_{\infty}} (\mathscr{O}, \mathscr{O}') := \alg{\mathscr{O}} (\mathscr{O}')^{\simeq}$, tells us that there is an equivalence of maximal $\infty$-subgroupoids
-    %
-    \begin{equation}
-        \alg{\disk_{/M}} (\catC)^{\simeq} \simeq \alg{\mathsf{Env}(\disk_{/M})} (\catC)^{\simeq} = \mathsf{Fun}^{\otimes} (\mathsf{Env} (\disk_{/M}), C)^{\simeq}.
-    \end{equation}
-    %
-    This implies that to check that $\rho$ is an equivalence of maximal $\infty$-subgroupoids we need to show that:
+
+    Or strategy will be to show that the pair of functors $\rho$ and $\gamma$ give rise to an equivalence by first checking that this is the case on maximal $\infty$-subgroupoids and subsequently that it is also so on morphism spaces.
+Towards the first goal we need to show that:
     %
     \begin{enumerate}
-        \item $A = \gamma (A_-, A_+)$ is actually even a symmetric monoidal functor, when viewed as a functor $\mathsf{Env} (\disk_{/M}) \xrightarrow{} \catC$,
-        \item $\rho(A)$ reproduces $(A_-, A_+)$ up to equivalence, and
+        \item $\rho( \gamma (A_-, A_+))$ reproduces $(A_-, A_+)$ up to equivalence, and
         \item $\gamma (\rho (A))$ reproduces $A$ up to equivalence.
@@
     We now check these in order.
-For the purposes of (1) denote $F_-(U) = \int_{U_-} A_-$, $F_0(U) = \int_{U_0 \times \mathbb{R}} A_0$, $F_+(U) = \int_{U_+} A_+$ and $\mathsf{B}_{\bullet} (R, A, L):\Delta^{\mathsf{op}} \rightarrow \catC$ for the simplicial object of the bar construction of a right module $R$, associative algebra $A$ and left module $L$.
-Given two objects $(U \xhookrightarrow{} M), (V \xhookrightarrow{} M) \in \mathsf{Env}(\disk_{/M})$ we have
-    %
-    \begin{align}
-        A(U \sqcup V) &= \mathsf{colim} (\mathsf{B}_{\bullet} (F_-(U \sqcup V), F_0(U \sqcup V), F_+(U \sqcup V)))\notag\\
-        &\simeq \mathsf{colim} (\mathsf{B}_{\bullet} (F_-(U) \otimes F_-(V), F_0(U) \otimes F_0(V), F_+(U) \otimes F_+(V)))\notag\\
-        &\simeq \mathsf{colim} (\mathsf{B}_{\bullet} (F_-(U), F_0(U), F_+(U)) \otimes \mathsf{B}_{\bullet} (F_-(V), F_0(V), F_+(V)))\notag\\
-        &\simeq \mathsf{colim} (\Delta^{\mathsf{op}} \rightarrow \Delta^{\mathsf{op}} \times \Delta^{\mathsf{op}} \xrightarrow{\mathsf{B}_{\bullet} (F_-(U), F_0(U), F_+(U)) \otimes \mathsf{B}_{*} (F_-(V), F_0(V), F_+(V))} \catC)\notag\\
-        &\simeq \mathsf{colim} (\Delta^{\mathsf{op}} \times \Delta^{\mathsf{op}} \xrightarrow{\mathsf{B}_{\bullet} (F_-(U), F_0(U), F_+(U)) \otimes \mathsf{B}_{*} (F_-(V), F_0(V), F_+(V))} \catC)\notag\\
-        &\simeq \mathsf{colim} (\mathsf{B}_{\bullet} (F_-(U), F_0(U), F_+(U))) \otimes \mathsf{colim} (\mathsf{B}_{*} (F_-(V), F_0(V), F_+(V)))\notag\\
-        &\simeq A(U) \otimes A(V),
-    \end{align}
-    %
-    where $\Delta^{\mathsf{op}} \rightarrow \Delta^{\mathsf{op}} \times \Delta^{\mathsf{op}}$ is the diagonal functor.
-The first equivalence comes about because factorization homology is symmetric monoidal, the second equivalence is given because $\catC$ is a symmetric monoidal $\infty$-category (and not simply monoidal).
-The fourth equivalence uses the finality of the diagonal functor which comes from the fact that $\Delta^{\mathsf{op}}$ is sifted.
-Finally, the fifth equivalence exists because the symmetric monoidal structure commutes with (sifted) colimits.
-This shows that $A$ is a monoidal functor; that it is symmetric too is immediately obvious from the above calculation.
-
-    Checking (2) amounts to evaluating disks $U$ which are contained in only one of the pieces $M_-$, $M_0 \times \mathbb{R}$ and $M_+$.
+Checking (1) amounts to evaluating disks $U$ which are contained in only one of the pieces $M_-$, $M_0 \times \mathbb{R}$ and $M_+$.
 For the case of $U_0 \times \mathbb{R} = \emptyset = U_+$, we have
@@
     %
-    where the last equivalence is provided by the collar-gluing property of factorization homology. This observation is also what confirms (3). Namely,
+    where the last equivalence is provided by the collar-gluing property of factorization homology. This observation is also what confirms (2). Namely,
     %
@@
 
-    Finally, we want to show that $\rho$ is fully faithful, i.e. we need to show that it is an equivalence of morphism spaces
-    %
-    \begin{equation}
-        \mathsf{Hom}_{\alg{\disk_{/M}} (\catC)}(A, B) \simeq \mathsf{Hom}_{\mathscr{P}}((A_-, A_+), (B_-, B_+)),
-    \end{equation}
-    %
-    for each $A, B \in \alg{\disk_{/M}} (\catC)$.
-By the definition of algebras over an $\infty$-operad we have that $\alg{\disk_{/M}} (\catC)$ is a full $\infty$-subcategory of $\mathsf{Fun}(\disk_{/M}, \catC)$, and since we already expressed the construction functorially with $\rho$ and $\gamma$, all that remains to be checked is that the already defined maps
+    Finally, we want to show that $\rho$ is fully faithful, i.e. we want to show that
     %
@@
         \begin{tikzcd}
-            \mathsf{Hom}_{\mathsf{Fun}(\disk_{/M}, \catC)}(A, B) \arrow[r, bend left=4, "\rho"] & \mathsf{Hom}_{\mathscr{P}}((A_-, A_+), (B_-, B_+)) \arrow[l, bend left=4, "\gamma"]
+            \mathsf{Hom}_{\alg{\disk_{/M}} (\catC)}(A, B) \arrow[r, bend left=4, "\rho"] & \mathsf{Hom}_{\mathscr{P}}((A_-, A_+), (B_-, B_+)) \arrow[l, bend left=4, "\gamma"]
         \end{tikzcd}
@@
     %
-    gives rise to an equivalence.
-That is, we have to do similar computations as (2) and (3) above, but now on the level of morphisms.
-Nothing new happens in the case of (2) since its logic essentially only depends on the properties of the bar construction when restricting.
-In the case of (3) we crucially used the collar-gluing property of factorization homology.
-That this property continues to hold at the morphism level is a consequence of the fact that \cref{prop:barconst=intinterval} is an equivalence not only at the level of objects, but also at the level of functors, together with the pushforward property which also holds functorially à la \cref{rem:fh_pushforward_functorial}.
+    represents an equivalence of spaces for each $A, B \in \alg{\disk_{/M}} (\catC)$.
+That is, we have to do similar computations as (1) and (2) above, but now on the level of morphisms.
+Nothing new happens in the calculations involving restrictions that don't involve multiple pieces, since their logic essentially only depends on the properties of the bar construction when restricting.
+In the rest of the calculations we crucially used the collar-gluing property of factorization homology.
+That this property continues to hold at the morphism level is a consequence of the fact that we made sure to elevate the statement of \cref{prop:barconst=intinterval} to the level of functors, together with the pushforward property which also holds functorially à la \cref{rem:fh_pushforward_functorial}.
+Namely, these provide equivalences of functors
+    %
+    \begin{equation}
+        \int_U - \simeq \int_{[-1,1]} (f|_U)_* - \simeq \mathsf{B} \circ (f|_U)_* = \int_{U_-} (-)_- \bigotimes\limits_{\int_{U_0 \times \mathbb{R}} (-)_0} \int_{U_+} (-)_+,
+    \end{equation}
+    %
+    which is exactly the collar-gluing property at the level of morphisms.
 \end{proof}

### 2024-03-01 sections/0intro.tex
minor changes in the intro

@@
 \textbf{\Cref{ch:strat_spaces} Stratified Spaces:} The first section deals with setting up the theory of stratified spaces that we will use.
-It is essentially a recap of the necessary results from the work of Ayala, Francis and Tanaka \cite{aft_localstrut}, which is one of our main sources.
+It is essentially a recap of the necessary results from the work of Ayala, Francis and Tanaka (AFT) \cite{aft_localstrut}, which is one of our main sources.
 The idea and fundamentals of stratified spaces have existed for a long time in different incarnation beginning with the work of Whitney \cite{whitney92}.
@@
 We will not go into the full details that this incarnation of the theory has to offer, but instead we will only mention results that we will make use of later on.
-Beyond, conical smoothness, this will include tangential structure and its stratified generalization, together with the packaging of both of these data into the concept of an $\infty$-category of basic singularity types.
-For the proofs of these statements the reader is encouraged to check \cite{aft_localstrut}.
+Beyond conical smoothness, this will include tangential structure and its stratified generalization, together with the packaging of both of these data into the concept of an $\infty$-category of basic singularity types.
+For the proofs of these statements the reader is encouraged to consult \cite{aft_localstrut}.
 
 \textbf{\Cref{ch:fact_hom} Factorization Homology:} The second section will present the theory of factorization homology.
-Similar to the first section this will mostly be a recap of useful results developed by Ayala, Francis and Tanaka.
+Similar to the first section this will mostly be a recap of useful results developed by AFT.
 Specifically, the stratified space results can be found in \cite{aft_fhstrat}, while the results for topological manifolds can be found in \cite{af_fhtop}.
 For the purposes of the theory we will need the concept of (structured) disk algebras, since this will be the algebraic input.
-Factorization homology will then return an invariant of a manifold.
+Factorization homology will then return an invariant of a manifold; or, depending on one's point of view, an invariant of the input algebra.
 We will explore the key example of factorization homology over the closed, oriented interval $[-1,1]$, and see how this gives rise to the algebraic concept of the two-sided bar construction.
 More generally, this underpins the theory because it codifies the property of $\otimes$-excision.
-Finally, we will also state a classification result about a certain type of disk algebras with stratified structure.
+Finally, we will also state a well-known classification result, due to AFT, about a certain type of disk algebras with stratified structure.
 
 \textbf{\Cref{ch:fact_alg} Factorization Algebras:} The third section introduces the concept of factorization algebras, together with its different variations, like prefactorization algebras and locally constant factorization algebras.
-Of these, the locally constant factorization algebras will be the ones that capture the different possible stratified structure that a manifold can have, and they will be a large focus of the work.
+Of these, the locally constant factorization algebras will be the ones that capture the different possible stratified structures that a manifold can have, and they will be a large focus of this work.
 The definitions of these will not be novel.
@@
 However, all of the above works take a slightly different perspective in their presentation of the definitions, which we hope to unite in this work.
-The key result of this section is \cref{thm:disk_alg=lcfa}:
+The key result of this section is the following:
 %
-\begin{theorem}
+\begin{theorem*}[\ref{thm:disk_alg=lcfa}]
     There is an equivalence of $\infty$-categories between locally constant factorization algebras over a stratified manifold $M$ and $\disk_{/M}$-algebras
@@
     given by factorization homology,
-\end{theorem}
+\end{theorem*}
 %
@@
 These show that the $\infty$-operad governing factorization algebras can be taken to be the slice $\infty$-operad $\disk_{/M}$ (or $\disk[r]_{/M}$ for the ordinary case).
-We then introduce some operations that we can do with factorization algebras like the pushforward and restriction, as well as state a result for locally constant factorization algebras on product spaces.
+We then introduce some operations that we can do with factorization algebras like the pushforward and restriction, as well as prove the following additivity result for locally constant factorization algebras on product spaces:
+\begin{theorem*}[\ref{prop:exp_of_products_lc}]
+    Let $M$ and $N$ be stratified manifolds. Then there is an equivalence
+    \[
+        \lcfa_{M \times N}(\catC) \simeq \lcfa_{M}(\lcfa_{N}(\catC))
+    \]
+    between the $\infty$-category of constructible factorization algebras on $M\times N$ and that of those on $M$ valued constructible factorization algebras on $N$.
+\end{theorem*}
+This result was conjectured by Ginot in \cite{ginot2015} and Ayala [private communication].
+
 Finally, we will examine some examples of factorization algebras whose construction is known, specifically, locally constant factorization algebras on the intervals $(-1,1)$, $[-1,1)$ and $[-1,1]$ as well as Euclidean spaces $\mathbb{R}^n$ more generally.
@@
 \textbf{\Cref{ch:gluing_disk_alg} Collar-gluings and Disk Algebras:} The fourth section presents a novel result about the behavior of certain types of disk algebras under the operation of collar-gluing in the manifold variable.
-It essentially shows that one can reproduce a disk algebra on a stratified manifold if we know it on some particular pieces of it together with the data of how to glue them.
+It essentially shows that we can reproduce a disk algebra on a stratified manifold if we know it on some particular pieces of it together with the data of how to glue them.
 Formally, we have
 %
-\begin{theorem}
+\begin{theorem*}[\ref{thm:gluing_alg_disk/M}]
     Given a collar-gluing of stratified manifolds $f: M \rightarrow [-1,1]$, the $\infty$-category of $\disk_{/M}$-algebras is equivalent to the pullback of $\infty$-categories
@@
     \end{equation}
-\end{theorem}
+\end{theorem*}
 %
 Together with the results of the previous section this gluing holds for locally constant factorization algebras too, and it hugely expands the number of manifolds for which the $\infty$-category of locally constant factorization algebras can be specified.
-As a small example, it gives a way to work on all higher spheres $S^n$, of which, only the circle has been described to date.
+As a straightforward example, it gives a way to work on and classify factorization algebras on all spheres $S^n$.
+Only the circle has been described to date (\cite{ginot2015}) using equivariant factorization algebras, so we should note the result above lets us obtain generalizations without falling back on covering space techniques.
 
 \textbf{\Cref{ch:classif_defect_mfld} Classifying $\lcfa$s on Defect Manifolds:} The fifth section focuses on the stratified structure and gives a way to express what effect this has on the locally constant factorization algebras.
-Specifically, we look at the data of a smooth manifold $M$ with a distinguished, properly embedded submanifold $\Sigma$ (also known as a defect) as the data of a stratified manifold $M_\Sigma$.
+Specifically, we look at the data of a smooth manifold $M$ with a distinguished, properly embedded submanifold $\Sigma$ (also known as a defect submanifolds) as the data of a stratified manifold $M_\Sigma$.
 We will show that, along with giving algebras associated to the different pieces, locally constant factorization algebras on these manifolds, in some (precise) sense, also encode a module structure associated with $\Sigma$.
@@
     \item Does there exist a version of factorization algebras that capture information both about the stratified structure of a manifold and about its tangential structure?
+An even more general, \emph{geometric} version was studied by Pe\~{n}a in \cite{pena2022geometric}.
+Extending our results and previous known results to such a setting remains desirable.
 \end{itemize}
@@
 %
-which are both equivalences in appropriate ways.
+which are both Quillen equivalences in appropriate ways.
 In particular, we will not distinguish notationally the nerve of an ordinary category from the ordinary category itself.
-Similarly, we will not distinguish between multicategories and their $\infty$-operadic nerve.
+Similarly, we will not distinguish between topological multicategories and their $\infty$-operadic nerve.
 

### 2024-03-01 sections/0intro.tex
Add files via upload

--- 2024-02-19 sections/0intro.tex
@@
 For the purposes of the theory we will need the concept of (structured) disk algebras, since this will be the algebraic input.
-Factorization homology will then return an invariant of a manifold.
+Factorization homology will then combine this with the data of a specific kind of (possibly stratified) manifold into an object that can be viewed either as an invariant of the manifold or an invariant of the algebra.
 We will explore the key example of factorization homology over the closed, oriented interval $[-1,1]$, and see how this gives rise to the algebraic concept of the two-sided bar construction.
 More generally, this underpins the theory because it codifies the property of $\otimes$-excision.
-Finally, we will also state a classification result about a certain type of disk algebras with stratified structure.
+Finally, we will also state a classification result \cite[prop.4.8]{aft_fhstrat} about a certain type of disk algebras with stratified structure.
 
@@
 These show that the $\infty$-operad governing factorization algebras can be taken to be the slice $\infty$-operad $\disk_{/M}$ (or $\disk[r]_{/M}$ for the ordinary case).
-We then introduce some operations that we can do with factorization algebras like the pushforward and restriction, as well as state a result for locally constant factorization algebras on product spaces.
+We then introduce some operations that we can do with factorization algebras like the pushforward and restriction, as well as state a result for locally constant factorization algebras on product spaces, which confirms a conjecture of \cite{ginot2015}:
+%
+\begin{proposition}
+    Let $M$ and $N$ be stratified manifolds. There is an equivalence of $\infty$-categories
+    %
+    \begin{equation}
+        \bar{\pi}: \lcfa_{M \times N}(\catC) \xrightarrow{\ \ \simeq \ \ } \lcfa_{M}(\lcfa_{N}(\catC)).
+    \end{equation}
+\end{proposition}
+%
 Finally, we will examine some examples of factorization algebras whose construction is known, specifically, locally constant factorization algebras on the intervals $(-1,1)$, $[-1,1)$ and $[-1,1]$ as well as Euclidean spaces $\mathbb{R}^n$ more generally.
@@
 \begin{itemize}
-    \item Does there exist a version of factorization algebras that capture information both about the stratified structure of a manifold and about its tangential structure?
+    \item Does there exist a version of factorization algebras that usefully capture information both about the stratified structure of a manifold and about its tangential structure?
 \end{itemize}
 %
+The recent thesis \cite{pena2022} could provide a fruitful direction of exploration of the former concept.
 In a similar vein, \cite{cg2016} explain why it's important to have the concept of a $G$-equivariant factorization algebra, where $G$ is a Lie group.
@@
 \end{itemize}
+%
+The beginnings of examining this idea can already be found in the thesis \cite{murray2020}, however the development there, while important, is still preliminary.
 
@@
 %
-which are both equivalences in appropriate ways.
+which are both Quillen-equivalences in appropriate ways.
+The interested reader can find accounts of these matters in e.g.
+.....
 In particular, we will not distinguish notationally the nerve of an ordinary category from the ordinary category itself.
-Similarly, we will not distinguish between multicategories and their $\infty$-operadic nerve.
+Similarly, we will not distinguish between (topological) multicategories and their $\infty$-operadic nerve.
 

### 2024-03-01 sections/0intro.tex

--- 2024-03-01 sections/0intro.tex
@@
 \textbf{\Cref{ch:fact_hom} Factorization Homology:} The second section will present the theory of factorization homology.
-Similar to the first section this will mostly be a recap of useful results developed by AFT.
+Similar to the first section this will mostly be a recap of useful results developed by Ayala, Francis and Tanaka.
 Specifically, the stratified space results can be found in \cite{aft_fhstrat}, while the results for topological manifolds can be found in \cite{af_fhtop}.
 For the purposes of the theory we will need the concept of (structured) disk algebras, since this will be the algebraic input.
-Factorization homology will then return an invariant of a manifold; or, depending on one's point of view, an invariant of the input algebra.
+Factorization homology will then combine this with the data of a specific kind of (possibly stratified) manifold into an object that can be viewed either as an invariant of the manifold or an invariant of the algebra.
 We will explore the key example of factorization homology over the closed, oriented interval $[-1,1]$, and see how this gives rise to the algebraic concept of the two-sided bar construction.
 More generally, this underpins the theory because it codifies the property of $\otimes$-excision.
-Finally, we will also state a well-known classification result, due to AFT, about a certain type of disk algebras with stratified structure.
+Finally, we will also state a classification result \cite[prop.4.8]{aft_fhstrat} about a certain type of disk algebras with stratified structure.
 
@@
 These show that the $\infty$-operad governing factorization algebras can be taken to be the slice $\infty$-operad $\disk_{/M}$ (or $\disk[r]_{/M}$ for the ordinary case).
-We then introduce some operations that we can do with factorization algebras like the pushforward and restriction, as well as prove the following additivity result for locally constant factorization algebras on product spaces:
-\begin{theorem*}[\ref{prop:exp_of_products_lc}]
-    Let $M$ and $N$ be stratified manifolds. Then there is an equivalence
-    \[
-        \lcfa_{M \times N}(\catC) \simeq \lcfa_{M}(\lcfa_{N}(\catC))
-    \]
-    between the $\infty$-category of constructible factorization algebras on $M\times N$ and that of those on $M$ valued constructible factorization algebras on $N$.
-\end{theorem*}
-This result was conjectured by Ginot in \cite{ginot2015} and Ayala [private communication].
-
+We then introduce some operations that we can do with factorization algebras like the pushforward and restriction, as well as state a result for locally constant factorization algebras on product spaces, which confirms a conjecture of \cite{ginot2015}:
+%
+\begin{proposition}
+    Let $M$ and $N$ be stratified manifolds. There is an equivalence of $\infty$-categories
+    %
+    \begin{equation}
+        \bar{\pi}: \lcfa_{M \times N}(\catC) \xrightarrow{\ \ \simeq \ \ } \lcfa_{M}(\lcfa_{N}(\catC)).
+    \end{equation}
+\end{proposition}
+%
 Finally, we will examine some examples of factorization algebras whose construction is known, specifically, locally constant factorization algebras on the intervals $(-1,1)$, $[-1,1)$ and $[-1,1]$ as well as Euclidean spaces $\mathbb{R}^n$ more generally.
@@
 \begin{itemize}
-    \item Does there exist a version of factorization algebras that capture information both about the stratified structure of a manifold and about its tangential structure?
-An even more general, \emph{geometric} version was studied by Pe\~{n}a in \cite{pena2022geometric}.
-Extending our results and previous known results to such a setting remains desirable.
+    \item Does there exist a version of factorization algebras that usefully capture information both about the stratified structure of a manifold and about its tangential structure?
 \end{itemize}
 %
+The recent thesis \cite{pena2022} could provide a fruitful direction of exploration of the former concept.
 In a similar vein, \cite{cg2016} explain why it's important to have the concept of a $G$-equivariant factorization algebra, where $G$ is a Lie group.
@@
 %
-which are both Quillen equivalences in appropriate ways.
+which are both Quillen-equivalences in appropriate ways.
+The interested reader can find accounts of these matters in e.g.
+.....
 In particular, we will not distinguish notationally the nerve of an ordinary category from the ordinary category itself.
-Similarly, we will not distinguish between topological multicategories and their $\infty$-operadic nerve.
+Similarly, we will not distinguish between (topological) multicategories and their $\infty$-operadic nerve.
 

### 2024-03-01 sections/2homology.tex

@@
 Variants that accommodate stratified manifolds instead of smooth ones and even $(\infty,n)$-categories instead of algebras have also been worked out.
+Given the focus of the present work, we will be concerned with the variant that can evaluate stratified manifolds.
+We will not be interested, however, in generalizing the algebraic input beyond disk algebras to the realm of $(\infty,n)$-categories.
 Fixing the algebra, the construction is functorial with respect to open embeddings in the manifold variable, which is the starting point to show that it is a chain level homology theory in a generalized sense, and giving the name.
@@
 Having said that, the first part of the proposition is just the classical statement that the little $n$-disks operad and the little $n$-cubes operad are equivalent.
+Through the work of \cite{lurie_tqft} and \cite{scheimbauer2014}, $\mathbb{E}_n$-algebras also serve as input for constructing fully extended TQFTs by using factorization homology.
 \end{remark}
@@
     as discussed in \cite[prop.4.1.1.8]{lurie_htt}, where the functor is the obvious one.
-Furthermore, \cite[\href{https://kerodon.net/tag/016H}{016H}]{lurie_kerodon} tells us that the coslice construction is functorial, which, after restricting, defines the functors
+Furthermore, \cite[\href{https://kerodon.net/tag/016H}{016H}]{lurie_kerodon} tells us that the slice construction is functorial, which, after restricting, defines the functors
     %
@@
     whose value on objects is given by $G \mapsto \mathscr{C}_{G/}$.
-We can now state that by naturality in $G$ we mean that the functors \cref{eq:fin_equivs_cat} assemble into an equivalence of functors
+We can now state that by naturality in $G$ we mean that the functors of \cref{eq:fin_equivs_cat} assemble into an equivalence of functors
     %

### 2024-03-01 sections/3algebras.tex

@@
 \begin{remark}\label{rem:op_to_op}
-    There is an obvious embedding functor from the poset $\opens[r](X)$ of open subsets of $X$, ordered by inclusion, to the multicategory $\opens[s](X)$, namely, the one which hits only those multi-morphisms $\{U_i\}_{i \in I} \rightarrow U$, where the cardinality of the finite set $I$ is 1.
+    There is an obvious inclusion functor from the poset $\opens[r](X)$ of open subsets of $X$, ordered by inclusion, to the multicategory $\opens[s](X)$, namely, the one which hits only those multi-morphisms $\{U_i\}_{i \in I} \rightarrow U$, where the cardinality of the finite set $I$ is 1.
 \end{remark}
@@
     %
-    of those Weiss sheaves whose underlying functor $F: \bsc_{/M} \xrightarrow{} \catC$ satisfies
+    of those Weiss cosheaves whose underlying functor $F: \bsc_{/M} \xrightarrow{} \catC$ satisfies
     %
@@
 \begin{remark}
-    Another perspective on why all of these constructions look the way they do is provided by \cref{lem:disk/M_to_disk}. It applies in all of the above cases:
+    Another perspective on why all of these constructions look the way they do is provided by \cref{lem:disk/M_to_disk}. It applies in all of the above cases, namely:
     %
@@
         \item For $\mathbb{R}$, the convenient $\infty$-category of basics is $\bstr = \mathsf{D}_1^*$,
-        \item For $\hoint$, the convenient $\infty$-category of basics is $\bstr = \mathsf{D}_1^{\partial, *}$ and
-        \item Similarly, for $[-1,1]$ the convenient $\infty$-category of basics is again $\bstr = \mathsf{D}_1^{\partial, *}$.
+        \item For $[-1,1]$ the convenient $\infty$-category of basics is $\bstr = \mathsf{D}_1^{\partial, *}$.
+        \item For $\hoint$, we could define a convenient $\infty$-category of basics which describes framed 1-dimensional manifolds which only have a right boundary (a concept that we can state because of the framing).
     \end{enumerate}
@@
 \begin{remark}
-    The proof of \cref{prop:exp_of_products_lc}, when specialized to ordinary manifolds, as given in \cite{ginot2015} actually depends on Dunn additivity to work, however the proof presented in \cite{lurie_ha} is independent.
+    The proof of \cref{prop:exp_of_products_lc}, when specialized to ordinary manifolds, as given in \cite{ginot2015} actually depends on Dunn additivity to work, however the proof presented above and the one in \cite{lurie_ha} are independent.
 \end{remark}

### 2024-03-01 sections/4gluing.tex

@@
 \end{proof}
+
+\begin{corollary}\label{cor:fbar_func_discrete}
+    Taking only the first part of the proof of \cref{lem:fbar_func} it is immediate that in the setting of $\mfld[r]_{/M}$ there is also a functor
+    %
+    \begin{equation}
+        \bar{f}: \mfld[r]_{/M} \xrightarrow{\ \ \ \ } \alg{\mathsf{Assoc^{RL}}} (\mfld[r]_{/M}),
+    \end{equation}
+    %
+    that is an algebra.
+\end{corollary}
 
@@
     %
-    which is exactly the collar-gluing property at the level of morphisms.
+    which is exactly the collar-gluing property extended to the level of morphisms.
 \end{proof}
@@
 \end{remark}
+
+Taking into account \cref{cor:disk_alg=falg} together with \cref{cor:fbar_func_discrete}, as well as the definition of factorization homology in the setting of the category $\disk[r]_{/M}$, the proof of \cref{thm:gluing_alg_disk/M} can be seen to clearly hold even in case of ordinary factorization algebras.
+
+\begin{corollary}\label{cor:gluing_falgs}
+    A collar-gluing of stratified manifolds $f: M \rightarrow [-1,1]$ induces an equivalence of $\infty$-categories
+    %
+    \begin{equation}
+        \falg_M (\catC) \simeq \falg_{M_-} (\catC) \bigtimes_{\falg_{M_0 \times \mathbb{R}} (\catC)} \falg_{M_+}(\catC).
+    \end{equation}
+\end{corollary}
 
@@
 
-    We should remark that the fact that we can take the opposite algebra in one direction only is a consequence of Dunn additivity \cref{prop:dunn_additivity}.
+    We should remark that the fact that we can take the opposite algebra in one direction only is a consequence of the Dunn additivity of \cref{prop:dunn_additivity}.
 Without it, we wouldn't be able to combine the opposite algebra in one direction with the original algebra in the other direction into a well-defined algebra in two dimensions.

### 2024-03-01 sections/1stratified.tex
Changed some things in section 1. More to be done.

@@
 For our purposes, we will follow the account of \cite{aft_localstrut}.
+A compatible source is also \cite[sec.A.5]{lurie_ha}.
 The majority of the work on factorization homology has so far been elaborated using this particular set of definitions, and similarly the stratified spaces used in the literature on factorization algebras are usually subsumed too.
@@
 
-\begin{definition}[\cite{lurie_ha}]
+\begin{definition}
     Let $P$ be a poset.
@@
 We will sometimes refer to $X$ as the underlying topological space of a stratified space.
-Furthermore, we denote the preimage of $p \in P$ as $X_p$ and call it the $p$th stratum of $X$.
+Furthermore, we denote the preimage of $p \in P$ as $X_p$ and call it the $p$th stratum of $X$\footnote{Sometimes the name stratum is reserved for the connected components of $X_p$ if strata are required to be connected.}.
 \end{definition}
@@
 Next, we construct the cone of a stratified space.
-This plays a very important role in the theory of stratified manifolds, since the neighborhoods of these spaces will always look like a cone over some space with a possible further thickening by some $\mathbb{R}^k$.
-That is, the cones will be the model space for singularities.
+This plays a very important role in the theory of conically smooth manifolds, because it provides the prototypical departure from smoothness.
+In other words, the local structure of these will always look like a cone over some space with a possible further thickening by some $\mathbb{R}^k$, just as the local structure of smooth manifolds is given by $\mathbb{R}^k$; the cones will be the model spaces for singularities.
 
@@
     \begin{equation}
-        \mathsf{C}(P) := * \coprod_{P \times \{ 0\}} P \times [1].
+        \mathsf{C}(P) := * \coprod_{P \times \{ 0\}} P \times [1] \cong P^{\vartriangleleft}.
     \end{equation}
@@
 
-\begin{remark}
-    Because of the above theorem, $C^0$ stratified spaces $X \rightarrow P$ have a natural filtration by dimension since there is a map $P \rightarrow \mathbb{N}$, which sends $p \mapsto \mathsf{dim}(X_p)$.
-In our examples of interest we will always choose dimension as the stratification.
-\end{remark}
+For topological spaces we have the concept of covering dimension $\mathsf{dim}_x (X)$ at a point $x \in X$.
+$C^0$ stratified spaces have an additional, related concept called depth.
+It plays a key role in describing these spaces, especially on the technical side\footnote{For example, we said that \cref{thm:basics_give_basis}, as a definition, would be circular.
+One way to resolve this is by induction on depth since $\mathsf{dpt} (\mathbb{R}^n \times \mathsf{C}(Z)) = \mathsf{dpt} (\mathsf{C}(Z)) = \mathsf{dpt} (Z) + 1$}.
+As the name suggests, it conveys information about how deep the stratification is.
 
-The smooth version of the above concepts also exists and will be the one that is of main interest.
+\begin{definition}
+    Given a $C^0$ stratified space $(X \xrightarrow{s} P)$ the \emph{depth at $x$} is
+    %
+    \begin{equation}
+        \mathsf{dpt}_x (X) := \mathsf{dim}_x (X) - \mathsf{dim}_x (X_{s(x)}).
+    \end{equation}
+    %
+    The depth of $X$, $\mathsf{dpt} (X)$, in general is the supremum of the depths over all points. Just as with dimension, the convention is that $\mathsf{dpt}(\emptyset) = -1$.
+\end{definition}
+
+The `smooth' version of the above concepts also exists and will be the one that is of main interest to us.
 As was the case for $C^0$ stratified spaces, we will not give the precise definition of a \emph{conically smooth stratified space} (or \emph{stratified manifold} for short), since the exact definition is involved.
@@
 
-The reason why the definition is involved is, because unlike in the smooth case the presence of the compact spaces $Z_\alpha$ means that we have to use induction to define conical smoothness.
+The reason why the definition is involved is, because unlike in the smooth case the presence of the compact spaces $Z_\alpha$ means that we have to use induction on depth to define conical smoothness.
 
@@
 %
-\begin{example}
+\begin{example}[{\cite[ex.1.2]{aft_fhstrat}}]
     Smooth manifolds fall under the definition of stratified manifolds as those that only have one stratum.
-A smooth map $f$ between compact smooth manifolds gives rise to a conically smooth map $\mathsf{f}$ between the cones of these manifolds.
-If we also have a smooth map between Euclidean spaces $g$ then the map $h \times \mathsf{C}(f)$ is also conically smooth.
-This already allows us to describe stratified manifolds with two strata.
+A smooth map $f: Z \xrightarrow{} Z'$ between compact smooth manifolds gives rise to a conically smooth map $\mathsf{C}(f)$ between the cones of these manifolds.
+If we also have a smooth map between Euclidean spaces $g: \mathbb{R}^{n} \xrightarrow{} \mathbb{R}^{n'}$ then the map $g \times \mathsf{C}(f): \mathbb{R}^{n} \times \mathsf{C} (Z) \xrightarrow{} \mathbb{R}^{n'} \times \mathsf{C} (Z')$ is conically smooth.
+This already allows us to describe stratified manifolds of depth 1.
 \end{example}
@@
         \item $f$ is an \emph{open embedding} if it is an open map that is conically diffeomorphic onto its image.
-        \item $f$ is a \emph{refinement} if it's a homeomorphism of underlying topological spaces, and it's restriction to each stratum of $M$ is an embedding.
+        \item $f$ is a \emph{refinement} if it's a homeomorphism of underlying topological spaces, and its restriction to each stratum of $M$ is an embedding.
         \item Let $P_N$ be the stratifying poset of $N$.

### 2024-03-04 sections/1stratified.tex

@@
 The majority of the work on factorization homology has so far been elaborated using this particular set of definitions, and similarly the stratified spaces used in the literature on factorization algebras are usually subsumed too.
-Here we will only recap the results that will be of use to us.
-Further details are, of course, discussed in \cite{aft_localstrut}, where one can find a great explanation of the definitions that are needed, and detailed proofs of the theorems that can be proven.
+Here we will only recap the definitions, results and examples that will be of use to us.
+Further details are, of course, discussed in the original \cite{aft_localstrut}, where one can find great explanations of the definitions that are needed, and detailed proofs of the theorems that can be proven.
 

### 2024-03-04 sections/0intro.tex
Standardized main result citing in introduction.
minor changes until §1.2

@@
 %
-\begin{proposition}
+\begin{proposition*}[\ref{prop:exp_of_products_lc}]
     Let $M$ and $N$ be stratified manifolds. There is an equivalence of $\infty$-categories
@@
     \end{equation}
-\end{proposition}
+\end{proposition*}
 %
@@
 \textbf{\Cref{ch:classif_defect_mfld} Classifying $\lcfa$s on Defect Manifolds:} The fifth section focuses on the stratified structure and gives a way to express what effect this has on the locally constant factorization algebras.
-Specifically, we look at the data of a smooth manifold $M$ with a distinguished, properly embedded submanifold $\Sigma$ (also known as a defect submanifolds) as the data of a stratified manifold $M_\Sigma$.
+Specifically, we look at the data of a smooth manifold $M$ with a distinguished, properly embedded submanifold $\Sigma$ (also known as a defect submanifold) as the data of a stratified manifold $M_\Sigma$.
 We will show that, along with giving algebras associated to the different pieces, locally constant factorization algebras on these manifolds, in some (precise) sense, also encode a module structure associated with $\Sigma$.
@@
 %
-which are both Quillen-equivalences in appropriate ways.
-The interested reader can find accounts of these matters in e.g.
-.....
+which are both Quillen-equivalences in appropriate ways (\cite{joyal2007quasi,bergner2010survey}).
 In particular, we will not distinguish notationally the nerve of an ordinary category from the ordinary category itself.
 Similarly, we will not distinguish between (topological) multicategories and their $\infty$-operadic nerve.
-
 \end{document}

### 2024-03-04 sections/1stratified.tex
minor changes until §1.2

@@
     Let $P$ be a poset.
-A \emph{$P$-stratified space} is a topological space $X$ together with a map $X \rightarrow P$, which we call the stratification of $X$.
+A \emph{$P$-stratified space} is a topological space $X$ together with a continuous map $X \rightarrow P$, which we call the \emph{stratification} of $X$.
+The poset $P$ is called the \emph{stratifying poset}.
 We will sometimes refer to $X$ as the underlying topological space of a stratified space.
-Furthermore, we denote the preimage of $p \in P$ as $X_p$ and call it the $p$th stratum of $X$\footnote{Sometimes the name stratum is reserved for the connected components of $X_p$ if strata are required to be connected.}.
+Furthermore, we denote the preimage of $p \in P$ as $X_p$ and call it the $p$'th stratum of $X$\footnote{Sometimes the name stratum is reserved for the connected components of $X_p$ if strata are required to be connected.}.
 \end{definition}
 
-\begin{example}
+\begin{example}\label{54HC9DC}
     Any CW complex $X$ can be made into a stratified space $X \rightarrow \mathbb{N}$, which sends all points in $X_{\leq k} \setminus {X_{\leq k-1}}$ to $k$, where $X_{\leq k}$ is the $k$-skeleton of $X$.
@@
 
-\begin{remark}
-    Given two stratified spaces $X \xrightarrow{s} P$ and $X' \xrightarrow{s'} P'$, we can form the product stratified space $X \times X' \xlongrightarrow{s \times s'} P \times P'$, where the partial order on the product poset is given by $(p,p') \leq (q, q') \iff (p \leq q) \land (p' \leq q')$.
-\end{remark}
-
 \begin{example}
@@
 
+\begin{example}
+    Any topological space $X$ can be stratified by its connected components, with $P$ discrete and $|P|=\pi_0(X)$.
+\end{example}
+
+\begin{remark}
+    Given two stratified spaces $X \xrightarrow{s} P$ and $X' \xrightarrow{s'} P'$, we can form the product stratified space $X \times X' \xlongrightarrow{s \times s'} P \times P'$, where the partial order on the product poset is given by $(p,p') \leq (q, q') \iff (p \leq q) \land (p' \leq q')$.
+\end{remark}
+
 \begin{definition}
-    Let $X \rightarrow P$ and $X' \rightarrow P'$ be two stratified spaces. A \emph{continuous stratified map} (or \emph{map of stratified spaces}) is a commutative diagram in $\mathsf{Top}$
+    Let $X \rightarrow P$ and $X' \rightarrow P'$ be two stratified spaces. A \emph{continuous stratified map} (or \emph{map of stratified spaces}) is a commutative diagram in $\mathsf{Top}$ of type
     %
@@
 This plays a very important role in the theory of conically smooth manifolds, because it provides the prototypical departure from smoothness.
-In other words, the local structure of these will always look like a cone over some space with a possible further thickening by some $\mathbb{R}^k$, just as the local structure of smooth manifolds is given by $\mathbb{R}^k$; the cones will be the model spaces for singularities.
+In other words, the local structure of these will always look like a cone over some space with a possible further thickening by a factor $\mathbb{R}^k$, just as the local structure of smooth manifolds is given by $\mathbb{R}^k$.
+The cones will be the model spaces for singularities.
 
@@
     Let $X \rightarrow P$ be a stratified space.
-The cone $\mathsf{C}(X \rightarrow P)$ is the stratified space constructed as follows.
+Its (\emph{open}) \emph{cone} $\mathsf{C}(X \rightarrow P)$ is the stratified space constructed as follows.
 At the level of topological spaces we define the pushout in $\mathsf{Top}$
@@
 
+The following will be used in the definition of the $\infty$-category $\mfld$ of stratified manifolds.
+
+\begin{definition}
+    Let $X\to P$ be a stratified space.
+Its \emph{closed cone} is the stratified space $\overline{C}(X)\to P^{\vartriangleleft}$ with $\overline{C}(X)=\ast\amalg_{X\times\{0\}}X\times[0,1]$ and the obvious stratification.
+\end{definition}
+
 The equivalent of a topological manifold in the stratified setting is a \emph{$C^0$ stratified space}.
@@
 We will however cite theorems that show that the spaces we consider in this work are $C^0$ stratified spaces.
-The reason why the below cannot be the actual definition is because it would partially be a cyclic statement.
-We cite it because it provides good intuition for the structure of $C^0$ stratified spaces.
+The following definition is partly cyclic, but we cite it because it provides good intuition for the structure of $C^0$ stratified spaces.
 
@@
 
-\begin{theorem}[{\cite[lem.2.2.2]{aft_localstrut}}]\label{thm:basics_give_basis}
+\begin{theorem}[{\cite[Lemma 2.2.2]{aft_localstrut}}]\label{thm:basics_give_basis}
     Let $X$ be a stratified, second countable, Hausdorff space, and consider the collection of open embeddings
@@
 
-\begin{theorem}[{\cite[cor.2.3.5]{aft_localstrut}}]
+\begin{theorem}[{\cite[Corollary 2.3.5]{aft_localstrut}}]
     Let $X \rightarrow P$ be a $C^0$ stratified space.
@@
 
-For topological spaces we have the concept of covering dimension $\mathsf{dim}_x (X)$ at a point $x \in X$.
+For topological spaces we have the concept of (\v{C}ech--Lebesgue) covering dimension $\mathsf{dim}_x (X)$ at a point $x \in X$.
 $C^0$ stratified spaces have an additional, related concept called depth.
-It plays a key role in describing these spaces, especially on the technical side\footnote{For example, we said that \cref{thm:basics_give_basis}, as a definition, would be circular.
-One way to resolve this is by induction on depth since $\mathsf{dpt} (\mathbb{R}^n \times \mathsf{C}(Z)) = \mathsf{dpt} (\mathsf{C}(Z)) = \mathsf{dpt} (Z) + 1$}.
-As the name suggests, it conveys information about how deep the stratification is.
+It plays a key role in describing these spaces.\footnote{For example, we said that \cref{thm:basics_give_basis}, as a definition, would be circular.
+One way to resolve this is by induction on depth since $\mathsf{dpt} (\mathbb{R}^n \times \mathsf{C}(Z)) = \mathsf{dpt} (\mathsf{C}(Z)) = \mathsf{dpt} (Z) + 1$} As the name suggests, it conveys information about how deep the stratification is.
+For instance, if the stratification is given by a filtration as in \Cref{54HC9DC}, then it coincides with the length of the filtration, or equivalently, with the length of the longest non-trivial chain of arrives in the stratifying poset.
+Similarly to $\mathsf{dim}$ it has a pointwise and a global version.
 
@@
 General maps of stratified manifolds will then be conically smooth if their representatives in basics are conically smooth.
-
 The reason why the definition is involved is, because unlike in the smooth case the presence of the compact spaces $Z_\alpha$ means that we have to use induction on depth to define conical smoothness.
@@
 %
-\begin{example}[{\cite[ex.1.2]{aft_fhstrat}}]
+\begin{example}[{\cite[Example 1.2]{aft_fhstrat}}]
     Smooth manifolds fall under the definition of stratified manifolds as those that only have one stratum.
@@
         \item Let $P_N$ be the stratifying poset of $N$.
-$f$ is a \emph{constructible bundle} if, for each $p \in P_N$, the restriction $f|_p: M|_{f^{-1} N_p} \rightarrow N_p$ is a fiber bundle of stratified spaces.
+Then $f$ is a \emph{constructible bundle} if, for each $p \in P_N$, the restriction $f|_p: M|_{f^{-1} N_p} \rightarrow N_p$ is a fiber bundle of stratified spaces.
+The map $f$ is a \emph{fiber bundle} if there exists a cover $\{U\hookrightarrow N\}$ of $N$ consisting of open embeddings such that the restriction of $f$ along $U$ is of type $\mathsf{pr}\colon F_U\times U\to U$ for a stratified manifold $F_U$.
     \end{enumerate}
@@
 Constructible bundles are obviously also weakly constructible.
+Their use owes to the Pushforward Theorem \cite[Theorem 2.25]{aft_fhstrat}, which states in particular that algebras may be pushed forward along weakly constructible bundles.
 \end{remark}
@@
 
-For the next definition we notice that all standard simplices are stratified manifolds.
+For the next definition we notice that all standard simplices are stratified manifolds, obtained as $\Delta^n\cong\overline{C}^n(\ast)\to\overline{C}(\{0\})\cong[n]$.
 
@@
     $\mfld$ is the $\infty$-category whose objects are stratified manifolds and whose morphisms are open embeddings among them.
-To get the higher categorical structure we consider a simplicial enrichment over $\mathsf{Set}$-valued presheaves on the unenriched category, so that given two objects $M$ and $N$
+It is presented as the $\mathsf{Kan}$-enriched category of stratified manifolds by taking the Kan complex of morphisms between two objects $M$ and $N$ to be defined by
     %
     \begin{equation}
-        \mathsf{Hom}_{\mfld} (M, N): [p] \mapsto \mathsf{Map}_{/\Delta^p} (M \times \Delta^p, N \times \Delta^p),
+        \mathsf{Hom}_{\mfld} (M, N): [p] \mapsto \mathsf{Mfld}_{/\Delta^p} (M \times \Delta^p, N \times \Delta^p).
     \end{equation}
     %
-    where $\Delta^p$ is the standard $p$-simplex and $\mathsf{Map}_{/\Delta^p}$ denotes those stratified maps that commute with projecting to $\Delta^p$.
-It can be shown that this enrichment factors through a $\mathsf{Kan}$-enrichment, which gives the appropriate structure.
+    Here, $\mathsf{Mfld}_{/\Delta^p}$ takes the morphism set in the over-category over $\Delta^p$.
 \end{definition}

### 2024-03-04 sections/2homology.tex
minor changes until §1.2

@@
 
-Factorization homology (also topological chiral homology) is a construction that to the data of a smooth manifold $M$ and an algebra $A$ valued in a symmetric monoidal $\infty$-category $\catC$ assigns an object
+Factorization homology (also known as topological chiral homology) is a construction that to the data of a smooth manifold $M$ and an algebra $A$ valued in a symmetric monoidal $\infty$-category $\catC$ assigns an object
 %

### 2024-03-06 sections/3algebras.tex
Added gluing example.

@@
 
-\subsection{Factorization Algebras on Intervals}\label{ssec:lcfa_on_1d_man}
+\subsection{Factorization Algebras on Intervals}\label{ssec:lcfa_on_ints}
 
@@
 
-\begin{corollary}
+\begin{corollary}\label{cor:lcfas_on_closed_int}
     There is an equivalence between the $\infty$-categories of locally constant factorization algebras on the closed interval and algebras over the $\infty$-operad $\mathsf{Assoc^{RL}}$

### 2024-03-06 sections/4gluing.tex
Added gluing example.

@@
     which on objects acts as $(N \xhookrightarrow{} M) \mapsto (N_- \xhookrightarrow{} M, N_0 \times \mathbb{R} \xhookrightarrow{} M, N_+ \xhookrightarrow{} M)$.
-Moreover, this functor is even an algebra.
+Moreover, this functor is even a map of $\infty$-operads.
 \end{lemma}
@@
     \end{equation}
+    %
+    That the functor is a map of $\infty$-operads is clear from the fact that the key role on both sides is played by disjoint union.
 
-    Need to be extended to $\mfld_{/M}$ by dealing with the homotopies.
-
-    %Formally, the relevant definition is \cite[def.2.1.2.7]{lurie_ha}, which says that we have to check two things: that the constructed functor $\gamma(A_-, A_+)$ lies over $\mathsf{Fin}_*$ and that it sends inert morphisms to inert morphisms.
-Factorization homology, $\int_- A_{0,\pm}$, satisfies this almost by definition, while \cref{lem:B_sym_mon} tells us that the bar construction similarly does so.
-All that is left to show is that $\bar{f}$ is a map of $\infty$-operads.
-But this is obviously the case since all it is doing is splitting the input into pieces while keeping track of how they relate to each other.
+    {\color{red}Needs to be extended to $\mfld_{/M}$ by dealing with the homotopies.
+Alternatively, we can prove the theorem for $\disk[r]_{/M}$-algebras first and then argue at the factorization algebra level that the glued algebra has to inherit local constancy.}
 \end{proof}
@@
 
+\begin{example}\label{ex:reproduce_lcfas_on_interval}
+    With the ingredients we have introduced up to now, specifically in \cref{ssec:lcfa_on_ints}, we can do a nontrivial check of the gluing theorem.
+This is because we can write a collar-gluing of the closed interval $[-1,1] \cong \left[-1,1\right) \coprod_{(-1,1)} \left(-1,1\right] \cong \mathbb{R}_{\geq 0} \coprod_{\mathbb{R}} \mathbb{R}_{\leq 0}$.
+We note here that we have written $\mathbb{R}_{\leq 0}$ and $\mathbb{R}_{\geq 0}$ to emphasize the maps forming the decomposition.
+At the level of unstructured objects these two are isomorphic (see also \cref{rem:left_or_right_module}).
+For this example, the theorem says that locally constant factorization algebras on the closed interval should be given by
+    %
+    \begin{equation}
+        \lcfa_{[-1,1]} (\catC) \simeq \lcfa_{\mathbb{R}_{\geq 0}} (\catC) \bigtimes_{\lcfa_{\mathbb{R}} (\catC)} \lcfa_{\mathbb{R}_{\leq 0}} (\catC) \simeq \mathsf{RMod} (\catC) \bigtimes_{\alg{\mathbb{E}_1} (\catC)} \mathsf{LMod} (\catC),
+    \end{equation}
+    %
+    where the functors are the ones that forget the module.
+At the level of objects, this is the data of an algebra with a right module $(A, R) \in \mathsf{RMod} (\catC)$ and an algebra with a left module $(B, L) \in \mathsf{LMod} (\catC)$, such that the algebras are equal $A = B$.
+But this is exactly the same as the description we gave in terms of an algebra with a left and a right module, i.e.
+an algebra over $\mathsf{Assoc^{RL}}$, in \cref{cor:lcfas_on_closed_int}.
+\end{example}
+
 \begin{example}\label{ex:reproduce_lcfas_on_S1}
+    A highly nontrivial check of the gluing theorem is given by the circle $S^1$.
 Using results from \cite[prop.4.0.1]{cg2016}, namely inheritance from a covering space, \cite[sec.5.5]{ginot2015} characterizes locally constant factorization algebras on the circle $S^1$ as
@@
 $\mathbb{E}_1$-algebras together with a self-equivalence.
+This result is not generalizable to higher spheres because it uses the technology of covering spaces.
 \Cref{cor:gluing_lcfas} allows us to recover this nontrivial result.
@@
 \begin{example}\label{ex:lcfas_on_S^n}
+    Unlike the covering space result for the circle \cite[sec.5.5]{ginot2015} which doesn't generalize to higher spheres, the gluing theorem has no such restriction.
 Just as for the circle, higher spheres can also be described as a collar-gluing $S^n \cong \mathbb{R}^n \coprod_{S^{n-1} \times \mathbb{R}} \mathbb{R^n}$.
@@
 
-    From this example we can easily see that beyond the dimensionality $n$ of the space, which is locally kept track of as an $\mathbb{E}_n$-algebra, locally constant factorization algebras for the higher spheres also keep track of higher coherent (self-)equivalences.
+    From this example we can easily see that beyond the dimensionality $n$ of the space, which is locally kept track of as an $\mathbb{E}_n$-algebra, locally constant factorization algebras for the higher spheres also keep track of higher coherent (self-)equivalences, which imitate traingulations of the spheres.
 \end{example}

### 2024-03-06 sections/5classification.tex
Added gluing example.

@@
 In \cref{ssec:lcfa_on_Rn} we discussed locally constant factorization algebras on Euclidean spaces of different dimension $n$, and we saw that they presented the data of $\mathbb{E}_n$-algebras.
-In \cref{ssec:lcfa_on_1d_man}, on the other hand we focused on 1 dimensional manifolds, but with different possible stratification structures, and we saw that the data encoded in defects was a module structure.
+In \cref{ssec:lcfa_on_ints}, on the other hand we focused on 1 dimensional manifolds, but with different possible stratification structures, and we saw that the data encoded in defects was a module structure.
 Here, in the spirit of this section, we work to extend both of these developments to the case of Euclidean spaces with the specific kind of defect that we have limited ourselves to, namely, $\mathbb{R}^{d \subset n}$.

### 2024-03-07 sections/1stratified.tex
amendmends to the tangent classifier

@@
 
-In a lot of cases we will want to add to our stratified manifold the data of tangential structure.
-This, for example, will be the geometric input for factorization homology.
-Thus, we introduce the concept of tangential structure here, first starting with smooth manifolds and then continuing to the stratified case.
+Tangential structure can be part of the input for factorization homology.
+Thus, in this section, we will recall the concept of tangential structure, first starting with smooth manifolds and then continuing to the stratified case.
 
 \begin{definition}
-    Let $\mfld_n$ be the $\infty$-category defined as a topological category, whose objects are smooth, $n$-dimensional manifolds and whose morphisms are embeddings between them, where the morphism spaces have the compact-open topology.
-This category can be endowed with a symmetric monoidal structure given by disjoint union.
+    Let $\mfld_n$ be the $\infty$-category given by the topological category whose objects are smooth $n$-dimensional manifolds and whose morphisms are embeddings between them, where the morphism spaces have the compact-open topology.
+It is endowed with the symmetric monoidal structure given by disjoint union.
 \end{definition}
 
-Given a smooth, $n$-dimensional manifold $M$, its tangent bundle is a rank-$n$ vector bundle on the manifold, which also makes it a principal $\mathsf{GL}(n)$-bundle.
-Because of the classification of principal bundles, the tangent bundle of a manifold $M$ can be classified, up to homotopy, by a map called the \emph{tangent classifier}
+Given a smooth, $n$-dimensional manifold $M$, (the frame bundle of) its tangent bundle is a principal $\mathsf{GL}(n)$-bundle whose bundle isomorphism class corresponds to the homotopy class of its classifying map
 %
@@
 \end{equation}
-%
-where $\mathsf{BO}(n)$ is the classifying space of $\mathsf{O}(n)$.
-Giving the manifold a $G$-structure, where $G$ is a Lie group with a group homomorphism to $\mathsf{GL}(n)$, is then equivalent to a factorization, up to homotopy, of the tangent classifier through $\mathsf{B}G$, in other words it is a lift $\phi$ of the tangent classifier such that the following diagram is homotopy commutative
+called the \emph{tangent classifier}.
+Here, $\mathsf{B}G$ is the classifying space of the (topological) group $G$.
+Giving the manifold a $G$-structure, where $G$ is a Lie group with a group homomorphism to $\mathsf{GL}(n)$ (or to $\mathsf{O}(n)$), is to find a lift $\phi$ of $\tau_M$ and a homotopy that commutes
 %
@@
 
-It is, in fact, this picture that will generalize to give us tangential structure in the more general case.
-As a first step, \cite[cor.2.13]{af_fhtop} shows that the tangent classifier can be understood as a functor
+A similar picture applies in the stratified case. As a first step, \cite[Corollary 2.13]{af_fhtop} shows that $M\mapsto\tau_M$ can be presented as the symmetric monoidal functor
 %
@@
 \end{equation}
-%
-and in fact a symmetric monoidal one, where the codomain's symmetric monoidal structure is given by coproduct.
-Namely, given a smooth manifold $M$, the functor returns the map of spaces $\tau_M:M \rightarrow \mathsf{BO}(n)$.
+where the codomain's symmetric monoidal structure is given by coproduct.
+As noted in \cite{af_fhtop}, the Kister--Mazur Theorem (\cite{kister1964microbundles}) provides an equivalence $\mathsf{Emb}(\mathbb{R}^n,\mathbb{R}^n)\simeq \mathsf{Top}(n)$, where $\mathsf{Top}(n)$ is the group of topological automorphisms of $\mathbb{R}^n$; $\mathsf{Emb}(\mathbb{R}^n,\mathbb{R}^n)\simeq\mfld_n(\mathbb{R}^n,\mathbb{R}^n)$ is the group of self-embeddings of $\mathbb{R}^n$; and both groups are equipped with the compact-open topology.
+This yields $\mathsf{PShv}(\mathbb{R}^n)\simeq\mathsf{PShv}(\mathsf{BTop}(n))$, which is equivalent to $\mathsf{Spaces}_{/\mathsf{BTop}(n)}$ by straightening-unstraightening (see \Cref{rem:grothendieck_construction}).\footnote{Preasheaves are space-valued, that is, $\mathsf{PShv}(\mathscr{C})=\mathsf{Fun}(\mathscr{C}^{\mathsf{op}},\mathsf{Spaces})$.} Finally, the inclusion $\mathsf{O}(n)\hookrightarrow\mathsf{Emb}(\mathbb{R}^n,\mathbb{R}^n)$ is also an equivalence (\cite[Proposition 2.2.6]{ayala2020primer}), yielding the displayed equivalence.
+The first map, the $\infty$-categorical Yoneda embedding, sends $M\mapsto((\mfld_{n})_{/M}\to\mfld_n)$ as a map with target $\mathsf{RFib}(\mfld_n)$, as in \cite{lurie_htt}.
 
-By fixing a space $B$ with a map $B \rightarrow \mathsf{BO}(n)$ (the role of which was previously played by $\mathsf{B}G$), we can define:
+By fixing a space $B$ with a map $B \rightarrow \mathsf{BO}(n)$ (the role of which was previously played by $\mathsf{B}G$), one has
 %

### 2024-03-08 sections/1stratified.tex
until 1.3 - a few more details

@@
 As noted in \cite{af_fhtop}, the Kister--Mazur Theorem (\cite{kister1964microbundles}) provides an equivalence $\mathsf{Emb}(\mathbb{R}^n,\mathbb{R}^n)\simeq \mathsf{Top}(n)$, where $\mathsf{Top}(n)$ is the group of topological automorphisms of $\mathbb{R}^n$; $\mathsf{Emb}(\mathbb{R}^n,\mathbb{R}^n)\simeq\mfld_n(\mathbb{R}^n,\mathbb{R}^n)$ is the group of self-embeddings of $\mathbb{R}^n$; and both groups are equipped with the compact-open topology.
-This yields $\mathsf{PShv}(\mathbb{R}^n)\simeq\mathsf{PShv}(\mathsf{BTop}(n))$, which is equivalent to $\mathsf{Spaces}_{/\mathsf{BTop}(n)}$ by straightening-unstraightening (see \Cref{rem:grothendieck_construction}).\footnote{Preasheaves are space-valued, that is, $\mathsf{PShv}(\mathscr{C})=\mathsf{Fun}(\mathscr{C}^{\mathsf{op}},\mathsf{Spaces})$.} Finally, the inclusion $\mathsf{O}(n)\hookrightarrow\mathsf{Emb}(\mathbb{R}^n,\mathbb{R}^n)$ is also an equivalence (\cite[Proposition 2.2.6]{ayala2020primer}), yielding the displayed equivalence.
+This yields $\mathsf{PShv}(\mathbb{R}^n)\simeq\mathsf{PShv}(\mathsf{BTop}(n))$, which is equivalent to $\mathsf{Spaces}_{/\mathsf{BTop}(n)}$ by straightening-unstraightening (see \Cref{rem:grothendieck_construction}).\footnote{Presheaves are space-valued, that is, $\mathsf{PShv}(\mathscr{C})=\mathsf{Fun}(\mathscr{C}^{\mathsf{op}},\mathsf{Spaces})$.} Finally, the inclusion $\mathsf{O}(n)\hookrightarrow\mathsf{Emb}(\mathbb{R}^n,\mathbb{R}^n)$ is also an equivalence (\cite[Proposition 2.2.6]{af_primer}), yielding the displayed equivalence.
 The first map, the $\infty$-categorical Yoneda embedding, sends $M\mapsto((\mfld_{n})_{/M}\to\mfld_n)$ as a map with target $\mathsf{RFib}(\mfld_n)$, as in \cite{lurie_htt}.
+The fiber of $(\mfld_{n})_{/M}\to\mfld_n$ at $N$ is equivalent to the space of embeddings of $N$ into $M$, and so the restricted presheaf on the full sub-$\infty$-category at $\mathbb{R}^n$ sends $\mathbb{R}^n$ to the space of embeddings of $\mathbb{R}^n$ into $M$.
 
@@
 \begin{remark}
-    Since the tangent classifier $\tau$ is symmetric monoidal, and since the right vertical map is canonically symmetric monoidal with the coproduct on both $\mathsf{Spaces}_{/B}$ and $\mathsf{Spaces}_{/\mathsf{BO}(n)}$, the newly defined $\infty$-category does indeed come with a canonical symmetric monoidal structure.
+    Since the tangent classifier $\tau$ is symmetric monoidal, and since the right vertical map is canonically symmetric monoidal with respect to disjoint union on both $\mathsf{Spaces}_{/B}$ and $\mathsf{Spaces}_{/\mathsf{BO}(n)}$, the newly defined $\infty$-category does indeed come with a canonical symmetric monoidal structure.
 \end{remark}
@@
     \begin{enumerate}
-        \item $(G \rightarrow \mathsf{O}(n)) = (\mathsf{O}(n) \xrightarrow{\mathrm{id}} \mathsf{O}(n))$ reproduces the case of no tangential structure,
+        \item $(G \rightarrow \mathsf{O}(n)) = (\mathsf{O}(n) \xrightarrow{\mathrm{id}} \mathsf{O}(n))$ reproduces the case of no tangential structure,\footnote{or the contractible choice of a riemannian metric}
         \item $(G \rightarrow \mathsf{O}(n)) = (\mathsf{SO}(n) \xhookrightarrow{} \mathsf{O}(n))$ is the case of oriented smooth manifolds,
-        \item $(G \rightarrow \mathsf{O}(n)) = (\mathsf{Spin}(n) \rightarrow \mathsf{SO}(n) \xhookrightarrow{} \mathsf{O}(n))$ is the case of spin structure,
+        \item $(G \rightarrow \mathsf{O}(n)) = (\mathsf{Spin}(n) \rightarrow \mathsf{SO}(n) \xhookrightarrow{} \mathsf{O}(n))$ is the case of spin manifolds,
         \item $(G \rightarrow \mathsf{O}(n)) = (* \rightarrow \mathsf{O}(n))$ is the case of framed smooth manifolds.
@@
 
-Moving on to the stratified setting, we note that the stratified version of the full $\infty$-subcategory $\mathbb{R}^n \subset \mfld_n$ is the $\infty$-category of basic singularity types $\bsc$.
-We can thus generalize the tangent classifier to this setting as the functor
+Moving on to the stratified setting, we note that the stratified version of the full $\infty$-subcategory $\mathbb{R}^n \subset \mfld_n$ is the $\infty$-category $\bsc$ of basic singularity types, obtaining
 %
@@
 %
-In this case, as in the previous, given a stratified manifold $M$, $\tau(M)$ is the functor that for each basic $U \in \bsc$, assigns the space of stratified smooth open embeddings of $U$ into $M$.
+In this case, as in the previous one, given a stratified manifold $M$, $\tau(M)$ is the functor that to each basic $U \in \bsc$ assigns the space of conically-smooth open embeddings of $U$ into $M$.
 
 \begin{remark}\label{rem:grothendieck_construction}
-    We can say something more about this situation if we use the unstraightening construction \cite[sec.2.2]{lurie_htt} which provides an equivalence between $\mathsf{Spaces}$-valued presheaves on a general $\infty$-category $\catC$ and right fibrations \footnote{More details can be found in the cited references, but for completeness we include the definition of right fibration.
-A \emph{right fibration} (over $\catC$) is a functor $f:\mathscr{E} \rightarrow \catC$ such that the diagram
+    The straightening-unstraightening construction of \cite[§2.2]{lurie_htt} provides an equivalence between $\mathsf{Spaces}$-valued presheaves on an $\infty$-category $\catC$ and right fibrations\footnote{A \emph{right fibration} (over $\catC$) is a functor $f:\mathscr{E} \rightarrow \catC$ such that whenever a square of type
     %
@@
     %
-    can be filled for any $0 < i \leq n$.} over this $\infty$-category
+    is given, there is a lift as depicted if $0 < i \leq n$.} thereon:
     %
@@
     %
-    More details on this equivalence in our context can be found in \cite[sec.4.2]{aft_localstrut}
+    More details on this equivalence in our context can be found in \cite[§4.2]{aft_localstrut}.
 Appending this equivalence to the definition of the tangent classifier would say that the value of the tangent classifier on a stratified manifold $M$ is given by the right fibration
@@
     i.e.
-the forgetful functor from the slice $\infty$-category.
-The $\infty$-category $\mathsf{Entr}(M)$ defined here is called the enter-path $\infty$-category of the stratified manifold $M$\footnote{A different version of this $\infty$-cateogry is defined in \cite[app.A.6]{lurie_ha} called the exit-path $\infty$-category of the stratified space $M$.
-It is shown in the work \cite{afr_homhyp} that this exit-path $\infty$-category is equivalent to the opposite of the enter-path $\infty$-category as defined above.}.
-In fact the statements that we will make next will take on this perspective for the tangent classifier.
+the forgetful functor from the over-$\infty$-category over $M$.\footnote{The notation is slightly misleading since $M$ need not be in $\bsc$.} The $\infty$-category $\mathsf{Entr}(M)$ defined here is called the enter-path $\infty$-category of the stratified manifold $M$.\footnote{A different version of this $\infty$-cateogry is defined in  called the exit-path $\infty$-category of the stratified space $M$.
+It is shown in \cite{afr_homhyp} that the exit-path $\infty$-category of \cite[§A.6]{lurie_ha} is equivalent to the opposite of the enter-path $\infty$-category mentioned above.} In fact the statements that we will make next will take on this perspective for the tangent classifier.
 \end{remark}
@@
 The key realization is that the data which the map of spaces $B \rightarrow \mathsf{BO}(n)$ provided before was the data of a presheaf on $\mathsf{BO}(n)$, standing in as the $\infty$-category of basics with only one object $\mathbb{R}^n$.
-The analogous construction in the stratified case is to provide a presheaf on $\bsc$, which by \cref{rem:grothendieck_construction} is given by a right fibration over $\bsc$.
+The analogous construction in the stratified case is to provide a presheaf on $\bsc$, which by \Cref{rem:grothendieck_construction} is given by a right fibration over $\bsc$.
 
 \begin{definition}
-    An $\infty$-category of basics is a right fibration $\bstr \rightarrow \bsc$
+    An $\infty$-category of basics, or a tangential structure, is a right fibration $\bstr \rightarrow \bsc$.
 \end{definition}
@@
             \mfld(\bstr) \arrow[dr, phantom, "\ulcorner", very near start] \arrow[r] \arrow[d] & (\mathsf{RFib}_{\bsc})_{/\bstr} \arrow[d] \\
-            \mfld \arrow[r, "\tau"] & \mathsf{RFib}_{\bsc}.
+            \mfld \arrow[r, "\tau"] & \mathsf{RFib}_{\bsc}
         \end{tikzcd}
     \end{equation}
-\end{definition}
-
-\begin{definition}
-    Given an $\infty$-category of basics $\bstr \rightarrow \bsc$, the ordinary category of $\bstr$-manifolds is the further pullback
-    %
-    \begin{equation}
-        \begin{tikzcd}
-            \mfld[r](\bstr) \arrow[dr, phantom, "\ulcorner", very near start] \arrow[r] \arrow[d] & \mfld(\bstr) \arrow[d] \\
-            \mfld[r] \arrow[r] & \mfld.
-        \end{tikzcd}
-    \end{equation}
+    where we abbreviated $(\bstr\to\bsc)\in\mathsf{RFib}_{\bsc}$ to $\bstr$.
+Similarly the ordinary category $\mfld[r](\bstr)$ of $\bstr$-manifolds is the further pullback along the inclusion $\mfld[r]\to\mfld$.
 \end{definition}
@@
 \begin{remark}
-    Specifying to the objects of $\mfld(\bstr)$ (which are also the objects of $\mfld[r](\bstr)$), we have that a $\bstr$-manifold is a stratified manifold $M$ together with a lift $\phi$
+    A $\bstr$-manifold is a stratified manifold $M$ together with a homotopy-lift $\phi$
     %
@@
     %
-    i.e.
-such that the triangle above is homotopy commutative in the $\infty$-category of $\infty$-categories $\cat$.
-This is how we can encode the stratification information while keeping the basic idea of a lift the same.
+    i.e., a filler of the $2$-horn in the $\infty$-category $\cat$ of $\infty$-categories  given by $\tau_M$ and $\bstr\to\bsc$.
 \end{remark}
@@
 In the case of smooth manifolds we argued that $\mfld_n^B$ was defined in a way that allowed it to inherit disjoint union as a symmetric monoidal structure.
-A similar argument, found in \cite{aft_fhstrat}, can be made for the stratified case too
+A similar argument, found in \cite{aft_fhstrat}, can be made for the stratified case too:
 
@@
     One should think of collar-gluings as analogous to the case of gluing two manifolds with boundary along their boundaries after choosing collars.
-This is exactly the special thing about them, the overlap region is collared, i.e.
-looks like a product with $\mathbb{R}$.
+This is exactly the special thing about them, the overlap region is collared, i.e., looks like a product with $\mathbb{R}$.
 We also note that the disjoint union is an example of a collar-gluing.

### 2024-03-11 sections/1stratified.tex
§1.3

@@
 
-\begin{example}
+\begin{example}\label{7UEDP24}
     Inspired by the previous example, any topological space $X$ with a filtration by closed subsets $\emptyset \subset X_{\leq 0} \subset \dots \subset X_{\leq n} = X$, is a stratified space, because the filtration induces a map $X \rightarrow \mathbb{N}$, which sends $X_{\leq i} \setminus X_{\leq i-1}$ to $i$.
@@
 \end{definition}
+
+\begin{example}
+    The open cone $C(S^k)$ on the $k$-sphere is canonically identified with $\mathbb{R}^k$ with stratification given by the filtration $\{0\}\subset\mathbb{R}^k$ as in \Cref{7UEDP24}.
+\end{example}
 
@@
 where the codomain's symmetric monoidal structure is given by coproduct.
+
+\begin{remark}\label{9EFM44H}
     As noted in \cite{af_fhtop}, the Kister--Mazur Theorem (\cite{kister1964microbundles}) provides an equivalence $\mathsf{Emb}(\mathbb{R}^n,\mathbb{R}^n)\simeq \mathsf{Top}(n)$, where $\mathsf{Top}(n)$ is the group of topological automorphisms of $\mathbb{R}^n$; $\mathsf{Emb}(\mathbb{R}^n,\mathbb{R}^n)\simeq\mfld_n(\mathbb{R}^n,\mathbb{R}^n)$ is the group of self-embeddings of $\mathbb{R}^n$; and both groups are equipped with the compact-open topology.
@@
 The fiber of $(\mfld_{n})_{/M}\to\mfld_n$ at $N$ is equivalent to the space of embeddings of $N$ into $M$, and so the restricted presheaf on the full sub-$\infty$-category at $\mathbb{R}^n$ sends $\mathbb{R}^n$ to the space of embeddings of $\mathbb{R}^n$ into $M$.
+\end{remark}
 
@@
 \begin{remark}
-    \Cref{thm:decom_strat_man} is the analogous theorem to handle decompositions of smooth manifolds.
+    \Cref{thm:decom_strat_man} is the analogue of handle decompositions for smooth manifolds.
 Namely, any compact, smooth manifold can be obtained by handle decomposition, and non-compact smooth manifolds are obtained by sequential colimits of finitary (including compact) smooth manifolds.
@@
 
-Along with the already familiar $\infty$-categories of basics $\mathsf{D}_n^{G} := \mathsf{B}G \xrightarrow{\{ \mathbb{R}^n\}} \bsc$, which govern smooth $n$-manifolds with $G$-structure, we introduce a few more $\infty$-categories of basics that will be useful for us.
-An $\infty$-category of basics that will play a big role for the development of factorization homology to come, is the particularly simple one describing oriented $1$-manifolds with boundary.
+Along with the already familiar $\infty$-categories of basics $\mathsf{D}_n^{G} := \mathsf{B}G \xrightarrow{\{ \mathbb{R}^n\}} \bsc$, which govern smooth $n$-manifolds with $G$-structure, we recall a few more $\infty$-categories of basics that will be of interest to us.
+
+\begin{example}[{\cite[Example 5.2.5]{aft_localstrut}}]
+    We denote by $\mathsf{D}_n\hookrightarrow \bsc$ or simply $\mathsf{D}_n$ the tangential structure given by the full sub-$\infty$-category inclusion of $\bsc_{0,n}$, the basics of depth $0$ and pure dimension $n$.\footnote{A stratified space $X\to P$ has \emph{pure dimension $n$} (\cite[Definition 2.4.1]{aft_localstrut}) if its local (\v{C}ech--Lebesgue) dimension $\mathsf{dim}_x(X)$ at every $x\in X$ is $n$.
+Connected topological manifolds are of this type.} Accordingly, $\mathsf{D}_n$-manifolds are topological $n$-manifolds.
+As in \Cref{9EFM44H}, we have an equivalence $\mathsf{D}_n\simeq \mathsf{BGL}(n)\simeq \mathsf{BO}(n)$ of $\infty$-groupoids.
+\end{example}
+
+An $\infty$-category of basics that will play a major role for the development of factorization homology to come is the particularly simple one describing oriented $1$-manifolds with boundary.
 
 \begin{construction}\label{con:d_1^bor_structure}
-    Consider the $\infty$-subcategory $\mathsf{D}_1^{\partial} \subset \bsc$ whose objects are $\mathbb{R}$ and $\hoint$.
+    Consider the $\infty$-subcategory $\mathsf{D}_1^{\partial} \subset \bsc$ whose objects are $\mathbb{R}$ and $\hoint=C(\ast)$.
 There is a unique right fibration $\mathsf{D}_1^{\partial, \mathsf{or}} \rightarrow \mathsf{D}_1^{\partial}$, whose fiber over $\mathbb{R}$ is a point $\{ \mathbb{R}\}$, and whose fiber over $\hoint$ is two points $\{ \hoint, {\mathbb{R}_{\leq 0}} \}$.
@@
 
+\begin{remark}
+    Insisting that tangential structures be \emph{right fibrations} over $\bsc$, as opposed to simply $\infty$-categories over it as, e.g., in \cite{ayala2020factorization}, leads to technical issues that lead to our over-simplified notation due to the property of being a right fibration not being invariant under equivalence.
+For instance, when $G=\ast$, so that $\mathsf{D}^\ast_n$ constrols framed $n$-manifolds, the map $BG=\ast\to \mathsf{BO}(n)\simeq\mathsf{D}_n$ is not a right fibration, owing to the observation that right fibrations of Kan complexes are Kan fibrations, and these, when surjective on objects, are epimorphisms.
+On the other hand, $B\ast=\ast\simeq (\mathsf{D}_n)_{/\mathbb{R}^n}$ since over-$\infty$-groupoids are contractible (\cite[018Y]{lurie_kerodon}), but $(\mathsf{D}_n)_{/\mathbb{R}^n}\to \mathsf{D}_n$ \emph{is} a right fibration since it is a projection from an over-$\infty$-category (\cite[Proposition 018F]{lurie_kerodon}, \cite{joyal}).
+Moreover, $\mathsf{D}_n\hookrightarrow \bsc$ is a right fibration since this full sub-$\infty$-category is trivially a sieve, so the composition $(\mathsf{D}_n)_{/\mathbb{R}^n}\to \bsc$ is a right fibration as well.
+In general, the map $\mathsf{B}G\to \mathsf{BO}(n)$ is not a right fibration unless $G\to\mathsf{O}(n)$ is an epimorphism.
+However, given the latter, we can consider the presheaf $\mathsf{D}_n^{\text{op}}\to\mathsf{Spaces}$ given by mapping $\mathbb{R}^n$ to the space of $G$-structures on it, and sending an embedding to the induced pullback map on the respective spaces of $G$-structures.
+By unstraightening, this determines a right fibration for which, by abuse, we write $\mathsf{D}^G_n=\mathsf{B}G\to \mathsf{D}_n\hookrightarrow\bsc$.
+\end{remark}
+
 Another type of stratified manifold that we will focus on heavily in this work is the case of a smooth manifold with a distinguished, properly embedded, smooth submanifold, which we alternatively call a \emph{defect}.
@@
 
-\begin{construction}[{\cite[ex.5.2.10]{aft_localstrut}}]
-    Let $\mathsf{D}_{d \subset n} \subset \bsc$ be the full $\infty$-subcategory whose objects are $\mathbb{R}^n$ and $\mathbb{R}^{d \subset n} := \mathbb{R}^{n-d} \times \mathsf{C}(S^{n-d-1})$, where $d < n$.
+\begin{construction}[{\cite[Example 5.2.10]{aft_localstrut}}]
+    Let $\mathsf{D}_{d \subset n} \subset \bsc$ be the full $\infty$-subcategory whose objects are $\mathbb{R}^n$ and $\mathbb{R}^{d \subset n} := \mathbb{R}^{d} \times \mathsf{C}(S^{n-d-1})$, where $d < n$.
 We elaborate that the morphism spaces are given as follows:
@@
 This final morphism space is given differently compared to the other ones because of intricacies related to smoothness around the defect.
-For more details on the matter there is a discussion in \cite[ex.5.1.7]{aft_localstrut}.
+For more details on the matter there is a discussion in \cite[Example 5.1.7]{aft_localstrut}.
     \end{enumerate}
@@
 
-    Explaining what exactly we mean by a framed stratified manifold is done in \cite[ex.5.2.12]{aft_localstrut}.
+    Explaining what exactly we mean by a framed stratified manifold is done in \cite[Example 5.2.12]{aft_localstrut}.
 According to that example, $\mathsf{D}_{d \subset n}^*$-manifolds are described by the data of a framed smooth $n$-manifold $M$, a properly embedded smooth $d$-submanifold $\Sigma$ together with a null-homotopy of the Gauss map $\Sigma \rightarrow \mathsf{Gr}_d(\mathbb{R}^n)$.
@@
 That is encoded as a map $\Sigma \rightarrow \mathsf{Gr}_d(\mathsf{T}M)$ to the Grassmann bundle of the tangent bundle of $M$.
-In our case, the framing of $M$ provides a preferred trivialization of the tangent bundle to $\mathbb{R}^n$.
-A null-homotopy of this map is a trivialization of the tangent (and subsequently also the normal) bundle of $\Sigma$ in a way that is compatible with the trivialization of $\mathsf{T}M$.
+The framing of $M$ is a diffeomorphism of type $\mathsf{T}M\cong M\times\mathbb{R}^n$ over, reducing said map to the Gauss map.
+A null-homotopy of this map is a trivialization of the tangent as well as the normal bundles of $\Sigma$ in a way that is compatible with the trivialization of the restriction of $\mathsf{T}M$ to $\Sigma$.
 \end{remark}

### 2024-03-13 4gluing_alt.tex
Add files via upload

--- 2024-03-06 sections/4gluing.tex
@@
 
-Given a stratified manifold $M$, we defined the $\infty$-category of locally constant factorization algebras on it $\lcfa_M (\catC)$.
-We want to examine what we can say about the behavior of this $\infty$-category under collar-gluings in the manifold variable.
-Our discussion will be in terms of disk algebras $\alg{\disk_{/M}} (\catC)$, but using \cref{thm:disk_alg=lcfa} there is no loss at all.
+Given a stratified manifold $M$, and a $\otimes$-presentable $\infty$-category $\catC$, we defined the $\infty$-category $\lcfa_M (\catC)$ of locally constant factorization algebras on $M$ valued in $\catC$.
+We also noticed, in \cref{thm:disk_alg=lcfa}, that factorization homology is involved in constructing these algebras from local data.
+This prompts us to ask if we can say something about the behavior of this $\infty$-category under collar-gluings in the manifold variable.
+In this section we will prove that such a result exists in both the cases of locally constant and ordinary factorization algebras.
 
@@
 
-\begin{theorem}\label{thm:gluing_alg_disk/M}
+\begin{theorem}\label{thm:gluing_lcfas}
     Given a collar-gluing of stratified manifolds $f: M \rightarrow [-1,1]$, the $\infty$-category of $\disk_{/M}$-algebras is equivalent to the pullback of $\infty$-categories
@@
     \begin{equation}
-        \alg{\disk_{/M}} (\catC) \simeq \alg{\disk_{/M_-}} (\catC) \bigtimes_{\alg{\disk_{/M_0 \times \mathbb{R}}} (\catC)} \alg{\disk_{/M_+}} (\catC).
+        \lcfa_M (\catC) \simeq \lcfa_{M_-} (\catC) \bigtimes_{\lcfa_{M_0 \times \mathbb{R}} (\catC)} \lcfa_{M_+}(\catC).
     \end{equation}
@@
 
-Before me move on to the proof we show a few useful lemmas.
+As in previous cases the proof of the above theorem will have a corollary that is easier to prove and whose proof goes along the same lines
+
+\begin{corollary}\label{cor:gluing_falgs}
+    A collar-gluing of stratified manifolds $f: M \rightarrow [-1,1]$ induces an equivalence of $\infty$-categories
+    %
+    \begin{equation}
+        \falg_M (\catC) \simeq \falg_{M_-} (\catC) \bigtimes_{\falg_{M_0 \times \mathbb{R}} (\catC)} \falg_{M_+}(\catC).
+    \end{equation}
+\end{corollary}
+
+Before me move on to the proof of the above two results we pause to record a few useful lemmas that will play a role in it.
 
@@
     \begin{equation}
-        \bar{f}: \mfld_{/M} \xrightarrow{\ \ \ \ } \alg{\mathsf{Assoc^{RL}}} (\mfld_{/M}),
+        \bar{f}: \mfld[r]_{/M} \xrightarrow{\ \ \ \ } \alg{\mathsf{Assoc^{RL}}} (\mfld[r]_{/M}),
     \end{equation}
@@
 \begin{proof}
-    Let us first look at the case of $\mfld[r]_{/M}$ instead of $\mfld_{/M}$.
-In this case the underlying $\infty$-category is actually (the nerve of) an ordinary category.
+    We recall that the underlying $\infty$-category of $\mfld[r]_{/M}$ is actually (the nerve of) an ordinary category.
 In particular, morphisms are given by the data of an embedding $N \xhookrightarrow{} N'$ such that $N \xhookrightarrow{} N' \xhookrightarrow{} M = N \xhookrightarrow{} M$ on the nose.
@@
     %
-    \begin{equation}
+    \begin{equation}\label{cd:factorization_of_e}
         \begin{tikzcd}
@@
     %
-    where the diagram commutes on the nose. This also points out the difficulties that we will have to deal with in the case of $\mfld_{/M}$ concerning the higher morphisms.
-
-    Sticking to $\mfld[r]_{/M}$ though, the assignment clearly plays well with the algebra structure of the right-hand side, through the existence of (on the nose) commutative diagrams like e.g.
+    where the diagram commutes on the nose.
+Such an assignment clearly plays well with the algebra structure of the right-hand side, through the existence of (on the nose) commutative diagrams like e.g.
     %
@@
     That the functor is a map of $\infty$-operads is clear from the fact that the key role on both sides is played by disjoint union. 
-
-    {\color{red}Needs to be extended to $\mfld_{/M}$ by dealing with the homotopies.
-Alternatively, we can prove the theorem for $\disk[r]_{/M}$-algebras first and then argue at the factorization algebra level that the glued algebra has to inherit local constancy.}
 \end{proof}
 
-\begin{corollary}\label{cor:fbar_func_discrete}
-    Taking only the first part of the proof of \cref{lem:fbar_func} it is immediate that in the setting of $\mfld[r]_{/M}$ there is also a functor
-    %
-    \begin{equation}
-        \bar{f}: \mfld[r]_{/M} \xrightarrow{\ \ \ \ } \alg{\mathsf{Assoc^{RL}}} (\mfld[r]_{/M}),
-    \end{equation}
-    %
-    that is an algebra.
-\end{corollary}
+\begin{remark}
+    In the above lemma it is important that we stuck to the comparatively simple $\mfld[r]_{/M}$ instead of $\mfld_{/M}$.
+It is not immediately obvious how to deal with the higher morphisms in the latter, as can be seen from the form of \cref{cd:factorization_of_e}.
+The issues are related to the ones that appear in the construction of the pushforward functor \cref{thm:fh_pushforward}.
+A simple case to ponder is an isotopy that maps one embedding of a disk in $M_- \setminus (M_0 \times \mathbb{R})$ to another one in $M_+ \setminus (M_0 \times \mathbb{R})$.
+\end{remark}
 
@@
 
-\begin{proof}[Proof of \cref{thm:gluing_alg_disk/M}]
+\begin{proof}[Proof of \cref{thm:gluing_lcfas}]
+    We will first focus on the case of factorization algebras and prove the statement of \cref{cor:gluing_falgs}. Moreover, because of \cref{cor:disk_alg=falg}, this means that we will focus on $
+    disk[r]_{/M}$-algebras.
+
     The data of a collar-gluing provides open embeddings $M_0 \times \mathbb{R} \xhookrightarrow{} M_-$ and $M_0 \times \mathbb{R} \xhookrightarrow{} M_+$, where $M_-$, $M_0$ and $M_+$ have the usual meanings as in \cref{def:collar-gluing}.
-This can be used to construct the cospan of restriction functors $\alg{\disk_{/M_-}} (\catC) \rightarrow \alg{\disk_{/M_0 \times \mathbb{R}}} (\catC) \leftarrow \alg{\disk_{/M_+}} (\catC)$.
+This can be used to construct the cospan of restriction functors $\alg{\disk[r]_{/M_-}} (\catC) \rightarrow \alg{\disk[r]_{/M_0 \times \mathbb{R}}} (\catC) \leftarrow \alg{\disk[r]_{/M_+}} (\catC)$.
 Using this data we can define the pullback $\infty$-category
@@
     \begin{equation}
-        \mathscr{P} := \alg{\disk_{/M_-}} (\catC) \bigtimes_{\alg{\disk_{/M_0 \times \mathbb{R}}} (\catC)} \alg{\disk_{/M_+}} (\catC).
+        \mathscr{P} := \alg{\disk[r]_{/M_-}} (\catC) \bigtimes_{\alg{\disk[r]_{/M_0 \times \mathbb{R}}} (\catC)} \alg{\disk[r]_{/M_+}} (\catC).
     \end{equation}
     %
-    The further open embeddings of $M_-$, $M_0 \times \mathbb{R}$ and $M_+$ into $M$ again give rise to restriction functors that form a commutative square
+    The further open embeddings of $M_-$, $M_0 \times \mathbb{R}$ and $M_+$ into $M$ again give rise to restriction functors that form a(n on the nose) commutative square
     %
@@
         \begin{tikzcd}
-            \alg{\disk_{/M}} (\catC) \arrow[r] \arrow[d] & \alg{\disk_{/M_+}} (\catC) \arrow[d] \\
-            \alg{\disk_{/M_-}} (\catC) \arrow[r] & \alg{\disk_{/M_0 \times \mathbb{R}}} (\catC),
+            \alg{\disk[r]_{/M}} (\catC) \arrow[r] \arrow[d] & \alg{\disk[r]_{/M_+}} (\catC) \arrow[d] \\
+            \alg{\disk[r]_{/M_-}} (\catC) \arrow[r] & \alg{\disk[r]_{/M_0 \times \mathbb{R}}} (\catC),
         \end{tikzcd}
@@
     %
-    which, by the universal property of the pullback, gives us a canonical functor $\rho: \alg{\disk_{/M}} (\catC) \rightarrow \mathscr{P}$. Our job is to find an inverse to this functor.
+    which, by the universal property of the pullback, gives us a canonical functor $\rho: \alg{\disk[r]_{/M}} (\catC) \rightarrow \mathscr{P}$. Our job is to find an inverse to this functor.
 
     Consider the following construction.
-Given the data of an object $(A_-, A_+) \in \alg{\disk_{/M_-}} (\catC) \times \alg{\disk_{/M_+}} (\catC)$ such that $A_-|_{M_0 \times \mathbb{R}} = A_+|_{M_0 \times \mathbb{R}} = : A_0$ we want to construct a functor $A: \disk_{/M} \xrightarrow{} \catC$.
+Given the data of an object $(A_-, A_+) \in \alg{\disk[r]_{/M_-}} (\catC) \times \alg{\disk[r]_{/M_+}} (\catC)$ such that $A_-|_{M_0 \times \mathbb{R}} = A_+|_{M_0 \times \mathbb{R}} = : A_0$ we want to construct a functor $A: \disk[r]_{/M} \xrightarrow{} \catC$.
 We do this by relying on factorization homology and the bar construction.
-Given $(U \xhookrightarrow{} M) \in \disk_{/M}$ we define
+Given $(U \xhookrightarrow{} M) \in \disk[r]_{/M}$ we define
     %
@@
     \begin{align}
-        \gamma: \mathscr{P} \xrightarrow{\ \ \int \ \ } &\alg{\mfld_{/M_-}}(\catC) \bigtimes\limits_{\alg{\mfld_{/M_0 \times \mathbb{R}}} (\catC)} \alg{\mfld_{/M_+}} (\catC)\notag\\ &\xrightarrow{\ - \circ \bar{f} \ } \mathsf{Fun}(\mfld_{/M}, \alg{\mathsf{Assoc^{RL}}} (\catC)) \xrightarrow{\ \mathsf{B} \circ - \ } \mathsf{Fun}(\mfld_{/M},\catC) \xrightarrow{\ } \mathsf{Fun}(\disk_{/M}, \catC),
+        \gamma: \mathscr{P} \xrightarrow{\ \ \int \ \ } &\alg{\mfld[r]_{/M_-}}(\catC) \bigtimes\limits_{\alg{\mfld[r]_{/M_0 \times \mathbb{R}}} (\catC)} \alg{\mfld[r]_{/M_+}} (\catC)\notag\\ &\xrightarrow{\ - \circ \bar{f} \ } \mathsf{Fun}(\mfld[r]_{/M}, \alg{\mathsf{Assoc^{RL}}} (\catC)) \xrightarrow{\ \mathsf{B} \circ - \ } \mathsf{Fun}(\mfld[r]_{/M},\catC) \xrightarrow{\ } \mathsf{Fun}(\disk[r]_{/M}, \catC),
     \end{align}
@@
 
-    Our first order of business is to show that $\gamma$ actually even lands in $\alg{\disk_{/M}} (\catC)$, and not just $\mathsf{Fun}(\disk_{/M}, \catC)$.
+    Our first order of business is to show that $\gamma$ actually even lands in $\alg{\disk[r]_{/M}} (\catC)$, and not just $\mathsf{Fun}(\disk[r]_{/M}, \catC)$.
 Since we have expressed the construction $A = \gamma(A_-, A_+)$ functorially, we can see that $A$ will inherit the structure of an algebra from the fact that factorization homology and the bar construction are symmetric monoidal functors (see \cref{lem:B_sym_mon} for the latter), together with \cref{lem:fbar_func} that lends this property to $\bar{f}$.
@@
     \begin{equation}
-        \gamma : \mathscr{P} \xrightarrow{\ \ \ \ } \alg{\disk_{/M}} (\catC).
+        \gamma : \mathscr{P} \xrightarrow{\ \ \ \ } \alg{\disk[r]_{/M}} (\catC).
     \end{equation}
@@
         \begin{tikzcd}
-            \mathsf{Hom}_{\alg{\disk_{/M}} (\catC)}(A, B) \arrow[r, bend left=4, "\rho"] & \mathsf{Hom}_{\mathscr{P}}((A_-, A_+), (B_-, B_+)) \arrow[l, bend left=4, "\gamma"]
+            \mathsf{Hom}_{\alg{\disk[r]_{/M}} (\catC)}(A, B) \arrow[r, bend left=4, "\rho"] & \mathsf{Hom}_{\mathscr{P}}((A_-, A_+), (B_-, B_+)) \arrow[l, bend left=4, "\gamma"]
         \end{tikzcd}
@@
     %
-    represents an equivalence of spaces for each $A, B \in \alg{\disk_{/M}} (\catC)$.
+    represents an equivalence of spaces for each $A, B \in \alg{\disk[r]_{/M}} (\catC)$.
 That is, we have to do similar computations as (1) and (2) above, but now on the level of morphisms.
@@
     %
-    which is exactly the collar-gluing property extended to the level of morphisms.
-\end{proof}
+    which is exactly the collar-gluing property extended to the level of morphisms. This shows the equivalence at the level of factorization algebras.
 
-Together with \cref{thm:disk_alg=lcfa} we immediately have the following corollary:
-
-\begin{corollary}\label{cor:gluing_lcfas}
-    A collar-gluing of stratified manifolds $f: M \rightarrow [-1,1]$ induces an equivalence of $\infty$-categories
+    Since we know that restriction does not destroy local constancy, extending the result to the case of locally constant factorization algebras simply requires us to show that the gluing $\gamma$ also preserves this property.
+Let $U \xhookrightarrow{} V$ be two disks of $M$.
+What we have to check is that there is an equivalence
     %
     \begin{equation}
-        \lcfa_M (\catC) \simeq \lcfa_{M_-} (\catC) \bigtimes_{\lcfa_{M_0 \times \mathbb{R}} (\catC)} \lcfa_{M_+}(\catC).
+        \int_U \gamma(A_-, A_+) \xrightarrow{\ \ \simeq \ \ } \int_U \gamma(A_-, A_+)
     \end{equation}
-\end{corollary}
+    %
+    in $\catC$.
+We will achieve this if we find compatible equivalences on each of the pieces $U_- \xhookrightarrow{} V_-, U_0 \times \mathbb{R} \xhookleftarrow{} V_0 \times \mathbb{R}, U_+ \xhookrightarrow{} V_+$ and combine them using the bar construction.
+Generically though, these pieces will not be disks again, so we  can't simply inherit the local constancy property immediately.
+However, using \cref{thm:decom_strat_man} we know that we can iterate the cutting and gluing process so that eventually the pieces will be disks.
+At this point we can inherit the local constancy from $\int A_-'$, $\int A_0'$ and $\int A_+'$ and we can propagate this inheritance through the chain of collar-gluing to the original $\int \gamma (A_-, A_+)$.
+\end{proof}
 
@@
 \end{remark}
-
-Taking into account \cref{cor:disk_alg=falg} together with \cref{cor:fbar_func_discrete}, as well as the definition of factorization homology in the setting of the category $\disk[r]_{/M}$, the proof of \cref{thm:gluing_alg_disk/M} can be seen to clearly hold even in case of ordinary factorization algebras.
-
-\begin{corollary}\label{cor:gluing_falgs}
-    A collar-gluing of stratified manifolds $f: M \rightarrow [-1,1]$ induces an equivalence of $\infty$-categories
-    %
-    \begin{equation}
-        \falg_M (\catC) \simeq \falg_{M_-} (\catC) \bigtimes_{\falg_{M_0 \times \mathbb{R}} (\catC)} \falg_{M_+}(\catC).
-    \end{equation}
-\end{corollary}
 
@@
 This result is not generalizable to higher spheres because it uses the technology of covering spaces.
-\Cref{cor:gluing_lcfas} allows us to recover this nontrivial result.
+\Cref{thm:gluing_lcfas} allows us to recover this nontrivial result.
 To wit, the circle can be exhibited as a collar-gluing $S^1 \cong \mathbb{R} \coprod_{S^0 \times \mathbb{R}} \mathbb{R} \cong \mathbb{R} \coprod_{\mathbb{R} \sqcup \mathbb{R}} \mathbb{R}$.

### 2024-03-14 4gluing_alt.tex
More details

@@
     \begin{equation}
-        \int_U \gamma(A_-, A_+) \xrightarrow{\ \ \simeq \ \ } \int_U \gamma(A_-, A_+)
+        \int_U \gamma(A_-, A_+) \xrightarrow{\ \ \simeq \ \ } \int_V \gamma(A_-, A_+)
     \end{equation}
     %
-    in $\catC$.
-We will achieve this if we find compatible equivalences on each of the pieces $U_- \xhookrightarrow{} V_-, U_0 \times \mathbb{R} \xhookleftarrow{} V_0 \times \mathbb{R}, U_+ \xhookrightarrow{} V_+$ and combine them using the bar construction.
+    in $\catC$. We will achieve this if we find compatible equivalences,
+    %
+    \begin{align}
+        &\int_{U_-} A_- \simeq \int_{V_-} A_-& &\int_{U_0 \times \mathbb{R}} A_0 \simeq \int_{V_0 \times \mathbb{R}} A_0& &\int_{U_+} A_+ \simeq \int_{V_+} A_+,&
+    \end{align}
+    %
+    on each of the pieces $(U_- \xhookrightarrow{} V_-), (U_0 \times \mathbb{R} \xhookrightarrow{} V_0 \times \mathbb{R}), (U_+ \xhookrightarrow{} V_+)$, and combine them using the bar construction.
+If these pieces were disks then the above equivalences would be given by the local constancy of the constituent locally constant factorization algebras.
+
     Generically though, these pieces will not be disks again, so we can't simply inherit the local constancy property immediately.
-However, using \cref{thm:decom_strat_man} we know that we can iterate the cutting and gluing process so that eventually the pieces will be disks.
-At this point we can inherit the local constancy from $\int A_-'$, $\int A_0'$ and $\int A_+'$ and we can propagate this inheritance through the chain of collar-gluing to the original $\int \gamma (A_-, A_+)$.
+To alleviate this issue we make use of \cref{thm:decom_strat_man} which assures us that every manifold can be obtained by collar-gluings and sequential colimits if we start with disks.
+In fact, since our largest manifold of interest is a disk, which is finitary, we only need collar-gluings, and not sequential colimits.
+Thus, we can work inductively and iterate the cutting and gluing process until the pieces become disks.
+The only thing that we need to check is that through one inductive step the equivalences remain compatible.
+Specifically, by compatibility here we mean that there is a commutative diagram
+    %
+    \begin{equation}\label{cd:equivs_from_lc}
+        \begin{tikzcd}
+            \int_{U_-} A_- \arrow[d, "\simeq"] & \int_{U_0 \times \mathbb{R}} A_0 \arrow[d, "\simeq"] \arrow[l] \arrow[r] & \int_{U_+} A_+ \arrow[d, "\simeq"] \\
+            \int_{V_-} A_- & \int_{V_0 \times \mathbb{R}} A_0 \arrow[l] \arrow[r] & \int_{V_+} A_+,
+        \end{tikzcd}
+    \end{equation}
+    %
+    where the horizontal arrows are induced by the relevant embeddings.
+A sufficient condition to guarantee compatibility is that all collar-gluings are defined as collar-gluings of $M$ and then inherited to every open submanifold through its embedding in $M$.
+Focusing on the final two consecutive collar-gluings we get a commutative diagram, which we schematically denote
+    %
+    \begin{equation}
+        \begin{tikzcd}
+            -+ & 0+ \arrow[l] \arrow[r] & ++\\
+            -0 \arrow[u] \arrow[d] & 00 \arrow[u] \arrow[l] \arrow[r] \arrow[d] & +0 \arrow[d] \arrow[u] \\
+            -- & 0- \arrow[l] \arrow[r] & +-,
+        \end{tikzcd}
+    \end{equation}
+    %
+    one for each of $U$ and $V$.
+Stacking these two with the equivalence as connecting arrows is again a commutative diagram.
+This is enough information to guarantee that after acting with the bar construction in one direction we again get compatible equivalences.
+The key point being that we consider the collar-gluings on all pieces in both orders to get all the necessary arrows.
 \end{proof}

### 2024-03-15 sections/1stratified.tex
Negligible notation changes.

@@
 
-\begin{example}\label{54HC9DC}
+\begin{example}\label{ex:strat_from_CW}
     Any CW complex $X$ can be made into a stratified space $X \rightarrow \mathbb{N}$, which sends all points in $X_{\leq k} \setminus {X_{\leq k-1}}$ to $k$, where $X_{\leq k}$ is the $k$-skeleton of $X$.
@@
 
-\begin{example}\label{7UEDP24}
+\begin{example}\label{ex:strat_from_filtration}
     Inspired by the previous example, any topological space $X$ with a filtration by closed subsets $\emptyset \subset X_{\leq 0} \subset \dots \subset X_{\leq n} = X$, is a stratified space, because the filtration induces a map $X \rightarrow \mathbb{N}$, which sends $X_{\leq i} \setminus X_{\leq i-1}$ to $i$.
@@
     Let $X \rightarrow P$ be a stratified space.
-Its (\emph{open}) \emph{cone} $\mathsf{C}(X \rightarrow P)$ is the stratified space constructed as follows.
+Its (\emph{open}) \emph{cone} $\cone(X \rightarrow P)$ is the stratified space constructed as follows.
 At the level of topological spaces we define the pushout in $\mathsf{Top}$
@@
     \begin{equation}
-        \mathsf{C}(X) := * \coprod_{X \times \{0\}} X \times \hoint.
+        \cone(X) := * \coprod_{X \times \{0\}} X \times \hoint.
     \end{equation}
@@
     \begin{equation}
-        \mathsf{C}(P) := * \coprod_{P \times \{ 0\}} P \times [1] \cong P^{\vartriangleleft}.
+        \cone(P) := * \coprod_{P \times \{ 0\}} P \times [1] \cong P^{\vartriangleleft}.
     \end{equation}
     %
-    The standard stratification of $\hoint$ together with the obvious map $* \rightarrow *$ induce a stratification $\mathsf{C}(X) \rightarrow \mathsf{C}(P)$ as a map between pushouts. 
+    The standard stratification of $\hoint$ together with the obvious map $* \rightarrow *$ induce a stratification $\cone(X) \rightarrow \cone(P)$ as a map between pushouts. 
 \end{definition}
@@
 \begin{example}
-    The open cone $C(S^k)$ on the $k$-sphere is canonically identified with $\mathbb{R}^k$ with stratification given by the filtration $\{0\}\subset\mathbb{R}^k$ as in \Cref{7UEDP24}.
+    The open cone $\cone(S^k)$ on the $k$-sphere is canonically identified with $\mathbb{R}^{k+1}_*$, which is the stratified space with stratification given by the filtration $\{0\}\subset\mathbb{R}^{k+1}$ as in \cref{ex:strat_from_filtration}.
 \end{example}
@@
 \begin{definition}
-    Let $X\to P$ be a stratified space.
-Its \emph{closed cone} is the stratified space $\overline{C}(X)\to P^{\vartriangleleft}$ with $\overline{C}(X)=\ast\amalg_{X\times\{0\}}X\times[0,1]$ and the obvious stratification.
+    Let $X \to P$ be a stratified space.
+Its \emph{closed cone} is the stratified space $\cone[b](X) \to P^{\vartriangleleft}$ with $\cone[b](X) = \ast\amalg_{X \times \{0\}} X \times [0,1]$ and the obvious stratification.
 \end{definition}
@@
 \begin{definition}
-    A \emph{$C^0$ basic}, which we will also often call a \emph{disk}, is a $C^0$ stratified space of the form $\mathbb{R}^k \times \mathsf{C}(Z)$, where $k \geq 0$, $\mathbb{R}^k$ has the trivial stratification, and $Z$ is a compact $C^0$ stratified space.
+    A \emph{$C^0$ basic}, which we will also often call a \emph{disk}, is a $C^0$ stratified space of the form $\mathbb{R}^k \times \cone(Z)$, where $k \geq 0$, $\mathbb{R}^k$ has the trivial stratification, and $Z$ is a compact $C^0$ stratified space.
 \end{definition}
@@
 It plays a key role in describing these spaces.\footnote{For example, we said that \cref{thm:basics_give_basis}, as a definition, would be circular.
-One way to resolve this is by induction on depth since $\mathsf{dpt} (\mathbb{R}^n \times \mathsf{C}(Z)) = \mathsf{dpt} (\mathsf{C}(Z)) = \mathsf{dpt} (Z) + 1$} As the name suggests, it conveys information about how deep the stratification is.
-For instance, if the stratification is given by a filtration as in \Cref{54HC9DC}, then it coincides with the length of the filtration, or equivalently, with the length of the longest non-trivial chain of arrives in the stratifying poset.
+One way to resolve this is by induction on depth since $\mathsf{dpt} (\mathbb{R}^n \times \cone(Z)) = \mathsf{dpt} (\cone(Z)) = \mathsf{dpt} (Z) + 1$} As the name suggests, it conveys information about how deep the stratification is.
+For instance, if the stratification is given by a filtration as in \Cref{ex:strat_from_CW}, then it coincides with the length of the filtration, or equivalently, with the length of the longest non-trivial chain of arrives in the stratifying poset.
 Similarly to $\mathsf{dim}$ it has a pointwise and a global version.
@@
 \begin{equation}
-    \{\mathbb{R}^{k_\alpha} \times \mathsf{C}(Z_\alpha) \hookrightarrow M\}_\alpha,
+    \{\mathbb{R}^{k_\alpha} \times \cone(Z_\alpha) \hookrightarrow M\}_\alpha,
 \end{equation}
@@
     Smooth manifolds fall under the definition of stratified manifolds as those that only have one stratum.
-A smooth map $f: Z \xrightarrow{} Z'$ between compact smooth manifolds gives rise to a conically smooth map $\mathsf{C}(f)$ between the cones of these manifolds.
-If we also have a smooth map between Euclidean spaces $g: \mathbb{R}^{n} \xrightarrow{} \mathbb{R}^{n'}$ then the map $g \times \mathsf{C}(f): \mathbb{R}^{n} \times \mathsf{C} (Z) \xrightarrow{} \mathbb{R}^{n'} \times \mathsf{C} (Z')$ is conically smooth.
+A smooth map $f: Z \xrightarrow{} Z'$ between compact smooth manifolds gives rise to a conically smooth map $\cone(f)$ between the cones of these manifolds.
+If we also have a smooth map between Euclidean spaces $g: \mathbb{R}^{n} \xrightarrow{} \mathbb{R}^{n'}$ then the map $g \times \cone(f): \mathbb{R}^{n} \times \cone (Z) \xrightarrow{} \mathbb{R}^{n'} \times \cone (Z')$ is conically smooth.
 This already allows us to describe stratified manifolds of depth 1.
@@
 
-For the next definition we notice that all standard simplices are stratified manifolds, obtained as $\Delta^n\cong\overline{C}^n(\ast)\to\overline{C}(\{0\})\cong[n]$.
+For the next definition we notice that all standard simplices are stratified manifolds, obtained as $\Delta^n \cong \cone[b]^n(\ast) \to \cone[b]^n(\{0\}) \cong [n]$.
 
@@
 \begin{equation}
-    \tau: \mfld_n \xrightarrow{\mathrm{Yoneda}} \mathsf{PShv}(\mfld_n) \xrightarrow{-|_{\mathbb{R}^n \subset \mfld_n}} \mathsf{PShv}(\mathbb{R}^n) \simeq \mathsf{Spaces}_{/\mathsf{BO}(n)},
+    \tau: \mfld_n \xrightarrow{\mathrm{Yoneda}} \mathsf{PShv}(\mfld_n) \xrightarrow{-|_{\{\mathbb{R}^n\} \subset \mfld_n}} \mathsf{PShv}(\mathbb{R}^n) \simeq \mathsf{Spaces}_{/\mathsf{BO}(n)},
 \end{equation}
@@
 
-\begin{remark}\label{9EFM44H}
+\begin{remark}\label{rem:explaining_tau}
     As noted in \cite{af_fhtop}, the Kister--Mazur Theorem (\cite{kister1964microbundles}) provides an equivalence $\mathsf{Emb}(\mathbb{R}^n,\mathbb{R}^n)\simeq \mathsf{Top}(n)$, where $\mathsf{Top}(n)$ is the group of topological automorphisms of $\mathbb{R}^n$; $\mathsf{Emb}(\mathbb{R}^n,\mathbb{R}^n)\simeq\mfld_n(\mathbb{R}^n,\mathbb{R}^n)$ is the group of self-embeddings of $\mathbb{R}^n$; and both groups are equipped with the compact-open topology.
-This yields $\mathsf{PShv}(\mathbb{R}^n)\simeq\mathsf{PShv}(\mathsf{BTop}(n))$, which is equivalent to $\mathsf{Spaces}_{/\mathsf{BTop}(n)}$ by straightening-unstraightening (see \Cref{rem:grothendieck_construction}).\footnote{Presheaves are space-valued, that is, $\mathsf{PShv}(\mathscr{C})=\mathsf{Fun}(\mathscr{C}^{\mathsf{op}},\mathsf{Spaces})$.} Finally, the inclusion $\mathsf{O}(n)\hookrightarrow\mathsf{Emb}(\mathbb{R}^n,\mathbb{R}^n)$ is also an equivalence (\cite[Proposition 2.2.6]{af_primer}), yielding the displayed equivalence.
+This yields $\mathsf{PShv}(\mathbb{R}^n)\simeq\mathsf{PShv}(\mathsf{BTop}(n))$, which is equivalent to $\mathsf{Spaces}_{/\mathsf{BTop}(n)}$ by straightening--unstraightening (see \Cref{rem:grothendieck_construction}).\footnote{Presheaves are space-valued, that is, $\mathsf{PShv}(\mathscr{C})=\mathsf{Fun}(\mathscr{C}^{\mathsf{op}},\mathsf{Spaces})$.} Finally, the inclusion $\mathsf{O}(n)\hookrightarrow\mathsf{Emb}(\mathbb{R}^n,\mathbb{R}^n)$ is also an equivalence (\cite[Proposition 2.2.6]{af_primer}), yielding the displayed equivalence.
 The first map, the $\infty$-categorical Yoneda embedding, sends $M\mapsto((\mfld_{n})_{/M}\to\mfld_n)$ as a map with target $\mathsf{RFib}(\mfld_n)$, as in \cite{lurie_htt}.
-The fiber of $(\mfld_{n})_{/M}\to\mfld_n$ at $N$ is equivalent to the space of embeddings of $N$ into $M$, and so the restricted presheaf on the full sub-$\infty$-category at $\mathbb{R}^n$ sends $\mathbb{R}^n$ to the space of embeddings of $\mathbb{R}^n$ into $M$.
+The fiber of $(\mfld_{n})_{/M}\to\mfld_n$ at $N$ is equivalent to the space of embeddings of $N$ into $M$, and so the restricted presheaf on the full $\infty$-subcategory at $\mathbb{R}^n$ sends $\mathbb{R}^n$ to the space of embeddings of $\mathbb{R}^n$ into $M$.
 \end{remark}
@@
     \begin{enumerate}
-        \item $(G \rightarrow \mathsf{O}(n)) = (\mathsf{O}(n) \xrightarrow{\mathrm{id}} \mathsf{O}(n))$ reproduces the case of no tangential structure,\footnote{or the contractible choice of a riemannian metric}
+        \item $(G \rightarrow \mathsf{O}(n)) = (\mathsf{O}(n) \xrightarrow{\mathrm{id}} \mathsf{O}(n))$ reproduces the case of no tangential structure\footnote{or the contractible choice of a Riemannian metric},
         \item $(G \rightarrow \mathsf{O}(n)) = (\mathsf{SO}(n) \xhookrightarrow{} \mathsf{O}(n))$ is the case of oriented smooth manifolds,
@@
 
-Moving on to the stratified setting, we note that the stratified version of the full $\infty$-subcategory $\mathbb{R}^n \subset \mfld_n$ is the $\infty$-category $\bsc$ of basic singularity types, obtaining
+Moving on to the stratified setting, we note that the stratified version of the full $\infty$-subcategory $\{\mathbb{R}^n\} \subset \mfld_n$ is the $\infty$-category $\bsc$ of basic singularity types, obtaining
 %
@@
 \begin{remark}\label{rem:grothendieck_construction}
-    The straightening-unstraightening construction of \cite[§2.2]{lurie_htt} provides an equivalence between $\mathsf{Spaces}$-valued presheaves on an $\infty$-category $\catC$ and right fibrations\footnote{A \emph{right fibration} (over $\catC$) is a functor $f:\mathscr{E} \rightarrow \catC$ such that whenever a square of type
+    The straightening--unstraightening construction of \cite[§2.2]{lurie_htt} provides an equivalence between $\mathsf{Spaces}$-valued presheaves on an $\infty$-category $\catC$ and right fibrations\footnote{A \emph{right fibration} (over $\catC$) is a functor $f:\mathscr{E} \rightarrow \catC$ such that whenever a square of type
     %
@@
     i.e.
-the forgetful functor from the over-$\infty$-category over $M$.\footnote{The notation is slightly misleading since $M$ need not be in $\bsc$.} The $\infty$-category $\mathsf{Entr}(M)$ defined here is called the enter-path $\infty$-category of the stratified manifold $M$.\footnote{A different version of this $\infty$-cateogry is defined in  called the exit-path $\infty$-category of the stratified space $M$.
+the forgetful functor from the over-$\infty$-category over $M$.\footnote{The notation is slightly misleading since $M$ need not be in $\bsc$.} The $\infty$-category $\mathsf{Entr}(M)$ defined here is called the enter-path $\infty$-category of the stratified manifold $M$.\footnote{A different version of this $\infty$-cateogry is defined in \cite[§A.6]{lurie_ha} called the exit-path $\infty$-category of the stratified space $M$.
 It is shown in \cite{afr_homhyp} that the exit-path $\infty$-category of \cite[§A.6]{lurie_ha} is equivalent to the opposite of the enter-path $\infty$-category mentioned above.} In fact the statements that we will make next will take on this perspective for the tangent classifier.
@@
 The key realization is that the data which the map of spaces $B \rightarrow \mathsf{BO}(n)$ provided before was the data of a presheaf on $\mathsf{BO}(n)$, standing in as the $\infty$-category of basics with only one object $\mathbb{R}^n$.
-The analogous construction in the stratified case is to provide a presheaf on $\bsc$, which by \Cref{rem:grothendieck_construction} is given by a right fibration over $\bsc$.
+The analogous construction in the stratified case is to provide a presheaf on $\bsc$, which by \cref{rem:grothendieck_construction} is given by a right fibration over $\bsc$.
 
 \begin{definition}
-    An $\infty$-category of basics, or a tangential structure, is a right fibration $\bstr \rightarrow \bsc$.
+    An $\infty$-category of basics is a right fibration $\bstr \rightarrow \bsc$. It provides both the data of the allowed singularity types and the data of (a generalization of) tangential structure.
 \end{definition}
@@
 \begin{example}[{\cite[Example 5.2.5]{aft_localstrut}}]
-    We denote by $\mathsf{D}_n\hookrightarrow \bsc$ or simply $\mathsf{D}_n$ the tangential structure given by the full sub-$\infty$-category inclusion of $\bsc_{0,n}$, the basics of depth $0$ and pure dimension $n$.\footnote{A stratified space $X\to P$ has \emph{pure dimension $n$} (\cite[Definition 2.4.1]{aft_localstrut}) if its local (\v{C}ech--Lebesgue) dimension $\mathsf{dim}_x(X)$ at every $x\in X$ is $n$.
+    We denote by $\mathsf{D}_n\hookrightarrow \bsc$ or simply $\mathsf{D}_n$ the tangential structure given by the full $\infty$-subcategory inclusion of $\bsc_{0,n}$, the basics of depth $0$ and pure dimension $n$.\footnote{A stratified space $X\to P$ has \emph{pure dimension $n$} (\cite[Definition 2.4.1]{aft_localstrut}) if its local (\v{C}ech--Lebesgue) dimension $\mathsf{dim}_x(X)$ at every $x\in X$ is $n$.
 Connected topological manifolds are of this type.} Accordingly, $\mathsf{D}_n$-manifolds are topological $n$-manifolds.
-As in \Cref{9EFM44H}, we have an equivalence $\mathsf{D}_n\simeq \mathsf{BGL}(n)\simeq \mathsf{BO}(n)$ of $\infty$-groupoids.
+As in \Cref{rem:explaining_tau}, we have an equivalence $\mathsf{D}_n\simeq \mathsf{BGL}(n)\simeq \mathsf{BO}(n)$ of $\infty$-groupoids.
 \end{example}
@@
 \begin{construction}\label{con:d_1^bor_structure}
-    Consider the $\infty$-subcategory $\mathsf{D}_1^{\partial} \subset \bsc$ whose objects are $\mathbb{R}$ and $\hoint=C(\ast)$.
+    Consider the $\infty$-subcategory $\mathsf{D}_1^{\partial} \subset \bsc$ whose objects are $\mathbb{R}$ and $\hoint = \cone(\ast)$.
 There is a unique right fibration $\mathsf{D}_1^{\partial, \mathsf{or}} \rightarrow \mathsf{D}_1^{\partial}$, whose fiber over $\mathbb{R}$ is a point $\{ \mathbb{R}\}$, and whose fiber over $\hoint$ is two points $\{ \hoint, {\mathbb{R}_{\leq 0}} \}$.
@@
 For instance, when $G=\ast$, so that $\mathsf{D}^\ast_n$ constrols framed $n$-manifolds, the map $BG=\ast\to \mathsf{BO}(n)\simeq\mathsf{D}_n$ is not a right fibration, owing to the observation that right fibrations of Kan complexes are Kan fibrations, and these, when surjective on objects, are epimorphisms.
-On the other hand, $B\ast=\ast\simeq (\mathsf{D}_n)_{/\mathbb{R}^n}$ since over-$\infty$-groupoids are contractible (\cite[018Y]{lurie_kerodon}), but $(\mathsf{D}_n)_{/\mathbb{R}^n}\to \mathsf{D}_n$ \emph{is} a right fibration since it is a projection from an over-$\infty$-category (\cite[Proposition 018F]{lurie_kerodon}, \cite{joyal}).
-Moreover, $\mathsf{D}_n\hookrightarrow \bsc$ is a right fibration since this full sub-$\infty$-category is trivially a sieve, so the composition $(\mathsf{D}_n)_{/\mathbb{R}^n}\to \bsc$ is a right fibration as well.
+On the other hand, $B\ast=\ast\simeq (\mathsf{D}_n)_{/\mathbb{R}^n}$ since over-$\infty$-groupoids are contractible (\cite[018Y]{lurie_kerodon}), but $(\mathsf{D}_n)_{/\mathbb{R}^n}\to \mathsf{D}_n$ \emph{is} a right fibration since it is a projection from an over-$\infty$-category (\cite[018F]{lurie_kerodon}, \cite{joyal}).
+Moreover, $\mathsf{D}_n\hookrightarrow \bsc$ is a right fibration since this full $\infty$-subcategory is trivially a sieve, so the composition $(\mathsf{D}_n)_{/\mathbb{R}^n}\to \bsc$ is a right fibration as well.
 In general, the map $\mathsf{B}G\to \mathsf{BO}(n)$ is not a right fibration unless $G\to\mathsf{O}(n)$ is an epimorphism.
@@
 \begin{construction}[{\cite[Example 5.2.10]{aft_localstrut}}]
-    Let $\mathsf{D}_{d \subset n} \subset \bsc$ be the full $\infty$-subcategory whose objects are $\mathbb{R}^n$ and $\mathbb{R}^{d \subset n} := \mathbb{R}^{d} \times \mathsf{C}(S^{n-d-1})$, where $d < n$.
+    Let $\mathsf{D}_{d \subset n} \subset \bsc$ be the full $\infty$-subcategory whose objects are $\mathbb{R}^n$ and $\mathbb{R}^{d \subset n} := \mathbb{R}^{d} \times \cone(S^{n-d-1})$, where $d < n$.
 We elaborate that the morphism spaces are given as follows:

### 2024-03-15 sections/5classification.tex
Negligible notation changes.

@@
     \begin{equation}
-        \mathsf{C}(\pi) \rightarrow M_\Sigma
+        \cone(\pi) \rightarrow M_\Sigma
     \end{equation}
@@
         \item the image is open, and
-        \item $\mathsf{C}(\pi)$ is the fiberwise open cone of the constructible bundle $\mathsf{L}_{\Sigma} \xrightarrow{\pi} \Sigma$ giving the link.
+        \item $\cone(\pi)$ is the fiberwise open cone of the constructible bundle $\mathsf{L}_{\Sigma} \xrightarrow{\pi} \Sigma$ giving the link.
     \end{enumerate}
     %
-    If $\Sigma$ is a stratum of $M_\Sigma$ then the map $\mathsf{C}(\pi) \rightarrow M_\Sigma$ is even an open embedding.
+    If $\Sigma$ is a stratum of $M_\Sigma$ then the map $\cone(\pi) \rightarrow M_\Sigma$ is even an open embedding.
 \end{theorem}
@@
 \begin{remark}
-    In more detail, specialized to our situation, the regular neighborhood $\mathsf{C}(\pi)$ is constructed as the pushout of stratified manifolds
+    In more detail, specialized to our situation, the regular neighborhood $\cone(\pi)$ is constructed as the pushout of stratified manifolds
     %
@@
             \mathsf{L}_{\Sigma} \times \{0\} \arrow[r, "\pi"] \arrow[d, "\mathrm{id} \times 0"', hook] & \Sigma \arrow[d] \\
-            \mathsf{L}_{\Sigma} \times \hoint \arrow[r] & \mathsf{C}(\pi) \arrow[ul, phantom, "\lrcorner", very near start],
+            \mathsf{L}_{\Sigma} \times \hoint \arrow[r] & \cone(\pi) \arrow[ul, phantom, "\lrcorner", very near start],
         \end{tikzcd}
@@
 \begin{construction}
-    The existence of $\mathsf{C}(\pi)$ allows us to define a collar-gluing for the stratified manifold $M_\Sigma$
+    The existence of $\cone(\pi)$ allows us to define a collar-gluing for the stratified manifold $M_\Sigma$
     %
     \begin{equation}\label{eq:M_Sigma_decomposition}
-        M_\Sigma \cong \left( M \setminus \Sigma \right) \coprod_{\mathsf{L}_\Sigma \times \mathbb{R}} \mathsf{C}(\pi),
+        M_\Sigma \cong \left( M \setminus \Sigma \right) \coprod_{\mathsf{L}_\Sigma \times \mathbb{R}} \cone(\pi),
     \end{equation}
     %
-    where the map $\mathsf{L}_\Sigma \times \mathbb{R} \rightarrow M \setminus \Sigma$ is provided by $\mathsf{L}_\Sigma \times \mathbb{R} \cong \mathsf{L}_\Sigma \times \mathbb{R}_{\gneq 0} \cong \mathsf{C}(\pi) \setminus \Sigma \xhookrightarrow{} M \setminus \Sigma$.
+    where the map $\mathsf{L}_\Sigma \times \mathbb{R} \rightarrow M \setminus \Sigma$ is provided by $\mathsf{L}_\Sigma \times \mathbb{R} \cong \mathsf{L}_\Sigma \times \mathbb{R}_{\gneq 0} \cong \cone(\pi) \setminus \Sigma \xhookrightarrow{} M \setminus \Sigma$.
 We also note that the properness of the embedding $\Sigma \xhookrightarrow{} M$ makes $M \setminus \Sigma$ an open submanifold of $M$.
@@
 \begin{equation}
-    \lcfa_{M_\Sigma} (\catC) \simeq \lcfa_{M \setminus \Sigma} (\catC) \bigtimes_{\lcfa_{\mathsf{L}_\Sigma \times \mathbb{R}} (\catC)} \lcfa_{\mathsf{C}(\pi)} (\catC),
+    \lcfa_{M_\Sigma} (\catC) \simeq \lcfa_{M \setminus \Sigma} (\catC) \bigtimes_{\lcfa_{\mathsf{L}_\Sigma \times \mathbb{R}} (\catC)} \lcfa_{\cone(\pi)} (\catC),
 \end{equation}
@@
 Similarly, this is the case for the locally constant factorization algebras $\lcfa_{\mathsf{L}_\Sigma \times \mathbb{R}}$.
-The more prescient question is about the classification of locally constant factorization algebras on the one remaining stratified space $\mathsf{C}(\pi)$.
+The more prescient question is about the classification of locally constant factorization algebras on the one remaining stratified space $\cone(\pi)$.
 
-By \cite[ex.3.6.6]{aft_localstrut} $\mathsf{C}(\pi)$ is always a bundle over $\Sigma$, fibered over basics.
-For our particular setup this means that $\mathsf{C}(\pi)$ a fiber bundle over $\Sigma$ with typical fiber $\mathbb{R}^{n-d}_*$.
+By \cite[ex.3.6.6]{aft_localstrut} $\cone(\pi)$ is always a bundle over $\Sigma$, fibered over basics.
+For our particular setup this means that $\cone(\pi)$ a fiber bundle over $\Sigma$ with typical fiber $\mathbb{R}^{n-d}_*$.
 Thus, the classification comes down to the classification of locally constant factorization algebras on stratified fiber bundles.
@@
 This is because, as discussed in \cref{def:framed_d_under_n_structure}, $\mathsf{D}_{d \subset n}^*$-manifolds come with a trivialization of the normal bundle of the distinguished submanifold $\Sigma$.
-This, in turn implies trivializations for $\mathsf{C}(\pi)$ and $\mathsf{L}_{\Sigma} \times \mathbb{R}$ as bundles over $\Sigma$ with typical fibers $\mathbb{R}^{n-d}_*$ and $S^{n-d-1} \times \mathbb{R}$, respectively.
+This, in turn implies trivializations for $\cone(\pi)$ and $\mathsf{L}_{\Sigma} \times \mathbb{R}$ as bundles over $\Sigma$ with typical fibers $\mathbb{R}^{n-d}_*$ and $S^{n-d-1} \times \mathbb{R}$, respectively.
 In other words, there are isomorphisms
@@
 \begin{align}
-    &\mathsf{C}(\pi) \cong \Sigma \times \mathbb{R}^{n-d}_*& &\mathrm{and}& &\mathsf{L}_{\Sigma} \times \mathbb{R} \cong \Sigma \times S^{n-d-1} \times \mathbb{R}.&
+    &\cone(\pi) \cong \Sigma \times \mathbb{R}^{n-d}_*& &\mathrm{and}& &\mathsf{L}_{\Sigma} \times \mathbb{R} \cong \Sigma \times S^{n-d-1} \times \mathbb{R}.&
 \end{align}
@@
 \begin{equation}
-    \lcfa_{\mathsf{C}(\pi)} (\catC) \simeq \mathsf{Mod}^{\mathbb{E}_{n-d}} (\lcfa_{\Sigma} (\catC)).
+    \lcfa_{\cone(\pi)} (\catC) \simeq \mathsf{Mod}^{\mathbb{E}_{n-d}} (\lcfa_{\Sigma} (\catC)).
 \end{equation}

### 2024-03-15 sections/2homology.tex
Miniscule changes.

@@
 Intuitively, those disks that have an open embedding into $M$ admit a $\bstr$-structure by restriction since $M$ admits one.
-From here, since over $\infty$-groupoids are contractible, there is an equivalence between the singleton space consisting of this inherited $\bstr$-structure and the space of $\bstr$-structures the disk originally had.
+From here, since over $\infty$-groupoids are contractible (\cite[\href{https://kerodon.net/tag/018Y}{018Y}]{lurie_kerodon}), there is an equivalence between the singleton space consisting of this inherited $\bstr$-structure and the space of $\bstr$-structures the disk originally had.
 The argument, of course, holds for $\disk(\bstr)_{/M}$ too, as well as $\mfld(\bstr)_{/M}$ and $\mfld[r](\bstr)_{/M}$.
@@
 The next result is of key importance to the technical side of the theory, and will be used extensively throughout.
-It alone, is essentially the reason for the appearance of constructible bundles in a lot of later developments.
+It alone, is essentially the reason for the appearance of weakly constructible bundles in a lot of later developments.
 
 \begin{lemma}[{\cite[lem.2.24]{aft_fhstrat}}]\label{lem:f^-1}
-    Let $f: M \xrightarrow{} N$ be a constructible bundle. There is a functor of $\infty$-operads
+    Let $f: M \xrightarrow{} N$ be a weakly constructible bundle. There is a functor of $\infty$-operads
     %
@@
 \begin{remark}
-    Because of \cref{rem:disk_b=disk_bsc}, the above construction works for manifolds with any general $\bstr$-structure, with no further requirements on the constructible bundle $f$.
+    Because of \cref{rem:disk_b=disk_bsc}, the above construction works for manifolds with any general $\bstr$-structure, with no further requirements on the weakly constructible bundle $f$.
 \end{remark}
@@
 \begin{theorem}[{\cite[thm.2.25]{aft_fhstrat}}]\label{thm:fh_pushforward}
-    Let $f: M \xrightarrow{} N$ be a constructible bundle. There is a pushforward functor
+    Let $f: M \xrightarrow{} N$ be a weakly constructible bundle. There is a pushforward functor
     %
@@
 Now that we have a pushforward operation, we can finally explicitly state what excision is in this context.
-This is because a collar-gluing of a stratified manifold $M$ is defined exactly as a constructible bundle $f: M \xrightarrow{} [-1,1]$.
+This is because a collar-gluing of a stratified manifold $M$ is defined exactly as a weakly constructible bundle $f: M \xrightarrow{} [-1,1]$.
 

### 2024-03-15 sections/3algebras.tex
Miniscule changes.

@@
 This means that locally constant factorization algebras record the data of coarser stratified structures as $\infty$-subcategories.
-Forgetting local constancy, the proof, of course, applies to factorization algebras of all flavors, however only locally constant factorization algebras can detect the stratified structure, so in all other cases that we have considered the above functor is even an equivalence, and not just fully-faithful.
+Forgetting local constancy, the proof, of course, applies to factorization algebras of all flavors, however for the types that don't detect the stratified structure the above functor is even an equivalence, and not just fully-faithful, and is of no interest.
 \end{remark}

### 2024-03-15 sections/4gluing.tex
Miniscule changes.

@@
 We denote the objects of $\alg{\mathsf{Assoc^{RL}}} (\catC)$ as $(R,A,L)$, and use $\mathsf{B}_{\bullet} (R, A, L):\Delta^{\mathsf{op}} \rightarrow \catC$ for the simplicial object of the bar construction.
-Using the language of \cite[def.2.1.2.7]{lurie_ha}, to prove that $\mathsf{B}$ is symmetric monoidal amounts to showing that for each basepoint-preserving map of based finite sets $f: I_* \xrightarrow{} J_*$ there is a commutative diagram of $\infty$-categories
+Using the language of \cite[def.2.1.2.7]{lurie_ha}, to prove that $\mathsf{B}$ is symmetric monoidal amounts to showing that for each basepoint--preserving map of based finite sets $f: I_* \xrightarrow{} J_*$ there is a commutative diagram of $\infty$-categories
     %
@@
 
-    From this example we can easily see that beyond the dimensionality $n$ of the space, which is locally kept track of as an $\mathbb{E}_n$-algebra, locally constant factorization algebras for the higher spheres also keep track of higher coherent (self-)equivalences, which imitate traingulations of the spheres.
+    From this example we can easily see that beyond the dimensionality $n$ of the space, which is locally kept track of as an $\mathbb{E}_n$-algebra, locally constant factorization algebras for the higher spheres also keep track of higher coherent (self-)equivalences, which imitate triangulations of the spheres.
 \end{example}

### 2024-03-15 sections/1stratified.tex
a few things in §2 (ongoing)

--- 2024-03-11 sections/1stratified.tex
@@
 For instance, when $G=\ast$, so that $\mathsf{D}^\ast_n$ constrols framed $n$-manifolds, the map $BG=\ast\to \mathsf{BO}(n)\simeq\mathsf{D}_n$ is not a right fibration, owing to the observation that right fibrations of Kan complexes are Kan fibrations, and these, when surjective on objects, are epimorphisms.
-On the other hand, $B\ast=\ast\simeq (\mathsf{D}_n)_{/\mathbb{R}^n}$ since over-$\infty$-groupoids are contractible (\cite[018Y]{lurie_kerodon}), but $(\mathsf{D}_n)_{/\mathbb{R}^n}\to \mathsf{D}_n$ \emph{is} a right fibration since it is a projection from an over-$\infty$-category (\cite[Proposition 018F]{lurie_kerodon}, \cite{joyal}).
+On the other hand, $B\ast=\ast\simeq (\mathsf{D}_n)_{/\mathbb{R}^n}$ since over-$\infty$-groupoids are contractible (\cite[Corollary 018Y]{lurie_kerodon}), but $(\mathsf{D}_n)_{/\mathbb{R}^n}\to \mathsf{D}_n$ \emph{is} a right fibration since it is a projection from an over-$\infty$-category (\cite[Proposition 018F]{lurie_kerodon}, \cite{joyal}).
 Moreover, $\mathsf{D}_n\hookrightarrow \bsc$ is a right fibration since this full sub-$\infty$-category is trivially a sieve, so the composition $(\mathsf{D}_n)_{/\mathbb{R}^n}\to \bsc$ is a right fibration as well.

### 2024-03-15 sections/2homology.tex
a few things in §2 (ongoing)

--- 2024-03-04 sections/2homology.tex
@@
 %
-In fact this is only the simplest variant of factorization homology.
-Variants that accommodate stratified manifolds instead of smooth ones and even $(\infty,n)$-categories instead of algebras have also been worked out.
-Given the focus of the present work, we will be concerned with the variant that can evaluate stratified manifolds.
-We will not be interested, however, in generalizing the algebraic input beyond disk algebras to the realm of $(\infty,n)$-categories.
-Fixing the algebra, the construction is functorial with respect to open embeddings in the manifold variable, which is the starting point to show that it is a chain level homology theory in a generalized sense, and giving the name.
+The physical interpretation is that given a spacetime $M$ and local observables $A$, $\int_MA$ returns global observables, though typically not all of them.
+
+This implementation, with $M$ relaxed to a stratified manifold and $A$ to an appropriate type of algebra, is sometimes termed `alpha' factorization homology, as opposed to the `beta' version of \cite{ayala2020factorization} that evaluates $(\infty,n)$-categories on variframed stratified $n$-manifolds.
+In this work, we will be concerned, in this sense, with alpha factorization homology.
+
+Fixing the algebra, the construction is functorial with respect to open embeddings in the manifold variable, which is the starting point to show that it is a chain level homology theory in a generalized sense.
 The initial chiral version was first introduced in \cite{bd2004}, and a topological version was introduced by \cite{lurie_ha}.
-Later, in \cref{thm:disk_alg=lcfa}, we will also see how factorization homology serves to construct factorization algebras.
-The theory of factorization homology has been deeply developed in \cite{af_fhtop, aft_fhstrat}, especially in the manner that we introduce it in here.
-A good introduction, is thus, given by \cite{af_primer}, which we will be following.
+Later, in \Cref{thm:disk_alg=lcfa}, we will also see how factorization homology serves to construct factorization algebras.
+The theory of factorization homology in the manner that we will recall here has been developed in \cite{francis2013,af_fhtop, aft_fhstrat}.
+We will follow the introductory text \cite{af_primer}.
 
@@
 \begin{enumerate}
-    \item $\catC$ is presentable: it admits colimits, and every object is a filtered colimit of compact objects\footnote{For the exact meaning of these terms we refer the reader to \cite[sec.5.3]{lurie_htt}.
+    \item $\catC$ is presentable: it admits colimits, and every object is a filtered colimit of compact objects\footnote{For the exact meaning of these terms we refer the reader to \cite[§5.3]{lurie_htt}.
 For us, it will suffice to give examples of $\infty$-categories that satisfy these requirements.}, and
@@
     %
-    In particular, $(\mathscr{C}\mathsf{h}_{\mathbb{k}}, \otimes)$ is the most useful for the purposes of mathematical physics, which is why it's the choice for the development in \cite{cg2016} and \cite{ginot2015}.
+    In particular, $(\mathscr{C}\mathsf{h}_{\mathbb{k}}, \otimes)$ is the most relevant for physical examples which is why it is the target of choice in \cite{cg2016} and \cite{ginot2015}.
 \end{example}
@@
 
+We will now recall the $\infty$-category of disk algebras with a chosen tangential structure valued in a symmetric monoidal $\infty$-category.
+First, recall Segal's category $\mathsf{Fin}_{\ast}$ of finite pointed sets and their maps.
+By abuse, we write $\mathsf{Fin}_\ast=\mathsf{N}(\mathsf{Fin}_\ast)$ for its nerve.
+Following \cite{lurie_ha}, we take the objects of $\mathsf{Fin}_{\ast}$ to be $\langle n\rangle=\{\ast,1,\dots,n\}$.
+For every $i\in\{1,\dots,n\}$ there is a map $\rho^i\colon\langle n\rangle\to\langle 1\rangle$ that sends $i$ to $1$ but is otherwise constant at $\ast\in\langle1\rangle$.
+A \emph{symmetric monoidal $\infty$-category} is, according to \cite[Definition 2.0.0.7]{lurie_ha}, a cocartesian fibration\footnote{A \emph{cocartesian fibration} (\cite[Definition 01T5]{lurie_kerodon}) $q\colon\mathscr{A}\to\mathscr{B}$ between simplicial sets is one such that every edge $f\colon\mathscr{A}_1$ is \emph{$q$-cocartesian}, that is, any horn of type $\Lambda^n_0\to\mathscr{A}$, $n\geq2$, whose restriction to $\{0<1\}$ is $f$, admits a filler if its projection to $\mathscr{B}$ admits a filler.} $\catC\to\mathsf{Fin}_\ast$ such that the maps the maps $\rho^i\colon\langle n\rangle\to\langle 1\rangle$, $1\leq i\leq n$, induce an equivalence $\catC_{\langle n\rangle}\simeq(\catC_{\langle 1\rangle})^{\times n}$ for every $n\geq0$, where $\catC_{x}$ is the fiber at $x$.
+We mostly abbreviate $\catC\to\mathsf{Fin}_\ast$ to $\catC$.
+
+The $\infty$-category $\mathsf{Fun}^{\otimes}(\catC,\mathscr{D})\subset\mathsf{Fun}_{/\mathsf{Fun}_\ast}(\catC,\mathscr{D})$ of \emph{symmetric monoidal functors} is the full sub-$\infty$-category of all the functor $\infty$-category on those functors that preserve cocartesian edges.
+
 \begin{definition}
@@
     %
-    and such that the swap in $\disk(\bstr)$, $U \sqcup V \simeq V \sqcup U$, is sent to the swap in $\catC$, $F(U) \otimes F(V) \simeq F(V) \otimes F(U)$, in a way that is compatible with the maps in \cref{eq:symmon_maps}.
+    and such that the swap in $\disk(\bstr)$, $U \sqcup V \simeq V \sqcup U$, is sent to the swap in $\catC$, $F(U) \otimes F(V) \simeq F(V) \otimes F(U)$, in a way that is compatible with the maps in \eqref{eq:symmon_maps}.
 A good informal explanation of this and other topics related to disk algebras can be found in the lecture notes \cite{tanaka20}.
@@
     For more details on $\mathbb{E}_n$-algebras and why these algebras encompass large portions of the examples one usually cares about see \cite[sec.5.1]{lurie_ha}.
-%or alternatively in appendix \cref{app:En_algebras}.
+%or alternatively in appendix \Cref{app:En_algebras}.
     Roughly speaking, $\mathbb{E}_1$-algebras are homotopy associative algebras and with increasing $n$ we get increasing levels of homotopy commutativity.
@@
 \begin{remark}
-    Because of \cref{rem:disk_b=disk_bsc}, the above construction works for manifolds with any general $\bstr$-structure, with no further requirements on the constructible bundle $f$.
+    Because of \Cref{rem:disk_b=disk_bsc}, the above construction works for manifolds with any general $\bstr$-structure, with no further requirements on the constructible bundle $f$.
 \end{remark}
@@
 Namely, the left Kan extension of underlying $\infty$-categories lifts to a symmetric monoidal, in the absolute case, and operadic, in the relative case, left Kan extension.
-In the relative case, we will almost always abuse notation and write $\int_N A$ instead of $\int_{N \xhookrightarrow{} M} A$, but because of \cref{lem:double_slice} this is not much of an abuse.
+In the relative case, we will almost always abuse notation and write $\int_N A$ instead of $\int_{N \xhookrightarrow{} M} A$, but because of \Cref{lem:double_slice} this is not much of an abuse.
 Furthermore, factorization homology is also shown to be fully faithful due to this being true for the inclusion $\disk(\bstr) \xrightarrow{} \mfld(\bstr)$, as well as, the relative version with slices.
@@
 
-We want to show that disk algebras with $\mathsf{D}_1^{\partial, *}$-structure, as defined in \cref{con:d_1^bor_structure}, can be described algebraically.
+We want to show that disk algebras with $\mathsf{D}_1^{\partial, *}$-structure, as defined in \Cref{con:d_1^bor_structure}, can be described algebraically.
 For this we set up two $\infty$-operads $\mathsf{Assoc^{RL}}$ and $\mathsf{O^{RL}}$.
@@
 \begin{remark}
-    More informally, what the \cref{con:assocRL} says is that the only multi-morphism domains possible are $\emptyset$, $(A,A,\dots,A)$, $(R,A,\dots,A)$ or $(A,\dots,A, L)$ and that there is one multi-morphism for each permutation of the $A$ entries.
+    More informally, what the \Cref{con:assocRL} says is that the only multi-morphism domains possible are $\emptyset$, $(A,A,\dots,A)$, $(R,A,\dots,A)$ or $(A,\dots,A, L)$ and that there is one multi-morphism for each permutation of the $A$ entries.
 This makes it clear that algebras over this $\infty$-operad will be unital, (homotopy) associative algebras, together with a unital left and a unital right module.
@@
     %
-    that descend to the equivalences of \cref{prop:disk1bor=assocRL}.
+    that descend to the equivalences of \Cref{prop:disk1bor=assocRL}.
 \end{proposition}
@@
 \begin{proof}
-    As in the proof of \cref{prop:disk1bor=assocRL} the first equivalence is clear.
+    As in the proof of \Cref{prop:disk1bor=assocRL} the first equivalence is clear.
 The idea to keep in mind is that since the boundary of $[-1,1]$ consists of a left point and a right point, there can only be oriented embeddings of disks into $[-1,1]$ with at most one of each of $\left[-1,1 \right)$ and $\left( -1, 1 \right]$.
@@
 \begin{proof}
-    The only thing to show is the middle equivalence. This follows from \cref{lem:disk/M_to_disk}, which we will introduce later. 
+    The only thing to show is the middle equivalence. This follows from \Cref{lem:disk/M_to_disk}, which we will introduce later. 
 \end{proof}
@@
 We remark here that these equivalences are actually even natural in $G$.
-To explain this, we first notice that the equivalences in \cref{eq:fin_equivs_obj} actually arise from equivalences between $\infty$-categories
+To explain this, we first notice that the equivalences in \Cref{eq:fin_equivs_obj} actually arise from equivalences between $\infty$-categories
     %
@@
     whose value on objects is given by $G \mapsto \mathscr{C}_{G/}$.
-We can now state that by naturality in $G$ we mean that the functors of \cref{eq:fin_equivs_cat} assemble into an equivalence of functors
+We can now state that by naturality in $G$ we mean that the functors of \Cref{eq:fin_equivs_cat} assemble into an equivalence of functors
     %
@@
     in $\mathsf{Fun}(\mathsf{Fun(\mathscr{B}, \mathscr{C})}, \cat)$.
-But this is obviously the case, given the description of the maps in \cref{eq:fin_equivs_cat}, and amounts to nothing more than bookkeeping.
+But this is obviously the case, given the description of the maps in \Cref{eq:fin_equivs_cat}, and amounts to nothing more than bookkeeping.
 \end{remark}
@@
 
-    Since the equivalences above come from an argument about finality, \cref{rem:fin_equiv_natural} tells us that they are actually even natural in the algebra variable $(R, A, L)$, so that the equivalence lifts to the level of functors.
+    Since the equivalences above come from an argument about finality, \Cref{rem:fin_equiv_natural} tells us that they are actually even natural in the algebra variable $(R, A, L)$, so that the equivalence lifts to the level of functors.
 \end{proof}
@@
 
-The construction of \cref{lem:f^-1} gives a functor which allows us to change the stratified manifold over which we work. This brings about the important operation of pushforward:
+The construction of \Cref{lem:f^-1} gives a functor which allows us to change the stratified manifold over which we work. This brings about the important operation of pushforward:
 
@@
 \begin{remark}\label{rem:fh_pushforward_functorial}
-    As was the case with the bar construction the equivalence of \cref{thm:fh_pushforward}, comes about through an argument about a final functor, this means that, through \cref{rem:fin_equiv_natural} there is even an equivalence between functors
+    As was the case with the bar construction the equivalence of \Cref{thm:fh_pushforward}, comes about through an argument about a final functor, this means that, through \Cref{rem:fin_equiv_natural} there is even an equivalence between functors
     %
@@
     %
-    By \cref{prop:disk1bor=assocRL} we know that this data defines an $\mathsf{Assoc^{RL}}$-algebra in $\catC$ whose right module, algebra and left module are exactly $F(M_-)$, $F(M_0 \times \mathbb{R})$ and $F(M_+)$.
-Further using \cref{prop:barconst=intinterval} we have
+    By \Cref{prop:disk1bor=assocRL} we know that this data defines an $\mathsf{Assoc^{RL}}$-algebra in $\catC$ whose right module, algebra and left module are exactly $F(M_-)$, $F(M_0 \times \mathbb{R})$ and $F(M_+)$.
+Further using \Cref{prop:barconst=intinterval} we have
     %
@@
 In this section we describe a result that clearly uses the stratified structure, and quantifies some additional information it can encode.
-It is a classification statement about disk algebras whose structure $\mathsf{D}_{d \subset n}^*$ is provided by \cref{def:framed_d_under_n_structure}.
-%We will, in a roundabout way, recover this result in \cref{ch:classif_defect_mfld}, but here we state it in the original form.
+It is a classification statement about disk algebras whose structure $\mathsf{D}_{d \subset n}^*$ is provided by \Cref{def:framed_d_under_n_structure}.
+%We will, in a roundabout way, recover this result in \Cref{ch:classif_defect_mfld}, but here we state it in the original form.
 
@@
     The above theorem is a slight generalization of, and heavily relies on, the proof of the higher Deligne conjecture on Hochschild cohomology as in \cite[sec.5.3]{lurie_ha}.
-Thus, from \cref{prop:framed_ndisk=En}, we know that it is very important to the theorem to work with framed disks since these are the ones that reproduce the $\mathbb{E}_n$-algebras of the higher Deligne conjecture.
+Thus, from \Cref{prop:framed_ndisk=En}, we know that it is very important to the theorem to work with framed disks since these are the ones that reproduce the $\mathbb{E}_n$-algebras of the higher Deligne conjecture.
 The proof of the proposition is not easily generalizable to other tangential structures.
@@
 all objects that act on $B$ factor through the action of the center $\mathsf{Z}(B)$ on $B$.
-Keeping this in mind, we see that, informally, \cref{thm:classif_disk_d_under_n*_alg} is saying that the structure of coupling the defect algebra $B$ to the bulk algebra $A$ is by giving $B$ a suitable module structure over $A$.
+Keeping this in mind, we see that, informally, \Cref{thm:classif_disk_d_under_n*_alg} is saying that the structure of coupling the defect algebra $B$ to the bulk algebra $A$ is by giving $B$ a suitable module structure over $A$.
 The complication then lies in proving what this suitable module structure is.

### 2024-03-15 sections/1stratified.tex

--- 2024-03-15 sections/1stratified.tex
@@
     %
-    The depth of $X$, $\mathsf{dpt} (X)$, in general is the supremum of the depths over all points. Just as with dimension, the convention is that $\mathsf{dpt}(\emptyset) = -1$.
+    The depth of $X$, $\mathsf{dpt} (X)$, in general, is the supremum of the depths over all points. Just as with dimension, the convention is that $\mathsf{dpt}(\emptyset) = -1$.
 \end{definition}
@@
     where we abbreviated $(\bstr\to\bsc)\in\mathsf{RFib}_{\bsc}$ to $\bstr$.
-Similarly the ordinary category $\mfld[r](\bstr)$ of $\bstr$-manifolds is the further pullback along the inclusion $\mfld[r]\to\mfld$.
+Similarly, the ordinary category $\mfld[r](\bstr)$ of $\bstr$-manifolds is the further pullback along the inclusion $\mfld[r]\to\mfld$.
 \end{definition}
@@
 \begin{remark}
-    \Cref{thm:decom_strat_man} is the analogue of handle decompositions for smooth manifolds.
+    \Cref{thm:decom_strat_man} is the analogue of handle decomposition for smooth manifolds.
 Namely, any compact, smooth manifold can be obtained by handle decomposition, and non-compact smooth manifolds are obtained by sequential colimits of finitary (including compact) smooth manifolds.
@@
     Insisting that tangential structures be \emph{right fibrations} over $\bsc$, as opposed to simply $\infty$-categories over it as, e.g., in \cite{ayala2020factorization}, leads to technical issues that lead to our over-simplified notation due to the property of being a right fibration not being invariant under equivalence.
-For instance, when $G=\ast$, so that $\mathsf{D}^\ast_n$ constrols framed $n$-manifolds, the map $BG=\ast\to \mathsf{BO}(n)\simeq\mathsf{D}_n$ is not a right fibration, owing to the observation that right fibrations of Kan complexes are Kan fibrations, and these, when surjective on objects, are epimorphisms.
-On the other hand, $B\ast=\ast\simeq (\mathsf{D}_n)_{/\mathbb{R}^n}$ since over-$\infty$-groupoids are contractible (\cite[018Y]{lurie_kerodon}), but $(\mathsf{D}_n)_{/\mathbb{R}^n}\to \mathsf{D}_n$ \emph{is} a right fibration since it is a projection from an over-$\infty$-category (\cite[018F]{lurie_kerodon}, \cite{joyal}).
+For instance, when $G=\ast$, so that $\mathsf{D}^\ast_n$ controls framed $n$-manifolds, the map $BG=\ast\to \mathsf{BO}(n)\simeq\mathsf{D}_n$ is not a right fibration, owing to the observation that right fibrations of Kan complexes are Kan fibrations, and these, when surjective on objects, are epimorphisms.
+On the other hand, $B\ast=\ast\simeq (\mathsf{D}_n)_{/\mathbb{R}^n}$ since over-$\infty$-groupoids are contractible (\cite[\href{https://kerodon.net/tag/018Y}{018Y}]{lurie_kerodon}), but $(\mathsf{D}_n)_{/\mathbb{R}^n}\to \mathsf{D}_n$ \emph{is} a right fibration since it is a projection from an over-$\infty$-category (\cite[\href{https://kerodon.net/tag/018F}{018F}]{lurie_kerodon}, \cite{joyal}).
 Moreover, $\mathsf{D}_n\hookrightarrow \bsc$ is a right fibration since this full $\infty$-subcategory is trivially a sieve, so the composition $(\mathsf{D}_n)_{/\mathbb{R}^n}\to \bsc$ is a right fibration as well.

### 2024-03-15 sections/4gluing_alt.tex
Moved 4gluing_alt.tex file.

--- 2024-03-14 4gluing_alt.tex
@@
 
-\begin{proof}[Proof of \cref{thm:gluing_lcfas}]
+\begin{proof}[Proof of \cref{cor:gluing_falgs}]
     We will first focus on the case of factorization algebras and prove the statement of \cref{cor:gluing_falgs}. Moreover, because of \cref{cor:disk_alg=falg}, this means that we will focus on $
@@
     which is exactly the collar-gluing property extended to the level of morphisms. This shows the equivalence at the level of factorization algebras.
+\end{proof}
 
+\begin{proof}[Proof of \cref{thm:gluing_lcfas}]
+    In the case that all $\infty$-categoies involved are locally constant we will extend the previous proof to provide the equivalence.
 Since we know that restriction does not destroy local constancy, extending the result to the case of locally constant factorization algebras simply requires us to show that the gluing $\gamma$ also preserves this property.
@@
 The only thing that we need to check is that through one inductive step the equivalences remain compatible.
+
     Specifically, by compatibility here we mean that there is a commutative diagram

### 2024-03-15 sections/2homology.tex

@@
 \begin{remark}
-    Because of \Cref{rem:disk_b=disk_bsc}, the above construction works for manifolds with any general $\bstr$-structure, with no further requirements on the constructible bundle $f$.
+    Because of \cref{rem:disk_b=disk_bsc}, the above construction works for manifolds with any general $\bstr$-structure, with no further requirements on the weakly constructible bundle $f$.
 \end{remark}

### 2024-03-15 sections/2homology.tex
cref -> Cref

@@
 \begin{remark}
-    Because of \cref{rem:disk_b=disk_bsc}, the above construction works for manifolds with any general $\bstr$-structure, with no further requirements on the weakly constructible bundle $f$.
+    Because of \Cref{rem:disk_b=disk_bsc}, the above construction works for manifolds with any general $\bstr$-structure, with no further requirements on the weakly constructible bundle $f$.
 \end{remark}

### 2024-03-15 sections/3algebras.tex
cref -> Cref

@@
 This result is immensely helpful in relating factorization algebras to results in the area of disk algebras.
-We will see one such example in \cref{ch:gluing_disk_alg}.
+We will see one such example in \Cref{ch:gluing_disk_alg}.
 
@@
 By the definition of $\csheaves[W](\mfld_{/M}, \catC)$, this means that the restriction of $\int F$ to $\mathsf{Fun}(\mfld[r]_{/M}, \catC)$ satisfies the cosheaf property for every Weiss sieve $\mathscr{U} \subset (\mfld[r]_{/M})_{/e}$, where $e:N \xhookrightarrow{} M$ is an open embedding.
-Here we notice that for the Weiss property to even make sense, we are implicitly using \cref{lem:double_slice}
+Here we notice that for the Weiss property to even make sense, we are implicitly using \Cref{lem:double_slice}
 
@@
     %
-    for each covering sieve $\mathscr{U}$. Since we aren't actually trying to get the value of these colimits we can rewrite \cref{eq:pointwiseKan} into the idiosyncratic form
+    for each covering sieve $\mathscr{U}$. Since we aren't actually trying to get the value of these colimits we can rewrite \Cref{eq:pointwiseKan} into the idiosyncratic form
     %
@@
     %
-    which is easier to compare to \cref{eq:cosheaf_colim_relative}.
-Using the fact that $\disk[r]_{/M} \xrightarrow{} \disk_{/M}$ is a final functor, which is a consequence of \cite[prop.2.22]{aft_fhstrat}, and the equivalences of \cref{lem:double_slice} we can rewrite \cref{eq:idiosync_form} further into
+    which is easier to compare to \Cref{eq:cosheaf_colim_relative}.
+Using the fact that $\disk[r]_{/M} \xrightarrow{} \disk_{/M}$ is a final functor, which is a consequence of \cite[prop.2.22]{aft_fhstrat}, and the equivalences of \Cref{lem:double_slice} we can rewrite \Cref{eq:idiosync_form} further into
     %
@@
     %
-    Denoting the functor $\mfld[r]_{/N} \simeq (\mfld[r]_{/M})_{/e} \xrightarrow{} \mfld[r]_{/M} \xrightarrow{} \mfld_{/M} \xrightarrow{\int F} \catC$ by $K_F$ and comparing with \cref{eq:cosheaf_colim_relative} we need to show
+    Denoting the functor $\mfld[r]_{/N} \simeq (\mfld[r]_{/M})_{/e} \xrightarrow{} \mfld[r]_{/M} \xrightarrow{} \mfld_{/M} \xrightarrow{\int F} \catC$ by $K_F$ and comparing with \Cref{eq:cosheaf_colim_relative} we need to show
     %
@@
 
-From the proof of \cref{prop:fh_disk_to_lcfa} it is easy to see that we can make a similar statement for ordinary factorization algebras too:
+From the proof of \Cref{prop:fh_disk_to_lcfa} it is easy to see that we can make a similar statement for ordinary factorization algebras too:
 
@@
     %
-    one for each $(U \xhookrightarrow{} M) \in \mfld[r]_{/M}$, which preserve the multiplicative structure (see \cref{cd:fa_morphisms}).
+    one for each $(U \xhookrightarrow{} M) \in \mfld[r]_{/M}$, which preserve the multiplicative structure (see \Cref{cd:fa_morphisms}).
 Since $F$ is a locally constant factorization algebra the functor
@@
 \begin{remark}
-    A version of \cref{thm:disk_alg=lcfa} was proven as \cite[thm.6]{gtz2014} in the case of smooth manifolds.
+    A version of \Cref{thm:disk_alg=lcfa} was proven as \cite[thm.6]{gtz2014} in the case of smooth manifolds.
 The proof there, however, made crucial use of choosing a Riemannian metric on the manifold and constructing geodesically convex neighborhoods.
@@
     We follow the proof of \cite[cor.2.33]{aft_fhstrat}.
-Using \cref{rem:disk_b=disk_bsc}, the forgetful functor from the slice $\infty$-operad, which is a map of $\infty$-operads, is what will provide the equivalence
+Using \Cref{rem:disk_b=disk_bsc}, the forgetful functor from the slice $\infty$-operad, which is a map of $\infty$-operads, is what will provide the equivalence
     %
@@
 
-The results of \cref{thm:disk_alg=lcfa} and \cref{cor:disk_alg=falg} can also be seen as lowering the amount of data that is necessary to say that we have defined a factorization algebra on a stratified manifold.
+The results of \Cref{thm:disk_alg=lcfa} and \Cref{cor:disk_alg=falg} can also be seen as lowering the amount of data that is necessary to say that we have defined a factorization algebra on a stratified manifold.
 There is a similar, but slightly weaker result by \cite{cg2016}, which nonetheless works for all Hausdorff topological spaces.
@@
 \begin{remark}
-    The proof of \cref{thm:fa_from_basis} can be found in \cite[ch.7.2]{cg2016}, and we will not reproduce it here.
+    The proof of \Cref{thm:fa_from_basis} can be found in \cite[ch.7.2]{cg2016}, and we will not reproduce it here.
 The target category there is the category of chain complexes, but it holds more generally in $\catC$ by considering simplicial objects and their geometric realizations (which exist by the colimit assumption on $\catC$) instead.
 
-    As mentioned, in the stratified manifold case, this is an easy corollary of the proof of \cref{prop:fh_disk_to_lcfa}, where we show that taking all disks as the Weiss cover of choice reproduces the result that we would have gotten with any other Weiss cover.
-It is important to point out though that disks are not necessarily closed under intersections, which means that we don't have the opposite implication, and the methods to prove \cref{prop:fh_disk_to_lcfa} are necessary.
+    As mentioned, in the stratified manifold case, this is an easy corollary of the proof of \Cref{prop:fh_disk_to_lcfa}, where we show that taking all disks as the Weiss cover of choice reproduces the result that we would have gotten with any other Weiss cover.
+It is important to point out though that disks are not necessarily closed under intersections, which means that we don't have the opposite implication, and the methods to prove \Cref{prop:fh_disk_to_lcfa} are necessary.
 \end{remark}
@@
 \begin{corollary}\label{cor:pushforward_for_lc}
-    Let $f: M \xrightarrow{} N$ be a constructible bundle of stratified manifolds. Then the pushforward functor for factorization homology of \cref{thm:fh_pushforward} serves as a pushforward
+    Let $f: M \xrightarrow{} N$ be a constructible bundle of stratified manifolds. Then the pushforward functor for factorization homology of \Cref{thm:fh_pushforward} serves as a pushforward
     %
@@
     %
-    by using \cref{thm:disk_alg=lcfa}.
+    by using \Cref{thm:disk_alg=lcfa}.
 \end{corollary}
@@
 \begin{lemma}\label{lem:ff_functor_to_refinement}
-    Let $u: X \rightarrow \hat{X}$ be the morphism of \cref{ex:forget_strat} that forgets the stratification.
+    Let $u: X \rightarrow \hat{X}$ be the morphism of \Cref{ex:forget_strat} that forgets the stratification.
     The functor $u_*: \lcfa_{X} (\catC) \rightarrow \lcfa_{\hat{X}} (\catC)$ has a fully faithful left adjoint.
@@
 \begin{remark}
-    The conditions we imposed on $\catC$ allowed us, in \cref{rem:sym_mon_inheritance}, to inherit a symmetric monoidal structure on the $\infty$-categories of factorization algebras of all varieties.
+    The conditions we imposed on $\catC$ allowed us, in \Cref{rem:sym_mon_inheritance}, to inherit a symmetric monoidal structure on the $\infty$-categories of factorization algebras of all varieties.
 It also allowed us to inherit the existence of colimits.
@@
 
-    It is not hard to check that the above also holds for the example of factorization algebras on topological spaces, by using \cref{thm:fa_from_basis}.
+    It is not hard to check that the above also holds for the example of factorization algebras on topological spaces, by using \Cref{thm:fa_from_basis}.
 However, we'll focus on manifolds, in which case, the construction from above immediately works since we now have to do it for $\disk[r]_{/X}$ instead of $\mfld[r]_{/X}$.
@@
 The equivalence proven there is for the case of smooth manifolds and relies on the local proof of \cite{lurie_ha} for $\mathbb{R}^n$.
-Using \cref{thm:disk_alg=lcfa}, the statement is implied by the fact that there is an equivalence of $\infty$-operads
+Using \Cref{thm:disk_alg=lcfa}, the statement is implied by the fact that there is an equivalence of $\infty$-operads
     %
@@
 \begin{proof}
-    The proof of existence of the functor goes along the same lines as the proof of \cref{prop:exp_of_products} because of \cref{thm:disk_alg=lcfa}.
-The thing to take into account is that the projection maps are both, trivially, constructible bundles so by \cref{cor:pushforward_for_lc}, pushing forward by them yields locally constant factorization algebras again.
+    The proof of existence of the functor goes along the same lines as the proof of \Cref{prop:exp_of_products} because of \Cref{thm:disk_alg=lcfa}.
+The thing to take into account is that the projection maps are both, trivially, constructible bundles so by \Cref{cor:pushforward_for_lc}, pushing forward by them yields locally constant factorization algebras again.
 This combined with the fact that for any $\infty$-operads $\mathscr{O}$, $\mathscr{O}'$ and $\mathscr{C}$ we have an equivalence
@@
 
-    One way to show the equivalence is to use factorization homology, as in \cref{thm:disk_alg=lcfa}, to write a locally constant factorization algebra as $\int_{-} A \in \lcfa_{X \times Y} (\catC)$.
-Then using the Fubini theorem \cite[cor.2.29]{aft_fhstrat}\footnote{The notation used in the citation is technically abusive because factorization homology is evaluating lower dimensional manifolds, but it is clear that this is to be understood exactly as the evaluation of the pushforward factorization algebra on the lower dimensional manifold (see \cref{rem:fh_is_pushingforward}).} for factorization homology we get essential surjectivity because there are equivalences
+    One way to show the equivalence is to use factorization homology, as in \Cref{thm:disk_alg=lcfa}, to write a locally constant factorization algebra as $\int_{-} A \in \lcfa_{X \times Y} (\catC)$.
+Then using the Fubini theorem \cite[cor.2.29]{aft_fhstrat}\footnote{The notation used in the citation is technically abusive because factorization homology is evaluating lower dimensional manifolds, but it is clear that this is to be understood exactly as the evaluation of the pushforward factorization algebra on the lower dimensional manifold (see \Cref{rem:fh_is_pushingforward}).} for factorization homology we get essential surjectivity because there are equivalences
     %
@@
     between objects of $\catC$.
-As argued in the proof of \cref{thm:disk_alg=lcfa}, these equivalences are natural in the open set variables, which means that they rise to equivalences at the level of locally constant factorization algebras.
+As argued in the proof of \Cref{thm:disk_alg=lcfa}, these equivalences are natural in the open set variables, which means that they rise to equivalences at the level of locally constant factorization algebras.
 In fact, looking at the proof of \cite[thm.2.25]{aft_fhstrat}, which is what underlies the construction of the above equivalences, we see that they arise from an argument about a final functor.
-By \cref{rem:fin_equiv_natural} this means that the equivalences are actually natural in the algebra variable, so it is immediate that the equivalences of individual locally constant factorization algebras lift to a full equivalence of $\infty$-categories.
+By \Cref{rem:fin_equiv_natural} this means that the equivalences are actually natural in the algebra variable, so it is immediate that the equivalences of individual locally constant factorization algebras lift to a full equivalence of $\infty$-categories.
 \end{proof}
@@
     Consider a unital, (homotopy) associative algebra $A$ in the category $\catC$.
-For a first pass we use \cref{thm:fa_from_basis} to construct a factorization algebra out of this data.
+For a first pass we use \Cref{thm:fa_from_basis} to construct a factorization algebra out of this data.
 We first check that the disks $\disk[r]_{/\mathbb{R}}$ of $\mathbb{R}$ form a factorizing basis.
 This is true since the disks are always a basis for any manifold, they are factorizing since we have all disjoint unions, and they are closed under finite intersections because the disks of $\mathbb{R}$ are intervals.
-Therefore, by \cref{thm:fa_from_basis}, we need only assign values to these.
+Therefore, by \Cref{thm:fa_from_basis}, we need only assign values to these.
 Given any disk $U$ we assign the same value, $F_A(U) := A$.
@@
 At this point we have constructed a prefactorization algebra on $\mathbb{R}$.
-To use \cref{thm:fa_from_basis} we need to first check the Weiss cosheaf condition.
-But because intervals are closed under finite intersections the \v{C}ech nerve definition of \cref{rem:check_nerve} makes this easy; the simplicial object $\cech_{\bullet}(\disk[r]_{/\mathbb{R}}, F_A)$ in all degrees will be a coproduct of copies of $A$.
+To use \Cref{thm:fa_from_basis} we need to first check the Weiss cosheaf condition.
+But because intervals are closed under finite intersections the \v{C}ech nerve definition of \Cref{rem:check_nerve} makes this easy; the simplicial object $\cech_{\bullet}(\disk[r]_{/\mathbb{R}}, F_A)$ in all degrees will be a coproduct of copies of $A$.
 Thus, $F_A$ is indeed a $\disk[r]_{/\mathbb{R}}$-factorization algebra and can be extended to a factorization algebra on $\mathbb{R}$.
@@
 An alternative is to get rid of the property of being closed under finite intersections altogether.
-It turns out, because of \cref{thm:disk_alg=lcfa}, that this is indeed possible, and that we can always stick to using disks even in the most general situations.
+It turns out, because of \Cref{thm:disk_alg=lcfa}, that this is indeed possible, and that we can always stick to using disks even in the most general situations.
 
@@
 From this data we will construct a locally constant factorization algebra $F_{(M, A)}$ on the stratified space $\hoint$.
-Considering \cref{con:lcfas_on_R} and the open embedding $\mathbb{R} \cong \mathbb{R}_{>0} \xhookrightarrow{} \hoint$, we will choose the restriction to be $F_{(M,A)}|_{\mathbb{R}} = F_A$, i.e.
-any disk that doesn't include the point $0 \in \hoint$, we regard as a disk of $\mathbb{R}$ through the given map, and we assign the value $A$ to it like in the \cref{con:lcfas_on_R}.
+Considering \Cref{con:lcfas_on_R} and the open embedding $\mathbb{R} \cong \mathbb{R}_{>0} \xhookrightarrow{} \hoint$, we will choose the restriction to be $F_{(M,A)}|_{\mathbb{R}} = F_A$, i.e.
+any disk that doesn't include the point $0 \in \hoint$, we regard as a disk of $\mathbb{R}$ through the given map, and we assign the value $A$ to it like in the \Cref{con:lcfas_on_R}.
 This leaves us only with the stratified disks $U_*$ that contain the point $0 \in \hoint$.
@@
 \begin{proof}
-    The proof goes along the same lines as the proof of \cref{prop:R_gives_E1}.
+    The proof goes along the same lines as the proof of \Cref{prop:R_gives_E1}.
 We can find the module by evaluating on $\hoint$, and we can find the algebra by evaluating on $\hoint \setminus \{ 0 \} \cong \mathbb{R}$, as a specified stratum of $\hoint$.
@@
 \begin{remark}\label{rem:left_or_right_module}
-    The fact that we chose left modules to provide the data in \cref{prop:hoint_gives_modules}, does not play much of a role because a left module is exactly a right module of the opposite algebra, giving $\mathsf{LMod}(\catC) \simeq \mathsf{RMod}(\catC)$.
+    The fact that we chose left modules to provide the data in \Cref{prop:hoint_gives_modules}, does not play much of a role because a left module is exactly a right module of the opposite algebra, giving $\mathsf{LMod}(\catC) \simeq \mathsf{RMod}(\catC)$.
 Where the distinction comes up, is if we want to fix the $\mathbb{E}_1$-algebra away from $0 \in \hoint$ beforehand.
@@
 
-It's not hard to extend \cref{con:lcfas_on_R} and \cref{con:lcfas_on_hoint} to the closed interval $[-1,1]$ by hand, but through \cref{thm:disk_alg=lcfa} we can see that \cref{prop:disk1bor_over_int=ORL} and \cref{prop:env_ORL=env_assocRL} already do all the necessary work.
+It's not hard to extend \Cref{con:lcfas_on_R} and \Cref{con:lcfas_on_hoint} to the closed interval $[-1,1]$ by hand, but through \Cref{thm:disk_alg=lcfa} we can see that \Cref{prop:disk1bor_over_int=ORL} and \Cref{prop:env_ORL=env_assocRL} already do all the necessary work.
 
@@
 \begin{remark}
-    Another perspective on why all of these constructions look the way they do is provided by \cref{lem:disk/M_to_disk}. It applies in all of the above cases, namely:
+    Another perspective on why all of these constructions look the way they do is provided by \Cref{lem:disk/M_to_disk}. It applies in all of the above cases, namely:
     %
@@
 In this section we want to describe locally constant factorization algebras on Euclidean spaces $\mathbb{R}^n$.
-By \cref{lem:disk/M_to_disk} we can hope for an $\infty$-category of basics such that we simplify the situation down to $\disk (\bstr)$-algebras.
+By \Cref{lem:disk/M_to_disk} we can hope for an $\infty$-category of basics such that we simplify the situation down to $\disk (\bstr)$-algebras.
 In fact, since $\mathbb{R}^n$ is frameable an $\infty$-category of basics that we can choose is $\mathsf{D}_n^* \simeq * \xrightarrow{\{ \mathbb{R}^n\}} \bsc$.
@@
 \begin{proof}
-    With our setup, thanks to \cref{thm:disk_alg=lcfa} and \cref{lem:disk/M_to_disk}, it is sufficient to show that there is an equivalence of $\infty$-operads
+    With our setup, thanks to \Cref{thm:disk_alg=lcfa} and \Cref{lem:disk/M_to_disk}, it is sufficient to show that there is an equivalence of $\infty$-operads
     %
@@
 \begin{remark}
-    We already encountered the $n=1$ version of the proposition above when we discussed locally constant factorization algebras on the open interval in \cref{prop:R_gives_E1}, and the construction there gives us an intuition about how to actually construct the locally constant factorization algebra from the data of the $\mathbb{E}_n$-algebra.
+    We already encountered the $n=1$ version of the proposition above when we discussed locally constant factorization algebras on the open interval in \Cref{prop:R_gives_E1}, and the construction there gives us an intuition about how to actually construct the locally constant factorization algebra from the data of the $\mathbb{E}_n$-algebra.
 The theorem formalizes that this assignment is, in fact, an equivalence.
@@
 That is, we know that given a locally constant factorization algebra $F$ on $\mathbb{R}^n$ we can restrict it to any open subset like, for example, $\mathbb{R}^n \setminus \{ 0 \} \cong S^{n-1} \times \mathbb{R}$ to get another locally constant factorization algebra $F|_{S^{n-1} \times \mathbb{R}}$.
-By \cref{prop:exp_of_products_lc} we know that $F|_{S^{n-1} \times \mathbb{R}} \in \lcfa_{\mathbb{R}} (\lcfa_{S^{n-1}} (\catC))$, so that in particular it is an $\mathbb{E}_1$-algebra.
-If we pushforward to $\mathbb{R}$, by the discussion at \cref{rem:fh_is_pushingforward} we could denote the resulting $\mathbb{E}_1$-algebra by \footnote{We again refer the reader to \cref{rem:fh_is_pushingforward} for a reason why this notation is good.}
+By \Cref{prop:exp_of_products_lc} we know that $F|_{S^{n-1} \times \mathbb{R}} \in \lcfa_{\mathbb{R}} (\lcfa_{S^{n-1}} (\catC))$, so that in particular it is an $\mathbb{E}_1$-algebra.
+If we pushforward to $\mathbb{R}$, by the discussion at \Cref{rem:fh_is_pushingforward} we could denote the resulting $\mathbb{E}_1$-algebra by \footnote{We again refer the reader to \Cref{rem:fh_is_pushingforward} for a reason why this notation is good.}
     %
@@
     %
-    This result goes towards an explanation of the appearance of factorization homology over higher spheres in the classification statement of \cref{thm:classif_disk_d_under_n*_alg}.
+    This result goes towards an explanation of the appearance of factorization homology over higher spheres in the classification statement of \Cref{thm:classif_disk_d_under_n*_alg}.
 \end{remark}
 
-We can view a Euclidean space $\mathbb{R}^{m+n}$ as a product space $\mathbb{R}^m \times \mathbb{R}^n$, in which case \cref{prop:exp_of_products_lc} specializes to give the famous result of Dunn additivity \cite{dunn1988} which can be found in the following form in \cite{lurie_ha}:
+We can view a Euclidean space $\mathbb{R}^{m+n}$ as a product space $\mathbb{R}^m \times \mathbb{R}^n$, in which case \Cref{prop:exp_of_products_lc} specializes to give the famous result of Dunn additivity \cite{dunn1988} which can be found in the following form in \cite{lurie_ha}:
 
@@
 \begin{remark}
-    The proof of \cref{prop:exp_of_products_lc}, when specialized to ordinary manifolds, as given in \cite{ginot2015} actually depends on Dunn additivity to work, however the proof presented above and the one in \cite{lurie_ha} are independent.
+    The proof of \Cref{prop:exp_of_products_lc}, when specialized to ordinary manifolds, as given in \cite{ginot2015} actually depends on Dunn additivity to work, however the proof presented above and the one in \cite{lurie_ha} are independent.
 \end{remark}

### 2024-03-15 sections/4gluing.tex
cref -> Cref

@@
 We want to examine what we can say about the behavior of this $\infty$-category under collar-gluings in the manifold variable.
-Our discussion will be in terms of disk algebras $\alg{\disk_{/M}} (\catC)$, but using \cref{thm:disk_alg=lcfa} there is no loss at all.
+Our discussion will be in terms of disk algebras $\alg{\disk_{/M}} (\catC)$, but using \Cref{thm:disk_alg=lcfa} there is no loss at all.
 
@@
 \begin{corollary}\label{cor:fbar_func_discrete}
-    Taking only the first part of the proof of \cref{lem:fbar_func} it is immediate that in the setting of $\mfld[r]_{/M}$ there is also a functor
+    Taking only the first part of the proof of \Cref{lem:fbar_func} it is immediate that in the setting of $\mfld[r]_{/M}$ there is also a functor
     %
@@
 
-\begin{proof}[Proof of \cref{thm:gluing_alg_disk/M}]
-    The data of a collar-gluing provides open embeddings $M_0 \times \mathbb{R} \xhookrightarrow{} M_-$ and $M_0 \times \mathbb{R} \xhookrightarrow{} M_+$, where $M_-$, $M_0$ and $M_+$ have the usual meanings as in \cref{def:collar-gluing}.
+\begin{proof}[Proof of \Cref{thm:gluing_alg_disk/M}]
+    The data of a collar-gluing provides open embeddings $M_0 \times \mathbb{R} \xhookrightarrow{} M_-$ and $M_0 \times \mathbb{R} \xhookrightarrow{} M_+$, where $M_-$, $M_0$ and $M_+$ have the usual meanings as in \Cref{def:collar-gluing}.
 This can be used to construct the cospan of restriction functors $\alg{\disk_{/M_-}} (\catC) \rightarrow \alg{\disk_{/M_0 \times \mathbb{R}}} (\catC) \leftarrow \alg{\disk_{/M_+}} (\catC)$.
@@
     %
-    where $\bar{f}$ is the functor from \cref{lem:fbar_func}.
+    where $\bar{f}$ is the functor from \Cref{lem:fbar_func}.
 
     Our first order of business is to show that $\gamma$ actually even lands in $\alg{\disk_{/M}} (\catC)$, and not just $\mathsf{Fun}(\disk_{/M}, \catC)$.
-Since we have expressed the construction $A = \gamma(A_-, A_+)$ functorially, we can see that $A$ will inherit the structure of an algebra from the fact that factorization homology and the bar construction are symmetric monoidal functors (see \cref{lem:B_sym_mon} for the latter), together with \cref{lem:fbar_func} that lends this property to $\bar{f}$.
+Since we have expressed the construction $A = \gamma(A_-, A_+)$ functorially, we can see that $A$ will inherit the structure of an algebra from the fact that factorization homology and the bar construction are symmetric monoidal functors (see \Cref{lem:B_sym_mon} for the latter), together with \Cref{lem:fbar_func} that lends this property to $\bar{f}$.
 With that we have constructed a functor
@@
 In the rest of the calculations we crucially used the collar-gluing property of factorization homology.
-That this property continues to hold at the morphism level is a consequence of the fact that we made sure to elevate the statement of \cref{prop:barconst=intinterval} to the level of functors, together with the pushforward property which also holds functorially à la \cref{rem:fh_pushforward_functorial}.
+That this property continues to hold at the morphism level is a consequence of the fact that we made sure to elevate the statement of \Cref{prop:barconst=intinterval} to the level of functors, together with the pushforward property which also holds functorially à la \Cref{rem:fh_pushforward_functorial}.
 Namely, these provide equivalences of functors
@@
 
-Together with \cref{thm:disk_alg=lcfa} we immediately have the following corollary:
+Together with \Cref{thm:disk_alg=lcfa} we immediately have the following corollary:
 
@@
 
-Taking into account \cref{cor:disk_alg=falg} together with \cref{cor:fbar_func_discrete}, as well as the definition of factorization homology in the setting of the category $\disk[r]_{/M}$, the proof of \cref{thm:gluing_alg_disk/M} can be seen to clearly hold even in case of ordinary factorization algebras.
+Taking into account \Cref{cor:disk_alg=falg} together with \Cref{cor:fbar_func_discrete}, as well as the definition of factorization homology in the setting of the category $\disk[r]_{/M}$, the proof of \Cref{thm:gluing_alg_disk/M} can be seen to clearly hold even in case of ordinary factorization algebras.
 
@@
 \begin{example}\label{ex:reproduce_lcfas_on_interval}
-    With the ingredients we have introduced up to now, specifically in \cref{ssec:lcfa_on_ints}, we can do a nontrivial check of the gluing theorem.
+    With the ingredients we have introduced up to now, specifically in \Cref{ssec:lcfa_on_ints}, we can do a nontrivial check of the gluing theorem.
 This is because we can write a collar-gluing of the closed interval $[-1,1] \cong \left[-1,1\right) \coprod_{(-1,1)} \left(-1,1\right] \cong \mathbb{R}_{\geq 0} \coprod_{\mathbb{R}} \mathbb{R}_{\leq 0}$.
 We note here that we have written $\mathbb{R}_{\leq 0}$ and $\mathbb{R}_{\geq 0}$ to emphasize the maps forming the decomposition.
-At the level of unstructured objects these two are isomorphic (see also \cref{rem:left_or_right_module}).
+At the level of unstructured objects these two are isomorphic (see also \Cref{rem:left_or_right_module}).
 For this example, the theorem says that locally constant factorization algebras on the closed interval should be given by
@@
 But this is exactly the same as the description we gave in terms of an algebra with a left and a right module, i.e.
-an algebra over $\mathsf{Assoc^{RL}}$, in \cref{cor:lcfas_on_closed_int}.
+an algebra over $\mathsf{Assoc^{RL}}$, in \Cref{cor:lcfas_on_closed_int}.
 \end{example}
@@
 Let's denote the restriction functors that restrict to the first and the second component of the disjoint union $\mathbb{R} \sqcup \mathbb{R}$ by $|_1$ and $|_2$ respectively.
-Going back to \cref{eq:lcfas_on_S1_gluing}, the data of a locally constant factorization algebra on $S^1$ is equivalent to the data of two $\mathbb{E}_1$-algebras $A$ and $B$ such that their restrictions $A|_1 = B|_1$ and $A|_2 = B|_2$ agree.
+Going back to \Cref{eq:lcfas_on_S1_gluing}, the data of a locally constant factorization algebra on $S^1$ is equivalent to the data of two $\mathbb{E}_1$-algebras $A$ and $B$ such that their restrictions $A|_1 = B|_1$ and $A|_2 = B|_2$ agree.
 Since all of these are $\mathbb{E}_1$-algebras there are equivalences with the restrictions forming
@@
 Just as for the circle, higher spheres can also be described as a collar-gluing $S^n \cong \mathbb{R}^n \coprod_{S^{n-1} \times \mathbb{R}} \mathbb{R^n}$.
-Thus, we can iterate the procedure from \cref{ex:reproduce_lcfas_on_S1} to get the locally constant factorization algebras on all higher spheres.
+Thus, we can iterate the procedure from \Cref{ex:reproduce_lcfas_on_S1} to get the locally constant factorization algebras on all higher spheres.
 For example, for the two-sphere $S^2$ we have
@@
 \begin{example}\label{ex:cylinder_mobius_band}
-    In \cref{ch:classif_defect_mfld} we will see that fiber bundles are important for the classification of some stratified manifolds.
+    In \Cref{ch:classif_defect_mfld} we will see that fiber bundles are important for the classification of some stratified manifolds.
 Here we will look at line bundles over the circle as a toy example, namely, the cylinder $C$ and M\"obius band $M$.
 The cylinder, as a trivial fiber bundle, is isomorphic to the product space $S^1 \times \mathbb{R}$.
-By \cref{prop:exp_of_products_lc} together with the results of \cref{ex:reproduce_lcfas_on_S1}, locally constant factorization algebras on it are given by $\mathbb{E}_2$-algebras together with an $\mathbb{E}_1$-self-equivalence
+By \Cref{prop:exp_of_products_lc} together with the results of \Cref{ex:reproduce_lcfas_on_S1}, locally constant factorization algebras on it are given by $\mathbb{E}_2$-algebras together with an $\mathbb{E}_1$-self-equivalence
     %
@@
 
-    Switching our attention to the M\"obius band $M$, we can use a similar logic as in \cref{ex:reproduce_lcfas_on_S1} to find a collar gluing of $M$.
+    Switching our attention to the M\"obius band $M$, we can use a similar logic as in \Cref{ex:reproduce_lcfas_on_S1} to find a collar gluing of $M$.
 The pieces are the same as they would be for the cylinder, namely $M_- \cong M_+ \cong \mathbb{R}^2$, and $M_0 \times \mathbb{R} \cong \mathbb{R}^2 \sqcup \mathbb{R}^2$, but they are glued differently because of the twist.
-Using the notation from \cref{ex:reproduce_lcfas_on_S1} the diagram becomes
+Using the notation from \Cref{ex:reproduce_lcfas_on_S1} the diagram becomes
     %
@@
 
-    We should remark that the fact that we can take the opposite algebra in one direction only is a consequence of the Dunn additivity of \cref{prop:dunn_additivity}.
+    We should remark that the fact that we can take the opposite algebra in one direction only is a consequence of the Dunn additivity of \Cref{prop:dunn_additivity}.
 Without it, we wouldn't be able to combine the opposite algebra in one direction with the original algebra in the other direction into a well-defined algebra in two dimensions.

### 2024-03-15 sections/2homology.tex
ignore this for the moment

--- 2024-03-15 sections/2homology.tex
@@
 We will now recall the $\infty$-category of disk algebras with a chosen tangential structure valued in a symmetric monoidal $\infty$-category.
-First, recall Segal's category $\mathsf{Fin}_{\ast}$ of finite pointed sets and their maps.
-By abuse, we write $\mathsf{Fin}_\ast=\mathsf{N}(\mathsf{Fin}_\ast)$ for its nerve.
-Following \cite{lurie_ha}, we take the objects of $\mathsf{Fin}_{\ast}$ to be $\langle n\rangle=\{\ast,1,\dots,n\}$.
+First, consider, following \cite{lurie_ha}, the category $\mathsf{Fin}_\ast$ whose objects are the sets $\langle n\rangle=\{\ast,1,\dots,n\}$ and whose morphisms are functions that preserve the distinguished point $\ast$.
 For every $i\in\{1,\dots,n\}$ there is a map $\rho^i\colon\langle n\rangle\to\langle 1\rangle$ that sends $i$ to $1$ but is otherwise constant at $\ast\in\langle1\rangle$.
-A \emph{symmetric monoidal $\infty$-category} is, according to \cite[Definition 2.0.0.7]{lurie_ha}, a cocartesian fibration\footnote{A \emph{cocartesian fibration} (\cite[Definition 01T5]{lurie_kerodon}) $q\colon\mathscr{A}\to\mathscr{B}$ between simplicial sets is one such that every edge $f\colon\mathscr{A}_1$ is \emph{$q$-cocartesian}, that is, any horn of type $\Lambda^n_0\to\mathscr{A}$, $n\geq2$, whose restriction to $\{0<1\}$ is $f$, admits a filler if its projection to $\mathscr{B}$ admits a filler.} $\catC\to\mathsf{Fin}_\ast$ such that the maps the maps $\rho^i\colon\langle n\rangle\to\langle 1\rangle$, $1\leq i\leq n$, induce an equivalence $\catC_{\langle n\rangle}\simeq(\catC_{\langle 1\rangle})^{\times n}$ for every $n\geq0$, where $\catC_{x}$ is the fiber at $x$.
-We mostly abbreviate $\catC\to\mathsf{Fin}_\ast$ to $\catC$.
+A \emph{symmetric monoidal $\infty$-category} is, after \cite[Definition 2.0.0.7]{lurie_ha}, a cocartesian fibration\footnote{A \emph{cocartesian fibration} (\cite[Definition 01T5]{lurie_kerodon}) $q\colon\mathscr{A}\to\mathscr{B}$ between simplicial sets is one such that every edge $f\in\mathscr{A}_1$ is \emph{($q$-)cocartesian}, that is, any horn of type $\Lambda^n_0\to\mathscr{A}$, $n\geq2$, whose restriction to $\{0<1\}$ is $f$, admits a filler if its projection to $\mathscr{B}$ admits a filler.
+By (un)straightening, such a $q$ corresponds to a $\cat$-valued copresheaf $\mathscr{B}\to\cat$.} $\catC\to\mathsf{Fin}_\ast$ such that the maps $\rho^i\colon\langle n\rangle\to\langle 1\rangle$, $1\leq i\leq n$, induce an equivalence $\catC_{\langle n\rangle}\simeq(\catC_{\langle 1\rangle})^{\times n}$ for every $n\geq0$, where $\catC_{x}$ is the fiber at $x$.
+We have abbreviated $\mathsf{N}(\mathsf{Fin}_\ast)$ to $\mathsf{Fin}_\ast$, and will mostly abbreviate $\catC\to\mathsf{Fin}_\ast$ to $\catC$.
 
-The $\infty$-category $\mathsf{Fun}^{\otimes}(\catC,\mathscr{D})\subset\mathsf{Fun}_{/\mathsf{Fun}_\ast}(\catC,\mathscr{D})$ of \emph{symmetric monoidal functors} is the full sub-$\infty$-category of all the functor $\infty$-category on those functors that preserve cocartesian edges.
+The $\infty$-category $\mathsf{Fun}^{\otimes}(\mathscr{O},\catC)\subset\mathsf{Fun}_{/\mathsf{Fin}_\ast}(\mathscr{O},\catC)$ of \emph{symmetric monoidal functors} between symmetric monoidal $\infty$-categories $\mathscr{O}$, $\catC$ is the full sub-$\infty$-category of the $\infty$-category of functors over $\mathsf{Fin}_\ast$ generated by those functors that preserve cocartesian edges.
+Following \cite{aft_fhstrat}, we write
+\[
+    \alg{\mathscr{O}}(\mathscr{C})\coloneqq\mathsf{Fun}^{\otimes}(\mathscr{O},\mathscr{C})
+\]
+when $\mathscr{O}$, $\mathscr{C}$ are symmetric monoidal $\infty$-categories.
+
+More generally, an \emph{$\infty$-operad}, after \cite{lurie_ha}, is a map $\mathscr{C}\to\mathsf{Fin}_\ast$ which is only required to be a cocartesian fibration upon restricting to $\mathsf{Fin}_{\ast}^{\text{inrt}}\subset\mathsf{Fin}_\ast$, the subcategory of \emph{inert} morphisms $f\colon\langle m\rangle\to \langle n\rangle$ for which, by definition, $f^{-1}\{i\}$ is a singleton whenever $i\in\langle n\rangle^{\circ}\coloneqq\{1,\dots,n\}\subset\langle n\rangle$.
 

### 2024-03-15 sections/2homology.tex
ignore this for the moment

@@
 
-More generally, an \emph{$\infty$-operad}, after \cite{lurie_ha}, is a map $\mathscr{C}\to\mathsf{Fin}_\ast$ which is only required to be a cocartesian fibration upon restricting to $\mathsf{Fin}_{\ast}^{\text{inrt}}\subset\mathsf{Fin}_\ast$, the subcategory of \emph{inert} morphisms $f\colon\langle m\rangle\to \langle n\rangle$ for which, by definition, $f^{-1}\{i\}$ is a singleton whenever $i\in\langle n\rangle^{\circ}\coloneqq\{1,\dots,n\}\subset\langle n\rangle$.
+More generally, an \emph{$\infty$-operad} is a map $\catC\to\mathsf{Fin}_\ast$ that satisfies a generalisation of the properties of a symmetric monoidal $\infty$-category -- see \cite[Definition 2.1.1.10]{lurie_ha}.
 

### 2024-03-18 sections/3algebras.tex
Added comment on physical interpretation.

@@
 This technique is, at least presently, not extendable to the stratified case, but our proof above subverts the need for it.
+\end{remark}
+
+\begin{remark}
+    As noted at the beginning of \ss 2, the physical interpretation of this version of factorization homology is a way to take a spacetime $M$ and its local observables $A$, and construct \emph{some}, and typically not all, of the global observables.
+The previous \Cref{thm:disk_alg=lcfa} and \Cref{cor:disk_alg=falg} transfer this observation to factorization algebras, which aligns with the observation of \cite{cg2016} that the current version of factorization algebras can only deal with perturbative quantum field theory.
 \end{remark}

### 2024-03-18 sections/4gluing_alt.tex
Added comment on physical interpretation.

--- 2024-03-14 4gluing_alt.tex
@@
 Given a stratified manifold $M$, and a $\otimes$-presentable $\infty$-category $\catC$, we defined the $\infty$-category $\lcfa_M (\catC)$ of locally constant factorization algebras on $M$ valued in $\catC$.
-We also noticed, in \cref{thm:disk_alg=lcfa}, that factorization homology is involved in constructing these algebras from local data.
+We also noticed, in \Cref{thm:disk_alg=lcfa}, that factorization homology is involved in constructing these algebras from local data.
 This prompts us to ask if we can say something about the behavior of this $\infty$-category under collar-gluings in the manifold variable.
@@
     In the above lemma it is important that we stuck to the comparatively simple $\mfld[r]_{/M}$ instead of $\mfld_{/M}$.
-It is not immediately obvious how to deal with the higher morphisms in the latter, as can be seen from the form of \cref{cd:factorization_of_e}.
-The issues are related to the ones that appear in the construction of the pushforward functor \cref{thm:fh_pushforward}.
+It is not immediately obvious how to deal with the higher morphisms in the latter, as can be seen from the form of \Cref{cd:factorization_of_e}.
+The issues are related to the ones that appear in the construction of the pushforward functor \Cref{thm:fh_pushforward}.
 A simple case to ponder is an isotopy that maps one embedding of a disk in $M_- \setminus (M_0 \times \mathbb{R})$ to another one in $M_+ \setminus (M_0 \times \mathbb{R})$.
@@
 
-\begin{proof}[Proof of \cref{thm:gluing_lcfas}]
-    We will first focus on the case of factorization algebras and prove the statement of \cref{cor:gluing_falgs}. Moreover, because of \cref{cor:disk_alg=falg}, this means that we will focus on $
+\begin{proof}[Proof of \Cref{cor:gluing_falgs}]
+    We will first focus on the case of factorization algebras and prove the statement of \Cref{cor:gluing_falgs}. Moreover, because of \Cref{cor:disk_alg=falg}, this means that we will focus on $
     disk[r]_{/M}$-algebras.
 
-    The data of a collar-gluing provides open embeddings $M_0 \times \mathbb{R} \xhookrightarrow{} M_-$ and $M_0 \times \mathbb{R} \xhookrightarrow{} M_+$, where $M_-$, $M_0$ and $M_+$ have the usual meanings as in \cref{def:collar-gluing}.
+    The data of a collar-gluing provides open embeddings $M_0 \times \mathbb{R} \xhookrightarrow{} M_-$ and $M_0 \times \mathbb{R} \xhookrightarrow{} M_+$, where $M_-$, $M_0$ and $M_+$ have the usual meanings as in \Cref{def:collar-gluing}.
 This can be used to construct the cospan of restriction functors $\alg{\disk[r]_{/M_-}} (\catC) \rightarrow \alg{\disk[r]_{/M_0 \times \mathbb{R}}} (\catC) \leftarrow \alg{\disk[r]_{/M_+}} (\catC)$.
@@
     %
-    where $\bar{f}$ is the functor from \cref{lem:fbar_func}.
+    where $\bar{f}$ is the functor from \Cref{lem:fbar_func}.
 
     Our first order of business is to show that $\gamma$ actually even lands in $\alg{\disk[r]_{/M}} (\catC)$, and not just $\mathsf{Fun}(\disk[r]_{/M}, \catC)$.
-Since we have expressed the construction $A = \gamma(A_-, A_+)$ functorially, we can see that $A$ will inherit the structure of an algebra from the fact that factorization homology and the bar construction are symmetric monoidal functors (see \cref{lem:B_sym_mon} for the latter), together with \cref{lem:fbar_func} that lends this property to $\bar{f}$.
+Since we have expressed the construction $A = \gamma(A_-, A_+)$ functorially, we can see that $A$ will inherit the structure of an algebra from the fact that factorization homology and the bar construction are symmetric monoidal functors (see \Cref{lem:B_sym_mon} for the latter), together with \Cref{lem:fbar_func} that lends this property to $\bar{f}$.
 With that we have constructed a functor
@@
     which is exactly the collar-gluing property extended to the level of morphisms. This shows the equivalence at the level of factorization algebras.
+\end{proof}
 
+\begin{proof}[Proof of \Cref{thm:gluing_lcfas}]
+    In the case that all $\infty$-categoies involved are locally constant we will extend the previous proof to provide the equivalence.
 Since we know that restriction does not destroy local constancy, extending the result to the case of locally constant factorization algebras simply requires us to show that the gluing $\gamma$ also preserves this property.
@@
     Generically though, these pieces will not be disks again, so we can't simply inherit the local constancy property immediately.
-To alleviate this issue we make use of \cref{thm:decom_strat_man} which assures us that every manifold can be obtained by collar-gluings and sequential colimits if we start with disks.
+To alleviate this issue we make use of \Cref{thm:decom_strat_man} which assures us that every manifold can be obtained by collar-gluings and sequential colimits if we start with disks.
 In fact, since our largest manifold of interest is a disk, which is finitary, we only need collar-gluings, and not sequential colimits.
@@
 
-\begin{remark}
-    The simple case when the collar-gluing is a disjoint union, and the manifolds are smooth can also be found as \cite[ex.5.4.5.4]{lurie_ha}.
-\end{remark}
-
 \subsection{Some Examples of Gluing}
@@
     \begin{equation}
-        \lcfa_{S^1} (\catC) \simeq \aut (\alg{\mathbb{E}_1} (\catC)),
+        \lcfa_{S^1} (\catC) \simeq \mathsf{Aut} (\alg{\mathbb{E}_1} (\catC)),
     \end{equation}
@@
     \begin{equation}
-        \lcfa_{\mathbb{R}^2}(\catC) \bigtimes_{\lcfa_{S^1 \times \mathbb{R}}(\catC)} \lcfa_{\mathbb{R}^2}(\catC) \simeq \alg{\mathbb{E}_2}(\catC) \bigtimes_{\alg{\mathbb{E}_1}( \aut (\alg{\mathbb{E}_1} (\catC))) } \alg{\mathbb{E}_2} (\catC),
+        \lcfa_{\mathbb{R}^2}(\catC) \bigtimes_{\lcfa_{S^1 \times \mathbb{R}}(\catC)} \lcfa_{\mathbb{R}^2}(\catC) \simeq \alg{\mathbb{E}_2}(\catC) \bigtimes_{\alg{\mathbb{E}_1}( \mathsf{Aut} (\alg{\mathbb{E}_1} (\catC))) } \alg{\mathbb{E}_2} (\catC),
     \end{equation}
@@
 \begin{example}\label{ex:cylinder_mobius_band}
-    In \cref{ch:classif_defect_mfld} we will see that fiber bundles are important for the classification of some stratified manifolds.
+    In \Cref{ch:classif_defect_mfld} we will see that fiber bundles are important for the classification of some stratified manifolds.
 Here we will look at line bundles over the circle as a toy example, namely, the cylinder $C$ and M\"obius band $M$.
 The cylinder, as a trivial fiber bundle, is isomorphic to the product space $S^1 \times \mathbb{R}$.
-By \cref{prop:exp_of_products_lc} together with the results of \cref{ex:reproduce_lcfas_on_S1}, locally constant factorization algebras on it are given by $\mathbb{E}_2$-algebras together with an $\mathbb{E}_1$-self-equivalence
+By \Cref{prop:exp_of_products_lc} together with the results of \Cref{ex:reproduce_lcfas_on_S1}, locally constant factorization algebras on it are given by $\mathbb{E}_2$-algebras together with an $\mathbb{E}_1$-self-equivalence
     %
     \begin{align}
-        \lcfa_C (\catC) \simeq \aut_{\mathbb{E}_1} (\alg{\mathbb{E}_2} (\catC)).
+        \lcfa_C (\catC) \simeq \mathsf{Aut}_{\mathbb{E}_1} (\alg{\mathbb{E}_2} (\catC)).
     \end{align}
 
-    Switching our attention to the M\"obius band $M$, we can use a similar logic as in \cref{ex:reproduce_lcfas_on_S1} to find a collar gluing of $M$.
+    Switching our attention to the M\"obius band $M$, we can use a similar logic as in \Cref{ex:reproduce_lcfas_on_S1} to find a collar gluing of $M$.
 The pieces are the same as they would be for the cylinder, namely $M_- \cong M_+ \cong \mathbb{R}^2$, and $M_0 \times \mathbb{R} \cong \mathbb{R}^2 \sqcup \mathbb{R}^2$, but they are glued differently because of the twist.
-Using the notation from \cref{ex:reproduce_lcfas_on_S1} the diagram becomes
+Using the notation from \Cref{ex:reproduce_lcfas_on_S1} the diagram becomes
     %

### 2024-03-18 sections/4gluing_alt.tex
Improvements to one version of gluing proof.

@@
 \begin{proof}[Proof of \Cref{cor:gluing_falgs}]
-    We will first focus on the case of factorization algebras and prove the statement of \Cref{cor:gluing_falgs}. Moreover, because of \Cref{cor:disk_alg=falg}, this means that we will focus on $
-    disk[r]_{/M}$-algebras.
+    We will first focus on the case of factorization algebras and prove the statement of \Cref{cor:gluing_falgs}.
+Moreover, because of \Cref{cor:disk_alg=falg}, this means that we will focus on $\disk[r]_{/M}$-algebras.
 
@@
 The key point being that we consider the collar-gluings on all pieces in both orders to get all the necessary arrows.
+
+    \begin{multicols}{2}
+        \begin{figure}[H]
+            \centering
+            \includegraphics[width=5cm]{../images/extend_gluing.png}
+            \caption{Extending a collar-gluing.}
+            \label{fig:extend_gluing}
+        \end{figure}
+        %
+        The final point to check is that we have not limited ourselves by insisting to only consider collar-gluings which are inherited from ones on $M$.
+This is best shown in \Cref{fig:extend_gluing}.
+Namely, given the disk $V \xhookrightarrow{} M$, we can take a larger disk $V'$, which is guaranteed to exist from the fact that $M$ is a manifold.
+The figure then shows that given any collar-gluing of $V$ we can find one particular collar-gluing of $M$ that extends the one of $V$.
+Since $V'$ is a disk, the figure does not obscure any detail.
+    \end{multicols}
 \end{proof}

### 2024-03-18 sections/0intro.tex

@@
 %
-as well as its \cref{cor:disk_alg=falg} for the case of ordinary factorization algebras.
+as well as its \Cref{cor:disk_alg=falg} for the case of ordinary factorization algebras.
 These show that the $\infty$-operad governing factorization algebras can be taken to be the slice $\infty$-operad $\disk_{/M}$ (or $\disk[r]_{/M}$ for the ordinary case).
@@
 %
-which are both Quillen-equivalences in appropriate ways (\cite{joyal2007quasi,bergner2010survey}).
+which are both Quillen--equivalences in appropriate ways (\cite{joyal2007quasi,bergner2010survey}).
 In particular, we will not distinguish notationally the nerve of an ordinary category from the ordinary category itself.

### 2024-03-18 sections/1stratified.tex

@@
 \begin{example}
-    The open cone $\cone(S^k)$ on the $k$-sphere is canonically identified with $\mathbb{R}^{k+1}_*$, which is the stratified space with stratification given by the filtration $\{0\}\subset\mathbb{R}^{k+1}$ as in \cref{ex:strat_from_filtration}.
+    The open cone $\cone(S^k)$ on the $k$-sphere is canonically identified with $\mathbb{R}^{k+1}_*$, which is the stratified space with stratification given by the filtration $\{0\}\subset\mathbb{R}^{k+1}$ as in \Cref{ex:strat_from_filtration}.
 \end{example}
@@
 $C^0$ stratified spaces have an additional, related concept called depth.
-It plays a key role in describing these spaces.\footnote{For example, we said that \cref{thm:basics_give_basis}, as a definition, would be circular.
+It plays a key role in describing these spaces.\footnote{For example, we said that \Cref{thm:basics_give_basis}, as a definition, would be circular.
 One way to resolve this is by induction on depth since $\mathsf{dpt} (\mathbb{R}^n \times \cone(Z)) = \mathsf{dpt} (\cone(Z)) = \mathsf{dpt} (Z) + 1$} As the name suggests, it conveys information about how deep the stratification is.
@@
 The key realization is that the data which the map of spaces $B \rightarrow \mathsf{BO}(n)$ provided before was the data of a presheaf on $\mathsf{BO}(n)$, standing in as the $\infty$-category of basics with only one object $\mathbb{R}^n$.
-The analogous construction in the stratified case is to provide a presheaf on $\bsc$, which by \cref{rem:grothendieck_construction} is given by a right fibration over $\bsc$.
+The analogous construction in the stratified case is to provide a presheaf on $\bsc$, which by \Cref{rem:grothendieck_construction} is given by a right fibration over $\bsc$.
 

### 2024-03-18 sections/4gluing_alt.tex
Miniscule fix.

--- 2024-03-18 sections/4gluing_alt.tex
@@
 
+\begin{remark}
+    The simple case when the collar-gluing is a disjoint union, and the manifolds are smooth can also be found as \cite[ex.5.4.5.4]{lurie_ha}.
+\end{remark}
+
 \subsection{Some Examples of Gluing}
@@
     \begin{equation}
-        \lcfa_{S^1} (\catC) \simeq \mathsf{Aut} (\alg{\mathbb{E}_1} (\catC)),
+        \lcfa_{S^1} (\catC) \simeq \aut (\alg{\mathbb{E}_1} (\catC)),
     \end{equation}
@@
     \begin{equation}
-        \lcfa_{\mathbb{R}^2}(\catC) \bigtimes_{\lcfa_{S^1 \times \mathbb{R}}(\catC)} \lcfa_{\mathbb{R}^2}(\catC) \simeq \alg{\mathbb{E}_2}(\catC) \bigtimes_{\alg{\mathbb{E}_1}( \mathsf{Aut} (\alg{\mathbb{E}_1} (\catC))) } \alg{\mathbb{E}_2} (\catC),
+        \lcfa_{\mathbb{R}^2}(\catC) \bigtimes_{\lcfa_{S^1 \times \mathbb{R}}(\catC)} \lcfa_{\mathbb{R}^2}(\catC) \simeq \alg{\mathbb{E}_2}(\catC) \bigtimes_{\alg{\mathbb{E}_1}( \aut (\alg{\mathbb{E}_1} (\catC))) } \alg{\mathbb{E}_2} (\catC),
     \end{equation}
@@
 
-    From this example we can easily see that beyond the dimensionality $n$ of the space, which is locally kept track of as an $\mathbb{E}_n$-algebra, locally constant factorization algebras for the higher spheres also keep track of higher coherent (self-)equivalences, which imitate triangulations of the spheres.
+    From this example we can easily see that beyond the dimensionality $n$ of the space, which is locally kept track of as an $\mathbb{E}_n$-algebra, locally constant factorization algebras for the higher spheres also keep track of higher coherent (self-)equivalences, which imitate traingulations of the spheres.
 \end{example}
@@
     \begin{align}
-        \lcfa_C (\catC) \simeq \mathsf{Aut}_{\mathbb{E}_1} (\alg{\mathbb{E}_2} (\catC)).
+        \lcfa_C (\catC) \simeq \aut_{\mathbb{E}_1} (\alg{\mathbb{E}_2} (\catC)).
     \end{align}

### 2024-03-18 sections/5classification.tex
Miniscule changes.

@@
 Specifically we will focus on the case of stratified manifolds $M_{\Sigma}$, which are described by a smooth, $n$-dimensional manifold $M$ together with a distinguished smooth, properly embedded, $d$-dimensional submanifold $\Sigma \xhookrightarrow{} M$, such that $d < n$.
-In other words we are considering objects $M_{\Sigma} \in \mfld(\mathsf{D}_{d \subset n})$ as discussed in \cref{def:mfld_disk_dn}.
+In other words we are considering objects $M_{\Sigma} \in \mfld(\mathsf{D}_{d \subset n})$ as discussed in \Cref{def:mfld_disk_dn}.
 More general statements can be achieved by iterating the procedure and explicating the information of more defects, stratum by stratum, in the stratified manifold.
@@
 \begin{remark}\label{rem:disk_not_enough}
-    Having already considered the classification of disk algebras with $\mathsf{D}_{d \subset n}^*$-structure in \cref{thm:classif_disk_d_under_n*_alg}, one might wonder whether the classification we are after is already done by simply using the factorization homology functor, and porting over the classification of disk algebras to the setting of locally constant factorization algebras.
+    Having already considered the classification of disk algebras with $\mathsf{D}_{d \subset n}^*$-structure in \Cref{thm:classif_disk_d_under_n*_alg}, one might wonder whether the classification we are after is already done by simply using the factorization homology functor, and porting over the classification of disk algebras to the setting of locally constant factorization algebras.
 There are two issues with this direction of inquiry.
-One problem is that not all $\mathsf{D}_{d \subset n}$-manifolds are frameable since this is not even the case for smooth manifolds; framed disk algebras like in \cref{thm:classif_disk_d_under_n*_alg} can only evaluate framed stratified manifolds.
+One problem is that not all $\mathsf{D}_{d \subset n}$-manifolds are frameable since this is not even the case for smooth manifolds; framed disk algebras like in \Cref{thm:classif_disk_d_under_n*_alg} can only evaluate framed stratified manifolds.
 
@@
     which is induced by the forgetful functor $\disk_{/M} \rightarrow \disk(\bstr)$, but this functor will, in general, not be an equivalence.
-We can see this, for example, by using \cref{rem:disk_b=disk_bsc} which tells us that the left-hand side depends on $\bstr$, while the right-hand side doesn't.
+We can see this, for example, by using \Cref{rem:disk_b=disk_bsc} which tells us that the left-hand side depends on $\bstr$, while the right-hand side doesn't.
 \end{remark}
@@
 
-In \cref{ssec:lcfa_on_Rn} we discussed locally constant factorization algebras on Euclidean spaces of different dimension $n$, and we saw that they presented the data of $\mathbb{E}_n$-algebras.
-In \cref{ssec:lcfa_on_ints}, on the other hand we focused on 1 dimensional manifolds, but with different possible stratification structures, and we saw that the data encoded in defects was a module structure.
+In \Cref{ssec:lcfa_on_Rn} we discussed locally constant factorization algebras on Euclidean spaces of different dimension $n$, and we saw that they presented the data of $\mathbb{E}_n$-algebras.
+In \Cref{ssec:lcfa_on_ints}, on the other hand we focused on 1 dimensional manifolds, but with different possible stratification structures, and we saw that the data encoded in defects was a module structure.
 Here, in the spirit of this section, we work to extend both of these developments to the case of Euclidean spaces with the specific kind of defect that we have limited ourselves to, namely, $\mathbb{R}^{d \subset n}$.
 
-Despite \cref{rem:disk_not_enough}, we know from \cref{lem:disk/M_to_disk} that sometimes the classification results for disk algebras can be used for factorization algebras.
+Despite \Cref{rem:disk_not_enough}, we know from \Cref{lem:disk/M_to_disk} that sometimes the classification results for disk algebras can be used for factorization algebras.
 In particular, this is the case for $\mathbb{R}^{d \subset n}$, since it is final in the $\infty$-category of basics $\bstr = \mathsf{D}_{d \subset n}^*$, as long as $d < n - 1$.
@@
 %
-together with \cref{prop:exp_of_products_lc}, which describes locally constant factorization algebras on product spaces.
-Since $\mathbb{R}^n_*$ is a basic the collar-gluing property \cref{cor:gluing_lcfas} can't help us to analyze the situation.
+together with \Cref{prop:exp_of_products_lc}, which describes locally constant factorization algebras on product spaces.
+Since $\mathbb{R}^n_*$ is a basic the collar-gluing property \Cref{cor:gluing_lcfas} can't help us to analyze the situation.
 We are left with two cases: $n=1$ and $n > 1$.
@@
     The first of these is equivalent to the space $\mathsf{Emb}^*((\mathbb{R}^n)^{\sqcup i}, \mathbb{R}^n)$ of framed open embeddings, which makes it is obvious that restricting to non-defect disks would give the data of an $\mathbb{E}_n$-algebra.
-This is related to \cref{lem:ff_functor_to_refinement}, which says that forgetting the stratification results in obtaining a full $\infty$-subcategory of locally constant factorization algebras.
+This is related to \Cref{lem:ff_functor_to_refinement}, which says that forgetting the stratification results in obtaining a full $\infty$-subcategory of locally constant factorization algebras.
 When $i=0$, the third space above is equivalent to a point, which makes it clear that restricting exclusively to pointed disks $\mathbb{R}^n_*$ would give rise to plain objects\footnote{We've omitted mentioning the fact that, because of morphisms like $\emptyset \xrightarrow{} U$, all of the above algebraic objects will be pointed.
@@
 
-    The isomorphism $\mathbb{R}^n \setminus \{ 0 \} \cong S^{n-1} \times \mathbb{R}$ together with an examination of \cite[prop.3.16]{francis2013}, which we recalled in \cref{univ_env_for_En}, and its proof leads us to suggest that the $\mathbb{E}_n$-algebra $A$ and the $\mathbb{E}_0$-algebra $B$ are further such that $B$ is a module over the universal enveloping algebra $U_A \simeq \int_{S^{n-1}} A$ as an $\mathbb{E}_1$-algebra.
+    The isomorphism $\mathbb{R}^n \setminus \{ 0 \} \cong S^{n-1} \times \mathbb{R}$ together with an examination of \cite[prop.3.16]{francis2013}, which we recalled in \Cref{univ_env_for_En}, and its proof leads us to suggest that the $\mathbb{E}_n$-algebra $A$ and the $\mathbb{E}_0$-algebra $B$ are further such that $B$ is a module over the universal enveloping algebra $U_A \simeq \int_{S^{n-1}} A$ as an $\mathbb{E}_1$-algebra.
 Remembering that we limited the whole discussion to the case when $n>1$, we propose:
@@
 \begin{proof}
-    From \cref{eq:focus_on_disk_dn} we know that when $n > 1$ we have
+    From \Cref{eq:focus_on_disk_dn} we know that when $n > 1$ we have
     %
@@
     %
-    where we used the notation from \cref{obs:explore_D*}. Specializing \cref{thm:classif_disk_d_under_n*_alg} to the case at hand, and rewriting gives the left pullback square of the diagram
+    where we used the notation from \Cref{obs:explore_D*}. Specializing \Cref{thm:classif_disk_d_under_n*_alg} to the case at hand, and rewriting gives the left pullback square of the diagram
     %
@@
 We believe that this is due to the fact that using the homotopy pullback is not what the proof provided in the reference actually does.
-The remaining discrepancy is then explained by our \cref{cor:gluing_lcfas}, which glues locally constant factorization algebras.
+The remaining discrepancy is then explained by our \Cref{cor:gluing_lcfas}, which glues locally constant factorization algebras.
 \end{remark}
@@
     The case $n=1$ is special because the higher stratum $\mathbb{R} \setminus \{0\}$ is now disconnected.
-Looking back at the construction leading up to \cref{prop:hoint_gives_modules} and at \cref{rem:left_or_right_module} we can guess that a statement like the following can hold true:
+Looking back at the construction leading up to \Cref{prop:hoint_gives_modules} and at \Cref{rem:left_or_right_module} we can guess that a statement like the following can hold true:
 \end{remark}
@@
 However, it is possible that the global topology introduces some twisting of this local understanding.
-Due to \cref{cor:gluing_lcfas} and the properties of stratified manifolds, in any particular case, it's possible to find some list of collar-gluings that reduce the problem down to the local case, but this doesn't tell us anything about the general structure.
+Due to \Cref{cor:gluing_lcfas} and the properties of stratified manifolds, in any particular case, it's possible to find some list of collar-gluings that reduce the problem down to the local case, but this doesn't tell us anything about the general structure.
 Despite this, there is a particular collar-gluing that is the obvious first step if we're looking at a general manifold $M_\Sigma$.
@@
 However, there is a special case that we can already tackle, which is the case of framed stratified manifolds.
-This is because, as discussed in \cref{def:framed_d_under_n_structure}, $\mathsf{D}_{d \subset n}^*$-manifolds come with a trivialization of the normal bundle of the distinguished submanifold $\Sigma$.
+This is because, as discussed in \Cref{def:framed_d_under_n_structure}, $\mathsf{D}_{d \subset n}^*$-manifolds come with a trivialization of the normal bundle of the distinguished submanifold $\Sigma$.
 This, in turn implies trivializations for $\cone(\pi)$ and $\mathsf{L}_{\Sigma} \times \mathbb{R}$ as bundles over $\Sigma$ with typical fibers $\mathbb{R}^{n-d}_*$ and $S^{n-d-1} \times \mathbb{R}$, respectively.
@@
 
-However, \cref{prop:exp_of_products_lc} already gives us a way to classify locally constant factorization algebras on product spaces, if we know them on the product components.
-Having classified locally constant factorization algebras on the pointed Euclidean space in \cref{thm:classif_Rn*}, we already have the result that
+However, \Cref{prop:exp_of_products_lc} already gives us a way to classify locally constant factorization algebras on product spaces, if we know them on the product components.
+Having classified locally constant factorization algebras on the pointed Euclidean space in \Cref{thm:classif_Rn*}, we already have the result that
 %
@@
 \end{equation}
-%
-where the only functor that we haven't mentioned above is $\lcfa_{M \setminus \Sigma} (\catC) \xrightarrow{} \lcfa_{\mathbb{R}^{n-d} \setminus \{ 0\} } (\lcfa_{\Sigma} (\catC))$, which is given by restriction to the fattened link.
 
@@
 Additionally, it exactly specifies what that module structure should be given by.
-In the case where the stratified manifold isn't framed we expect that the above structure will be `twisted' as seen in \cref{ex:cylinder_mobius_band} for the case of the M\"obius band.
+In the case where the stratified manifold isn't framed we expect that the above structure will be `twisted' as seen in \Cref{ex:cylinder_mobius_band} for the case of the M\"obius band.
 

### 2024-03-18 sections/0intro.tex

@@
 
-\textbf{\Cref{ch:gluing_disk_alg} Collar-gluings and Disk Algebras:} The fourth section presents a novel result about the behavior of certain types of disk algebras under the operation of collar-gluing in the manifold variable.
-It essentially shows that we can reproduce a disk algebra on a stratified manifold if we know it on some particular pieces of it together with the data of how to glue them.
+\textbf{\Cref{ch:gluing_disk_alg} Collar-gluings and Disk Algebras:} The fourth section presents a novel result about the behavior of certain types of factorization algebras under the operation of collar-gluing in the manifold variable.
+It essentially shows that we can reproduce factorization algebras on a stratified manifold if we know them on some particular pieces of it together with the data of how to glue them.
 Formally, we have
 %
-\begin{theorem*}[\ref{thm:gluing_alg_disk/M}]
-    Given a collar-gluing of stratified manifolds $f: M \rightarrow [-1,1]$, the $\infty$-category of $\disk_{/M}$-algebras is equivalent to the pullback of $\infty$-categories
+\begin{theorem*}[\ref{thm:gluing_lcfas}]
+    Given a collar-gluing of stratified manifolds $f: M \rightarrow [-1,1]$, the $\infty$-category of locally constant factorization algebras is equivalent to the pullback of $\infty$-categories
     %
     \begin{equation}
-        \alg{\disk_{/M}} (\catC) \simeq \alg{\disk_{/M_-}} (\catC) \bigtimes_{\alg{\disk_{/M_0 \times \mathbb{R}}} (\catC)} \alg{\disk_{/M_+}} (\catC).
+        \lcfa_{M} (\catC) \simeq \lcfa_{M_-} (\catC) \bigtimes_{\lcfa{M_0 \times \mathbb{R}} (\catC)} \\cfa_{M_+} (\catC).
     \end{equation}
@@
 %
-Together with the results of the previous section this gluing holds for locally constant factorization algebras too, and it hugely expands the number of manifolds for which the $\infty$-category of locally constant factorization algebras can be specified.
-As a straightforward example, it gives a way to work on and classify factorization algebras on all spheres $S^n$.
-Only the circle has been described to date (\cite{ginot2015}) using equivariant factorization algebras, so we should note the result above lets us obtain generalizations without falling back on covering space techniques.
+The results of the previous section a very important in the proof of this statement, because we heavily use the properties of factorization homology.
+A similar version holds for ordinary factorization algebras in the for of \Cref{cor:disk_alg=falg}.
+This result hugely expands the number of manifolds for which the $\infty$-category of locally constant factorization algebras can be specified.
+As a straightforward example, it gives a way to work on, and classify, factorization algebras on all higher spheres $S^n$.
+Without it, only the circle has been described to date (\cite{ginot2015}) using equivariant factorization algebras and inheritance from covering spaces.
 

### 2024-03-18 sections/3algebras.tex

@@
 \begin{remark}
-    As noted at the beginning of \ss 2, the physical interpretation of this version of factorization homology is a way to take a spacetime $M$ and its local observables $A$, and construct \emph{some}, and typically not all, of the global observables.
+    As noted at the beginning of \S 2, the physical interpretation of this version of factorization homology is a way to take a spacetime $M$ and its local observables $A$, and construct \emph{some}, and typically not all, of the global observables.
 The previous \Cref{thm:disk_alg=lcfa} and \Cref{cor:disk_alg=falg} transfer this observation to factorization algebras, which aligns with the observation of \cite{cg2016} that the current version of factorization algebras can only deal with perturbative quantum field theory.

### 2024-03-20 sections/1stratified.tex
Changed to Emb and some work in \S 4.

@@
 
-\begin{definition}
+\begin{definition}\label{def:mfld_infty_cat}
     $\mfld$ is the $\infty$-category whose objects are stratified manifolds and whose morphisms are open embeddings among them.
@@
     \begin{equation}
-        \mathsf{Hom}_{\mfld} (M, N): [p] \mapsto \mathsf{Mfld}_{/\Delta^p} (M \times \Delta^p, N \times \Delta^p).
+        \mathsf{Hom}_{\mfld} (M, N): [p] \mapsto \mathsf{Emb}_{\Delta^p} (M \times \Delta^p, N \times \Delta^p),
     \end{equation}
     %
-    Here, $\mathsf{Mfld}_{/\Delta^p}$ takes the morphism set in the over-category over $\Delta^p$.
+    where $\mathsf{Emb}_{\Delta^p} (M \times \Delta^p, N \times \Delta^p)$ denotes the embeddings from $M \times \Delta^p$ to $N \times \Delta^p$ that commute on the nose with the projections to $\Delta^p$.
 \end{definition}

### 2024-03-20 sections/4gluing_alt.tex
Pushing previous changes.

--- 2024-03-18 sections/4gluing_alt.tex
@@
 
+\begin{remark}
+    The simple case when the collar-gluing is a disjoint union, and the manifolds are smooth can also be found as \cite[ex.5.4.5.4]{lurie_ha}.
+\end{remark}
+
+\subsection{An Outside View of Factorization Algebras}
+
+After the results of the previous section we remark on a general view that we can take for the $\infty$-categories of (locally constant) factorization algebras.
+Namely, we notice factorization algebras can be cast as a functor
+%
+\begin{equation}
+    \falg_{-}(\catC), \lcfa_{-}(\catC): \mfld[r] \xrightarrow{\ \ \ \ } \cat^{\mathsf{op}},
+\end{equation}
+%
+where the action on morphisms is given by restriction, which is what gives rise to the $^{\mathsf{op}}$.
+
+\begin{proposition}
+    Factorization algebras can be formulated as functors
+    %
+    \begin{equation}
+        \falg_{-}(\catC), \lcfa_{-}(\catC): \mfld \xrightarrow{\ \ \ \ } \cat^{\mathsf{op}}.
+    \end{equation}
+\end{proposition}
+
+\begin{proof}
+    The proof will go along the same lines for both, so we will focus on factorization algebras, and shorten notation to $\mathscr{F} := \falg (\catC): \mfld[r] \xrightarrow{} \cat^{\mathsf{op}}$.
+Beyond the obvious assignment on objects, to define the functor we need to provide a map of spaces
+    %
+    \begin{equation}
+        \mathsf{Hom}_{\mfld}(M, N) \xrightarrow{\ \ \eta \ \ } \mathsf{Fun}(\mathscr{F}(N), \mathscr{F}(M))^{\simeq}.
+    \end{equation}
+    %
+    This data can be provided in the form of a map of simplicial sets, whose components are
+    %
+    \begin{equation}
+        \mathsf{Emb}_{\Delta^p}(M \times \Delta^p, N \times \Delta^p) \xrightarrow{\ \ \eta_p \ \ } \mathsf{Fun}(\mathscr{F}(N), \mathscr{F}(M))^{\simeq}_p,
+    \end{equation}
+    %
+    where the morphism space notation was introduced in \Cref{def:mfld_infty_cat}.
+Any map from a space will factor through the maximal $\infty$-groupoid of the codomain, so that we can drop the $^{\simeq}$ requirement on the target.
+Unraveling the definition of a functor category at the same time means that we need to provide maps
+    %
+    \begin{equation}
+        \mathsf{Emb}_{\Delta^p}(M \times \Delta^p, N \times \Delta^p) \xrightarrow{\ \ \eta_p \ \ } \mathsf{Hom}_{\mathsf{sSet}}(\mathscr{F}(N) \times \Delta^p, \mathscr{F}(M)).
+    \end{equation}
+    %
+    But indeed,
+    %
+    \begin{align}
+        \mathsf{Emb}_{\Delta^p}(M \times \Delta^p, N \times \Delta^p) \xhookrightarrow{\ \ \ \ \ \ \ }& \mathsf{Emb}(M \times \Delta^p, N \times \Delta^p) \\
+        \xrightarrow{\mathrm{restrict}}& \mathsf{Hom_{sSet}} (\mathscr{F}(N \times \Delta^p), F(M \times \Delta^p)) \\
+        \xrightarrow{\ \pi_{1*} \circ -}& \mathsf{Hom_{sSet}} (F(N \times \Delta^p) , F(M)) \\
+        \xrightarrow{\ - \circ \alpha^p \ }& \mathsf{Hom_{sSet}} (F(N) \times \Delta^p , F(M))
+    \end{align}
+
+    WORK IN PROGRESS.
+\end{proof}
+
+In the case of disjoint union, \Cref{thm:gluing_lcfas} and \Cref{cor:gluing_falgs} then provide the equivalences that are needed to make this into a symmetric monoidal functor, where the symmetric monoidal product on $\cat^{\mathsf{op}}$ is given by \emph{coproduct}.
+With that understanding the same two results, \Cref{thm:gluing_lcfas} and \Cref{cor:gluing_falgs}, can be understood as saying that the functors $\falg(\catC)$ and $\lcfa(\catC)$ satisfy $\otimes$-excision as outlined in \Cref{sec:excision_homology}.% We can even work a bit more to show:
+%
+%\begin{proposition}
+%    The functors $\falg(\catC)$ and $\lcfa(\catC)$ respect sequential colimits.
+%\end{proposition}
+%
+%\begin{proof}
+%    The proof will go along the same lines for both, so we will focus on factorization algebras, and shorten notation to $\mathscr{F} := \falg (\catC): \mfld[r] \xrightarrow{} \cat^{\mathsf{op}}$.
+We will also use the convention that we work in $\cat$ instead of its opposite.
+In these terms, the statement we need to prove is that the canonical functor
+%    %
+%    \begin{equation}
+%        \mathscr{F}(M) \xrightarrow[\alpha]{\ \ \simeq \ \ } \mathsf{lim} (\mathscr{F}(M_0) \xleftarrow{} \mathscr{F}(M_1) \xleftarrow{} \dots)
+%    \end{equation}
+%    %
+%    is an equivalence of $\infty$-categories, where $M := \cup_{i \geq 0} M_i$. All functors used to make the diagram are restriction functors. 
+%
+%    An object of the limit is a collection $(A_0, A_1, \dots)$ of factorization algebras on $M_0, M_1, \dots$, respectively, together with equivalences $\eta_i: A_{i+1}|_{M_i} \simeq A_i$ for $i \geq 0$.
+%\end{proof}
+
 \subsection{Some Examples of Gluing}

### 2024-03-20 sections/5classification.tex
Pushing previous changes.

@@
 together with \Cref{prop:exp_of_products_lc}, which describes locally constant factorization algebras on product spaces.
-Since $\mathbb{R}^n_*$ is a basic the collar-gluing property \Cref{cor:gluing_lcfas} can't help us to analyze the situation.
+Since $\mathbb{R}^n_*$ is a basic the collar-gluing property \Cref{thm:gluing_lcfas} can't help us to analyze the situation.
 We are left with two cases: $n=1$ and $n > 1$.
@@
 We believe that this is due to the fact that using the homotopy pullback is not what the proof provided in the reference actually does.
-The remaining discrepancy is then explained by our \Cref{cor:gluing_lcfas}, which glues locally constant factorization algebras.
+The remaining discrepancy is then explained by our \Cref{thm:gluing_lcfas}, which glues locally constant factorization algebras.
 \end{remark}
@@
 However, it is possible that the global topology introduces some twisting of this local understanding.
-Due to \Cref{cor:gluing_lcfas} and the properties of stratified manifolds, in any particular case, it's possible to find some list of collar-gluings that reduce the problem down to the local case, but this doesn't tell us anything about the general structure.
+Due to \Cref{thm:gluing_lcfas} and the properties of stratified manifolds, in any particular case, it's possible to find some list of collar-gluings that reduce the problem down to the local case, but this doesn't tell us anything about the general structure.
 Despite this, there is a particular collar-gluing that is the obvious first step if we're looking at a general manifold $M_\Sigma$.
@@
 
-\Cref{cor:gluing_lcfas} allows us to use the collar-gluing from above to write the equivalence of $\infty$-categories
+\Cref{thm:gluing_lcfas} allows us to use the collar-gluing from above to write the equivalence of $\infty$-categories
 %

### 2024-03-24 sections/4gluing_alt.tex
Some work in section 4.

--- 2024-03-18 sections/4gluing_alt.tex
@@
 
+\begin{remark}
+    The simple case when the collar-gluing is a disjoint union, and the manifolds are smooth can also be found as \cite[ex.5.4.5.4]{lurie_ha}.
+\end{remark}
+
+\subsection{An Outside View of Factorization Algebras ({\color{red} Work In Progress})}
+
+After the results of the previous section we remark on a general view that we can take for the $\infty$-categories of (locally constant) factorization algebras.
+Namely, we notice factorization algebras can be cast as a functor
+%
+\begin{equation}
+    \falg_{-}(\catC), \lcfa_{-}(\catC): \mfld[r] \xrightarrow{\ \ \ \ } \cat^{\mathsf{op}},
+\end{equation}
+%
+where the action on morphisms is given by restriction, which is what gives rise to the $^{\mathsf{op}}$.
+In the case of disjoint union, \Cref{thm:gluing_lcfas} and \Cref{cor:gluing_falgs} then provide the equivalences that are needed to make these into symmetric monoidal functors, where the symmetric monoidal product on $\cat^{\mathsf{op}}$ is given by \emph{coproduct}.
+
+We know from \Cref{thm:decom_strat_man} that any manifold can be constructed from basics by iterated collar-gluings and sequential colimits.
+Having described what happens to a locally constant factorization algebras under collar-gluings of manifolds, we now turn to sequential colimits.
+
+\begin{proposition}
+    The functors $\falg(\catC)$ and $\lcfa(\catC)$ respect sequential colimits.
+\end{proposition}
+
+\begin{proof}
+    The proof will go along the same lines for both, so we will focus on factorization algebras, and shorten notation to $\mathscr{F} := \falg (\catC): \mfld[r] \xrightarrow{} \cat^{\mathsf{op}}$.
+We will also use the convention that we work in $\cat$ instead of its opposite.
+In these terms, the statement we need to prove is that the canonical functor
+    %
+    \begin{equation}
+        \mathscr{F}(M) \xrightarrow[\alpha]{\ \ \simeq \ \ } \mathsf{lim} (\mathscr{F}(M_0) \xleftarrow{} \mathscr{F}(M_1) \xleftarrow{} \dots)
+    \end{equation}
+    %
+    is an equivalence of $\infty$-categories, where $M := \cup_{i \geq 0} M_i$. All functors used to make the diagram are restriction functors.
+
+    An object of the limit is a collection $(A_0, A_1, \dots)$ of factorization algebras on $M_0, M_1, \dots$, respectively, together with equivalences $\eta_i: A_i \simeq A_{i+1}|_{M_i}$ for $i \geq 0$.
+Towards showing essential surjectivity of $\alpha$ we will construct the factorization algebra $A$ on $M$ given by the following prescription.
+Given any open $U \subset M$, there will be an integer $i$, such that $U \subset M_i$; we take the smallest such integer, call it $i_U$, and define
+    %
+    \begin{equation}
+        A(U) := A_{i_U} (U).
+    \end{equation}
+    %
+    Given a morphism $U \xhookrightarrow{} V$ we know that $i_U \leq i_V$, and the morphism we assign is
+    %
+    \begin{equation}
+        A(U \xhookrightarrow{} V) := A_{i_U}(U) \xrightarrow{\eta_{i_U}(U)} \cdots \xrightarrow{\eta_{i_V - 1}(U)} A_{i_V} (U) \xrightarrow{A_{i_V} (U \xhookrightarrow{} V)} A_{i_V} (V).
+    \end{equation}
+
+    ...
+
+    Using \Cref{thm:disk_alg=lcfa} and \Cref{cor:disk_alg=falg}, we will take the disk algebra incarnation of the relevant $\infty$-categories.
+\end{proof}
+
+\begin{proposition}
+    {\color{red} (Probably untrue)} Factorization algebras can be formulated as functors
+    %
+    \begin{equation}
+        \falg_{-}(\catC), \lcfa_{-}(\catC): \mfld \xrightarrow{\ \ \ \ } \cat^{\mathsf{op}}.
+    \end{equation}
+\end{proposition}
+
+\begin{proof}
+    The proof will go along the same lines for both, so we will focus on factorization algebras, and shorten notation to $\mathscr{F} := \falg (\catC): \mfld[r] \xrightarrow{} \cat^{\mathsf{op}}$.
+Beyond the obvious assignment on objects, to define the functor we need to provide a map of spaces
+    %
+    \begin{equation}
+        \mathsf{Hom}_{\mfld}(M, N) \xrightarrow{\ \ \eta \ \ } \mathsf{Fun}(\mathscr{F}(N), \mathscr{F}(M))^{\simeq}.
+    \end{equation}
+    %
+    This data can be provided in the form of a map of simplicial sets, whose components are
+    %
+    \begin{equation}
+        \mathsf{Emb}_{\Delta^p}(M \times \Delta^p, N \times \Delta^p) \xrightarrow{\ \ \eta_p \ \ } \mathsf{Fun}(\mathscr{F}(N), \mathscr{F}(M))^{\simeq}_p,
+    \end{equation}
+    %
+    where the morphism space notation was introduced in \Cref{def:mfld_infty_cat}.
+Any map from a space will factor through the maximal $\infty$-groupoid of the codomain, so that we can drop the $^{\simeq}$ requirement.
+Unraveling the definition of a functor category at the same time means that we need to provide maps
+    %
+    \begin{equation}
+        \mathsf{Emb}_{\Delta^p}(M \times \Delta^p, N \times \Delta^p) \xrightarrow{\ \ \eta_p \ \ } \mathsf{Hom}_{\mathsf{sSet}}(\mathscr{F}(N) \times \Delta^p, \mathscr{F}(M)).
+    \end{equation}
+    %
+    And indeed,
+    %
+    \begin{align}
+        \mathsf{Emb}_{\Delta^p}(M \times \Delta^p, N \times \Delta^p) \xhookrightarrow{\ \ \ \ \ \ \ }& \mathsf{Emb}(M \times \Delta^p, N \times \Delta^p) \\
+        \xrightarrow{\mathrm{restrict}}& \mathsf{Hom_{sSet}} (\mathscr{F}(N \times \Delta^p), \mathscr{F}(M \times \Delta^p)) \\
+        \xrightarrow{\ \pi_{1*} \circ -}& \mathsf{Hom_{sSet}} (\mathscr{F}(N \times \Delta^p) , \mathscr{F}(M)) \\
+        \xrightarrow{\ - \circ \alpha^p \ }& \mathsf{Hom_{sSet}} (\mathscr{F}(N) \times \Delta^p , \mathscr{F}(M)).
+    \end{align}
+    %
+    Let us further describe the final arrow. It arises as a functor
+    %
+    \begin{equation}
+        \mathscr{F} (N) \times \Delta^p \xrightarrow{\ \ \alpha^p \ \ } \mathscr{F}(N \times \Delta^p),
+    \end{equation}
+    %
+    whose components are given by
+    %
+    \begin{equation}
+        \alpha^p_m: \mathscr{F} (N)_m \times \mathsf{Hom}_{\Delta}([m], [p]) \xrightarrow{} \mathscr{F}(N \times \Delta^p)_m.
+    \end{equation}
+    %
+    ......
+\end{proof}
+
+{\color{red} Work in progress}
+
+This perspective on the theory of locally constant factorization algebras as a functor reframes the gluing result \Cref{thm:gluing_lcfas}, and together with lemma \Cref{lem:disk/M_to_disk} points towards a result like the following:
+
+\begin{conjecture}
+    The theory of locally constant factorization algebras is fully determined, using factorization homology, by the data of a functor
+    %
+    \begin{equation}
+        \bsc \xrightarrow{\ \ \ \ } \cat^{\mathsf{op}},
+    \end{equation}
+    %
+    which to each basic $U$ attaches the $\infty$-category $\mathsf{Fun}^{\otimes} (\disk(\mathsf{B}_U), \catC)$ of disk algebras with $\mathsf{B}_U$ structure, where $\mathsf{B}_U$ is the sieve poset whose maximal element is $U$.
+\end{conjecture}
+
+%\begin{proof}
+%    The second part of the statement simply concerns what data defines a locally constant factorization algebra on a disk. 
+%\end{proof}
+
 \subsection{Some Examples of Gluing}

### 2024-03-27 sections/4gluing_alt.tex
More work in section 4.

@@
 
-\begin{proposition}
+\begin{proposition}\label{prop:fa_seq_col}
     The functors $\falg(\catC)$ and $\lcfa(\catC)$ respect sequential colimits.
@@
 Towards showing essential surjectivity of $\alpha$ we will construct the factorization algebra $A$ on $M$ given by the following prescription.
-Given any open $U \subset M$, there will be an integer $i$, such that $U \subset M_i$; we take the smallest such integer, call it $i_U$, and define
+Using \Cref{cor:disk_alg=falg}, we will take the disk algebra incarnation of the relevant $\infty$-categories, so that we want to construct $A \in \alg{\disk[r]_{/M}}$.
+Given any disk $U \subset M$, there will be an integer $i$, such that $U \subset M_i$; we take the smallest such integer, call it $i_U$, and define
     %
@@
     %
+    \begin{equation}\label{eq:seq_col_gluing}
+        A(U \xhookrightarrow{} V) := \left( A_{i_U}(U) \xrightarrow{\eta_{i_U}(U)} \cdots \xrightarrow{\eta_{i_V - 1}(U)} A_{i_V} (U) \xrightarrow{A_{i_V} (U \xhookrightarrow{} V)} A_{i_V} (V) \right).
+    \end{equation}
+    %
+    The same construction works for multimorphisms too, e.g. for $U \sqcup U' \xhookrightarrow{} V$ we would have
+    %
+    \begin{align}
+        A(U \sqcup U' \xhookrightarrow{} V) := \left( A_{i_U}(U) \otimes A_{i_{U'}} (U') \xrightarrow{\eta_{i_U}(U) \otimes \mathbb{1}} \cdots \xrightarrow{\eta_{i_V - 1}(U) \otimes \mathbb{1}} A_{i_V} (U) \otimes A_{i_{U'}}(U') \right.
+\notag\\
+        \left.\xrightarrow{\mathbb{1} \otimes \eta_{i_{U'}}(U')} \cdots \xrightarrow{\mathbb{1} \otimes \eta_{i_V - 1}(U')} A_{i_V} (U) \otimes A_{i_V} (U') \xrightarrow{} A_{i_V} (U \sqcup U') \xrightarrow{A_{i_V} (U \sqcup U' \xhookrightarrow{} V)} A_{i_V} (V) \right).
+    \end{align} 
+    %
+    This describes the data of a $\disk[r]_{/M}$-algebra.
+When applying the above construction to locally constant factorization algebras it's also clear that the property of local constancy is inherited since then all the arrows in \cref{eq:seq_col_gluing} are equivalences.
+
+    To show essential surjectivity of $\alpha$ we need to find equivalences $\epsilon_i: A|_{M_i} \xrightarrow{\simeq} A_i$ for all $i \geq 0$, which fit into a commutative diagram
+    %
+    \begin{equation}\label{cd:seq_col_equivs}
+        \begin{tikzcd}
+            & A|_{M_i} = (A|_{M_{i+1}})|_{M_i} \arrow[ld, "\epsilon_i"'] \arrow[rd, "\epsilon_i|_{M_i}"] & \\
+            A_i \arrow[rr, "\eta_i"] & & A_{i+1}|_{M_i},
+        \end{tikzcd}
+    \end{equation}
+    %
+    where we have remembered that consecutive restrictions commute on the nose.
+The equivalence $\epsilon_i$ is given by its components $\epsilon_i(U): A|_{M_i} \xrightarrow{} A_i(U)$, which we define as
+    %
     \begin{equation}
-        A(U \xhookrightarrow{} V) := A_{i_U}(U) \xrightarrow{\eta_{i_U}(U)} \cdots \xrightarrow{\eta_{i_V - 1}(U)} A_{i_V} (U) \xrightarrow{A_{i_V} (U \xhookrightarrow{} V)} A_{i_V} (V).
+        \epsilon_i(U) := \left( A|_{M_i}(U) = A_{i_U}(U) \xrightarrow{\eta_{i_U}(U)} \cdots \xrightarrow{\eta_{i-1}(U)} A_i (U) \right).
     \end{equation}
+    %
+    That these assemble into a natural transformation is provided by commutative diagrams like
+    %
+    \begin{equation}
+        \begin{tikzcd}[column sep = {2.5cm}]
+            A_{i_U}(U) \arrow[d, "\eta_{i_V-1}(U) \circ \cdots \circ \eta_{i_U}(U)"'] \arrow[r, "\eta_{i-1}(U) \circ \cdots \circ \eta_{i_U}(U)"] & A_i(U) \arrow[d, "="] \\
+            A_{i_V}(U) \arrow[d] \arrow[r, "\eta_{i-1}(U) \circ \cdots \circ \eta_{i_V}(U)"] & A_i (U) \arrow[d] \\
+            A_{i_V}(V) \arrow[r, "\eta_{i-1}(V) \circ \cdots \circ \eta_{i_V}(V)"] & A_i (V).
+        \end{tikzcd}
+    \end{equation}
+    %
+    That these equivalences $\epsilon_i$ fit into diagrams like in \cref{cd:seq_col_equivs} is obvious from their definition.
+
+    Showing full faithfulness of $\alpha$ is the same for ordinary and locally constant factorization algebras since the later are a full $\infty$-subcategory of the former.
+What we have to show is that
+    %
+    \begin{equation}
+        \mathsf{Hom}_{\mathscr{F} (M)}(A, B) \xrightarrow{\ \ \alpha \ \ } \mathsf{Hom}_{\mathsf{lim}} (\alpha (A), \alpha(B)) \simeq \mathsf{lim}_{i \geq 0} (\mathsf{Hom}_{\mathscr{F}(M_i)} (A_i, B_i))
+    \end{equation}
+    %
+    is an equivalence of spaces.
+In the last equivalence we made use of the essential surjectivity from above.
+The same idea as for the construction of $A$ work here too, the main point being that any disk $U$ will have a finite $i_U$.
 
     ...
-
-    Using \Cref{thm:disk_alg=lcfa} and \Cref{cor:disk_alg=falg}, we will take the disk algebra incarnation of the relevant $\infty$-categories.
 \end{proof}
 
-\begin{proposition}
-    {\color{red} (Probably untrue)} Factorization algebras can be formulated as functors
+Considering \Cref{thm:decom_strat_man} together with the statements of \Cref{cor:disk_alg=falg} (or \Cref{thm:disk_alg=lcfa} in the locally constant case), together with the above \Cref{prop:fa_seq_col}, we have an algorithm of how to compute the $\infty$-category of factorization algebras on any manifold if we know it on the basics.
+In other words, the theory of (locally constant) factorization algebras is fully determined by the assignment
 %
 \begin{equation}
-        \falg_{-}(\catC), \lcfa_{-}(\catC): \mfld \xrightarrow{\ \ \ \ } \cat^{\mathsf{op}}.
-    \end{equation}
-\end{proposition}
-
-\begin{proof}
-    The proof will go along the same lines for both, so we will focus on factorization algebras, and shorten notation to $\mathscr{F} := \falg (\catC): \mfld[r] \xrightarrow{} \cat^{\mathsf{op}}$.
-Beyond the obvious assignment on objects, to define the functor we need to provide a map of spaces
-    %
-    \begin{equation}
-        \mathsf{Hom}_{\mfld}(M, N) \xrightarrow{\ \ \eta \ \ } \mathsf{Fun}(\mathscr{F}(N), \mathscr{F}(M))^{\simeq}.
+    U \mapsto \falg_U (\catC),
 \end{equation}
 %
-    This data can be provided in the form of a map of simplicial sets, whose components are
-    %
-    \begin{equation}
-        \mathsf{Emb}_{\Delta^p}(M \times \Delta^p, N \times \Delta^p) \xrightarrow{\ \ \eta_p \ \ } \mathsf{Fun}(\mathscr{F}(N), \mathscr{F}(M))^{\simeq}_p,
-    \end{equation}
-    %
-    where the morphism space notation was introduced in \Cref{def:mfld_infty_cat}.
-Any map from a space will factor through the maximal $\infty$-groupoid of the codomain, so that we can drop the $^{\simeq}$ requirement.
-Unraveling the definition of a functor category at the same time means that we need to provide maps
-    %
-    \begin{equation}
-        \mathsf{Emb}_{\Delta^p}(M \times \Delta^p, N \times \Delta^p) \xrightarrow{\ \ \eta_p \ \ } \mathsf{Hom}_{\mathsf{sSet}}(\mathscr{F}(N) \times \Delta^p, \mathscr{F}(M)).
-    \end{equation}
-    %
-    And indeed,
-    %
-    \begin{align}
-        \mathsf{Emb}_{\Delta^p}(M \times \Delta^p, N \times \Delta^p) \xhookrightarrow{\ \ \ \ \ \ \ }& \mathsf{Emb}(M \times \Delta^p, N \times \Delta^p) \\
-        \xrightarrow{\mathrm{restrict}}& \mathsf{Hom_{sSet}} (\mathscr{F}(N \times \Delta^p), \mathscr{F}(M \times \Delta^p)) \\
-        \xrightarrow{\ \pi_{1*} \circ -}& \mathsf{Hom_{sSet}} (\mathscr{F}(N \times \Delta^p) , \mathscr{F}(M)) \\
-        \xrightarrow{\ - \circ \alpha^p \ }& \mathsf{Hom_{sSet}} (\mathscr{F}(N) \times \Delta^p , \mathscr{F}(M)).
-    \end{align}
-    %
-    Let us further describe the final arrow. It arises as a functor
-    %
-    \begin{equation}
-        \mathscr{F} (N) \times \Delta^p \xrightarrow{\ \ \alpha^p \ \ } \mathscr{F}(N \times \Delta^p),
-    \end{equation}
-    %
-    whose components are given by
-    %
-    \begin{equation}
-        \alpha^p_m: \mathscr{F} (N)_m \times \mathsf{Hom}_{\Delta}([m], [p]) \xrightarrow{} \mathscr{F}(N \times \Delta^p)_m.
-    \end{equation}
-    %
-    ......
-\end{proof}
+for each basic $U \in \bsc$.
 
-{\color{red} Work in progress}
-
-This perspective on the theory of locally constant factorization algebras as a functor reframes the gluing result \Cref{thm:gluing_lcfas}, and together with lemma \Cref{lem:disk/M_to_disk} points towards a result like the following:
+After a simplification down to disks, in the locally constant case , lemma \Cref{lem:disk/M_to_disk} points towards a result like the following:
 
@@
 %    The second part of the statement simply concerns what data defines a locally constant factorization algebra on a disk. 
+%\end{proof}
+
+%\begin{proposition}
+%    {\color{red} (Probably untrue)} Factorization algebras can be formulated as functors
+%    %
+%    \begin{equation}
+%        \lcfa_{-}(\catC): \mfld \xrightarrow{\ \ \ \ } \cat^{\mathsf{op}}.
+%    \end{equation}
+%\end{proposition}
+
+%\begin{proof}
+%    The proof will go along the same lines for both, so we will focus on factorization algebras, and shorten notation to $\mathscr{F} := \falg (\catC): \mfld[r] \xrightarrow{} \cat^{\mathsf{op}}$.
+Beyond the obvious assignment on objects, to define the functor we need to provide a map of spaces
+%    %
+%    \begin{equation}
+%        \mathsf{Hom}_{\mfld}(M, N) \xrightarrow{\ \ \eta \ \ } \mathsf{Fun}(\mathscr{F}(N), \mathscr{F}(M))^{\simeq}.
+%    \end{equation}
+%    %
+%    This data can be provided in the form of a map of simplicial sets, whose components are
+%    %
+%    \begin{equation}
+%        \mathsf{Emb}_{\Delta^p}(M \times \Delta^p, N \times \Delta^p) \xrightarrow{\ \ \eta_p \ \ } \mathsf{Fun}(\mathscr{F}(N), \mathscr{F}(M))^{\simeq}_p,
+%    \end{equation}
+%    %
+%    where the morphism space notation was introduced in \Cref{def:mfld_infty_cat}.
+Any map from a space will factor through the maximal $\infty$-groupoid of the codomain, so that we can drop the $^{\simeq}$ requirement.
+Unraveling the definition of a functor category at the same time means that we need to provide maps
+%    %
+%    \begin{equation}
+%        \mathsf{Emb}_{\Delta^p}(M \times \Delta^p, N \times \Delta^p) \xrightarrow{\ \ \eta_p \ \ } \mathsf{Hom}_{\mathsf{sSet}}(\mathscr{F}(N) \times \Delta^p, \mathscr{F}(M)).
+%    \end{equation}
+%    %
+%    And indeed,
+%    %
+%    \begin{align}
+%        \mathsf{Emb}_{\Delta^p}(M \times \Delta^p, N \times \Delta^p) \xhookrightarrow{\ \ \ \ \ \ \ }& \mathsf{Emb}(M \times \Delta^p, N \times \Delta^p) \\
+%        \xrightarrow{\mathrm{restrict}}& \mathsf{Hom_{sSet}} (\mathscr{F}(N \times \Delta^p), \mathscr{F}(M \times \Delta^p)) \\
+%        \xrightarrow{\ \pi_{1*} \circ -}& \mathsf{Hom_{sSet}} (\mathscr{F}(N \times \Delta^p) , \mathscr{F}(M)) \\
+%        \xrightarrow{\ - \circ \alpha^p \ }& \mathsf{Hom_{sSet}} (\mathscr{F}(N) \times \Delta^p , \mathscr{F}(M)).
+%    \end{align}
+%    %
+%    Let us further describe the final arrow. It arises as a functor
+%    %
+%    \begin{equation}
+%        \mathscr{F} (N) \times \Delta^p \xrightarrow{\ \ \alpha^p \ \ } \mathscr{F}(N \times \Delta^p),
+%    \end{equation}
+%    %
+%    whose components are given by
+%    %
+%    \begin{equation}
+%        \alpha^p_m: \mathscr{F} (N)_m \times \mathsf{Hom}_{\Delta}([m], [p]) \xrightarrow{} \mathscr{F}(N \times \Delta^p)_m.
+%    \end{equation}
+%    %
+%    ......
 %\end{proof}

### 2024-03-27 text_condensed.tex
First pass of a condensed version. Fell free to change at will.

--- 2024-03-18 sections/3algebras.tex
@@
-\documentclass[../text]{subfiles}
+% Run only with XeLaTeX!
+%---------------------------------------------------------------------
+%	FORMATING AND TYPESETTING
+%---------------------------------------------------------------------
+
+% Set document class
+\documentclass[12pt,a4paper]{article}
+
+% Option to change margin size
+\usepackage[margin=2cm]{geometry}
+
+% Font and encoding settings
+\usepackage[T1]{fontenc}
+%\usepackage[utf8]{inputenc} not necessary with xelatex?
+\usepackage{yfonts} % germanic fonts (fraktur...)
+%\defaultfontfeatures{Ligatures=TeX} %??
+
+% Footnotes
+\usepackage[stable]{footmisc}
+
+% Indentation and spacing
+\usepackage{indentfirst} % indentation
+\usepackage{enumitem}[leftmargin=0pt] % spacing
+\setlist{nosep}
+
+% Multi column environment
+\usepackage{multicol}
+
+% Formating of titles
+\usepackage{titlesec}
+\titleformat{\section}
+{\normalfont\large\bfseries}{\thesection}{1em}{}
+\titleformat{\subsection}
+{\normalfont\normalsize\bfseries}{\thesubsection}{1em}{}
+\titleformat{\subsubsection}
+{\normalfont\small\bfseries}{\thesubsubsection}{1em}{}
+\titleformat{\paragraph}[runin]
+{\normalfont\small\bfseries}{\theparagraph}{1em}{}
+\titleformat{\subparagraph}[runin]
+{\normalfont\small\bfseries}{\thesubparagraph}{1em}{}
+\usepackage[titletoc]{appendix}
+
+% Math typesetting packages
+\usepackage{amsmath, amssymb, amsthm, mathtools, commath}
+\usepackage[warnings-off={mathtools-colon,mathtools-overbracket}]{unicode-math} % makes \mathbb{1} work and changes font of mathbb
+\usepackage[mathscr]{euscript} % euler script font
+\usepackage{tikz-cd} % tikz commutative diagrams
+\usepackage{thmtools, thm-restate} % theorem tools, especially restatable
+
+\AtBeginDocument{\renewcommand\setminus{\smallsetminus}} % \setminus doesn't work in unicode-math
+
+%---------------------------------------------------------------------
+
+%---------------------------------------------------------------------
+%	GRAPHICS
+%---------------------------------------------------------------------
+
+\usepackage{float}
+\usepackage{caption}
+\usepackage{graphicx}
+\graphicspath{{images/}}
+
+\usepackage{pdfpages} % for inserting pdf pages
+
+%---------------------------------------------------------------------
+
+%---------------------------------------------------------------------
+%	BIBLIOGRAPHY
+%---------------------------------------------------------------------
+
+\usepackage[backend=biber,style=alphabetic]{biblatex}
+\renewcommand*{\bibfont}{\small}
+\addbibresource{text.bib}
+
+%---------------------------------------------------------------------
+
+%---------------------------------------------------------------------
+%	HYPERLINKS
+%---------------------------------------------------------------------
+
+% Define the colors
+\usepackage{xcolor}
+\definecolor{brown}{HTML}{CD853F}
+\definecolor{blue}{HTML}{4169E1}
+\definecolor{green}{HTML}{2E8B57}
+
+% Setup options for hyperlinks
+\usepackage{hyperref}
+\hypersetup{
+colorlinks=true, linkcolor=black, breaklinks=true,
+linktoc=all, bookmarksnumbered=true,
+urlcolor=brown, linkcolor=blue, citecolor=green, % Link colors
+}
+
+% Referencing package
+\usepackage{cleveref}
+\crefname{section}{\S\!}{\S\S\!}
+\Crefname{section}{\S\!}{\S\S\!}
+
+%---------------------------------------------------------------------
+%	THEOREM STYLES
+%---------------------------------------------------------------------
+
+% Define a dummy counter to keep count for all sub-environments
+\newcounter{counter} \numberwithin{counter}{section}
+
+% Define theorem styles here based on the definition style
+\theoremstyle{definition}
+\newtheorem{definition}[counter]{Definition}
+\newtheorem{construction}[counter]{Construction}
+\newtheorem{observation}[counter]{Observation}
+
+% Define theorem styles here based on the plain style
+\theoremstyle{plain} 
+\newtheorem{theorem}[counter]{Theorem}
+\newtheorem*{theorem*}{Theorem}
+\newtheorem{corollary}[counter]{Corollary}
+\newtheorem{lemma}[counter]{Lemma}
+\newtheorem{proposition}[counter]{Proposition}
+\newtheorem*{proposition*}{Proposition}
+\newtheorem{conjecture}[counter]{Conjecture}
+
+% Define theorem styles here based on the remark style
+\theoremstyle{remark}
+\newtheorem{example}[counter]{Example}
+\newtheorem{remark}[counter]{Remark}
+
+%---------------------------------------------------------------------
+
+%---------------------------------------------------------------------
+%	NEW COMMANDS
+%---------------------------------------------------------------------
+
+% general target category
+\newcommand{\catC}{\mathscr{C}}
+
+% categories of factorization algebras
+\newcommand{\falg}{\mathscr{F} \mathsf{Alg}}
+\newcommand{\lcfa}{\mathscr{F} \mathsf{Alg}^{\mathsf{lc}}}
+
+% category of manifolds
+\newcommand{\mfld}[1][s]{%
+    \ifx r#1\mathsf{Mfld}\else
+    \ifx s#1\mathscr{M} \mathsf{fld}\else
+    \mathrm{Illegal~option}%
+    \fi\fi
+}
+
+% category of disks
+\newcommand{\disk}[1][s]{%
+    \ifx r#1\mathsf{Disk}\else
+    \ifx s#1\mathscr{D} \mathsf{isk}\else
+    \mathrm{Illegal~option}%
+    \fi\fi
+}
+
+% category of opens
+\newcommand{\opens}[1][s]{%
+    \ifx r#1\mathsf{Opns}\else
+    \ifx s#1\mathscr{O} \mathsf{pns}\else
+    \mathrm{Illegal~option}%
+    \fi\fi
+}
+
+% category of cosheaves
+\newcommand{\csheaves}[1][n]{%
+    \ifx n#1 \mathsf{c} \mathscr{S} \mathsf{hv}\else
+    \mathsf{c} \mathscr{S} \mathsf{hv}^{\mathsf{#1}}
+    \fi
+}
+
+% category of infinity categories
+\newcommand{\cat}{\mathscr{C} \mathsf{at}_{\infty}}
+
+% template for category of algebras
+\newcommand{\alg}[1]{\mathscr{A} \mathsf{lg}_{#1}}
+
+% template for category of locally constant algebras
+\newcommand{\lcalg}[1]{\mathscr{A} \mathsf{lg}^{\mathsf{lc}}_{#1}}
+
+% half-open interval
+\newcommand{\hoint}{\mathbb{R}_{\geq 0}}
+
+% Cech complex
+\newcommand{\cech}{\check{\mathsf{C}}}
+
+% Category of basics
+\newcommand{\bsc}{\mathscr{B} \mathsf{sc}}
+\newcommand{\bstr}{\mathscr{B}}
+
+% Open cone
+\newcommand{\cone}[1][n]{%
+    \ifx b#1\overline{\mathsf{C}}\else
+    \ifx n#1\mathsf{C}\else
+    \mathrm{Illegal~option}%
+    \fi\fi
+}
+
+%---------------------------------------------------------------------
+
+%\usepackage{subfiles}
+
+\setcounter{section}{-1}
 
 \begin{document}
+
+% Set title, author and date
+\title{Factorization Algebras and Factorization Homology on Stratified Spaces}
+\author{Aleksandar Ivanov, Ödül Tetik}
+\date{}
+\maketitle
+
+\begin{abstract}
+    We endeavor to fully describe (locally constant) factorization algebras on stratified spaces, by giving a description of the $\infty$-operad that underlies them through the use of factorization homology.
+We also give a result about a collar-gluing property that the $\infty$-categories of (locally constant) factorization algebras satisfy, which enables novel descriptions of these on more complicated spaces.
+Finally, we outline a classification scheme for locally constant factorization algebras on some stratified manifolds.
+Parts of this work were adapted from a Master's thesis dissertation submitted to ETH Z\"urich for the first author.
+\end{abstract}
+
+\tableofcontents
+
+\section{Introduction}
+
+{\color{red} Needs to be rewritten slightly when we finalize decision on what to include.}
+
+In this work we will explore the concepts of factorization algebras and factorization homology over stratified spaces.
+These two concepts, which at first sight will looks very different, will turn out to be closely related.
+We will strive to keep the discussion at the level of stratified spaces, while making a comparison to results in the smooth case.
+Some results we will meet have been proven in the smooth case, but with methods which do not (at the present moment) generalize to the stratified case.
+We will endeavor to point these out and give proofs that hold more generally.
+The outline of the text is as follows:
+
+%\textbf{\Cref{ch:strat_spaces} Stratified Spaces:} The first section deals with setting up the theory of stratified spaces that we will use.
+It is essentially a recap of the necessary results from the work of Ayala, Francis and Tanaka (AFT) \cite{aft_localstrut}, which is one of our main sources.
+The idea and fundamentals of stratified spaces have existed for a long time in different incarnation beginning with the work of Whitney \cite{whitney92}.
+The reason why we choose to work with this particular version of stratified spaces is due to them supporting a notion of conical smoothness that is a generalization of smoothness of manifolds.
+Furthermore, the theory of factorization homology has been developed with these spaces in mind, which eases the process of extending certain results to the stratified case much easier.
+We will not go into the full details that this incarnation of the theory has to offer, but instead we will only mention results that we will make use of later on.
+Beyond conical smoothness, this will include tangential structure and its stratified generalization, together with the packaging of both of these data into the concept of an $\infty$-category of basic singularity types.
+For the proofs of these statements the reader is encouraged to consult \cite{aft_localstrut}.
+
+%\textbf{\Cref{ch:fact_hom} Factorization Homology:} The second section will present the theory of factorization homology.
+Similar to the first section this will mostly be a recap of useful results developed by Ayala, Francis and Tanaka.
+Specifically, the stratified space results can be found in \cite{aft_fhstrat}, while the results for topological manifolds can be found in \cite{af_fhtop}.
+For the purposes of the theory we will need the concept of (structured) disk algebras, since this will be the algebraic input.
+Factorization homology will then combine this with the data of a specific kind of (possibly stratified) manifold into an object that can be viewed either as an invariant of the manifold or an invariant of the algebra.
+We will explore the key example of factorization homology over the closed, oriented interval $[-1,1]$, and see how this gives rise to the algebraic concept of the two-sided bar construction.
+More generally, this underpins the theory because it codifies the property of $\otimes$-excision.
+Finally, we will also state a classification result \cite[prop.4.8]{aft_fhstrat} about a certain type of disk algebras with stratified structure.
+
+\textbf{\Cref{ch:fact_alg} Factorization Algebras:} The third section introduces the concept of factorization algebras, together with its different variations, like prefactorization algebras and locally constant factorization algebras.
+Of these, the locally constant factorization algebras will be the ones that capture the different possible stratified structures that a manifold can have, and they will be a large focus of this work.
+The definitions of these will not be novel.
+They can be found in the works \cite{cg2016}, \cite{ginot2015} and even \cite{af_primer}.
+In fact, in the slightly different context of vertex algebras the idea can be traced back to \cite{bd2004}.
+However, all of the above works take a slightly different perspective in their presentation of the definitions, which we hope to unite in this work.
+The key result of this section is the following:
+%
+\begin{theorem*}[\ref{thm:disk_alg=lcfa}]
+    There is an equivalence of $\infty$-categories between locally constant factorization algebras over a stratified manifold $M$ and $\disk_{/M}$-algebras
+    %
+    \begin{equation}
+        \int: \alg{\disk_{/M}} (\catC) \xrightarrow{\ \ \simeq \ \ } \lcfa_M (\catC),
+    \end{equation}
+    %
+    given by factorization homology,
+\end{theorem*}
+%
+as well as its \Cref{cor:disk_alg=falg} for the case of ordinary factorization algebras.
+These show that the $\infty$-operad governing factorization algebras can be taken to be the slice $\infty$-operad $\disk_{/M}$ (or $\disk[r]_{/M}$ for the ordinary case).
+We then introduce some operations that we can do with factorization algebras like the pushforward and restriction, as well as state a result for locally constant factorization algebras on product spaces, which confirms a conjecture of \cite{ginot2015}:
+%
+\begin{proposition*}[\ref{prop:exp_of_products_lc}]
+    Let $M$ and $N$ be stratified manifolds. There is an equivalence of $\infty$-categories
+    %
+    \begin{equation}
+        \bar{\pi}: \lcfa_{M \times N}(\catC) \xrightarrow{\ \ \simeq \ \ } \lcfa_{M}(\lcfa_{N}(\catC)).
+    \end{equation}
+\end{proposition*}
+%
+Finally, we will examine some examples of factorization algebras whose construction is known, specifically, locally constant factorization algebras on the intervals $(-1,1)$, $[-1,1)$ and $[-1,1]$ as well as Euclidean spaces $\mathbb{R}^n$ more generally.
+
+\textbf{\Cref{ch:gluing_disk_alg} Collar-gluings and Disk Algebras:} The fourth section presents a novel result about the behavior of certain types of factorization algebras under the operation of collar-gluing in the manifold variable.
+It essentially shows that we can reproduce factorization algebras on a stratified manifold if we know them on some particular pieces of it together with the data of how to glue them.
+Formally, we have
+%
+\begin{theorem*}[\ref{thm:gluing_lcfas}]
+    Given a collar-gluing of stratified manifolds $f: M \rightarrow [-1,1]$, the $\infty$-category of locally constant factorization algebras is equivalent to the pullback of $\infty$-categories
+    %
+    \begin{equation}
+        \lcfa_{M} (\catC) \simeq \lcfa_{M_-} (\catC) \bigtimes_{\lcfa{M_0 \times \mathbb{R}} (\catC)} \\cfa_{M_+} (\catC).
+    \end{equation}
+\end{theorem*}
+%
+The results of the previous section a very important in the proof of this statement, because we heavily use the properties of factorization homology.
+A similar version holds for ordinary factorization algebras in the for of \Cref{cor:disk_alg=falg}.
+This result hugely expands the number of manifolds for which the $\infty$-category of locally constant factorization algebras can be specified.
+As a straightforward example, it gives a way to work on, and classify, factorization algebras on all higher spheres $S^n$.
+Without it, only the circle has been described to date (\cite{ginot2015}) using equivariant factorization algebras and inheritance from covering spaces.
+
+\textbf{\Cref{ch:classif_defect_mfld} Classifying $\lcfa$s on Defect Manifolds:} The fifth section focuses on the stratified structure and gives a way to express what effect this has on the locally constant factorization algebras.
+Specifically, we look at the data of a smooth manifold $M$ with a distinguished, properly embedded submanifold $\Sigma$ (also known as a defect submanifold) as the data of a stratified manifold $M_\Sigma$.
+We will show that, along with giving algebras associated to the different pieces, locally constant factorization algebras on these manifolds, in some (precise) sense, also encode a module structure associated with $\Sigma$.
+
+\textbf{Further Questions:} The exploration below naturally leads to questions that are beyond the scope of this work.
+As we will see, factorization algebras only need a topological space to be defined, but locally constant factorization algebras also capture information about the stratified structure.
+Neither of these, however, capture information about the tangential structure of the manifold, so the question arises:
+%
+\begin{itemize}
+    \item Does there exist a version of factorization algebras that usefully capture information both about the stratified structure of a manifold and about its tangential structure?
+\end{itemize}
+%
+The recent thesis \cite{pena2022} could provide a fruitful direction of exploration of the former concept.
+In a similar vein, \cite{cg2016} explain why it's important to have the concept of a $G$-equivariant factorization algebra, where $G$ is a Lie group.
+In particular, according to them, this asks for some definition of a smooth action of $G$ on factorization algebras.
+%
+\begin{itemize}
+    \item Is there a suitable way to encompass this notion in the formalism presented here?
+\end{itemize}
+%
+The beginnings of examining this idea can already be found in the thesis \cite{murray2020}, however the development there, while important, is still preliminary.
+
+\subsection{Conventions on \texorpdfstring{$\infty$}{infinity}-categories}
+
+The $\infty$-categories in this work will use the quasi-category model of $\infty$-category theory introduced by Joyal in \cite{joyal}, which is based on the simplicial sets introduced by \cite{bv73}.
+The work by Lurie in \cite{lurie_htt} and \cite{lurie_ha} greatly builds on this theory, and questions about fundamental objects or constructions that are in this text will always be answered in those references.
+This choice is because a great deal of the theory of factorization homology, as well as factorization algebras deal with $\infty$-categories of functors, which are most easily defined for quasi-categories.
+
+It is also important to note that we will not be making a notational distinction between topological categories, Kan enriched categories and $\infty$-categories because of the functors
+%
+\begin{equation}
+    \{ \mathsf{Top}\mathrm{-categories}\} \xrightarrow{\mathsf{Sing}} \{ \mathsf{Kan}\mathrm{-categories}\} \xrightarrow{\mathsf{N}} \cat,
+\end{equation}
+%
+which are both Quillen--equivalences in appropriate ways (\cite{joyal2007quasi,bergner2010survey}).
+In particular, we will not distinguish notationally the nerve of an ordinary category from the ordinary category itself.
+Similarly, we will not distinguish between (topological) multicategories and their $\infty$-operadic nerve.
+
+\subsection{Stratified Spaces}\label{ssec:strat_spaces}
+
+The spaces that this work will be set in will very often be stratified spaces.
+Thus, we first need to define what we mean by this concept.
+There are multiple definitions of stratified spaces in the literature, all of which have their advantages and disadvantages.
+For our purposes, we will follow the account of \cite{aft_localstrut}.
+A compatible source is also \cite[sec.A.5]{lurie_ha}.
+The majority of the work on factorization homology has so far been elaborated using this particular set of definitions, and similarly the stratified spaces used in the literature on factorization algebras are usually subsumed too.
+Further details are, of course, discussed in the original \cite{aft_localstrut}, where one can find great explanations of the definitions that are needed, and detailed proofs of the theorems that can be proven.
+
+\subsection{Factorization Homology}\label{ssec:fact_hom}
+
+Factorization homology (also known as topological chiral homology) is a construction that to the data of a smooth manifold $M$ and an algebra $A$ valued in a symmetric monoidal $\infty$-category $\catC$ assigns an object
+%
+\begin{equation}
+    \int_{M} A \in \catC.
+\end{equation}
+%
+The physical interpretation is that given a spacetime $M$ and local observables $A$, $\int_MA$ returns global observables, though typically not all of them.
+
+This implementation, with $M$ relaxed to a stratified manifold and $A$ to an appropriate type of algebra, is sometimes termed `alpha' factorization homology, as opposed to the `beta' version of \cite{ayala2020factorization} that evaluates $(\infty,n)$-categories on variframed stratified $n$-manifolds.
+In this work, we will be concerned, in this sense, with alpha factorization homology.
+
+Fixing the algebra, the construction is functorial with respect to open embeddings in the manifold variable, which is the starting point to show that it is a chain level homology theory in a generalized sense.
+The initial chiral version was first introduced in \cite{bd2004}, and a topological version was introduced by \cite{lurie_ha}.
+The theory of factorization homology in the manner that we will recall here has been developed in \cite{francis2013,af_fhtop, aft_fhstrat}.
+We will also follow the introductory text \cite{af_primer}.
+
+In the entirety of this work, we fix our target $\catC$ to be a symmetric monoidal $\infty$-category that is \emph{$\otimes$-presentable} \cite{af_fhtop}, i.e. it satisfies:
+%
+\begin{enumerate}
+    \item $\catC$ is presentable: it admits colimits, and every object is a filtered colimit of compact objects, and
+    \item the monoidal structure distributes over colimits: for all $c \in \catC$, the functor $c \otimes -: \catC \xrightarrow{} \catC$ takes colimit diagrams to colimit diagrams.
+\end{enumerate}
+
+\begin{remark}\label{rem:inherit_sym_mon_struct}
+    For developing the theory of factorization homology the assumption that $\catC$ has all \emph{sifted} colimits, and that the monoidal structure commutes with these, is enough.
+However, if we want the $\infty$-category of algebras valued in $\catC$ to inherit the properties of having sifted colimits that commute with the monoidal structure, then we must require that $\catC$ has \emph{all} (small) colimits.
+This will similarly be the case for factorization algebras.
+The stronger requirement also doesn't exclude any of the core examples that we are interested in.
+\end{remark}
+
+\begin{example}
+    The following are examples of $\otimes$-presentable categories:
+    %
+    \begin{enumerate}
+        \item chain complexes $\mathscr{C}\mathsf{h}_{\mathbb{k}}$ over a commutative ring $\mathbb{k}$, where equivalences are given by quasi-isomorphism.
+The symmetric monoidal structure can be both direct sum $\oplus$ or tensor product $\otimes$.
+        \item Any cocomplete, Cartesian closed $\infty$-category together with categorical product. (for example $\mathsf{Spaces}$ or $\cat$).
+    \end{enumerate}
+    %
+    In particular, $(\mathscr{C}\mathsf{h}_{\mathbb{k}}, \otimes)$ is the most relevant for physical examples which is why it is the target of choice in \cite{cg2016} and \cite{ginot2015}.
+\end{example}
+
+We also fix an $\infty$-category of basics $\bstr \xrightarrow{} \bsc$.
+
+\begin{remark}\label{rem:disk_b=disk_bsc}
+    Since we will be dealing with the relative case for the majority of the work, and because $\disk(\bstr)_{/M}$ (and the related slice $\infty$-operads) does not actually depend on the particular tangential structure, as long as $M$ admits it, we will simplify our notation down to $\disk_{/M}$.
+\end{remark}
+
+\begin{remark}\label{rem:fin_equiv_natural}
+    A few times in this work we will encounter the fact that a final functor $F: \mathscr{A} \xrightarrow{} \mathscr{B}$ between $\infty$-categories induces an equivalence
+    %
+    \begin{equation}\label{eq:fin_equivs_obj}
+        \mathsf{colim}(G) \xrightarrow{\ \ \simeq \ \ } \mathsf{colim}(G \circ F),
+    \end{equation}
+    %
+    for each functor $G: \mathscr{B} \xrightarrow{} \mathscr{C}$, whenever both colimits exist.
+We remark here that these equivalences are actually even natural in $G$.
+To explain this, we first notice that the equivalences in \Cref{eq:fin_equivs_obj} actually arise from equivalences between $\infty$-categories
+    %
+    \begin{equation}\label{eq:fin_equivs_cat}
+        \mathscr{C}_{G/} \xrightarrow{\ \ \simeq \ \ } \mathscr{C}_{G \circ F /},
+    \end{equation}
+    %
+    as discussed in \cite[prop.4.1.1.8]{lurie_htt}, where the functor is the obvious one.
+Furthermore, \cite[\href{https://kerodon.net/tag/016H}{016H}]{lurie_kerodon} tells us that the slice construction is functorial, which, after restricting, defines the functors
+    %
+    \begin{align}
+        &S: \mathsf{Fun}(\mathscr{B}, \mathscr{C}) \xrightarrow{\ \ \ } \cat& \mathrm{and}& &S': \mathsf{Fun}(\mathscr{A}, \mathscr{C}) \xrightarrow{\ \ \ } \cat,&
+    \end{align}
+    %
+    whose value on objects is given by $G \mapsto \mathscr{C}_{G/}$.
+We can now state that by naturality in $G$ we mean that the functors of \Cref{eq:fin_equivs_cat} assemble into an equivalence of functors
+    %
+    \begin{equation}
+        S \xrightarrow{\ \ \simeq \ \ } S' \circ F^*
+    \end{equation}
+    %
+    in $\mathsf{Fun}(\mathsf{Fun(\mathscr{B}, \mathscr{C})}, \cat)$.
+But this is obviously the case, given the description of the maps in \Cref{eq:fin_equivs_cat}, and amounts to nothing more than bookkeeping.
+\end{remark}
+
+In particular, the above remark slightly extends \cite[prop.2.34]{aft_fhstrat}, as well as \cite[thm.2.25]{aft_fhstrat}, which become:
+%
+\begin{proposition}[{\cite[thm.2.34]{aft_fhstrat}}]\label{prop:barconst=intinterval}
+    There is an equivalence of functors between the two-sided bar construction
+    %
+    \begin{equation}
+        \mathsf{B}: \alg{\mathsf{Assoc^{RL}}}(\catC) \xrightarrow{} \catC
+    \end{equation}
+    %
+    and factorization homology over the oriented closed interval
+    %
+    \begin{equation}
+        \int_{[-1,1]}: \alg{\mathsf{Assoc^{RL}}}(\catC)\simeq \alg{\disk_{/[-1,1]}} (\catC) \xrightarrow{\ \int \ } \alg{\mfld_{/[-1,1]}} (\catC) \xrightarrow{\ \mathsf{ev}_{[-1,1]} \ } \catC.
+    \end{equation}
+    %
+    In particular, given a unital, (homotopy) associative algebra $A$, a unital right $A$-module $R$ and a unital left $A$-module $L$, there is an equivalence of objects
+    %
+    \begin{equation}
+        \int_{[-1,1]} (R, A, L) \xrightarrow{\ \ \simeq \ \ } R \bigotimes\limits_{A} L.
+    \end{equation}
+\end{proposition}
+
+\begin{proposition}[{\cite[thm.2.25]{aft_fhstrat}}]\label{prop:fh_pushforward}
+    Let $f: M \xrightarrow{} N$ be a weakly constructible bundle. There is a pushforward functor
+    %
+    \begin{equation}
+        f_*: \alg{\disk_{/M}}(\catC) \xrightarrow{\quad} \alg{\disk_{/N}}(\catC).
+    \end{equation}
+    %
+    This functor is such that there is a canonical equivalence between functors
+    %
+    \begin{equation}
+        \int_M -, \int_N f_* - : \alg{\disk_{/M}} (\catC) \xrightarrow{\ \ \ \ } \catC.
+    \end{equation}
+\end{proposition}
 
@@
 The topological version that we present was then introduced by Lurie and subsequently further developed in \cite{cg2016}, especially for the purposes of mathematical physics.
-Here we will present these ideas following \cite{cg2016} and also \cite{af_primer}.
-A similar exposition can be found in \cite{ginot2015}.
-
-\begin{remark}
-    We note that we have fixed a symmetric monoidal $\infty$-category $\catC$ that is $\otimes$-presentable to serve as the $\infty$-category that our algebras will be valued in.
-\end{remark}
+
+Here we will present these ideas following \cite{cg2016} and \cite{ginot2015} while also trying to express them more categorically in the style of \cite{af_primer}.
+In this sense, the present work bridges a gap in how factorization algebras are usually presented.
 
@@
 \begin{remark}
-    It is obvious that in the case of (stratified) manifolds we have already seen alternative notation for the $\infty$-operad $\opens(X)$ before, namely $\mfld[r]_{/M}$.
+    Restricting to the case of (stratified) manifolds we have an alternative notation for the $\infty$-operad $\opens(X)$, namely $\mfld[r]_{/M}$.
 This makes a connection to the standard notation used around factorization homology, and is something that we'll make use of later.
@@
 \begin{remark}
-    The category $\opens[r](X)$ can be replaced with any other category that supports an analogue of the Weiss Grothendieck topology.
-In the case of (stratified) manifolds, $\opens[r](X)$ is already the same as $\mfld[r]_{/X}$, be we could just as well define Weiss cosheaves on $\mfld[r]$, i.e.
-$\csheaves[W](\mfld[r], \catC)$.
-If we're working with the $\infty$-categories $\mfld$ or $\mfld_{/X}$, then we define cosheaves on them through the pullback
+    If we're working with the $\infty$-category $\mfld_{/X}$, then we define cosheaves on it through the pullback
     %
@@
         \begin{tikzcd}
-            \csheaves[W] (\mfld, \catC) \arrow[dr, phantom, "\ulcorner", very near start] \arrow[r] \arrow[d] & \mathsf{Fun}(\mfld, \catC) \arrow[d] \\
-            \csheaves[W] (\mfld[r], \catC) \arrow[r] & \mathsf{Fun}(\mfld[r], \catC),
+            \csheaves[W] (\mfld_{/X}, \catC) \arrow[dr, phantom, "\ulcorner", very near start] \arrow[r] \arrow[d] & \mathsf{Fun}(\mfld_{/X}, \catC) \arrow[d] \\
+            \csheaves[W] (\mfld_{/X}, \catC) \arrow[r] & \mathsf{Fun}(\mfld_{/X}, \catC).
         \end{tikzcd}
     \end{equation}
-    %
-    and similarly for the relative case $\mfld_{/X}$.
 \end{remark}
@@
 
-\begin{remark}\label{rem:check_nerve}
+\begin{remark}\label{rem:cech_nerve}
     A factorization algebra is a prefactorization algebra whose restriction to $\opens[r](X)$ is a Weiss cosheaf.
@@
 
-All of our definitions above are valid for all topological spaces, so in particular, also the stratified spaces we introduced at the beginning.
+All of our definitions above are valid for all topological spaces, so in particular, also stratified spaces.
 For the next definition of locally constant factorization algebras though, it will be important to specify more information about the space.
 In other words, they will capture information about the stratification.
-
-There is a general definition of locally constant algebra objects in the context of any $\infty$-operad given in \cite[def.2.3.3.20]{lurie_ha}, which, of course, applies here.
-In our case one can also take a perspective more akin to \cite[def.A.1.12]{lurie_ha} by defining locally constant cosheaves and then pulling back this property to factorization algebras.
-This is what we will do, along with focusing our attention to stratified (and therefore also to smooth) manifolds.
-The definitions we will make can in a lot of cases also be expanded for any $C^0$ stratified space or topological manifold.
 
@@
 \begin{definition}
-    The $\infty$-category $\lcfa_M (\catC)$ of \emph{locally constant factorization algebras on a stratified manifold $M$ valued in $\catC$} is the full $\infty$-subcategory of $\falg_M (\catC)$ as in the pullback
+    The $\infty$-category $\lcfa_M (\catC)$ of \emph{locally constant}\footnote{There is a general definition of locally constant algebra objects in the context of any $\infty$-operad given in \cite[def.2.3.3.20]{lurie_ha}, which, of course, applies here.
+Our present perspective is more akin to \cite[def.A.1.12]{lurie_ha} whereby we define locally constant cosheaves and then pull this property back to factorization algebras.} \emph{factorization algebras on a stratified manifold $M$ valued in $\catC$} is the full $\infty$-subcategory of $\falg_M (\catC)$ as in the pullback
     %
@@
 \begin{remark}\label{rem:sym_mon_inheritance}
-    The $\infty$-categories of factorization algebras of all varieties acquire a symmetric monoidal structure from the symmetric monoidal structure of $\catC$ pointwise
+    As mentioned in \Cref{rem:inherit_sym_mon_struct}, our assumptions on the target $\catC$ allow the $\infty$-categories of factorization algebras of all varieties to acquire a symmetric monoidal structure from the symmetric monoidal structure of $\catC$ pointwise
     %
@@
     %
-    The only subtlety is the cosheaf condition, where the symmetric monoidal structure is induced only if we also take into account that in $\catC$ colimits commute with its symmetric monoidal structure.
+    To satisfy the cosheaf condition we use the property that colimits in $\catC$ commute with its symmetric monoidal structure.
 
@@
 
-Now that we have introduced all the varieties of factorization algebras, it's a natural and useful question to ask what the $\infty$-operad governing them is.
-For prefactorization algebras, the answer comes by definition, but this is not the case for factorization algebras.
-In the case of stratified manifolds, we will show that the $\infty$-operad that governs locally constant factorization algebras can be taken to be $\disk_{/M}$, and the one that governs ordinary factorization algebras can be taken to be $\disk[r]_{/M}$.
+The way that we have defined the different kinds of factorization algebras only makes clear what the $\infty$-operad governing them is in the case of prefactorization algebras.
+Limiting our discussion to stratified manifolds, as opposed to general topological spaces, we will show that the $\infty$-operad that governs locally constant factorization algebras can be taken to be $\disk_{/M}$, where we use the notation of \cite{aft_fhstrat}, (which \cite{lurie_ha} alternatively denotes $\mathbb{E}_M^{\otimes}$), and the one that governs ordinary factorization algebras can be taken to be $\disk[r]_{/M}$ (which \cite{lurie_ha} denotes $\mathrm{N}(\mathrm{Disk}(M))^\otimes$).
 This result is immensely helpful in relating factorization algebras to results in the area of disk algebras.
@@
 \begin{proposition}\label{prop:fh_disk_to_lcfa}
-    Given a stratified manifold $M$ factorization homology provides a functor between the $\infty$-categories of $\disk_{/M}$-algebras and locally constant factorization algebras $\lcfa_M$
+    Given a stratified manifold $M$, factorization homology provides a functor between the $\infty$-categories of $\disk_{/M}$-algebras and locally constant factorization algebras $\lcfa_M$
     %
@@
 By the definition of $\csheaves[W](\mfld_{/M}, \catC)$, this means that the restriction of $\int F$ to $\mathsf{Fun}(\mfld[r]_{/M}, \catC)$ satisfies the cosheaf property for every Weiss sieve $\mathscr{U} \subset (\mfld[r]_{/M})_{/e}$, where $e:N \xhookrightarrow{} M$ is an open embedding.
-Here we notice that for the Weiss property to even make sense, we are implicitly using \Cref{lem:double_slice}
+Here we notice that for the Weiss property to even make sense, we are implicitly using $(\mfld[r]_{/M})_{/(N \xhookrightarrow{} M)} \simeq \mfld[r]_{/N}$.
 
@@
     which is easier to compare to \Cref{eq:cosheaf_colim_relative}.
-Using the fact that $\disk[r]_{/M} \xrightarrow{} \disk_{/M}$ is a final functor, which is a consequence of \cite[prop.2.22]{aft_fhstrat}, and the equivalences of \Cref{lem:double_slice} we can rewrite \Cref{eq:idiosync_form} further into
+Using the fact that $\disk[r]_{/M} \xrightarrow{} \disk_{/M}$ is a final functor, which is a consequence of \cite[prop.2.22]{aft_fhstrat}, and the equivalence $(\disk_{/M})_{/(N \xhookrightarrow{} M)} \simeq \disk_{/N}$ we can rewrite \Cref{eq:idiosync_form} further into
     %
@@
 
+\begin{remark}
+    One perspective on this result, provided by \cite[thm.2.43]{aft_fhstrat}, is that the theory of locally constant factorization algebras captures as much information as (generalized) homology theory in the sense of \cite[def.2.37]{aft_fhstrat}.
+\end{remark}
+
 As before, the case of ordinary factorization algebras gets a similar statement whose proof goes along the same lines:
@@
 \begin{remark}
-    As noted at the beginning of \S 2, the physical interpretation of this version of factorization homology is a way to take a spacetime $M$ and its local observables $A$, and construct \emph{some}, and typically not all, of the global observables.
+    As noted at the beginning of \Cref{ssec:fact_hom}, the physical interpretation of this version of factorization homology is a way to take a spacetime $M$ and its local observables $A$, and construct \emph{some}, and typically not all, of the global observables.
 The previous \Cref{thm:disk_alg=lcfa} and \Cref{cor:disk_alg=falg} transfer this observation to factorization algebras, which aligns with the observation of \cite{cg2016} that the current version of factorization algebras can only deal with perturbative quantum field theory.
@@
 \end{lemma}
-
-\begin{remark}
-    If we limit $M$ to be a basic then the requirements of the lemma are exactly that $M$ is final in $\bstr_M$.
-\end{remark}
 
@@
     This functor is an equivalence on maximal $\infty$-subgroupoids because for any $V \in \disk(\bstr_M)$ the space of morphisms to $M$ is contractible, so, up to equivalence it is unique.
-%To check that it is fully faithful we need to show that the induced maps
-    %
-    %\begin{equation}
-    %    \mathsf{Hom}_{\disk(\bstr)_{/U}} (V \xhookrightarrow{} U, V' \xhookrightarrow{} U) \xrightarrow{\ \ \ \ } \mathsf{Hom}_{\disk(\bstr)} (V, V')
-    %\end{equation}
-    %
-    %are equivalences. Giving a functor $\disk (\bstr) \xrightarrow{} \disk (\bstr)_{/U}$ is the same as giving a functor
-    %
-    %\begin{equation}
-    %    \disk (\bstr) ^{\vartriangleright} \xrightarrow{} \disk (\bstr)_{/U},
-    %\end{equation}
-    %
-    %which sends the cone point to $U$ (see e.g. \cite[prop.3.2]{joyal}).
 Full faithfulness is provided by the fact that the functor on the active $\infty$-subcategories $\disk_{/M} \xrightarrow{} \disk(\bstr_M)$ is a right fibration.
@@
 The results of \Cref{thm:disk_alg=lcfa} and \Cref{cor:disk_alg=falg} can also be seen as lowering the amount of data that is necessary to say that we have defined a factorization algebra on a stratified manifold.
-There is a similar, but slightly weaker result by \cite{cg2016}, which nonetheless works for all Hausdorff topological spaces.
-We recount this result here for comparison.
-
-\begin{definition}
-    A \emph{factorizing basis} of a topological space $X$ is a basis $\{ U_i \xhookrightarrow{} X\}_{i \in I}$ for the topology of $X$ which is closed under finite intersections, and which satisfies that for each finite set $S \subset X$, there exists a finite sub-collection of pairwise disjoint open subsets $\{ U_j \xhookrightarrow{} X\}_{j \in J}$, for which $S \subset \bigsqcup_{j \in J} U_j$.
-\end{definition}
-
-\begin{definition}
-    We will call factorization algebras defined only on the open subsets of an open cover $\mathscr{U}$ (in particular, for example, a factorizing basis), a $\mathscr{U}$-factorization algebra and the $\infty$-category of such $\falg_{\mathscr{U}}(\catC)$.
-\end{definition}
-
-\begin{theorem}[\cite{cg2016}]\label{thm:fa_from_basis}
-    Given a Hausdorff topological space $X$, there is an equivalence of $\infty$-categories between the $\infty$-categories of $\mathscr{U}$-factorization algebras defined on a factorizing basis $\mathscr{U}$ and factorization algebras defined on the full topological space $X$
-    %
-    \begin{equation}
-        \begin{tikzcd}
-            \falg_X(\catC) \arrow[rr, bend left=10, "\mathrm{-|_{\mathscr{U}}}"] &  & \falg_{\mathscr{U}}(\catC) \arrow[ll, bend left=10, "\mathrm{ext}"],
-        \end{tikzcd}
-    \end{equation}
-    %
-    where the top functor is given by restriction.
-\end{theorem}
-
-\begin{remark}
-    Looking into the proof of this statement we see that the value of the extension on open sets $U \subset X$ is defined as
-    %
-    \begin{equation}
-        \mathrm{ext}(F)(U) := \cech(\mathscr{U}_U, F),
-    \end{equation}
-    %
-    where $\mathscr{U}_U$ is a Weiss cover of $U$ generated by $\mathscr{U}$.
-That such a cover exists is already guaranteed by the Hausdorffness of $X$ and the basis property of $\mathscr{U}$.
-Namely, given any finite set $S \subset U$, Hausdorffness gives us the existence of pairwise disjoint open sets $\{ V_s \ni s\}_{s \in S}$, while the basis property of $\mathscr{U}$ gives us open subsets $\{ U_s \in \mathscr{U} \}_{s \in S}$ such that $s \in U_s \subset V_s$.
-$\sqcup_{s \in S} U_s$ then gives an open set that covers $S$.
-\end{remark}
-
-\begin{remark}
-    The proof of \Cref{thm:fa_from_basis} can be found in \cite[ch.7.2]{cg2016}, and we will not reproduce it here.
-The target category there is the category of chain complexes, but it holds more generally in $\catC$ by considering simplicial objects and their geometric realizations (which exist by the colimit assumption on $\catC$) instead.
-
-    As mentioned, in the stratified manifold case, this is an easy corollary of the proof of \Cref{prop:fh_disk_to_lcfa}, where we show that taking all disks as the Weiss cover of choice reproduces the result that we would have gotten with any other Weiss cover.
-It is important to point out though that disks are not necessarily closed under intersections, which means that we don't have the opposite implication, and the methods to prove \Cref{prop:fh_disk_to_lcfa} are necessary.
-\end{remark}
+There is a similar, but slightly weaker result \cite[ch.7.2]{cg2016}, which nonetheless works for all Hausdorff topological spaces.
+The main difference between our result and the result of \cite{cg2016} is that, unlike the `factorizing basis' defined there, we don't require our disks to be closed under finite intersections.
 
@@
 There are a few important operations that we can do with factorization algebras (and the other mentioned variants) that will be important for our considerations.
-They allow us to compare factorization algebras from different spaces and will play a big role in any kind of classification statement one might make.
 
@@
 \begin{corollary}\label{cor:pushforward_for_lc}
-    Let $f: M \xrightarrow{} N$ be a constructible bundle of stratified manifolds. Then the pushforward functor for factorization homology of \Cref{thm:fh_pushforward} serves as a pushforward
+    Let $f: M \xrightarrow{} N$ be a constructible bundle of stratified manifolds. Then the pushforward functor for factorization homology of \Cref{prop:fh_pushforward} serves as a pushforward
     %
@@
 \begin{lemma}\label{lem:ff_functor_to_refinement}
-    Let $u: X \rightarrow \hat{X}$ be the morphism of \Cref{ex:forget_strat} that forgets the stratification.
-    The functor $u_*: \lcfa_{X} (\catC) \rightarrow \lcfa_{\hat{X}} (\catC)$ has a fully faithful left adjoint.
+    Let $u: X \rightarrow \hat{X}$ be the morphism that forgets the stratification. The functor $u_*: \lcfa_{X} (\catC) \rightarrow \lcfa_{\hat{X}} (\catC)$ has a fully faithful left adjoint.
 \end{lemma}
@@
 In the opposite direction, we do not, in general, have a pullback functor.
-\cite{cg2016} provide a construction of a pullback in the case of open immersions, but we will only focus on the case of restrictions.
-Namely, given an open subset $U \subset X$ of a topological space $X$, and given a factorization algebra $F \in \falg_X$ we can clearly define a factorization algebra $F|_{U} \in \falg_U$ by restricting to those open subsets that are fully contained in $U$.
+\Cite{cg2016} provide a construction of a pullback in the case of open immersions, but we will only focus on the case of restrictions.
+Namely, given an open subset $U \subset X$ of a topological space $X$, and given a factorization algebra $F \in \falg_X$ we can clearly define a factorization algebra $F|_{U} \in \falg_U$ by restricting to those open subsets that are fully contained in $U$, which gives a functor
+%
+\begin{equation}
+    \falg_X (\catC) \xrightarrow{\ \ -|_U \ \ } \falg_U (\catC).
+\end{equation}
+%
 Furthermore, this clearly holds not only for factorization algebras, but prefactorization algebras and locally constant factorization algebras too.
@@
 \end{proposition}
-
-\begin{remark}
-    The conditions we imposed on $\catC$ allowed us, in \Cref{rem:sym_mon_inheritance}, to inherit a symmetric monoidal structure on the $\infty$-categories of factorization algebras of all varieties.
-It also allowed us to inherit the existence of colimits.
-This is the reason why the above can even be stated.
-\end{remark}
 
@@
 
-    It is not hard to check that the above also holds for the example of factorization algebras on topological spaces, by using \Cref{thm:fa_from_basis}.
+    It is not hard to check that the above also holds for the example of factorization algebras on topological spaces, by using the result of \cite[ch.7.2]{cg2016}.
 However, we'll focus on manifolds, in which case, the construction from above immediately works since we now have to do it for $\disk[r]_{/X}$ instead of $\mfld[r]_{/X}$.
@@
 
-As was the case with factorization homology, so too with factorization algebras we now turn to a few very important constructions of locally constant factorization algebras on intervals.
+We now turn to a few very important constructions of locally constant factorization algebras on intervals.
 Namely, we will consider how we can construct a locally constant factorization algebra on the spaces $\mathbb{R}$ (a.k.a.
@@
     Consider a unital, (homotopy) associative algebra $A$ in the category $\catC$.
-For a first pass we use \Cref{thm:fa_from_basis} to construct a factorization algebra out of this data.
-We first check that the disks $\disk[r]_{/\mathbb{R}}$ of $\mathbb{R}$ form a factorizing basis.
-This is true since the disks are always a basis for any manifold, they are factorizing since we have all disjoint unions, and they are closed under finite intersections because the disks of $\mathbb{R}$ are intervals.
-Therefore, by \Cref{thm:fa_from_basis}, we need only assign values to these.
-Given any disk $U$ we assign the same value, $F_A(U) := A$.
+We take the opportunity to construct a factorization algebra out of this data by hand.
+This is a feasible task since any open is some disjoint union of intervals.
+Thus, given any disk $U$ we assign the same value, $F_A(U) := A$.
 Similarly, given a multi-morphism $\sqcup_{i \in I} U_i \xhookrightarrow{} U$, with $I$ non-empty, we assign the map given by the multiplication of $A$
@@
 At this point we have constructed a prefactorization algebra on $\mathbb{R}$.
-To use \Cref{thm:fa_from_basis} we need to first check the Weiss cosheaf condition.
-But because intervals are closed under finite intersections the \v{C}ech nerve definition of \Cref{rem:check_nerve} makes this easy; the simplicial object $\cech_{\bullet}(\disk[r]_{/\mathbb{R}}, F_A)$ in all degrees will be a coproduct of copies of $A$.
-Thus, $F_A$ is indeed a $\disk[r]_{/\mathbb{R}}$-factorization algebra and can be extended to a factorization algebra on $\mathbb{R}$.
-By definition, it is also obviously locally constant.
+Next we need to check the Weiss cosheaf condition.
+Because intervals are closed under finite intersections the \v{C}ech nerve definition of \Cref{rem:cech_nerve} makes this easy; the simplicial object $\cech_{\bullet}(\disk[r]_{/\mathbb{R}}, F_A)$ in all degrees will be a coproduct of copies of $A$.
+Thus, $F_A$ is indeed a factorization algebra.
+From the definition, it is also obviously locally constant.
 
@@
 As before, the unit comes from the map $F(\emptyset \xhookrightarrow{} \mathbb{R}) = (\mathbb{1} \rightarrow A)$.
-Thus, we have constructed an $\mathbb{E}_1$-algebra from the given data, and the proposition holds.
 \end{proof}
@@
 
-It's not hard to extend \Cref{con:lcfas_on_R} and \Cref{con:lcfas_on_hoint} to the closed interval $[-1,1]$ by hand, but through \Cref{thm:disk_alg=lcfa} we can see that \Cref{prop:disk1bor_over_int=ORL} and \Cref{prop:env_ORL=env_assocRL} already do all the necessary work.
+It's not hard to extend \Cref{con:lcfas_on_R} and \Cref{con:lcfas_on_hoint} to the closed interval $[-1,1]$ by hand, but through \Cref{thm:disk_alg=lcfa} we can see that \cite[cor.2.33]{aft_fhstrat} already do all the necessary work.
 
@@
 
-In this section we want to describe locally constant factorization algebras on Euclidean spaces $\mathbb{R}^n$.
-By \Cref{lem:disk/M_to_disk} we can hope for an $\infty$-category of basics such that we simplify the situation down to $\disk (\bstr)$-algebras.
-In fact, since $\mathbb{R}^n$ is frameable an $\infty$-category of basics that we can choose is $\mathsf{D}_n^* \simeq * \xrightarrow{\{ \mathbb{R}^n\}} \bsc$.
-Specifically, this makes us focus on framed $n$-dimensional disk algebras
-%
-\begin{equation}
-    \lcfa_{\mathbb{R}^n} (\catC) \simeq \alg{\disk (\mathsf{D}_n^*)} (\catC).
-\end{equation}
-%
-
 \begin{theorem}[{\cite[thm.5.5.4.10]{lurie_ha}}]
@@
 \begin{proof}
-    With our setup, thanks to \Cref{thm:disk_alg=lcfa} and \Cref{lem:disk/M_to_disk}, it is sufficient to show that there is an equivalence of $\infty$-operads
+    Since $\mathbb{R}^n$ is frameable, we can choose the $\infty$-category of basics $\mathsf{D}_n^* \simeq * \xrightarrow{\{ \mathbb{R}^n\}} \bsc$, and use \Cref{lem:disk/M_to_disk} to simplify the question; This makes us focus on framed $n$-dimensional disk algebras
+    %
+    \begin{equation}
+        \lcfa_{\mathbb{R}^n} (\catC) \simeq \alg{\disk (\mathsf{D}_n^*)} (\catC).
+    \end{equation}
+    %
+    With this, it is sufficient to show that there is an equivalence of $\infty$-operads
     %
@@
     But this is just the classical fact, that the little $n$-disks operad and the little $n$-cubes operad are equivalent, in disguise.
+One account of this fact with our terminology is, for example, \cite[prop.2.12]{aft_fhstrat}.
 \end{proof}
-
-\begin{remark}
-    We already encountered the $n=1$ version of the proposition above when we discussed locally constant factorization algebras on the open interval in \Cref{prop:R_gives_E1}, and the construction there gives us an intuition about how to actually construct the locally constant factorization algebra from the data of the $\mathbb{E}_n$-algebra.
-The theorem formalizes that this assignment is, in fact, an equivalence.
-\end{remark}
 
@@
 By \Cref{prop:exp_of_products_lc} we know that $F|_{S^{n-1} \times \mathbb{R}} \in \lcfa_{\mathbb{R}} (\lcfa_{S^{n-1}} (\catC))$, so that in particular it is an $\mathbb{E}_1$-algebra.
-If we pushforward to $\mathbb{R}$, by the discussion at \Cref{rem:fh_is_pushingforward} we could denote the resulting $\mathbb{E}_1$-algebra by \footnote{We again refer the reader to \Cref{rem:fh_is_pushingforward} for a reason why this notation is good.}
+If we pushforward to $\mathbb{R}$, by the discussion at \Cref{rem:fh_is_pushingforward} we could denote the resulting $\mathbb{E}_1$-algebra by
     %
@@
     %
-    This result goes towards an explanation of the appearance of factorization homology over higher spheres in the classification statement of \Cref{thm:classif_disk_d_under_n*_alg}.
+    This result goes towards an explanation of the appearance of factorization homology over higher spheres in the classification statement of \cite[prop.4.8]{aft_fhstrat}.
 \end{remark}
@@
 
+% Generate bibliography
+\newpage
+\printbibliography
+
 \end{document}

### 2024-04-04 sections/4gluing_alt.tex
Small addition to 4.

@@
 
-\section{Collar-gluings and Disk Algebras}\label{ch:gluing_disk_alg}
+\section{Collar-gluings and Factorization Algebras}\label{ch:gluing_disk_alg}
 
@@
 Having described what happens to a locally constant factorization algebras under collar-gluings of manifolds, we now turn to sequential colimits.
+{\color{red} The gluing result has an ordinary (nonhomotopy) limit.
+Is this also the output of the (co)bar construction?}
 
@@
 %
-for each basic $U \in \bsc$.
+for each disk $U \in \bsc$.
 
-After a simplification down to disks, in the locally constant case , lemma \Cref{lem:disk/M_to_disk} points towards a result like the following:
+After a simplification down to disks, in the locally constant case, lemma \Cref{lem:disk/M_to_disk} points towards a result like the following:
 
-\begin{conjecture}
-    The theory of locally constant factorization algebras is fully determined, using factorization homology, by the data of a functor
-    %
-    \begin{equation}
-        \bsc \xrightarrow{\ \ \ \ } \cat^{\mathsf{op}},
-    \end{equation}
-    %
-    which to each basic $U$ attaches the $\infty$-category $\mathsf{Fun}^{\otimes} (\disk(\mathsf{B}_U), \catC)$ of disk algebras with $\mathsf{B}_U$ structure, where $\mathsf{B}_U$ is the sieve poset whose maximal element is $U$.
-\end{conjecture}
+%\begin{conjecture}
+%    The theory of factorization algebras is fully determined, using factorization homology, by the data of a functor
+%    %
+%    \begin{equation}
+%        \mathsf{Bsc} \xrightarrow{\ \ \ \ } \cat^{\mathsf{op}}.
+%    \end{equation}
+%    %
+%    In the locally constant case, we can even say that to each basic $U$ this functor attaches the $\infty$-category $\mathsf{Fun}^{\otimes} (\disk(\mathsf{B}_U), \catC)$ of disk algebras with $\mathsf{B}_U$ structure, where $\mathsf{B}_U$ is the sieve poset whose maximal element is $U$.
+%\end{conjecture}
+
+%\begin{remark}
+%    The $\infty$-category of basics $\mathsf{B}_{U}$ for our purposes provides a kind of generalization of framing, which makes calculation easier.
+%\end{remark}
 

### 2024-04-04 sections/5classification.tex
Small addition to 4.

@@
     for all $i \in \mathbb{N}$, where $\mathsf{Emb}^* ((\mathbb{R}^n)^{\sqcup i}, \mathbb{R}^n \setminus \{0\})$ is the space of framed embeddings of $i$ $n$-dimensional disks into the punctured $\mathbb{R}^n$.
-All of these facts are partially an elaboration of the fact that $\mathsf{D}_{0 \subset n}^*$ is equivalent to $\Delta^1 = \{0 \xrightarrow{} 1\}$ as $\infty$-categories (saying nothing about the right fibration to $\bsc$).
+%All of these facts are partially an elaboration of the fact that $\mathsf{D}_{0 \subset n}^*$ is equivalent to $\Delta^1 = \{0 \xrightarrow{} 1\}$ as $\infty$-categories (saying nothing about the right fibration to $\bsc$).
 
@@
 \begin{proof}
-    From \Cref{eq:focus_on_disk_dn} we know that when $n > 1$ we have
+    From \cref{eq:focus_on_disk_dn} we know that when $n > 1$ we have
     %

### 2024-04-12 sections/3algebras.tex
Some work in section 4.
Small correction in section 3.5.

@@
 \end{proof}
+
+\begin{remark}
+    One perspective on this result, provided by \cite[thm.2.43]{aft_fhstrat}, is that the theory of locally constant factorization algebras captures as much information as (generalized) homology theory in the sense of \cite[def.2.37]{aft_fhstrat}.
+\end{remark}
 
@@
 \begin{proof}
-    With our setup, thanks to \Cref{thm:disk_alg=lcfa} and \Cref{lem:disk/M_to_disk}, it is sufficient to show that there is an equivalence of $\infty$-operads
+    With our setup, thanks to \Cref{thm:disk_alg=lcfa} and \Cref{lem:disk/M_to_disk}, it is sufficient to show that there is a weak equivalence of $\infty$-operads between $\disk (\mathsf{D}_n^*)$ and $\mathbb{E}_n$, i.e.
     %
     \begin{equation}
-        \disk (\mathsf{D}_n^*) \xrightarrow{\ \ \simeq \ \ } \mathbb{E}_n.
+        \alg{\disk (\mathsf{D}_n^*)} \xrightarrow{\ \ \simeq \ \ } \alg{\mathbb{E}_n}.
     \end{equation}
     %
-    But this is just the classical fact, that the little $n$-disks operad and the little $n$-cubes operad are equivalent, in disguise.
+    But this is just the fact that the $\disk_{/M}$ $\infty$-operad gives rise to $E_n$-algebras from \cref{prop:framed_ndisk=En}.
 \end{proof}

### 2024-04-17 sections/4gluing_alt.tex
Work in section 4.2.

--- 2024-03-24 sections/4gluing_alt.tex
@@
 Namely, given the disk $V \xhookrightarrow{} M$, we can take a larger disk $V'$, which is guaranteed to exist from the fact that $M$ is a manifold.
-The figure then shows that given any collar-gluing of $V$ we can find one particular collar-gluing of $M$ that extends the one of $V$.
+The figure then shows that given any collar-gluing of $V$ how we can find one particular collar-gluing of $M$ that extends the one of $V$.
 Since $V'$ is a disk, the figure does not obscure any detail.
@@
 
-\subsection{An Outside View of Factorization Algebras ({\color{red} Work In Progress})}
+\subsection{An Outside View of Factorization Algebras}
 
@@
 In the case of disjoint union, \Cref{thm:gluing_lcfas} and \Cref{cor:gluing_falgs} then provide the equivalences that are needed to make these into symmetric monoidal functors, where the symmetric monoidal product on $\cat^{\mathsf{op}}$ is given by \emph{coproduct}.
+We emphasize that the domain of these functors, as defined, is $\mfld[r]$; there is no clear way of how to define the above functors so that they have the domain $\mfld$ with the idea of restriction functors as morphisms.
 
@@
 Having described what happens to a locally constant factorization algebras under collar-gluings of manifolds, we now turn to sequential colimits.
+{\color{red} The gluing result has an ordinary (nonhomotopy) limit.
+Is this also the output of the (co)bar construction?}
 
-\begin{proposition}
+\begin{proposition}\label{prop:fa_seq_col}
     The functors $\falg(\catC)$ and $\lcfa(\catC)$ respect sequential colimits.
@@
 \begin{proof}
-    The proof will go along the same lines for both, so we will focus on factorization algebras, and shorten notation to $\mathscr{F} := \falg (\catC): \mfld[r] \xrightarrow{} \cat^{\mathsf{op}}$.
-We will also use the convention that we work in $\cat$ instead of its opposite.
-In these terms, the statement we need to prove is that the canonical functor
+    Using \Cref{thm:disk_alg=lcfa} and \Cref{cor:disk_alg=falg} we will argue in terms of algebras over $\infty$-operads.
+Since the formation of algebras is contravariantly functorial (as precomposition), it is sufficient to show that there is an equivalence of $\infty$-operads
     %
     \begin{equation}
-        \mathscr{F}(M) \xrightarrow[\alpha]{\ \ \simeq \ \ } \mathsf{lim} (\mathscr{F}(M_0) \xleftarrow{} \mathscr{F}(M_1) \xleftarrow{} \dots)
+        \mathsf{colim}_{i \geq 0} \disk_{/M_i} \xrightarrow{\ \ \simeq \ \ } \disk_{M},
     \end{equation}
     %
-    is an equivalence of $\infty$-categories, where $M := \cup_{i \geq 0} M_i$. All functors used to make the diagram are restriction functors.
-
-    An object of the limit is a collection $(A_0, A_1, \dots)$ of factorization algebras on $M_0, M_1, \dots$, respectively, together with equivalences $\eta_i: A_i \simeq A_{i+1}|_{M_i}$ for $i \geq 0$.
-Towards showing essential surjectivity of $\alpha$ we will construct the factorization algebra $A$ on $M$ given by the following prescription.
-Given any open $U \subset M$, there will be an integer $i$, such that $U \subset M_i$; we take the smallest such integer, call it $i_U$, and define
+    as well as the same for $\disk[r]_{/M}$.
+In the case of the former, as originally noted in the proof of \cite[cor.2.40]{aft_fhstrat}, the result follows from using \cite[cor.1.6.]{dugger2004hypercovers}, an argument about configuration spaces, as well as \cite[lem.2.21]{aft_fhstrat}, which explains the relation of these to the above operad.
+In the case of the latter, the situation is even simpler because of its discrete nature.
+One way to show this is to notice that the functor from the ordinary, nonhomtopy colimit factors through $\mathsf{colim}_{i \geq 0} \disk[r]_{/M_i} \xrightarrow{} \disk[r]_{/M}$, in which case it suffices to find an equivalence of \emph{ordinary} categories
     %
     \begin{equation}
-        A(U) := A_{i_U} (U).
+        \mathsf{colim}_{i \geq 0} \disk[r]_{/M_i} \xrightarrow{} \disk[r]_{/M},
     \end{equation}
     %
-    Given a morphism $U \xhookrightarrow{} V$ we know that $i_U \leq i_V$, and the morphism we assign is
+    where the colimit is now the one relevant to ordinary category theory, namely the nonhomotopy one.
+But it's now easy to see that this the canonical morphism above is an equivalence since for every $U \in \disk_{/M}$ there will be a finite integer $i$, such that $U \subset M_i$.
+\end{proof}
+
+With this result we have fully described an algorithm of how to compute the $\infty$-category of factorization algebras on any stratified manifold if we know how to compute it on the basics.
+Through this algorithm the theory of (locally constant) factorization algebras is fully determined by the assignment
 %
 \begin{equation}
-        A(U \xhookrightarrow{} V) := A_{i_U}(U) \xrightarrow{\eta_{i_U}(U)} \cdots \xrightarrow{\eta_{i_V - 1}(U)} A_{i_V} (U) \xrightarrow{A_{i_V} (U \xhookrightarrow{} V)} A_{i_V} (V).
-    \end{equation}
-
-    ...
-
-    Using \Cref{thm:disk_alg=lcfa} and \Cref{cor:disk_alg=falg}, we will take the disk algebra incarnation of the relevant $\infty$-categories.
-\end{proof}
-
-\begin{proposition}
-    {\color{red} (Probably untrue)} Factorization algebras can be formulated as functors
-    %
-    \begin{equation}
-        \falg_{-}(\catC), \lcfa_{-}(\catC): \mfld \xrightarrow{\ \ \ \ } \cat^{\mathsf{op}}.
-    \end{equation}
-\end{proposition}
-
-\begin{proof}
-    The proof will go along the same lines for both, so we will focus on factorization algebras, and shorten notation to $\mathscr{F} := \falg (\catC): \mfld[r] \xrightarrow{} \cat^{\mathsf{op}}$.
-Beyond the obvious assignment on objects, to define the functor we need to provide a map of spaces
-    %
-    \begin{equation}
-        \mathsf{Hom}_{\mfld}(M, N) \xrightarrow{\ \ \eta \ \ } \mathsf{Fun}(\mathscr{F}(N), \mathscr{F}(M))^{\simeq}.
+    U \mapsto \falg_U (\catC),
 \end{equation}
 %
-    This data can be provided in the form of a map of simplicial sets, whose components are
+for each disk $U \in \mathsf{Bsc}$.
+
+%\begin{conjecture}
+%    The theory of factorization algebras is fully determined, using factorization homology, by the data of a functor
+%    %
+%    \begin{equation}
+%        \mathsf{Bsc} \xrightarrow{\ \ \ \ } \cat^{\mathsf{op}}.
+%    \end{equation}
+%    %
+%    In the locally constant case, we can even say that to each basic $U$ this functor attaches the $\infty$-category $\mathsf{Fun}^{\otimes} (\disk(\mathsf{B}_U), \catC)$ of disk algebras with $\mathsf{B}_U$ structure, where $\mathsf{B}_U$ is the sieve poset whose maximal element is $U$.
+%\end{conjecture}
 %
-    \begin{equation}
-        \mathsf{Emb}_{\Delta^p}(M \times \Delta^p, N \times \Delta^p) \xrightarrow{\ \ \eta_p \ \ } \mathsf{Fun}(\mathscr{F}(N), \mathscr{F}(M))^{\simeq}_p,
-    \end{equation}
-    %
-    where the morphism space notation was introduced in \Cref{def:mfld_infty_cat}.
-Any map from a space will factor through the maximal $\infty$-groupoid of the codomain, so that we can drop the $^{\simeq}$ requirement.
-Unraveling the definition of a functor category at the same time means that we need to provide maps
-    %
-    \begin{equation}
-        \mathsf{Emb}_{\Delta^p}(M \times \Delta^p, N \times \Delta^p) \xrightarrow{\ \ \eta_p \ \ } \mathsf{Hom}_{\mathsf{sSet}}(\mathscr{F}(N) \times \Delta^p, \mathscr{F}(M)).
-    \end{equation}
-    %
-    And indeed,
-    %
-    \begin{align}
-        \mathsf{Emb}_{\Delta^p}(M \times \Delta^p, N \times \Delta^p) \xhookrightarrow{\ \ \ \ \ \ \ }& \mathsf{Emb}(M \times \Delta^p, N \times \Delta^p) \\
-        \xrightarrow{\mathrm{restrict}}& \mathsf{Hom_{sSet}} (\mathscr{F}(N \times \Delta^p), \mathscr{F}(M \times \Delta^p)) \\
-        \xrightarrow{\ \pi_{1*} \circ -}& \mathsf{Hom_{sSet}} (\mathscr{F}(N \times \Delta^p) , \mathscr{F}(M)) \\
-        \xrightarrow{\ - \circ \alpha^p \ }& \mathsf{Hom_{sSet}} (\mathscr{F}(N) \times \Delta^p , \mathscr{F}(M)).
-    \end{align}
-    %
-    Let us further describe the final arrow. It arises as a functor
-    %
-    \begin{equation}
-        \mathscr{F} (N) \times \Delta^p \xrightarrow{\ \ \alpha^p \ \ } \mathscr{F}(N \times \Delta^p),
-    \end{equation}
-    %
-    whose components are given by
-    %
-    \begin{equation}
-        \alpha^p_m: \mathscr{F} (N)_m \times \mathsf{Hom}_{\Delta}([m], [p]) \xrightarrow{} \mathscr{F}(N \times \Delta^p)_m.
-    \end{equation}
-    %
-    ......
-\end{proof}
-
-{\color{red} Work in progress}
-
-This perspective on the theory of locally constant factorization algebras as a functor reframes the gluing result \Cref{thm:gluing_lcfas}, and together with lemma \Cref{lem:disk/M_to_disk} points towards a result like the following:
-
-\begin{conjecture}
-    The theory of locally constant factorization algebras is fully determined, using factorization homology, by the data of a functor
-    %
-    \begin{equation}
-        \bsc \xrightarrow{\ \ \ \ } \cat^{\mathsf{op}},
-    \end{equation}
-    %
-    which to each basic $U$ attaches the $\infty$-category $\mathsf{Fun}^{\otimes} (\disk(\mathsf{B}_U), \catC)$ of disk algebras with $\mathsf{B}_U$ structure, where $\mathsf{B}_U$ is the sieve poset whose maximal element is $U$.
-\end{conjecture}
-
-%\begin{proof}
-%    The second part of the statement simply concerns what data defines a locally constant factorization algebra on a disk. 
-%\end{proof}
+%\begin{remark}
+%    The $\infty$-category of basics $\mathsf{B}_{U}$ for our purposes provides a kind of generalization of framing, which makes calculation easier.
+%\end{remark}
 

### 2024-04-23 sections/1stratified.tex
until 2.3

--- 2024-03-18 sections/1stratified.tex
@@
 In other words, $\mathsf{D}_1^{\partial, \mathsf{or}}$ has objects $\mathbb{R}$, $\hoint$ and $\mathbb{R}_{\leq 0}$ with their canonical orientations, and the morphisms are orientation preserving embeddings between them.
-In this way, $\mathsf{D}_1^{\partial, \mathsf{or}}$ is the $\infty$-category of basics that describes oriented (or, equivalently in this case, framed), smooth 1-manifolds with boundary.
+In this way, $\mathsf{D}_1^{\partial, \mathsf{or}}$ is the $\infty$-category of basics that describes oriented (or, equivalently in this dimension, framed), smooth 1-manifolds with boundary.
 \end{construction}
 
-\begin{remark}
+\begin{remark}\label{16GY5V1}
     Insisting that tangential structures be \emph{right fibrations} over $\bsc$, as opposed to simply $\infty$-categories over it as, e.g., in \cite{ayala2020factorization}, leads to technical issues that lead to our over-simplified notation due to the property of being a right fibration not being invariant under equivalence.

### 2024-04-23 sections/2homology.tex
Pushing previous changes.
until 2.3

@@
 We will now recall the $\infty$-category of disk algebras with a chosen tangential structure valued in a symmetric monoidal $\infty$-category.
-First, consider, following \cite{lurie_ha}, the category $\mathsf{Fin}_\ast$ whose objects are the sets $\langle n\rangle=\{\ast,1,\dots,n\}$ and whose morphisms are functions that preserve the distinguished point $\ast$.
-For every $i\in\{1,\dots,n\}$ there is a map $\rho^i\colon\langle n\rangle\to\langle 1\rangle$ that sends $i$ to $1$ but is otherwise constant at $\ast\in\langle1\rangle$.
+First, consider, following \cite{lurie_ha}, the category $\mathsf{Fin}_\ast$ whose objects are the sets $\langle n\rangle=\{\ast,1,\dots,n\}$ and whose morphisms are functions that preserve the distinguished point $\ast$.\footnote{\label{YNAXOHZ}This category is meant to re-express the category of finite sets and \emph{partially-defined} functions over which the notion of a multicategory may be reformulated; cf.\ \cite[Construction 2.1.1.7]{lurie_ha}.
+A partially-defined function $f\colon\lrangle{n}^\circ\coloneqq\{1,\dots,n\}\to\lrangle{m}$ induces an ordinary function $\lrangle{n}\to\lrangle{m}$ that maps the elements on which $f$ is not defined to $\ast\in\lrangle{m}$.} For every $i\in\{1,\dots,n\}$ there is a map $\rho^i\colon\langle n\rangle\to\langle 1\rangle$ that sends $i$ to $1$ but is otherwise constant at $\ast\in\langle1\rangle$.
 A \emph{symmetric monoidal $\infty$-category} is, after \cite[Definition 2.0.0.7]{lurie_ha}, a cocartesian fibration\footnote{A \emph{cocartesian fibration} (\cite[Definition 01T5]{lurie_kerodon}) $q\colon\mathscr{A}\to\mathscr{B}$ between simplicial sets is one such that every edge $f\in\mathscr{A}_1$ is \emph{($q$-)cocartesian}, that is, any horn of type $\Lambda^n_0\to\mathscr{A}$, $n\geq2$, whose restriction to $\{0<1\}$ is $f$, admits a filler if its projection to $\mathscr{B}$ admits a filler.
-By (un)straightening, such a $q$ corresponds to a $\cat$-valued copresheaf $\mathscr{B}\to\cat$.} $\catC\to\mathsf{Fin}_\ast$ such that the maps $\rho^i\colon\langle n\rangle\to\langle 1\rangle$, $1\leq i\leq n$, induce an equivalence $\catC_{\langle n\rangle}\simeq(\catC_{\langle 1\rangle})^{\times n}$ for every $n\geq0$, where $\catC_{x}$ is the fiber at $x$.
+By (un)straightening, such a $q$ corresponds to a $\cat$-valued copresheaf $\mathscr{B}\to\cat$.} $p\colon\catC\to\mathsf{Fin}_\ast$ such that the maps $\rho^i\colon\langle n\rangle\to\langle 1\rangle$, $1\leq i\leq n$, induce an equivalence
+\begin{equation}\label{W1183QD}
+\catC_{\langle n\rangle}\simeq(\catC_{\langle 1\rangle})^{\times n}
+\end{equation} 
+of $\infty$-categories for every $n\geq0$, where $\catC_{x}$ is the fiber at $x$.
 We have abbreviated $\mathsf{N}(\mathsf{Fin}_\ast)$ to $\mathsf{Fin}_\ast$, and will mostly abbreviate $\catC\to\mathsf{Fin}_\ast$ to $\catC$.
+One thinks of $\catC_{\langle n\rangle}$ as the collection of $n$-tuples of elements from the \emph{underlying $\infty$-category} $\catC_{\lrangle{1}}$, and $\rho^i$ as the $i$'th coordinate projection.
 
@@
 when $\mathscr{O}$, $\mathscr{C}$ are symmetric monoidal $\infty$-categories.
+This does \emph{not} coincide with the notation in \cite{lurie_ha}; nevertheless, see \Cref{NBR8AQB}.
+Informally, the objects will be symmetric monoidal functors from $\disk(\bstr)$ to $\catC$.
+These are given by functors $F:\disk(\bstr) \xrightarrow{} \catC$ together with maps
+%
+\begin{equation}\label{eq:symmon_maps}
+    F(U \sqcup V) \xrightarrow{\ \ \simeq \ \ } F(U) \otimes F(V),
+\end{equation}
+%
+and such that the swap in $\disk(\bstr)$, $U \sqcup V \simeq V \sqcup U$, is sent to the swap in $\catC$, $F(U) \otimes F(V) \simeq F(V) \otimes F(U)$, in a way that is compatible with the maps in \eqref{eq:symmon_maps}.
+A good informal explanation of this and other topics related to disk algebras can be found in the lecture notes \cite{tanaka20}.
 
-More generally, an \emph{$\infty$-operad} is a map $\catC\to\mathsf{Fin}_\ast$ that satisfies a generalisation of the properties of a symmetric monoidal $\infty$-category -- see \cite[Definition 2.1.1.10]{lurie_ha}.
+More generally, an \emph{$\infty$-operad} is a map $\catC\to\mathsf{Fin}_\ast$ that satisfies a generalisation of the properties of a symmetric monoidal $\infty$-category: see \cite[Definition 2.1.1.10]{lurie_ha}.
+For these, \eqref{W1183QD} still holds: see \cite[Remark 2.1.1.14]{lurie_ha}.
 
@@
 
-\begin{remark}
-    The exact specification of the above $\infty$-category is not immediate, but the explanations given in \cite[def.2.0.0.7]{lurie_ha}, \cite[rem.2.1.2.19]{lurie_ha} and \cite[def.2.1.3.7]{lurie_ha} clarify the matter.
+% \begin{remark}
+%     The exact specification of the above $\infty$-category is not immediate, but the explanations given in \cite[def.2.0.0.7]{lurie_ha}, \cite[rem.2.1.2.19]{lurie_ha} and \cite[def.2.1.3.7]{lurie_ha} clarify the matter.
 A succinct explanation is also given around \cite[def.1.11]{aft_fhstrat}.
-Informally, the objects will be symmetric monoidal functors from $\disk(\bstr)$ to $\catC$.
-These are given by functors $F:\disk(\bstr) \xrightarrow{} \catC$ together with maps
+% \end{remark}
+
+These algebras will be the algebraic input of factorization homology.
+To convince ourselves that this is not a huge limitation on the types of algebras that can be evaluated, we have, keeping in mind \Cref{16GY5V1}, the following:
 %
-    \begin{equation}\label{eq:symmon_maps}
-        F(U \sqcup V) \xrightarrow{\ \ \simeq \ \ } F(U) \otimes F(V),
-    \end{equation}
-    %
-    and such that the swap in $\disk(\bstr)$, $U \sqcup V \simeq V \sqcup U$, is sent to the swap in $\catC$, $F(U) \otimes F(V) \simeq F(V) \otimes F(U)$, in a way that is compatible with the maps in \eqref{eq:symmon_maps}.
-A good informal explanation of this and other topics related to disk algebras can be found in the lecture notes \cite{tanaka20}.
-\end{remark}
-
-These algebras will be the algebraic input of factorization homology. To convince ourselves that this is not a huge limitation on the types of algebras that can be evaluated we have:
-%
-\begin{proposition}[{\cite[prop.2.12]{aft_fhstrat}}]\label{prop:framed_ndisk=En}
+\begin{proposition}[{\cite[Proposition 2.12]{aft_fhstrat}}]\label{prop:framed_ndisk=En}
     Let $(\bstr \xrightarrow{} \bsc) = (* \xrightarrow{\{ \mathbb{R}^n\}} \bsc)$, namely the $\infty$-category of basics describing framed smooth $n$-manifolds.
@@
 \begin{remark}
-    For more details on $\mathbb{E}_n$-algebras and why these algebras encompass large portions of the examples one usually cares about see \cite[sec.5.1]{lurie_ha}.
+    For more details on $\mathbb{E}_n$-algebras and why these algebras encompass large portions of the examples one usually cares about see \cite[§5.1]{lurie_ha}.
 %or alternatively in appendix \Cref{app:En_algebras}.
-    Roughly speaking, $\mathbb{E}_1$-algebras are homotopy associative algebras and with increasing $n$ we get increasing levels of homotopy commutativity.
+    Roughly speaking, $\mathbb{E}_1$-algebras are homotopy-associative algebras and with increasing $n$ we get increasing levels of homotopy commutativity, such that the colimit $\mathbb{E}_\infty$ parametrises homotopy-commtuative algebras.
 Having said that, the first part of the proposition is just the classical statement that the little $n$-disks operad and the little $n$-cubes operad are equivalent.
-Through the work of \cite{lurie_tqft} and \cite{scheimbauer2014}, $\mathbb{E}_n$-algebras also serve as input for constructing fully extended TQFTs by using factorization homology.
+Through \cite{lurie_tqft} and \cite{scheimbauer2014}, $\mathbb{E}_n$-algebras also serve as input for constructing fully extended TQFTs by using factorization homology.
 \end{remark}
@@
 
-\begin{remark}
-    $\disk(\bstr)$ is a symmetric monoidal $\infty$-category, however there is no way to inherit this structure to $\disk(\bstr)_{/M}$.
-Intuitively, this is because disjoint union cannot serve as a monoidal structure now that the disks are equipped with an embedding into a given manifold $M$; they could be such that they intersect.
-However, as explained in \cite[not.1.21]{aft_fhstrat}, we \emph{can} equip $\disk(\bstr)_{/M}$ with the structure of an $\infty$-operad because the symmetric monoidal unit $\emptyset$ of $\disk(\bstr)$ and $\mfld(\bstr)$ is initial.
-This is also the case for $\mfld(\bstr)_{/M}$ itself.
+    While $\disk(\bstr)$ is a symmetric monoidal $\infty$-category, $\disk(\bstr)_{/M}$ need not be, since two embeddings, if their images intersect, do not lift to an embedding from the disjoint union of their domains.
+However, \cite[Notation 1.21]{aft_fhstrat} equips $\disk(\bstr)_{/M}$ with the structure of an $\infty$-operad.
+We briefly explain the idea behind the construction.
+It applies in the same way to $\mfld(\bstr)_{/M}$.
 
-    In more details, following \cite[ex.2.5]{aft_fhstrat}, objects of $\disk(\bstr)_{/M}$ are finite sets of open embeddings of disks $(U \xhookrightarrow{} M)$.
-A morphism between two open embeddings $(U \xhookrightarrow{} M) \xrightarrow{} (V \xhookrightarrow{} M)$ is specified by an open embedding $U \xhookrightarrow{} V$ together with an isotopy between $U \xhookrightarrow{} M$ and $U \xhookrightarrow{} V \xhookrightarrow{} M$.
-A morphism $((U_1 \xhookrightarrow{} M), (U_2 \xhookrightarrow{} M)) \xrightarrow{} (V \xhookrightarrow{} M)$ is given by an open embedding $U_1 \sqcup U_2 \xhookrightarrow{} V$ together with two isotopies from $U_1 \xhookrightarrow{} M$ to $U_1 \xhookrightarrow{} U_1 \sqcup U_2 \xhookrightarrow{} M$, and from $U_2 \xhookrightarrow{} M$ to $U_2 \xhookrightarrow{} U_1 \sqcup U_2 \xhookrightarrow{} M$.
-\end{remark}
+    Let $\iota_{1/2}\colon D_{1/2}\hookrightarrow M$ be two embeddings. A morphism over $\lrangle{2}\to\lrangle{1}$ from $(\iota_{1},\iota_2)$ to $\iota\colon D\to M$ will consist of
+    \begin{enumerate}
+        \item two $1$-simplices
+        \[
+        \begin{tikzcd}
+            D_{1}\ar[dr,hook]\ar[rr,hook] && D\ar[dl,hook']\\
+            & M
+        \end{tikzcd},\quad
+        \begin{tikzcd}
+            D_{2}\ar[dr,hook]\ar[rr,hook] && D\ar[dl,hook']\\
+            & M
+        \end{tikzcd}
+        \]
+        in the slice $\disk(\bstr)_{/M}$;
+        \item an embedding $ D_1\amalg D_2\hookrightarrow D$;
+        \item and two isotopies -- to be explained below -- between the resulting embeddings $D_{1/2}\hookrightarrow D_{1}\amalg D_2 \hookrightarrow D$ and the previously given embeddings $D_{1/2}\hookrightarrow D$.
+    \end{enumerate}
+
+    The first piece is in $\prod_{\nu=1,2}\mathsf{Hom}_{\disk(\bstr)_{/M}}(\iota_\nu,\iota)$, and projecting from the slice gives maps $\prod_{\nu=1,2}\mathsf{Hom}_{\disk(\bstr)_{/M}}(\iota_\nu,\iota)\to \prod_{\nu=1,2}\mathsf{Hom}_{\disk(\bstr)}(D_\nu,D)$, producing the maps $D_\nu\hookrightarrow D$ mentioned in piece 3.
+Piece 2 is in $\disk(\bstr)$.
+The monoidal unit $\emptyset\in\disk(\bstr)$ is initial, so we obtain the map $\mathsf{Mul}_{\disk(\bstr)}(D_1, D_2; D)\to\prod_{\nu=1,2}\mathsf{Hom}_{\disk(\bstr)}(D_\nu,D)$ as indicated above.
+See \cite[Notation 2.1.1.16]{lurie_ha} for $\mathsf{Mul}$.
+
+    Now, \cite[§2.4.3]{lurie_ha} contains a construction which associates an $\infty$-operad $\mathscr{C}^{\amalg}$ to any $\infty$-category $\mathscr{C}$ such that $\mathsf{Mul}_{\mathscr{C}^{\amalg}}(x_1\oplus\cdots\oplus x_n; y)\simeq \prod_{\nu=1}^{n}\mathsf{Hom}_{\mathscr{C}}(x_\nu,y)$.
+If $\mathscr{C}$ is already an $\infty$-operad with a initial unit $0\in\mathscr{C}_{\lrangle{1}}$, then there is (\cite[Lemma 1.20]{aft_fhstrat}) a canonical map of $\infty$-operads $\mathscr{C}\to(\mathscr{C}_{\lrangle{1}})^\amalg$ generalising the idea above.
+
+    We see that piece 1 is in $(\disk(\bstr)_{/M})^{\amalg}$, piece 2 is in $\disk(\bstr)$, and piece (3) describes equivalences in $\disk(\bstr)^{\amalg}$.
+The full collection is thus in the homotopy pullback $\infty$-operad
+    \[
+        \begin{tikzcd}
+        \disk(\bstr)_{/M}\ar[r]\ar[d]\arrow[dr, phantom, "\ulcorner", very near start] & (\disk(\bstr)_{/M})^{\amalg}\ar[d]\\
+        \disk(\bstr)\ar[r] & \disk(\bstr)^{\amalg}
+        \end{tikzcd}.
+    \]
+    A representative is then the following ordinary iterated fibre product of $\infty$-operads:
+    \[
+        \disk(\bstr)_{/M}\coloneqq \disk(\bstr)\times_{(\disk(\bstr)^{\amalg})^{\{0\}}}\mathsf{Isom}(\disk(\bstr)^{\amalg})\times_{(\disk(\bstr)^{\amalg})^{\{1\}}}(\disk(\bstr)_{/M})^{\amalg},
+    \]
+    where $\mathsf{Isom}(\disk(\bstr)^{\amalg})\subset\mathsf{Ar}(\disk(\bstr)^{\amalg})=(\disk(\bstr)^{\amalg})^{\Delta[1]}$ is the full sub-$\infty$-category of the arrow $\infty$-category generated by those morphisms that are isomorphisms in the associated homotopy category, whence the isotopies mentioned in piece 3.
 
 \begin{remark}
-    The constructions of the slice category also holds, word for word, in the case of $\disk[r](\bstr)_{/M}$ and $\mfld[r](\bstr)_{/M}$.
-The fact that they are $\infty$-operads is also true.
-The key difference is what the objects and morphisms are, say, in $\disk[r](\bstr)_{/M}$ as compared to $\disk(\bstr)_{/M}$.
-The objects are the same as before, i.e.
-finite sets of open embeddings into $M$.
-However, the morphisms now contain less information.
-A morphism $(U \xhookrightarrow{} M) \xrightarrow{} (V \xhookrightarrow{} M)$ is specified only by open embedding $U \xhookrightarrow{} V$, such that $(U \xhookrightarrow{} M) = (U \xhookrightarrow{} V \xhookrightarrow{} M)$, and no further information.
-This also holds for higher arity morphisms too.
-
+    Analogous statements hold for $\disk[r](\bstr)_{/M}$ and $\mfld[r](\bstr)_{/M}$ and the resulting $\infty$-operads.
+The difference is what the objects and morphisms are, say, in $\disk[r](\bstr)_{/M}$ as compared to $\disk(\bstr)_{/M}$.
+The objects are the same as before, i.e., finite sets of open embeddings into $M$.
+However, a morphism $(U \xhookrightarrow{} M) \xrightarrow{} (V \xhookrightarrow{} M)$ is specified only by open embedding $U \xhookrightarrow{} V$ such that $(U \xhookrightarrow{} M) = (U \xhookrightarrow{} V \xhookrightarrow{} M)$, and no further information.
 That is, a morphism in $\disk(\bstr)_{/M}$ is a diagram in $\disk (\bstr)$
@@
     %
-    which is homotopy commutative, while in $\disk[r](\bstr)_{/M}$ a morphism is a diagram as above that commutes on the nose\footnote{Regarding notation, \cite{lurie_ha} introduces both the $\infty$-operad $\disk(\bstr)_{/M}$ and $\disk[r](\bstr)_{/M}$, however there they are denoted by $\mathbb{E}_M^\otimes$ and $\mathrm{N}(\mathrm{Disk}(M))^\otimes$, respectively.}.
+    which is homotopy commutative as explained above, while in $\disk[r](\bstr)_{/M}$ a morphism is a diagram as above that commutes on the nose.\footnote{Regarding notation, \cite{lurie_ha} introduces both the $\infty$-operad $\disk(\bstr)_{/M}$ and $\disk[r](\bstr)_{/M}$, however there they are denoted by $\mathbb{E}_M^\otimes$ and $\mathrm{N}(\mathrm{Disk}(M))^\otimes$, respectively.}
+    Similarly for higher arity-morphisms.
 \end{remark}
@@
 \begin{definition}
-    We will refer to the $\infty$-category of algebras over the $\infty$-operads $\disk(\bstr)_{/M}$, $\disk[r](\bstr)_{/M}$, $\mfld(\bstr)_{/M}$ and $\mfld[r](\bstr)_{/M}$ in the usual way as
+    We will denote the $\infty$-category of algebras over the $\infty$-operads $\disk(\bstr)_{/M}$, $\disk[r](\bstr)_{/M}$, $\mfld(\bstr)_{/M}$ and $\mfld[r](\bstr)_{/M}$ by
     %
@@
     \end{align}
+    Following AFT, a map $\disk(\bstr)_{/M}\to \catC$, for instance, is in $\alg{\disk(\bstr)_/M}(\catC)$ iff, by definition, it is a map of $\infty$-operads in the sense of \cite[Definition 2.1.2.7]{lurie_ha} which maps pre-cocartesian edges to cocartesian edges.
+A \emph{pre-cocartesian} edge in $\disk(\bstr)_{/M}$ is an edge whose projection to $\disk(\bstr)$ is cocartesian over $\mathsf{Fin}_\ast$.
 \end{definition}
@@
 
-\begin{proposition}[{\cite[prop.2.2.4.9]{lurie_ha}}]
+\begin{proposition}[{\cite[prop.2.2.4.9]{lurie_ha}}]\label{NBR8AQB}
     Let $\mathscr{O}$ be an $\infty$-operad and let $\catC$ be a symmetric monoidal $\infty$-category. Then there is an equivalence
@@
     %
-    between the $\infty$-categories of $\mathscr{O}$-algebras in $\catC$ and symmetric monoidal functors from the symmetric monoidal envelope\footnote{A full definition of the symmetric monoidal envelope of an $\infty$-operad can be found in \cite[sec.2.2.4]{lurie_ha}.
+    between the $\infty$-categories of $\mathscr{O}$-algebras in $\catC$ and symmetric monoidal functors from the symmetric monoidal envelope\footnote{A full definition of the symmetric monoidal envelope of an $\infty$-operad can be found in \cite[§2.2.4]{lurie_ha}.
 For our purposes the two important facts about $\mathsf{Env}$ are that it is a left adjoint to the forgetful functor $U: \cat^\otimes \xrightarrow{} \mathscr{O}\mathsf{p}_{\infty}$, and that the underlying $\infty$-category of $\mathsf{Env} (\mathscr{O})$ is the $\infty$-subcategory of $\mathscr{O}$ spanned by the active morphisms.
-Informally, the symmetric monoidal structure of $\mathsf{Env}(\mathscr{O})$ is given by concatenating these active morphisms \cite[rem.2.2.4.6]{lurie_ha}.} of $\mathscr{O}$ to $\catC$.
+Informally, the symmetric monoidal structure of $\mathsf{Env}(\mathscr{O})$ is given by concatenating these active morphisms: see \cite[Remark 2.2.4.6]{lurie_ha}.} of $\mathscr{O}$ to $\catC$.
 \end{proposition}
@@
 
-Essentially the same argument as above, namely that over $\infty$-groupoids are contractible, also has another important consequence that we will need to make use of later:
+Essentially the same argument as above, namely that over-$\infty$-groupoids are contractible, also has another important consequence that we will need to make use of later:
 
@@
 The next result is of key importance to the technical side of the theory, and will be used extensively throughout.
-It alone, is essentially the reason for the appearance of weakly constructible bundles in a lot of later developments.
+It alone is essentially the reason for the appearance of weakly constructible bundles in a lot of later developments.
 
-\begin{lemma}[{\cite[lem.2.24]{aft_fhstrat}}]\label{lem:f^-1}
+\begin{lemma}[{\cite[Lemma 2.24]{aft_fhstrat}}]\label{lem:f^-1}
     Let $f: M \xrightarrow{} N$ be a weakly constructible bundle. There is a functor of $\infty$-operads
@@
 \begin{construction}\label{con:assocRL}
-    Let $\mathsf{Assoc^{RL}}$ denote the multicategory\footnote{A \emph{multicategory} is like an (ordinary) category except that morphisms (now called multi-morphisms) are allowed to have multiple objects in their domain while still having only a single object in their codomain.} with three objects $R$, $A$ and $L$.
+    Let $\mathsf{Assoc^{RL}}$ denote the multicategory\footnote{A \emph{multicategory}, or \emph{(colored) operad}, is like an (ordinary) category except that morphisms (now called multi-morphisms) are allowed to have multiple objects in their domain while still having only a single object in their codomain.
+The operadic nerve of a topological or Kan-enriched multicategy is an $\infty$-operad: see \cite[Proposition 2.1.1.27]{lurie_ha}.} with three objects $R$, $A$ and $L$.
 To describe the multi-morphisms let $I$ be an arbitrary finite list of the objects of $\mathsf{Assoc^{RL}}$.

### 2024-04-24 sections/4gluing_alt.tex
..

@@
 \begin{proof}[Proof of \Cref{thm:gluing_lcfas}]
-    In the case that all $\infty$-categoies involved are locally constant we will extend the previous proof to provide the equivalence.
+    In the case that all $\infty$-categories involved are locally constant we will extend the previous proof to provide the equivalence.
 Since we know that restriction does not destroy local constancy, extending the result to the case of locally constant factorization algebras simply requires us to show that the gluing $\gamma$ also preserves this property.
@@
 
-%\begin{conjecture}
-%    The theory of factorization algebras is fully determined, using factorization homology, by the data of a functor
-%    %
-%    \begin{equation}
-%        \mathsf{Bsc} \xrightarrow{\ \ \ \ } \cat^{\mathsf{op}}.
-%    \end{equation}
-%    %
-%    In the locally constant case, we can even say that to each basic $U$ this functor attaches the $\infty$-category $\mathsf{Fun}^{\otimes} (\disk(\mathsf{B}_U), \catC)$ of disk algebras with $\mathsf{B}_U$ structure, where $\mathsf{B}_U$ is the sieve poset whose maximal element is $U$.
-%\end{conjecture}
-%
-%\begin{remark}
-%    The $\infty$-category of basics $\mathsf{B}_{U}$ for our purposes provides a kind of generalization of framing, which makes calculation easier.
-%\end{remark}
-
 \subsection{Some Examples of Gluing}

### 2024-05-08 sections/2homology.tex
Removing mistake.

@@
 %or alternatively in appendix \Cref{app:En_algebras}.
-    Roughly speaking, $\mathbb{E}_1$-algebras are homotopy-associative algebras and with increasing $n$ we get increasing levels of homotopy commutativity, such that the colimit $\mathbb{E}_\infty$ parametrises homotopy-commtuative algebras.
-Having said that, the first part of the proposition is just the classical statement that the little $n$-disks operad and the little $n$-cubes operad are equivalent.
+    Roughly speaking, $\mathbb{E}_1$-algebras are homotopy-associative algebras and with increasing $n$ we get increasing levels of homotopy commutativity, such that the colimit $\mathbb{E}_\infty$ parametrizes homotopy-commtuative algebras.
+Having said that, the first part of the proposition is just the classical statement that the little $n$-disks operad and the little $n$-cubes operad are weakly equivalent.
 Through \cite{lurie_tqft} and \cite{scheimbauer2014}, $\mathbb{E}_n$-algebras also serve as input for constructing fully extended TQFTs by using factorization homology.
@@
 
-\subsection{\texorpdfstring{$\otimes$}{tensor}-excision and Homology Theories}
+\subsection{\texorpdfstring{$\otimes$}{tensor}-excision and Homology Theories}\label{sec:excision_homology}
 

### 2024-05-08 sections/2homology.tex
.

--- 2024-04-23 sections/2homology.tex
@@
     between the $\infty$-categories of $\mathscr{O}$-algebras in $\catC$ and symmetric monoidal functors from the symmetric monoidal envelope\footnote{A full definition of the symmetric monoidal envelope of an $\infty$-operad can be found in \cite[§2.2.4]{lurie_ha}.
-For our purposes the two important facts about $\mathsf{Env}$ are that it is a left adjoint to the forgetful functor $U: \cat^\otimes \xrightarrow{} \mathscr{O}\mathsf{p}_{\infty}$, and that the underlying $\infty$-category of $\mathsf{Env} (\mathscr{O})$ is the $\infty$-subcategory of $\mathscr{O}$ spanned by the active morphisms.
-Informally, the symmetric monoidal structure of $\mathsf{Env}(\mathscr{O})$ is given by concatenating these active morphisms: see \cite[Remark 2.2.4.6]{lurie_ha}.} of $\mathscr{O}$ to $\catC$.
+For our purposes the two important facts about $\mathsf{Env}$ are that it is a left adjoint to the forgetful functor $U: \cat^\otimes \xrightarrow{} \mathscr{O}\mathsf{p}_{\infty}$, and that the underlying $\infty$-category of $\mathsf{Env} (\mathscr{O})$ is the $\infty$-subcategory of $\mathscr{O}$ spanned by the \emph{active morphisms}, i.e., those which cover maps in $\mathsf{Fin}_\ast$ that send only the basepoint to the basepoint.
+Informally, the symmetric monoidal structure of $\mathsf{Env}(\mathscr{O})$ is given by concatenating these active morphisms: see \cite[Remark 2.2.4.3/6]{lurie_ha}.} of $\mathscr{O}$ to $\catC$.
 \end{proposition}

### 2024-05-08 sections/4gluing_alt.tex

@@
 In the case of the former, as originally noted in the proof of \cite[cor.2.40]{aft_fhstrat}, the result follows from using \cite[cor.1.6.]{dugger2004hypercovers}, an argument about configuration spaces, as well as \cite[lem.2.21]{aft_fhstrat}, which explains the relation of these to the above operad.
-In the case of the latter, the situation is even simpler because of its discrete nature.
+%In the case of the latter, the situation is even simpler because of its discrete nature.
 One way to show this is to notice that the functor from the ordinary, nonhomtopy colimit factors through $\mathsf{colim}_{i \geq 0} \disk[r]_{/M_i} \xrightarrow{} \disk[r]_{/M}$, in which case it suffices to find an equivalence of \emph{ordinary} categories
     %
-    \begin{equation}
-        \mathsf{colim}_{i \geq 0} \disk[r]_{/M_i} \xrightarrow{} \disk[r]_{/M},
-    \end{equation}
+    %\begin{equation}
+    %    \mathsf{colim}_{i \geq 0} \disk[r]_{/M_i} \xrightarrow{} \disk[r]_{/M},
+    %\end{equation}
     %
-    where the colimit is now the one relevant to ordinary category theory, namely the nonhomotopy one.
+    %where the colimit is now the one relevant to ordinary category theory, namely the nonhomotopy one.
 But it's now easy to see that this the canonical morphism above is an equivalence since for every $U \in \disk_{/M}$ there will be a finite integer $i$, such that $U \subset M_i$.

### 2024-05-23 sections/3algebras.tex
Typo in previous commit.
added todos in Prop 3.16

@@
     \begin{equation}
-        \int : \alg{\disk_M} (\catC) \xrightarrow{\ \ \ \ } \lcfa_M (\catC).
+        \int : \alg{\disk_{/M}} (\catC) \xrightarrow{\ \ \ \ } \lcfa_M (\catC).
     \end{equation}
@@
     is final.
+
+    {\color{red} \bf TODOs:} \cite[prop.2.22]{af_primer} is smooth, we need stratified.
+    \begin{itemize} 
+        \item It rests on \cite[Lemma 2.30]{af_primer} which is about what happens when you do a base change from $\mathsf{RFib}_{\disk_n}$ to $\mathsf{RFib}_{\disk_n^{\simeq}}$ where $-^\simeq$ takes the core.
+The same base change in the stratified setting will be allowed because we will still be working with right fibrations.
+Probably in the stratified core $\disk^\simeq$ basic disks with different stratifications disconnect into separate connected components.\footnote{Not "probably", but surely.} This should lead to a similar argument.
+        \item Then the following remark: a covering sieve $\mathscr{U}$ on $M$ being Weiss is exactly saying that the smallest sieve on $M$ containing $\{\mathrm{Conf}_i(U)_{\Sigma_i}\hookrightarrow\mathrm{Conf}_i(M)_{\Sigma_i}\}_{U\in\mathscr{U}}$ is a covering sieve on $\mathrm{Conf}_i(M)_{\Sigma_i}$.\footnote{Here $i$ is the number disks, fixed but arbitrary; $(-)_{\Sigma_i}$ makes the configurations unordered.} Then the fact that $\mathrm{Conf}_i(M)_{\Sigma_i}$ is Hausdorff and paracompact gives the desired equivalence.
+Something similar might hold in the stratified case but this is not obvious.
+Hopefully AFT already wrote it down somewhere.
+I vaguely remember a statement that conically-smooth stratified spaces have partitions of unity, possibly in their "Factorization homology I" paper.
+If so, it's either there or I'd guess in the local structures paper.
+        \item In the first place, the replacement of $\mathsf{Cat}_\infty$ by $\mathsf{RFib}_{\disk_n}$ in the calculation needs to be check to be benign.
+This is probably something obvious and has (I'd say) least priority.
+    \end{itemize}
 \end{proof}
@@
     %
-    But this is just the fact that the $\disk_{/M}$ $\infty$-operad gives rise to $E_n$-algebras from \cref{prop:framed_ndisk=En}.
+    But this is just the fact that the $\disk_{/M}$ $\infty$-operad gives rise to $\mathbb{E}_n$-algebras from \cref{prop:framed_ndisk=En}.
 \end{proof}

### 2024-06-03 sections/1stratified.tex
Todo is partially done.

@@
 \begin{equation}
-    \tau: \mfld_n \xrightarrow{\mathrm{Yoneda}} \mathsf{PShv}(\mfld_n) \xrightarrow{-|_{\{\mathbb{R}^n\} \subset \mfld_n}} \mathsf{PShv}(\mathbb{R}^n) \simeq \mathsf{Spaces}_{/\mathsf{BO}(n)},
+    \tau: \mfld_n \xrightarrow{\mathrm{Yoneda}} \mathsf{PShv}(\mfld_n) \xrightarrow{-|_{\{\mathbb{R}^n\} \subset \mfld_n}} \mathsf{PShv}(\mathbb{R}^n) \simeq \mathsf{Sp}_{/\mathsf{BO}(n)},
 \end{equation}
@@
     As noted in \cite{af_fhtop}, the Kister--Mazur Theorem (\cite{kister1964microbundles}) provides an equivalence $\mathsf{Emb}(\mathbb{R}^n,\mathbb{R}^n)\simeq \mathsf{Top}(n)$, where $\mathsf{Top}(n)$ is the group of topological automorphisms of $\mathbb{R}^n$; $\mathsf{Emb}(\mathbb{R}^n,\mathbb{R}^n)\simeq\mfld_n(\mathbb{R}^n,\mathbb{R}^n)$ is the group of self-embeddings of $\mathbb{R}^n$; and both groups are equipped with the compact-open topology.
-This yields $\mathsf{PShv}(\mathbb{R}^n)\simeq\mathsf{PShv}(\mathsf{BTop}(n))$, which is equivalent to $\mathsf{Spaces}_{/\mathsf{BTop}(n)}$ by straightening--unstraightening (see \Cref{rem:grothendieck_construction}).\footnote{Presheaves are space-valued, that is, $\mathsf{PShv}(\mathscr{C})=\mathsf{Fun}(\mathscr{C}^{\mathsf{op}},\mathsf{Spaces})$.} Finally, the inclusion $\mathsf{O}(n)\hookrightarrow\mathsf{Emb}(\mathbb{R}^n,\mathbb{R}^n)$ is also an equivalence (\cite[Proposition 2.2.6]{af_primer}), yielding the displayed equivalence.
+This yields $\mathsf{PShv}(\mathbb{R}^n)\simeq\mathsf{PShv}(\mathsf{BTop}(n))$, which is equivalent to $\mathsf{Sp}_{/\mathsf{BTop}(n)}$ by straightening--unstraightening (see \Cref{rem:grothendieck_construction}).\footnote{Presheaves are space-valued, that is, $\mathsf{PShv}(\mathscr{C})=\mathsf{Fun}(\mathscr{C}^{\mathsf{op}},\mathsf{Sp})$.} Finally, the inclusion $\mathsf{O}(n)\hookrightarrow\mathsf{Emb}(\mathbb{R}^n,\mathbb{R}^n)$ is also an equivalence (\cite[Proposition 2.2.6]{af_primer}), yielding the displayed equivalence.
 The first map, the $\infty$-categorical Yoneda embedding, sends $M\mapsto((\mfld_{n})_{/M}\to\mfld_n)$ as a map with target $\mathsf{RFib}(\mfld_n)$, as in \cite{lurie_htt}.
@@
         \begin{tikzcd}
-            \mfld_n^B \arrow[dr, phantom, "\ulcorner", very near start] \arrow[r] \arrow[d] & \mathsf{Spaces}_{/B} \arrow[d] \\
-            \mfld_n \arrow[r, "\tau"] & \mathsf{Spaces}_{/\mathsf{BO}(n)},
+            \mfld_n^B \arrow[dr, phantom, "\ulcorner", very near start] \arrow[r] \arrow[d] & \mathsf{Sp}_{/B} \arrow[d] \\
+            \mfld_n \arrow[r, "\tau"] & \mathsf{Sp}_{/\mathsf{BO}(n)},
         \end{tikzcd}
@@
 \begin{remark}
-    Since the tangent classifier $\tau$ is symmetric monoidal, and since the right vertical map is canonically symmetric monoidal with respect to disjoint union on both $\mathsf{Spaces}_{/B}$ and $\mathsf{Spaces}_{/\mathsf{BO}(n)}$, the newly defined $\infty$-category does indeed come with a canonical symmetric monoidal structure.
+    Since the tangent classifier $\tau$ is symmetric monoidal, and since the right vertical map is canonically symmetric monoidal with respect to disjoint union on both $\mathsf{Sp}_{/B}$ and $\mathsf{Sp}_{/\mathsf{BO}(n)}$, the newly defined $\infty$-category does indeed come with a canonical symmetric monoidal structure.
 \end{remark}
@@
 \begin{remark}\label{rem:grothendieck_construction}
-    The straightening--unstraightening construction of \cite[§2.2]{lurie_htt} provides an equivalence between $\mathsf{Spaces}$-valued presheaves on an $\infty$-category $\catC$ and right fibrations\footnote{A \emph{right fibration} (over $\catC$) is a functor $f:\mathscr{E} \rightarrow \catC$ such that whenever a square of type
+    The straightening--unstraightening construction of \cite[§2.2]{lurie_htt} provides an equivalence between $\mathsf{Sp}$-valued presheaves on an $\infty$-category $\catC$ and right fibrations\footnote{A \emph{right fibration} (over $\catC$) is a functor $f:\mathscr{E} \rightarrow \catC$ such that whenever a square of type
     %
@@
 In general, the map $\mathsf{B}G\to \mathsf{BO}(n)$ is not a right fibration unless $G\to\mathsf{O}(n)$ is an epimorphism.
-However, given the latter, we can consider the presheaf $\mathsf{D}_n^{\text{op}}\to\mathsf{Spaces}$ given by mapping $\mathbb{R}^n$ to the space of $G$-structures on it, and sending an embedding to the induced pullback map on the respective spaces of $G$-structures.
+However, given the latter, we can consider the presheaf $\mathsf{D}_n^{\text{op}}\to\mathsf{Sp}$ given by mapping $\mathbb{R}^n$ to the space of $G$-structures on it, and sending an embedding to the induced pullback map on the respective spaces of $G$-structures.
 By unstraightening, this determines a right fibration for which, by abuse, we write $\mathsf{D}^G_n=\mathsf{B}G\to \mathsf{D}_n\hookrightarrow\bsc$.

### 2024-06-03 sections/3algebras.tex
Todo is partially done.

--- 2024-04-12 sections/3algebras.tex
@@
 Now that we have introduced all the varieties of factorization algebras, it's a natural and useful question to ask what the $\infty$-operad governing them is.
-For prefactorization algebras, the answer comes by definition, but this is not the case for factorization algebras.
-In the case of stratified manifolds, we will show that the $\infty$-operad that governs locally constant factorization algebras can be taken to be $\disk_{/M}$, and the one that governs ordinary factorization algebras can be taken to be $\disk[r]_{/M}$.
-This result is immensely helpful in relating factorization algebras to results in the area of disk algebras.
-We will see one such example in \Cref{ch:gluing_disk_alg}.
-
+For prefactorization algebras, the answer comes by definition, but this is not the case for (locally constant) factorization algebras.
+We will be working in the generality of stratified manifolds, and all our results in this section will come in pairs, one for the locally constant case and one not.
+We call the results in the not-necessarily-locally-constant case corollaries since their proofs will be obvious from the proofs of the statements in the locally constant case.
+To connect factorization algebras to the theory of algebras over an $\infty$-operad we will work in two steps.
+First we have the following results:
+%
 \begin{proposition}\label{prop:fh_disk_to_lcfa}
@@
     \begin{equation}
-        \int : \alg{\disk_M} (\catC) \xrightarrow{\ \ \ \ } \lcfa_M (\catC).
+        \int : \alg{\disk_{/M}} (\catC) \xrightarrow{\ \ \ \ } \lcfa_M (\catC).
     \end{equation}
 \end{proposition}
+%
+\begin{corollary}\label{cor:fh_disk_to_falg}
+    Given a stratified manifold $M$ factorization homology provides a functor
+    %
+    \begin{equation}
+        \int: \alg{\disk[r]_{/M}} (\catC) \xrightarrow{\ \ \ \ } \falg_{M} (\catC).
+    \end{equation}
+\end{corollary}
+
+The second step is then showing that the functors constructed above are equivalences, which we summarize in the following results:
+%
+\begin{theorem}\label{thm:disk_alg=lcfa}
+    For each stratified manifold $M$, the previously constructed factorization homology functor provides an equivalence of $\infty$-categories between $\disk_{/M}$-algebras and locally constant factorization algebras on $M$.
+Equivalently, the $\infty$-operad governing locally constant factorization algebras can be taken to be $\disk_{/M}$
+    %
+    \begin{equation}
+        \alg{\disk_{/M}} (\catC) \xrightarrow[\int]{\ \ \simeq \ \ } \lcfa_M (\catC).
+    \end{equation}
+\end{theorem}
+%
+\begin{corollary}\label{cor:disk_alg=falg}
+    The $\infty$-operad governing factorization algebras on a stratified manifold $M$ can be taken to be $\disk[r]_{/M}$,
+    %
+    \begin{equation}
+        \alg{\disk[r]_{/M}} (\catC) \xrightarrow{\ \ \simeq \ \ } \falg_M (\catC).
+    \end{equation}
+\end{corollary}
+%
+The reason for the phrasing in these results is that, technically speaking, equivalence of the $\infty$-categories of algebras does not imply equivalence of the underlying operads.
+However since we only defined (locally constant) factorization algebras at the level of algebras and not on the level of $\infty$-operads, we can take the operadic definition as the basic one, and interpret the results as connecting this to the classical definition.
+The theorems that we present in this section are immensely helpful in relating factorization algebras to results in the area of disk algebras, which will be obvious throughout the rest of this work.
+One important example that we will see is in \Cref{ch:gluing_disk_alg}.
+
+In the service of working towards proofs of all of these results we first have to pause and develop some necessary technically results regarding Weiss covers.
+
+\begin{lemma}\label{lem:weiss_to_ordinary}
+    Let $M$ be a topological space with a sieve $\mathscr{U}$. The following are equivalent:
+    %
+    \begin{enumerate}
+        \item $\mathscr{U}$ is a Weiss sieve of $M$,
+        \item for all $n \geq 0$, the sieve $\{ \mathrm{Conf}_n(U)_{\Sigma_n} \xhookrightarrow{} \mathrm{Conf}_n(M)_{\Sigma_n} \mid U \in \mathscr{U} \}$ is a covering sieve of the unordered configuration space $\mathrm{Conf}_n(M)_{\Sigma_n}$ of $n$ points in $M$.
+    \end{enumerate}
+\end{lemma}
 
 \begin{proof}
+    In the forward direction, let $[(x_1, \dots, x_n)] \in \mathrm{Conf}_n(M)_{\Sigma_n}$ be an equivalence class of $n$ points under the action of the symmetric group.
+By definition of Weiss sieve, there is a $U \in \mathscr{U}$ such that $\{x_1, \dots, x_n\} \subset U$.
+Since none of the points are the same this means that $(x_1, \dots, x_n) \in U^{\times n}$, and subsequently that $(x_1, \dots, x_n) \in \mathrm{Conf}_n(U)$.
+Taking quotients we get that $[(x_1, \dots, x_n)] \in \mathrm{Conf}_n(U)_{\Sigma_n}$.
+Since $\mathrm{Conf}_n(U)_{\Sigma_n}$ is open in the topology of $\mathrm{Conf}_n(M)_{\Sigma_n}$, the collection of these form a covering sieve.
+
+    In the opposite direction, let $S \subset M$ be a finite set with cardinality $|S| = n$.
+Naming its elements $x_1, \dots, x_n$ in an arbitrary order that will not matter because of the $\Sigma_n$ quotient, we get the $[(x_1, \dots, x_n)] \in \mathrm{Conf}_n(M)_{\Sigma_n}$.
+By assumption there exists a $U \in \mathscr{U}$ such that $[(x_1, \dots, x_n)] \in \mathrm{Conf}_n(U)_{\Sigma_n}$.
+In particular, this means that $(x_1, \dots, x_n) \in U^{\times n}$, or in other words that $x_i \in U$ for all $1 \leq i \leq n$.
+This implies that $\mathscr{U}$ satisfies the Weiss property.
+\end{proof}
+
+\begin{lemma}\label{lem:gluing_disk/M}
+    A Weiss sieve $\mathscr{U} \subset \mfld[r]_{/M}$ canonically determines a morphism
+    %
+    \begin{equation}
+        \mathsf{colim} (\mathscr{U} \xrightarrow{} \mfld[r] \xrightarrow{\disk_{/-}} \mathsf{RFib}_{\disk(\bstr)}) \xrightarrow{\ \ \simeq \ \ } \disk_{/M}
+    \end{equation}
+    of right fibrations over $\disk(\bstr)$, which moreover, is an equivalence.
+\end{lemma}
+
+\begin{proof}
+    The morphism is determined by the universal property of the colimit with the component maps $\disk_{/U} \xrightarrow{} \disk_{/M}$ given from the open embeddings $U \xhookrightarrow{} M$.
+To show the equivalence, we follow the strategy laid out in part 2 of the proof of \cite[Prop.2.22]{af_primer}, while at the same time adapting it to the stratified setting.
+A morphism of right fibrations, as in the statement, is an equivalence if, and only if, it is so when looked at as a right fibration over the maximal $\infty$-groupoid of the base (cite ...).
+In our case this is\footnote{Specifically, the wreath product of groups in the notation is referring to $\mathsf{End}_{\bstr}(U) \wr_{\{1, 2, \dots, i\}} \Sigma_i$, the one whose underlying set is $\mathsf{End}_{\bstr}(U)^{\times \{1, 2, \dots, i\}} \times \Sigma_i$.}
+    %
+    \begin{equation}
+        \disk(\bstr)^{\simeq} \simeq \coprod_{i \geq 0} \prod_{[U]} \mathsf{B}(\mathsf{End}_{\bstr}(U) \wr \Sigma_i),
+    \end{equation}
+    %
+    as given by \cite[Lem.2.21]{aft_fhstrat}.
+The same lemma also tells us that the maximal $\infty$-groupoid of $\disk_{/M}$ is given by\footnote{The notation $M_{[U]}$ denotes the $[U]$-stratum of the stratified manifold $M$, which is a \emph{smooth} manifold, as defined in \cite[Def.4.4.5]{aft_localstrut}.}
+    %
+    \begin{equation}
+        \disk_{/M}^{\simeq} \simeq \coprod_{i \geq 0} \prod_{[U]} \mathrm{Conf}_{i}(M_{[U]})_{\Sigma_i}.
+    \end{equation}
+    %
+    In both cases, the product runs over isomorphism classes of basics.
+It is also clear that the map $\disk_{/M}^{\simeq} \xrightarrow{} \disk(\bstr)^{\simeq}$ resulting from the right fibration from the slice respects this decomposition in that there result maps of spaces
+    %
+    \begin{equation}
+        \mathrm{Conf}_i(M_{[U]})_{\Sigma_i} \xrightarrow{\ \ \ \ } \mathsf{B}(\mathsf{End}_{\bstr}(U) \wr \Sigma_i),
+    \end{equation}
+    %
+    for each $i \geq 0$, and each isomorphism class $[U]$ of basics in $\bstr$. Thus, working piece by piece, we need to show that
+    %
+    \begin{equation}
+        \mathsf{colim} (\mathscr{U} \xrightarrow{} \mfld[r](\bstr) \xrightarrow{\mathrm{Conf}_{i}(-_{[U]})_{\Sigma_i}} \mathsf{Sp}_{/\mathsf{B}(\mathsf{End}_{\bstr}(U) \wr \Sigma_i)}) \xrightarrow{\ \ \simeq \ \ } \mathrm{Conf}_{i}(M_{[U]})_{\Sigma_i},
+    \end{equation}
+    %
+    for all $i$ and $[U]$ as specified before, where we notice that the decomposition into maps of spaces means that our target is even $\mathsf{Sp}_{/\mathsf{B}(\mathsf{End}_{\bstr}(U) \wr \Sigma_i)}$ and not just right fibrations.
+We will first explain this equivalence at the level of spaces and only after will we argue why the equivalence respects the maps to $\mathsf{B}(\mathsf{End}_{\bstr}(U) \wr \Sigma_i)$.
+From a Weiss sieve $\mathscr{U}$ of $M$ we easily get a Weiss sieve $\mathscr{U}_{[U]}$ of $M_{[U]}$ by intersecting with $M_{[U]}$ as a submanifold of $M$.
+Using $\mathscr{U}_{[U]}$, we define $\mathscr{U}_{i, [U]}$ to be the sieve of $\mathrm{Conf}_i(M_{[U]})_{\Sigma_i}$ as in \Cref{lem:weiss_to_ordinary}.
+These considerations give us equivalences
+    %
+    \begin{align}\label{eq:ord_to_W_equivs}
+        \mathsf{colim} (\mathscr{U} \xrightarrow{} \mfld[r](\bstr) \xrightarrow{\mathrm{Conf}_{i}(-_{[U]})_{\Sigma_i}} \mathsf{Sp}) &\simeq \mathsf{colim} (\mathscr{U}_{[U]} \xrightarrow{} \mfld[r](\bstr) \xrightarrow{\mathrm{Conf}_{i}(-)_{\Sigma_i}} \mathsf{Sp})\notag\\
+        &\simeq \mathsf{colim} (\mathscr{U}_{i,[U]} \xrightarrow{} \mfld[r](\bstr) \xrightarrow{} \mathsf{Sp}).
+    \end{align}
+    %
+    The second equivalence in the above is simply a statement about the unions over the two covers and is a restatement of \Cref{lem:weiss_to_ordinary}.
+But, by \cite[Prop.A.3.2]{lurie_ha} there is an equivalence
+    %
+    \begin{equation}\label{eq:gluing_top_lurie}
+        \mathsf{colim} (\mathscr{U}_{i,[U]} \xrightarrow{} \mfld[r](\bstr) \xrightarrow{} \mathsf{Sp}) \xrightarrow{\ \ \simeq \ \ } \mathrm{Conf}_{i}(M_{[U]})_{\Sigma_i}.
+    \end{equation}
+    %
+    It is obvious that the equivalences in \Cref{eq:ord_to_W_equivs} lie over $\mathsf{B}(\mathsf{End}_{\bstr}(U) \wr \Sigma_i)$, since they're nothing more than a rewriting.
+The equivalence in \Cref{eq:gluing_top_lurie} also lies over $\mathsf{B}(\mathsf{End}_{\bstr}(U) \wr \Sigma_i)$ because all the various pieces that we're gluing in $\mathsf{Sp}$ come from unordered configuration space manifolds.............
+\end{proof}
+
+\begin{remark}
+    That the maps to $\mathsf{B}(\mathsf{End}_{\bstr}(U) \wr \Sigma_i)$ don't play much of a role can also be seen through the fact that this is the only place where the choice of tangential structure $\bstr$ enters the discussion in the form of including or excluding certain endomorphisms.
+\end{remark}
+
+\begin{proof}[Proof of {\Cref{prop:fh_disk_to_lcfa}}]
     We adopt a proof strategy similar to \cite[prop.3.14]{af_primer}.
@@
 By the definition of $\csheaves[W](\mfld_{/M}, \catC)$, this means that the restriction of $\int F$ to $\mathsf{Fun}(\mfld[r]_{/M}, \catC)$ satisfies the cosheaf property for every Weiss sieve $\mathscr{U} \subset (\mfld[r]_{/M})_{/e}$, where $e:N \xhookrightarrow{} M$ is an open embedding.
-Here we notice that for the Weiss property to even make sense, we are implicitly using \Cref{lem:double_slice}
+Here we notice that for the Weiss property to even make sense, we are implicitly using \Cref{lem:double_slice}, so that the Weiss sieve $\mathscr{U}$ is defined as a subcategory of $\mfld[r]_{/N}$.
 
-    Since $\catC$ has all relevant colimits the left Kan extension $\int F$ is given pointwise by
+    A similar calculation appears in part 2 of the proof of \cite[prop.2.22]{af_primer}, with the caveat that there things are presented for smooth manifolds.
+However, because of \Cref{lem:weiss_to_ordinary} and \Cref{lem:gluing_disk/M} we can adapt the proof to the stratified setting as well.
+Namely, we're trying to show that the canonical map
     %
-    \begin{equation}\label{eq:pointwiseKan}
-        \int_e F \simeq \mathsf{colim} ((\disk_{/M})_{/e} \xrightarrow{} \disk_{/M} \xrightarrow{F} \catC),
+    \begin{equation}\label{eq:fhfunc_canonical_map}
+        \mathsf{colim}(\mathscr{U} \xhookrightarrow{} \mfld[r]_{/N} \xrightarrow{} \mfld[r]_{/M} \xrightarrow{} \mfld_{/M} \xrightarrow{\int F} \catC) \xrightarrow{\ \ \ \ } \int_e F
     \end{equation}
     %
-    so what we need to show is that this colimit is equivalent to the colimit
+    is an equivalence for each sieve $\mathscr{U}$. Since $\catC$ has all relevant colimits the left Kan extension $\int F$ is given pointwise by
     %
-    \begin{equation}\label{eq:cosheaf_colim_relative}
-        \mathsf{colim} (\mathscr{U} \xrightarrow{} (\mfld[r]_{/M})_{/e} \xrightarrow{} \mfld[r]_{/M} \rightarrow \mfld_{/M} \xrightarrow{\int F} \catC),
+    \begin{equation}
+        \int_e F \simeq \mathsf{colim} (\disk_{/N} \xrightarrow{\simeq} (\disk_{/M})_{/e} \xrightarrow{} \disk_{/M} \xrightarrow{F} \catC),
     \end{equation}
     %
-    for each covering sieve $\mathscr{U}$. Since we aren't actually trying to get the value of these colimits we can rewrite \Cref{eq:pointwiseKan} into the idiosyncratic form
-    %
-    \begin{equation}\label{eq:idiosync_form}
-        \mathsf{colim} ((\disk_{/M})_{/e} \xrightarrow{} (\mfld_{/M})_{/e} \xrightarrow{} \mfld_{/M} \xrightarrow{\int F} \catC),
-    \end{equation}
-    %
-    which is easier to compare to \Cref{eq:cosheaf_colim_relative}.
-Using the fact that $\disk[r]_{/M} \xrightarrow{} \disk_{/M}$ is a final functor, which is a consequence of \cite[prop.2.22]{aft_fhstrat}, and the equivalences of \Cref{lem:double_slice} we can rewrite \Cref{eq:idiosync_form} further into
+    and this allows us to rewrite our canonical map from \Cref{eq:fhfunc_canonical_map} into
     %
     \begin{align}
-        \mathsf{colim} ((\disk[r]_{/M})_{/e} \xrightarrow{} (\disk_{/M})_{/e} \xrightarrow{} (\mfld_{/M})_{/e} \xrightarrow{} \mfld_{/M} \xrightarrow{\int F} \catC) \\ \simeq \mathsf{colim} ((\disk[r]_{/M})_{/e} \xrightarrow{} (\mfld[r]_{/M})_{/e} \xrightarrow{} \mfld[r]_{/M} \xrightarrow{} \mfld_{/M} \xrightarrow{\int F} \catC).
+        \mathsf{colim} \Big( \mathsf{colim} (\mathscr{U} \xrightarrow{} \mfld[r](\bstr) \xrightarrow{\disk_{/-}} \cat) \xrightarrow{} &\disk_{/N} \rightarrow \disk_{/M} \xrightarrow{F} \catC \Big)\notag\\
+        \xrightarrow{\ \ \ \ \ } \mathsf{colim} (&\disk_{/N} \xrightarrow{} \disk_{/M} \xrightarrow{F} \catC).
     \end{align}
     %
-    Denoting the functor $\mfld[r]_{/N} \simeq (\mfld[r]_{/M})_{/e} \xrightarrow{} \mfld[r]_{/M} \xrightarrow{} \mfld_{/M} \xrightarrow{\int F} \catC$ by $K_F$ and comparing with \Cref{eq:cosheaf_colim_relative} we need to show
-    %
-    \begin{equation}
-        \mathsf{colim} (\mathscr{U} \xrightarrow{} \mfld[r]_{/N} \xrightarrow{K_F} C) \simeq \mathsf{colim} (\disk[r]_{/N} \xrightarrow{} \mfld[r]_{/N} \xrightarrow{K_F} C),
-    \end{equation}
-    %
-    but this already follows from part 2 of the proof of \cite[prop.2.22]{af_primer}, and is equivalent to the statement that the functor
-    %
-    \begin{equation}
-        \mathsf{colim} (\mathscr{U} \xrightarrow{} \mfld[r]_{/N} \xrightarrow{} \mfld[r] \xrightarrow{\disk_{/-}} \cat) \xrightarrow{} \disk_{/N},
-    \end{equation}
-    %
-    is final.
+    However, the statement of \Cref{lem:gluing_disk/M} is exactly the statement that the above map is an equivalence.
 \end{proof}
@@
 
-From the proof of \Cref{prop:fh_disk_to_lcfa} it is easy to see that we can make a similar statement for ordinary factorization algebras too:
-
-\begin{corollary}\label{cor:fh_disk_to_falg}
-    Given a stratified manifold $M$ factorization homology provides a functor
-    %
-    \begin{equation}
-        \int: \alg{\disk[r]_{/M}} (\catC) \xrightarrow{\ \ \ \ } \falg_{M} (\catC).
-    \end{equation}
-\end{corollary}
-
-\begin{theorem}\label{thm:disk_alg=lcfa}
-    For each stratified manifold $M$, the previously constructed factorization homology functor provides an equivalence of $\infty$-categories between $\disk_{/M}$-algebras and locally constant factorization algebras on $M$.
-Equivalently, the $\infty$-operad governing locally constant factorization algebras can be taken to be $\disk_{/M}$
-    %
-    \begin{equation}
-        \alg{\disk_{/M}} (\catC) \xrightarrow{\ \ \simeq \ \ } \lcfa_M (\catC).
-    \end{equation}
-\end{theorem}
-
-\begin{proof}
+\begin{proof}[Proof of {\Cref{thm:disk_alg=lcfa}}]
     To show essential surjectivity of $\int$, for each $F \in \lcfa_M (\catC)$ we will find an equivalence $\int F| \simeq F$ in $\lcfa_M (\catC)$, with $F|$ to be defined later.
@@
 As before, the case of ordinary factorization algebras gets a similar statement whose proof goes along the same lines:
-
-\begin{corollary}\label{cor:disk_alg=falg}
-    The $\infty$-operad governing factorization algebras on a stratified manifold $M$ can be taken to be $\disk[r]_{/M}$,
-    %
-    \begin{equation}
-        \alg{\disk[r]_{/M}} (\catC) \xrightarrow{\ \ \simeq \ \ } \falg_M (\catC).
-    \end{equation}
-\end{corollary}
 

### 2024-06-05 sections/3algebras.tex
More progress on todo.

@@
     \begin{equation}
-        \alg{\disk[r]_{/M}} (\catC) \xrightarrow{\ \ \simeq \ \ } \falg_M (\catC).
+        \alg{\disk[r]_{/M}} (\catC) \xrightarrow[\int]{\ \ \simeq \ \ } \falg_M (\catC).
     \end{equation}
@@
     The morphism is determined by the universal property of the colimit with the component maps $\disk_{/U} \xrightarrow{} \disk_{/M}$ given from the open embeddings $U \xhookrightarrow{} M$.
-To show the equivalence, we follow the strategy laid out in part 2 of the proof of \cite[Prop.2.22]{af_primer}, while at the same time adapting it to the stratified setting.
-A morphism of right fibrations, as in the statement, is an equivalence if, and only if, it is so when looked at as a right fibration over the maximal $\infty$-groupoid of the base (cite ...).
-In our case this is\footnote{Specifically, the wreath product of groups in the notation is referring to $\mathsf{End}_{\bstr}(U) \wr_{\{1, 2, \dots, i\}} \Sigma_i$, the one whose underlying set is $\mathsf{End}_{\bstr}(U)^{\times \{1, 2, \dots, i\}} \times \Sigma_i$.}
+To show the equivalence, we follow a related strategy to the one laid out in part 2 of the proof of \cite[Prop.2.22]{af_primer}.
+By \cite[Def.2.2.3.2]{lurie_htt}, a morphism of right fibrations, as in the statement, is an equivalence if, and only if, it induces equivalences of spaces on the fibers over each object of the base.
+The objects of the base $\disk(\bstr)$ (e.g.
+acroding to \cite[Lem.2.21]{aft_fhstrat}) are lists $(i_{[U]} | [U] \in [\bstr])$ of integers, one for each isomorphism class of objects in $\bstr$.
+According to the same lemma, the fibers are given by the spaces
     %
     \begin{equation}
-        \disk(\bstr)^{\simeq} \simeq \coprod_{i \geq 0} \prod_{[U]} \mathsf{B}(\mathsf{End}_{\bstr}(U) \wr \Sigma_i),
+        (\disk_{/M})_{(i_{[U]} | [U])} \simeq \coprod_{[U]} \mathrm{Conf}_{i_{[U]}}(M_{[U]})_{\Sigma_{i_{[U]}}}.
     \end{equation}
     %
-    as given by \cite[Lem.2.21]{aft_fhstrat}.
-The same lemma also tells us that the maximal $\infty$-groupoid of $\disk_{/M}$ is given by\footnote{The notation $M_{[U]}$ denotes the $[U]$-stratum of the stratified manifold $M$, which is a \emph{smooth} manifold, as defined in \cite[Def.4.4.5]{aft_localstrut}.}
+    Thus, we endeavor to show that the induced morphism
     %
     \begin{equation}
-        \disk_{/M}^{\simeq} \simeq \coprod_{i \geq 0} \prod_{[U]} \mathrm{Conf}_{i}(M_{[U]})_{\Sigma_i}.
+        \mathsf{colim} (\mathscr{U} \xrightarrow{} \mfld[r](\bstr) \xrightarrow{\mathrm{Conf}_{i_{[U]}}(-_{[U]})_{\Sigma_{i_{[U]}}}} \mathsf{Sp}) \xrightarrow{\ \ \ \ \ } \mathrm{Conf}_{i_{[U]}}(M_{[U]})_{\Sigma_{i_{[U]}}}
     \end{equation}
     %
-    In both cases, the product runs over isomorphism classes of basics.
-It is also clear that the map $\disk_{/M}^{\simeq} \xrightarrow{} \disk(\bstr)^{\simeq}$ resulting from the right fibration from the slice respects this decomposition in that there result maps of spaces
-    %
-    \begin{equation}
-        \mathrm{Conf}_i(M_{[U]})_{\Sigma_i} \xrightarrow{\ \ \ \ } \mathsf{B}(\mathsf{End}_{\bstr}(U) \wr \Sigma_i),
-    \end{equation}
-    %
-    for each $i \geq 0$, and each isomorphism class $[U]$ of basics in $\bstr$. Thus, working piece by piece, we need to show that
-    %
-    \begin{equation}
-        \mathsf{colim} (\mathscr{U} \xrightarrow{} \mfld[r](\bstr) \xrightarrow{\mathrm{Conf}_{i}(-_{[U]})_{\Sigma_i}} \mathsf{Sp}_{/\mathsf{B}(\mathsf{End}_{\bstr}(U) \wr \Sigma_i)}) \xrightarrow{\ \ \simeq \ \ } \mathrm{Conf}_{i}(M_{[U]})_{\Sigma_i},
-    \end{equation}
-    %
-    for all $i$ and $[U]$ as specified before, where we notice that the decomposition into maps of spaces means that our target is even $\mathsf{Sp}_{/\mathsf{B}(\mathsf{End}_{\bstr}(U) \wr \Sigma_i)}$ and not just right fibrations.
-We will first explain this equivalence at the level of spaces and only after will we argue why the equivalence respects the maps to $\mathsf{B}(\mathsf{End}_{\bstr}(U) \wr \Sigma_i)$.
+    is an equivalence of spaces for all isomorphism classes of basics $[U]$ and for all $i_{[U]} \geq 0$.
 From a Weiss sieve $\mathscr{U}$ of $M$ we easily get a Weiss sieve $\mathscr{U}_{[U]}$ of $M_{[U]}$ by intersecting with $M_{[U]}$ as a submanifold of $M$.
-Using $\mathscr{U}_{[U]}$, we define $\mathscr{U}_{i, [U]}$ to be the sieve of $\mathrm{Conf}_i(M_{[U]})_{\Sigma_i}$ as in \Cref{lem:weiss_to_ordinary}.
+Using $\mathscr{U}_{[U]}$, we define $\mathscr{U}_{i_{[U]}, [U]}$ to be the sieve of $\mathrm{Conf}_{i_{[U]}}(M_{[U]})_{\Sigma_{i_{[U]}}}$ as in \Cref{lem:weiss_to_ordinary}.
 These considerations give us equivalences
@@
     \begin{align}\label{eq:ord_to_W_equivs}
-        \mathsf{colim} (\mathscr{U} \xrightarrow{} \mfld[r](\bstr) \xrightarrow{\mathrm{Conf}_{i}(-_{[U]})_{\Sigma_i}} \mathsf{Sp}) &\simeq \mathsf{colim} (\mathscr{U}_{[U]} \xrightarrow{} \mfld[r](\bstr) \xrightarrow{\mathrm{Conf}_{i}(-)_{\Sigma_i}} \mathsf{Sp})\notag\\
-        &\simeq \mathsf{colim} (\mathscr{U}_{i,[U]} \xrightarrow{} \mfld[r](\bstr) \xrightarrow{} \mathsf{Sp}).
+        \mathsf{colim} (\mathscr{U} \xrightarrow{} \mfld[r](\bstr) \xrightarrow{\mathrm{Conf}_{i_{[U]}}(-_{[U]})_{\Sigma_{i_{[U]}}}} \mathsf{Sp}) &\simeq \mathsf{colim} (\mathscr{U}_{[U]} \xrightarrow{} \mfld[r](\bstr) \xrightarrow{\mathrm{Conf}_{i_{[U]}}(-)_{\Sigma_{i_{[U]}}}} \mathsf{Sp})\notag\\
+        &\simeq \mathsf{colim} (\mathscr{U}_{i_{[U]},[U]} \xrightarrow{} \mfld[r](\bstr) \xrightarrow{} \mathsf{Sp}).
     \end{align}
@@
     The second equivalence in the above is simply a statement about the unions over the two covers and is a restatement of \Cref{lem:weiss_to_ordinary}.
-But, by \cite[Prop.A.3.2]{lurie_ha} there is an equivalence
+But, by \cite[Prop.A.3.2]{lurie_ha} the induced map is an equivalence
     %
     \begin{equation}\label{eq:gluing_top_lurie}
-        \mathsf{colim} (\mathscr{U}_{i,[U]} \xrightarrow{} \mfld[r](\bstr) \xrightarrow{} \mathsf{Sp}) \xrightarrow{\ \ \simeq \ \ } \mathrm{Conf}_{i}(M_{[U]})_{\Sigma_i}.
+        \mathsf{colim} (\mathscr{U}_{i_{[U]},[U]} \xrightarrow{} \mfld[r](\bstr) \xrightarrow{} \mathsf{Sp}) \xrightarrow{\ \ \simeq \ \ } \mathrm{Conf}_{i_{[U]}}(M_{[U]})_{\Sigma_{i_{[U]}}}.
     \end{equation}
-    %
-    It is obvious that the equivalences in \Cref{eq:ord_to_W_equivs} lie over $\mathsf{B}(\mathsf{End}_{\bstr}(U) \wr \Sigma_i)$, since they're nothing more than a rewriting.
-The equivalence in \Cref{eq:gluing_top_lurie} also lies over $\mathsf{B}(\mathsf{End}_{\bstr}(U) \wr \Sigma_i)$ because all the various pieces that we're gluing in $\mathsf{Sp}$ come from unordered configuration space manifolds.............
 \end{proof}
-
-\begin{remark}
-    That the maps to $\mathsf{B}(\mathsf{End}_{\bstr}(U) \wr \Sigma_i)$ don't play much of a role can also be seen through the fact that this is the only place where the choice of tangential structure $\bstr$ enters the discussion in the form of including or excluding certain endomorphisms.
-\end{remark}
 
@@
     %
-    \begin{equation}
+    \begin{equation}\label{eq:fh_colim_formula}
         \int_e F \simeq \mathsf{colim} (\disk_{/N} \xrightarrow{\simeq} (\disk_{/M})_{/e} \xrightarrow{} \disk_{/M} \xrightarrow{F} \catC),
@@
     %
-    and this allows us to rewrite our canonical map from \Cref{eq:fhfunc_canonical_map} into
+    and this allows us to rewrite our canonical map from \Cref{eq:fhfunc_canonical_map}.
+On the right-hand side we just insert \Cref{eq:fh_colim_formula}, but the left-hand side requires more elaboration.
+After substituting \Cref{eq:fh_colim_formula} into the left-hand side of \Cref{eq:fhfunc_canonical_map} we're doing two colimits, and we can pull some information from the inner colimit into the outer one, namely as
     %
+    \begin{equation}
+        \mathsf{colim} \Big( \mathscr{U} \xrightarrow{} \mfld[r](\bstr) \xrightarrow{\disk_{/-}} \cat| \xrightarrow{\mathsf{colim}(- \xrightarrow{} \disk_{/M} \xrightarrow{F} \catC)} \catC \Big),
+    \end{equation}
+    %
+    where $\cat|$ is the restriction to the image of the functor $\mfld[r]_{/M} \xrightarrow{} \mfld[r](\bstr) \xrightarrow{} \cat$ in the above.... We want to show that $ $
+
     \begin{align}
         \mathsf{colim} \Big( \mathsf{colim} (\mathscr{U} \xrightarrow{} \mfld[r](\bstr) \xrightarrow{\disk_{/-}} \cat) \xrightarrow{} &\disk_{/N} \rightarrow \disk_{/M} \xrightarrow{F} \catC \Big)\notag\\
-        \xrightarrow{\ \ \ \ \ } \mathsf{colim} (&\disk_{/N} \xrightarrow{} \disk_{/M} \xrightarrow{F} \catC).
+        \xrightarrow{\ \ \ \ \ } \mathsf{colim} (&\disk_{/N} \xrightarrow{} \disk_{/M} \xrightarrow{F} \catC),
     \end{align}
     %
+    where for the right-hand side we've just inserted \Cref{eq:fh_colim_formula}, while for the left-hand side we've further included a rewriting of the two colimits in play.
 However, the statement of \Cref{lem:gluing_disk/M} is exactly the statement that the above map is an equivalence.
@@
     Intuitively, the key idea for the statement and proof is that $\disk[r]_{/N}$ is a basis for the Weiss Grothendieck topology on manifolds.
-This is essentially because for each finite set of points $S \subset N$, and each Weiss cover of it $U_S$, we can take small enough disks $\{ D_s \}_{s \in S}$ around each point, by virtue of $N$ being a manifold, and their disjoint union will cover $S$, as well as satisfy $\sqcup_{s \in S} D_s \subset U_S$.
-The proof of \cite[prop.2.22]{af_primer} makes this precise, and the above proof transports that idea to the relative case.
+This is essentially because for each finite set of points $S \subset N$ we can take disks $\{ D_s \}_{s \in S}$ around each point, by virtue of $N$ being a manifold.
+Subsequently, for each $U_S$ that covers $S$ we can take small enough disks, whose disjoint union will cover $S$ by construction, as well as satisfy $\sqcup_{s \in S} D_s \subset U_S$.
+The proof makes this idea precise, and tells us that we can calculate factorization homology using any Weiss sieve
+    %
+    \begin{equation}
+        \int_M F \simeq \mathsf{colim}(\disk[r]_{/M} \xrightarrow{} \disk_{/M} \xrightarrow{F} \catC)
+        \simeq \mathsf{colim}(\mathscr{U} \xrightarrow{} \disk_{/M} \xrightarrow{F} \catC).
+    \end{equation}
 \end{remark}
+
+The above proof already shows how the ideas that went into defining factorization algebras are not that different from the ideas that went into defining factorization homology.
+Namely, the ideas of Weiss cosheaves and algebras over disks are deeply connected.
+Now that this connection has been illuminated, the proof of \Cref{thm:disk_alg=lcfa}, which we delve into promptly, is not hard to establish.
 
@@
     To show essential surjectivity of $\int$, for each $F \in \lcfa_M (\catC)$ we will find an equivalence $\int F| \simeq F$ in $\lcfa_M (\catC)$, with $F|$ to be defined later.
-Since $\lcfa_M (\catC) \xrightarrow{} \alg{\opens(M)}$ is fully faithful, this amounts to finding equivalences of prefactorization algebras, namely a family of equivalences
+Since $\lcfa_M (\catC) \xrightarrow{} \alg{\opens(M)}$ is fully faithful, this amounts to finding an equivalence of prefactorization algebras, namely a family of equivalences
     %
@@
     %
-    one for each $(U \xhookrightarrow{} M) \in \mfld[r]_{/M}$, which preserve the multiplicative structure (see \Cref{cd:fa_morphisms}).
+    one for each $(U \xhookrightarrow{} M) \in \mfld[r]_{/M}$, which are natural in $U$ and preserve the multiplicative structure (see \Cref{cd:fa_morphisms}).
 Since $F$ is a locally constant factorization algebra the functor
@@
     %
-    and using the fact that $\disk[r]_{/U} \xrightarrow{} \disk_{/U}$ is final (\cite[prop.2.22]{aft_fhstrat}) immediately gives us that
+    where $F|$ is the restriction of $F$ to disks, and using the fact that $\disk[r]_{/U} \xrightarrow{} \disk_{/U}$ is final (\cite[prop.2.22]{aft_fhstrat}) immediately gives us that
     %
     \begin{equation}
-        F(U) \simeq \mathsf{colim} (\disk_{/U} \xrightarrow{} \disk_{/M} \xrightarrow{F|} \catC) =: \int_U F|.
+        F(U) \simeq \mathsf{colim} (\disk_{/U} \xrightarrow{} \disk_{/M} \xrightarrow{F|} \catC) \simeq \int_U F|.
     \end{equation}
     %
-    To preserve the multiplicative structure, these equivalences have to be natural, and there also has to be a commutative diagram
+    Naturality of these equivalences is immediate from the construction because, as already used, each inclusion of open subsets $V \xhookrightarrow{} U$ gives a full subcategory inclusion $\disk[r]_{/V} \xhookrightarrow{} \disk[r]_{/U}$.
+Given this fact, to preserve the multiplicative structure it is enough to show that the following is a commutative diagram
     %
@@
     %
-    for each collection of disjoint open sets $\{U_i\}$.
-Naturality is immediate from the construction because, as already used, each inclusion of open subsets $V \xhookrightarrow{} U$ gives a full subcategory inclusion $\disk[r]_{/V} \xhookrightarrow{} \disk[r]_{/U}$.
-On the other hand, the existence of the commutative diagram is guaranteed by the equivalence
+    for each collection of disjoint open sets $\{U_i\}$. This, however, is guaranteed by the equivalences
     %
@@
 
-As before, the case of ordinary factorization algebras gets a similar statement whose proof goes along the same lines:
-
 \begin{remark}
@@
 \begin{remark}
-    As noted at the beginning of \S 2, the physical interpretation of this version of factorization homology is a way to take a spacetime $M$ and its local observables $A$, and construct \emph{some}, and typically not all, of the global observables.
-The previous \Cref{thm:disk_alg=lcfa} and \Cref{cor:disk_alg=falg} transfer this observation to factorization algebras, which aligns with the observation of \cite{cg2016} that the current version of factorization algebras can only deal with perturbative quantum field theory.
+    As noted at the beginning of \S2, the physical interpretation of this version of factorization homology is a way to take a spacetime $M$ and its local observables $A$, and construct \emph{some}, though typically not all, of the global observables.
+The previous \Cref{thm:disk_alg=lcfa} and \Cref{cor:disk_alg=falg} transfer this observation to factorization algebras, which aligns with the observation of \cite{cg2016} that the current version of factorization algebras can only deal with perturbative quantum field theories.
+\end{remark}
+
+\begin{remark}
+    The results of \Cref{thm:disk_alg=lcfa} and \Cref{cor:disk_alg=falg} can be seen as lowering the amount of data that is necessary to define a factorization algebra.
+There is a similar, but slightly weaker result in \cite[\S7.2]{cg2016}, which nonetheless works for all Hausdorff topological spaces.
+The key tool for them are factorizing bases, which play the role of Weiss covers but are further required to be closed under finite intersections.
+Their result then says that a factorization algebra defined on such a basis $\mathscr{U}$ can be extended to the full space $X$, namely there is an equivalence
+    %
+    \begin{equation}
+        \begin{tikzcd}
+            \falg_X(\catC) \arrow[rr, bend left=10, "\mathrm{-|_{\mathscr{U}}}"] \arrow[rr, phantom, "\simeq"]&  & \falg_{\mathscr{U}}(\catC) \arrow[ll, bend left=10, "\mathrm{ext}"].
+        \end{tikzcd}
+    \end{equation}
+    %
+    In comparison, our result drops the intersection requirement, while maintaining the statement.
 \end{remark}
@@
 The lemma says that for stratified manifolds $M$ that satisfy the conditions, the classification of locally constant factorization algebras on $M$, i.e.
-algebras over $\disk_{/M}$ simplifies to the classification of $\disk(\bstr_M)$-algebras in the usual sense
+algebras over $\disk_{/M}$ simplifies to the classification of $\disk(\bstr_M)$-algebras in the usual sense, which are typically easier to work with,
 %
@@
 \end{equation}
-%
-This is an improvement because $\disk(\bstr_M)$-algebras are easier to work with, one reason being that $\disk(\bstr_M)$ has the benefit of being not just an $\infty$-operad but even a symmetric monoidal $\infty$-category.
-
-The results of \Cref{thm:disk_alg=lcfa} and \Cref{cor:disk_alg=falg} can also be seen as lowering the amount of data that is necessary to say that we have defined a factorization algebra on a stratified manifold.
-There is a similar, but slightly weaker result by \cite{cg2016}, which nonetheless works for all Hausdorff topological spaces.
-We recount this result here for comparison.
-
-\begin{definition}
-    A \emph{factorizing basis} of a topological space $X$ is a basis $\{ U_i \xhookrightarrow{} X\}_{i \in I}$ for the topology of $X$ which is closed under finite intersections, and which satisfies that for each finite set $S \subset X$, there exists a finite sub-collection of pairwise disjoint open subsets $\{ U_j \xhookrightarrow{} X\}_{j \in J}$, for which $S \subset \bigsqcup_{j \in J} U_j$.
-\end{definition}
-
-\begin{definition}
-    We will call factorization algebras defined only on the open subsets of an open cover $\mathscr{U}$ (in particular, for example, a factorizing basis), a $\mathscr{U}$-factorization algebra and the $\infty$-category of such $\falg_{\mathscr{U}}(\catC)$.
-\end{definition}
-
-\begin{theorem}[\cite{cg2016}]\label{thm:fa_from_basis}
-    Given a Hausdorff topological space $X$, there is an equivalence of $\infty$-categories between the $\infty$-categories of $\mathscr{U}$-factorization algebras defined on a factorizing basis $\mathscr{U}$ and factorization algebras defined on the full topological space $X$
-    %
-    \begin{equation}
-        \begin{tikzcd}
-            \falg_X(\catC) \arrow[rr, bend left=10, "\mathrm{-|_{\mathscr{U}}}"] &  & \falg_{\mathscr{U}}(\catC) \arrow[ll, bend left=10, "\mathrm{ext}"],
-        \end{tikzcd}
-    \end{equation}
-    %
-    where the top functor is given by restriction.
-\end{theorem}
-
-\begin{remark}
-    Looking into the proof of this statement we see that the value of the extension on open sets $U \subset X$ is defined as
-    %
-    \begin{equation}
-        \mathrm{ext}(F)(U) := \cech(\mathscr{U}_U, F),
-    \end{equation}
-    %
-    where $\mathscr{U}_U$ is a Weiss cover of $U$ generated by $\mathscr{U}$.
-That such a cover exists is already guaranteed by the Hausdorffness of $X$ and the basis property of $\mathscr{U}$.
-Namely, given any finite set $S \subset U$, Hausdorffness gives us the existence of pairwise disjoint open sets $\{ V_s \ni s\}_{s \in S}$, while the basis property of $\mathscr{U}$ gives us open subsets $\{ U_s \in \mathscr{U} \}_{s \in S}$ such that $s \in U_s \subset V_s$.
-$\sqcup_{s \in S} U_s$ then gives an open set that covers $S$.
-\end{remark}
-
-\begin{remark}
-    The proof of \Cref{thm:fa_from_basis} can be found in \cite[ch.7.2]{cg2016}, and we will not reproduce it here.
-The target category there is the category of chain complexes, but it holds more generally in $\catC$ by considering simplicial objects and their geometric realizations (which exist by the colimit assumption on $\catC$) instead.
-
-    As mentioned, in the stratified manifold case, this is an easy corollary of the proof of \Cref{prop:fh_disk_to_lcfa}, where we show that taking all disks as the Weiss cover of choice reproduces the result that we would have gotten with any other Weiss cover.
-It is important to point out though that disks are not necessarily closed under intersections, which means that we don't have the opposite implication, and the methods to prove \Cref{prop:fh_disk_to_lcfa} are necessary.
-\end{remark}
 
@@
 
-    It is not hard to check that the above also holds for the example of factorization algebras on topological spaces, by using \Cref{thm:fa_from_basis}.
+    It is not hard to check that the above also holds for the example of factorization algebras on topological spaces, by using \cite[\S7.2]{cg2016}.
 However, we'll focus on manifolds, in which case, the construction from above immediately works since we now have to do it for $\disk[r]_{/X}$ instead of $\mfld[r]_{/X}$.
@@
     Consider a unital, (homotopy) associative algebra $A$ in the category $\catC$.
-For a first pass we use \Cref{thm:fa_from_basis} to construct a factorization algebra out of this data.
+For a first pass we use \cite[\S7.2]{cg2016} to construct a factorization algebra out of this data.
 We first check that the disks $\disk[r]_{/\mathbb{R}}$ of $\mathbb{R}$ form a factorizing basis.
 This is true since the disks are always a basis for any manifold, they are factorizing since we have all disjoint unions, and they are closed under finite intersections because the disks of $\mathbb{R}$ are intervals.
-Therefore, by \Cref{thm:fa_from_basis}, we need only assign values to these.
+Therefore, by \cite[\S7.2]{cg2016}, we need only assign values to these.
 Given any disk $U$ we assign the same value, $F_A(U) := A$.
@@
 At this point we have constructed a prefactorization algebra on $\mathbb{R}$.
-To use \Cref{thm:fa_from_basis} we need to first check the Weiss cosheaf condition.
+To use \cite[\S7.2]{cg2016} we need to first check the Weiss cosheaf condition.
 But because intervals are closed under finite intersections the \v{C}ech nerve definition of \Cref{rem:check_nerve} makes this easy; the simplicial object $\cech_{\bullet}(\disk[r]_{/\mathbb{R}}, F_A)$ in all degrees will be a coproduct of copies of $A$.

### 2024-06-21 sections/3algebras.tex
..

@@
 \begin{proposition}\label{prop:fh_disk_to_lcfa}
-    Given a stratified manifold $M$ factorization homology provides a functor between the $\infty$-categories of $\disk_{/M}$-algebras and locally constant factorization algebras $\lcfa_M$
+    Given a stratified manifold $M$ factorization homology provides a functor
     %
     \begin{equation}
-        \int : \alg{\disk_{/M}} (\catC) \xrightarrow{\ \ \ \ } \lcfa_M (\catC).
+        \int : \alg{\disk_{/M}} (\catC) \xrightarrow{\ \ \ \ } \lcfa_M (\catC)
     \end{equation}
+    %
+    between the $\infty$-categories of $\disk_{/M}$-algebras and locally constant factorization algebras $\lcfa_M$.
 \end{proposition}
@@
 \begin{theorem}\label{thm:disk_alg=lcfa}
-    For each stratified manifold $M$, the previously constructed factorization homology functor provides an equivalence of $\infty$-categories between $\disk_{/M}$-algebras and locally constant factorization algebras on $M$.
-Equivalently, the $\infty$-operad governing locally constant factorization algebras can be taken to be $\disk_{/M}$
+    For each stratified manifold $M$, the previously constructed factorization homology functor provides an equivalence of $\infty$-categories
     %
     \begin{equation}
-        \alg{\disk_{/M}} (\catC) \xrightarrow[\int]{\ \ \simeq \ \ } \lcfa_M (\catC).
+        \alg{\disk_{/M}} (\catC) \xrightarrow[\int]{\ \ \simeq \ \ } \lcfa_M (\catC)
     \end{equation}
+    %
+    between $\disk_{/M}$-algebras and locally constant factorization algebras on $M$.
+Equivalently, the $\infty$-operad governing locally constant factorization algebras can be taken to be $\disk_{/M}$.
 \end{theorem}
@@
 
-In the service of working towards proofs of all of these results we first have to pause and develop some necessary technically results regarding Weiss covers.
+In the service of working towards proofs of all of these results we first have to pause and develop some necessary technically results regarding Weiss covers and preservation of colimits.
 
@@
         \item $\mathscr{U}$ is a Weiss sieve of $M$,
-        \item for all $n \geq 0$, the sieve $\{ \mathrm{Conf}_n(U)_{\Sigma_n} \xhookrightarrow{} \mathrm{Conf}_n(M)_{\Sigma_n} \mid U \in \mathscr{U} \}$ is a covering sieve of the unordered configuration space $\mathrm{Conf}_n(M)_{\Sigma_n}$ of $n$ points in $M$.
+        \item for all $n \geq 0$, the smallest sieve containing $\{ \mathrm{Conf}_n(U)_{\Sigma_n} \xhookrightarrow{} \mathrm{Conf}_n(M)_{\Sigma_n} \mid U \in \mathscr{U} \}$ is a covering sieve of the unordered configuration space $\mathrm{Conf}_n(M)_{\Sigma_n}$ of $n$ points in $M$.
     \end{enumerate}
@@
 
+{\color{red} This is the statement in the absolute case, needs to be adapted to the relative case.}
+
 \begin{lemma}\label{lem:gluing_disk/M}
@@
 The objects of the base $\disk(\bstr)$ (e.g.
-acroding to \cite[Lem.2.21]{aft_fhstrat}) are lists $(i_{[U]} | [U] \in [\bstr])$ of integers, one for each isomorphism class of objects in $\bstr$.
+according to \cite[Lem.2.21]{aft_fhstrat}) are lists $(i_{[U]} | [U] \in [\bstr])$ of integers, one for each isomorphism class of objects in $\bstr$\footnote{The choice of $\bstr$-structure does not play much of a role, because if we don't choose the appropriate one some fibers can be trivial, but this does not impede the result.}.
 According to the same lemma, the fibers are given by the spaces
@@
     \end{equation}
+\end{proof}
+
+\begin{lemma}\label{lem:gluing_disk/M/e}
+    A Weiss sieve $\mathscr{U} \subset \mfld[r]_{/M}$ canonically determines a morphism
+    %
+    \begin{equation}
+        \mathsf{colim} (\mathscr{U} \xrightarrow{} \mfld[r]_{/M} \xrightarrow{(\disk_{/M})_{/-}} \mathsf{RFib}_{\disk_{/M}}) \xrightarrow{\ \ \simeq \ \ } (\disk_{/M})_{/-}
+    \end{equation}
+    of right fibrations over $\disk_{/M}$, which moreover, is an equivalence.
+\end{lemma}
+
+\begin{proof}
+    .....
+\end{proof}
+
+The following lemma about preservation of colimits is sketched out in \cite{rezk2023lan}.
+%
+\begin{lemma}\label{lem:Lan_preserve_colim}
+    Let $F: \mathscr{D} \xrightarrow{} \catC$ and $\iota: \mathscr{D} \xrightarrow{} \mathscr{M}$ be functors of (locally small) $\infty$-categories, where $\mathscr{M}$ and $\catC$ are cocomplete.
+Let $L_{\iota} F: \mathscr{M} \xrightarrow{} \catC$ be the left Kan extension of $F$ along $\iota$.
+$L_{\iota} F$ preserves a given colimit if, and only if, the restricted Yoneda embedding
+    %
+    \begin{align}
+        T_{\iota}: \mathscr{M} \xrightarrow{\ y_{\mathscr{M}} \ } \mathsf{PShv}(\mathscr{M}) \xrightarrow{\ \iota^* \ } \mathsf{PShv}(\mathscr{D}) 
+    \end{align}
+    %
+    does so.
+\end{lemma}
+
+\begin{proof}
+    First consider the special case when $(\iota: \mathscr{D} \xrightarrow{} \mathscr{M}) = (y_{\mathscr{D}}: \mathscr{D} \xrightarrow{} \mathsf{PShv}(\mathscr{D}))$ the Yoneda embedding of $\mathscr{D}$.
+We will see that in this case, $L_{y_{\mathscr{D}}} F$ is colimit preserving because it is a left adjoint to the functor
+    %
+    \begin{equation}
+        T_F: \catC \xrightarrow{y_{\catC}} \mathsf{PShv} (\catC) \xrightarrow{F^*} \mathsf{PShv} (\mathscr{D}).
+    \end{equation}
+    %
+    %Indeed, let $X \simeq y_{\mathscr{D}} (d)$ be a representable presheaf, then there is an equivalence of morphism spaces $\mathsf{Hom}_{\catC} (L_{y_{\mathscr{D}}} F (X), c) \simeq \mathsf{Hom}_{\mathsf{PShv}(\mathscr{D})} (X, T_F (c))$ given by
+    %
+    %\begin{align}
+    %    \mathsf{Hom}_{\catC} (L_{y_{\mathscr{D}}} F (X), c) &\simeq \mathsf{Hom}_{\catC} (F (d), c) \simeq \mathsf{Hom}_{\mathsf{PShv}(\catC)} (y_{\catC}(F(d)), y_{\catC}(c))\notag\\ &\simeq \mathsf{Hom}_{\mathsf{PShv}(\mathscr{D})} (F^*(y_{\catC}(F(d))), T_F(c)) \simeq \mathsf{Hom}_{\mathsf{PShv}(\mathscr{D})} (X, T_F(c)).
+    %\end{align}
+    %
+    %In general, the Yoneda embedding $y_{\mathscr{D}}$ is a dense functor
+
+    {\color{red} Proof of being adjoint}
+
+    In the general situation where $\iota$ is not necessarily the Yoneda embedding we can partially reduce to the previous case because we can write
+    %
+    \begin{equation}
+        L_{\iota} F \simeq L_{y_{\mathscr{D}}}F \circ L_{\iota} y_{\mathscr{D}}.
+    \end{equation}
+    %
+    Namely, this is because we know that $L_{y_{\mathscr{D}}} F$ preserves colimits, and by the assumptions in the lemma, $L_{\iota} F$ and $L_{\iota} y_{\mathscr{D}}$ are computed pointwise, as colimits over the same indexing $\infty$-category.
+
+    Finally, we claim that there is an equivalence of functors
+    %
+    \begin{equation}
+        \Big( L_{\iota} y_{\mathscr{D}} \simeq T_{\iota} \Big) \in \mathsf{Fun}(\mathscr{M}, \mathsf{PShv}(\mathscr{D})) 
+    \end{equation}
+
+    {\color{red} Proof of functor equivalence}
+
 \end{proof}
@@
 By the definition of $\csheaves[W](\mfld_{/M}, \catC)$, this means that the restriction of $\int F$ to $\mathsf{Fun}(\mfld[r]_{/M}, \catC)$ satisfies the cosheaf property for every Weiss sieve $\mathscr{U} \subset (\mfld[r]_{/M})_{/e}$, where $e:N \xhookrightarrow{} M$ is an open embedding.
-Here we notice that for the Weiss property to even make sense, we are implicitly using \Cref{lem:double_slice}, so that the Weiss sieve $\mathscr{U}$ is defined as a subcategory of $\mfld[r]_{/N}$.
+Here we notice that for the Weiss property to even make sense, we are implicitly using \Cref{lem:double_slice}, so that the Weiss sieve $\mathscr{U}$ is defined as an $\infty$-subcategory of $\mfld[r]_{/N}$.
 
-    A similar calculation appears in part 2 of the proof of \cite[prop.2.22]{af_primer}, with the caveat that there things are presented for smooth manifolds.
-However, because of \Cref{lem:weiss_to_ordinary} and \Cref{lem:gluing_disk/M} we can adapt the proof to the stratified setting as well.
-Namely, we're trying to show that the canonical map
+    With the Weiss cosheaf property being a statement about preserving colimits, and with $\int F$ being a left Kan extension we are exactly in the situation of \Cref{lem:Lan_preserve_colim}.
+Thus, we only need to show that functor $T: \mfld_{/M} \xrightarrow{} \mathsf{PShv} (\disk_{/M})$\footnote{This functor is related to the tangent classifier, with the differences being that we're now in the relative case, and we're not fully limiting to $\bsc$ but instead only to disks.} preserves Weiss colimits, namely that there is an equivalence
     %
-    \begin{equation}\label{eq:fhfunc_canonical_map}
-        \mathsf{colim}(\mathscr{U} \xhookrightarrow{} \mfld[r]_{/N} \xrightarrow{} \mfld[r]_{/M} \xrightarrow{} \mfld_{/M} \xrightarrow{\int F} \catC) \xrightarrow{\ \ \ \ } \int_e F
+    \begin{equation}
+        \mathsf{colim} (\mathscr{U} \xrightarrow{} \mfld_{/M} \xrightarrow{T} \mathsf{PShv} (\disk_{/M})) \simeq T(N \xhookrightarrow{} M),
     \end{equation}
     %
-    is an equivalence for each sieve $\mathscr{U}$. Since $\catC$ has all relevant colimits the left Kan extension $\int F$ is given pointwise by
+    where on the right-hand side we've used the fact that $\mathscr{U}$ is, in particular, a covering sieve.
+If we also append the straightening--unstraightening construction to $T$, we can write the desired equivalence as
     %
-    \begin{equation}\label{eq:fh_colim_formula}
-        \int_e F \simeq \mathsf{colim} (\disk_{/N} \xrightarrow{\simeq} (\disk_{/M})_{/e} \xrightarrow{} \disk_{/M} \xrightarrow{F} \catC),
+    \begin{equation}
+        \mathsf{colim} (\mathscr{U} \xrightarrow{} \mfld_{/M} \xrightarrow{ (\disk_{/M})_{/-}} \mathsf{RFib}_{\disk_{/M}}) \simeq (\disk_{/M})_{/e}.
     \end{equation}
     %
-    and this allows us to rewrite our canonical map from \Cref{eq:fhfunc_canonical_map}.
-On the right-hand side we just insert \Cref{eq:fh_colim_formula}, but the left-hand side requires more elaboration.
-After substituting \Cref{eq:fh_colim_formula} into the left-hand side of \Cref{eq:fhfunc_canonical_map} we're doing two colimits, and we can pull some information from the inner colimit into the outer one, namely as
-    %
-    \begin{equation}
-        \mathsf{colim} \Big( \mathscr{U} \xrightarrow{} \mfld[r](\bstr) \xrightarrow{\disk_{/-}} \cat| \xrightarrow{\mathsf{colim}(- \xrightarrow{} \disk_{/M} \xrightarrow{F} \catC)} \catC \Big),
-    \end{equation}
-    %
-    where $\cat|$ is the restriction to the image of the functor $\mfld[r]_{/M} \xrightarrow{} \mfld[r](\bstr) \xrightarrow{} \cat$ in the above.... We want to show that $ $
-
-    \begin{align}
-        \mathsf{colim} \Big( \mathsf{colim} (\mathscr{U} \xrightarrow{} \mfld[r](\bstr) \xrightarrow{\disk_{/-}} \cat) \xrightarrow{} &\disk_{/N} \rightarrow \disk_{/M} \xrightarrow{F} \catC \Big)\notag\\
-        \xrightarrow{\ \ \ \ \ } \mathsf{colim} (&\disk_{/N} \xrightarrow{} \disk_{/M} \xrightarrow{F} \catC),
-    \end{align}
-    %
-    where for the right-hand side we've just inserted \Cref{eq:fh_colim_formula}, while for the left-hand side we've further included a rewriting of the two colimits in play.
-However, the statement of \Cref{lem:gluing_disk/M} is exactly the statement that the above map is an equivalence.
+    \Cref{lem:gluing_disk/M/e} guarantees the existence of this equivalence.
 \end{proof}
@@
 Namely, the ideas of Weiss cosheaves and algebras over disks are deeply connected.
-Now that this connection has been illuminated, the proof of \Cref{thm:disk_alg=lcfa}, which we delve into promptly, is not hard to establish.
+Now that this connection has been explained, the proof of \Cref{thm:disk_alg=lcfa}, which we delve into promptly, is not hard to establish.
 

### 2024-07-17 sections/3algebras.tex
Adding the changes discussed yesterday to section 3.2.

@@
 
-{\color{red} This is the statement in the absolute case, needs to be adapted to the relative case.}
-
-\begin{lemma}\label{lem:gluing_disk/M}
-    A Weiss sieve $\mathscr{U} \subset \mfld[r]_{/M}$ canonically determines a morphism
-    %
-    \begin{equation}
-        \mathsf{colim} (\mathscr{U} \xrightarrow{} \mfld[r] \xrightarrow{\disk_{/-}} \mathsf{RFib}_{\disk(\bstr)}) \xrightarrow{\ \ \simeq \ \ } \disk_{/M}
-    \end{equation}
-    of right fibrations over $\disk(\bstr)$, which moreover, is an equivalence.
+%To show the equivalence, we follow a related strategy to the one laid out in part 2 of the proof of \cite[Prop.2.22]{af_primer}.
+
+\begin{lemma}\label{lem:gluing_disk/M/e}
+    A Weiss sieve $\mathscr{U} \subset (\mfld[r]_{/M})_{/e}$ canonically determines a morphism
+    %
+    \begin{equation}
+        \mathsf{colim} \big( \mathscr{U} \xrightarrow{} \mfld[r]_{/M} \xrightarrow{\mathsf{Hom}_{\mfld_{/M}}(\cdot, -)} \mathsf{PShv}(\disk_{/M}) \big) \xrightarrow{\ \ \simeq \ \ } \mathsf{Hom}_{\mfld_{/M}}(\cdot, e)
+    \end{equation}
+    of presheaves over $\disk_{/M}$, which moreover, is an equivalence.
 \end{lemma}
@@
 \begin{proof}
-    The morphism is determined by the universal property of the colimit with the component maps $\disk_{/U} \xrightarrow{} \disk_{/M}$ given from the open embeddings $U \xhookrightarrow{} M$.
-To show the equivalence, we follow a related strategy to the one laid out in part 2 of the proof of \cite[Prop.2.22]{af_primer}.
-By \cite[Def.2.2.3.2]{lurie_htt}, a morphism of right fibrations, as in the statement, is an equivalence if, and only if, it induces equivalences of spaces on the fibers over each object of the base.
-The objects of the base $\disk(\bstr)$ (e.g.
-according to \cite[Lem.2.21]{aft_fhstrat}) are lists $(i_{[U]} | [U] \in [\bstr])$ of integers, one for each isomorphism class of objects in $\bstr$\footnote{The choice of $\bstr$-structure does not play much of a role, because if we don't choose the appropriate one some fibers can be trivial, but this does not impede the result.}.
-According to the same lemma, the fibers are given by the spaces
-    %
-    \begin{equation}
-        (\disk_{/M})_{(i_{[U]} | [U])} \simeq \coprod_{[U]} \mathrm{Conf}_{i_{[U]}}(M_{[U]})_{\Sigma_{i_{[U]}}}.
-    \end{equation}
-    %
-    Thus, we endeavor to show that the induced morphism
-    %
-    \begin{equation}
-        \mathsf{colim} (\mathscr{U} \xrightarrow{} \mfld[r](\bstr) \xrightarrow{\mathrm{Conf}_{i_{[U]}}(-_{[U]})_{\Sigma_{i_{[U]}}}} \mathsf{Sp}) \xrightarrow{\ \ \ \ \ } \mathrm{Conf}_{i_{[U]}}(M_{[U]})_{\Sigma_{i_{[U]}}}
-    \end{equation}
-    %
-    is an equivalence of spaces for all isomorphism classes of basics $[U]$ and for all $i_{[U]} \geq 0$.
-From a Weiss sieve $\mathscr{U}$ of $M$ we easily get a Weiss sieve $\mathscr{U}_{[U]}$ of $M_{[U]}$ by intersecting with $M_{[U]}$ as a submanifold of $M$.
-Using $\mathscr{U}_{[U]}$, we define $\mathscr{U}_{i_{[U]}, [U]}$ to be the sieve of $\mathrm{Conf}_{i_{[U]}}(M_{[U]})_{\Sigma_{i_{[U]}}}$ as in \Cref{lem:weiss_to_ordinary}.
-These considerations give us equivalences
-    %
-    \begin{align}\label{eq:ord_to_W_equivs}
-        \mathsf{colim} (\mathscr{U} \xrightarrow{} \mfld[r](\bstr) \xrightarrow{\mathrm{Conf}_{i_{[U]}}(-_{[U]})_{\Sigma_{i_{[U]}}}} \mathsf{Sp}) &\simeq \mathsf{colim} (\mathscr{U}_{[U]} \xrightarrow{} \mfld[r](\bstr) \xrightarrow{\mathrm{Conf}_{i_{[U]}}(-)_{\Sigma_{i_{[U]}}}} \mathsf{Sp})\notag\\
-        &\simeq \mathsf{colim} (\mathscr{U}_{i_{[U]},[U]} \xrightarrow{} \mfld[r](\bstr) \xrightarrow{} \mathsf{Sp}).
-    \end{align}
-    %
-    The second equivalence in the above is simply a statement about the unions over the two covers and is a restatement of \Cref{lem:weiss_to_ordinary}.
-But, by \cite[Prop.A.3.2]{lurie_ha} the induced map is an equivalence
-    %
-    \begin{equation}\label{eq:gluing_top_lurie}
-        \mathsf{colim} (\mathscr{U}_{i_{[U]},[U]} \xrightarrow{} \mfld[r](\bstr) \xrightarrow{} \mathsf{Sp}) \xrightarrow{\ \ \simeq \ \ } \mathrm{Conf}_{i_{[U]}}(M_{[U]})_{\Sigma_{i_{[U]}}}.
-    \end{equation}
-\end{proof}
-
-\begin{lemma}\label{lem:gluing_disk/M/e}
-    A Weiss sieve $\mathscr{U} \subset \mfld[r]_{/M}$ canonically determines a morphism
-    %
-    \begin{equation}
-        \mathsf{colim} (\mathscr{U} \xrightarrow{} \mfld[r]_{/M} \xrightarrow{(\disk_{/M})_{/-}} \mathsf{RFib}_{\disk_{/M}}) \xrightarrow{\ \ \simeq \ \ } (\disk_{/M})_{/-}
-    \end{equation}
-    of right fibrations over $\disk_{/M}$, which moreover, is an equivalence.
-\end{lemma}
-
-\begin{proof}
-    .....
+    The morphism is determined by the universal property of the colimit. The components of the morphism of presheaves are given by
+    %
+    \begin{equation}
+        \mathsf{colim} \big( \mathscr{U} \xrightarrow{} \mfld[r]_{/M} \xrightarrow{\mathsf{Hom}_{\mfld_{/M}}(\iota, -)} \mathsf{Sp} \big) \xrightarrow{\ \ \ \ \ } \mathsf{Hom}_{\mfld_{/M}}(\iota, e),
+    \end{equation}
+    %
+    for each $\iota \in \disk_{/M}$, an open embedding of disks in $M$, and these morphisms are now maps of spaces which we want to show are equivalences.
+We now study the hom-spaces appearing above.
+By definition of the slice $\infty$-category, the hom-spaces are given as the homotopy fibers
+    %
+    \begin{equation}
+        \begin{tikzcd}
+            \mathsf{Hom}_{\mfld_{/M}} (\iota, e) \arrow[d] \arrow[r] & \mathsf{Hom}_{\mfld}(D, N) \arrow[d, "e^*"] \\
+            * \arrow[r, "\{\iota\}"] & \mathsf{Hom}_{\mfld}(D, M),
+        \end{tikzcd}
+    \end{equation}
+    %
+    where we have fixed the notation $\iota: D \xhookrightarrow{} M$ and $e: N \xhookrightarrow{} M$, for the domains of these maps.
+We further establish the notation that for each isomorphism class of basics $[B]$, the fixed $D$ has $i_[B]$-many disks of type $[B]$.
+With this notation in hand, by the characterization of the maximal $\infty$-subgroupoid of $\disk_{/M}$ \cite[Lem.2.21]{aft_fhstrat} for example, we know that
+    %
+    \begin{equation}
+        \mathsf{Hom}_{\mfld}(D, M) \simeq \coprod_{[B]} \mathrm{UConf}_{i_{[B]}}(M_{[B]}),
+    \end{equation}
+    %
+    where the notation $M_{[B]}$ denotes the $[B]$-stratum of $M$ (see \cite[Prop.4.4.7]{aft_localstrut}).
+We also note that under these equivalences the map $e^*$ is given by $\coprod_{[B]} \mathrm{UConf}_{i_{[B]}}(e_{[B]})$, which is even an open inclusion.
+Thus, the hom-spaces of the slice $\infty$-category are given as
+    %
+    \begin{equation}
+        \mathsf{Hom}_{\mfld_{/M}} (\iota, e) \simeq \coprod_{[B]} \mathsf{Fib}_\iota^{[B]}(e),
+    \end{equation}
+    %
+    where $\mathsf{Fib}_\iota^{[B]}(e)$ is defined as the homotopy fiber
+    %
+    \begin{equation}
+        \begin{tikzcd}
+            \mathsf{Fib}_\iota^{[B]}(e) \arrow[d] \arrow[r] & \mathrm{UConf}_{i_{[B]}}(N_{[B]}) \arrow[d, "\mathrm{UConf}_{i_{[B]}}(e_{[B]})"] \\
+            * \arrow[r, "\{\iota_{[B]}\}"] & \mathrm{UConf}_{i_{[B]}}(M_{[B]}),
+        \end{tikzcd}
+    \end{equation}
+    %
+    where, by slight abuse, we denoted the point over which the fiber lies with $\iota_{[B]}$ as well.
+With all of this notation in place, and by switching the places of the colimits, what we want to show is that the canonical maps
+    %
+    \begin{equation}
+        \mathsf{colim} \big( \mathscr{U} \xrightarrow{} \mfld[r]_{/M} \xrightarrow{\mathsf{Fib}_{\iota}^{[B]}(-)} \mathsf{Sp} \big) \xrightarrow{\ \ \ \ \ } \mathsf{Fib}_{\iota}^{[B]}(e),
+    \end{equation}
+    %
+    are equivalences for every $\iota$ and every $[B]$.
+Using \cite[Prop.A.3.2]{lurie_ha}, a sufficient condition for these maps to be equivalences is for the composition $\mathscr{U} \xrightarrow{} \mfld[r]_{/M} \xrightarrow{\mathsf{Fib}_{\iota}^{[B]}(-)} \mathsf{Sp}$ to be a covering sieve of $\mathsf{Fib}_{\iota}^{[B]}(e)$.
+To exhibit such a property we pick a particular model for the homotopy fiber $\mathsf{Fib}_{\iota}^{[B]}(e)$, namely
+    %
+    \begin{equation}
+        \widetilde{\mathsf{Fib}_{\iota}^{[B]}}(N) := \big( \mathsf{P}(\mathrm{UConf}_{i_{[B]}}(M_{[B]})) \times \mathrm{UConf}_{i_{[B]}}(N_{[B]}) \big) / (s (p) = \iota_{[B]}, t (p) = e(x)),
+    \end{equation}
+    %
+    the space of paths in $\mathrm{UConf}_{i_{[B]}}(M_{[B]})$ that start at $\iota_{[B]}$ and end at a point $x$ in $\mathrm{UConf}_{i_{[B]}}(N_{[B]})$.
+With this model, for each $(U \xhookrightarrow{} N) \in \mathscr{U} \subset (\mfld[r]_{/M})_{/e} \simeq \mfld[r]_{/N}$ (by \Cref{lem:double_slice}) we get an open inclusion
+    %
+    \begin{equation}
+        \widetilde{\mathsf{Fib}_{\iota}^{[B]}}(U) \xhookrightarrow{\ \ \ \ } \widetilde{\mathsf{Fib}_{\iota}^{[B]}}(N),
+    \end{equation}
+    %
+    and we're trying to show that the collection $\mathscr{V}_{\iota}^{[B]}$ of these is a cover.
+
+    Given a Weiss cover $\mathscr{U}$ on $N$ we can restrict it to a Weiss cover $\mathscr{U}_{[B]}$ of $N_{[B]}$ by intersecting.
+The statement of \Cref{lem:weiss_to_ordinary} is that we can build an ordinary cover $\mathscr{U}_{i_{[B]},[B]}$ of $\mathrm{UConf}_{i_{[B]}}(N_{[B]})$.
+$\mathscr{V}_{\iota}^{[B]}$ is a cover if for any $p \in \widetilde{\mathsf{Fib}_{\iota}^{[B]}}(N)$ we can find an open $\widetilde{\mathsf{Fib}_{\iota}^{[B]}}(U)$ that contains it.
+But this is indeed the case, because looking at the target $t(p)$ of the path $p$, we get $t(p) \in \mathrm{UConf}_{i_{[B]}}(N_{[B]})$, and we know that there exists a $U \in \mathscr{U}$ such that $\mathrm{UConf}_{i_{[B]}}(U_{[B]})$ covers $t(p)$ and subsequently also that $\widetilde{\mathsf{Fib}_{\iota}^{[B]}}(U)$ covers $p$.
+
+    ...
 \end{proof}
@@
     %
-    %Indeed, let $X \simeq y_{\mathscr{D}} (d)$ be a representable presheaf, then there is an equivalence of morphism spaces $\mathsf{Hom}_{\catC} (L_{y_{\mathscr{D}}} F (X), c) \simeq \mathsf{Hom}_{\mathsf{PShv}(\mathscr{D})} (X, T_F (c))$ given by
-    %
-    %\begin{align}
-    %    \mathsf{Hom}_{\catC} (L_{y_{\mathscr{D}}} F (X), c) &\simeq \mathsf{Hom}_{\catC} (F (d), c) \simeq \mathsf{Hom}_{\mathsf{PShv}(\catC)} (y_{\catC}(F(d)), y_{\catC}(c))\notag\\ &\simeq \mathsf{Hom}_{\mathsf{PShv}(\mathscr{D})} (F^*(y_{\catC}(F(d))), T_F(c)) \simeq \mathsf{Hom}_{\mathsf{PShv}(\mathscr{D})} (X, T_F(c)).
-    %\end{align}
-    %
-    %In general, the Yoneda embedding $y_{\mathscr{D}}$ is a dense functor
+    Indeed, let $X \simeq y_{\mathscr{D}} (d)$ be a representable presheaf, then there are maps of morphism spaces
+    %
+    \begin{align}
+        \mathsf{Hom}_{\catC} (L_{y_{\mathscr{D}}} F (X), c) &\xrightarrow[\simeq]{} \mathsf{Hom}_{\catC} (F (d), c) \xrightarrow[\simeq]{y_{\mathscr{C}}} \mathsf{Hom}_{\mathsf{PShv}(\catC)} (y_{\catC}(F(d)), y_{\catC}(c))\notag\\ &\xrightarrow{F^*} \mathsf{Hom}_{\mathsf{PShv}(\mathscr{D})} (F^*(y_{\catC}(F(d))), T_F(c)) \xrightarrow[\simeq]{} \mathsf{Hom}_{\mathsf{PShv}(\mathscr{D})} (X, T_F(c)).
+    \end{align}
+    %
+    The Yoneda embedding $y_{\mathscr{D}}$ is a dense functor, so the above argument holds
 
@@
     With the Weiss cosheaf property being a statement about preserving colimits, and with $\int F$ being a left Kan extension we are exactly in the situation of \Cref{lem:Lan_preserve_colim}.
-Thus, we only need to show that functor $T: \mfld_{/M} \xrightarrow{} \mathsf{PShv} (\disk_{/M})$\footnote{This functor is related to the tangent classifier, with the differences being that we're now in the relative case, and we're not fully limiting to $\bsc$ but instead only to disks.} preserves Weiss colimits, namely that there is an equivalence
-    %
-    \begin{equation}
-        \mathsf{colim} (\mathscr{U} \xrightarrow{} \mfld_{/M} \xrightarrow{T} \mathsf{PShv} (\disk_{/M})) \simeq T(N \xhookrightarrow{} M),
-    \end{equation}
-    %
-    where on the right-hand side we've used the fact that $\mathscr{U}$ is, in particular, a covering sieve.
-If we also append the straightening--unstraightening construction to $T$, we can write the desired equivalence as
+Thus, we only need to show that the functor $T: \mfld_{/M} \xrightarrow{} \mathsf{PShv} (\disk_{/M})$ preserves Weiss colimits.
+Namely, we need to show that there is an equivalence
+    %
+    \begin{equation}
+        \mathsf{colim} \big( \mathscr{U} \xrightarrow{} \mfld[r]_{/M} \xrightarrow{\mathsf{Hom}_{\mfld_{/M}}(\cdot, -)} \mathsf{PShv} (\disk_{/M}) \big) \xrightarrow{\ \ \simeq \ \ } \mathsf{Hom}_{\mfld_{/M}}(\cdot, e),
+    \end{equation}
+    %
+    where on the right-hand side we've used the fact that $\mathscr{U}$ is, in particular, a covering sieve.\footnote{If we also append the straightening--unstraightening construction to $T$, the desired equivalence can equivalently be written as
     %
@@
         \mathsf{colim} (\mathscr{U} \xrightarrow{} \mfld_{/M} \xrightarrow{ (\disk_{/M})_{/-}} \mathsf{RFib}_{\disk_{/M}}) \simeq (\disk_{/M})_{/e}.
-    \end{equation}
-    %
-    \Cref{lem:gluing_disk/M/e} guarantees the existence of this equivalence.
+    \end{equation}}
+    %
+    But this is exactly the result of \Cref{lem:gluing_disk/M/e}.
 \end{proof}
@@
 
-The above proof already shows how the ideas that went into defining factorization algebras are not that different from the ideas that went into defining factorization homology.
+The above proof also shows how the ideas that went into defining factorization algebras are not that different from the ideas that went into defining factorization homology.
 Namely, the ideas of Weiss cosheaves and algebras over disks are deeply connected.
@@
     \end{equation}
+    %
+    Indeed, the fact that (sifted) colimits commute with the monoidal product on $\catC$ means that, for example in the case of two objects
+    %
+    \begin{align}
+        \mathsf{colim}(K \xrightarrow{F} \catC) \otimes \mathsf{colim}(K' \xrightarrow{F'} \catC) &\simeq \mathsf{colim}(K \xrightarrow{F(-) \otimes \mathsf{colim}(K' \xrightarrow{F'} \catC)} \catC)\notag\\
+        &\simeq \mathsf{colim}(K \xrightarrow{\mathsf{colim}(K' \xrightarrow{F(-) \otimes F'(-)} \catC)} \catC)\notag\\
+        &\simeq \mathsf{colim}(K \times K' \xrightarrow{F \times F'} \catC \times \catC \xrightarrow{- \otimes -} \catC),
+    \end{align}
+    %
+    for any (sifted) indexing $\infty$-categories $K, K'$.
 
@@
     %
-    The existence of these is exactly the requirement that factorization homology in the usual sense is fully faithful, which is part of the statement of \cite[lem.2.17]{aft_fhstrat}
+    The existence of these is exactly the requirement that factorization homology in the usual sense is fully faithful, which is part of the statement of \cite[lem.2.17]{aft_fhstrat}.
 \end{proof}

### 2024-07-24 sections/3algebras.tex
.

@@
 %
-The reason for the phrasing in these results is that, technically speaking, equivalence of the $\infty$-categories of algebras does not imply equivalence of the underlying operads.
-However since we only defined (locally constant) factorization algebras at the level of algebras and not on the level of $\infty$-operads, we can take the operadic definition as the basic one, and interpret the results as connecting this to the classical definition.
+The reason for the phrasing in these results is that, technically speaking, equivalence of the $\infty$-categories of algebras does not imply equivalence of the underlying $\infty$-operads.
+However since we only defined (locally constant) factorization algebras at the level of algebras and not at the level of $\infty$-operads, we can take the operadic definition as the basic one, and interpret the results as connecting this to the classical definition.
 The theorems that we present in this section are immensely helpful in relating factorization algebras to results in the area of disk algebras, which will be obvious throughout the rest of this work.
@@
     where we have fixed the notation $\iota: D \xhookrightarrow{} M$ and $e: N \xhookrightarrow{} M$, for the domains of these maps.
-We further establish the notation that for each isomorphism class of basics $[B]$, the fixed $D$ has $i_[B]$-many disks of type $[B]$.
+We further establish the notation that for each isomorphism class of basics $[B]$, the fixed $D$ has $i_{[B]}$-many disks of type $[B]$.
 With this notation in hand, by the characterization of the maximal $\infty$-subgroupoid of $\disk_{/M}$ \cite[Lem.2.21]{aft_fhstrat} for example, we know that
@@
     %
-    But this is just the fact that the $\disk_{/M}$ $\infty$-operad gives rise to $\mathbb{E}_n$-algebras from \cref{prop:framed_ndisk=En}.
+    But this is just the fact that the $\disk_{\mathsf{D}_n^*}$ $\infty$-operad gives rise to $\mathbb{E}_n$-algebras from \cref{prop:framed_ndisk=En}.
 \end{proof}

### 2024-08-05 sections/3algebras.tex
Minor changes.

@@
 
-\begin{remark}
+\begin{remark}\label{rem:unpack_pfac_def}
     Let's unwind the above definition to understand the underlying data needed to define a prefactorization algebra.
@@
 But this is indeed the case, because looking at the target $t(p)$ of the path $p$, we get $t(p) \in \mathrm{UConf}_{i_{[B]}}(N_{[B]})$, and we know that there exists a $U \in \mathscr{U}$ such that $\mathrm{UConf}_{i_{[B]}}(U_{[B]})$ covers $t(p)$ and subsequently also that $\widetilde{\mathsf{Fib}_{\iota}^{[B]}}(U)$ covers $p$.
-
-    ...
 \end{proof}
@@
     %
-    one for each $(U \xhookrightarrow{} M) \in \mfld[r]_{/M}$, which are natural in $U$ and preserve the multiplicative structure (see \Cref{cd:fa_morphisms}).
+    one for each $(U \xhookrightarrow{} M) \in \mfld[r]_{/M}$, which are natural in $U$ and preserve the multiplicative structure (see \Cref{rem:unpack_pfac_def,cd:fa_morphisms}).
 Since $F$ is a locally constant factorization algebra the functor
@@
 
+In the opposite direction, we do not, in general, have a pullback functor.
+\cite{cg2016} provide a construction of a pullback in the case of open immersions, but we will only focus on the case of restrictions.
+Namely, given an open subset $U \subset X$ of a topological space $X$, and given a factorization algebra $F \in \falg_X$ we can clearly define a factorization algebra $F|_{U} \in \falg_U$ by restricting to those open subsets that are fully contained in $U$.
+Furthermore, this clearly holds not only for factorization algebras, but prefactorization algebras and locally constant factorization algebras too.
+As an interesting sidenote regarding stratifications, though, we note the following lemma.
+
 \begin{lemma}\label{lem:ff_functor_to_refinement}
@@
 
-In the opposite direction, we do not, in general, have a pullback functor.
-\cite{cg2016} provide a construction of a pullback in the case of open immersions, but we will only focus on the case of restrictions.
-Namely, given an open subset $U \subset X$ of a topological space $X$, and given a factorization algebra $F \in \falg_X$ we can clearly define a factorization algebra $F|_{U} \in \falg_U$ by restricting to those open subsets that are fully contained in $U$.
-Furthermore, this clearly holds not only for factorization algebras, but prefactorization algebras and locally constant factorization algebras too.
-
 In the special case of product spaces $X \times Y$, we now know that the projections $\pi_1: X \times Y \rightarrow X$ and $\pi_2: X \times Y \rightarrow Y$, give us pushforwards.
@@
 
-\begin{proposition}\label{prop:exp_of_products_lc}
+\begin{proposition}[Additivity]\label{prop:exp_of_products_lc}
     Let $M$ and $N$ be stratified manifolds. The functor $\bar{\pi}$ descends to locally constant factorization algebras, and moreover, it is an equivalence of $\infty$-categories
@@
     \begin{equation}
-        \disk_{/M} \otimes \disk_{/N} \xrightarrow{\ \ \simeq \ \ } \disk_{/M \times N},
-    \end{equation}
-    %
-    with the tensor product of $\infty$-opeards. Again for smooth manifolds this is found in \cite[ex.5.4.5.5]{lurie_ha}.
+        \disk_{/M} \otimes \disk_{/N} \xrightarrow{\ \ \ \ \ } \disk_{/M \times N},
+    \end{equation}
+    %
+    with $\otimes$ the tensor product of $\infty$-opeards. Again for smooth manifolds this is found in \cite[ex.5.4.5.5]{lurie_ha}.
 \end{remark}
@@
 
-    One way to show the equivalence is to use factorization homology, as in \Cref{thm:disk_alg=lcfa}, to write a locally constant factorization algebra as $\int_{-} A \in \lcfa_{X \times Y} (\catC)$.
-Then using the Fubini theorem \cite[cor.2.29]{aft_fhstrat}\footnote{The notation used in the citation is technically abusive because factorization homology is evaluating lower dimensional manifolds, but it is clear that this is to be understood exactly as the evaluation of the pushforward factorization algebra on the lower dimensional manifold (see \Cref{rem:fh_is_pushingforward}).} for factorization homology we get essential surjectivity because there are equivalences
-    %
-    \begin{equation}
-        \int_{U \times V} A \xrightarrow{\ \ \simeq \ \ } \int_U \int_V \bar{\pi} A
-    \end{equation}
-    %
-    between objects of $\catC$.
-As argued in the proof of \Cref{thm:disk_alg=lcfa}, these equivalences are natural in the open set variables, which means that they rise to equivalences at the level of locally constant factorization algebras.
-In fact, looking at the proof of \cite[thm.2.25]{aft_fhstrat}, which is what underlies the construction of the above equivalences, we see that they arise from an argument about a final functor.
-By \Cref{rem:fin_equiv_natural} this means that the equivalences are actually natural in the algebra variable, so it is immediate that the equivalences of individual locally constant factorization algebras lift to a full equivalence of $\infty$-categories.
-\end{proof}
+    One way to show the equivalence is to use factorization homology, as in \Cref{thm:disk_alg=lcfa}.
+In this language, first we have to provide, for each locally constant factorization algebra in two variables $\int_{-}(\int_{-} A) \in \lcfa_{X}(\lcfa_{Y}(\catC))$, a locally constant factorization algebra $\int_{-} \bar{A} \in \lcfa_{X \times Y} (\catC)$ and an equivalence
+    %
+    \begin{equation}
+        \bar{\pi} \int_{-} \bar{A} \xrightarrow[\simeq]{\ \ \phi \ \ } \int_{-} \big( \int_{-} A \big).
+    \end{equation}
+    %
+    This is an equivalence in $\lcfa_{X}(\lcfa_{Y}(\catC))$, which means that it is a family of equivalences $\phi(U,V)$ in $\catC$
+    %
+    \begin{equation}
+        \int_{U \times V} \bar{A} \xrightarrow[\simeq]{\ \ \phi (U,V)\ \ } \int_{U} \big( \int_{V} A \big),
+    \end{equation}
+    %
+    one for each open $U \subset X$, and each open $V \subset Y$.
+Furthermore, this family is natural in $U$ and $V$ separately, and it is also multiplicative in $U$ and $V$ separately (cf.
+\Cref{rem:unpack_pfac_def}).
+Such a family of equivalences is provided by the Fubini theorem \cite[cor.2.29]{aft_fhstrat}\footnote{The notation used in the citation is technically abusive because factorization homology is evaluating lower dimensional manifolds, but it is clear from the context that this is to be understood exactly as the evaluation of the pushforward factorization algebra on the lower dimensional manifold (see \Cref{rem:fh_is_pushingforward}).} for factorization homology, which pointwise gives us the equivalences $\phi(U,V)$.
+As argued in the proof of \Cref{thm:disk_alg=lcfa}, these equivalences are natural in the open set variables by the very functoriality of factorization homology, and they also preserve the multiplicative structure dues to the equivalences
+    %
+    \begin{equation}
+        \disk[r]_{\sqcup_{i} U_i} \xrightarrow{\ \ \simeq \ \ } \bigtimes_{i} \disk[r]_{U_i},
+    \end{equation}
+    %
+    together with the colimit preserving property of the monoidal product of $\catC$.
+This makes $\phi$ a fully-fledged equivalence of locally constant factorization algebras, which means that $\bar{pi}$ is essentially surjective.
+Moreover, looking at the proof of \cite[thm.2.25]{aft_fhstrat}, which is what underlies the construction of the above equivalences, we see that they arise from an argument about a final functor.
+By \Cref{rem:fin_equiv_natural} this means that the equivalences are actually natural (or rather functorial) in the algebra variable, so it is immediate that the equivalences of individual locally constant factorization algebras lift to a full equivalence of $\infty$-categories.
+\end{proof}
+
+\begin{example}
+    We can view a Euclidean space $\mathbb{R}^{m+n}$ as a product space $\mathbb{R}^m \times \mathbb{R}^n$, in which case \Cref{prop:exp_of_products_lc} specializes to give the famous result of Dunn additivity \cite{dunn1988} which can be found in the following form in \cite{lurie_ha}:
+
+    \begin{proposition}\label{prop:dunn_additivity}
+        There is an equivalence of $\infty$-categories
+        %
+        \begin{equation}
+            \alg{\mathbb{E}_{n + m}} (\catC) \xrightarrow{\ \ \simeq \ \ } \alg{\mathbb{E}_n} (\alg{\mathbb{E}_m} (\catC)).
+        \end{equation}
+    \end{proposition}
+\end{example}
+
+\begin{remark}
+    The proof of \Cref{prop:exp_of_products_lc}, when specialized to ordinary manifolds, as given in \cite{ginot2015} actually depends on Dunn additivity to work, however the proof presented above and the one in \cite{lurie_ha} are both independent of this special case.
+\end{remark}
 
@@
     %
-    But this is just the fact that the $\disk_{\mathsf{D}_n^*}$ $\infty$-operad gives rise to $\mathbb{E}_n$-algebras from \cref{prop:framed_ndisk=En}.
+    But this is just the fact that the $\disk_{\mathsf{D}_n^*}$ $\infty$-operad gives rise to $\mathbb{E}_n$-algebras from \Cref{prop:framed_ndisk=En}.
 \end{proof}
@@
 
-We can view a Euclidean space $\mathbb{R}^{m+n}$ as a product space $\mathbb{R}^m \times \mathbb{R}^n$, in which case \Cref{prop:exp_of_products_lc} specializes to give the famous result of Dunn additivity \cite{dunn1988} which can be found in the following form in \cite{lurie_ha}:
-
-\begin{proposition}\label{prop:dunn_additivity}
-    There is an equivalence of $\infty$-categories
-    %
-    \begin{equation}
-        \alg{\mathbb{E}_{n + m}} (\catC) \xrightarrow{\ \ \simeq \ \ } \alg{\mathbb{E}_n} (\alg{\mathbb{E}_m} (\catC)). 
-    \end{equation}
-\end{proposition}
-
-\begin{remark}
-    The proof of \Cref{prop:exp_of_products_lc}, when specialized to ordinary manifolds, as given in \cite{ginot2015} actually depends on Dunn additivity to work, however the proof presented above and the one in \cite{lurie_ha} are independent.
-\end{remark}
-
 \end{document}

### 2024-08-19 sections/0intro.tex
..

@@
-\documentclass[../text]{subfiles}
+\documentclass[../text.tex]{subfiles}
 
@@
 
-\textbf{\Cref{ch:gluing_disk_alg} Collar-gluings and Disk Algebras:} The fourth section presents a novel result about the behavior of certain types of factorization algebras under the operation of collar-gluing in the manifold variable.
+\textbf{\Cref{ch:gluing_disk_alg} Collar--gluings and Disk Algebras:} The fourth section presents a novel result about the behavior of certain types of factorization algebras under the operation of collar-gluing in the manifold variable.
 It essentially shows that we can reproduce factorization algebras on a stratified manifold if we know them on some particular pieces of it together with the data of how to glue them.
@@
 Similarly, we will not distinguish between (topological) multicategories and their $\infty$-operadic nerve.
+
 \end{document}

### 2024-08-19 sections/1stratified.tex
..

@@
 \begin{remark}
-    A $\bstr$-manifold is a stratified manifold $M$ together with a homotopy-lift $\phi$
+    A $\bstr$-manifold is a stratified manifold $M$ together with a homotopy--lift $\phi$
     %
@@
 \begin{definition}\label{def:collar-gluing}
-    A collar-gluing of a stratified manifold $M$ is a weakly constructible bundle $M \xrightarrow{f} [-1,1]$. We denote collar-gluings as
+    A collar-gluing of a stratified manifold $M$ is a weakly constructible bundle $M \xrightarrow{f} [-1,1]$. We denote collar--gluings as
     %
@@
 \begin{remark}
-    One should think of collar-gluings as analogous to the case of gluing two manifolds with boundary along their boundaries after choosing collars.
+    One should think of collar--gluings as analogous to the case of gluing two manifolds with boundary along their boundaries after choosing collars.
 This is exactly the special thing about them, the overlap region is collared, i.e., looks like a product with $\mathbb{R}$.
@@
 \begin{theorem}[\cite{aft_localstrut}]\label{thm:decom_strat_man}
-    $\mfld(\bstr)$ is generated by $\bstr$ through iteratively forming collar-gluings and taking sequential colimits.
+    $\mfld(\bstr)$ is generated by $\bstr$ through iteratively forming collar--gluings and taking sequential colimits.
 \end{theorem}
@@
     Explaining what exactly we mean by a framed stratified manifold is done in \cite[Example 5.2.12]{aft_localstrut}.
-According to that example, $\mathsf{D}_{d \subset n}^*$-manifolds are described by the data of a framed smooth $n$-manifold $M$, a properly embedded smooth $d$-submanifold $\Sigma$ together with a null-homotopy of the Gauss map $\Sigma \rightarrow \mathsf{Gr}_d(\mathbb{R}^n)$.
+According to that example, $\mathsf{D}_{d \subset n}^*$-manifolds are described by the data of a framed smooth $n$-manifold $M$, a properly embedded smooth $d$-submanifold $\Sigma$ together with a null--homotopy of the Gauss map $\Sigma \rightarrow \mathsf{Gr}_d(\mathbb{R}^n)$.
 In more detail, for a general embedded submanifold $\Sigma \xhookrightarrow{} M$ the Gauss map gives the tangent (or equivalently normal) subspace to $\Sigma$ at every point.
@@
 The framing of $M$ is a diffeomorphism of type $\mathsf{T}M\cong M\times\mathbb{R}^n$ over, reducing said map to the Gauss map.
-A null-homotopy of this map is a trivialization of the tangent as well as the normal bundles of $\Sigma$ in a way that is compatible with the trivialization of the restriction of $\mathsf{T}M$ to $\Sigma$.
+A null--homotopy of this map is a trivialization of the tangent as well as the normal bundles of $\Sigma$ in a way that is compatible with the trivialization of the restriction of $\mathsf{T}M$ to $\Sigma$.
 \end{remark}

### 2024-08-19 sections/2homology.tex
Todo is partially done.
..

@@
 The stronger requirement also doesn't exclude any of the core examples that we are interested in.
-In fact, in some situations, the full requirement of presentability makes examples tractable.
+In fact, in some situations, the full requirement of presentability makes examples more tractable.
 \end{remark}
@@
 The symmetric monoidal structure can be both direct sum $\oplus$ or tensor product $\otimes$.
-        \item Any cocomplete, Cartesian closed $\infty$-category together with categorical product. (for example $\mathsf{Spaces}$ or $\cat$).
+        \item Any cocomplete, Cartesian closed $\infty$-category together with categorical product. (for example $\mathsf{Sp}$ or $\cat$).
     \end{enumerate}
@@
 
-More generally, an \emph{$\infty$-operad} is a map $\catC\to\mathsf{Fin}_\ast$ that satisfies a generalisation of the properties of a symmetric monoidal $\infty$-category: see \cite[Definition 2.1.1.10]{lurie_ha}.
+More generally, an \emph{$\infty$-operad} is a map $\catC\to\mathsf{Fin}_\ast$ that satisfies a generalization of the properties of a symmetric monoidal $\infty$-category: see \cite[Definition 2.1.1.10]{lurie_ha}.
 For these, \eqref{W1183QD} still holds: see \cite[Remark 2.1.1.14]{lurie_ha}.
@@
 %or alternatively in appendix \Cref{app:En_algebras}.
-    Roughly speaking, $\mathbb{E}_1$-algebras are homotopy-associative algebras and with increasing $n$ we get increasing levels of homotopy commutativity, such that the colimit $\mathbb{E}_\infty$ parametrizes homotopy-commtuative algebras.
+    Roughly speaking, $\mathbb{E}_1$-algebras are homotopy--associative algebras and with increasing $n$ we get increasing levels of homotopy commutativity, such that the colimit $\mathbb{E}_\infty$ parametrizes homotopy--commutative algebras.
 Having said that, the first part of the proposition is just the classical statement that the little $n$-disks operad and the little $n$-cubes operad are weakly equivalent.
@@
     Now, \cite[§2.4.3]{lurie_ha} contains a construction which associates an $\infty$-operad $\mathscr{C}^{\amalg}$ to any $\infty$-category $\mathscr{C}$ such that $\mathsf{Mul}_{\mathscr{C}^{\amalg}}(x_1\oplus\cdots\oplus x_n; y)\simeq \prod_{\nu=1}^{n}\mathsf{Hom}_{\mathscr{C}}(x_\nu,y)$.
-If $\mathscr{C}$ is already an $\infty$-operad with a initial unit $0\in\mathscr{C}_{\lrangle{1}}$, then there is (\cite[Lemma 1.20]{aft_fhstrat}) a canonical map of $\infty$-operads $\mathscr{C}\to(\mathscr{C}_{\lrangle{1}})^\amalg$ generalising the idea above.
+If $\mathscr{C}$ is already an $\infty$-operad with a initial unit $0\in\mathscr{C}_{\lrangle{1}}$, then there is (\cite[Lemma 1.20]{aft_fhstrat}) a canonical map of $\infty$-operads $\mathscr{C}\to(\mathscr{C}_{\lrangle{1}})^\amalg$ generalizing the idea above.
 
@@
     \]
-    A representative is then the following ordinary iterated fibre product of $\infty$-operads:
+    A representative is then the following ordinary iterated fiber product of $\infty$-operads:
     \[
@@
     %
-    which is homotopy commutative as explained above, while in $\disk[r](\bstr)_{/M}$ a morphism is a diagram as above that commutes on the nose.\footnote{Regarding notation, \cite{lurie_ha} introduces both the $\infty$-operad $\disk(\bstr)_{/M}$ and $\disk[r](\bstr)_{/M}$, however there they are denoted by $\mathbb{E}_M^\otimes$ and $\mathrm{N}(\mathrm{Disk}(M))^\otimes$, respectively.}
-    Similarly for higher arity-morphisms.
+    which is homotopy commutative as explained above, while in $\disk[r](\bstr)_{/M}$ a morphism is a diagram as above that commutes on the nose\footnote{Regarding notation, \cite{lurie_ha} introduces both the $\infty$-operad $\disk(\bstr)_{/M}$ and $\disk[r](\bstr)_{/M}$, however there they are denoted by $\mathbb{E}_M^\otimes$ and $\mathrm{N}(\mathrm{Disk}(M))^\otimes$, respectively.}.
+Similarly for higher arity morphisms.
 \end{remark}
@@
     Let $\mathsf{Assoc^{RL}}$ denote the multicategory\footnote{A \emph{multicategory}, or \emph{(colored) operad}, is like an (ordinary) category except that morphisms (now called multi-morphisms) are allowed to have multiple objects in their domain while still having only a single object in their codomain.
-The operadic nerve of a topological or Kan-enriched multicategy is an $\infty$-operad: see \cite[Proposition 2.1.1.27]{lurie_ha}.} with three objects $R$, $A$ and $L$.
+The operadic nerve of a topological or Kan-enriched multicategory is an $\infty$-operad: see \cite[Proposition 2.1.1.27]{lurie_ha}.} with three objects $R$, $A$ and $L$.
 To describe the multi-morphisms let $I$ be an arbitrary finite list of the objects of $\mathsf{Assoc^{RL}}$.

### 2024-08-19 sections/3algebras.tex
..

@@
 
-\subsection{The \texorpdfstring{$\infty$-}{infinity }operad of Factorization Algebras}
+\subsection{The \texorpdfstring{$\infty$-}{infinity-}operad of Factorization Algebras}
 
@@
     for each $\iota \in \disk_{/M}$, an open embedding of disks in $M$, and these morphisms are now maps of spaces which we want to show are equivalences.
-We now study the hom-spaces appearing above.
-By definition of the slice $\infty$-category, the hom-spaces are given as the homotopy fibers
+We now study the hom--spaces appearing above.
+By definition of the slice $\infty$-category, the hom--spaces are given as the homotopy fibers
     %
@@
 We also note that under these equivalences the map $e^*$ is given by $\coprod_{[B]} \mathrm{UConf}_{i_{[B]}}(e_{[B]})$, which is even an open inclusion.
-Thus, the hom-spaces of the slice $\infty$-category are given as
+Thus, the hom--spaces of the slice $\infty$-category are given as
     %
@@
     \begin{equation}
-        \int_{U \times V} \bar{A} \xrightarrow[\simeq]{\ \ \phi (U,V)\ \ } \int_{U} \big( \int_{V} A \big),
-    \end{equation}
-    %
-    one for each open $U \subset X$, and each open $V \subset Y$.
-Furthermore, this family is natural in $U$ and $V$ separately, and it is also multiplicative in $U$ and $V$ separately (cf.
+        \int_{U \times V} \bar{A} \xrightarrow[\simeq]{\ \ \phi (U,V)\ \ } \int_{V} \big( \int_{U} A \big),
+    \end{equation}
+    %
+    one for each open $U \subset X$, and each open $V \subset Y$, such that the family is natural in $U$ and $V$ separately, and it is also multiplicative in $U$ and $V$ separately (cf.
 \Cref{rem:unpack_pfac_def}).
 Such a family of equivalences is provided by the Fubini theorem \cite[cor.2.29]{aft_fhstrat}\footnote{The notation used in the citation is technically abusive because factorization homology is evaluating lower dimensional manifolds, but it is clear from the context that this is to be understood exactly as the evaluation of the pushforward factorization algebra on the lower dimensional manifold (see \Cref{rem:fh_is_pushingforward}).} for factorization homology, which pointwise gives us the equivalences $\phi(U,V)$.
-As argued in the proof of \Cref{thm:disk_alg=lcfa}, these equivalences are natural in the open set variables by the very functoriality of factorization homology, and they also preserve the multiplicative structure dues to the equivalences
-    %
-    \begin{equation}
-        \disk[r]_{\sqcup_{i} U_i} \xrightarrow{\ \ \simeq \ \ } \bigtimes_{i} \disk[r]_{U_i},
-    \end{equation}
-    %
-    together with the colimit preserving property of the monoidal product of $\catC$.
-This makes $\phi$ a fully-fledged equivalence of locally constant factorization algebras, which means that $\bar{pi}$ is essentially surjective.
-Moreover, looking at the proof of \cite[thm.2.25]{aft_fhstrat}, which is what underlies the construction of the above equivalences, we see that they arise from an argument about a final functor.
+
+    ...
+
+    As argued in the proof of \Cref{thm:disk_alg=lcfa}, these equivalences are natural in the open set variables by the very functoriality of factorization homology, and they also preserve the multiplicative structure %due to the equivalences
+    %%
+    %\begin{equation}
+    %    \disk[r]_{\sqcup_{i} U_i} \xrightarrow{\ \ \simeq \ \ } \bigtimes_{i} \disk[r]_{/U_i},
+    %\end{equation}
+    %%
+    %together with the colimit preserving property of the monoidal product of $\catC$.
+This makes $\phi$ a fully-fledged equivalence of locally constant factorization algebras, which means that $\bar{\pi}$ is essentially surjective.
+
+    Finally, looking at the proof of \cite[thm.2.25]{aft_fhstrat}, which is what underlies the construction of the above equivalences, we see that they arise from an argument about a final functor.
 By \Cref{rem:fin_equiv_natural} this means that the equivalences are actually natural (or rather functorial) in the algebra variable, so it is immediate that the equivalences of individual locally constant factorization algebras lift to a full equivalence of $\infty$-categories.

### 2024-08-19 sections/4gluing_alt.tex
Minor changes.
..

@@
 
-\section{Collar-gluings and Factorization Algebras}\label{ch:gluing_disk_alg}
+\section{Collar--gluings and Factorization Algebras}\label{ch:gluing_disk_alg}
 
@@
 We also noticed, in \Cref{thm:disk_alg=lcfa}, that factorization homology is involved in constructing these algebras from local data.
-This prompts us to ask if we can say something about the behavior of this $\infty$-category under collar-gluings in the manifold variable.
+This prompts us to ask if we can say something about the behavior of this $\infty$-category under collar--gluings in the manifold variable.
 In this section we will prove that such a result exists in both the cases of locally constant and ordinary factorization algebras.
@@
     which on objects acts as $(N \xhookrightarrow{} M) \mapsto (N_- \xhookrightarrow{} M, N_0 \times \mathbb{R} \xhookrightarrow{} M, N_+ \xhookrightarrow{} M)$.
-Moreover, this functor is even a map of $\infty$-operads.
 \end{lemma}
@@
     \end{equation}
-    %
-    That the functor is a map of $\infty$-operads is clear from the fact that the key role on both sides is played by disjoint union. 
 \end{proof}
@@
     Generically though, these pieces will not be disks again, so we can't simply inherit the local constancy property immediately.
-To alleviate this issue we make use of \Cref{thm:decom_strat_man} which assures us that every manifold can be obtained by collar-gluings and sequential colimits if we start with disks.
-In fact, since our largest manifold of interest is a disk, which is finitary, we only need collar-gluings, and not sequential colimits.
+To alleviate this issue we make use of \Cref{thm:decom_strat_man} which assures us that every manifold can be obtained by collar--gluings and sequential colimits if we start with disks.
+In fact, since our largest manifold of interest is a disk, which is finitary, we only need collar--gluings, and not sequential colimits.
 Thus, we can work inductively and iterate the cutting and gluing process until the pieces become disks.
@@
     where the horizontal arrows are induced by the relevant embeddings.
-A sufficient condition to guarantee compatibility is that all collar-gluings are defined as collar-gluings of $M$ and then inherited to every open submanifold through its embedding in $M$.
-Focusing on the final two consecutive collar-gluings we get a commutative diagram, which we schematically denote
+A sufficient condition to guarantee compatibility is that all collar--gluings are defined as collar--gluings of $M$ and then inherited to every open submanifold through its embedding in $M$.
+Focusing on the final two consecutive collar--gluings we get a commutative diagram, which we schematically denote
     %
@@
 This is enough information to guarantee that after acting with the bar construction in one direction we again get compatible equivalences.
-The key point being that we consider the collar-gluings on all pieces in both orders to get all the necessary arrows.
+The key point being that we consider the collar--gluings on all pieces in both orders to get all the necessary arrows.
 
@@
         %
-        The final point to check is that we have not limited ourselves by insisting to only consider collar-gluings which are inherited from ones on $M$.
+        The final point to check is that we have not limited ourselves by insisting to only consider collar--gluings which are inherited from ones on $M$.
 This is best shown in \Cref{fig:extend_gluing}.
@@
 
-We know from \Cref{thm:decom_strat_man} that any manifold can be constructed from basics by iterated collar-gluings and sequential colimits.
-Having described what happens to a locally constant factorization algebras under collar-gluings of manifolds, we now turn to sequential colimits.
+We know from \Cref{thm:decom_strat_man} that any manifold can be constructed from basics by iterated collar--gluings and sequential colimits.
+Having described what happens to a locally constant factorization algebras under collar--gluings of manifolds, we now turn to sequential colimits.
 {\color{red} The gluing result has an ordinary (nonhomotopy) limit.

### 2024-08-30 sections/2homology.tex
.
Additivity write-up from meeting.

@@
 
+\begin{remark}\label{rem:details_disk/M}
     While $\disk(\bstr)$ is a symmetric monoidal $\infty$-category, $\disk(\bstr)_{/M}$ need not be, since two embeddings, if their images intersect, do not lift to an embedding from the disjoint union of their domains.
@@
     where $\mathsf{Isom}(\disk(\bstr)^{\amalg})\subset\mathsf{Ar}(\disk(\bstr)^{\amalg})=(\disk(\bstr)^{\amalg})^{\Delta[1]}$ is the full sub-$\infty$-category of the arrow $\infty$-category generated by those morphisms that are isomorphisms in the associated homotopy category, whence the isotopies mentioned in piece 3.
+\end{remark}
 
@@
 Observing the definition of $\mathsf{O^{RL}}$ clearly offers a bijection on morphism spaces since they are by definition order preserving maps, and the embeddings are oriented.
-It is trivial to check that these maps lie over $\mathsf{Fin}_*$ and that they send active morphisms to active morphisms completing the proof.
+It is trivial to check that these maps lie over $\mathsf{Fin}_*$, and that they send inert morphisms to inert morphisms, completing the proof.
 \end{proof}

### 2024-08-30 sections/3algebras.tex
Additivity write-up from meeting.

@@
 
-In the special case of product spaces $X \times Y$, we now know that the projections $\pi_1: X \times Y \rightarrow X$ and $\pi_2: X \times Y \rightarrow Y$, give us pushforwards.
+\subsection{Additivity of \texorpdfstring{$\lcfa$}{lcfa}s on Stratified Spaces}
+
+In the special case of product spaces $X \times Y$, from the previous discussion we now know that the projections $\pi_1: X \times Y \rightarrow X$ and $\pi_2: X \times Y \rightarrow Y$, give us pushforwards.
+This is true even in the locally constant case since the projections are (even trivial) fiber bundles, which is a concept that is a special case of constructible bundles.
 For $\pi_1$, for example, this essentially uses the fact that if we can evaluate all open sets of $X \times Y$ then we can definitely evaluate the open sets that look like $U \times Y$, with $U \subset X$ an open set.
-But in this case we can do even more, because we can even evaluate the more granular open subsets $U \times V$ with $U \subset X$ and $V \subset Y$ opens.
-More formally, we claim:
+But, in fact, we can do even more, because we can even evaluate the more granular open subsets $U \times V$ with $U \subset X$ and $V \subset Y$ opens.
+To capture this idea in formal terms we claim:
 %
@@
     Let $X$ and $Y$ be topological spaces.
-There is a functor from the $\infty$-category of prefactorization algebras on the product $X \times Y$ to the $\infty$-category of prefactorization algebras on $X$ valued in the category of prefactorization algebras on $Y$
+There is a functor from the $\infty$-category of prefactorization algebras on the product $X \times Y$ to the $\infty$-category of prefactorization algebras on $X$ valued in the $\infty$-category of prefactorization algebras on $Y$
     %
@@
 
-\begin{proposition}[Additivity]\label{prop:exp_of_products_lc}
-    Let $M$ and $N$ be stratified manifolds. The functor $\bar{\pi}$ descends to locally constant factorization algebras, and moreover, it is an equivalence of $\infty$-categories
-    %
-    \begin{equation}
-        \bar{\pi}: \lcfa_{M \times N}(\catC) \xrightarrow{\ \ \simeq \ \ } \lcfa_{M}(\lcfa_{N}(\catC)).
-    \end{equation}
-\end{proposition}
-
-\begin{remark}
-    The above proposition also appears as \cite[prop.18]{ginot2015}.
+\begin{theorem}[Additivity]\label{thm:exp_of_products_lc}
+    Let $M$ and $N$ be stratified manifolds. There is an equivalence of $\infty$-operads
+    %
+    \begin{equation}
+        \disk_{/M} \otimes \disk_{/N} \xrightarrow{\ \ \simeq \ \ } \disk_{/M \times N},
+    \end{equation}
+    %
+    between the tensor product of $\infty$-operads $\disk_{/M}$ and $\disk_{/N}$ and the $\infty$-operad $\disk_{/M \times N}$.
+In particular, there is an equivalence of $\infty$-categories of algebras
+    %
+    \begin{equation}
+        \bar{\pi}: \lcfa_{M \times N}(\catC) \xrightarrow{\ \ \simeq \ \ } \lcfa_{M}(\lcfa_{N}(\catC)),
+    \end{equation}
+    which can be seen to be induced by the functor $\bar{\pi}$.
+\end{theorem}
+
+\begin{remark}
+    A version of the above theorem also appears as \cite[prop.18]{ginot2015}.
 The equivalence proven there is for the case of smooth manifolds and relies on the local proof of \cite{lurie_ha} for $\mathbb{R}^n$.
-Using \Cref{thm:disk_alg=lcfa}, the statement is implied by the fact that there is an equivalence of $\infty$-operads
-    %
-    \begin{equation}
-        \disk_{/M} \otimes \disk_{/N} \xrightarrow{\ \ \ \ \ } \disk_{/M \times N},
-    \end{equation}
-    %
-    with $\otimes$ the tensor product of $\infty$-opeards. Again for smooth manifolds this is found in \cite[ex.5.4.5.5]{lurie_ha}.
-\end{remark}
+The statement at the level of $\infty$-operads is slightly stronger and, using \Cref{thm:disk_alg=lcfa}, it implies the statement for factorization algebras.
+This $\infty$-operadic statement, again for smooth manifolds, is found in \cite[ex.5.4.5.5]{lurie_ha}.
+\end{remark}
+
+\begin{proof}
+    Following \cite[\S.2.2.5]{lurie_ha} the tensor product of $\infty$-operads is defined through a universal property.
+Namely, we define a bifunctor of $\infty$-operads to be a map $f: \mathscr{O}_1 \times \mathscr{O}_2 \xrightarrow{} \mathscr{O}$ such that:
+    %
+    \begin{enumerate}
+        \item The diagram
+        %
+        \begin{equation}
+            \begin{tikzcd}
+                \mathscr{O}_1 \times \mathscr{O}_2 \arrow[r, "f"] \arrow[d] & \mathscr{O} \arrow[d] \\
+                \mathsf{Fin}_* \times \mathsf{Fin}_* \arrow[r, "\wedge"] & \mathsf{Fin}_*
+            \end{tikzcd}
+        \end{equation}
+        %
+        commutes, and
+        \item $f$ sends pairs of inert morphisms in $\mathscr{O}_1$ and $\mathscr{O}_2$ to inert morphisms in $\mathscr{O}$.
+    \end{enumerate}
+    %
+    We denote the full $\infty$-subcategory of $\mathsf{Fun}_{\mathsf{Fin}_*}(\mathscr{O}_1 \times \mathscr{O}_2, \mathscr{O})$ consisting of the bifunctors of $\infty$-operads by $\mathsf{BiFunc}(\mathscr{O}_1, \mathscr{O}_2; \mathscr{O})$.
+The universal property of the tensor product is then that it is the $\infty$-operad $\mathscr{O}_1 \otimes \mathscr{O}_2$ together with a bifunctor of $\infty$-operads $f: \mathscr{O}_1 \times \mathscr{O}_2 \xrightarrow{} \mathscr{O}_1 \otimes \mathscr{O}_2$ such that composition with $f$ determines an equivalence
+    %
+    \begin{equation}
+        \alg{\mathscr{O}_1 \otimes \mathscr{O}_2} (\mathscr{O}) \xrightarrow{\ \ \simeq \ \ } \mathsf{BiFunc}(\mathscr{O}_1, \mathscr{O}_1; \mathscr{O}),
+    \end{equation}
+    %
+    for every $\infty$-operad $\mathscr{O}$\footnote{More details about the construction, its existence, and the fact that it captures a nontrivial concept can be found in the provided reference.}.
+
+    For us this means that we can show the desired equivalence of $\infty$-operads if we provide a bifunctor of $\infty$-operads $\disk_{/M} \times \disk_{/N} \xrightarrow{} \disk_{/M \times N}$ that is an equivalence.
+Our candidate bifunctor for this purpose will be $\times$, the product of stratified spaces.
+We now explain what this means on a technical level.
+
+    By \Cref{rem:details_disk/M} the definition of $\disk_{/M}$ as an $\infty$-operad is given by the pullback
+    %
+    \begin{equation}
+        \begin{tikzcd}
+            \disk_{/M} \arrow[rd, phantom, "\ulcorner", very near start] \arrow[r] \arrow[d] & (\disk_{/M})^{\amalg} \arrow[d] \\
+            \disk(\bsc) \arrow[r] & \disk(\bsc)^{\amalg}
+        \end{tikzcd},
+    \end{equation}
+    %
+    where on the right-hand side $\disk_{/M}$ and $\disk(\bsc)$ are appearing in their role as $\infty$-categories through \cite[Con.2.4.3.1]{lurie_ha}, while on the left-hand side they're appearing in their role as $\infty$-operads.
+We note here that the construction of $\mathscr{O}^{\amalg}$ for any $\infty$-category $\mathscr{O}$ is given through a universal property from which it immediately follows that $\mathscr{O}_1^{\amalg} \times \mathscr{O}_2^{\amalg} \simeq (\mathscr{O}_1 \times \mathscr{O}_2)^{\amalg}$.
+Keeping this in mind together with the fact that products and pullbacks commute we can draw the following commutative diagram
+    %
+    \begin{equation}
+        \begin{tikzcd}[column sep = 25]
+            \disk_{/M} \times \disk_{/N} \arrow[rd, phantom, "\ulcorner", very near start] \arrow[r] \arrow[d] & (\disk_{/M})^{\amalg} \times (\disk_{/N})^{\amalg} \arrow[r, "\simeq"] \arrow[d] & (\disk_{/M} \times \disk_{/N})^{\amalg} \arrow[d] \\
+            \disk(\bsc) \times \disk(\bsc) \arrow[r] & \disk(\bsc)^{\amalg} \times \disk(\bsc)^{\amalg} \arrow[r, "\simeq"] & (\disk(\bsc) \times \disk(\bsc))^{\amalg}  
+        \end{tikzcd}.
+    \end{equation}
+    %
+    Since $\disk_{/M \times N}$ is also given by a pullback, to provide an equivalence of $\infty$-operads $\disk_{/M} \times \disk_{/N} \xrightarrow{} \disk_{/M \times N}$ it is then sufficient to provide a commutative diagram of equivalences of $\infty$-operads
+    %
+    \begin{equation}
+        \begin{tikzcd}
+            \disk(\bsc) \times \disk(\bsc) \arrow[r] \arrow[d, "\simeq"] & (\disk(\bsc) \times \disk(\bsc))^{\amalg} \arrow[d, "\simeq"] & (\disk_{/M} \times \disk_{/N})^{\amalg} \arrow[l] \arrow[d, "\simeq"] \\
+            \disk(\bsc) \arrow[r] & \disk(\bsc)^{\amalg} & (\disk_{/M \times N})^{\amalg} \arrow[l]
+        \end{tikzcd}
+    \end{equation}
+    %
+    Looking back at the construction \cite[Con.2.4.3.1]{lurie_ha} of $\mathscr{O}^{\coprod}$, since it is given by a universal property we see that an equivalence of $\infty$-categories $\mathscr{O}_1 \simeq \mathscr{O}_2$ implies an equivalence of $\infty$-operads $\mathscr{O}_1^{\amalg} \simeq \mathscr{O}_2^{\amalg}$ such that the left-hand square in the above diagram would come for free.
+With this the ingredients we need are:
+    %
+    \begin{enumerate}
+        \item an equivalence of $\infty$-operads
+        %
+        \begin{equation}
+            \disk(\bsc) \times \disk(\bsc) \xrightarrow[\ \ \simeq \ \ ]{\times} \disk(\bsc),
+        \end{equation}
+        %
+        \item an equivalence, now only, of $\infty$-categories
+        %
+        \begin{equation}
+            \disk_{/M} \times \disk_{/N} \xrightarrow[\ \ \simeq \ \ ]{\times} \disk_{/M \times N},
+        \end{equation}
+        %
+        \item such that there is a commutative diagram of $\infty$-categories
+        %
+        \begin{equation}
+            \begin{tikzcd}
+                \disk_{/M} \times \disk_{/N} \arrow[r, "\times", "\simeq"'] \arrow[d] & \disk_{/M \times N} \arrow[d] \\
+                \disk(\bsc) \times \disk(\bsc) \arrow[r, "\times", "\simeq"'] & \disk(\bsc)
+            \end{tikzcd},
+        \end{equation}
+        %
+        where we have forgotten the $\infty$-operad equivalence down to an $\infty$-category equivalence.
+    \end{enumerate}
+    %
+    In the above we have already used the notation $\times$ to express an idea about what the maps we will provide are.
+Though there is abuse of notation it is clear from context which map $\times$ we want.
+Since the vertical maps are the canonical forgetful functors it will be clear from the construction that (3) is satisfied.
+
+    To get the data of (2) (..... reduce to $\bsc$). So we need to provide an equivalence of $\infty$-categories
+    %
+    \begin{equation}\label{eq:b/M_x_b/N=b/MxN}
+        \bsc_{/M} \times \bsc_{/N} \xrightarrow[\ \ \simeq \ \ ]{\times} \bsc_{/M \times N}.
+    \end{equation}
+
+    To get (1), we remember that as an $\infty$-operad $\disk(\bsc)$ is, in fact, the free symmetric monoidal $\infty$-category generated by $\bsc$, thus it suffices to provide and equivalence of $\infty$-categories
+    %
+    \begin{equation}
+        \bsc \times \bsc \xrightarrow[\ \ \simeq \ \ ]{\times} \bsc.
+    \end{equation}
+    %
+    Remembering that $\bsc$ has a terminal object $*$ so that $\bsc_{/*} \simeq \bsc$, this equivalence is just a special case of \Cref{eq:b/M_x_b/N=b/MxN} in the case when $M = N = *$.
+
+    The $\infty$-category $\bsc_{/M}$ is also known, by definition, as $\mathsf{Entr(M)}$, the enter-path $\infty$-category of the stratified manifold $M$.
+By \cite[Lem.3.3.9]{afr_homhyp} this is equivalent to the opposite $\infty$-category of the exit-path $\infty$-category of $M$.
+By \cite[Obs.3.3.3]{afr_homhyp} the equivalence
+    %
+    \begin{equation}
+        \mathsf{Exit}(M) \times \mathsf{Exit}(N) \xrightarrow[\ \ \simeq \ \ ]{\times} \mathsf{Exit}(M \times N)
+    \end{equation}
+    %
+    is immediate.
+
+    To complete the proof we only have to check that $\times: \disk_{/M} \times \disk_{/N} \xrightarrow{} \disk_{M \times N}$ satisfies the conditions to qualify as a bifunctor of $\infty$-operads.
+\end{proof}
 

### 2024-08-30 sections/3algebras.tex
Additivity write-up small addition.

@@
     To complete the proof we only have to check that $\times: \disk_{/M} \times \disk_{/N} \xrightarrow{} \disk_{M \times N}$ satisfies the conditions to qualify as a bifunctor of $\infty$-operads.
-\end{proof}
-
-\begin{proof}
-    The proof of existence of the functor goes along the same lines as the proof of \Cref{prop:exp_of_products} because of \Cref{thm:disk_alg=lcfa}.
-The thing to take into account is that the projection maps are both, trivially, constructible bundles so by \Cref{cor:pushforward_for_lc}, pushing forward by them yields locally constant factorization algebras again.
-This combined with the fact that for any $\infty$-operads $\mathscr{O}$, $\mathscr{O}'$ and $\mathscr{C}$ we have an equivalence
-    %
-    \begin{equation}
-        \alg{\mathscr{O}} (\alg{\mathscr{O}'} (\catC)) \simeq \alg{\mathscr{O}'} (\alg{\mathscr{O}} (\catC))
-    \end{equation}
-    %
-    allows us to conclude that the functor lands in locally constant factorization algebras
-    %
-    \begin{equation}
-        \bar{\pi}: \lcfa_{X \times Y}(\catC) \xrightarrow{\ \ \ \ } \lcfa_{X}(\lcfa_{Y}(\catC)).
-    \end{equation}
-
-    One way to show the equivalence is to use factorization homology, as in \Cref{thm:disk_alg=lcfa}.
-In this language, first we have to provide, for each locally constant factorization algebra in two variables $\int_{-}(\int_{-} A) \in \lcfa_{X}(\lcfa_{Y}(\catC))$, a locally constant factorization algebra $\int_{-} \bar{A} \in \lcfa_{X \times Y} (\catC)$ and an equivalence
-    %
-    \begin{equation}
-        \bar{\pi} \int_{-} \bar{A} \xrightarrow[\simeq]{\ \ \phi \ \ } \int_{-} \big( \int_{-} A \big).
-    \end{equation}
-    %
-    This is an equivalence in $\lcfa_{X}(\lcfa_{Y}(\catC))$, which means that it is a family of equivalences $\phi(U,V)$ in $\catC$
-    %
-    \begin{equation}
-        \int_{U \times V} \bar{A} \xrightarrow[\simeq]{\ \ \phi (U,V)\ \ } \int_{V} \big( \int_{U} A \big),
-    \end{equation}
-    %
-    one for each open $U \subset X$, and each open $V \subset Y$, such that the family is natural in $U$ and $V$ separately, and it is also multiplicative in $U$ and $V$ separately (cf.
-\Cref{rem:unpack_pfac_def}).
-Such a family of equivalences is provided by the Fubini theorem \cite[cor.2.29]{aft_fhstrat}\footnote{The notation used in the citation is technically abusive because factorization homology is evaluating lower dimensional manifolds, but it is clear from the context that this is to be understood exactly as the evaluation of the pushforward factorization algebra on the lower dimensional manifold (see \Cref{rem:fh_is_pushingforward}).} for factorization homology, which pointwise gives us the equivalences $\phi(U,V)$.
-
-    ...
-
-    As argued in the proof of \Cref{thm:disk_alg=lcfa}, these equivalences are natural in the open set variables by the very functoriality of factorization homology, and they also preserve the multiplicative structure %due to the equivalences
-    %%
-    %\begin{equation}
-    %    \disk[r]_{\sqcup_{i} U_i} \xrightarrow{\ \ \simeq \ \ } \bigtimes_{i} \disk[r]_{/U_i},
-    %\end{equation}
-    %%
-    %together with the colimit preserving property of the monoidal product of $\catC$.
-This makes $\phi$ a fully-fledged equivalence of locally constant factorization algebras, which means that $\bar{\pi}$ is essentially surjective.
-
-    Finally, looking at the proof of \cite[thm.2.25]{aft_fhstrat}, which is what underlies the construction of the above equivalences, we see that they arise from an argument about a final functor.
-By \Cref{rem:fin_equiv_natural} this means that the equivalences are actually natural (or rather functorial) in the algebra variable, so it is immediate that the equivalences of individual locally constant factorization algebras lift to a full equivalence of $\infty$-categories.
-\end{proof}
+
+    ....
+
+    The equivalence of $\infty$-operads $\disk_{/M} \otimes \disk_{/N} \xrightarrow{\ \ \simeq \ \ } \disk_{/M \times N}$ implies and equivalence at the level of $\alg{\disk_{/M}}$, which together with \Cref{thm:disk_alg=lcfa} this the equivalence of factorization algebras of the statement.
+That this is related to the functor $\bar{\pi}$ can be seen by inspection of the objects and morphisms.
+\end{proof}
+
+\begin{remark}
+    At the pointwise level of evaluating specific opens this statement is related to the Fubini theorem for factorization homology \cite[cor.2.29]{aft_fhstrat}.
+The notation used in the citation is technically abusive because factorization homology is evaluating lower dimensional manifolds, but it is clear from the context that this is to be understood exactly as the evaluation of the pushforward factorization algebra on the lower dimensional manifold (see \Cref{rem:fh_is_pushingforward}).
+\end{remark}
 
 \begin{example}
-    We can view a Euclidean space $\mathbb{R}^{m+n}$ as a product space $\mathbb{R}^m \times \mathbb{R}^n$, in which case \Cref{prop:exp_of_products_lc} specializes to give the famous result of Dunn additivity \cite{dunn1988} which can be found in the following form in \cite{lurie_ha}:
-
+    We can view a Euclidean space $\mathbb{R}^{m+n}$ as a product space $\mathbb{R}^m \times \mathbb{R}^n$, in which case \Cref{thm:additivity_lc} specializes to give the famous result of Dunn additivity \cite{dunn1988} which can be found in the following form in \cite{lurie_ha}:
+    %
     \begin{proposition}\label{prop:dunn_additivity}
@@
 \begin{remark}
-    The proof of \Cref{prop:exp_of_products_lc}, when specialized to ordinary manifolds, as given in \cite{ginot2015} actually depends on Dunn additivity to work, however the proof presented above and the one in \cite{lurie_ha} are both independent of this special case.
+    The proof of \Cref{thm:additivity_lc}, when specialized to ordinary manifolds, as given in \cite{ginot2015} actually depends on Dunn additivity to work, however the proof presented above and the one in \cite{lurie_ha} are both independent of this special case.
 \end{remark}
@@
 That is, we know that given a locally constant factorization algebra $F$ on $\mathbb{R}^n$ we can restrict it to any open subset like, for example, $\mathbb{R}^n \setminus \{ 0 \} \cong S^{n-1} \times \mathbb{R}$ to get another locally constant factorization algebra $F|_{S^{n-1} \times \mathbb{R}}$.
-By \Cref{prop:exp_of_products_lc} we know that $F|_{S^{n-1} \times \mathbb{R}} \in \lcfa_{\mathbb{R}} (\lcfa_{S^{n-1}} (\catC))$, so that in particular it is an $\mathbb{E}_1$-algebra.
+By \Cref{thm:additivity_lc} we know that $F|_{S^{n-1} \times \mathbb{R}} \in \lcfa_{\mathbb{R}} (\lcfa_{S^{n-1}} (\catC))$, so that in particular it is an $\mathbb{E}_1$-algebra.
 If we pushforward to $\mathbb{R}$, by the discussion at \Cref{rem:fh_is_pushingforward} we could denote the resulting $\mathbb{E}_1$-algebra by

### 2024-09-05 sections/3algebras.tex
minor.

@@
 
-\begin{theorem}[Additivity]\label{thm:exp_of_products_lc}
+\begin{theorem}[Additivity]\label{thm:additivity_lc}
     Let $M$ and $N$ be stratified manifolds. There is an equivalence of $\infty$-operads
@@
     \begin{equation}
-        \alg{\mathscr{O}_1 \otimes \mathscr{O}_2} (\mathscr{O}) \xrightarrow{\ \ \simeq \ \ } \mathsf{BiFunc}(\mathscr{O}_1, \mathscr{O}_1; \mathscr{O}),
+        \alg{\mathscr{O}_1 \otimes \mathscr{O}_2} (\mathscr{O}) \xrightarrow{\ \ \simeq \ \ } \mathsf{BiFunc}(\mathscr{O}_1, \mathscr{O}_2; \mathscr{O}),
     \end{equation}
@@
     \begin{equation}\label{eq:b/M_x_b/N=b/MxN}
-        \bsc_{/M} \times \bsc_{/N} \xrightarrow[\ \ \simeq \ \ ]{\times} \bsc_{/M \times N}.
-    \end{equation}
-
-    To get (1), we remember that as an $\infty$-operad $\disk(\bsc)$ is, in fact, the free symmetric monoidal $\infty$-category generated by $\bsc$, thus it suffices to provide and equivalence of $\infty$-categories
+        \bsc_{/M} \times \bsc_{/N} \xrightarrow{\times} \bsc_{/M \times N}.
+    \end{equation}
+
+    To get (1), we remember that as an $\infty$-operad $\disk(\bsc)$ is, in fact, the free symmetric monoidal $\infty$-category generated by $\bsc$, thus it suffices to provide an equivalence of $\infty$-categories
     %
@@
 
-    The equivalence of $\infty$-operads $\disk_{/M} \otimes \disk_{/N} \xrightarrow{\ \ \simeq \ \ } \disk_{/M \times N}$ implies and equivalence at the level of $\alg{\disk_{/M}}$, which together with \Cref{thm:disk_alg=lcfa} this the equivalence of factorization algebras of the statement.
+    The equivalence of $\infty$-operads $\disk_{/M} \otimes \disk_{/N} \xrightarrow{\ \ \simeq \ \ } \disk_{/M \times N}$ implies an equivalence at the level of $\alg{\disk_{/M}}$, which together with \Cref{thm:disk_alg=lcfa} gives rise to the equivalence of factorization algebras in the theorem statement.
 That this is related to the functor $\bar{\pi}$ can be seen by inspection of the objects and morphisms.

### 2024-09-05 sections/3algebras.tex
Lemma 3.22 partial (Lan extensions)

@@
 \begin{proof}
-    First consider the special case when $(\iota: \mathscr{D} \xrightarrow{} \mathscr{M}) = (y_{\mathscr{D}}: \mathscr{D} \xrightarrow{} \mathsf{PShv}(\mathscr{D}))$ the Yoneda embedding of $\mathscr{D}$.
-We will see that in this case, $L_{y_{\mathscr{D}}} F$ is colimit preserving because it is a left adjoint to the functor
-    %
-    \begin{equation}
-        T_F: \catC \xrightarrow{y_{\catC}} \mathsf{PShv} (\catC) \xrightarrow{F^*} \mathsf{PShv} (\mathscr{D}).
-    \end{equation}
-    %
-    Indeed, let $X \simeq y_{\mathscr{D}} (d)$ be a representable presheaf, then there are maps of morphism spaces
-    %
-    \begin{align}
-        \mathsf{Hom}_{\catC} (L_{y_{\mathscr{D}}} F (X), c) &\xrightarrow[\simeq]{} \mathsf{Hom}_{\catC} (F (d), c) \xrightarrow[\simeq]{y_{\mathscr{C}}} \mathsf{Hom}_{\mathsf{PShv}(\catC)} (y_{\catC}(F(d)), y_{\catC}(c))\notag\\ &\xrightarrow{F^*} \mathsf{Hom}_{\mathsf{PShv}(\mathscr{D})} (F^*(y_{\catC}(F(d))), T_F(c)) \xrightarrow[\simeq]{} \mathsf{Hom}_{\mathsf{PShv}(\mathscr{D})} (X, T_F(c)).
-    \end{align}
-    %
-    The Yoneda embedding $y_{\mathscr{D}}$ is a dense functor, so the above argument holds
-
-    {\color{red} Proof of being adjoint}
-
-    In the general situation where $\iota$ is not necessarily the Yoneda embedding we can partially reduce to the previous case because we can write
-    %
-    \begin{equation}
-        L_{\iota} F \simeq L_{y_{\mathscr{D}}}F \circ L_{\iota} y_{\mathscr{D}}.
-    \end{equation}
-    %
-    Namely, this is because we know that $L_{y_{\mathscr{D}}} F$ preserves colimits, and by the assumptions in the lemma, $L_{\iota} F$ and $L_{\iota} y_{\mathscr{D}}$ are computed pointwise, as colimits over the same indexing $\infty$-category.
-
-    Finally, we claim that there is an equivalence of functors
-    %
-    \begin{equation}
-        \Big( L_{\iota} y_{\mathscr{D}} \simeq T_{\iota} \Big) \in \mathsf{Fun}(\mathscr{M}, \mathsf{PShv}(\mathscr{D})) 
-    \end{equation}
-
-    {\color{red} Proof of functor equivalence}
-
+    We use the standard notation $y_{\mscr{X}}=h_\bullet\colon\mscr{X}\to\msf{PShv}(\mscr{X})$ for `the' covariant Yoneda embedding of a locally small $\infty$-category $\mscr{X}$ [see Kerodon Definition II.8.3.3.9/03NF; Proposition II.8.3.3.2/03N2].
+First, note that a left Kan extension of type
+    \[
+        L_{y_{\mscr{D}}}F\colon\msf{PShv}(\mscr{D})\to\mscr{C}
+    \]
+    preserves colimits as a consequence of [Kerodon Theorem II.8.4.3.6/03WH]. 
+    Next, we claim that there is an equivalence of functors
+    \begin{equation}\label{WZUZC5F}
+        L_{\iota}(F)\simeq L_{y_{\mscr{D}}}(F)\circ L_{\iota}(y_{\mscr{D}}).
+    \end{equation}
+    as functors $\mscr{M}\to\mscr{C}$. Indeed, consider the diagram 
+    \[
+        \begin{tikzcd}[sep=large]
+             & \mscr{D}\ar[dl,"{\iota}"']\ar[dr,"{F}"]\ar[d,"{y_{\mscr{D}}}"]\\
+            \mscr{M}\ar[rr,bend right=40,"{L_{\iota}(F)}"']\ar[r,"{L_{\iota}(y_{\mscr{D}})}"'] &[4em] \msf{PShv}(\mscr{D})\ar[r,"{L_{y_{\mscr{D}}}(F)}"'] & \mscr{C}
+        \end{tikzcd}
+    \]
+    and note that by [Kerodon Theorem II.8.4.0.3/03W9 and Theorem II.8.4.3.6/03WH] there is an isomorphism $L_{y_{\mscr{D}}}(F)\circ y_{\mscr{D}}\cong F$ which commutes the right triangle.
+Consequently, using [Kerodon Remark 7.3.1.10/02YH], we have $L_{\iota}(F)\simeq L_{\iota}(L_{y_{\mscr{D}}}(F)\circ y_{\mscr{D}})$.
+Since $L_{y_{\mscr{D}}}(F)$ preserves colimits, we have $L_{\iota}(L_{y_{\mscr{D}}}(F)\circ y_{\mscr{D}})\simeq L_{y_{\mscr{D}}}(F)\circ L_{\iota}(y_{\mscr{D}})$, obtaining \eqref{WZUZC5F}.
+
+    Finally, we claim
+    \begin{equation}\label{D9NQYMT}
+        L_{\iota}(y_{\mscr{D}})\simeq T_{\iota}=\iota^*\circ y_{\mscr{M}}
+    \end{equation}
+    as functors $\mscr{M}\to\msf{PShv}(\mscr{D})$, which will imply the Lemma by \eqref{WZUZC5F}.
+To prove \eqref{D9NQYMT}, let us observe that $L_{\iota}(y_{\mscr{D}})\simeq L_{y_{\mscr{M}}}(L_{\iota}(y_{\mscr{D}}))\circ y_{\mscr{M}}$ similarly to the above, and that $L_{y_{\mscr{M}}}(L_{\iota}(y_{\mscr{D}}))\simeq L_{y_{\mscr{M}}\circ\iota}(y_{\mscr{D}})$ by [Kerodon Proposition II.7.3.8.18/031M].
+Thus, it suffices to show that $\iota^*\simeq L_{y_{\mscr{M}}\circ\iota}(y_{\mscr{D}})$.
 \end{proof}

### 2024-09-05 main_theorem.tex
Finished writting up lem:Lan_preserve_colim and prepared main_theorem.tex that encapsulates the main definitions and results.

--- 2024-09-05 sections/3algebras.tex
@@
-\documentclass[../text.tex]{subfiles}
+% Run only with XeLaTeX!
+%---------------------------------------------------------------------
+%	FORMATING AND TYPESETTING
+%---------------------------------------------------------------------
+
+% Set document class
+\documentclass[12pt,a4paper]{article}
+
+% Option to change margin size
+\usepackage[margin=2cm]{geometry}
+
+% Font and encoding settings
+\usepackage[T1]{fontenc}
+%\usepackage[utf8]{inputenc} not necessary with xelatex?
+\usepackage{yfonts} % germanic fonts (fraktur...)
+%\defaultfontfeatures{Ligatures=TeX} %??
+
+% Footnotes
+\usepackage[stable]{footmisc}
+
+% Indentation and spacing
+\usepackage{indentfirst} % indentation
+\usepackage{enumitem}[leftmargin=0pt] % spacing
+\setlist{nosep}
+
+% Multi column environment
+\usepackage{multicol}
+
+% Formating of titles
+\usepackage{titlesec}
+\titleformat{\section}
+{\normalfont\large\bfseries}{\thesection}{1em}{}
+\titleformat{\subsection}
+{\normalfont\normalsize\bfseries}{\thesubsection}{1em}{}
+\titleformat{\subsubsection}
+{\normalfont\small\bfseries}{\thesubsubsection}{1em}{}
+\titleformat{\paragraph}[runin]
+{\normalfont\small\bfseries}{\theparagraph}{1em}{}
+\titleformat{\subparagraph}[runin]
+{\normalfont\small\bfseries}{\thesubparagraph}{1em}{}
+\usepackage[titletoc]{appendix}
+
+% Math typesetting packages
+\usepackage{amsmath, amssymb, amsthm, mathtools, commath}
+\usepackage[warnings-off={mathtools-colon,mathtools-overbracket}]{unicode-math} % makes \mathbb{1} work and changes font of mathbb
+\usepackage[mathscr]{euscript} % euler script font
+\usepackage{tikz-cd} % tikz commutative diagrams
+\usepackage{thmtools, thm-restate} % theorem tools, especially restatable
+
+\AtBeginDocument{\renewcommand\setminus{\smallsetminus}} % \setminus doesn't work in unicode-math
+
+%---------------------------------------------------------------------
+
+%---------------------------------------------------------------------
+%	GRAPHICS
+%---------------------------------------------------------------------
+
+\usepackage{float}
+\usepackage{caption}
+\usepackage{graphicx}
+\graphicspath{{images/}}
+
+\usepackage{pdfpages} % for inserting pdf pages
+
+%---------------------------------------------------------------------
+
+%---------------------------------------------------------------------
+%	BIBLIOGRAPHY
+%---------------------------------------------------------------------
+
+\usepackage[backend=biber,style=alphabetic]{biblatex}
+\renewcommand*{\bibfont}{\small}
+\addbibresource{text.bib}
+
+%---------------------------------------------------------------------
+
+%---------------------------------------------------------------------
+%	HYPERLINKS
+%---------------------------------------------------------------------
+
+% Define the colors
+\usepackage{xcolor}
+\definecolor{brown}{HTML}{CD853F}
+\definecolor{blue}{HTML}{4169E1}
+\definecolor{green}{HTML}{2E8B57}
+
+% Setup options for hyperlinks
+\usepackage{hyperref}
+\hypersetup{
+colorlinks=true, linkcolor=black, breaklinks=true,
+linktoc=all, bookmarksnumbered=true,
+urlcolor=brown, linkcolor=blue, citecolor=green, % Link colors
+}
+
+% Referencing package
+\usepackage{cleveref}
+\crefname{section}{\S\!}{\S\S\!}
+\Crefname{section}{\S\!}{\S\S\!}
+
+%---------------------------------------------------------------------
+%	THEOREM STYLES
+%---------------------------------------------------------------------
+
+% Define a dummy counter to keep count for all sub-environments
+\newcounter{counter} \numberwithin{counter}{section}
+
+% Define theorem styles here based on the definition style
+\theoremstyle{definition}
+\newtheorem{definition}[counter]{Definition}
+\newtheorem{construction}[counter]{Construction}
+\newtheorem{observation}[counter]{Observation}
+
+% Define theorem styles here based on the plain style
+\theoremstyle{plain} 
+\newtheorem{theorem}[counter]{Theorem}
+\newtheorem*{theorem*}{Theorem}
+\newtheorem{corollary}[counter]{Corollary}
+\newtheorem{lemma}[counter]{Lemma}
+\newtheorem{proposition}[counter]{Proposition}
+\newtheorem*{proposition*}{Proposition}
+\newtheorem{conjecture}[counter]{Conjecture}
+
+% Define theorem styles here based on the remark style
+\theoremstyle{remark}
+\newtheorem{example}[counter]{Example}
+\newtheorem{remark}[counter]{Remark}
+
+%---------------------------------------------------------------------
+
+%---------------------------------------------------------------------
+%	NEW COMMANDS
+%---------------------------------------------------------------------
+
+% general target category
+\newcommand{\catC}{\mathscr{C}}
+
+% categories of factorization algebras
+\newcommand{\falg}{\mathscr{F} \mathsf{Alg}}
+\newcommand{\lcfa}{\mathscr{F} \mathsf{Alg}^{\mathsf{lc}}}
+
+% category of manifolds
+\newcommand{\mfld}[1][s]{%
+    \ifx r#1\mathsf{Mfld}\else
+    \ifx s#1\mathscr{M} \mathsf{fld}\else
+    \mathrm{Illegal~option}%
+    \fi\fi
+}
+
+% category of disks
+\newcommand{\disk}[1][s]{%
+    \ifx r#1\mathsf{Disk}\else
+    \ifx s#1\mathscr{D} \mathsf{isk}\else
+    \mathrm{Illegal~option}%
+    \fi\fi
+}
+
+% category of opens
+\newcommand{\opens}[1][s]{%
+    \ifx r#1\mathsf{Opns}\else
+    \ifx s#1\mathscr{O} \mathsf{pns}\else
+    \mathrm{Illegal~option}%
+    \fi\fi
+}
+
+% category of cosheaves
+\newcommand{\csheaves}[1][n]{%
+    \ifx n#1 \mathsf{c} \mathscr{S} \mathsf{hv}\else
+    \mathsf{c} \mathscr{S} \mathsf{hv}^{\mathsf{#1}}
+    \fi
+}
+
+% category of infinity categories
+\newcommand{\cat}{\mathscr{C} \mathsf{at}_{\infty}}
+
+% template for category of algebras
+\newcommand{\alg}[1]{\mathscr{A} \mathsf{lg}_{#1}}
+
+% template for category of locally constant algebras
+\newcommand{\lcalg}[1]{\mathscr{A} \mathsf{lg}^{\mathsf{lc}}_{#1}}
+
+% half-open interval
+\newcommand{\hoint}{\mathbb{R}_{\geq 0}}
+
+% Cech complex
+\newcommand{\cech}{\check{\mathsf{C}}}
+
+% Category of basics
+\newcommand{\bsc}{\mathscr{B} \mathsf{sc}}
+\newcommand{\bstr}{\mathscr{B}}
+
+% Open cone
+\newcommand{\cone}[1][n]{%
+    \ifx b#1\overline{\mathsf{C}}\else
+    \ifx n#1\mathsf{C}\else
+    \mathrm{Illegal~option}%
+    \fi\fi
+}
+
+\newcommand{\lrangle}[1]{\langle #1 \rangle}
+
+%---------------------------------------------------------------------
+
+\usepackage{subfiles}
+
+%\setcounter{section}{-1}
 
 \begin{document}
+
+% Set title, author and date
+\title{Factorization Algebras and Factorization Homology on Stratified Spaces}
+\author{Aleksandar Ivanov, Ödül Tetik}
+\date{}
+\maketitle
 
@@
 \subsection{Definition of Factorization Algebras}
-
-Factorization algebras are a rigorous way to capture the idea of assigning an object to each piece of a space, together with a local-to-global principle that allows one to find out about larger pieces from smaller ones.
-The first ideas around factorization algebras were introduced by \cite{bd2004} in the context of vertex algebras in CFTs.
-These were geometric in nature.
-The topological version that we present was then introduced by Lurie and subsequently further developed in \cite{cg2016}, especially for the purposes of mathematical physics.
-Here we will present these ideas following \cite{cg2016} and also \cite{af_primer}.
-A similar exposition can be found in \cite{ginot2015}.
-
-\begin{remark}
-    We note that we have fixed a symmetric monoidal $\infty$-category $\catC$ that is $\otimes$-presentable to serve as the $\infty$-category that our algebras will be valued in.
-\end{remark}
+    We fix a symmetric monoidal $\infty$-category $\catC$ that is $\otimes$-presentable to serve as the target $\infty$-category.
 
@@
 \end{definition}
-
-\begin{remark}
-    It is obvious that in the case of (stratified) manifolds we have already seen alternative notation for the $\infty$-operad $\opens(X)$ before, namely $\mfld[r]_{/M}$.
-This makes a connection to the standard notation used around factorization homology, and is something that we'll make use of later.
-\end{remark}
 
@@
     \end{equation}
-
 \end{remark}
-
-\begin{remark}\label{rem:op_to_op}
-    There is an obvious inclusion functor from the poset $\opens[r](X)$ of open subsets of $X$, ordered by inclusion, to the multicategory $\opens[s](X)$, namely, the one which hits only those multi-morphisms $\{U_i\}_{i \in I} \rightarrow U$, where the cardinality of the finite set $I$ is 1.
-\end{remark}
-
-A factorization algebra will be a prefactorization algebra that further satisfies a certain gluing condition that lets us construct its value on `larger' sets if we know it on `smaller' sets.
-More formally, this will be a kind of cosheaf condition, that we describe now, following \cite{weiss1999,af_primer}.
 
@@
 \begin{remark}
-    In other words, $F$ is a Weiss cosheaf if it is a functor that sends colimits (which, in this case, are unions) of Weiss covers $\{ U_i \xhookrightarrow{} U \}_{i \in I}$ to colimits in $\catC$
-    %
-    \begin{equation}
-        F(U) \simeq F \bigg( \bigcup_{i \in I} U_i \bigg) \simeq \mathrm{colim}_{i \in I} F(U_i).
-    \end{equation}
-\end{remark}
-
-\begin{remark}
     The category $\opens[r](X)$ can be replaced with any other category that supports an analogue of the Weiss Grothendieck topology.
@@
 \begin{definition}
-    The $\infty$-category of \emph{($\catC$-valued) factorization algebras on $X$}\footnote{These are called homotopy factorization algebras in \cite{cg2016}, however we do not consider the lax version of factorization algebras that they also present.} is the full $\infty$-subcategory of $\alg{\opens[s](X)}$ as in the pullback
+    The $\infty$-category of \emph{($\catC$-valued) factorization algebras on $X$} is the full $\infty$-subcategory of $\alg{\opens[s](X)}$ as in the pullback
     %
@@
 
-\begin{remark}\label{rem:check_nerve}
-    A factorization algebra is a prefactorization algebra whose restriction to $\opens[r](X)$ is a Weiss cosheaf.
-This means that the definition can be rewritten in an equivalent way as with all cosheaves.
-Following \cite{nlab} (which presents the dual case of sheaves) we can express the condition through the \v{C}ech nerve.
-Let $\mathscr{U}_U = \{ U_i \rightarrow U\}_{i \in I}$ be a (Weiss) cover of an open set $U$ and $F$ be a copresheaf, and define the simplicial object
-    %
-    \begin{equation}
-        \cech_{\bullet}(\mathscr{U}_U, F) := \left( \coprod_{i \in I} F(U_i) \leftleftarrows \coprod_{i, j \in I} F(U_i \cap U_j) \mathrel{\substack{\textstyle\leftarrow\\[-0.6ex]
-        \textstyle\leftarrow\\[-0.6ex]\textstyle\leftarrow}} \coprod_{i, j, k \in I} F(U_i \cap U_j \cap U_k) \mathrel{\substack{\textstyle\leftarrow\\[-0.6ex]\textstyle\leftarrow\\[-0.6ex]\textstyle\leftarrow\\[-0.6ex]\textstyle\leftarrow}} \cdots  \right),
-    \end{equation}
-    %
-    where the maps are induced by the value of $F$ on the inclusions of opens. There are canonical maps $F(U_i) \rightarrow F(U)$, so that at the level of simplicial objects there is a canonical map
-    %
-    \begin{equation}
-        \cech_{\bullet} (\mathscr{U}_U, F) \xrightarrow{\quad} F(U)_{\bullet},
-    \end{equation}
-    %
-    to the constant simplicial complex at $F(U)$. Since $\catC$ has (sifted) colimits we can take the geometric realization to obtain a morphism
-    %
-    \begin{equation}
-        \cech(\mathscr{U}_U, F) \xrightarrow{\quad} F(U).
-    \end{equation}
-    %
-    $F$ is a (homotopy) cosheaf if, and only if, this morphism is an equivalence for every open set $U$ and every Weiss cover of it $\mathscr{U}_U$.
-\end{remark}
-
 All of our definitions above are valid for all topological spaces, so in particular, also the stratified spaces we introduced at the beginning.
@@
 In other words, they will capture information about the stratification.
-
-There is a general definition of locally constant algebra objects in the context of any $\infty$-operad given in \cite[def.2.3.3.20]{lurie_ha}, which, of course, applies here.
-In our case one can also take a perspective more akin to \cite[def.A.1.12]{lurie_ha} by defining locally constant cosheaves and then pulling back this property to factorization algebras.
-This is what we will do, along with focusing our attention to stratified (and therefore also to smooth) manifolds.
-The definitions we will make can in a lot of cases also be expanded for any $C^0$ stratified space or topological manifold.
 
@@
 Now that we have introduced all the varieties of factorization algebras, it's a natural and useful question to ask what the $\infty$-operad governing them is.
-For prefactorization algebras, the answer comes by definition, but this is not the case for (locally constant) factorization algebras.
+For prefactorization algebras, the answer comes by definition, but this is not the case for factorization algebras, locally constant or not.
 We will be working in the generality of stratified manifolds, and all our results in this section will come in pairs, one for the locally constant case and one not.
@@
 However since we only defined (locally constant) factorization algebras at the level of algebras and not at the level of $\infty$-operads, we can take the operadic definition as the basic one, and interpret the results as connecting this to the classical definition.
-The theorems that we present in this section are immensely helpful in relating factorization algebras to results in the area of disk algebras, which will be obvious throughout the rest of this work.
-One important example that we will see is in \Cref{ch:gluing_disk_alg}.
 
-In the service of working towards proofs of all of these results we first have to pause and develop some necessary technically results regarding Weiss covers and preservation of colimits.
+In the service of working towards proofs of all of these results we first have to pause and develop some necessary technically results regarding Weiss covers and preservation of colimits, as well as record a known fact about the relative versions of the $\infty$-operads in play.
+We start with this fact first.
+
+\begin{lemma}\label{lem:double_slice}
+    Every open embedding $e: N \xhookrightarrow{} M$ induces an equivalence of $\infty$-categories
+    %
+    \begin{equation}
+        (\mfld_{/M})_{/e} \simeq \mfld_{/N}.
+    \end{equation}
+    %
+    The same holds for $\mfld[r]$, as well as, $\disk$ and $\disk[r]$.
+\end{lemma}
 
@@
 \end{proof}
-
-%To show the equivalence, we follow a related strategy to the one laid out in part 2 of the proof of \cite[Prop.2.22]{af_primer}.
 
@@
 
-The following lemma about preservation of colimits is sketched out in \cite{rezk2023lan}.
+A suggestion regarding the following lemma about preservation of colimits is sketched out in \cite{rezk2023lan}.
 %
 \begin{lemma}\label{lem:Lan_preserve_colim}
-    Let $F: \mathscr{D} \xrightarrow{} \catC$ and $\iota: \mathscr{D} \xrightarrow{} \mathscr{M}$ be functors of (locally small) $\infty$-categories, where $\mathscr{M}$ and $\catC$ are cocomplete.
+    Let $F: \mathscr{D} \xrightarrow{} \catC$ and $\iota: \mathscr{D} \xrightarrow{} \mathscr{M}$ be functors of $\infty$-categories, where $\mathscr{D}$ is essentially small, while $\mathscr{M}$ and $\catC$ are locally small and cocomplete.
 Let $L_{\iota} F: \mathscr{M} \xrightarrow{} \catC$ be the left Kan extension of $F$ along $\iota$.
@@
 \begin{proof}
-    First consider the special case when $(\iota: \mathscr{D} \xrightarrow{} \mathscr{M}) = (y_{\mathscr{D}}: \mathscr{D} \xrightarrow{} \mathsf{PShv}(\mathscr{D}))$ the Yoneda embedding of $\mathscr{D}$.
-We will see that in this case, $L_{y_{\mathscr{D}}} F$ is colimit preserving because it is a left adjoint to the functor
+    We use the standard notation $y_{\mathscr{X}}=h_\bullet\colon\mathscr{X}\to\mathsf{PShv}(\mathscr{X})$ for `the' covariant Yoneda embedding of a locally small $\infty$-category $\mathscr{X}$ (see \cite[\href{https://kerodon.net/tag/03NF}{03NF},\href{https://kerodon.net/tag/03N2}{03N2}]{lurie_kerodon}).
+First, note that a left Kan extension of type
     %
     \begin{equation}
-        T_F: \catC \xrightarrow{y_{\catC}} \mathsf{PShv} (\catC) \xrightarrow{F^*} \mathsf{PShv} (\mathscr{D}).
+        L_{y_{\mathscr{D}}}F \colon \mathsf{PShv}(\mathscr{D}) \xrightarrow{\ \ \ \ } \mathscr{C}
     \end{equation}
     %
-    Indeed, let $X \simeq y_{\mathscr{D}} (d)$ be a representable presheaf, then there are maps of morphism spaces
+    preserves colimits as a consequence of \cite[\href{https://kerodon.net/tag/03WH}{03WH}]{lurie_kerodon}. Next, we claim that there is an equivalence
     %
-    \begin{align}
-        \mathsf{Hom}_{\catC} (L_{y_{\mathscr{D}}} F (X), c) &\xrightarrow[\simeq]{} \mathsf{Hom}_{\catC} (F (d), c) \xrightarrow[\simeq]{y_{\mathscr{C}}} \mathsf{Hom}_{\mathsf{PShv}(\catC)} (y_{\catC}(F(d)), y_{\catC}(c))\notag\\ &\xrightarrow{F^*} \mathsf{Hom}_{\mathsf{PShv}(\mathscr{D})} (F^*(y_{\catC}(F(d))), T_F(c)) \xrightarrow[\simeq]{} \mathsf{Hom}_{\mathsf{PShv}(\mathscr{D})} (X, T_F(c)).
-    \end{align}
+    \begin{equation}\label{WZUZC5F}
+        L_{\iota}F \simeq L_{y_{\mathscr{D}}}F \circ L_{\iota}y_{\mathscr{D}}
+    \end{equation}
     %
-    The Yoneda embedding $y_{\mathscr{D}}$ is a dense functor, so the above argument holds
-
-    {\color{red} Proof of being adjoint}
-
-    In the general situation where $\iota$ is not necessarily the Yoneda embedding we can partially reduce to the previous case because we can write
+    as functors $\mathscr{M} \to \mathscr{C}$. Indeed, consider the diagram
     % 
     \begin{equation}
-        L_{\iota} F \simeq L_{y_{\mathscr{D}}}F \circ L_{\iota} y_{\mathscr{D}}.
+        \begin{tikzcd}[sep = large]
+            & \mathscr{D}\ar[dl,"{\iota}"']\ar[dr,"{F}"]\ar[d,"{y_{\mathscr{D}}}"]\\
+            \mathscr{M}\ar[rr,bend right=40,"{L_{\iota}F}"']\ar[r,"{L_{\iota}y_{\mathscr{D}}}"'] &[4em] \mathsf{PShv}(\mathscr{D})\ar[r,"{L_{y_{\mathscr{D}}}F}"'] & \mathscr{C},
+        \end{tikzcd}
     \end{equation}
     %
-    Namely, this is because we know that $L_{y_{\mathscr{D}}} F$ preserves colimits, and by the assumptions in the lemma, $L_{\iota} F$ and $L_{\iota} y_{\mathscr{D}}$ are computed pointwise, as colimits over the same indexing $\infty$-category.
+    and note that by \cite[\href{https://kerodon.net/tag/03W9}{03W9},\href{https://kerodon.net/tag/03WH}{03WH}]{lurie_kerodon} there is an equivalence (actually even an isomorphism) $L_{y_{\mathscr{D}}}F \circ y_{\mathscr{D}} \simeq F$ which commutes the right triangle.
+Consequently, using \cite[\href{https://kerodon.net/tag/02YH}{02YH}]{lurie_kerodon}, we have $L_{\iota}F \simeq L_{\iota}(L_{y_{\mathscr{D}}}F \circ y_{\mathscr{D}})$.
+Since $L_{y_{\mathscr{D}}}F$ preserves colimits, we have $L_{\iota}(L_{y_{\mathscr{D}}}F \circ y_{\mathscr{D}})\simeq L_{y_{\mathscr{D}}}F \circ L_{\iota}y_{\mathscr{D}}$, obtaining \Cref{WZUZC5F}.
 
-    Finally, we claim that there is an equivalence of functors
+    Finally, we claim
+    %
+    \begin{equation}\label{D9NQYMT}
+        L_{\iota}y_{\mathscr{D}} \simeq T_{\iota} := \iota^* \circ y_{\mathscr{M}}
+    \end{equation}
+    %
+    as functors $\mathscr{M} \to \mathsf{PShv}(\mathscr{D})$, which will imply the Lemma by \Cref{WZUZC5F}.
+By \cite[\href{https://kerodon.net/tag/03WN}{03WN}]{lurie_kerodon} we have the following diagram in which the triangle commutes
     %
     \begin{equation}
-        \Big( L_{\iota} y_{\mathscr{D}} \simeq T_{\iota} \Big) \in \mathsf{Fun}(\mathscr{M}, \mathsf{PShv}(\mathscr{D})) 
+        \begin{tikzcd}
+            \mathscr{M} \arrow[r, "y_{\mathscr{M}}"] & \mathsf{PShv}(\mathscr{M}) \arrow[r, "\iota^*"] \arrow[d, "\top", phantom, very near start] & \mathsf{PShv}(\mathscr{D}) \arrow[ll, "H", bend left] \\
+            & {} & \mathscr{D} \arrow[u, "y_{\mathscr{D}}"'] \arrow[llu, "\iota", bend left]
+            \end{tikzcd},
     \end{equation}
-
-    {\color{red} Proof of functor equivalence}
-
+    %
+    so that $H$ is a left adjoint to $\iota^* \circ y_{\mathscr{M}}$.
+Being a right adjoint, we can write $\iota^* \circ y_{\mathscr{M}}$ as a left Kan extension, which allows for the following calculation
+    %
+    \begin{equation}
+        \iota^* \circ y_{\mathscr{M}} \simeq L_{H}\mathrm{id}_{\mathsf{PShv}(\mathscr{D})} \simeq L_{H}(L_{y_{\mathscr{D}}} y_{\mathscr{D}}) \simeq L_{H \circ y_{\mathscr{D}}}(\mathscr{D}) \simeq L_{\iota}(y_\mathscr{D}),
+    \end{equation}
+    %
+    where for the second equivalence we used the fact that $y_{\mathscr{D}}$ is a dense functor \cite[\href{https://kerodon.net/tag/03W2}{03W2}]{lurie_kerodon} (using the definition of dense functor as in \cite[\href{https://kerodon.net/tag/03VP}{03VP}]{lurie_kerodon}) and in the third equivalence we used \cite[\href{https://kerodon.net/tag/031M}{031M}]{lurie_kerodon}.
 \end{proof}
@@
     %
-    where on the right-hand side we've used the fact that $\mathscr{U}$ is, in particular, a covering sieve.\footnote{If we also append the straightening--unstraightening construction to $T$, the desired equivalence can equivalently be written as
+    where on the right-hand side we've used the fact that $\mathscr{U}$ is, in particular, a covering sieve.\footnote{If we also append the straightening--unstraightening construction to $T$, the desired equivalence can be thought of as an equivalence
     %
@@
     %
-    one for each $(U \xhookrightarrow{} M) \in \mfld[r]_{/M}$, which are natural in $U$ and preserve the multiplicative structure (see \Cref{rem:unpack_pfac_def,cd:fa_morphisms}).
+    one for each $(U \xhookrightarrow{} M) \in \mfld[r]_{/M}$, which are natural in $U$ and preserve the multiplicative structure of prefactorization algebras (see \Cref{rem:unpack_pfac_def,cd:fa_morphisms}).
 Since $F$ is a locally constant factorization algebra the functor
@@
 
-\begin{remark}
-    One perspective on this result, provided by \cite[thm.2.43]{aft_fhstrat}, is that the theory of locally constant factorization algebras captures as much information as (generalized) homology theory in the sense of \cite[def.2.37]{aft_fhstrat}.
-\end{remark}
-
-\begin{remark}
-    A version of \Cref{thm:disk_alg=lcfa} was proven as \cite[thm.6]{gtz2014} in the case of smooth manifolds.
-The proof there, however, made crucial use of choosing a Riemannian metric on the manifold and constructing geodesically convex neighborhoods.
-This technique is, at least presently, not extendable to the stratified case, but our proof above subverts the need for it.
-\end{remark}
-
-\begin{remark}
-    As noted at the beginning of \S2, the physical interpretation of this version of factorization homology is a way to take a spacetime $M$ and its local observables $A$, and construct \emph{some}, though typically not all, of the global observables.
-The previous \Cref{thm:disk_alg=lcfa} and \Cref{cor:disk_alg=falg} transfer this observation to factorization algebras, which aligns with the observation of \cite{cg2016} that the current version of factorization algebras can only deal with perturbative quantum field theories.
-\end{remark}
-
-\begin{remark}
-    The results of \Cref{thm:disk_alg=lcfa} and \Cref{cor:disk_alg=falg} can be seen as lowering the amount of data that is necessary to define a factorization algebra.
-There is a similar, but slightly weaker result in \cite[\S7.2]{cg2016}, which nonetheless works for all Hausdorff topological spaces.
-The key tool for them are factorizing bases, which play the role of Weiss covers but are further required to be closed under finite intersections.
-Their result then says that a factorization algebra defined on such a basis $\mathscr{U}$ can be extended to the full space $X$, namely there is an equivalence
-    %
-    \begin{equation}
-        \begin{tikzcd}
-            \falg_X(\catC) \arrow[rr, bend left=10, "\mathrm{-|_{\mathscr{U}}}"] \arrow[rr, phantom, "\simeq"]&  & \falg_{\mathscr{U}}(\catC) \arrow[ll, bend left=10, "\mathrm{ext}"].
-        \end{tikzcd}
-    \end{equation}
-    %
-    In comparison, our result drops the intersection requirement, while maintaining the statement.
-\end{remark}
-
-The $\infty$-operad $\disk_{/M}$ is, in general, harder to deal with than its symmetric monoidal counterpart $\disk(\bstr)$. The next lemma outlines a certain situation where this is not the case.
-
-\begin{lemma}\label{lem:disk/M_to_disk}
-    Let $M$ be a stratified manifold. If we can find an $\infty$-category of basics $\bstr_M$ such that $M$ admits a $\bstr_M$-structure and such that
-    %
-    \begin{equation}
-        \mathsf{Hom}_{\mfld(\bstr_M)} (V, M) \simeq *
-    \end{equation}
-    %
-    for all $V \in \bstr_M$, then there is an equivalence of symmetric monoidal $\infty$-categories
-    %
-    \begin{equation}
-        \mathsf{Env}(\disk_{/M}) \xrightarrow{\ \ \simeq \ \ } \disk(\bstr_M).
-    \end{equation}
-\end{lemma}
-
-\begin{remark}
-    If we limit $M$ to be a basic then the requirements of the lemma are exactly that $M$ is final in $\bstr_M$.
-\end{remark}
-
-\begin{proof}
-    We follow the proof of \cite[cor.2.33]{aft_fhstrat}.
-Using \Cref{rem:disk_b=disk_bsc}, the forgetful functor from the slice $\infty$-operad, which is a map of $\infty$-operads, is what will provide the equivalence
-    %
-    \begin{equation}
-        \disk_{/M} \simeq \disk(\bstr_M)_{/M} \xrightarrow{\ \ \ \ } \disk(\bstr_M).
-    \end{equation}
-    %
-    This functor is an equivalence on maximal $\infty$-subgroupoids because for any $V \in \disk(\bstr_M)$ the space of morphisms to $M$ is contractible, so, up to equivalence it is unique.
-Full faithfulness is provided by the fact that the functor on the active $\infty$-subcategories $\disk_{/M} \xrightarrow{} \disk(\bstr_M)$ is a right fibration.
-\end{proof}
-
-The lemma says that for stratified manifolds $M$ that satisfy the conditions, the classification of locally constant factorization algebras on $M$, i.e.
-algebras over $\disk_{/M}$ simplifies to the classification of $\disk(\bstr_M)$-algebras in the usual sense, which are typically easier to work with,
-%
-\begin{equation}
-    \lcfa_M (\catC) \simeq \mathsf{Fun}^\otimes (\mathsf{Env}(\disk_{/M}), \catC) \simeq \alg{\disk(\bstr_M)} (\catC).
-\end{equation}
-
-\subsection{Operations on Factorization Algebras}
-
-There are a few important operations that we can do with factorization algebras (and the other mentioned variants) that will be important for our considerations.
-They allow us to compare factorization algebras from different spaces and will play a big role in any kind of classification statement one might make.
-
-\begin{proposition}\label{prop:pushforward}
-    Given a continuous map $f:X \rightarrow Y$ between topological spaces, there are pushforward functors
-    %
-    \begin{align}
-        &f_*: \alg{\opens[s](X)} \xrightarrow{\quad} \alg{\opens[s](Y)} &f_*: \falg_X \xrightarrow{\quad} \falg_Y,
-    \end{align}
-    %
-    which, on objects, are given by the prescription
-    %
-    \begin{equation}
-        f_*F (U) := F(f^{-1}U).
-    \end{equation}
-\end{proposition}
-
-\begin{proof}
-    By the definition of continuity, the case of prefactorization algebras is trivial.
-Thus, the only thing we are left to show is that if $F$ satisfies the Weiss cosheaf property then so does $f_* F$.
-Given a Weiss cover $\{U_i \xhookrightarrow{} U\}_{i \in I}$ of $U$, we observe that $\{f^{-1}U_i \xhookrightarrow{} f^{-1}U\}_{i \in I}$ is a Weiss cover of $f^{-1}U$.
-Namely, if $S \subset f^{-1}U$ is a finite subset of $U$, then $f(S)$ is contained in some $U_i$ by the Weiss cover property of $\{U_i \xhookrightarrow{} U\}_{i \in I}$.
-But in that case $S$ has to be contained in $f^{-1}U_i$, giving it the Weiss cover property too.
-Thus, by the definition of the pushforward on objects the Weiss cosheaf property is preserved.
-\end{proof}
-
-The case of locally constant factorization algebras is different when it comes to the pushforward.
-This is because it's not immediate that local constancy is preserved when pushed forward.
-However, if we limit the types of maps we pushforward with we can still construct a functor.
-The following two results give the flavor of what is required.
-
-\begin{proposition}[{\cite[prop.15]{ginot2015}}]
-    If $f: X \rightarrow Y$ is a locally trivial fibration between smooth manifolds then the pushforward functor exists even between the $\infty$-categories of locally constant factorization algebras
-    %
-    \begin{equation}
-        f_*: \lcfa_X \xrightarrow{\quad} \lcfa_Y.
-    \end{equation}
-\end{proposition}
-
-\begin{corollary}\label{cor:pushforward_for_lc}
-    Let $f: M \xrightarrow{} N$ be a constructible bundle of stratified manifolds. Then the pushforward functor for factorization homology of \Cref{thm:fh_pushforward} serves as a pushforward
-    %
-    \begin{equation}
-        f_*: \lcfa_M \xrightarrow{\quad} \lcfa_N,
-    \end{equation}
-    %
-    by using \Cref{thm:disk_alg=lcfa}.
-\end{corollary}
-
-\begin{remark}\label{rem:fh_is_pushingforward}
-    Having defined the pushforward functor of factorization algebras we can consider the map $\mathsf{p}:M \rightarrow *$.
-Given any $A \in \alg{\disk(\bstr)_{/M}}$ the factorization algebra $F_A$ generated by $A$ satisfies
-    %
-    \begin{equation}
-        \int_M A  = F_A(M) \simeq (\mathsf{p}_* F_A)(*).
-    \end{equation}
-    %
-    The one point manifold is a very simple space, which makes the concepts of prefactorization algebras, factorization algebras and locally constant factorization algebras coincide.
-All of them are in fact given by a pointed object of the target category.
-Evaluation at $*$ simply returns the underlying object.
-Thus, in a sense evaluating factorization homology on a space $M$ is the same procedure as pushing-forward by the map $\mathsf{p}$.
-Versions of factorization homology that can evaluate lower dimensional manifolds (as compared to the structure of the disk algebra), for example as in \cite[cor.2.29]{aft_fhstrat}, can then be seen as relaxing this pushforward from $*$ to a manifold with more structure.
-\end{remark}
-
-In the opposite direction, we do not, in general, have a pullback functor.
-\cite{cg2016} provide a construction of a pullback in the case of open immersions, but we will only focus on the case of restrictions.
-Namely, given an open subset $U \subset X$ of a topological space $X$, and given a factorization algebra $F \in \falg_X$ we can clearly define a factorization algebra $F|_{U} \in \falg_U$ by restricting to those open subsets that are fully contained in $U$.
-Furthermore, this clearly holds not only for factorization algebras, but prefactorization algebras and locally constant factorization algebras too.
-As an interesting sidenote regarding stratifications, though, we note the following lemma.
-
-\begin{lemma}\label{lem:ff_functor_to_refinement}
-    Let $u: X \rightarrow \hat{X}$ be the morphism of \Cref{ex:forget_strat} that forgets the stratification.
-The functor $u_*: \lcfa_{X} (\catC) \rightarrow \lcfa_{\hat{X}} (\catC)$ has a fully faithful left adjoint.
-\end{lemma}
-
-\begin{proof}
-    Consider the functor $\hat{-}: \falg_{\hat{X}} \rightarrow \falg_{X}$, which acts as $\hat{F}(U) := F(u(U))$, namely it returns algebras that evaluate open subsets by forgetting their stratification first.
-We claim this functor is the left adjoint of $u_*$.
-Indeed, given a morphism $(\phi: \hat{F} \rightarrow G) \in \falg_{X}$, i.e.
-a family of morphisms $\phi(U): \hat{F}(U) \rightarrow G(U)$ for all opens $U$ in $X$, it is easy to verify that we can construct a morphism of algebras over $\hat{X}$, $\hat{\phi}(u(U)): F(u(U)) \rightarrow u_*G (u(U))$, since $\hat{F}(U) = F(u(U))$ and $u_*G(u(U)) = G(u^{-1}(u(U))) = G(U)$.
-The last equality holds because $u$ is an injective map.
-In fact, this last observation also proves that the unit of this adjunction is an isomorphism, granting the full faithfulness.
-\end{proof}
-
-\begin{remark}
-    In fact, the above proof is true more generally for any map of stratified spaces that is a homeomorphism of the underlying topological spaces (so, in particular, any refinement).
-This means that locally constant factorization algebras record the data of coarser stratified structures as $\infty$-subcategories.
-Forgetting local constancy, the proof, of course, applies to factorization algebras of all flavors, however for the types that don't detect the stratified structure the above functor is even an equivalence, and not just fully-faithful, and is of no interest.
-\end{remark}
-
-\subsection{Additivity of \texorpdfstring{$\lcfa$}{lcfa}s on Stratified Spaces}
-
-In the special case of product spaces $X \times Y$, from the previous discussion we now know that the projections $\pi_1: X \times Y \rightarrow X$ and $\pi_2: X \times Y \rightarrow Y$, give us pushforwards.
-This is true even in the locally constant case since the projections are (even trivial) fiber bundles, which is a concept that is a special case of constructible bundles.
-For $\pi_1$, for example, this essentially uses the fact that if we can evaluate all open sets of $X \times Y$ then we can definitely evaluate the open sets that look like $U \times Y$, with $U \subset X$ an open set.
-But, in fact, we can do even more, because we can even evaluate the more granular open subsets $U \times V$ with $U \subset X$ and $V \subset Y$ opens.
-To capture this idea in formal terms we claim:
-%
-\begin{proposition}\label{prop:exp_of_products}
-    Let $X$ and $Y$ be topological spaces.
-There is a functor from the $\infty$-category of prefactorization algebras on the product $X \times Y$ to the $\infty$-category of prefactorization algebras on $X$ valued in the $\infty$-category of prefactorization algebras on $Y$
-    %
-    \begin{equation}
-        \bar{\pi}: \alg{\opens(X \times Y)}(\catC) \xrightarrow{\qquad} \alg{\opens(X)} (\alg{\opens(Y)} (\catC)).
-    \end{equation}
-    %
-    This functor descends to factorization algebras too
-    %
-    \begin{equation}
-        \bar{\pi}: \falg_{X \times Y}(\catC) \xrightarrow{\qquad} \falg_{X}(\falg_{Y}(\catC)).
-    \end{equation}
-\end{proposition}
-
-\begin{remark}
-    The conditions we imposed on $\catC$ allowed us, in \Cref{rem:sym_mon_inheritance}, to inherit a symmetric monoidal structure on the $\infty$-categories of factorization algebras of all varieties.
-It also allowed us to inherit the existence of colimits.
-This is the reason why the above can even be stated.
-\end{remark}
-
-\begin{proof}
-    Indeed, given opens $U \subset X$ and $V \subset Y$, the values we assign are $(\bar{\pi}F) (U)(V) = F(U \times V)$.
-Fixing an open subset $U \subset X$, we obviously get a prefactorization algebra $(\pi_2|_U)_* (F|_U) \in \alg{\opens(Y)}$ by pushing forward with $\pi_2|_U: U \times Y \rightarrow Y$, which shows that $\bar{\pi}F$ is valued in $\alg{\opens(Y)}$.
-The only thing left to show is that $\bar{\pi} F$ has the structure of a prefactorization algebra on $X$.
-To do this, for each multi-morphism $(\{ U_i \}_{i \in I} \rightarrow U) \in \opens(X)$ we assign a map $\bar{\pi}F (\{ U_i \}_{i \in I}, U)$ of factorization algebras on $Y$.
-Such an algebra map is specified by giving its value on all opens of $Y$ separately.
-We can thus assign
-    %
-    \begin{equation}
-        \bar{\pi}F (\{ U_i \}_{i \in I}, U)(V) = F(\{ U_i \times V \}_{i \in I}, U \times V),
-    \end{equation}
-    %
-    which uses the projections $\pi_1|_V : X \times V \rightarrow X$ to assign $\pi_1|_V^{-1}(U) = U \times V$.
-
-    It is not hard to check that the above also holds for the example of factorization algebras on topological spaces, by using \cite[\S7.2]{cg2016}.
-However, we'll focus on manifolds, in which case, the construction from above immediately works since we now have to do it for $\disk[r]_{/X}$ instead of $\mfld[r]_{/X}$.
-The only things to mention is that products of disks are again disks \cite[cor.3.4.9]{aft_localstrut}.
-\end{proof}
-
-\begin{theorem}[Additivity]\label{thm:additivity_lc}
-    Let $M$ and $N$ be stratified manifolds. There is an equivalence of $\infty$-operads
-    %
-    \begin{equation}
-        \disk_{/M} \otimes \disk_{/N} \xrightarrow{\ \ \simeq \ \ } \disk_{/M \times N},
-    \end{equation}
-    %
-    between the tensor product of $\infty$-operads $\disk_{/M}$ and $\disk_{/N}$ and the $\infty$-operad $\disk_{/M \times N}$.
-In particular, there is an equivalence of $\infty$-categories of algebras
-    %
-    \begin{equation}
-        \bar{\pi}: \lcfa_{M \times N}(\catC) \xrightarrow{\ \ \simeq \ \ } \lcfa_{M}(\lcfa_{N}(\catC)),
-    \end{equation}
-    which can be seen to be induced by the functor $\bar{\pi}$.
-\end{theorem}
-
-\begin{remark}
-    A version of the above theorem also appears as \cite[prop.18]{ginot2015}.
-The equivalence proven there is for the case of smooth manifolds and relies on the local proof of \cite{lurie_ha} for $\mathbb{R}^n$.
-The statement at the level of $\infty$-operads is slightly stronger and, using \Cref{thm:disk_alg=lcfa}, it implies the statement for factorization algebras.
-This $\infty$-operadic statement, again for smooth manifolds, is found in \cite[ex.5.4.5.5]{lurie_ha}.
-\end{remark}
-
-\begin{proof}
-    Following \cite[\S.2.2.5]{lurie_ha} the tensor product of $\infty$-operads is defined through a universal property.
-Namely, we define a bifunctor of $\infty$-operads to be a map $f: \mathscr{O}_1 \times \mathscr{O}_2 \xrightarrow{} \mathscr{O}$ such that:
-    %
-    \begin{enumerate}
-        \item The diagram
-        %
-        \begin{equation}
-            \begin{tikzcd}
-                \mathscr{O}_1 \times \mathscr{O}_2 \arrow[r, "f"] \arrow[d] & \mathscr{O} \arrow[d] \\
-                \mathsf{Fin}_* \times \mathsf{Fin}_* \arrow[r, "\wedge"] & \mathsf{Fin}_*
-            \end{tikzcd}
-        \end{equation}
-        %
-        commutes, and
-        \item $f$ sends pairs of inert morphisms in $\mathscr{O}_1$ and $\mathscr{O}_2$ to inert morphisms in $\mathscr{O}$.
-    \end{enumerate}
-    %
-    We denote the full $\infty$-subcategory of $\mathsf{Fun}_{\mathsf{Fin}_*}(\mathscr{O}_1 \times \mathscr{O}_2, \mathscr{O})$ consisting of the bifunctors of $\infty$-operads by $\mathsf{BiFunc}(\mathscr{O}_1, \mathscr{O}_2; \mathscr{O})$.
-The universal property of the tensor product is then that it is the $\infty$-operad $\mathscr{O}_1 \otimes \mathscr{O}_2$ together with a bifunctor of $\infty$-operads $f: \mathscr{O}_1 \times \mathscr{O}_2 \xrightarrow{} \mathscr{O}_1 \otimes \mathscr{O}_2$ such that composition with $f$ determines an equivalence
-    %
-    \begin{equation}
-        \alg{\mathscr{O}_1 \otimes \mathscr{O}_2} (\mathscr{O}) \xrightarrow{\ \ \simeq \ \ } \mathsf{BiFunc}(\mathscr{O}_1, \mathscr{O}_2; \mathscr{O}),
-    \end{equation}
-    %
-    for every $\infty$-operad $\mathscr{O}$\footnote{More details about the construction, its existence, and the fact that it captures a nontrivial concept can be found in the provided reference.}.
-
-    For us this means that we can show the desired equivalence of $\infty$-operads if we provide a bifunctor of $\infty$-operads $\disk_{/M} \times \disk_{/N} \xrightarrow{} \disk_{/M \times N}$ that is an equivalence.
-Our candidate bifunctor for this purpose will be $\times$, the product of stratified spaces.
-We now explain what this means on a technical level.
-
-    By \Cref{rem:details_disk/M} the definition of $\disk_{/M}$ as an $\infty$-operad is given by the pullback
-    %
-    \begin{equation}
-        \begin{tikzcd}
-            \disk_{/M} \arrow[rd, phantom, "\ulcorner", very near start] \arrow[r] \arrow[d] & (\disk_{/M})^{\amalg} \arrow[d] \\
-            \disk(\bsc) \arrow[r] & \disk(\bsc)^{\amalg}
-        \end{tikzcd},
-    \end{equation}
-    %
-    where on the right-hand side $\disk_{/M}$ and $\disk(\bsc)$ are appearing in their role as $\infty$-categories through \cite[Con.2.4.3.1]{lurie_ha}, while on the left-hand side they're appearing in their role as $\infty$-operads.
-We note here that the construction of $\mathscr{O}^{\amalg}$ for any $\infty$-category $\mathscr{O}$ is given through a universal property from which it immediately follows that $\mathscr{O}_1^{\amalg} \times \mathscr{O}_2^{\amalg} \simeq (\mathscr{O}_1 \times \mathscr{O}_2)^{\amalg}$.
-Keeping this in mind together with the fact that products and pullbacks commute we can draw the following commutative diagram
-    %
-    \begin{equation}
-        \begin{tikzcd}[column sep = 25]
-            \disk_{/M} \times \disk_{/N} \arrow[rd, phantom, "\ulcorner", very near start] \arrow[r] \arrow[d] & (\disk_{/M})^{\amalg} \times (\disk_{/N})^{\amalg} \arrow[r, "\simeq"] \arrow[d] & (\disk_{/M} \times \disk_{/N})^{\amalg} \arrow[d] \\
-            \disk(\bsc) \times \disk(\bsc) \arrow[r] & \disk(\bsc)^{\amalg} \times \disk(\bsc)^{\amalg} \arrow[r, "\simeq"] & (\disk(\bsc) \times \disk(\bsc))^{\amalg}  
-        \end{tikzcd}.
-    \end{equation}
-    %
-    Since $\disk_{/M \times N}$ is also given by a pullback, to provide an equivalence of $\infty$-operads $\disk_{/M} \times \disk_{/N} \xrightarrow{} \disk_{/M \times N}$ it is then sufficient to provide a commutative diagram of equivalences of $\infty$-operads
-    %
-    \begin{equation}
-        \begin{tikzcd}
-            \disk(\bsc) \times \disk(\bsc) \arrow[r] \arrow[d, "\simeq"] & (\disk(\bsc) \times \disk(\bsc))^{\amalg} \arrow[d, "\simeq"] & (\disk_{/M} \times \disk_{/N})^{\amalg} \arrow[l] \arrow[d, "\simeq"] \\
-            \disk(\bsc) \arrow[r] & \disk(\bsc)^{\amalg} & (\disk_{/M \times N})^{\amalg} \arrow[l]
-        \end{tikzcd}
-    \end{equation}
-    %
-    Looking back at the construction \cite[Con.2.4.3.1]{lurie_ha} of $\mathscr{O}^{\coprod}$, since it is given by a universal property we see that an equivalence of $\infty$-categories $\mathscr{O}_1 \simeq \mathscr{O}_2$ implies an equivalence of $\infty$-operads $\mathscr{O}_1^{\amalg} \simeq \mathscr{O}_2^{\amalg}$ such that the left-hand square in the above diagram would come for free.
-With this the ingredients we need are:
-    %
-    \begin{enumerate}
-        \item an equivalence of $\infty$-operads
-        %
-        \begin{equation}
-            \disk(\bsc) \times \disk(\bsc) \xrightarrow[\ \ \simeq \ \ ]{\times} \disk(\bsc),
-        \end{equation}
-        %
-        \item an equivalence, now only, of $\infty$-categories
-        %
-        \begin{equation}
-            \disk_{/M} \times \disk_{/N} \xrightarrow[\ \ \simeq \ \ ]{\times} \disk_{/M \times N},
-        \end{equation}
-        %
-        \item such that there is a commutative diagram of $\infty$-categories
-        %
-        \begin{equation}
-            \begin{tikzcd}
-                \disk_{/M} \times \disk_{/N} \arrow[r, "\times", "\simeq"'] \arrow[d] & \disk_{/M \times N} \arrow[d] \\
-                \disk(\bsc) \times \disk(\bsc) \arrow[r, "\times", "\simeq"'] & \disk(\bsc)
-            \end{tikzcd},
-        \end{equation}
-        %
-        where we have forgotten the $\infty$-operad equivalence down to an $\infty$-category equivalence.
-    \end{enumerate}
-    %
-    In the above we have already used the notation $\times$ to express an idea about what the maps we will provide are.
-Though there is abuse of notation it is clear from context which map $\times$ we want.
-Since the vertical maps are the canonical forgetful functors it will be clear from the construction that (3) is satisfied.
-
-    To get the data of (2) (..... reduce to $\bsc$). So we need to provide an equivalence of $\infty$-categories
-    %
-    \begin{equation}\label{eq:b/M_x_b/N=b/MxN}
-        \bsc_{/M} \times \bsc_{/N} \xrightarrow{\times} \bsc_{/M \times N}.
-    \end{equation}
-
-    To get (1), we remember that as an $\infty$-operad $\disk(\bsc)$ is, in fact, the free symmetric monoidal $\infty$-category generated by $\bsc$, thus it suffices to provide an equivalence of $\infty$-categories
-    %
-    \begin{equation}
-        \bsc \times \bsc \xrightarrow[\ \ \simeq \ \ ]{\times} \bsc.
-    \end{equation}
-    %
-    Remembering that $\bsc$ has a terminal object $*$ so that $\bsc_{/*} \simeq \bsc$, this equivalence is just a special case of \Cref{eq:b/M_x_b/N=b/MxN} in the case when $M = N = *$.
-
-    The $\infty$-category $\bsc_{/M}$ is also known, by definition, as $\mathsf{Entr(M)}$, the enter-path $\infty$-category of the stratified manifold $M$.
-By \cite[Lem.3.3.9]{afr_homhyp} this is equivalent to the opposite $\infty$-category of the exit-path $\infty$-category of $M$.
-By \cite[Obs.3.3.3]{afr_homhyp} the equivalence
-    %
-    \begin{equation}
-        \mathsf{Exit}(M) \times \mathsf{Exit}(N) \xrightarrow[\ \ \simeq \ \ ]{\times} \mathsf{Exit}(M \times N)
-    \end{equation}
-    %
-    is immediate.
-
-    To complete the proof we only have to check that $\times: \disk_{/M} \times \disk_{/N} \xrightarrow{} \disk_{M \times N}$ satisfies the conditions to qualify as a bifunctor of $\infty$-operads.
-
-    ....
-
-    The equivalence of $\infty$-operads $\disk_{/M} \otimes \disk_{/N} \xrightarrow{\ \ \simeq \ \ } \disk_{/M \times N}$ implies an equivalence at the level of $\alg{\disk_{/M}}$, which together with \Cref{thm:disk_alg=lcfa} gives rise to the equivalence of factorization algebras in the theorem statement.
-That this is related to the functor $\bar{\pi}$ can be seen by inspection of the objects and morphisms.
-\end{proof}
-
-\begin{remark}
-    At the pointwise level of evaluating specific opens this statement is related to the Fubini theorem for factorization homology \cite[cor.2.29]{aft_fhstrat}.
-The notation used in the citation is technically abusive because factorization homology is evaluating lower dimensional manifolds, but it is clear from the context that this is to be understood exactly as the evaluation of the pushforward factorization algebra on the lower dimensional manifold (see \Cref{rem:fh_is_pushingforward}).
-\end{remark}
-
-\begin{example}
-    We can view a Euclidean space $\mathbb{R}^{m+n}$ as a product space $\mathbb{R}^m \times \mathbb{R}^n$, in which case \Cref{thm:additivity_lc} specializes to give the famous result of Dunn additivity \cite{dunn1988} which can be found in the following form in \cite{lurie_ha}:
-    %
-    \begin{proposition}\label{prop:dunn_additivity}
-        There is an equivalence of $\infty$-categories
-        %
-        \begin{equation}
-            \alg{\mathbb{E}_{n + m}} (\catC) \xrightarrow{\ \ \simeq \ \ } \alg{\mathbb{E}_n} (\alg{\mathbb{E}_m} (\catC)).
-        \end{equation}
-    \end{proposition}
-\end{example}
-
-\begin{remark}
-    The proof of \Cref{thm:additivity_lc}, when specialized to ordinary manifolds, as given in \cite{ginot2015} actually depends on Dunn additivity to work, however the proof presented above and the one in \cite{lurie_ha} are both independent of this special case.
-\end{remark}
-
-\subsection{Factorization Algebras on Intervals}\label{ssec:lcfa_on_ints}
-
-As was the case with factorization homology, so too with factorization algebras we now turn to a few very important constructions of locally constant factorization algebras on intervals.
-Namely, we will consider how we can construct a locally constant factorization algebra on the spaces $\mathbb{R}$ (a.k.a.
-the open interval) and $\hoint$ (a.k.a.
-the half-open interval).
-These will be a very important backbone for intuition about locally constant factorization algebras, as well as a key part of proofs later on.
-We finish with factorization algebras for the closed interval $[-1,1]$.
-
-\begin{construction}\label{con:lcfas_on_R}
-    Consider a unital, (homotopy) associative algebra $A$ in the category $\catC$.
-For a first pass we use \cite[\S7.2]{cg2016} to construct a factorization algebra out of this data.
-We first check that the disks $\disk[r]_{/\mathbb{R}}$ of $\mathbb{R}$ form a factorizing basis.
-This is true since the disks are always a basis for any manifold, they are factorizing since we have all disjoint unions, and they are closed under finite intersections because the disks of $\mathbb{R}$ are intervals.
-Therefore, by \cite[\S7.2]{cg2016}, we need only assign values to these.
-Given any disk $U$ we assign the same value, $F_A(U) := A$.
-Similarly, given a multi-morphism $\sqcup_{i \in I} U_i \xhookrightarrow{} U$, with $I$ non-empty, we assign the map given by the multiplication of $A$
-    %
-    \begin{equation}
-        F_A(\sqcup_{i \in I} U_i \xhookrightarrow{} U) := \otimes_{i \in I} A \rightarrow A.
-    \end{equation}
-    %
-    The implicit convention, is that the ordering of the intervals, provided by the standard orientation (or framing) of $\mathbb{R}$, determines the order in which we multiply.
-Associativity forbids any other ordering except the completely opposite one, which would yield the opposite multiplication, and thus the opposite algebra.
-Finally, in the case of $\emptyset \xhookrightarrow{} U$, we assign the map that chooses the unit $\mathbb{1} \rightarrow A$.
-At this point we have constructed a prefactorization algebra on $\mathbb{R}$.
-To use \cite[\S7.2]{cg2016} we need to first check the Weiss cosheaf condition.
-But because intervals are closed under finite intersections the \v{C}ech nerve definition of \Cref{rem:check_nerve} makes this easy; the simplicial object $\cech_{\bullet}(\disk[r]_{/\mathbb{R}}, F_A)$ in all degrees will be a coproduct of copies of $A$.
-Thus, $F_A$ is indeed a $\disk[r]_{/\mathbb{R}}$-factorization algebra and can be extended to a factorization algebra on $\mathbb{R}$.
-By definition, it is also obviously locally constant.
-
-    In this simple case the disks are closed under finite intersections, so the construction works out.
-More generally, one would need to find another factorizing basis.
-In the case of smooth manifolds one possible way is to choose a Riemannian metric and take the geodesically convex neighborhoods.
-An alternative is to get rid of the property of being closed under finite intersections altogether.
-It turns out, because of \Cref{thm:disk_alg=lcfa}, that this is indeed possible, and that we can always stick to using disks even in the most general situations.
-
-    In whatever way we go about it, it is immediate that we have constructed a functor $\alg{\mathbb{E}_1}(\catC) \rightarrow \lcfa_{\mathbb{R}} (\catC)$ from the $\infty$-category of unital, (homotopy) associative algebras, or $\mathbb{E}_1$-algebras to the $\infty$-category of locally constant factorization algebras on $\mathbb{R}$.
-In fact, we claim that this functor is actually an equivalence, i.e., that every locally constant factorization algebra on $\mathbb{R}$ is equivalent to one induced like in the construction.
-\end{construction}
-
-\begin{proposition}\label{prop:R_gives_E1}
-    There is an equivalence of $\infty$-categories
-    %
-    \begin{equation}
-        \alg{\mathbb{E}_1}(\catC) \xrightarrow{\ \ \simeq \ \ } \lcfa_{\mathbb{R}} (\catC).
-    \end{equation}
-\end{proposition}
-
-\begin{proof}
-    What is left to show is the essential surjectivity of the functor.
-This holds because every disk in $\mathbb{R}$ is diffeomorphic to $\mathbb{R}$ itself.
-So, given $F \in \lcfa_{\mathbb{R}}$, we can get an underlying object for our $\mathbb{E}_1$-algebra as $A = F(\mathbb{R})$.
-The previous observation and the local constancy then force the value on each disk to be equivalent to this.
-The space of embeddings of two disks $\mathbb{R} \sqcup \mathbb{R} \xhookrightarrow{} \mathbb{R}$ is, up to homotopy, equivalent to two points, which provide exactly the multiplication map $ A \otimes A \rightarrow A$ of the algebra and its opposite multiplication.
-Associativity, up to homotopy, comes about exactly because all embeddings of any number of disks can, up to homotopy, be factorized through the embedding of two disks at a time.
-As before, the unit comes from the map $F(\emptyset \xhookrightarrow{} \mathbb{R}) = (\mathbb{1} \rightarrow A)$.
-Thus, we have constructed an $\mathbb{E}_1$-algebra from the given data, and the proposition holds.
-\end{proof}
-
-\begin{construction}\label{con:lcfas_on_hoint}
-    Consider a unital, (homotopy) associative algebra $A$ in the category $\catC$, as above, together with a unital right module $M$ of $A$ in the category $\catC$.
-From this data we will construct a locally constant factorization algebra $F_{(M, A)}$ on the stratified space $\hoint$.
-Considering \Cref{con:lcfas_on_R} and the open embedding $\mathbb{R} \cong \mathbb{R}_{>0} \xhookrightarrow{} \hoint$, we will choose the restriction to be $F_{(M,A)}|_{\mathbb{R}} = F_A$, i.e.
-any disk that doesn't include the point $0 \in \hoint$, we regard as a disk of $\mathbb{R}$ through the given map, and we assign the value $A$ to it like in the \Cref{con:lcfas_on_R}.
-This leaves us only with the stratified disks $U_*$ that contain the point $0 \in \hoint$.
-To these we assign the module $F_{(M,A)}(U_*) = M$.
-Since there can be at most one stratified disk that includes the point $0 \in \hoint$, the maps that we have to assign values to look like $U_* \sqcup (\sqcup_{i \in I} U_i) \xhookrightarrow{} U'_*$, but this is exactly what is provided by the right module structure
-    %
-    \begin{equation}
-        F_{(M,A)} (U_* \sqcup (\sqcup_{i \in I} U_i) \xhookrightarrow{} U'_*) = M \otimes (\otimes_{i \in I} A) \rightarrow M.
-    \end{equation}
-    %
-    Of course the pointing of the module comes from $F_{(M,A)}(\emptyset \xhookrightarrow{} U_*) = \mathbb{1} \rightarrow M$. As before, even more is true:
-\end{construction}
-
-\begin{proposition}\label{prop:hoint_gives_modules}
-    There is an equivalence of $\infty$-categories between the $\infty$-categories of $\mathbb{E}_1$-algebras together with a right module and locally constant factorization algebras on the half-open interval
-    %
-    \begin{equation}
-        \mathsf{RMod}(\catC) \xrightarrow{\ \ \simeq \ \ } \lcfa_{\hoint} (\catC).
-    \end{equation}
-\end{proposition}
-
-\begin{proof}
-    The proof goes along the same lines as the proof of \Cref{prop:R_gives_E1}.
-We can find the module by evaluating on $\hoint$, and we can find the algebra by evaluating on $\hoint \setminus \{ 0 \} \cong \mathbb{R}$, as a specified stratum of $\hoint$.
-\end{proof}
-
-\begin{remark}\label{rem:left_or_right_module}
-    The fact that we chose left modules to provide the data in \Cref{prop:hoint_gives_modules}, does not play much of a role because a left module is exactly a right module of the opposite algebra, giving $\mathsf{LMod}(\catC) \simeq \mathsf{RMod}(\catC)$.
-Where the distinction comes up, is if we want to fix the $\mathbb{E}_1$-algebra away from $0 \in \hoint$ beforehand.
-In that case we have to use one of the two possible conventions on the order of multiplication.
-If we choose the increasing convention then the subset containing $0 \in \hoint$ is on the left making it a right module, while with the opposite convention it would be a left module of the opposite algebra.
-\end{remark}
-
-It's not hard to extend \Cref{con:lcfas_on_R} and \Cref{con:lcfas_on_hoint} to the closed interval $[-1,1]$ by hand, but through \Cref{thm:disk_alg=lcfa} we can see that \Cref{prop:disk1bor_over_int=ORL} and \Cref{prop:env_ORL=env_assocRL} already do all the necessary work.
-
-\begin{corollary}\label{cor:lcfas_on_closed_int}
-    There is an equivalence between the $\infty$-categories of locally constant factorization algebras on the closed interval and algebras over the $\infty$-operad $\mathsf{Assoc^{RL}}$
-    %
-    \begin{equation}
-        \lcfa_{[-1,1]} (\catC) \xrightarrow{\ \ \simeq \ \ } \alg{\mathsf{Assoc^{RL}}} (\catC).
-    \end{equation} 
-\end{corollary}
-
-\begin{remark}
-    Another perspective on why all of these constructions look the way they do is provided by \Cref{lem:disk/M_to_disk}. It applies in all of the above cases, namely:
-    %
-    \begin{enumerate}
-        \item For $\mathbb{R}$, the convenient $\infty$-category of basics is $\bstr = \mathsf{D}_1^*$,
-        \item For $[-1,1]$ the convenient $\infty$-category of basics is $\bstr = \mathsf{D}_1^{\partial, *}$.
-        \item For $\hoint$, we could define a convenient $\infty$-category of basics which describes framed 1-dimensional manifolds which only have a right boundary (a concept that we can state because of the framing).
-    \end{enumerate}
-    %
-    We can see that even though factorization algebras, as we have defined them here, don't detect the tangential structure of the manifold, it is usually favorable, if possible, to give the manifold some structure anyway.
-In particular, the rigid structure of framing is very useful because it massively reduces the spaces of allowed open embeddings.
-\end{remark}
-
-\subsection{Factorization Algebras on Euclidean Spaces}\label{ssec:lcfa_on_Rn}
-
-In this section we want to describe locally constant factorization algebras on Euclidean spaces $\mathbb{R}^n$.
-By \Cref{lem:disk/M_to_disk} we can hope for an $\infty$-category of basics such that we simplify the situation down to $\disk (\bstr)$-algebras.
-In fact, since $\mathbb{R}^n$ is frameable an $\infty$-category of basics that we can choose is $\mathsf{D}_n^* \simeq * \xrightarrow{\{ \mathbb{R}^n\}} \bsc$.
-Specifically, this makes us focus on framed $n$-dimensional disk algebras
-%
-\begin{equation}
-    \lcfa_{\mathbb{R}^n} (\catC) \simeq \alg{\disk (\mathsf{D}_n^*)} (\catC).
-\end{equation}
-%
-
-\begin{theorem}[{\cite[thm.5.5.4.10]{lurie_ha}}]
-    There is an equivalence of $\infty$-categories between the $\infty$-categories of locally constant factorization algebras on $\mathbb{R}^n$ and $\mathbb{E}_n$-algebras
-    %
-    \begin{equation}
-        \alg{\mathbb{E}_n} (\catC) \xrightarrow{\ \ \simeq \ \ } \lcfa_{\mathbb{R}^n} (\catC).
-    \end{equation}
-\end{theorem}
-
-\begin{proof}
-    With our setup, thanks to \Cref{thm:disk_alg=lcfa} and \Cref{lem:disk/M_to_disk}, it is sufficient to show that there is a weak equivalence of $\infty$-operads between $\disk (\mathsf{D}_n^*)$ and $\mathbb{E}_n$, i.e.
-    %
-    \begin{equation}
-        \alg{\disk (\mathsf{D}_n^*)} \xrightarrow{\ \ \simeq \ \ } \alg{\mathbb{E}_n}.
-    \end{equation}
-    %
-    But this is just the fact that the $\disk_{\mathsf{D}_n^*}$ $\infty$-operad gives rise to $\mathbb{E}_n$-algebras from \Cref{prop:framed_ndisk=En}.
-\end{proof}
-
-\begin{remark}
-    We already encountered the $n=1$ version of the proposition above when we discussed locally constant factorization algebras on the open interval in \Cref{prop:R_gives_E1}, and the construction there gives us an intuition about how to actually construct the locally constant factorization algebra from the data of the $\mathbb{E}_n$-algebra.
-The theorem formalizes that this assignment is, in fact, an equivalence.
-\end{remark}
-
-\begin{remark}[{\cite[prop.3.16]{francis2013}, \cite[ex.5.5.4.16]{lurie_ha}}]
-    In the case of Euclidean spaces like $\mathbb{R}^n$, essentially because of translation invariance, a special thing happens when we restrict away from the origin.
-That is, we know that given a locally constant factorization algebra $F$ on $\mathbb{R}^n$ we can restrict it to any open subset like, for example, $\mathbb{R}^n \setminus \{ 0 \} \cong S^{n-1} \times \mathbb{R}$ to get another locally constant factorization algebra $F|_{S^{n-1} \times \mathbb{R}}$.
-By \Cref{thm:additivity_lc} we know that $F|_{S^{n-1} \times \mathbb{R}} \in \lcfa_{\mathbb{R}} (\lcfa_{S^{n-1}} (\catC))$, so that in particular it is an $\mathbb{E}_1$-algebra.
-If we pushforward to $\mathbb{R}$, by the discussion at \Cref{rem:fh_is_pushingforward} we could denote the resulting $\mathbb{E}_1$-algebra by
-    %
-    \begin{equation}
-        \int_{S^{n-1}} F.
-    \end{equation}
-    %
-    What \cite[prop.3.16]{francis2013} shows is then:
-
-    \begin{proposition}\label{univ_env_for_En}
-        Given a locally constant factorization algebra $F$ on $\mathbb{R}^n$, its universal enveloping algebra is given by $\int_{S^{n-1}} F$, i.e. there is an equivalence of $\infty$-categories
-        %
-        \begin{equation}
-            \mathsf{Mod}^{\mathbb{E}_n}_{F} (\catC) \xrightarrow{\ \ \simeq \ \ } \mathsf{LMod}_{\int_{S^{n-1}} F} (\catC).
-        \end{equation}
-    \end{proposition}
-    %
-    This result goes towards an explanation of the appearance of factorization homology over higher spheres in the classification statement of \Cref{thm:classif_disk_d_under_n*_alg}.
-\end{remark}
+% Generate bibliography
+\newpage
+\printbibliography
 

### 2024-09-05 sections/3algebras.tex
Finished writting up lem:Lan_preserve_colim and prepared main_theorem.tex that encapsulates the main definitions and results.

--- 2024-09-05 sections/3algebras.tex
@@
 \begin{lemma}\label{lem:Lan_preserve_colim}
-    Let $F: \mathscr{D} \xrightarrow{} \catC$ and $\iota: \mathscr{D} \xrightarrow{} \mathscr{M}$ be functors of (locally small) $\infty$-categories, where $\mathscr{M}$ and $\catC$ are cocomplete.
+    Let $F: \mathscr{D} \xrightarrow{} \catC$ and $\iota: \mathscr{D} \xrightarrow{} \mathscr{M}$ be functors of $\infty$-categories, where $\mathscr{D}$ is essentially small, while $\mathscr{M}$ and $\catC$ are locally small and cocomplete.
 Let $L_{\iota} F: \mathscr{M} \xrightarrow{} \catC$ be the left Kan extension of $F$ along $\iota$.
@@
 \begin{proof}
-    First consider the special case when $(\iota: \mathscr{D} \xrightarrow{} \mathscr{M}) = (y_{\mathscr{D}}: \mathscr{D} \xrightarrow{} \mathsf{PShv}(\mathscr{D}))$ the Yoneda embedding of $\mathscr{D}$.
-We will see that in this case, $L_{y_{\mathscr{D}}} F$ is colimit preserving because it is a left adjoint to the functor
-    %
-    \begin{equation}
-        T_F: \catC \xrightarrow{y_{\catC}} \mathsf{PShv} (\catC) \xrightarrow{F^*} \mathsf{PShv} (\mathscr{D}).
-    \end{equation}
-    %
-    Indeed, let $X \simeq y_{\mathscr{D}} (d)$ be a representable presheaf, then there are maps of morphism spaces
-    %
-    \begin{align}
-        \mathsf{Hom}_{\catC} (L_{y_{\mathscr{D}}} F (X), c) &\xrightarrow[\simeq]{} \mathsf{Hom}_{\catC} (F (d), c) \xrightarrow[\simeq]{y_{\mathscr{C}}} \mathsf{Hom}_{\mathsf{PShv}(\catC)} (y_{\catC}(F(d)), y_{\catC}(c))\notag\\ &\xrightarrow{F^*} \mathsf{Hom}_{\mathsf{PShv}(\mathscr{D})} (F^*(y_{\catC}(F(d))), T_F(c)) \xrightarrow[\simeq]{} \mathsf{Hom}_{\mathsf{PShv}(\mathscr{D})} (X, T_F(c)).
-    \end{align}
-    %
-    The Yoneda embedding $y_{\mathscr{D}}$ is a dense functor, so the above argument holds
-
-    {\color{red} Proof of being adjoint}
-
-    In the general situation where $\iota$ is not necessarily the Yoneda embedding we can partially reduce to the previous case because we can write
-    %
-    \begin{equation}
-        L_{\iota} F \simeq L_{y_{\mathscr{D}}}F \circ L_{\iota} y_{\mathscr{D}}.
-    \end{equation}
-    %
-    Namely, this is because we know that $L_{y_{\mathscr{D}}} F$ preserves colimits, and by the assumptions in the lemma, $L_{\iota} F$ and $L_{\iota} y_{\mathscr{D}}$ are computed pointwise, as colimits over the same indexing $\infty$-category.
-
-    Finally, we claim that there is an equivalence of functors
-    %
-    \begin{equation}
-        \Big( L_{\iota} y_{\mathscr{D}} \simeq T_{\iota} \Big) \in \mathsf{Fun}(\mathscr{M}, \mathsf{PShv}(\mathscr{D})) 
-    \end{equation}
-
-    {\color{red} Proof of functor equivalence}
-
+    We use the standard notation $y_{\mathscr{X}}=h_\bullet\colon\mathscr{X}\to\mathsf{PShv}(\mathscr{X})$ for `the' covariant Yoneda embedding of a locally small $\infty$-category $\mathscr{X}$ (see \cite[\href{https://kerodon.net/tag/03NF}{03NF},\href{https://kerodon.net/tag/03N2}{03N2}]{lurie_kerodon}).
+First, note that a left Kan extension of type
+    %
+    \begin{equation}
+        L_{y_{\mathscr{D}}}F \colon \mathsf{PShv}(\mathscr{D}) \xrightarrow{\ \ \ \ } \mathscr{C}
+    \end{equation}
+    %
+    preserves colimits as a consequence of \cite[\href{https://kerodon.net/tag/03WH}{03WH}]{lurie_kerodon}. Next, we claim that there is an equivalence
+    %
+    \begin{equation}\label{WZUZC5F}
+        L_{\iota}F \simeq L_{y_{\mathscr{D}}}F \circ L_{\iota}y_{\mathscr{D}}
+    \end{equation}
+    %
+    as functors $\mathscr{M} \to \mathscr{C}$. Indeed, consider the diagram
+    % 
+    \begin{equation}
+        \begin{tikzcd}[sep = large]
+            & \mathscr{D}\ar[dl,"{\iota}"']\ar[dr,"{F}"]\ar[d,"{y_{\mathscr{D}}}"]\\
+            \mathscr{M}\ar[rr,bend right=40,"{L_{\iota}F}"']\ar[r,"{L_{\iota}y_{\mathscr{D}}}"'] &[4em] \mathsf{PShv}(\mathscr{D})\ar[r,"{L_{y_{\mathscr{D}}}F}"'] & \mathscr{C},
+        \end{tikzcd}
+    \end{equation}
+    %
+    and note that by \cite[\href{https://kerodon.net/tag/03W9}{03W9},\href{https://kerodon.net/tag/03WH}{03WH}]{lurie_kerodon} there is an equivalence (actually even an isomorphism) $L_{y_{\mathscr{D}}}F \circ y_{\mathscr{D}} \simeq F$ which commutes the right triangle.
+Consequently, using \cite[\href{https://kerodon.net/tag/02YH}{02YH}]{lurie_kerodon}, we have $L_{\iota}F \simeq L_{\iota}(L_{y_{\mathscr{D}}}F \circ y_{\mathscr{D}})$.
+Since $L_{y_{\mathscr{D}}}F$ preserves colimits, we have $L_{\iota}(L_{y_{\mathscr{D}}}F \circ y_{\mathscr{D}})\simeq L_{y_{\mathscr{D}}}F \circ L_{\iota}y_{\mathscr{D}}$, obtaining \Cref{WZUZC5F}.
+
+    Finally, we claim
+    %
+    \begin{equation}\label{D9NQYMT}
+        L_{\iota}y_{\mathscr{D}} \simeq T_{\iota} := \iota^* \circ y_{\mathscr{M}}
+    \end{equation}
+    %
+    as functors $\mathscr{M} \to \mathsf{PShv}(\mathscr{D})$, which will imply the Lemma by \Cref{WZUZC5F}.
+By \cite[\href{https://kerodon.net/tag/03WN}{03WN}]{lurie_kerodon} we have the following diagram in which the triangle commutes
+    %
+    \begin{equation}
+        \begin{tikzcd}
+            \mathscr{M} \arrow[r, "y_{\mathscr{M}}"] & \mathsf{PShv}(\mathscr{M}) \arrow[r, "\iota^*"] \arrow[d, "\top", phantom, very near start] & \mathsf{PShv}(\mathscr{D}) \arrow[ll, "H", bend left] \\
+            & {} & \mathscr{D} \arrow[u, "y_{\mathscr{D}}"'] \arrow[llu, "\iota", bend left]
+            \end{tikzcd},
+    \end{equation}
+    %
+    so that $H$ is a left adjoint to $\iota^* \circ y_{\mathscr{M}}$.
+Being a right adjoint, we can write $\iota^* \circ y_{\mathscr{M}}$ as a left Kan extension, which allows for the following calculation
+    %
+    \begin{equation}
+        \iota^* \circ y_{\mathscr{M}} \simeq L_{H}\mathrm{id}_{\mathsf{PShv}(\mathscr{D})} \simeq L_{H}(L_{y_{\mathscr{D}}} y_{\mathscr{D}}) \simeq L_{H \circ y_{\mathscr{D}}}(\mathscr{D}) \simeq L_{\iota}(y_\mathscr{D}),
+    \end{equation}
+    %
+    where for the second equivalence we used the fact that $y_{\mathscr{D}}$ is a dense functor \cite[\href{https://kerodon.net/tag/03W2}{03W2}]{lurie_kerodon} (using the definition of dense functor as in \cite[\href{https://kerodon.net/tag/03VP}{03VP}]{lurie_kerodon}) and in the third equivalence we used \cite[\href{https://kerodon.net/tag/031M}{031M}]{lurie_kerodon}.
 \end{proof}

### 2024-09-13 sections/3algebras.tex
Put additivity in new section for ease of access.

@@
 Forgetting local constancy, the proof, of course, applies to factorization algebras of all flavors, however for the types that don't detect the stratified structure the above functor is even an equivalence, and not just fully-faithful, and is of no interest.
-\end{remark}
-
-\subsection{Additivity of \texorpdfstring{$\lcfa$}{lcfa}s on Stratified Spaces}
-
-In the special case of product spaces $X \times Y$, from the previous discussion we now know that the projections $\pi_1: X \times Y \rightarrow X$ and $\pi_2: X \times Y \rightarrow Y$, give us pushforwards.
-This is true even in the locally constant case since the projections are (even trivial) fiber bundles, which is a concept that is a special case of constructible bundles.
-For $\pi_1$, for example, this essentially uses the fact that if we can evaluate all open sets of $X \times Y$ then we can definitely evaluate the open sets that look like $U \times Y$, with $U \subset X$ an open set.
-But, in fact, we can do even more, because we can even evaluate the more granular open subsets $U \times V$ with $U \subset X$ and $V \subset Y$ opens.
-To capture this idea in formal terms we claim:
-%
-\begin{proposition}\label{prop:exp_of_products}
-    Let $X$ and $Y$ be topological spaces.
-There is a functor from the $\infty$-category of prefactorization algebras on the product $X \times Y$ to the $\infty$-category of prefactorization algebras on $X$ valued in the $\infty$-category of prefactorization algebras on $Y$
-    %
-    \begin{equation}
-        \bar{\pi}: \alg{\opens(X \times Y)}(\catC) \xrightarrow{\qquad} \alg{\opens(X)} (\alg{\opens(Y)} (\catC)).
-    \end{equation}
-    %
-    This functor descends to factorization algebras too
-    %
-    \begin{equation}
-        \bar{\pi}: \falg_{X \times Y}(\catC) \xrightarrow{\qquad} \falg_{X}(\falg_{Y}(\catC)).
-    \end{equation}
-\end{proposition}
-
-\begin{remark}
-    The conditions we imposed on $\catC$ allowed us, in \Cref{rem:sym_mon_inheritance}, to inherit a symmetric monoidal structure on the $\infty$-categories of factorization algebras of all varieties.
-It also allowed us to inherit the existence of colimits.
-This is the reason why the above can even be stated.
-\end{remark}
-
-\begin{proof}
-    Indeed, given opens $U \subset X$ and $V \subset Y$, the values we assign are $(\bar{\pi}F) (U)(V) = F(U \times V)$.
-Fixing an open subset $U \subset X$, we obviously get a prefactorization algebra $(\pi_2|_U)_* (F|_U) \in \alg{\opens(Y)}$ by pushing forward with $\pi_2|_U: U \times Y \rightarrow Y$, which shows that $\bar{\pi}F$ is valued in $\alg{\opens(Y)}$.
-The only thing left to show is that $\bar{\pi} F$ has the structure of a prefactorization algebra on $X$.
-To do this, for each multi-morphism $(\{ U_i \}_{i \in I} \rightarrow U) \in \opens(X)$ we assign a map $\bar{\pi}F (\{ U_i \}_{i \in I}, U)$ of factorization algebras on $Y$.
-Such an algebra map is specified by giving its value on all opens of $Y$ separately.
-We can thus assign
-    %
-    \begin{equation}
-        \bar{\pi}F (\{ U_i \}_{i \in I}, U)(V) = F(\{ U_i \times V \}_{i \in I}, U \times V),
-    \end{equation}
-    %
-    which uses the projections $\pi_1|_V : X \times V \rightarrow X$ to assign $\pi_1|_V^{-1}(U) = U \times V$.
-
-    It is not hard to check that the above also holds for the example of factorization algebras on topological spaces, by using \cite[\S7.2]{cg2016}.
-However, we'll focus on manifolds, in which case, the construction from above immediately works since we now have to do it for $\disk[r]_{/X}$ instead of $\mfld[r]_{/X}$.
-The only things to mention is that products of disks are again disks \cite[cor.3.4.9]{aft_localstrut}.
-\end{proof}
-
-\begin{theorem}[Additivity]\label{thm:additivity_lc}
-    Let $M$ and $N$ be stratified manifolds. There is an equivalence of $\infty$-operads
-    %
-    \begin{equation}
-        \disk_{/M} \otimes \disk_{/N} \xrightarrow{\ \ \simeq \ \ } \disk_{/M \times N},
-    \end{equation}
-    %
-    between the tensor product of $\infty$-operads $\disk_{/M}$ and $\disk_{/N}$ and the $\infty$-operad $\disk_{/M \times N}$.
-In particular, there is an equivalence of $\infty$-categories of algebras
-    %
-    \begin{equation}
-        \bar{\pi}: \lcfa_{M \times N}(\catC) \xrightarrow{\ \ \simeq \ \ } \lcfa_{M}(\lcfa_{N}(\catC)),
-    \end{equation}
-    which can be seen to be induced by the functor $\bar{\pi}$.
-\end{theorem}
-
-\begin{remark}
-    A version of the above theorem also appears as \cite[prop.18]{ginot2015}.
-The equivalence proven there is for the case of smooth manifolds and relies on the local proof of \cite{lurie_ha} for $\mathbb{R}^n$.
-The statement at the level of $\infty$-operads is slightly stronger and, using \Cref{thm:disk_alg=lcfa}, it implies the statement for factorization algebras.
-This $\infty$-operadic statement, again for smooth manifolds, is found in \cite[ex.5.4.5.5]{lurie_ha}.
-\end{remark}
-
-\begin{proof}
-    Following \cite[\S.2.2.5]{lurie_ha} the tensor product of $\infty$-operads is defined through a universal property.
-Namely, we define a bifunctor of $\infty$-operads to be a map $f: \mathscr{O}_1 \times \mathscr{O}_2 \xrightarrow{} \mathscr{O}$ such that:
-    %
-    \begin{enumerate}
-        \item The diagram
-        %
-        \begin{equation}
-            \begin{tikzcd}
-                \mathscr{O}_1 \times \mathscr{O}_2 \arrow[r, "f"] \arrow[d] & \mathscr{O} \arrow[d] \\
-                \mathsf{Fin}_* \times \mathsf{Fin}_* \arrow[r, "\wedge"] & \mathsf{Fin}_*
-            \end{tikzcd}
-        \end{equation}
-        %
-        commutes, and
-        \item $f$ sends pairs of inert morphisms in $\mathscr{O}_1$ and $\mathscr{O}_2$ to inert morphisms in $\mathscr{O}$.
-    \end{enumerate}
-    %
-    We denote the full $\infty$-subcategory of $\mathsf{Fun}_{\mathsf{Fin}_*}(\mathscr{O}_1 \times \mathscr{O}_2, \mathscr{O})$ consisting of the bifunctors of $\infty$-operads by $\mathsf{BiFunc}(\mathscr{O}_1, \mathscr{O}_2; \mathscr{O})$.
-The universal property of the tensor product is then that it is the $\infty$-operad $\mathscr{O}_1 \otimes \mathscr{O}_2$ together with a bifunctor of $\infty$-operads $f: \mathscr{O}_1 \times \mathscr{O}_2 \xrightarrow{} \mathscr{O}_1 \otimes \mathscr{O}_2$ such that composition with $f$ determines an equivalence
-    %
-    \begin{equation}
-        \alg{\mathscr{O}_1 \otimes \mathscr{O}_2} (\mathscr{O}) \xrightarrow{\ \ \simeq \ \ } \mathsf{BiFunc}(\mathscr{O}_1, \mathscr{O}_2; \mathscr{O}),
-    \end{equation}
-    %
-    for every $\infty$-operad $\mathscr{O}$\footnote{More details about the construction, its existence, and the fact that it captures a nontrivial concept can be found in the provided reference.}.
-
-    For us this means that we can show the desired equivalence of $\infty$-operads if we provide a bifunctor of $\infty$-operads $\disk_{/M} \times \disk_{/N} \xrightarrow{} \disk_{/M \times N}$ that is an equivalence.
-Our candidate bifunctor for this purpose will be $\times$, the product of stratified spaces.
-We now explain what this means on a technical level.
-
-    By \Cref{rem:details_disk/M} the definition of $\disk_{/M}$ as an $\infty$-operad is given by the pullback
-    %
-    \begin{equation}
-        \begin{tikzcd}
-            \disk_{/M} \arrow[rd, phantom, "\ulcorner", very near start] \arrow[r] \arrow[d] & (\disk_{/M})^{\amalg} \arrow[d] \\
-            \disk(\bsc) \arrow[r] & \disk(\bsc)^{\amalg}
-        \end{tikzcd},
-    \end{equation}
-    %
-    where on the right-hand side $\disk_{/M}$ and $\disk(\bsc)$ are appearing in their role as $\infty$-categories through \cite[Con.2.4.3.1]{lurie_ha}, while on the left-hand side they're appearing in their role as $\infty$-operads.
-We note here that the construction of $\mathscr{O}^{\amalg}$ for any $\infty$-category $\mathscr{O}$ is given through a universal property from which it immediately follows that $\mathscr{O}_1^{\amalg} \times \mathscr{O}_2^{\amalg} \simeq (\mathscr{O}_1 \times \mathscr{O}_2)^{\amalg}$.
-Keeping this in mind together with the fact that products and pullbacks commute we can draw the following commutative diagram
-    %
-    \begin{equation}
-        \begin{tikzcd}[column sep = 25]
-            \disk_{/M} \times \disk_{/N} \arrow[rd, phantom, "\ulcorner", very near start] \arrow[r] \arrow[d] & (\disk_{/M})^{\amalg} \times (\disk_{/N})^{\amalg} \arrow[r, "\simeq"] \arrow[d] & (\disk_{/M} \times \disk_{/N})^{\amalg} \arrow[d] \\
-            \disk(\bsc) \times \disk(\bsc) \arrow[r] & \disk(\bsc)^{\amalg} \times \disk(\bsc)^{\amalg} \arrow[r, "\simeq"] & (\disk(\bsc) \times \disk(\bsc))^{\amalg}  
-        \end{tikzcd}.
-    \end{equation}
-    %
-    Since $\disk_{/M \times N}$ is also given by a pullback, to provide an equivalence of $\infty$-operads $\disk_{/M} \times \disk_{/N} \xrightarrow{} \disk_{/M \times N}$ it is then sufficient to provide a commutative diagram of equivalences of $\infty$-operads
-    %
-    \begin{equation}
-        \begin{tikzcd}
-            \disk(\bsc) \times \disk(\bsc) \arrow[r] \arrow[d, "\simeq"] & (\disk(\bsc) \times \disk(\bsc))^{\amalg} \arrow[d, "\simeq"] & (\disk_{/M} \times \disk_{/N})^{\amalg} \arrow[l] \arrow[d, "\simeq"] \\
-            \disk(\bsc) \arrow[r] & \disk(\bsc)^{\amalg} & (\disk_{/M \times N})^{\amalg} \arrow[l]
-        \end{tikzcd}
-    \end{equation}
-    %
-    Looking back at the construction \cite[Con.2.4.3.1]{lurie_ha} of $\mathscr{O}^{\coprod}$, since it is given by a universal property we see that an equivalence of $\infty$-categories $\mathscr{O}_1 \simeq \mathscr{O}_2$ implies an equivalence of $\infty$-operads $\mathscr{O}_1^{\amalg} \simeq \mathscr{O}_2^{\amalg}$ such that the left-hand square in the above diagram would come for free.
-With this the ingredients we need are:
-    %
-    \begin{enumerate}
-        \item an equivalence of $\infty$-operads
-        %
-        \begin{equation}
-            \disk(\bsc) \times \disk(\bsc) \xrightarrow[\ \ \simeq \ \ ]{\times} \disk(\bsc),
-        \end{equation}
-        %
-        \item an equivalence, now only, of $\infty$-categories
-        %
-        \begin{equation}
-            \disk_{/M} \times \disk_{/N} \xrightarrow[\ \ \simeq \ \ ]{\times} \disk_{/M \times N},
-        \end{equation}
-        %
-        \item such that there is a commutative diagram of $\infty$-categories
-        %
-        \begin{equation}
-            \begin{tikzcd}
-                \disk_{/M} \times \disk_{/N} \arrow[r, "\times", "\simeq"'] \arrow[d] & \disk_{/M \times N} \arrow[d] \\
-                \disk(\bsc) \times \disk(\bsc) \arrow[r, "\times", "\simeq"'] & \disk(\bsc)
-            \end{tikzcd},
-        \end{equation}
-        %
-        where we have forgotten the $\infty$-operad equivalence down to an $\infty$-category equivalence.
-    \end{enumerate}
-    %
-    In the above we have already used the notation $\times$ to express an idea about what the maps we will provide are.
-Though there is abuse of notation it is clear from context which map $\times$ we want.
-Since the vertical maps are the canonical forgetful functors it will be clear from the construction that (3) is satisfied.
-
-    To get the data of (2) (..... reduce to $\bsc$). So we need to provide an equivalence of $\infty$-categories
-    %
-    \begin{equation}\label{eq:b/M_x_b/N=b/MxN}
-        \bsc_{/M} \times \bsc_{/N} \xrightarrow{\times} \bsc_{/M \times N}.
-    \end{equation}
-
-    To get (1), we remember that as an $\infty$-operad $\disk(\bsc)$ is, in fact, the free symmetric monoidal $\infty$-category generated by $\bsc$, thus it suffices to provide an equivalence of $\infty$-categories
-    %
-    \begin{equation}
-        \bsc \times \bsc \xrightarrow[\ \ \simeq \ \ ]{\times} \bsc.
-    \end{equation}
-    %
-    Remembering that $\bsc$ has a terminal object $*$ so that $\bsc_{/*} \simeq \bsc$, this equivalence is just a special case of \Cref{eq:b/M_x_b/N=b/MxN} in the case when $M = N = *$.
-
-    The $\infty$-category $\bsc_{/M}$ is also known, by definition, as $\mathsf{Entr(M)}$, the enter-path $\infty$-category of the stratified manifold $M$.
-By \cite[Lem.3.3.9]{afr_homhyp} this is equivalent to the opposite $\infty$-category of the exit-path $\infty$-category of $M$.
-By \cite[Obs.3.3.3]{afr_homhyp} the equivalence
-    %
-    \begin{equation}
-        \mathsf{Exit}(M) \times \mathsf{Exit}(N) \xrightarrow[\ \ \simeq \ \ ]{\times} \mathsf{Exit}(M \times N)
-    \end{equation}
-    %
-    is immediate.
-
-    To complete the proof we only have to check that $\times: \disk_{/M} \times \disk_{/N} \xrightarrow{} \disk_{M \times N}$ satisfies the conditions to qualify as a bifunctor of $\infty$-operads.
-
-    ....
-
-    The equivalence of $\infty$-operads $\disk_{/M} \otimes \disk_{/N} \xrightarrow{\ \ \simeq \ \ } \disk_{/M \times N}$ implies an equivalence at the level of $\alg{\disk_{/M}}$, which together with \Cref{thm:disk_alg=lcfa} gives rise to the equivalence of factorization algebras in the theorem statement.
-That this is related to the functor $\bar{\pi}$ can be seen by inspection of the objects and morphisms.
-\end{proof}
-
-\begin{remark}
-    At the pointwise level of evaluating specific opens this statement is related to the Fubini theorem for factorization homology \cite[cor.2.29]{aft_fhstrat}.
-The notation used in the citation is technically abusive because factorization homology is evaluating lower dimensional manifolds, but it is clear from the context that this is to be understood exactly as the evaluation of the pushforward factorization algebra on the lower dimensional manifold (see \Cref{rem:fh_is_pushingforward}).
-\end{remark}
-
-\begin{example}
-    We can view a Euclidean space $\mathbb{R}^{m+n}$ as a product space $\mathbb{R}^m \times \mathbb{R}^n$, in which case \Cref{thm:additivity_lc} specializes to give the famous result of Dunn additivity \cite{dunn1988} which can be found in the following form in \cite{lurie_ha}:
-    %
-    \begin{proposition}\label{prop:dunn_additivity}
-        There is an equivalence of $\infty$-categories
-        %
-        \begin{equation}
-            \alg{\mathbb{E}_{n + m}} (\catC) \xrightarrow{\ \ \simeq \ \ } \alg{\mathbb{E}_n} (\alg{\mathbb{E}_m} (\catC)).
-        \end{equation}
-    \end{proposition}
-\end{example}
-
-\begin{remark}
-    The proof of \Cref{thm:additivity_lc}, when specialized to ordinary manifolds, as given in \cite{ginot2015} actually depends on Dunn additivity to work, however the proof presented above and the one in \cite{lurie_ha} are both independent of this special case.
 \end{remark}

### 2024-09-13 sections/4additivity.tex
Put additivity in new section for ease of access.

\documentclass[../text.tex]{subfiles}

\begin{document}

\section{Additivity of \texorpdfstring{$\lcfa$}{lcfa}s on Stratified Spaces}

In the special case of product spaces $X \times Y$, from the previous discussion we now know that the projections $\pi_1: X \times Y \rightarrow X$ and $\pi_2: X \times Y \rightarrow Y$, give us pushforwards. This is true even in the locally constant case since the projections are (even trivial) fiber bundles, which is a concept that is a special case of constructible bundles. For $\pi_1$, for example, this essentially uses the fact that if we can evaluate all open sets of $X \times Y$ then we can definitely evaluate the open sets that look like $U \times Y$, with $U \subset X$ an open set. But, in fact, we can do even more, because we can even evaluate the more granular open subsets $U \times V$ with $U \subset X$ and $V \subset Y$ opens. To capture this idea in formal terms we claim:
%
\begin{proposition}\label{prop:exp_of_products}
    Let $X$ and $Y$ be topological spaces. There is a functor from the $\infty$-category of prefactorization algebras on the product $X \times Y$ to the $\infty$-category of prefactorization algebras on $X$ valued in the $\infty$-category of prefactorization algebras on $Y$
    %
    \begin{equation}
        \bar{\pi}: \alg{\opens(X \times Y)}(\catC) \xrightarrow{\qquad} \alg{\opens(X)} (\alg{\opens(Y)} (\catC)).
    \end{equation}
    %
    This functor descends to factorization algebras too
    %
    \begin{equation}
        \bar{\pi}: \falg_{X \times Y}(\catC) \xrightarrow{\qquad} \falg_{X}(\falg_{Y}(\catC)).
    \end{equation}
\end{proposition}

\begin{remark}
    The conditions we imposed on $\catC$ allowed us, in \Cref{rem:sym_mon_inheritance}, to inherit a symmetric monoidal structure on the $\infty$-categories of factorization algebras of all varieties. It also allowed us to inherit the existence of colimits. This is the reason why the above can even be stated.
\end{remark}

\begin{proof}
    Indeed, given opens $U \subset X$ and $V \subset Y$, the values we assign are $(\bar{\pi}F) (U)(V) = F(U \times V)$. Fixing an open subset $U \subset X$, we obviously get a prefactorization algebra $(\pi_2|_U)_* (F|_U) \in \alg{\opens(Y)}$ by pushing forward with $\pi_2|_U: U \times Y \rightarrow Y$, which shows that $\bar{\pi}F$ is valued in $\alg{\opens(Y)}$. The only thing left to show is that $\bar{\pi} F$ has the structure of a prefactorization algebra on $X$. To do this, for each multi-morphism $(\{ U_i \}_{i \in I} \rightarrow U) \in \opens(X)$ we assign a map $\bar{\pi}F (\{ U_i \}_{i \in I}, U)$ of factorization algebras on $Y$. Such an algebra map is specified by giving its value on all opens of $Y$ separately. We can thus assign
    %
    \begin{equation}
        \bar{\pi}F (\{ U_i \}_{i \in I}, U)(V) = F(\{ U_i \times V \}_{i \in I}, U \times V),
    \end{equation}
    %
    which uses the projections $\pi_1|_V : X \times V \rightarrow X$ to assign $\pi_1|_V^{-1}(U) = U \times V$.

    It is not hard to check that the above also holds for the example of factorization algebras on topological spaces, by using \cite[\S7.2]{cg2016}. However, we'll focus on manifolds, in which case, the construction from above immediately works since we now have to do it for $\disk[r]_{/X}$ instead of $\mfld[r]_{/X}$. The only things to mention is that products of disks are again disks \cite[cor.3.4.9]{aft_localstrut}.
\end{proof}

\begin{theorem}[Additivity]\label{thm:additivity_lc}
    Let $M$ and $N$ be stratified manifolds. There is an equivalence of $\infty$-operads
    %
    \begin{equation}
        \disk_{/M} \otimes \disk_{/N} \xrightarrow{\ \ \simeq \ \ } \disk_{/M \times N},
    \end{equation}
    %
    between the tensor product of $\infty$-operads $\disk_{/M}$ and $\disk_{/N}$ and the $\infty$-operad $\disk_{/M \times N}$. In particular, there is an equivalence of $\infty$-categories of algebras
    %
    \begin{equation}
        \bar{\pi}: \lcfa_{M \times N}(\catC) \xrightarrow{\ \ \simeq \ \ } \lcfa_{M}(\lcfa_{N}(\catC)),
    \end{equation}
    which can be seen to be induced by the functor $\bar{\pi}$.
\end{theorem}

\begin{remark}
    A version of the above theorem also appears as \cite[prop.18]{ginot2015}. The equivalence proven there is for the case of smooth manifolds and relies on the local proof of \cite{lurie_ha} for $\mathbb{R}^n$. The statement at the level of $\infty$-operads is slightly stronger and, using \Cref{thm:disk_alg=lcfa}, it implies the statement for factorization algebras. This $\infty$-operadic statement, again for smooth manifolds, is found in \cite[ex.5.4.5.5]{lurie_ha}.
\end{remark}

\begin{proof}
    Following \cite[\S.2.2.5]{lurie_ha} the tensor product of $\infty$-operads is defined through a universal property. Namely, we define a bifunctor of $\infty$-operads to be a map $f: \mathscr{O}_1 \times \mathscr{O}_2 \xrightarrow{} \mathscr{O}$ such that:
    %
    \begin{enumerate}
        \item The diagram
        %
        \begin{equation}
            \begin{tikzcd}
                \mathscr{O}_1 \times \mathscr{O}_2 \arrow[r, "f"] \arrow[d] & \mathscr{O} \arrow[d] \\
                \mathsf{Fin}_* \times \mathsf{Fin}_* \arrow[r, "\wedge"] & \mathsf{Fin}_*
            \end{tikzcd}
        \end{equation}
        %
        commutes, and
        \item $f$ sends pairs of inert morphisms in $\mathscr{O}_1$ and $\mathscr{O}_2$ to inert morphisms in $\mathscr{O}$.
    \end{enumerate}
    %
    We denote the full $\infty$-subcategory of $\mathsf{Fun}_{\mathsf{Fin}_*}(\mathscr{O}_1 \times \mathscr{O}_2, \mathscr{O})$ consisting of the bifunctors of $\infty$-operads by $\mathsf{BiFunc}(\mathscr{O}_1, \mathscr{O}_2; \mathscr{O})$. The universal property of the tensor product is then that it is the $\infty$-operad $\mathscr{O}_1 \otimes \mathscr{O}_2$ together with a bifunctor of $\infty$-operads $f: \mathscr{O}_1 \times \mathscr{O}_2 \xrightarrow{} \mathscr{O}_1 \otimes \mathscr{O}_2$ such that composition with $f$ determines an equivalence
    %
    \begin{equation}
        \alg{\mathscr{O}_1 \otimes \mathscr{O}_2} (\mathscr{O}) \xrightarrow{\ \ \simeq \ \ } \mathsf{BiFunc}(\mathscr{O}_1, \mathscr{O}_2; \mathscr{O}),
    \end{equation}
    %
    for every $\infty$-operad $\mathscr{O}$\footnote{More details about the construction, its existence, and the fact that it captures a nontrivial concept can be found in the provided reference.}.

    For us this means that we can show the desired equivalence of $\infty$-operads if we provide a bifunctor of $\infty$-operads $\disk_{/M} \times \disk_{/N} \xrightarrow{} \disk_{/M \times N}$ that is an equivalence. Our candidate bifunctor for this purpose will be $\times$, the product of stratified spaces. We now explain what this means on a technical level.

    By \Cref{rem:details_disk/M} the definition of $\disk_{/M}$ as an $\infty$-operad is given by the pullback
    %
    \begin{equation}
        \begin{tikzcd}
            \disk_{/M} \arrow[rd, phantom, "\ulcorner", very near start] \arrow[r] \arrow[d] & (\disk_{/M})^{\amalg} \arrow[d] \\
            \disk(\bsc) \arrow[r] & \disk(\bsc)^{\amalg}
        \end{tikzcd},
    \end{equation}
    %
    where on the right-hand side $\disk_{/M}$ and $\disk(\bsc)$ are appearing in their role as $\infty$-categories through \cite[Con.2.4.3.1]{lurie_ha}, while on the left-hand side they're appearing in their role as $\infty$-operads. We note here that the construction of $\mathscr{O}^{\amalg}$ for any $\infty$-category $\mathscr{O}$ is given through a universal property from which it immediately follows that $\mathscr{O}_1^{\amalg} \times \mathscr{O}_2^{\amalg} \simeq (\mathscr{O}_1 \times \mathscr{O}_2)^{\amalg}$. Keeping this in mind together with the fact that products and pullbacks commute we can draw the following commutative diagram
    %
    \begin{equation}
        \begin{tikzcd}[column sep = 25]
            \disk_{/M} \times \disk_{/N} \arrow[rd, phantom, "\ulcorner", very near start] \arrow[r] \arrow[d] & (\disk_{/M})^{\amalg} \times (\disk_{/N})^{\amalg} \arrow[r, "\simeq"] \arrow[d] & (\disk_{/M} \times \disk_{/N})^{\amalg} \arrow[d] \\
            \disk(\bsc) \times \disk(\bsc) \arrow[r] & \disk(\bsc)^{\amalg} \times \disk(\bsc)^{\amalg} \arrow[r, "\simeq"] & (\disk(\bsc) \times \disk(\bsc))^{\amalg}  
        \end{tikzcd}.
    \end{equation}
    %
    Since $\disk_{/M \times N}$ is also given by a pullback, to provide an equivalence of $\infty$-operads $\disk_{/M} \times \disk_{/N} \xrightarrow{} \disk_{/M \times N}$ it is then sufficient to provide a commutative diagram of equivalences of $\infty$-operads
    %
    \begin{equation}
        \begin{tikzcd}
            \disk(\bsc) \times \disk(\bsc) \arrow[r] \arrow[d, "\simeq"] & (\disk(\bsc) \times \disk(\bsc))^{\amalg} \arrow[d, "\simeq"] & (\disk_{/M} \times \disk_{/N})^{\amalg} \arrow[l] \arrow[d, "\simeq"] \\
            \disk(\bsc) \arrow[r] & \disk(\bsc)^{\amalg} & (\disk_{/M \times N})^{\amalg} \arrow[l]
        \end{tikzcd}
    \end{equation}
    %
    Looking back at the construction \cite[Con.2.4.3.1]{lurie_ha} of $\mathscr{O}^{\coprod}$, since it is given by a universal property we see that an equivalence of $\infty$-categories $\mathscr{O}_1 \simeq \mathscr{O}_2$ implies an equivalence of $\infty$-operads $\mathscr{O}_1^{\amalg} \simeq \mathscr{O}_2^{\amalg}$ such that the left-hand square in the above diagram would come for free. With this the ingredients we need are:
    %
    \begin{enumerate}
        \item an equivalence of $\infty$-operads
        %
        \begin{equation}
            \disk(\bsc) \times \disk(\bsc) \xrightarrow[\ \ \simeq \ \ ]{\times} \disk(\bsc),
        \end{equation}
        %
        \item an equivalence, now only, of $\infty$-categories
        %
        \begin{equation}
            \disk_{/M} \times \disk_{/N} \xrightarrow[\ \ \simeq \ \ ]{\times} \disk_{/M \times N},
        \end{equation}
        %
        \item such that there is a commutative diagram of $\infty$-categories
        %
        \begin{equation}
            \begin{tikzcd}
                \disk_{/M} \times \disk_{/N} \arrow[r, "\times", "\simeq"'] \arrow[d] & \disk_{/M \times N} \arrow[d] \\
                \disk(\bsc) \times \disk(\bsc) \arrow[r, "\times", "\simeq"'] & \disk(\bsc)
            \end{tikzcd},
        \end{equation}
        %
        where we have forgotten the $\infty$-operad equivalence down to an $\infty$-category equivalence.
    \end{enumerate}
    %
    In the above we have already used the notation $\times$ to express an idea about what the maps we will provide are. Though there is abuse of notation it is clear from context which map $\times$ we want. Since the vertical maps are the canonical forgetful functors it will be clear from the construction that (3) is satisfied.

    To get the data of (2) (..... reduce to $\bsc$). So we need to provide an equivalence of $\infty$-categories
    %
    \begin{equation}\label{eq:b/M_x_b/N=b/MxN}
        \bsc_{/M} \times \bsc_{/N} \xrightarrow{\times} \bsc_{/M \times N}.
    \end{equation}

    To get (1), we remember that as an $\infty$-operad $\disk(\bsc)$ is, in fact, the free symmetric monoidal $\infty$-category generated by $\bsc$, thus it suffices to provide an equivalence of $\infty$-categories
    %
    \begin{equation}
        \bsc \times \bsc \xrightarrow[\ \ \simeq \ \ ]{\times} \bsc.
    \end{equation}
    %
    Remembering that $\bsc$ has a terminal object $*$ so that $\bsc_{/*} \simeq \bsc$, this equivalence is just a special case of \Cref{eq:b/M_x_b/N=b/MxN} in the case when $M = N = *$.

    The $\infty$-category $\bsc_{/M}$ is also known, by definition, as $\mathsf{Entr(M)}$, the enter-path $\infty$-category of the stratified manifold $M$. By \cite[Lem.3.3.9]{afr_homhyp} this is equivalent to the opposite $\infty$-category of the exit-path $\infty$-category of $M$. By \cite[Obs.3.3.3]{afr_homhyp} the equivalence
    %
    \begin{equation}
        \mathsf{Exit}(M) \times \mathsf{Exit}(N) \xrightarrow[\ \ \simeq \ \ ]{\times} \mathsf{Exit}(M \times N)
    \end{equation}
    %
    is immediate.

    To complete the proof we only have to check that $\times: \disk_{/M} \times \disk_{/N} \xrightarrow{} \disk_{M \times N}$ satisfies the conditions to qualify as a bifunctor of $\infty$-operads.

    ....

    The equivalence of $\infty$-operads $\disk_{/M} \otimes \disk_{/N} \xrightarrow{\ \ \simeq \ \ } \disk_{/M \times N}$ implies an equivalence at the level of $\alg{\disk_{/M}}$, which together with \Cref{thm:disk_alg=lcfa} gives rise to the equivalence of factorization algebras in the theorem statement. That this is related to the functor $\bar{\pi}$ can be seen by inspection of the objects and morphisms.
\end{proof}

\begin{remark}
    At the pointwise level of evaluating specific opens this statement is related to the Fubini theorem for factorization homology \cite[cor.2.29]{aft_fhstrat}. The notation used in the citation is technically abusive because factorization homology is evaluating lower dimensional manifolds, but it is clear from the context that this is to be understood exactly as the evaluation of the pushforward factorization algebra on the lower dimensional manifold (see \Cref{rem:fh_is_pushingforward}).
\end{remark}

\begin{example}
    We can view a Euclidean space $\mathbb{R}^{m+n}$ as a product space $\mathbb{R}^m \times \mathbb{R}^n$, in which case \Cref{thm:additivity_lc} specializes to give the famous result of Dunn additivity \cite{dunn1988} which can be found in the following form in \cite{lurie_ha}:
    %
    \begin{proposition}\label{prop:dunn_additivity}
        There is an equivalence of $\infty$-categories
        %
        \begin{equation}
            \alg{\mathbb{E}_{n + m}} (\catC) \xrightarrow{\ \ \simeq \ \ } \alg{\mathbb{E}_n} (\alg{\mathbb{E}_m} (\catC)).
        \end{equation}
    \end{proposition}
\end{example}

\begin{remark}
    The proof of \Cref{thm:additivity_lc}, when specialized to ordinary manifolds, as given in \cite{ginot2015} actually depends on Dunn additivity to work, however the proof presented above and the one in \cite{lurie_ha} are both independent of this special case. 
\end{remark}

\end{document}

### 2024-09-13 sections/6classification.tex
Put additivity in new section for ease of access.

--- 2024-04-04 sections/5classification.tex
@@
 However, it is possible that the global topology introduces some twisting of this local understanding.
-Due to \Cref{thm:gluing_lcfas} and the properties of stratified manifolds, in any particular case, it's possible to find some list of collar-gluings that reduce the problem down to the local case, but this doesn't tell us anything about the general structure.
+Due to \Cref{thm:gluing_lcfas} and the properties of stratified manifolds, in any particular case, it's possible to find some list of collar--gluings that reduce the problem down to the local case, but this doesn't tell us anything about the general structure.
 Despite this, there is a particular collar-gluing that is the obvious first step if we're looking at a general manifold $M_\Sigma$.

### 2024-09-13 sections/4additivity.tex
Outline of additivity.

@@
 
+{\color{red} The following lemmas are just an outline for a possible proof following Lurie as an example}
+
+\begin{lemma}\label{lem:slicing_disk_functor}
+    The construction of $\disk_{/M}$ elevates to a functor
+    %
+    \begin{equation}
+        \disk_{/-}: \mfld \xrightarrow{\ \ \ \ \ } \mathscr{O}\mathsf{p}_{\infty}.
+    \end{equation}
+\end{lemma}
+
 \begin{proof}
+    .....
+\end{proof}
+
+\begin{lemma}
+    The functor $\disk_{/-}$ from \Cref{lem:slicing_disk_functor} factorizes as in the commutative diagram
+    %
+    \begin{equation}
+        \begin{tikzcd}
+            \mfld \arrow[rr, "\disk_{/-}"] \arrow[dr, "\mathsf{Entr}"'] & & \mathscr{O} \mathsf{p}_{\infty} \\
+            & \cat \arrow[ur, "(-)^\sqcup ??"'] &
+        \end{tikzcd}
+    \end{equation}
+\end{lemma}
+
+\begin{proof}
+    .....
+\end{proof}
+
+\begin{proof}[Proof of \Cref{thm:additivity_lc}]
     Following \cite[\S.2.2.5]{lurie_ha} the tensor product of $\infty$-operads is defined through a universal property.
@@
 
-    The equivalence of $\infty$-operads $\disk_{/M} \otimes \disk_{/N} \xrightarrow{\ \ \simeq \ \ } \disk_{/M \times N}$ implies an equivalence at the level of $\alg{\disk_{/M}}$, which together with \Cref{thm:disk_alg=lcfa} gives rise to the equivalence of factorization algebras in the theorem statement.
+    The equivalence of $\infty$-operads $\disk_{/M} \otimes \disk_{/N} \xrightarrow{\ \ \simeq \ \ } \disk_{/M \times N}$ implies an equivalence at the level of $\alg{\disk_{/M}} (\catC)$, which together with \Cref{thm:disk_alg=lcfa} gives rise to the equivalence of factorization algebras in the theorem statement.
 That this is related to the functor $\bar{\pi}$ can be seen by inspection of the objects and morphisms.
@@
     %
-    \begin{proposition}\label{prop:dunn_additivity}
+    \begin{corollary}\label{prop:dunn_additivity}
         There is an equivalence of $\infty$-categories
@@
         \end{equation}
-    \end{proposition}
+    \end{corollary}
 \end{example}

### 2025-04-07 paperversion/paper.tex
paper version

\documentclass[]{amsart}

% from preamble ->

\usepackage[ngerman,french,british]{babel} % clashes with q.uiver/tikzcd
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{mathtools} % \coloneqq
\usepackage{amsmath}
\usepackage[outline]{contour}
\usepackage[mathscr]{euscript}
\usepackage[all,2cell,cmtip]{xy}
\usepackage{csquotes}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[
  %hidelinks
]{hyperref}
\usepackage{microtype}

% quiver ->

% `tikz-cd` is necessary to draw commutative diagrams.
\usepackage{tikz-cd}
% `amssymb` is necessary for `\lrcorner` and `\ulcorner`.
\usepackage{amssymb}
% `calc` is necessary to draw curved arrows.
\usetikzlibrary{calc}
% `pathmorphing` is necessary to draw squiggly arrows.
\usetikzlibrary{decorations.pathmorphing}

\usetikzlibrary{babel} % ADDED MYSELF, OTHERWISE CLASHES WITH TIKZ-CD KEYS -Ö

% A TikZ style for curved arrows of a fixed height, due to AndréC.
\tikzset{curve/.style={settings={#1},to path={(\tikztostart)
    .. controls ($(\tikztostart)!\pv{pos}!(\tikztotarget)!\pv{height}!270:(\tikztotarget)$)
    and ($(\tikztostart)!1-\pv{pos}!(\tikztotarget)!\pv{height}!270:(\tikztotarget)$)
    .. (\tikztotarget)\tikztonodes}},
    settings/.code={\tikzset{quiver/.cd,#1}
        \def\pv##1{\pgfkeysvalueof{/tikz/quiver/##1}}},
    quiver/.cd,pos/.initial=0.35,height/.initial=0}

% TikZ arrowhead/tail styles.
\tikzset{tail reversed/.code={\pgfsetarrowsstart{tikzcd to}}}
\tikzset{2tail/.code={\pgfsetarrowsstart{Implies[reversed]}}}
\tikzset{2tail reversed/.code={\pgfsetarrowsstart{Implies}}}
% TikZ arrow styles.
\tikzset{no body/.style={/tikz/dash pattern=on 0 off 1mm}}

% <- quiver

\usepackage[hyperref,
maxbibnames=99,
backend=biber,
%backref, %& "cit. on p.X",
%backrefstyle=none,
%style=numeric,
style=alphabetic-verb,
%citestyle=numeric,
citestyle=alphabetic-verb,
giveninits=true
%sorting=none
%citestyle=alphabetic
]{biblatex}
\DefineBibliographyStrings{english}{% %REMOVE "p." and "pp."
  page             = {},
  pages            = {},
} 
\renewbibmacro{in:}{} % gets rid of "In:[journal]"
\emergencystretch=1.5em
\addbibresource{text.bib}
\renewcommand*{\bibfont}{\footnotesize}

\usepackage{graphicx}
\usepackage{cleveref}   % use with \cref and \Cref
\usepackage{underscore} % use _ in text

%%%%%%%%%%%INCLUDING INKSCAPE %%%%%%%%%%%%%%
\usepackage{import}
\usepackage{color} % NECESSARY for inkscape for some reason
\usepackage{xifthen}

\usepackage{rotating} 
\newcommand{\incfig}[1]{%
    \def\svgwidth{0.3\columnwidth}
    \import{./figures/}{#1.pdf_tex}
}

\newcommand{\mcal}[1]{\mathcal{#1}}
\newcommand{\msc}[1]{\mathscr{#1}}
\newcommand{\msf}[1]{\mathsf{#1}}
\newcommand{\mscc}[1]{\mathbf{#1}}
\newcommand{\mrm}[1]{\mathrm{#1}}
\newcommand{\mbf}[1]{\mathbf{#1}}
\newcommand{\mbb}[1]{\mathbb{#1}}
\newcommand{\mfrak}[1]{\mathfrak{#1}}
\newcommand{\down}[3][ ]{(#2 \downarrow #3)^{#1}}
\newcommand{\paren}[1]{\left( #1 \right)}

\newcommand{\R}{\mbb{R}}
\newcommand{\Imm}{\mathrm{Im}}
\newcommand{\id}{{\mathrm{id}}}
\newcommand{\colim}{\mathrm{colim}}
\newcommand{\Hom}{\mathrm{Hom}}
\newcommand{\dfnt}{\bfseries \itshape}
\newcommand{\hyph}{{\mbox{-}}}
\newcommand{\Bred}{\mathcal{B}\mbox{-}\mathrm{red}}
\newcommand{\Yred}{Y\mbox{-}\mathrm{red}}
\newcommand{\Bopen}{\mathcal{B}\mbox{-}\mathrm{open}}
\newcommand{\Snglr}{\mathcal{S}\mathrm{nglr}}
\newcommand{\bighrule}{\vspace{\baselineskip} \hrule \hrule \hrule\vspace{\baselineskip}}
\newcommand{\solidone}{\mathbf{s}\ast_1} 
\newcommand{\Vinj}{{\mscc{V}^{\mathrm{inj}}}}
\newcommand{\Vhook}{\mscc{V}^{\hookrightarrow}}
\newcommand{\Vsim}{{\mscc{V}^{\simeq}}}
\newcommand{\Vlhook}{\mscc{V}^{\hookleftarrow}}
\newcommand{\TB}{T^{\mathcal{B}}}
\newcommand{\EX}{{\mathbf{Ex}}}
\newcommand{\Disk}{{\mathcal{D}\mathrm{isk}}}
\newcommand{\scB}{{\mathcal{B}}}
\newcommand{\OB}{{\mathbb{O}^{\mathcal{B}}}}
\newcommand{\Mnf}{{\mscc{M}\mathrm{nf}}}
\newcommand{\sfr}{{\mathbf{s}\ast}}
\newcommand{\solid}{\mathbf{s}}
\newcommand{\Bord}{{\mathrm{Bord}}}
\newcommand{\BM}{{\mathcal{B}\mathbf{M}}}
\newcommand{\pt}{{\mathrm{pt}}}
\newcommand{\falc}{{\mathrm{FA}^{\mathrm{lc}}}}
\newcommand{\stfr}{{\mathbf{st}\ast}}
\newcommand{\Tang}{{\mathcal{T}\mathrm{ang}}}
\newcommand{\opp}{{\mathrm{op}}}
\newcommand{\Opp}{{\mathrm{Op}}}
\newcommand{\Vsur}{{\mathcal{V}^{\twoheadrightarrow}}}
\newcommand{\EN}{{\mathbf{En}}}
\newcommand{\codim}{{\mathrm{codim}\,}}
\newcommand{\red}{{\text{-}\mathrm{red}}}
\newcommand{\Vect}{{\mathcal{V}}}
\newcommand{\Cinfty}{\mscc{C}\mathrm{at}_{\infty}}
\newcommand{\Sp}{{\mathcal{S}\mathrm{p}}}
\newcommand{\BhookO}{{\mathcal{B}^{\hookrightarrow}\mathrm{O}}}
\newcommand{\EhookO}{{\mathcal{E}^{\hookrightarrow}\mathrm{O}}}
\newcommand{\purp}{\color{purple}}
\newcommand{\Eop}{{\mathcal{E}^{\mathrm{op}}}}
\newcommand{\E}{{\mathcal{E}}}
\newcommand{\Tw}{{\mathrm{Tw}}}
\newcommand{\Map}{{\mathrm{Map}}}
\newcommand{\gpdinf}{{\mathcal{G}\mathrm{pd}_{\infty}}}
\newcommand{\cdon}{\[\begin{tikzcd}}
\newcommand{\cdoff}{\end{tikzcd}\]}
\newcommand{\ncdon}{\begin{equation}\begin{tikzcd}}
\newcommand{\ncdoff}{\end{tikzcd}\end{equation}}
\newcommand{\OO}{{\mathrm{O}}}
\newcommand{\pbarrow}{\ar[dr,phantom,"\ulcorner" very near start]}
\newcommand{\Gr}{{\mathrm{Gr}}}
\newcommand{\arrowedruleron}{{\vspace{5pt}{\purp\hrule\hrule\hrule}
\begin{center}\purp
	$\downarrow$
\end{center}}}
\newcommand{\arrowedruleroff}{{\begin{center}\purp
	$\uparrow$
\end{center}
\vspace{5pt}{\purp\hrule\hrule\hrule}}}
\newcommand{\blue}{\color{blue}}
\newcommand{\Sing}{{\mathrm{Sing}}}
\newcommand{\Bbox}{\mathcal{B}^{\oplus}}
\newcommand{\bbox}{B^{\oplus}}
\newcommand{\bboxop}{B^{\oplus}_{\opp}}
\newcommand{\Nerve}{{\mathrm{N}}}
\newcommand{\Ndelta}{\mathrm{N}^{\mbf{\Delta}}}
\newcommand{\Nhc}{\mathrm{N}^{\mathrm{hc}}}
\newcommand{\sSet}{\mathrm{sSet}}
\newcommand{\Cdelta}{{\mathcal{C}\mathrm{at}_{\mbf{\Delta}}}}
\newcommand{\pSh}{\mathrm{pSh}}
\newcommand{\EEx}{\mathbf{EX}}
\newcommand{\Pnsim}{\mscc{P}^{\nsim}}
\newcommand{\Phat}{\mscc{P}^{\Delta}}
\newcommand{\Pbox}{\mscc{P}^{\Box}}
\newcommand{\Nhat}{\widehat{\mathcal{N}}}
\newcommand{\Fun}{\mathrm{Fun}}
\newcommand{\Path}{\mathrm{Path}}
\newcommand{\Tangent}{\mathrm{T}}
\newcommand{\Normal}{\mathrm{N}}
\newcommand{\vfr}{\mathrm{vfr}}
\newcommand{\hty}{\mathrm{h}}
\newcommand{\evv}{\mathrm{ev}}
\newcommand{\Ar}{\mathrm{Ar}}
\newcommand{\inc}{$\infty$-category}
\newcommand{\btu}{\bigtriangleup}
\makeatletter
\newcommand{\btd}{\mathord{\mathpalette\raise@half\bigtriangledown}}
\newcommand\raise@half[2]{%
  \raisebox{.9\depth}{$\m@th#1#2$}%
}
\makeatother
\newcommand{\ashrk}{\text{\textexclamdown}}
\newcommand{\dash}{\mbox{-}}
\newcommand{\cat}[2]{\mscc{#1}\mathrm{#2}}
\newcommand{\htimes}{\times^{\mathrm{h}}}

\newcommand{\spans}{\mscc{S}^{\mrm{sp}}}
\newcommand{\OEEx}{\overrightarrow{\EEx}}
\newcommand{\Ssp}{\mscc{S}^{\mrm{sp}}}
\newcommand{\ocat}[1]{\mathrm{#1}}
\newcommand{\Ctop}{\mscc{C}\mrm{at}_{\mrm{Top}}}
\newcommand{\Tame}{\Hom^{t}}
\newcommand{\tame}{\tau}
\newcommand{\Unzip}{\mrm{Unzip}}

\numberwithin{equation}{section}

\theoremstyle{definition}
\newtheorem{definition}[equation]{Definition}%[section]
\newtheorem*{definition*}{Definition}
\newtheorem{notation}[equation]{Notation}
\newtheorem*{notation*}{Notation}
\newtheorem{construction}[equation]{Construction}
\newtheorem*{construction*}{Construction}

\theoremstyle{remark}
\newtheorem{remark}[equation]{Remark}
\newtheorem*{remark*}{Remark}
\newtheorem{example}[equation]{Example}
\newtheorem*{example*}{Example}
\newtheorem{warning}[equation]{Warning}
\newtheorem*{warning*}{Warning}
\newtheorem{convention}[equation]{Convention}
\newtheorem*{convention*}{Convention}

\theoremstyle{plain}
\newtheorem{proposition}[equation]{Proposition}
\newtheorem*{proposition*}{Proposition}
\newtheorem{theorem}[equation]{Theorem}
\newtheorem*{theorem*}{Theorem}
\newtheorem{definition-theorem}[equation]{Definition-Theorem}
\newtheorem*{definition-theorem*}{Definition-Theorem}
\newtheorem{postulate}[equation]{Postulate}
\newtheorem*{postulate*}{Postulate}
\newtheorem{lemma}[equation]{Lemma}
\newtheorem*{lemma*}{Lemma}
\newtheorem{observation}[equation]{Observation}
\newtheorem*{observation*}{Observation}
\newtheorem{corollary}[equation]{Corollary}
\newtheorem*{corollary*}{Corollary}
\newtheorem{question}[equation]{Question}
\newtheorem*{question*}{Question}

% <- from preamble

\title{{Good covers and algebras on conically smooth spaces}}
\address{University of Vienna, Faculty of Physics, Mathematical Physics Group, Boltzmanngasse 5, 1090 Vienna, Austria}
\thanks{The authors were supported by the Austrian Science Fund (FWF) through Project no.\ P 37046.}
\author{Aleksandar Ivanov}
\email{aleksandar.ivanov@univie.ac.at}
\author{\"Od\"ul Tet\.{i}k}
\email{oeduel.tetik@univie.ac.at}
\date{}

\begin{document}

\maketitle

\begin{abstract}
    We construct good covers for conically smooth spaces {\color{MidnightBlue} over depth-$1$ posets}. By a result of Karlsson--Scheimbauer--Walde, this implies that, for every such space $X$, constructible factorisation algebras on $X$ and disk algebras over $X$ coincide. We also give a simplified proof of that result.
\end{abstract}

\tableofcontents

\section{Introduction}

\subsubsection*{Acknowledgments} We thank Tashi Walde for very useful exchanges.

\section{Good covers}

\begin{definition}
    Let $X$ be a CSS. A \emph{good cover} of $X$ is an open cover $\mcal{U}$ of $X$ consisting of basics whose finite intersections are also in $\mcal{U}$.
\end{definition}

\begin{definition}
    Let $Y$ be a smooth manifold with or without boundary, equipped with a riemannian metric. We call a cover of $Y$ \emph{geodesically convex} if it consists of geodesically convex basics.
\end{definition}

%It is classical that geodesically convex covers are good. In particular, the union of geodesically convex covers of an arbitrary cover of a smooth manifold with or without boundary is good.

\begin{theorem}
    Let $X$ be a CSS {\color{MidnightBlue} over a depth-$1$ poset}. Then $X$ has a good cover.
\end{theorem}

\begin{proof}
    Without loss of generality, suppose $X$ is stratified over $[1]$ and let $M=X_0$ and $N=X_1$. Recall the blow-up of $M$, the smooth manifold
    \[
        \mrm{Unzip}\cong L\amalg_{L\times(0,\infty)}N
    \]
    with boundary $L=\partial\mrm{Unzip}$. We write $\pi\colon L\to M$ for the accompanying proper fibre bundle. Let us equip $\mrm{Unzip}$ with a riemannian metric which splits along the boundary.

    Using the paracompactness of $M$, let $\mcal{U}$ be a locally finite good cover of $M$ which trivialises $\pi$. For each $U\in\mcal{U}$, let $\epsilon_U>0$ be the radius of injectivity in the normal direction on the compact closure $\overline{U}$ so that there is a smooth embedding 
    \[
        I_U\colon \pi^{-1}U\times[0,\epsilon_U)\hookrightarrow \mrm{Unzip}
    \]
    whose restriction $I_U|_{\pi^{-1}U\times\{0\}}$ to $\pi^{-1}U\subset L$ is given by the boundary inclusion, and the path $I_U(q,-)\colon[0,\epsilon_U)\hookrightarrow \mrm{Unzip}$, for every $q\in\pi^{-1}U$, is the minimising geodesic given by the normal exponential map. More precisely, for $\nu$ the inward-pointing unit normal vector field along the boundary, we set $I_U(x,t)=\exp_x(t\nu_x)$.\footnote{A global $\epsilon$ need not exist unless $\mrm{Unzip}$ is of bounded geometry; see e.g.\ Schick \cite{schick2001bounded}.} Let 
    \[
        C=\bigcup_{U\in\mcal{U}}\mrm{Im}(I_U)
    \]
    be the induced `collar' and consider the cover
    \[  
        \mcal{C}=\{I_U(\pi^{-1}U\times[0,\delta)) : U\in\mcal{U},\ \delta\leq\epsilon_U\}
    \]
    of $C$. Let us write $C_{U,\delta}=I_U(\pi^{-1}U\times[0,\delta))\in\mcal{C}$. Note that $\mcal{C}$ is closed under finite intersections since so is $\mcal{U}$: we have $\pi^{-1}U\cap\pi^{-1}V=\pi^{-1}(U\cap V)$ and
    \[
        C_{U,\delta}\cap C_{V,\delta'}=C_{U\cap V,\min(\delta,\delta')}\in\mcal{C}
    \] 
    since $\min(\delta,\delta')\leq\epsilon_{U\cap V}$ for $\delta\leq\epsilon_U$, $\delta'\leq\epsilon_V$.

    Consider now the collection $\mcal{V}$ of those convex geodesic disks $V$ in $N$ such that $V\cap C_{U,\delta}$ is either empty or a convex geodesic disk for every $C_{U,\delta}\in\mcal{C}$. Then $\mcal{V}$ is a good cover of $N$. To prove this, it suffices to show that every $p\in C$ has a neighbourhood $V_p\in\mcal{V}$, since convex geodesic disks are closed under finite intersections and so $V\cap V'\cap C_{U,\delta}=V\cap V''\in\mcal{V}$. Let now $p\in I_U(\pi^{-1}U\times [0,\delta))\in\mcal{C}$, which uniquely determines a point $l_p=\pi(\mrm{pr}_1(p))\in\pi^{-1}U\subset L$. Let $W\subset\pi^{-1}U$ be a convex geodesic disk neighbourhood of $l_p$. Now, since $\mcal{U}$ is locally finite, so is the  cover $\widetilde{\mcal{C}}=\{I_U(\pi^{-1}U\times[0,\epsilon_U))\}$ of $C$ (which is not necessarily closed under finite intersections), so in particular $p$ is contained within finitely many members $I_{U_i}(\pi^{-1}U_i\times[0,\epsilon_i))\in\widetilde{\mcal{C}}$. We necessarily have $p\in I_{U}(\pi^{-1}U\times[0,\min_i(\epsilon_i)))$ with $U\in\{U_i\}_i$ an open satisfying $\epsilon_U=\min_i(\epsilon_i)$. Then $W\times[0,\min_i(\epsilon_i))\ni p$ is a convex geodesic half-disk since the riemannian metric on $\mrm{Unzip}$ splits along the boundary, and so we have $p\in V_p= W\times(0,\min_i(\epsilon_i))\in \mcal{V}$.

    Let us now observe that $\pi^{-1}U\cong L_p\times U$ for $p\in U$ implies that each
    \[
        C(L_p)\times U\cong U\amalg_{\pi^{-1}U}C_{U,\delta} \subseteq X
    \]
    is a basic in $X$. Thus, writing $\widehat{C_{U,\delta}}=U\amalg_{\pi^{-1}U}C_{U,\delta}$, we obtain that
    \[
        \widehat{\mcal{C}}=\{\widehat{C_{U,\delta}} : C_{U,\delta}\in \mcal{C}\}
    \]
    is a cover by basics of the `tubular neighbourhood' 
    \[
        \widehat{C}=\bigcup_{U\in\mcal{C}}\widehat{C_{U,\epsilon_U}}\subseteq X
    \]
    of $M$. It is closed intersections since so is $\mcal{C}$. Finally, since for $V\in\mcal{V}$ we have $\widehat{C_{U,\delta}}\cap V=C_{U,\delta}\cap V\in\mcal{V}$, we conclude that
    \[
        \widehat{\mcal{C}}\cup \mcal{V}
    \]
    is a good cover of $X$. 
\end{proof}

\section{A proof of...}

\printbibliography

\end{document}

### 2025-08-21 paperversion/paper.tex
localities section, clean part

@@
 \newcommand{\R}{\mbb{R}}
-\newcommand{\Imm}{\mathrm{Im}}
-\newcommand{\id}{{\mathrm{id}}}
-\newcommand{\colim}{\mathrm{colim}}
+\DeclareMathOperator{\Imm}{Im}
+\newcommand{\id}{\mathrm{id}}
 \newcommand{\Hom}{\mathrm{Hom}}
@@
 \newcommand{\hyph}{{\mbox{-}}}
-\newcommand{\Bred}{\mathcal{B}\mbox{-}\mathrm{red}}
-\newcommand{\Yred}{Y\mbox{-}\mathrm{red}}
-\newcommand{\Bopen}{\mathcal{B}\mbox{-}\mathrm{open}}
-\newcommand{\Snglr}{\mathcal{S}\mathrm{nglr}}
-\newcommand{\bighrule}{\vspace{\baselineskip} \hrule \hrule \hrule\vspace{\baselineskip}}
-\newcommand{\solidone}{\mathbf{s}\ast_1} 
-\newcommand{\Vinj}{{\mscc{V}^{\mathrm{inj}}}}
-\newcommand{\Vhook}{\mscc{V}^{\hookrightarrow}}
-\newcommand{\Vsim}{{\mscc{V}^{\simeq}}}
-\newcommand{\Vlhook}{\mscc{V}^{\hookleftarrow}}
-\newcommand{\TB}{T^{\mathcal{B}}}
-\newcommand{\EX}{{\mathbf{Ex}}}
-\newcommand{\Disk}{{\mathcal{D}\mathrm{isk}}}
-\newcommand{\scB}{{\mathcal{B}}}
-\newcommand{\OB}{{\mathbb{O}^{\mathcal{B}}}}
-\newcommand{\Mnf}{{\mscc{M}\mathrm{nf}}}
-\newcommand{\sfr}{{\mathbf{s}\ast}}
-\newcommand{\solid}{\mathbf{s}}
-\newcommand{\Bord}{{\mathrm{Bord}}}
-\newcommand{\BM}{{\mathcal{B}\mathbf{M}}}
-\newcommand{\pt}{{\mathrm{pt}}}
-\newcommand{\falc}{{\mathrm{FA}^{\mathrm{lc}}}}
-\newcommand{\stfr}{{\mathbf{st}\ast}}
-\newcommand{\Tang}{{\mathcal{T}\mathrm{ang}}}
-\newcommand{\opp}{{\mathrm{op}}}
-\newcommand{\Opp}{{\mathrm{Op}}}
-\newcommand{\Vsur}{{\mathcal{V}^{\twoheadrightarrow}}}
-\newcommand{\EN}{{\mathbf{En}}}
-\newcommand{\codim}{{\mathrm{codim}\,}}
-\newcommand{\red}{{\text{-}\mathrm{red}}}
-\newcommand{\Vect}{{\mathcal{V}}}
-\newcommand{\Cinfty}{\mscc{C}\mathrm{at}_{\infty}}
-\newcommand{\Sp}{{\mathcal{S}\mathrm{p}}}
-\newcommand{\BhookO}{{\mathcal{B}^{\hookrightarrow}\mathrm{O}}}
-\newcommand{\EhookO}{{\mathcal{E}^{\hookrightarrow}\mathrm{O}}}
-\newcommand{\purp}{\color{purple}}
-\newcommand{\Eop}{{\mathcal{E}^{\mathrm{op}}}}
-\newcommand{\E}{{\mathcal{E}}}
-\newcommand{\Tw}{{\mathrm{Tw}}}
-\newcommand{\Map}{{\mathrm{Map}}}
-\newcommand{\gpdinf}{{\mathcal{G}\mathrm{pd}_{\infty}}}
-\newcommand{\cdon}{\[\begin{tikzcd}}
-\newcommand{\cdoff}{\end{tikzcd}\]}
-\newcommand{\ncdon}{\begin{equation}\begin{tikzcd}}
-\newcommand{\ncdoff}{\end{tikzcd}\end{equation}}
-\newcommand{\OO}{{\mathrm{O}}}
-\newcommand{\pbarrow}{\ar[dr,phantom,"\ulcorner" very near start]}
-\newcommand{\Gr}{{\mathrm{Gr}}}
-\newcommand{\arrowedruleron}{{\vspace{5pt}{\purp\hrule\hrule\hrule}
-\begin{center}\purp
-	$\downarrow$
-\end{center}}}
-\newcommand{\arrowedruleroff}{{\begin{center}\purp
-	$\uparrow$
-\end{center}
-\vspace{5pt}{\purp\hrule\hrule\hrule}}}
-\newcommand{\blue}{\color{blue}}
-\newcommand{\Sing}{{\mathrm{Sing}}}
-\newcommand{\Bbox}{\mathcal{B}^{\oplus}}
-\newcommand{\bbox}{B^{\oplus}}
-\newcommand{\bboxop}{B^{\oplus}_{\opp}}
-\newcommand{\Nerve}{{\mathrm{N}}}
-\newcommand{\Ndelta}{\mathrm{N}^{\mbf{\Delta}}}
-\newcommand{\Nhc}{\mathrm{N}^{\mathrm{hc}}}
-\newcommand{\sSet}{\mathrm{sSet}}
-\newcommand{\Cdelta}{{\mathcal{C}\mathrm{at}_{\mbf{\Delta}}}}
-\newcommand{\pSh}{\mathrm{pSh}}
-\newcommand{\EEx}{\mathbf{EX}}
-\newcommand{\Pnsim}{\mscc{P}^{\nsim}}
-\newcommand{\Phat}{\mscc{P}^{\Delta}}
-\newcommand{\Pbox}{\mscc{P}^{\Box}}
-\newcommand{\Nhat}{\widehat{\mathcal{N}}}
+\newcommand{\pt}{\mathrm{pt}}
 \newcommand{\Fun}{\mathrm{Fun}}
-\newcommand{\Path}{\mathrm{Path}}
 \newcommand{\Tangent}{\mathrm{T}}
 \newcommand{\Normal}{\mathrm{N}}
-\newcommand{\vfr}{\mathrm{vfr}}
-\newcommand{\hty}{\mathrm{h}}
 \newcommand{\evv}{\mathrm{ev}}  
-\newcommand{\Ar}{\mathrm{Ar}}
-\newcommand{\inc}{$\infty$-category}
-\newcommand{\btu}{\bigtriangleup}
-\makeatletter
-\newcommand{\btd}{\mathord{\mathpalette\raise@half\bigtriangledown}}
-\newcommand\raise@half[2]{%
-  \raisebox{.9\depth}{$\m@th#1#2$}%
-}
-\makeatother
-\newcommand{\ashrk}{\text{\textexclamdown}}
-\newcommand{\dash}{\mbox{-}}
-\newcommand{\cat}[2]{\mscc{#1}\mathrm{#2}}
-\newcommand{\htimes}{\times^{\mathrm{h}}}
-
-\newcommand{\spans}{\mscc{S}^{\mrm{sp}}}
-\newcommand{\OEEx}{\overrightarrow{\EEx}}
-\newcommand{\Ssp}{\mscc{S}^{\mrm{sp}}}
-\newcommand{\ocat}[1]{\mathrm{#1}}
-\newcommand{\Ctop}{\mscc{C}\mrm{at}_{\mrm{Top}}}
-\newcommand{\Tame}{\Hom^{t}}
-\newcommand{\tame}{\tau}
-\newcommand{\Unzip}{\mrm{Unzip}}
+\DeclareMathOperator{\Unzip}{Unzip}
+\DeclareMathOperator{\Link}{Link}
 
@@
 \subsubsection*{Acknowledgments} We thank Tashi Walde for very useful exchanges.
+
+\section{Localities of the full unzip}
+
+\begin{definition}
+    $S_X\subset X$.
+\end{definition}
+
+\begin{proposition}\label{7GBVGBA}
+    $S_X\subset X$ proper constructible bundle with $\Unzip_{S_X}(X)\cong\Unzip(X)$ and $\Link_{S_X}(X)=\partial\Unzip(X)$.
+\end{proposition}
+
+\begin{lemma}\label{DNFREG0}
+    {\color{gray}Locally finite good cover on $S_X$. (?)} {\bf unnecessary - second-countability implies more than paracompactness - see [Lee, Smooth, Thm 1.15]}
+\end{lemma}
+
+\begin{lemma}\label{K52SWOM}
+    Let $X$ be a smooth manifold with corners. Then for every boundary collar $I\colon \R_{\geq0}\times \partial X\hookrightarrow X$ there exists a homeomorphism
+    \[
+        \alpha_I\colon X^+\xrightarrow{\cong}\R_{\geq0}\times X
+    \]
+    where $X^+=\bigcup_{r\in\R_{\geq0}}[0,r]\times\partial X\cup_{\{r\}\times\partial X}X$.
+\end{lemma}
+\begin{proof}
+    Let $I\colon\R_{\geq0}\times\partial X\hookrightarrow X$ be a collar, which is a homeomorphism onto its image.
+We have $X=I(\R_{\geq0}\times \partial X)\cup_{I((0,\infty)\times\partial X)}X^\circ$.
+Similarly, for each $r$, we have a diffeomorphism
+    \[
+        \alpha_r\colon X\to X\smallsetminus I([0,r)\times\partial X)=I([r,\infty)\times\partial X)\cup_{I((r,\infty)\times\partial X)}X\smallsetminus I([0,r]\times\partial X)
+    \]
+    given by $I(t,q)\mapsto I(t+r,q)$ on $I(\R_{\geq0}\times\partial X)$ and by the identity on $X\smallsetminus \Imm(I)$.
+We suppress the dependence on $I$ in notation.
+We obtain a well-defined homeomorphism
+    \[
+        I\cup\alpha_r\colon [0,r]\times\partial X\cup_{\{r\}\times \partial X}X\to X,
+    \]
+    well-defined since $\alpha_r(q)=\alpha_r(I(0,q))=I(r,q)$ for $q\in\partial X$, and thereupon, writing $X^{+r}=[0,r]\times\partial X\cup_{\{r\}\times \partial X}X$, the bijection 
+    \begin{align*}
+        &\alpha_I\colon X^+\to \R_{\geq0}\times X,\\
+        &\alpha|_{X^{+r}}=\{r\}\times I\cup\alpha_r.
+    \end{align*}
+    We equip $X^+$ with the induced topology, promoting $\alpha$ to a homeomorphism.
+\end{proof}
+
+\begin{lemma}\label{DGSR46V}
+    Let $X$ be a smooth manifold with corners. Then there is a homeomorphism $\R_{\geq0}\times \partial(\R_{\geq0}\times X)\cong\R_{\geq0} \times X$. Consequently, there is a homeomorphism
+    \[
+        \Unzip_{C(L)}(C(Z))\cong\R_{\geq0}\times\Link_{C(L)}(C(Z))
+    \] 
+    for $L=S_Z$.
+\end{lemma}
+
+\begin{proof}
+    Using \Cref{K52SWOM} it suffices to provide a homeomorphism
+    \[
+        \phi\colon\R_{\geq0}\times\partial(\R_{\geq0}\times X)\to\bigcup_{r\in\R_{\geq0}}[0,r]\times\partial X\cup_{\{r\}\times\partial X}X.
+    \]
+    Noting 
+    \[
+        \partial(\R_{\geq0}\times X)=\{0\}\times X\cup_{\{0\}\times \partial X}\R_{\geq0}\times\partial X,
+    \] 
+    we define $\phi$ to be the following map: 
+    \begin{align*}
+        \R_{\geq0}\times\{0\}\times X\ni (t,0,x)&\mapsto x\in X\subset[0,t]\times \partial X\cup_{\{t\}\times\partial X}X\\
+        \R_{\geq0}\times\R_{\geq0}\times\partial X\ni(t,s,q)&\mapsto (t,q)\in[0,t+s]\times\partial X.
+    \end{align*}
+    This map and its inverse $\phi^{-1}$ given by
+    \begin{align*}
+        [0,r]\times\partial X \ni (t,q) &\mapsto (t,r-t,q)\in \R_{\geq0}\times\R_{\geq0}\times\partial X\\
+        [0,r]\times\partial X\cup_{\{r\}\times\partial X}X\supset X\ni x&\mapsto (r,0,x)\in\R_{\geq0}\times\{0\}\times X
+    \end{align*}
+    are well-defined and continous. Note that $\phi$ does not nepend on a collar.
+
+    The second statement is the special case where $X=\Unzip_L(Z)$ using \Cref{7GBVGBA} and that $\Unzip_{C(L)} C(Z)=\R_{\geq0}\times \Unzip_L(Z)$ and $\Link_{C(L)}C(Z)=\partial\Unzip_{C(L)}(C(Z))$.  
+\end{proof}
+
+\begin{remark}
+    In the situation of \Cref{K52SWOM} we will regard $X^+$ as a smooth manifold with corners with respect to the smooth structure induced by $\alpha_I$.
+Up to equivalence, this structure does not depend on the choice of collar.
+Similarly, in the situation of \Cref{DGSR46V} we will regard $\R_{\geq0}\times\Link_{C(L)}C(Z)$ as a smooth manifold with corners, tautologically diffeomorphic to $\Unzip_{C(L)}C(Z)$ with respect to the induced smooth structure.
+\end{remark}
+
+\begin{construction}\label{O6BEXS3}
+    Let $X$ be a smooth manifold with corners of dimension $n$, let $\{(U,\phi_U)\}$ a cover of $X$ by coordinate neighbourhoods where each $\phi_U\colon\R^{n-c_U}\times\R^{c_U}_{\geq0}$ is a homeomorphism, and let $\{\rho_U\colon X\to[0,1]\}$ be a partition of unity subordinate to this cover.
+Recall that a collar $I=I(\{U,\phi_U,\rho_U\})\colon \R_{\geq0}\times\partial X\hookrightarrow X$ is then constructed by defining to be the flow along the nowhere-vanishing inward-pointing vector field $V=\sum\rho_U V_U$ where, in local coordinates, $V_U=\sum_{1\leq i\leq c_U}\partial_i$ where $\{\partial_i\}$ is the standard basis of $\Tangent_0\R^{c_U}_{\geq0}\subset\Tangent_0(\R^{n-c_U}\times\R^{c_U}_{\geq0})$.
+
+    Let $X$ and $I=I_{\{U,\phi_U,\rho_U\}}$ be as above. Then there is a canonically induced a collar 
+    \[
+        I^+=I(\{\R_{\geq0}\times U,\id_{\R_{\geq0}}\times\phi_U,\mrm\rho_U\circ\mrm{pr}_X\})\colon \R_{\geq0}\times\partial(\R_{\geq0}\times\partial X)\hookrightarrow \R_{\geq0}\times X
+    \] 
+    on $\R_{\geq0}\times X$, where $\mrm{pr}_X\colon \R_{\geq}\times X\to X$ is the coordinate projection.
+It is the flow along the vector field $V^+=\sum(\rho_U\circ\mrm{pr}_X)\cdot V_U^+$ where $V_U^+=\partial_s+V_U$ where $\partial_s$ is the standard basis of $\Tangent_0\R_{\geq0}\subset\Tangent_0(\R_{\geq0}\times\R^{n-c_U}\times\R^{c_U}_{\geq0})$.
+\end{construction}
+
+\begin{lemma}
+    Let $X$ be a smooth manifold with corners and let $I^+\colon\R_{\geq0}\times \partial(\R_{\geq0}\times\partial X)\hookrightarrow\R_{\geq0}\times X$ be as in \Cref{O6BEXS3}. Then 
+    \[
+        I^+=\alpha_I\circ\phi
+    \]
+    where $\alpha_I$ is as in \Cref{K52SWOM} and $\phi$ is as in the proof of \Cref{DGSR46V}.
+\end{lemma}
+\begin{proof}
+    We observe the restrictions 
+    \begin{align*}
+        \R_{\geq0}\times\{0\}\times X&\xrightarrow{\alpha_I\circ\phi}\R_{\geq0}\times X\\
+        (t,0,x)&\mapsto \begin{cases}
+            (t,I(t_x+t,q)), & x=I(t_x,q)\\
+            (t,x), & x\in X\smallsetminus\Imm(I)
+        \end{cases}
+    \end{align*}
+    and
+    \begin{align*}
+        \R_{\geq0}\times\R_{\geq0}\times\partial X&\xrightarrow{\alpha_I\circ \phi} \R_{\geq0} \times X\\
+        (t,s,q)&\mapsto (t+s,I(t,q)).
+    \end{align*}
+    Both maps are the flow (for time $t$) along the vector field $V^+=\sum(\rho_U\circ\mrm{pr}_X)\cdot(\partial_s+V_U)$.
+\end{proof}
+
+In the following, $\mbb{D}^n\subset\R^n$ denotes the unit open $n$-disk and $C^{<1}(Z)=\ast\amalg_{\{0\}\times Z}[0,1)\times Z$.
+
+\begin{definition}
+    We say an embedded basic $\phi\colon \R^k\times C(Z)\hookrightarrow X$ in a conically smooth space $X$ is \emph{extendable} if there exists an embedding $\widehat{\phi}\colon\R^n\times C(Z)\hookrightarrow X$ such that $\phi$ factors as $\phi\colon\R^{k}\times C(Z)\to \mbb{D}^n\times C^{<1}(Z)\hookrightarrow \R^n\times C^{<1}(Z)\xhookrightarrow{\widehat{\phi}}X$ where the first map is the isomorphism given by the cartesian product of the isomorphisms $\R^n\to\mbb{D}^n$, $x\mapsto \frac{x}{|x|+1}$ and $C(Z)\to C^{<1}(Z)$, $(t,z)\mapsto (\frac{t}{t+1},z)$.
+\end{definition}
+
+\begin{definition}
+    Suppose $\mcal{U}$ is a cover of a topological space $X$ which is closed under finite intersections.
+We say $\mcal{U}$ is \emph{generated} by a cover $\mcal{V}$ and write $\mcal{U}=\langle\mcal{V}\rangle$ if every member of $\mcal{U}$ is a finite intersection of members of $\mcal{V}$.
+\end{definition}
+
+\begin{lemma}\label{2978BNV}
+    Every smooth manifold $M$ has a good cover $\mcal{U}$ which is generated by extendable basics.
+\end{lemma}
+\begin{proof}
+    Equip $M$ with a riemannian metric.
+We can put $\mcal{U}=\langle\mcal{V}\rangle$ for $\mcal{V}=\{D_p\}_{p\in M}$ where $D_p$ is the convex disk which is the interior of the image of a ball in $\Tangent_p M$ under the exponential map, with radius strictly smaller than the radius of injectivity.
+\end{proof}
+
+\begin{lemma}
+    Suppose $U\subset C(Z)$ be conically smooth basics with $S_{C(Z)}\cong U$, and suppose that $U\cong C(L)$ is extendable.
+Let $\pi\colon \Link(C(Z))|_{U}\to U$ denote the link projection of $\Unzip (C(Z))$ over $U$.
+Then there is an isomorphism
+    \[
+        \partial\overline{\pi^{-1}U}\cong \Link_L(Z)
+    \]
+    and an induced conically smooth collar 
+    \[
+        (0,1]\times\partial\overline{\pi^{-1}U}\hookrightarrow \overline{\pi^{-1}U}
+    \]
+    which is a refinement onto its image.
+\end{lemma}
+\begin{proof}
+    Up to isomorphism we have that $U=C^{<1}(L)\subset C^{<1}(Z)\subset C(Z)$ is induced by the inclusion $L=S_Z\subset Z$.
+Abbreviating $S=S_{C(Z)}$, the inclusion of $U$ factors as $U\subset S=C(L)$ .
+Now, using \Cref{7GBVGBA} we have $\Unzip C(Z)=\Unzip_{S}C(Z)=\R_{\geq0}\times\Unzip_L Z$ and so
+    \begin{align*}
+        \Unzip C(Z)|_{U}&=\Link_{C(L)}C(Z)|_{C^{<1}(L)}\\
+        &=\{0\}\times \Unzip_L Z\cup_{\{0\}\times\Link_LZ}[0,1)\times\Link_L Z\\
+    \end{align*}
+    since the projection $\pi\colon\Link_{C(L)}C(Z)=\{0\}\times\Unzip_L Z\cup_{\{0\}\times\Link_LZ}\R_{\geq0}\times \Link_L Z\to C(L)=\ast\amalg_{\{0\}\times L}\R_{\geq0}\times L$ is given by mapping all of $\{0\}\times\Unzip_L Z$ to $\ast$ and on $\R_{\geq0}\times \Link_LZ$ by $\id_{\R_{\geq0}}\times\pi'$ where $\pi'\colon \Link_LZ\to L$ is the link projection.
+    Thus 
+    \[
+        \pi^{-1}\overline{U}=\pi^{-1}C^{\leq 1}(U)=\{0\}\times\Unzip_LZ\cup[0,1]\times\Link_LZ 
+    \]
+    and consequently 
+    \[
+        \pi^{-1}\partial\overline{U}=\pi^{-1}\{1\}\times L=\{1\}\times\Link_L Z,
+    \]
+    proving the first claim. The collar is immediate.
+\end{proof}
+
+\begin{example}
+
+\end{example}
+
+\begin{corollary}
+
+\end{corollary}
 

### 2025-08-21 paperversion/paper.tex
mini fixes

@@
 \begin{abstract}
-    We construct good covers for conically smooth spaces {\color{MidnightBlue} over depth-$1$ posets}.
+    We construct good covers for conically smooth spaces.
 By a result of Karlsson--Scheimbauer--Walde, this implies that, for every such space $X$, constructible factorisation algebras on $X$ and disk algebras over $X$ coincide.
@@
     Equip $M$ with a riemannian metric.
-We can put $\mcal{U}=\langle\mcal{V}\rangle$ for $\mcal{V}=\{D_p\}_{p\in M}$ where $D_p$ is the convex disk which is the interior of the image of a ball in $\Tangent_p M$ under the exponential map, with radius strictly smaller than the radius of injectivity.
+We can put $\mcal{U}=\langle\mcal{V}\rangle$ for $\mcal{V}=\{D_p\}_{p\in M}$ where $D_p$ is the convex disk which is the interior of the image of a ball in $\Tangent_p M$ under the exponential map, with a radius that is strictly smaller than the radius of injectivity.
 \end{proof}

### 2025-09-02 paperversion/paper.tex
more localities

@@
-\documentclass[]{amsart}
+\documentclass[11pt]{amsart}
 
@@
 
-\begin{lemma}
+\begin{lemma}\label{DYQ422D}
     Let $X$ be a smooth manifold with corners and let $I^+\colon\R_{\geq0}\times \partial(\R_{\geq0}\times\partial X)\hookrightarrow\R_{\geq0}\times X$ be as in \Cref{O6BEXS3}. Then 
@@
 
-\begin{lemma}
-    Suppose $U\subset C(Z)$ be conically smooth basics with $S_{C(Z)}\cong U$, and suppose that $U\cong C(L)$ is extendable.
-Let $\pi\colon \Link(C(Z))|_{U}\to U$ denote the link projection of $\Unzip (C(Z))$ over $U$.
-Then there is an isomorphism
+\begin{lemma}\label{V6RIX5L}
+    Let $L=S_Z$ and let $U=C^{<1}(L)\subset C^{<1}(Z)\subset C(Z)$. Let $\pi\colon \Link(C(Z))|_{U}\to U$ denote the link projection of $\Unzip (C(Z))$ over $U$. Then there is an isomorphism
     \[
@@
     and an induced conically smooth collar 
-    \[
+    \(
         (0,1]\times\partial\overline{\pi^{-1}U}\hookrightarrow \overline{\pi^{-1}U}
-    \]
+    \)
     which is a refinement onto its image.
@@
 \begin{proof}
-    Up to isomorphism we have that $U=C^{<1}(L)\subset C^{<1}(Z)\subset C(Z)$ is induced by the inclusion $L=S_Z\subset Z$.
-Abbreviating $S=S_{C(Z)}$, the inclusion of $U$ factors as $U\subset S=C(L)$ .
-Now, using \Cref{7GBVGBA} we have $\Unzip C(Z)=\Unzip_{S}C(Z)=\R_{\geq0}\times\Unzip_L Z$ and so
+    Using \Cref{7GBVGBA} we have $\Unzip C(Z)=\Unzip_{S}C(Z)=\R_{\geq0}\times\Unzip_L Z$ and so 
     \begin{align*}
@@
     and consequently 
+    \begin{equation}\label{QX54WZB}
+        \pi^{-1}\partial\overline{U}=\pi^{-1}\{1\}\times L=\{1\}\times\Link_L Z,
+    \end{equation}
+    proving the first claim. The collar is immediate.
+\end{proof}
+
+\begin{example}
+
+\end{example}
+
+\begin{lemma}\label{FBLD2TE}
+    Let $\R^n$ be equipped with a riemannian metric, and let $c\in\{0,\dots,n\}$. Then for any convex disk $D\subset\R^n$ about the origin the intersections
+    \begin{enumerate}
+        \item $D\cap (\R^{n-c}\times(\R^{c}\smallsetminus\R^{c}_{\geq0}))$
+        \item $D \cap (\R^{n-c}\times\R^{c}_{>0})$
+    \end{enumerate}
+    are disks.
+\end{lemma}
+\begin{proof}
+
+\end{proof}
+
+\begin{proposition}
+    Let $L=S_Z$ and let $I=J^+\colon \R_{\geq0}\times\Link_{C(L)}C(Z)\hookrightarrow\Unzip_{C(L)}C(Z)$ be the collar induced, according to \Cref{O6BEXS3}, by a collar $J\colon\R_{\geq0}\times\Link_L(Z)\hookrightarrow \Unzip_L(Z)$.
+Let $U$ be as in \Cref{V6RIX5L}, and let
     \[
-        \pi^{-1}\partial\overline{U}=\pi^{-1}\{1\}\times L=\{1\}\times\Link_L Z,
+        p\in I(\{1\}\times\partial\overline{\pi^{-1}U}).
     \]
-    proving the first claim. The collar is immediate.
+    Then:
+    \begin{enumerate} 
+        \item There is a diffeomorphism 
+        \[
+            \R_{>1}\times J(\R_{>0}\times\Link_LZ)\cap I([0,1]\times\overline{\pi^{-1}U})\cong (1,2]\times J((0,1]\times\Link_LZ)
+        \]
+        of smooth manifolds with corners.
+        \item There exists a convex disk $D\subset\Unzip_{C(L)}C(Z)^\circ$ about $p$ such that $D\cap I([0,1)\times\pi^{-1}U)$ is a disk. 
+        % \item There exists a chart neighbourhood $V\subset\Unzip_{C(L)}C(Z)^\circ$ of $p$ which is diffeomorphic to $\R_{>0}\times J(\R_{>0}\times W)$ where $W\subset\Link_L(Z)$ is the boundary of a chart neighbourhood in $\Unzip_LZ$.
+        % \item There exists a homeomorphism 
+        % \[
+        %     \Psi\colon\R^2\times\Link_LZ\to \R_{>1}\times J(\R_{>0}\times\Link_LZ)
+        % \]
+        % such that 
+        % \[
+        %     \R_{>1}\times J(\R_{>0}\times\Link_LZ)\cap I([0,1]\times\overline{\pi^{-1}U})=\Psi(\R_{\leq0}^2\times\Link_LZ).
+        % \]
+    \end{enumerate}
+\end{proposition}
+\begin{proof}
+    From the proof of \Cref{V6RIX5L} we recall that
+    \(
+        \overline{\pi^{-1}U}=\{0\}\times\Unzip_LZ\cup_{\{0\}\times\Link_LZ}[0,1]\times\Link_LZ.
+    \)
+    By \Cref{DYQ422D} we have $I=\alpha_J\circ\phi$, and observe that 
+    \begin{align*}
+        \phi([0,1]\times\overline{\pi^{-1}U})&= A'\cup B'\\
+        &\coloneqq\bigcup_{t\in[0,1]}(X\subset X^{+t})\cup\{(t,q)\in X^{+(t+s)} : t,s\in[0,1]\}.
+    \end{align*}
+    Thus $I([0,1]\times\overline{\pi^{-1}U})=A\cup B\subset\Unzip_{C(L)}C(Z)=\R_{\geq0}\times\Unzip_LZ$ where $A=\alpha_J(A')$, $B=\alpha_J(B')$. We have 
+    \begin{align*}
+        &A=\{(r,x)\in\R_{\geq0}\times\Unzip_LZ : r\in[0,1],\ x\in \Unzip_LZ\smallsetminus J([0,r)\times\Link_LZ\}\\
+        &B=\{(t+s,J(t,q))\in\R_{\geq0}\times\Unzip_LZ : t,s\in[0,1]\}
+    \end{align*}
+    and hence
+    \[
+        \R_{>1}\times J(\R_{>0}\times\Link_LZ)\cap(A\cup B)=\{(t+s,J(t,q)) : t\in(0,1],\ s\in[0,1],\ t+s>1\}
+    \]
+    as the intersection with $A$ is empty.
+
+    Consider now the diffeomorphism 
+    \begin{align*}
+    \psi=\rho\circ\begin{pmatrix}
+        1 & 1\\ 
+        0 & 1
+    \end{pmatrix}\circ\rho^{-1}\colon\R_{>1}\times\R_{>0}&\to\R_{>1}\times\R_{>0},\\
+     (x,y)&\mapsto ((x-1)y+1,y)
+    \end{align*} 
+    where $\rho\colon\R^2\to\R_{>1}\times\R_{>0}$, $(x,y)\mapsto(e^x+1,e^y)$. Now $\psi$ fixes $(2,1)$ and satisfies 
+    \[
+        \psi((1,2]\times(0,1])=\{(t+s,t) : t\in(0,1],\ s\in[0,1],\ t+s>1\}.
+    \] 
+    Putting 
+    \[
+        \Psi=\id_{\R_{>1}}\times J\circ\psi\times\id_{\Link_LZ}\colon\R_{>1}\times\R_{>0}\times\Link_LZ\to\R_{>1}\times J(\R_{>0}\times\Link_LZ)
+    \] 
+    we obtain the map
+    \begin{align*}
+        (1,2]\times J((0,1]\times\Link_LZ)&\xrightarrow{\cong}(1,2]\times(0,1]\times\Link_LZ\\
+        &\xrightarrow{\Psi|}\R_{>1}\times J(\R_{>0}\times\Link_LZ)\cap I([0,1]\times\overline{\pi^{-1}U}).
+    \end{align*}
+    The first map, which is a homeomorphism, is tautologically a diffeomorphism of smooth manifolds with corners with respect to the induced smooth structure on its target.
+With respect to the latter, $\Psi$ is a diffeomorphism as well.
+Hence the composition is a diffeomorphism.
+In particular, we obtain the restricted diffeomorphism
+    \[
+        (1,2)\times J((0,1)\times\Link_LZ)\cong\R_{>1}\times J(\R_{>0}\times\Link_LZ)\cap C_{U}.
+    \]
+    of smooth manifolds without boundary.
+
+    Finally, consider $p=I(1,(1,q))=(2,J(1,q))$ where $q\in\Link_LZ$ (recall \eqref{QX54WZB}).
+Let $\R^{n-c}\times\R^{c}_{\geq0}\cong W\subset\Unzip_LZ$ be a chart neighbourhood of $q$.
+Without loss of generality we may assume $c=n$ for simplicity.
+Up to diffeomorphism we may write the restriction of the collar of $\Link_LZ$ as $J\colon\R_{\geq0}\times\partial\R^c_{\geq0})\hookrightarrow \R^c_{\geq0}$, given by the flow along the vector field $\sum_{1\leq i\leq c}\partial_i$ where $\{\partial_i\}$ is the standard basis of $\Tangent_0\R^c_{\geq0}$ (recall \Cref{O6BEXS3}).
+We now observe the diffeomorphism
+    \[
+        J((0,1]\times\partial \R^{c}_{\geq0})=\R^c_{>0}\smallsetminus\left(\begin{pmatrix}
+        1 \\ \vdots \\ 1
+        \end{pmatrix}
+        +\R^c_{\geq0}\right)
+        \cong\R^c\smallsetminus\R^c_{>0}
+    \]
+    of smooth manifolds with corners.
+    Consequently we have $(1,2]\times J((0,1]\times\partial\R^c_{\geq0})\cong\R^{c+1}\smallsetminus\R^{c+1}_{>0}$.
+These diffeomorphisms restrict to $J((0,1)\times \partial\R^c_{\geq0})\cong\R^c\smallsetminus\R^c_{\geq0}$ and so $(1,2)\times J((0,1)\times\partial\R^c_{\geq0})\cong \R^{c+1}\smallsetminus\R^{c+1}_{\geq0}$.
+Hence, the intersection of any convex disk $D\subset\R_{>1}\times J(\R_{>0}\times W)$ centred at $(2,J(1,q))=p$ with $I([0,1)\times\pi^{-1}U)$ is a disk by the first statement of \Cref{FBLD2TE}.
 \end{proof}

### 2025-09-10 paperversion/paper.tex
silly lemma

@@
 \DeclareMathOperator{\Link}{Link}
+\DeclareMathOperator{\Span}{span}
 
@@
 \begin{lemma}\label{FBLD2TE}
-    Let $\R^n$ be equipped with a riemannian metric, and let $c\in\{0,\dots,n\}$. Then for any convex disk $D\subset\R^n$ about the origin the intersections
+    Let $\R^n$ be equipped with a riemannian metric, and let $c\in\{0,\dots,n\}$. Then for all geodesic disks $D\subset\R^n$ about the origin the intersections
     \begin{enumerate}
@@
 \begin{proof}
-
+    Let us suppose $n=c$ for simplicity.
+For $r>0$, recall the diffeomorphism $[0,r)\to[0,\infty)$, $x\mapsto\frac{x}{r-x}$.
+In the same way, $\rho_r\colon B_r\to\R^n$, $v\mapsto \frac{d(0,v)}{r-d(0,v)}v$ is a diffeomorphism from the disk $B_r=\{x:\R^n : d(0,x)<r\}$ of radius $r$ about the origin to all of $\R^n$, where $d$ is the metric associated with the given riemannian metric.
+Now we need only note that $\rho_r$ restricts to diffeomorphisms $B_r\cap\R^n_{>0}\to\R^n{>0}$ and $B_r\cap(\R^n\smallsetminus\R^n_{\geq0})\to\R^n\smallsetminus\R^n_{\geq0}$, and that both targets are disks.
 \end{proof}

### 2025-09-10 paperversion/paper.tex
typo

@@
 In the same way, $\rho_r\colon B_r\to\R^n$, $v\mapsto \frac{d(0,v)}{r-d(0,v)}v$ is a diffeomorphism from the disk $B_r=\{x:\R^n : d(0,x)<r\}$ of radius $r$ about the origin to all of $\R^n$, where $d$ is the metric associated with the given riemannian metric.
-Now we need only note that $\rho_r$ restricts to diffeomorphisms $B_r\cap\R^n_{>0}\to\R^n{>0}$ and $B_r\cap(\R^n\smallsetminus\R^n_{\geq0})\to\R^n\smallsetminus\R^n_{\geq0}$, and that both targets are disks.
+Now we need only note that $\rho_r$ restricts to diffeomorphisms $B_r\cap\R^n_{>0}\to\R^n_{>0}$ and $B_r\cap(\R^n\smallsetminus\R^n_{\geq0})\to\R^n\smallsetminus\R^n_{\geq0}$, and that both targets are disks.
 \end{proof}

### 2025-09-10 paperversion/paper.tex
def of S_X and first properties

@@
 \DeclareMathOperator{\Span}{span}
+\newcommand{\opp}{{\mathrm{op}}}
 
@@
 \begin{definition}
-    $S_X\subset X$.
+    Let $X$ be a CSS. Its \emph{singular locus} $S_X=\bigcup_{k>0} X_k\subset X$ consists of all points in $X$ which have strictly positive depth.
 \end{definition}
+
+\begin{lemma}
+    For every CSS $X$, the inclusion $S_X\hookrightarrow X$ is a proper constructible embedding of conically smooth spaces.
+\end{lemma}
+\begin{proof}
+    Let $X\to P$ be the stratification of $X$ and let $X\to P\to\mbb{P}=\mbb{Z}^{\opp}\times\mbb{Z}^{\opp}$ be its depth-dimension stratification \cite[Lemma 2.4.10]{ayala2017local}.
+The inclusion $\mbb{Z}_{>0}^{\opp}\subset\mbb{Z}^\opp$ (where in the subscript $>$ refers to the ordinary ordering and not to its opposite) is a full subcategory inclusion and is thus consecutive \cite[Definition 2.3.1]{ayala2017local}, hence so is $\mbb{P}_{+}=\mbb{Z}_{>0}^\opp\times\mbb{Z}^\opp\hookrightarrow\mbb{P}$.
+Since consecutive poset maps are stable under pullbacks, $\mbb{P}_{+}\times_{\mbb{P}}P\hookrightarrow P$ is likewise consecutive, proving that the inclusion $S_X=X|_{\mbb{P}_+\times_{\mbb{P}}P}\hookrightarrow X$ is a constructible map of conically smooth spaces \cite[Lemma 3.4.5, Example 3.4.7]{ayala2017local}.
+Finally, as $\mbb{Z}_{>0}^{\opp}\subset\mbb{Z}^\opp$ is downward-closed, $S_X$ is closed in $X$, so (since CSSs are Hausdorff) the inclusion map is proper.
+\end{proof}
 

### 2025-09-10 paperversion/paper.tex
typo

@@
 For $r>0$, recall the diffeomorphism $[0,r)\to[0,\infty)$, $x\mapsto\frac{x}{r-x}$.
-In the same way, $\rho_r\colon B_r\to\R^n$, $v\mapsto \frac{d(0,v)}{r-d(0,v)}v$ is a diffeomorphism from the disk $B_r=\{x:\R^n : d(0,x)<r\}$ of radius $r$ about the origin to all of $\R^n$, where $d$ is the metric associated with the given riemannian metric.
+In the same way, $\rho_r\colon B_r\to\R^n$, $v\mapsto \frac{d(0,v)}{r-d(0,v)}v$ is a diffeomorphism from the disk $B_r=\{x\in\R^n : d(0,x)<r\}$ of radius $r$ about the origin to all of $\R^n$, where $d$ is the metric associated with the given riemannian metric.
 Now we need only note that $\rho_r$ restricts to diffeomorphisms $B_r\cap\R^n_{>0}\to\R^n_{>0}$ and $B_r\cap(\R^n\smallsetminus\R^n_{\geq0})\to\R^n\smallsetminus\R^n_{\geq0}$, and that both targets are disks.

### 2025-09-11 paperversion/paper.tex
unzip along S_X

@@
 \newcommand{\opp}{{\mathrm{op}}}
+\DeclareMathOperator{\depth}{depth}
 
@@
 
-\begin{lemma}
+\begin{lemma}\label{8W651JS}
     For every CSS $X$, the inclusion $S_X\hookrightarrow X$ is a proper constructible embedding of conically smooth spaces.
@@
 
+By virtue of \Cref{8W651JS} we may apply unzip $X$ along $S_X$ according to \cite[Proposition 7.3.10]{ayala2017local}.
+
 \begin{proposition}\label{7GBVGBA}
-    $S_X\subset X$ proper constructible bundle with $\Unzip_{S_X}(X)\cong\Unzip(X)$ and $\Link_{S_X}(X)=\partial\Unzip(X)$.
+    The unzip of $X$ is its unzip along its singular locus. That is, $\Unzip(X)\cong\Unzip_{S_X}(X)$ and consequently $\partial\Unzip(X)\cong\Link_{S_X}(X)$.
 \end{proposition}
+\begin{proof}
+    If $\depth(X)=0$ the statement holds trivially, so let us suppose that $\depth(X)\leq n\geq1$ and that the statement holds for all CSSs $Y$ with $\depth(Y)\leq n-1$.
+    The problem is local, so, suppressing euclidean factors for simplicity, let $X=C(Z)$ be a conically smooth basic.
+By \cite[Lemma 7.3.5, (5) and (6)]{ayala2017local} and by the inductive hypothesis we have $\Unzip(C(Z))=\R_{\geq0}\times\Unzip(Z)=\R_{\geq0}\times\Unzip_{S_Z}(Z)$, as $Z$ has strictly lower depth.
+On the other hand, since $S_{C(Z)}=C(S_Z)$ by inspection, we have $\Unzip_{S_{C(Z)}}C(Z)=\Unzip_{C(S_Z)}C(Z)=\R_{\geq0}\times\Unzip_{S_Z}(Z)$ by construction (cf.\ the proof of \cite[Proposition 7.3.10]{ayala2017local}), proving $\Unzip(C(Z))=\Unzip_{S_{C(Z)}}(C(Z))$.
+\end{proof}
 

### 2025-09-16 paperversion/paper.tex
filling out the main proof, part 1

@@
 
-\usepackage[ngerman,french,british]{babel} % clashes with q.uiver/tikzcd
+% \usepackage{geometry}
+% \geometry{textwidth=14cm, textheight=21.3cm, marginratio={4:4,4:4}}
+
+\usepackage[ngerman,french,british]{babel}
 \usepackage[utf8]{inputenc}
@@
 
-\begin{lemma}\label{DNFREG0}
-    {\color{gray}Locally finite good cover on $S_X$. (?)} {\bf unnecessary - second-countability implies more than paracompactness - see [Lee, Smooth, Thm 1.15]}
-\end{lemma}
+% \begin{lemma}\label{DNFREG0}
+%     {\color{gray}Locally finite good cover on $S_X$. (?)} {\bf unnecessary - second-countability implies more than paracompactness - see [Lee, Smooth, Thm 1.15]}
+% \end{lemma}
 
@@
 \begin{definition}
-    We say an embedded basic $\phi\colon \R^k\times C(Z)\hookrightarrow X$ in a conically smooth space $X$ is \emph{extendable} if there exists an embedding $\widehat{\phi}\colon\R^n\times C(Z)\hookrightarrow X$ such that $\phi$ factors as $\phi\colon\R^{k}\times C(Z)\to \mbb{D}^n\times C^{<1}(Z)\hookrightarrow \R^n\times C^{<1}(Z)\xhookrightarrow{\widehat{\phi}}X$ where the first map is the isomorphism given by the cartesian product of the isomorphisms $\R^n\to\mbb{D}^n$, $x\mapsto \frac{x}{|x|+1}$ and $C(Z)\to C^{<1}(Z)$, $(t,z)\mapsto (\frac{t}{t+1},z)$.
+    We say an embedded basic $\phi\colon \R^k\times C(Z)\hookrightarrow X$ in a conically smooth space $X$ is \emph{extendable} if there exists an embedding $\widehat{\phi}\colon\R^k\times C(Z)\hookrightarrow X$ such that $\phi$ factors as $\phi\colon\R^{k}\times C(Z)\to \mbb{D}^k\times C^{<1}(Z)\hookrightarrow \R^k\times C^{<1}(Z)\xhookrightarrow{\widehat{\phi}}X$ where the first map is the isomorphism given by the cartesian product of the isomorphisms $\R^k\to\mbb{D}^k$, $x\mapsto \frac{x}{|x|+1}$ and $C(Z)\to C^{<1}(Z)$, $(t,z)\mapsto (\frac{t}{t+1},z)$.
 \end{definition}
@@
     Let us suppose $n=c$ for simplicity.
-For $r>0$, recall the diffeomorphism $[0,r)\to[0,\infty)$, $x\mapsto\frac{x}{r-x}$.
-In the same way, $\rho_r\colon B_r\to\R^n$, $v\mapsto \frac{d(0,v)}{r-d(0,v)}v$ is a diffeomorphism from the disk $B_r=\{x\in\R^n : d(0,x)<r\}$ of radius $r$ about the origin to all of $\R^n$, where $d$ is the metric associated with the given riemannian metric.
+The map $\rho_r\colon B_r\to\R^n$, $v\mapsto \frac{d(0,v)}{r-d(0,v)}v$ is a diffeomorphism from the geodesic disk $B_r=\{x\in\R^n : d(0,x)<r\}$ of radius $r$ about the origin to all of $\R^n$, where $d$ is the metric associated with the given riemannian metric.
 Now we need only note that $\rho_r$ restricts to diffeomorphisms $B_r\cap\R^n_{>0}\to\R^n_{>0}$ and $B_r\cap(\R^n\smallsetminus\R^n_{\geq0})\to\R^n\smallsetminus\R^n_{\geq0}$, and that both targets are disks.
@@
 
-\begin{proposition}
+\begin{lemma}
+    Version of \Cref{FBLD2TE} for star-shaped (to apply to intersections of convex disks later) using Whitney approximation for functions!
+\end{lemma}
+
+\begin{proposition}\label{DEA068T}
     Let $L=S_Z$ and let $I=J^+\colon \R_{\geq0}\times\Link_{C(L)}C(Z)\hookrightarrow\Unzip_{C(L)}C(Z)$ be the collar induced, according to \Cref{O6BEXS3}, by a collar $J\colon\R_{\geq0}\times\Link_L(Z)\hookrightarrow \Unzip_L(Z)$.
@@
 
+\begin{theorem}
+    Every conically smooth space admits a good cover.
+\end{theorem}
+
+\begin{proof}
+    Let $n\geq0$ denote the depth of $X$.
+If $n=0$ then $X$ is smooth and we are done, so suppose $n\geq1$.
+\Cref{7GBVGBA} gives that $\Unzip(X)\cong\Unzip_{S}(X)$ and that $\partial=\partial\Unzip(X)\cong\Link_S(X)$ where $S=S_X\subset X$ is the union of the depth-$k$ strata of $X$ for all $k\geq1$.
+We obtain the pullback-pushout diagram
+    \[
+    \begin{tikzcd}
+        \partial\ar[r,hook]\ar[d,two heads,"{\pi}"] & \Unzip(X)\ar[d,two heads]\\
+        S\ar[r,hook] & X
+    \end{tikzcd}
+    \] 
+    where every map is a proper constructible bundle.
+Moreover, $\Unzip(X)$ is a smooth manifold with corners.
+We equip its interior with a riemannian metric.
+Note that $S\subset X$ being closed in a compact space is compact, hence so is $\partial$.
+    As in (the proof of) \cite[Proposition 8.2.5]{ayala2017local} there is a conically smooth collar 
+    \[
+        I\colon \R_{\geq0}\times\partial\hookrightarrow \Unzip
+    \]
+    which is a refinement onto its open image.
+Further, since $\mrm{depth}(S)<\mrm{depth}(X)$ we may choose by induction a locally finite good cover $\mcal{U}$ on $S$.
+By \Cref{2978BNV} we may assume that $\mcal{U}=\langle\mbb{U}\rangle$ where $\mbb{U}$ is a cover of $S$ by extendable basics.
+
+    We will write 
+    \(
+        C_{A,B}=I(A\times\pi^{-1}B)
+    \)
+    where $A\subseteq \R_{\geq0}$ and $B\subset S$ are subsets, and set 
+    \(
+        C_U=C_{[0,1),U}.
+    \)
+
+    \subsection*{Step A}
+    Consider the cover 
+    \[
+        \mcal{C}=\{C_U : U\in\mcal{U}\}
+    \]
+    of $C_{[0,1),S}$, an open neighbourhood of $\partial$ in $\Unzip$, and the cover $\mcal{I}$ of $\Unzip\smallsetminus C_{[0,1],S}$ consisting of all convex disks therein.
+Since $C_{U}\cap C_{V}=C_{U\cap V}$ and $\mcal{U}$ is good, $\mcal{C}$ is closed under finite intersections.
+We will adjoin to $\mcal{C}\cup\mcal{I}$ an open cover $\mcal{D}$ of $C_{\{1\},S}=\Unzip\smallsetminus \bigcup\mcal{C}\cup\bigcup\mcal{I}$ consisting of convex disks whose intersections with members of $\mcal{C}$ are (not necessarily convex) disks and is itself closed under finite intersections, thus constructing a cover of $\Unzip$ which consists of the $C_U$ and disks in the interior $\Unzip^\circ$ and is closed under finite intersections.
+
+    Let us first observe that such a cover induces a good cover $X$ upon passing from $\Unzip$ to $X$. We claim that 
+    \[
+        \widehat{C_{U}}=U\amalg_{\pi^{-1}U}C_{U}\subset X
+    \]
+    is a basic for each $U\in\mcal{U}$.
+To see this, suppose, by ignoring euclidean factors without loss of generality, that $U\cong C(L)\subset C(Z)\subset X$, induced by an inclusion $L\subset Z$ where $L=S_Z$.
+Then we have that
+    \begin{multline*}
+        \widehat{C_U}\cong C(L)\amalg_{\Link_{C(L)}(C(Z))}\R_{\geq0}\times\Link_{C(L)}(C(Z))\\
+        \hookrightarrow C(L)\amalg_{\Link_{C(L)}(C(Z))}\Unzip_{C(L)}(C(Z))
+    \end{multline*} 
+    is an isomorphism since the collar $\R_{\geq0}\times\Link_{C(L)}(C(Z))\hookrightarrow \Unzip_{C(L)}(C(Z))$ is an isomorphism by \Cref{DGSR46V}. But 
+    \[
+        C(L)\amalg_{\Link_{C(L)}(C(Z))}\Unzip_{C(L)}(C(Z))\cong C(Z)
+    \]
+    by the unzip square of $C(Z)$, showing that 
+    \[
+        \widehat{C_{C(L)}}\cong C(Z)
+    \]
+    is a basic. We conclude that 
+    \[
+        \widehat{\mcal{C}}=\{\widehat{C_U} : U\in\mcal{U}\}
+    \]
+    is an open cover of $S$ by basics.
+It is closed under finite intersections since so is $\mcal{C}$.
+The cover consisting of $\mcal{D}$ and $\mcal{I}$ and the resulting finite intersections with $\widehat{\mcal{C}}$ descends on $X$ to a cover, contained within the depth-$0$ stratum $X_0$ (cf.\ the last statement of \cite[Proposition 7.3.10]{ayala2017local}), consisting of disks and is closed under finite intersections.
+
+    \subsection*{Step B} It remains to construct the cover $\mcal{D}$ of $C_{\{1\},S}$ with the desired properties. Let $p\in C_{\{1\},S}$ and let 
+    \[
+        k(p)=\#\{U\in \mcal{U} : p\in\partial \overline{C_{\{1\},U}}\}\geq0
+    \]
+    where 
+    \[
+        \partial\overline{C_{\{1\},U}}=\partial C_{\{1\},\overline{U}}=C_{\{1\},\partial\overline{U}}.
+    \]
+    We will write $\overline{p}\in\partial$ for the image of $p$ under the projection $\partial^i\overline{C_{<1,S}}=C_{\{1\},S}\to \{1\}\times\partial\to\partial$ given by $I^{-1}$.
+We will also write $\overline{p}=\pi(\overline{p})\in S$ by abuse.
+Let $c\colon\Unzip\to \langle m \rangle$ denote the corner stratification of $\Unzip$ so that around $\overline{p}$ there is a chart $\phi\colon\R^{n-|c(p)|}\times\R_{\geq0}^{|c(p)|}\hookrightarrow \Unzip$ with restriction $\phi|_{\partial}\colon\partial(\R^{n-|c(p)|}\times\R_{\geq0}^{|c(p)|})=\R^{n-|c(p)|}\times\partial\R_{\geq0}^{|c(p)|}\hookrightarrow \partial$.
+Using $I$, we obtain an open neighbourhood
+    \[
+        I|_{>0}\circ\phi|_{\partial}\colon (0,\infty)\times\R^{n-|c(p)|}\times\partial\R_{\geq0}^{|c(p)|}\hookrightarrow \Unzip^\circ
+    \]
+    such that $p\in I\circ\phi|_{\partial}(\{1\}\times\partial\R_{\geq0}^n)$. Let us put 
+    \[
+        W=W_\phi=\mrm{Im}(I|_{>0}\circ\phi|_{\partial})
+    \] 
+    and note the diffeomorphism $W\cong\R^n$.
+
+    \subsection*{Step C} Suppose now that $k(p)=0$.
+By the local finitude of $\mcal{U}$ we may pick a member $U'_p\in\mcal{U}$ which contains $\overline{p}$ and intersect only finitely many members of $\mcal{U}$ non-trivially.
+This yields
+    \[
+        U''_p=\bigcap_{\overline{p}\in U}U\cap U'_p\in \mcal{U},
+    \]
+    which satisfies $p\in C_{\{1\},U_p}$. Next, consider
+    \[
+        V_p=\bigcup_{\substack{V\in\mcal{U},\\\overline{p}\notin \overline{V},\\ V\cap U''_p\neq\emptyset}} \overline{V}.
+    \]
+    and put 
+    \[
+        U_p=U''_p\smallsetminus V_p.
+    \]
+    Since $V_p$ is likewise a finite union it is closed and thus $U_p$ is an open neighbourhood of $\overline{p}$ within $S$ (which need not be in $\mcal{U}$).
+We may now pick the chart $\phi$ above small enough such that $\phi|_{\partial}$ factors through $\pi^{-1}U_{p}\subset\partial$ and so $W\cap U_{p}=\mrm{Im}(I|_{(0,1)}\circ\phi|_{\partial})$.
+We may now pick a convex disk $D$ about $p$ with $D\subset W$, ensuring $D\cap C_{U_{p}}=D\cap\mrm{Im}(I|_{(0,1)}\circ\phi|_{\partial})$, and so
+    \[
+        D\cap C_{U_{p}}\cong\R^{n-|c(p)|}\times(\R^{|c(p)|}\smallsetminus\R_{\geq0}^{|c(p)|})\cong\R^n
+    \]
+    is a disk by \Cref{FBLD2TE}.
+For each $U\in\mcal{U}$ with $D\cap C_U\neq\emptyset$ we have $D\cap C_U=D\cap C_{U_p}$ by construction, so $D\cap C_U$ is a disk for every $U\in\mcal{U}$ if it is not empty.
+
+    \subsection*{Step D} Suppose now that $k(p)>0$, and let $U\in\mcal{U}$ be such that $p\in\partial\overline{C_{\{1\},U}}$.
+Suppose first that $U\in\mbb{U}$.
+Since $U$ is extendable, \Cref{DEA068T} gives that every geodesic disk $D$ about $p$ contained within a small-enough coordinate neighbourhood $M_U$ satisfies $D\cap C_U$.
+Consequently, every geodesic disk $D$ about $p$ with
+    \[
+        D\subset\bigcap_{\substack{U\in\mbb{U}\\ p\in\partial\overline{C_{\{1\},U}}}} M_U,
+    \]
+    the intersection being finite by local finitude, satisfies $D\cap C_U=D\cap M_U$ for every $U\in\mcal{U}$ with $p\in\partial\overline{C_{\{1\},U}}$.
+\end{proof}
+
+\iffalse
+
 \begin{definition}
@@
 
+\fi
+
 \printbibliography

### 2025-09-30 good_covers(ignore)/good_covers.tex
(ignore)

--- 2024-09-05 main_theorem.tex
@@
 
-%\setcounter{section}{-1}
+\setcounter{section}{-1}
 
@@
 % Set title, author and date
-\title{Factorization Algebras and Factorization Homology on Stratified Spaces}
+\title{\sc Good Covers of Stratified Spaces}
 \author{Aleksandar Ivanov, Ödül Tetik}
@@
 
-\section{Factorization Algebras}\label{ch:fact_alg}
+\tableofcontents
 
-\subsection{Definition of Factorization Algebras}
-    We fix a symmetric monoidal $\infty$-category $\catC$ that is $\otimes$-presentable to serve as the target $\infty$-category.
+\section{Theorem}
+
+\begin{theorem}
+    Every stratified manifold has a good cover.
+\end{theorem}
+
+\subsection{Riemannian Metrics}
+
+We do not claim that this is the most general structure that deserves the name `Riemannian metric' on a stratified space.
+This is why we opt to add the adjective `tame' to the name.
+Whatever that most general definition of a Riemannian metric is it should certainly include, as an example, the structure that we consider here.
+For the purposes of defining good covers this restricted structure is enough.
+
+\begin{remark}
+    Recall that, by ......., every stratum of a stratified manifold is a smooth manifold.
+Furthermore, by ......., every stratum has a tubular neighborhood in the stratified manifold that is characterized by the link.
+\end{remark}
+
+As a preliminary, we consider the construction of a Riemannian metric on a stratified manifold of depth 1.
+The general construction, that we will describe in ......, proceeds by induction on this case.
 
 \begin{definition}
-    Let $X$ be a topological space.
-We regard $\opens[s](X)$ as a multicategory (and consequently as an $\infty$-operad) whose objects are the open sets of $X$, and through the assignment of a unique multi-morphism from $\{U_i\}_{i \in I}$ to $U$ if the $U_i$ are pairwise disjoint and if $\bigcup_{i \in I} U_i \subset U$.
-A \emph{prefactorization algebra $F$ on $X$ with values in $\catC$} is an algebra in $\catC$ over this $\infty$-operad
+    Let $M$ be a stratified manifold of depth 1, so that $M_0$ is its lower stratum, $M_1$ is its higher one, and the link is $M_0 \twoheadleftarrow{\pi} L \xhookrightarrow{\iota} M_1$.
+A \emph{tame Riemannian metric} $g$ on $M$ is prescribed by Riemannian metrics $g_0$ and $g_1$ on the respective strata such that under the canonical isomorphism
     %
     \begin{equation}
-        F \in \alg{\opens[s](X)}(\catC).
+        \mathsf{T}L \cong \iota^*\mathsf{T}M_1 \oplus \mathsf{T}M_0 \oplus \underbar{\mathbb{R}}
+    \end{equation}
+    %
+    the pullback metric $\iota^* g_1$ on the link decomposes as
+    %
+    \begin{equation}
+        (r^2 g_1, g_0, dr^2).
     \end{equation}
@@
 
-\begin{remark}\label{rem:unpack_pfac_def}
-    Let's unwind the above definition to understand the underlying data needed to define a prefactorization algebra.
-On the level of objects, for every open set $U$ we need to assign an object $F(U) \in \catC$.
-On the level of morphisms, given a pairwise disjoint set of opens $\{U_i\}_{i \in I}$ and an open $U$, such that the $U_i$ all lie in $U$ we need to assign a morphism in $\catC$
+\begin{definition}\label{def:Riem_met_on_strat}
+    A tame Riemannian metric on a stratified manifold is ... 
+\end{definition}
+
+\begin{example}
+    If a stratified manifold $M$ is such that it has an underlying smooth manifold $\bar{M}$, like in the case of stratified manifolds created through a filtration of closed subsets, then a Riemannian metric $g_{\bar{M}}$ on $\bar{M}$ provides the data of a tame Riemannian metric on the stratified manifold $M$, as in definition \Cref{def:Riem_met_on_strat}.
+Namely, .......
+\end{example}
+
+\begin{definition}
+    Let $\gamma: [0,1] \xrightarrow{} M$ be a curve in the stratified manifold $M \xrightarrow{} P$, and let $M$ be equipped with a tame Riemannian metric. The length of $\gamma$ is defined to be
     %
     \begin{equation}
-        \bigotimes_{i \in I} F(U_i) \xrightarrow{F(\{U_i\},U)} F(U).
+        \mathrm{len}_{g}(\gamma) := \sum_{p \in P} \mathrm{len}_{g_p} (\gamma|_{M_p}),
     \end{equation}
     %
-    As the notation suggests and the operadic symmetry condition guarantees, the maps $F(\{U_i\},U)$ only depend on the set of $U_i$ and not on any particular order of the $U_i$, which is also allowed on the left-hand side by the symmetric monoidal structure of $\catC$.
-Furthermore, the operadic associativity condition imposes that given pairwise disjoint $\{U_i\}_{i \in I}$ that all lie in $U$, and for each $i \in I$, pairwise disjoint $\{ V_{i, j}\}_{j \in J_i}$ that all lie in $U_i$, there is a commutative diagram in $\catC$
-    %
-    \begin{equation}
-        \begin{tikzcd}
-            \bigotimes\limits_{(i,j)} F(V_{i,j}) \arrow[rd, shorten <=-2ex, "\bigotimes\limits_{i} F(\{V_{i, j}\} {,} U_i)"'] \arrow[rr, "F( \{V_{i, j}\} {,} U)"] &   & F(U) \\
-            & \bigotimes\limits_{i} F(U_i) \arrow[ru, "F( \{U_i \} {,} U)"'] &,          
-        \end{tikzcd}
-    \end{equation}
-    %
-    where the $(i,j)$ tensor product runs over all possible pairs $i \in I$ and $j \in J_i$.
-Finally, the operadic unitarity condition actually tells us that the morphisms $F(\{U\}, U)$ are equivalent to the identity morphism.
-
-    We also get out that an algebra morphism $\phi: F \rightarrow G$ is simply a family of maps $\phi(U): F(U) \rightarrow G(U)$ for each open set $U$, such that it respects the operations of the algebra.
-Namely, for each multi-morphism $\{ U_i \}_{i \in I} \rightarrow U$ there is a commuting square
-    %
-    \begin{equation}\label{cd:fa_morphisms}
-        \begin{tikzcd}[row sep=large, column sep = large]
-            \bigotimes\limits_{i \in I} F(U_i) \arrow[r, "F(\{ U_i\} {,} U)"] \arrow[d, "\bigotimes\limits_{i \in I} \phi(U_i)"'] & F(U) \arrow[d, "\phi(U)"] \\
-            \bigotimes\limits_{i \in I} G(U_i) \arrow[r, "G(\{ U_i\} {,} U)"'] & G(U).
-        \end{tikzcd}
-    \end{equation}
-\end{remark}
-
-We endow the poset $\opens[r](X)$ with a Grothendieck topology called the \emph{Weiss} Grothendieck topology \cite{weiss1999}.
-In this topology a sieve $\mathscr{U} \subset \opens[r](X)_{/U}$ on $U$ is a covering sieve if for each finite subset $S \subset U$, there is an object $(e: V \rightarrow U) \in \mathscr{U}$ for which $S \subset e(V)$.
-In other words, a family $\{ V_i \rightarrow U\}_{i \in I}$ is a Weiss cover of $U$ if every set of finitely many points in $U$ is contained in some $V_i$.
-Contrast this with the standard Grothendieck topology on the poset of opens $\opens[r](X)$, in which instead of a finite set we have a one-element set.
-Thus, every Weiss cover is a cover in the standard sense, but not necessarily the other way around.
-
-\begin{definition}
-    The $\infty$-category of \emph{$\catC$-valued Weiss (homotopy) cosheaves on $X$} is the full $\infty$-subcategory
-    %
-    \begin{equation}
-        \csheaves[W]_{X}(\catC) \subset \mathsf{Fun}(\opens[r](X), \catC),
-    \end{equation}
-    %
-    of the $\infty$-category of copresheaves, consisting of those functors $F: \opens[r](X) \rightarrow \catC$ for which, for each Weiss covering sieve $\mathscr{U} \subset \opens[r](X)_{/U}$, the canonical functor
-    %
-    \begin{equation}
-        \mathscr{U}^{\vartriangleright} \rightarrow \opens[r](X)_{/U} \rightarrow \opens[r](X) \xrightarrow{F} \catC,
-    \end{equation}
-    %
-    where $\mathscr{U}^{\vartriangleright} \rightarrow \opens[r](X)_{/U}$ is the functor from the colimit cone that assigns $U$ to the colimit object, is a colimit diagram.
+    the sum of the lengths in each stratum. If the metric is clear from context we will drop the subscript notation.
 \end{definition}
 
-\begin{remark}
-    The category $\opens[r](X)$ can be replaced with any other category that supports an analogue of the Weiss Grothendieck topology.
-In the case of (stratified) manifolds, $\opens[r](X)$ is already the same as $\mfld[r]_{/X}$, be we could just as well define Weiss cosheaves on $\mfld[r]$, i.e.
-$\csheaves[W](\mfld[r], \catC)$.
-If we're working with the $\infty$-categories $\mfld$ or $\mfld_{/X}$, then we define cosheaves on them through the pullback
-    %
-    \begin{equation}
-        \begin{tikzcd}
-            \csheaves[W] (\mfld, \catC) \arrow[dr, phantom, "\ulcorner", very near start] \arrow[r] \arrow[d] & \mathsf{Fun}(\mfld, \catC) \arrow[d] \\
-            \csheaves[W] (\mfld[r], \catC) \arrow[r] & \mathsf{Fun}(\mfld[r], \catC),
-        \end{tikzcd}
-    \end{equation}
-    %
-    and similarly for the relative case $\mfld_{/X}$.
-\end{remark}
+\begin{lemma}\label{lem:length_space}
+    Let $(M,g)$ be a stratified manifold with a tame Riemannian metric.
+Then $M$ can be made into a length space, by equipping it with the intrinsic length metric $d_g$, so that the distance between two points is the infimum of the lengths of admissible curves joining them.
+\end{lemma}
 
-\begin{definition}
-    The $\infty$-category of \emph{($\catC$-valued) factorization algebras on $X$} is the full $\infty$-subcategory of $\alg{\opens[s](X)}$ as in the pullback
-    %
-    \begin{equation}
-        \begin{tikzcd}
-            \falg_X (\catC) \arrow[dr, phantom, "\ulcorner", very near start] \arrow[r] \arrow[d] & \alg{\opens[s](X)}(\catC) \arrow[d] \\
-            \csheaves[W]_X(\catC) \arrow[r] & \mathsf{Fun}(\opens[r](X), \catC).
-        \end{tikzcd}
-    \end{equation}
-\end{definition}
+\begin{proposition}
+    Let $(M, g)$ be a connected stratified manifold with a tame Riemannian metric. Then every two points of $M$ can be connected by a minimizing curve.
+\end{proposition}
 
 \begin{proof}
-    The previous definition implies that the top horizontal functor is fully faithful, which is something we need to prove.
-The bottom horizontal functor is fully faithful, by the definition of cosheaf, and the right vertical functor forgets the operations with arity higher than $1$.
-The key observation is that a Weiss cover is pairwise disjoint only when it consists of a single subset.
-Thus, the cosheaf condition does not affect the algebra morphisms and an equivalence of morphism spaces is trivial to find, namely one is given by the identity map.
+    By \Cref{lem:length_space}, $(M,d_g)$ is a length space, where $d_g$ is the intrinsic metric generated by the tame Riemannian metric $g$.
+By virtue of being a stratified manifold it is also a locally compact topological space.
+Then using the Hopf--Rinow--Cohn-Vossen theorem .......
+for a locally compact length space, and its immediate corollaries, we know that what we need to show is that every closed and bounded subset of $M$ is compact.........
 \end{proof}
 
-All of our definitions above are valid for all topological spaces, so in particular, also the stratified spaces we introduced at the beginning.
-For the next definition of locally constant factorization algebras though, it will be important to specify more information about the space.
-In other words, they will capture information about the stratification.
-
-\begin{definition}
-    The $\infty$-category of locally constant Weiss cosheaves on a stratified manifold $M$ (or, equivalently, on $\mfld[r]_{/M}$) is the full $\infty$-subcategory
-    %
-    \begin{equation}
-        \csheaves[W, lc]_M (\catC) \subset \csheaves[W]_M (\catC),
-    \end{equation}
-    %
-    of those Weiss cosheaves whose underlying functor $F: \bsc_{/M} \xrightarrow{} \catC$ satisfies
-    %
-    \begin{equation}
-        f(U) \simeq f(V) \Rightarrow F(U) \simeq F(V),
-    \end{equation}
-    %
-    for all $U, V \in \bsc_{/M}$, where $f: \bsc_{/M} \xrightarrow{} \bsc$ denotes the forgetful functor.
-\end{definition}
-
-\begin{remark}
-    Thus, a functor is locally constant if it takes open embeddings of basics $V \xhookrightarrow{} U$, with equivalent stratifications to equivalences in $\catC$.
-We emphasize this last point about stratification; the disks have to have equivalent stratifications inherited from the stratified space.
-In the case of $\hoint$, for example, open embeddings like $(a, b) \rightarrow \left[0, c\right)$, for $0 \leq a < b \leq c$, would \emph{not} be taken to equivalences since the disks have different stratifications.
-\end{remark}
-
-\begin{remark}
-    Since being locally constant according to the previous definition is only a property of the underlying functor the definition can easily be used to define locally constant prefactorization algebras too.
-\end{remark}
-
-\begin{definition}
-    The $\infty$-category $\lcfa_M (\catC)$ of \emph{locally constant factorization algebras on a stratified manifold $M$ valued in $\catC$} is the full $\infty$-subcategory of $\falg_M (\catC)$ as in the pullback
-    %
-    \begin{equation}
-        \begin{tikzcd}
-            \lcfa_M (\catC) \arrow[dr, phantom, "\ulcorner", very near start] \arrow[r] \arrow[d] & \falg_M (\catC) \arrow[d] \\
-            \csheaves[W, lc]_M (\catC) \arrow[r] & \csheaves[W]_M (\catC).
-        \end{tikzcd}
-    \end{equation}
-\end{definition}
-
-\begin{remark}\label{rem:sym_mon_inheritance}
-    The $\infty$-categories of factorization algebras of all varieties acquire a symmetric monoidal structure from the symmetric monoidal structure of $\catC$ pointwise
-    %
-    \begin{equation}
-        (F \otimes G)(U) = F(U) \otimes G(U).
-    \end{equation}
-    %
-    The only subtlety is the cosheaf condition, where the symmetric monoidal structure is induced only if we also take into account that in $\catC$ colimits commute with its symmetric monoidal structure.
-
-    The existence of colimits is also inherited from $\catC$ pointwise through the collection of evaluation functors $\{ \mathsf{ev}_U: \falg_X (\catC) \rightarrow \catC \}$, one for each open $U \subset X$.
-\end{remark}
-
-\subsection{The \texorpdfstring{$\infty$-}{infinity-}operad of Factorization Algebras}
-
-Now that we have introduced all the varieties of factorization algebras, it's a natural and useful question to ask what the $\infty$-operad governing them is.
-For prefactorization algebras, the answer comes by definition, but this is not the case for factorization algebras, locally constant or not.
-We will be working in the generality of stratified manifolds, and all our results in this section will come in pairs, one for the locally constant case and one not.
-We call the results in the not-necessarily-locally-constant case corollaries since their proofs will be obvious from the proofs of the statements in the locally constant case.
-To connect factorization algebras to the theory of algebras over an $\infty$-operad we will work in two steps.
-First we have the following results:
-%
-\begin{proposition}\label{prop:fh_disk_to_lcfa}
-    Given a stratified manifold $M$ factorization homology provides a functor
-    %
-    \begin{equation}
-        \int : \alg{\disk_{/M}} (\catC) \xrightarrow{\ \ \ \ } \lcfa_M (\catC)
-    \end{equation}
-    %
-    between the $\infty$-categories of $\disk_{/M}$-algebras and locally constant factorization algebras $\lcfa_M$.
-\end{proposition}
-%
-\begin{corollary}\label{cor:fh_disk_to_falg}
-    Given a stratified manifold $M$ factorization homology provides a functor
-    %
-    \begin{equation}
-        \int: \alg{\disk[r]_{/M}} (\catC) \xrightarrow{\ \ \ \ } \falg_{M} (\catC).
-    \end{equation}
-\end{corollary}
-
-The second step is then showing that the functors constructed above are equivalences, which we summarize in the following results:
-%
-\begin{theorem}\label{thm:disk_alg=lcfa}
-    For each stratified manifold $M$, the previously constructed factorization homology functor provides an equivalence of $\infty$-categories
-    %
-    \begin{equation}
-        \alg{\disk_{/M}} (\catC) \xrightarrow[\int]{\ \ \simeq \ \ } \lcfa_M (\catC)
-    \end{equation}
-    %
-    between $\disk_{/M}$-algebras and locally constant factorization algebras on $M$.
-Equivalently, the $\infty$-operad governing locally constant factorization algebras can be taken to be $\disk_{/M}$.
-\end{theorem}
-%
-\begin{corollary}\label{cor:disk_alg=falg}
-    The $\infty$-operad governing factorization algebras on a stratified manifold $M$ can be taken to be $\disk[r]_{/M}$,
-    %
-    \begin{equation}
-        \alg{\disk[r]_{/M}} (\catC) \xrightarrow[\int]{\ \ \simeq \ \ } \falg_M (\catC).
-    \end{equation}
-\end{corollary}
-%
-The reason for the phrasing in these results is that, technically speaking, equivalence of the $\infty$-categories of algebras does not imply equivalence of the underlying $\infty$-operads.
-However since we only defined (locally constant) factorization algebras at the level of algebras and not at the level of $\infty$-operads, we can take the operadic definition as the basic one, and interpret the results as connecting this to the classical definition.
-
-In the service of working towards proofs of all of these results we first have to pause and develop some necessary technically results regarding Weiss covers and preservation of colimits, as well as record a known fact about the relative versions of the $\infty$-operads in play.
-We start with this fact first.
-
-\begin{lemma}\label{lem:double_slice}
-    Every open embedding $e: N \xhookrightarrow{} M$ induces an equivalence of $\infty$-categories
-    %
-    \begin{equation}
-        (\mfld_{/M})_{/e} \simeq \mfld_{/N}.
-    \end{equation}
-    %
-    The same holds for $\mfld[r]$, as well as, $\disk$ and $\disk[r]$.
-\end{lemma}
-
-\begin{lemma}\label{lem:weiss_to_ordinary}
-    Let $M$ be a topological space with a sieve $\mathscr{U}$. The following are equivalent:
-    %
-    \begin{enumerate}
-        \item $\mathscr{U}$ is a Weiss sieve of $M$,
-        \item for all $n \geq 0$, the smallest sieve containing $\{ \mathrm{Conf}_n(U)_{\Sigma_n} \xhookrightarrow{} \mathrm{Conf}_n(M)_{\Sigma_n} \mid U \in \mathscr{U} \}$ is a covering sieve of the unordered configuration space $\mathrm{Conf}_n(M)_{\Sigma_n}$ of $n$ points in $M$.
-    \end{enumerate}
-\end{lemma}
-
-\begin{proof}
-    In the forward direction, let $[(x_1, \dots, x_n)] \in \mathrm{Conf}_n(M)_{\Sigma_n}$ be an equivalence class of $n$ points under the action of the symmetric group.
-By definition of Weiss sieve, there is a $U \in \mathscr{U}$ such that $\{x_1, \dots, x_n\} \subset U$.
-Since none of the points are the same this means that $(x_1, \dots, x_n) \in U^{\times n}$, and subsequently that $(x_1, \dots, x_n) \in \mathrm{Conf}_n(U)$.
-Taking quotients we get that $[(x_1, \dots, x_n)] \in \mathrm{Conf}_n(U)_{\Sigma_n}$.
-Since $\mathrm{Conf}_n(U)_{\Sigma_n}$ is open in the topology of $\mathrm{Conf}_n(M)_{\Sigma_n}$, the collection of these form a covering sieve.
-
-    In the opposite direction, let $S \subset M$ be a finite set with cardinality $|S| = n$.
-Naming its elements $x_1, \dots, x_n$ in an arbitrary order that will not matter because of the $\Sigma_n$ quotient, we get the $[(x_1, \dots, x_n)] \in \mathrm{Conf}_n(M)_{\Sigma_n}$.
-By assumption there exists a $U \in \mathscr{U}$ such that $[(x_1, \dots, x_n)] \in \mathrm{Conf}_n(U)_{\Sigma_n}$.
-In particular, this means that $(x_1, \dots, x_n) \in U^{\times n}$, or in other words that $x_i \in U$ for all $1 \leq i \leq n$.
-This implies that $\mathscr{U}$ satisfies the Weiss property.
-\end{proof}
-
-\begin{lemma}\label{lem:gluing_disk/M/e}
-    A Weiss sieve $\mathscr{U} \subset (\mfld[r]_{/M})_{/e}$ canonically determines a morphism
-    %
-    \begin{equation}
-        \mathsf{colim} \big( \mathscr{U} \xrightarrow{} \mfld[r]_{/M} \xrightarrow{\mathsf{Hom}_{\mfld_{/M}}(\cdot, -)} \mathsf{PShv}(\disk_{/M}) \big) \xrightarrow{\ \ \simeq \ \ } \mathsf{Hom}_{\mfld_{/M}}(\cdot, e)
-    \end{equation}
-    of presheaves over $\disk_{/M}$, which moreover, is an equivalence.
-\end{lemma}
-
-\begin{proof}
-    The morphism is determined by the universal property of the colimit. The components of the morphism of presheaves are given by
-    %
-    \begin{equation}
-        \mathsf{colim} \big( \mathscr{U} \xrightarrow{} \mfld[r]_{/M} \xrightarrow{\mathsf{Hom}_{\mfld_{/M}}(\iota, -)} \mathsf{Sp} \big) \xrightarrow{\ \ \ \ \ } \mathsf{Hom}_{\mfld_{/M}}(\iota, e),
-    \end{equation}
-    %
-    for each $\iota \in \disk_{/M}$, an open embedding of disks in $M$, and these morphisms are now maps of spaces which we want to show are equivalences.
-We now study the hom--spaces appearing above.
-By definition of the slice $\infty$-category, the hom--spaces are given as the homotopy fibers
-    %
-    \begin{equation}
-        \begin{tikzcd}
-            \mathsf{Hom}_{\mfld_{/M}} (\iota, e) \arrow[d] \arrow[r] & \mathsf{Hom}_{\mfld}(D, N) \arrow[d, "e^*"] \\
-            * \arrow[r, "\{\iota\}"] & \mathsf{Hom}_{\mfld}(D, M),
-        \end{tikzcd}
-    \end{equation}
-    %
-    where we have fixed the notation $\iota: D \xhookrightarrow{} M$ and $e: N \xhookrightarrow{} M$, for the domains of these maps.
-We further establish the notation that for each isomorphism class of basics $[B]$, the fixed $D$ has $i_{[B]}$-many disks of type $[B]$.
-With this notation in hand, by the characterization of the maximal $\infty$-subgroupoid of $\disk_{/M}$ \cite[Lem.2.21]{aft_fhstrat} for example, we know that
-    %
-    \begin{equation}
-        \mathsf{Hom}_{\mfld}(D, M) \simeq \coprod_{[B]} \mathrm{UConf}_{i_{[B]}}(M_{[B]}),
-    \end{equation}
-    %
-    where the notation $M_{[B]}$ denotes the $[B]$-stratum of $M$ (see \cite[Prop.4.4.7]{aft_localstrut}).
-We also note that under these equivalences the map $e^*$ is given by $\coprod_{[B]} \mathrm{UConf}_{i_{[B]}}(e_{[B]})$, which is even an open inclusion.
-Thus, the hom--spaces of the slice $\infty$-category are given as
-    %
-    \begin{equation}
-        \mathsf{Hom}_{\mfld_{/M}} (\iota, e) \simeq \coprod_{[B]} \mathsf{Fib}_\iota^{[B]}(e),
-    \end{equation}
-    %
-    where $\mathsf{Fib}_\iota^{[B]}(e)$ is defined as the homotopy fiber
-    %
-    \begin{equation}
-        \begin{tikzcd}
-            \mathsf{Fib}_\iota^{[B]}(e) \arrow[d] \arrow[r] & \mathrm{UConf}_{i_{[B]}}(N_{[B]}) \arrow[d, "\mathrm{UConf}_{i_{[B]}}(e_{[B]})"] \\
-            * \arrow[r, "\{\iota_{[B]}\}"] & \mathrm{UConf}_{i_{[B]}}(M_{[B]}),
-        \end{tikzcd}
-    \end{equation}
-    %
-    where, by slight abuse, we denoted the point over which the fiber lies with $\iota_{[B]}$ as well.
-With all of this notation in place, and by switching the places of the colimits, what we want to show is that the canonical maps
-    %
-    \begin{equation}
-        \mathsf{colim} \big( \mathscr{U} \xrightarrow{} \mfld[r]_{/M} \xrightarrow{\mathsf{Fib}_{\iota}^{[B]}(-)} \mathsf{Sp} \big) \xrightarrow{\ \ \ \ \ } \mathsf{Fib}_{\iota}^{[B]}(e),
-    \end{equation}
-    %
-    are equivalences for every $\iota$ and every $[B]$.
-Using \cite[Prop.A.3.2]{lurie_ha}, a sufficient condition for these maps to be equivalences is for the composition $\mathscr{U} \xrightarrow{} \mfld[r]_{/M} \xrightarrow{\mathsf{Fib}_{\iota}^{[B]}(-)} \mathsf{Sp}$ to be a covering sieve of $\mathsf{Fib}_{\iota}^{[B]}(e)$.
-To exhibit such a property we pick a particular model for the homotopy fiber $\mathsf{Fib}_{\iota}^{[B]}(e)$, namely
-    %
-    \begin{equation}
-        \widetilde{\mathsf{Fib}_{\iota}^{[B]}}(N) := \big( \mathsf{P}(\mathrm{UConf}_{i_{[B]}}(M_{[B]})) \times \mathrm{UConf}_{i_{[B]}}(N_{[B]}) \big) / (s (p) = \iota_{[B]}, t (p) = e(x)),
-    \end{equation}
-    %
-    the space of paths in $\mathrm{UConf}_{i_{[B]}}(M_{[B]})$ that start at $\iota_{[B]}$ and end at a point $x$ in $\mathrm{UConf}_{i_{[B]}}(N_{[B]})$.
-With this model, for each $(U \xhookrightarrow{} N) \in \mathscr{U} \subset (\mfld[r]_{/M})_{/e} \simeq \mfld[r]_{/N}$ (by \Cref{lem:double_slice}) we get an open inclusion
-    %
-    \begin{equation}
-        \widetilde{\mathsf{Fib}_{\iota}^{[B]}}(U) \xhookrightarrow{\ \ \ \ } \widetilde{\mathsf{Fib}_{\iota}^{[B]}}(N),
-    \end{equation}
-    %
-    and we're trying to show that the collection $\mathscr{V}_{\iota}^{[B]}$ of these is a cover.
-
-    Given a Weiss cover $\mathscr{U}$ on $N$ we can restrict it to a Weiss cover $\mathscr{U}_{[B]}$ of $N_{[B]}$ by intersecting.
-The statement of \Cref{lem:weiss_to_ordinary} is that we can build an ordinary cover $\mathscr{U}_{i_{[B]},[B]}$ of $\mathrm{UConf}_{i_{[B]}}(N_{[B]})$.
-$\mathscr{V}_{\iota}^{[B]}$ is a cover if for any $p \in \widetilde{\mathsf{Fib}_{\iota}^{[B]}}(N)$ we can find an open $\widetilde{\mathsf{Fib}_{\iota}^{[B]}}(U)$ that contains it.
-But this is indeed the case, because looking at the target $t(p)$ of the path $p$, we get $t(p) \in \mathrm{UConf}_{i_{[B]}}(N_{[B]})$, and we know that there exists a $U \in \mathscr{U}$ such that $\mathrm{UConf}_{i_{[B]}}(U_{[B]})$ covers $t(p)$ and subsequently also that $\widetilde{\mathsf{Fib}_{\iota}^{[B]}}(U)$ covers $p$.
-\end{proof}
-
-A suggestion regarding the following lemma about preservation of colimits is sketched out in \cite{rezk2023lan}.
-%
-\begin{lemma}\label{lem:Lan_preserve_colim}
-    Let $F: \mathscr{D} \xrightarrow{} \catC$ and $\iota: \mathscr{D} \xrightarrow{} \mathscr{M}$ be functors of $\infty$-categories, where $\mathscr{D}$ is essentially small, while $\mathscr{M}$ and $\catC$ are locally small and cocomplete.
-Let $L_{\iota} F: \mathscr{M} \xrightarrow{} \catC$ be the left Kan extension of $F$ along $\iota$.
-$L_{\iota} F$ preserves a given colimit if, and only if, the restricted Yoneda embedding
-    %
-    \begin{align}
-        T_{\iota}: \mathscr{M} \xrightarrow{\ y_{\mathscr{M}} \ } \mathsf{PShv}(\mathscr{M}) \xrightarrow{\ \iota^* \ } \mathsf{PShv}(\mathscr{D}) 
-    \end{align}
-    %
-    does so.
-\end{lemma}
-
-\begin{proof}
-    We use the standard notation $y_{\mathscr{X}}=h_\bullet\colon\mathscr{X}\to\mathsf{PShv}(\mathscr{X})$ for `the' covariant Yoneda embedding of a locally small $\infty$-category $\mathscr{X}$ (see \cite[\href{https://kerodon.net/tag/03NF}{03NF},\href{https://kerodon.net/tag/03N2}{03N2}]{lurie_kerodon}).
-First, note that a left Kan extension of type
-    %
-    \begin{equation}
-        L_{y_{\mathscr{D}}}F \colon \mathsf{PShv}(\mathscr{D}) \xrightarrow{\ \ \ \ } \mathscr{C}
-    \end{equation}
-    %
-    preserves colimits as a consequence of \cite[\href{https://kerodon.net/tag/03WH}{03WH}]{lurie_kerodon}. Next, we claim that there is an equivalence
-    %
-    \begin{equation}\label{WZUZC5F}
-        L_{\iota}F \simeq L_{y_{\mathscr{D}}}F \circ L_{\iota}y_{\mathscr{D}}
-    \end{equation}
-    %
-    as functors $\mathscr{M} \to \mathscr{C}$. Indeed, consider the diagram
-    % 
-    \begin{equation}
-        \begin{tikzcd}[sep = large]
-            & \mathscr{D}\ar[dl,"{\iota}"']\ar[dr,"{F}"]\ar[d,"{y_{\mathscr{D}}}"]\\
-            \mathscr{M}\ar[rr,bend right=40,"{L_{\iota}F}"']\ar[r,"{L_{\iota}y_{\mathscr{D}}}"'] &[4em] \mathsf{PShv}(\mathscr{D})\ar[r,"{L_{y_{\mathscr{D}}}F}"'] & \mathscr{C},
-        \end{tikzcd}
-    \end{equation}
-    %
-    and note that by \cite[\href{https://kerodon.net/tag/03W9}{03W9},\href{https://kerodon.net/tag/03WH}{03WH}]{lurie_kerodon} there is an equivalence (actually even an isomorphism) $L_{y_{\mathscr{D}}}F \circ y_{\mathscr{D}} \simeq F$ which commutes the right triangle.
-Consequently, using \cite[\href{https://kerodon.net/tag/02YH}{02YH}]{lurie_kerodon}, we have $L_{\iota}F \simeq L_{\iota}(L_{y_{\mathscr{D}}}F \circ y_{\mathscr{D}})$.
-Since $L_{y_{\mathscr{D}}}F$ preserves colimits, we have $L_{\iota}(L_{y_{\mathscr{D}}}F \circ y_{\mathscr{D}})\simeq L_{y_{\mathscr{D}}}F \circ L_{\iota}y_{\mathscr{D}}$, obtaining \Cref{WZUZC5F}.
-
-    Finally, we claim
-    %
-    \begin{equation}\label{D9NQYMT}
-        L_{\iota}y_{\mathscr{D}} \simeq T_{\iota} := \iota^* \circ y_{\mathscr{M}}
-    \end{equation}
-    %
-    as functors $\mathscr{M} \to \mathsf{PShv}(\mathscr{D})$, which will imply the Lemma by \Cref{WZUZC5F}.
-By \cite[\href{https://kerodon.net/tag/03WN}{03WN}]{lurie_kerodon} we have the following diagram in which the triangle commutes
-    %
-    \begin{equation}
-        \begin{tikzcd}
-            \mathscr{M} \arrow[r, "y_{\mathscr{M}}"] & \mathsf{PShv}(\mathscr{M}) \arrow[r, "\iota^*"] \arrow[d, "\top", phantom, very near start] & \mathsf{PShv}(\mathscr{D}) \arrow[ll, "H", bend left] \\
-            & {} & \mathscr{D} \arrow[u, "y_{\mathscr{D}}"'] \arrow[llu, "\iota", bend left]
-            \end{tikzcd},
-    \end{equation}
-    %
-    so that $H$ is a left adjoint to $\iota^* \circ y_{\mathscr{M}}$.
-Being a right adjoint, we can write $\iota^* \circ y_{\mathscr{M}}$ as a left Kan extension, which allows for the following calculation
-    %
-    \begin{equation}
-        \iota^* \circ y_{\mathscr{M}} \simeq L_{H}\mathrm{id}_{\mathsf{PShv}(\mathscr{D})} \simeq L_{H}(L_{y_{\mathscr{D}}} y_{\mathscr{D}}) \simeq L_{H \circ y_{\mathscr{D}}}(\mathscr{D}) \simeq L_{\iota}(y_\mathscr{D}),
-    \end{equation}
-    %
-    where for the second equivalence we used the fact that $y_{\mathscr{D}}$ is a dense functor \cite[\href{https://kerodon.net/tag/03W2}{03W2}]{lurie_kerodon} (using the definition of dense functor as in \cite[\href{https://kerodon.net/tag/03VP}{03VP}]{lurie_kerodon}) and in the third equivalence we used \cite[\href{https://kerodon.net/tag/031M}{031M}]{lurie_kerodon}.
-\end{proof}
-
-\begin{proof}[Proof of {\Cref{prop:fh_disk_to_lcfa}}]
-    We adopt a proof strategy similar to \cite[prop.3.14]{af_primer}.
-Unlike there, we work in the relative case of $\disk_{/M}$ instead of $\disk(\bstr)$.
-Since the $\infty$-category of factorization algebras is defined as a pullback, we will look for a commutative diagram involving $\alg{\disk_{/M}}$, so that, by the universal property of the pullback, we get the stated functor.
-
-    We first observe that, by definition, the $\infty$-operad $\opens(M) := \mfld[r]_{/M}$. There are clear functors of $\infty$-operads
-    %
-    \begin{equation}
-        \disk_{/M} \xhookrightarrow{\ \ \ } \mfld_{/M} \xleftarrow{\ \ \ } \mfld[r]_{/M}.
-    \end{equation}
-    %
-    At the level of algebras over them, they give rise to the commutative diagram
-    %
-    \begin{equation}
-        \begin{tikzcd}
-            \alg{\disk_{/M}} (\catC) \arrow[d] & \alg{\mfld_{/M}} (\catC) \arrow[l] \arrow[r] \arrow[d] & \alg{\opens(M)} (\catC) \arrow[d] \\
-            \mathsf{Fun}(\disk_{/M}, \catC) & \mathsf{Fun}(\mfld_{/M}, \catC) \arrow[l] \arrow[r] & \mathsf{Fun}(\opens(M), \catC),
-        \end{tikzcd}
-    \end{equation}
-    %
-    where the vertical arrows are forgetful functors. Factorization homology as a left Kan extension gives one the adjoints indicated below
-    %
-    \begin{equation}
-        \begin{tikzcd}[row sep = large, column sep = large]
-            \alg{\disk_{/M}} (\catC) \arrow[r, bend left=10, "\int"] \arrow[d] & \alg{\mfld_{/M}} (\catC) \arrow[l, bend left=10] \arrow[r] \arrow[d] & \alg{\opens(M)} (\catC) \arrow[d] \\
-            \mathsf{Fun}(\disk_{/M}, \catC) \arrow[r, bend left=10, "\int"] & \mathsf{Fun}(\mfld_{/M}, \catC) \arrow[l, bend left=10] \arrow[r] & \mathsf{Fun}(\opens(M), \catC).
-        \end{tikzcd}
-    \end{equation}
-    %
-    A result found in \cite[thm.1.2.5]{aft_localstrut} (where they use slightly different notation and call locally constant sheaves constructible) gives us the equivalence
-    %
-    \begin{equation}
-        \csheaves[W](\mfld_{/M}, \catC) \simeq \csheaves[W, lc](\mfld[r]_{/M}, \catC) =: \csheaves[W, lc]_M(\catC),
-    \end{equation}
-    %
-    which at the level of underlying functors, is exactly the restriction along the functor $\opens(M) \xrightarrow{} \mfld_{/M}$, so that we can append this to our commutative diagram
-    %
-    \begin{equation}
-        \begin{tikzcd}[row sep = large, column sep = large]
-            \alg{\disk_{/M}} (\catC) \arrow[r, bend left=10, "\int"] \arrow[d] & \alg{\mfld_{/M}} (\catC) \arrow[l, bend left=10] \arrow[r] \arrow[d] & \alg{\opens(M)} (\catC) \arrow[d] \\
-            \mathsf{Fun}(\disk_{/M}, \catC) \arrow[r, bend left=10, "\int"] \arrow[dr, dashed] & \mathsf{Fun}(\mfld_{/M}, \catC) \arrow[l, bend left=10] \arrow[r] & \mathsf{Fun}(\opens(M), \catC) \\
-            & \csheaves[W](\mfld_{/M}, \catC) \arrow[r, "\simeq"] \arrow[u] & \csheaves[W, lc]_M(\catC) \arrow[u].
-        \end{tikzcd}
-    \end{equation}
-    %
-    If we can find the dashed functor which makes the diagram commute, as indicated above, we would be done with the construction.
-This amounts to showing that the left Kan extension $\int F$ of a functor $F \in \mathsf{Fun}(\disk_{/M}, \catC)$ along $\disk_{/M} \xhookrightarrow{} \mfld_{/M}$ is automatically a Weiss cosheaf.
-By the definition of $\csheaves[W](\mfld_{/M}, \catC)$, this means that the restriction of $\int F$ to $\mathsf{Fun}(\mfld[r]_{/M}, \catC)$ satisfies the cosheaf property for every Weiss sieve $\mathscr{U} \subset (\mfld[r]_{/M})_{/e}$, where $e:N \xhookrightarrow{} M$ is an open embedding.
-Here we notice that for the Weiss property to even make sense, we are implicitly using \Cref{lem:double_slice}, so that the Weiss sieve $\mathscr{U}$ is defined as an $\infty$-subcategory of $\mfld[r]_{/N}$.
-
-    With the Weiss cosheaf property being a statement about preserving colimits, and with $\int F$ being a left Kan extension we are exactly in the situation of \Cref{lem:Lan_preserve_colim}.
-Thus, we only need to show that the functor $T: \mfld_{/M} \xrightarrow{} \mathsf{PShv} (\disk_{/M})$ preserves Weiss colimits.
-Namely, we need to show that there is an equivalence
-    %
-    \begin{equation}
-        \mathsf{colim} \big( \mathscr{U} \xrightarrow{} \mfld[r]_{/M} \xrightarrow{\mathsf{Hom}_{\mfld_{/M}}(\cdot, -)} \mathsf{PShv} (\disk_{/M}) \big) \xrightarrow{\ \ \simeq \ \ } \mathsf{Hom}_{\mfld_{/M}}(\cdot, e),
-    \end{equation}
-    %
-    where on the right-hand side we've used the fact that $\mathscr{U}$ is, in particular, a covering sieve.\footnote{If we also append the straightening--unstraightening construction to $T$, the desired equivalence can be thought of as an equivalence
-    %
-    \begin{equation}
-        \mathsf{colim} (\mathscr{U} \xrightarrow{} \mfld_{/M} \xrightarrow{ (\disk_{/M})_{/-}} \mathsf{RFib}_{\disk_{/M}}) \simeq (\disk_{/M})_{/e}.
-    \end{equation}}
-    %
-    But this is exactly the result of \Cref{lem:gluing_disk/M/e}.
-\end{proof}
-
-\begin{remark}
-    Intuitively, the key idea for the statement and proof is that $\disk[r]_{/N}$ is a basis for the Weiss Grothendieck topology on manifolds.
-This is essentially because for each finite set of points $S \subset N$ we can take disks $\{ D_s \}_{s \in S}$ around each point, by virtue of $N$ being a manifold.
-Subsequently, for each $U_S$ that covers $S$ we can take small enough disks, whose disjoint union will cover $S$ by construction, as well as satisfy $\sqcup_{s \in S} D_s \subset U_S$.
-The proof makes this idea precise, and tells us that we can calculate factorization homology using any Weiss sieve
-    %
-    \begin{equation}
-        \int_M F \simeq \mathsf{colim}(\disk[r]_{/M} \xrightarrow{} \disk_{/M} \xrightarrow{F} \catC)
-        \simeq \mathsf{colim}(\mathscr{U} \xrightarrow{} \disk_{/M} \xrightarrow{F} \catC).
-    \end{equation}
-\end{remark}
-
-The above proof also shows how the ideas that went into defining factorization algebras are not that different from the ideas that went into defining factorization homology.
-Namely, the ideas of Weiss cosheaves and algebras over disks are deeply connected.
-Now that this connection has been explained, the proof of \Cref{thm:disk_alg=lcfa}, which we delve into promptly, is not hard to establish.
-
-\begin{proof}[Proof of {\Cref{thm:disk_alg=lcfa}}]
-    To show essential surjectivity of $\int$, for each $F \in \lcfa_M (\catC)$ we will find an equivalence $\int F| \simeq F$ in $\lcfa_M (\catC)$, with $F|$ to be defined later.
-Since $\lcfa_M (\catC) \xrightarrow{} \alg{\opens(M)}$ is fully faithful, this amounts to finding an equivalence of prefactorization algebras, namely a family of equivalences
-    %
-    \begin{equation}
-        \int_U F| \xrightarrow[\simeq]{\ \ \phi (U) \ \ } F(U),
-    \end{equation}
-    %
-    one for each $(U \xhookrightarrow{} M) \in \mfld[r]_{/M}$, which are natural in $U$ and preserve the multiplicative structure of prefactorization algebras (see \Cref{rem:unpack_pfac_def,cd:fa_morphisms}).
-Since $F$ is a locally constant factorization algebra the functor
-    %
-    \begin{equation}
-        \lcfa_M (\catC) \xrightarrow{} \csheaves[W, lc](\mfld[r]_{/M}, \catC) \simeq \csheaves[W](\mfld_{/M}, \catC) \xrightarrow{} \mathsf{Fun}(\mfld_{/M}, \catC),
-    \end{equation}
-    %
-    which we omit in the notation, allows us to consider $F$ as a functor from $\mfld_{/M}$. Furthermore, since $\disk[r]_{/U}$ is a Weiss sieve we can write
-    %
-    \begin{align}
-        F(U) &\simeq \mathsf{colim} (\disk[r]_{/U} \xrightarrow{} \disk[r]_{/M} \xrightarrow{} \mfld[r]_{/M} \xrightarrow{} \mfld_{/M} \xrightarrow{F} \catC).
-    \end{align}
-    %
-    By consulting the commutative diagram
-    % 
-    \begin{equation}
-        \begin{tikzcd}
-            \disk[r]_{/U} \arrow[d] \arrow[r] & \disk_{/U} \arrow[d] & \\
-            \disk[r]_{/M} \arrow[d] \arrow[r] & \disk_{/M} \arrow[d] \arrow[r, "F|"] & \catC, \\
-            \mfld[r]_{/M} \arrow[r] & \mfld_{/M} \arrow[ru, "F"'] &  
-        \end{tikzcd}
-    \end{equation}
-    %
-    where $F|$ is the restriction of $F$ to disks, and using the fact that $\disk[r]_{/U} \xrightarrow{} \disk_{/U}$ is final (\cite[prop.2.22]{aft_fhstrat}) immediately gives us that
-    %
-    \begin{equation}
-        F(U) \simeq \mathsf{colim} (\disk_{/U} \xrightarrow{} \disk_{/M} \xrightarrow{F|} \catC) \simeq \int_U F|.
-    \end{equation}
-    %
-    Naturality of these equivalences is immediate from the construction because, as already used, each inclusion of open subsets $V \xhookrightarrow{} U$ gives a full subcategory inclusion $\disk[r]_{/V} \xhookrightarrow{} \disk[r]_{/U}$.
-Given this fact, to preserve the multiplicative structure it is enough to show that the following is a commutative diagram
-    %
-    \begin{equation}\label{eq:mult_strut_comm_square}
-        \begin{tikzcd}
-            \otimes_i \int_{U_i} F| \arrow[r, "\simeq"] \arrow[d, "\otimes_i \phi (U_i)"', "\simeq"] & \int_{\sqcup_i U_i} F| \arrow[d, "\phi (\sqcup_i U_i)", "\simeq"']\\
-            \otimes_i F (U_i) \arrow[r, "\simeq"] & F (\sqcup_i U_i),
-        \end{tikzcd}
-    \end{equation}
-    %
-    for each collection of disjoint open sets $\{U_i\}$. This, however, is guaranteed by the equivalences
-    %
-    \begin{equation}
-        \disk[r]_{/\sqcup_i U_i} \xrightarrow{\ \ \simeq \ \ } \bigtimes_i \disk[r]_{/U_i}.
-    \end{equation}
-    %
-    Indeed, the fact that (sifted) colimits commute with the monoidal product on $\catC$ means that, for example in the case of two objects
-    %
-    \begin{align}
-        \mathsf{colim}(K \xrightarrow{F} \catC) \otimes \mathsf{colim}(K' \xrightarrow{F'} \catC) &\simeq \mathsf{colim}(K \xrightarrow{F(-) \otimes \mathsf{colim}(K' \xrightarrow{F'} \catC)} \catC)\notag\\
-        &\simeq \mathsf{colim}(K \xrightarrow{\mathsf{colim}(K' \xrightarrow{F(-) \otimes F'(-)} \catC)} \catC)\notag\\
-        &\simeq \mathsf{colim}(K \times K' \xrightarrow{F \times F'} \catC \times \catC \xrightarrow{- \otimes -} \catC),
-    \end{align}
-    %
-    for any (sifted) indexing $\infty$-categories $K, K'$.
-
-    To show full faithfulness we need to find equivalences of morphism spaces
-    %
-    \begin{equation}
-        \mathsf{Hom}_{\alg{\disk_{/M}} (\catC)} (A, B) \simeq \mathsf{Hom}_{\lcfa_M (\catC)} (\int A, \int B),
-    \end{equation}
-    %
-    for each $A, B \in \alg{\disk_{/M}}$. However, since the functors
-    %
-    \begin{align}
-        &\alg{\disk_{/M}} (\catC) \xrightarrow{\mathsf{f.f.}} \alg{\disk[r]_{/M}} (\catC) &\lcfa_M (\catC) \xrightarrow{\mathsf{f.f.}} \alg{\mfld[r]_{/M}} (\catC)
-    \end{align}
-    %
-    are both fully faithful we are reduced to finding equivalences
-    %
-    \begin{equation}
-        \mathsf{Hom}_{\alg{\disk[r]_{/M}} (\catC)} (A, B) \simeq \mathsf{Hom}_{\alg{\mfld[r]_{/M}} (\catC)} (\int A, \int B).
-    \end{equation}
-    %
-    The existence of these is exactly the requirement that factorization homology in the usual sense is fully faithful, which is part of the statement of \cite[lem.2.17]{aft_fhstrat}.
-\end{proof}
-
-% Generate bibliography
-\newpage
-\printbibliography
-
 \end{document}
